### 2019-01-24 Paper/AgreementAttraction.Rmd
all-update

---
title: 'Agreement Attraction in Turkish: Effects of Nominal and Verbal Plural Morphemes'

author:

- name: Utku Turk
  affilnum: 1
  email: utku.turk@boun.edu.tr

- name: Pavel Logacev 
  affilnum: 1

affiliation:

- affilnum: 1
  affil: Bogazici University, South Campus, John Freely Building, Department of Linguistics, 34342, Istanbul, Turkey

output:

  pdf_document:
    fig_caption: yes
    fig_width: 7
    fig_height: 7
    keep_tex: yes
    number_sections: yes
    template: manuscript.latex
    includes:
      in_header: header.tex

  html_document: null

  word_document: null

documentclass: article
classoption: a4paper
capsize: normalsize
fontsize: 11pt
geometry: margin=1in
linenumbers: yes
spacing: singlespacing
footerdate: yes
bibliography: 
  - references.bib
  - knitcitations.bib
csl: ecology.csl

---

```{r setup, include=FALSE, cache=FALSE, message = FALSE}

library("knitr")

#opts_knit$set(root.dir=normalizePath('../'))

### Chunk options: see http://yihui.name/knitr/options/ ###

## Text results
opts_chunk$set(echo = TRUE, warning = TRUE, message = TRUE, include = TRUE)

## Code decoration
opts_chunk$set(tidy = TRUE, comment = NA, highlight = TRUE)

## Cache
opts_chunk$set(cache = 2, cache.path = "output/cache/")

## Plots
opts_chunk$set(fig.path = "output/figures/")

```

```{r outline, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
Introduction
Recap on what Lago did
My experiment
  Reasoning
  Experiment Details
    Environments
    Items
    Fillers
    Participants
    Exclusions
    Results and Discussions
  ...

```

```{r knitcitations, echo=FALSE, cache = FALSE}
library(knitcitations)
cleanbib()   
cite_options(citation_format = "pandoc")
```

\vspace{2mm}\hrule

In this paper, our objective is to explore the source of agreement attraction effects in Turkish found by @Lago. The interpretation of their finding is complicated by the fact that in their possessive form all head nouns in their stimuli are morphologically ambiguous between possessive and accusative. Due to the mismatch in the frequency of usage of accusative and genitive, which is used as a attractor in this experiment, as a controller, @Lago's findings could potentially be explained with occasional shallow processing. We have replicated @Lago's experiment with unambigious head nouns, and we have found the same agreement attraction effects. However, this may mean that participants may engage in even more shallow processing than we imagined. We postulate that participants solely check for the presence of a *-lAr* morpheme, while largely disregarding the remainder of the sentence. We utilize an experiment design in which we use a relative clause with or without plural agreement on the verb in place of the genitive possessor since both verbal and nominal plural morphemes are the same in Turkish. If participants did, in fact, adopt a superficial processing strategy, we would expect to find a number agreement attraction effect similar in magnitude to @Lago's. However, if number attraction is not an artifact of shallow processing strategies, we should expect to find no number attraction in this experiment.

\vspace{3mm}\hrule

*Keywords*: Turkish, agreement attraction, task effect, shallow processing

\bleft

---
nocite: | 
  @woolford
...

# INTRODUCTION

Attraction errors in production and comprehension of subject-verb agrrement, in which a verb does not agree with the grammatical agreement controller, but with a potential attractors, have been the focal point of many research for quite a long time. In fact, it is still a widely researched are in psycholinguistic studies. Despite the thorough research that has been carried out, studies that have been conducted on agreement attraction in Turkish have been extremely few. In fact, @Lago has been the only study to look into this phenomenon in Turkish. @Lago's study make use of genitive-possessive structures in the subject position, in which the possessive-marked noun is the head of the noun phrase which acts as the grammatical agreement controller, and the genitive noun serves as a potential attractor. In a speeded acceptability judgment study, they found a significant effect of number agreement attraction. However, the interpretation of their finding may be a result of a non-subjecthood cues originating from their use of morphologically ambiguous forms of possessive. In their possessive form all head nouns in their stimuli are ambigiuous between possessive and accusative.

In Turkish, accusative number agreement controllers are extremely rare, while genitive agreement controllers are very frequent. Thus, @Lago's finding could possibly be explained by occasional shallow processing. When all syntactic relations in the sentence were processed fully, the possessive noun should have been identified as the controller. Meanwhile the genitive noun may sometimes have been erroneously identified as the controller during shallow processing, because genitives are more likely to act as agreement controllers than accusatives. A second alternative explanation of @Lago's finding may be the fact that participants may engage in even more shallow processing than outlined above. Participants may have erroneously responded *Yes* on some trials due to (i) the presence of a plural morpheme on a noun (attractor or controller) and (ii) the presence of a plural agreement morpheme on the verb. We speculate that on such trials, participants would have simply tried to check for the presence of such morphemes, while largely disregarding the remainder of the sentence.

We first replicated @Lago's experiment with unambiuous head nouns. To this end, we have revised the items that were used previously, to avoid morphological ambiguity between possessive and accusative forms. The effect found by @Lago replicates with unambiguous nouns as discused in \S 2.

\S 3 discussses the alternative account that posits even more shallow processing as mentioned above and offers a pre-registered experiment using RC attractors with possible outcomes and their indications. Since both nominal and verbal plural morphemes in Turkish take on the same form (*-ler* or *-lar* depending on the phonological environment), we can test this possibility with an experiment, in which we use relative clause with or without plural agreement on the verb in the place of the genitive possessors. An agreement attraction effect similar in magnitude to @Lago's would mean that participants use aforementioned strategies.

\S 4 presents a discussion revolving around possible 
Lastly, \S 5 offers a brief conclusion and presents topics for future researches.

# REPLICATON OF @Lago

In their study, @Lago investigated the comprehension of subject-verb agreement in Turkish-German bilinguals and Turkish monolinguals. They used speeded acceptability judments for the effects of number attraction in Turkish. Their sentences makes us of genitive-possessive constructions in the subject position, where the genitive is the attractor and the possessive is the head noun. They have manipulated the grammaticality of the sentence by changing the plural morphology of the verb, and they also manipulated the plurality of the attractor noun. In grammatical conditions, subject and the verb both bears the singular morphology with no overt morpheme. Moreover, in the ungrammatical conditions the verb bears the overt *-lAr* morpheme whereas the subject is still singular as exemplified below.

\begin{exe}
\ex
\begin{xlist}
\ex \underline{Grammatical, SG attractor} \label{lago1}
\gll \c{S}ark{\i}c{\i}-n{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}\\
singer-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-$\varnothing$\\
\glt The singer's backup vocalist jumped on the stage non-stop.

\ex \underline{Grammatical, PL attractor} \label{lago2}
\gll \c{S}ark{\i}c{\i}-lar-{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}\\
singer-\textsc{pl}-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-$\varnothing$\\
\glt The singer's backup vocalist jumped on the stage non-stop.

\ex \underline{Ungrammatical, PL attractor} \label{lago3}
\gll \c{S}ark{\i}c{\i}-lar-{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}-lar.\\
singer-\textsc{pl}-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-\textsc{3Pl}\\
\glt The singer's backup vocalist jumped on the stage non-stop.

\ex \underline{Ungrammatical, SG attractor} \label{lago4}
\gll \c{S}ark{\i}c{\i}-n{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}-lar.\\
singer-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-\textsc{3Pl}\\
\glt The singer's backup vocalist jumped on the stage non-stop.
\end{xlist}
\end{exe}

They have found a significant effect of number attraction in Turkish ranging between 11%--15% across monolinguals. As seen from the results of statistical analysis in Table (\ref{lagomodel}), acceptability judgments showed an immense effect of grammaticality, and there is also interaction between grammaticality and attractor number which indicates an number attraction effect.

\begin{table}[]
\centering
\begin{tabular}{llcccc}
\hline
    &                                        & \multicolumn{4}{l}{Monolingual Speakers}                                               \\ \cline{3-6} 
    &                                        & $\beta$        & SE            & \emph{z} & \emph{p} \\ \hline
\multicolumn{2}{l}{\textbf{Attraction Task}} &                &               &                           &                           \\
    & Grammaticality                         & \textbf{-5.51} & \textbf{0.33} & \textbf{-16.69}           & \textbf{.000}             \\
    & Attractor Number                       & 0.14           & 0.25          & 0.57                      & .571                      \\
    & Grammaticality x Attractor Number      & \textbf{1.69}  & \textbf{0.53} & \textbf{3.19}             & \textbf{.001}             \\
    & Attractor Number: Ungram conditions    & \textbf{0.94}  & \textbf{0.26} & \textbf{3.68}             & \textbf{.000}             \\
    & Attractor Number: Gram conditions      & -0.79          & 0.52          & -1.51                     & .131                      \\ \hline
\end{tabular}
\caption{Model results for the judgments of monolingual cited from @Lago.}
\label{lagomodel}
\end{table}

According to @Lago's stipulation, Turkish genitive case does not provide a strong cue against subjecthood since it is extremely common to see genitive marked subjects in Turkish embedded clauses, as in example (\ref{gensubj}). Unlike English, genitive case is compatible with the subjecthood in English. Thus, @Lago attributes the robust agreement attraction effects to the case information.

\begin{exe}
\ex \label{gensubj}
\gll k\"{o}y-\"{u} bir haydut-un bas-t{\i}\u{g}-{\i}n-{\i} duy-du-m.\\
village-\textsc{acc} a bandit-\textsc{gen} raid-\textsc{nmlz}-\textsc{3Sg}-\textsc{acc} hear-\textsc{pst}-\textsc{1Sg}\\
\glt I heard that a (certain) robber raided the village. (Adapted from Woolford (2009))
\end{exe}

However, we argue that not only genitive case but also possessive case plays a significant role in delivering the case information. None of the experimental items in @Lago has a head noun which ends with a vowel; thus, all of the possessive markers are morphologically and phonologically ambiguous between the accusative case and the possessive.

## Modifications
## Participants
## Filler Items
## Results and Discussion

# EXPERIMENT 2: RC ATTRACTOR
## Motivation
## Items and Fillers
## Expectations
## Possible Outcomes and Discussion

# DISCUSSION

Discuss.

# CONCLUSIONS

Intro and repeat.

# ACKNOWLEDGEMENTS
We used the statistical language `R` `r citep(citation())` for all our analyses. These were implemented in dynamic rmarkdown documents using `knitr` `r citep(citation("knitr"))` and `rmarkdown` `r citep(citation("rmarkdown"))` packages. All graphs have been done with `ggplot` `r citep(citation("ggplot2"))`. Thank the Mine and Kadir for their student from courses.

# REFERENCES

```{r write_citations, cache=FALSE, include=FALSE}
write.bibtex(file="knitcitations.bib")
```

<div id = "refs"></div>

\eleft

\clearpage

\listoftables

\newpage

```{r Table1, results='asis', echo=FALSE, cache=FALSE}
kable(head(iris), caption = "A glimpse of the famous *Iris* dataset.")
```

\newpage

```{r Table2, results='asis', echo=FALSE, cache=FALSE}
kable(mtcars[10:16, ], caption = "Now a subset of mtcars dataset.")
```

\clearpage

\listoffigures

\newpage

```{r Fig1, echo=FALSE, fig.cap="Just my first figure with a very fantastic caption.", cache=FALSE}
x <- rnorm(100)
y <- jitter(x, 1000)
plot(x, y)
```

\newpage

\blandscape

```{r Fig2, echo=FALSE, fig.cap="Second figure in landscape format.", cache=FALSE}
a <- sort(rnorm(100))
b <- c(rep("Group Small", 35), rep("Group Big", 65))
boxplot(a ~ b)
```

\elandscape

\clearpage

```{r sessioninfo, echo = FALSE, eval = FALSE}
# set eval = FALSE if you don't want this info (useful for reproducibility) to appear 
sessionInfo()
```

### 2019-01-24 Paper/AgreementAttraction.tex
all-update

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Original default rstudio/pandoc latex file
%% upated by @jhollist 09/15/2014
%% inspired by @cboetting https://github.com/cboettig/template and
%% @rmflight blog posts:
%% http://rmflight.github.io/posts/2014/07/analyses_as_packages.html 
%% http://rmflight.github.io/posts/2014/07/vignetteAnalysis.html).  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
\usepackage{graphicx}
% Redefine \includegraphics so that, unless explicit options are
% given, the image width will not exceed the width of the page.
% Images get their normal width if they fit onto the page, but
% are scaled down if they would overflow the margins.
\makeatletter
\def\ScaleIfNeeded{%
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother
\let\Oldincludegraphics\includegraphics
{%
 \catcode`\@=11\relax%
 \gdef\includegraphics{\@ifnextchar[{\Oldincludegraphics}{\Oldincludegraphics[width=\ScaleIfNeeded]}}%
}%
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Agreement Attraction in Turkish: Effects of Nominal and Verbal Plural Morphemes},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{5}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Changes borrowed from @cboettig, added by @jhollist 
% A modified page layout 
\textwidth 6.75in
\oddsidemargin -0.15in
\evensidemargin -0.15in
\textheight 9in
\topmargin -0.5in
\usepackage{lineno} % add 
  \linenumbers % turns line numbering on 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%Packages and layout changes by @jhollist 09/15/2014
\usepackage{ragged2e}
\usepackage[font=normalsize]{caption}
  \usepackage[singlespacing]{setspace}
\usepackage{parskip}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
  \rfoot{\today}
\lfoot{\thepage}
%%Changed default abstract width and added lines
\renewenvironment{abstract}{
  \hfill\begin{minipage}{1\textwidth}
  \rule{\textwidth}{1pt}\vspace{5pt}
  \normalsize
  \begin{justify}
  \bfseries\abstractname\vspace{5pt}
  \end{justify}}
  {\par\noindent\rule{\textwidth}{1pt}\end{minipage}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Agreement Attraction in Turkish: Effects of Nominal and Verbal Plural
Morphemes}
\author{
Utku Turk
Pavel Logacev
}
\date{}
% Allowing for landscape pages
\usepackage{lscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}

% Left justification of the text: see https://www.sharelatex.com/learn/Text_alignment
% \usepackage[document]{ragged2e} % already in the latex template
\newcommand{\bleft}{\begin{flushleft}}
\newcommand{\eleft}{\end{flushleft}}

% multicols
\usepackage{multicol}
\usepackage{paracol}

% enumerated examples
\usepackage{enumitem}

% for linguistic examples &  interlinear glosses
\usepackage{gb4e}
\exewidth{(10.159)}
\noautomath
\let\eachwordone=\it

\usepackage{qtree}

%%Fix tightlist error: https://stackoverflow.com/questions/40438037/tightlist-error-using-pandoc-with-markdown
%%Added 2018-03-26 
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
%%%

\begin{document}
%%Edited by @jhollist 09/15/2014
%%Adds title from YAML
\begin{singlespace}
\begin{center}
\huge Agreement Attraction in Turkish: Effects of Nominal and Verbal Plural
Morphemes
\end{center}
%%Adds Author, correspond email asterisk, and affilnum from YAML
\begin{center}
\large
Utku Turk \textsuperscript{*} \textsuperscript{1} 
Pavel Logacev \textsuperscript{1} 
\end{center}
%%Adds affiliations from YAML
\begin{justify}
\footnotesize \emph{ 
\\*
\textsuperscript{1}Bogazici University, South Campus, John Freely Building, Department of
Linguistics, 34342, Istanbul, Turkey\\*
}
%%Adds corresponding author email(s) from YAML
\newcounter{num}
\setcounter{num}{1}
\\[0.1cm]
\footnotesize \emph{ 
\ifnum\value{num}=1%
\textsuperscript{*} corresponding author:
\fi
\href{mailto:utku.turk@boun.edu.tr}{\nolinkurl{utku.turk@boun.edu.tr}}
\stepcounter{num}
}
\end{justify}
%%Adds date from YAML
\normalsize

\end{singlespace}

\vspace{2mm}\hrule

In this paper, our objective is to explore the source of agreement
attraction effects in Turkish found by Lago (2018). The interpretation
of their finding is complicated by the fact that in their possessive
form all head nouns in their stimuli are morphologically ambiguous
between possessive and accusative. Due to the mismatch in the frequency
of usage of accusative and genitive, which is used as a attractor in
this experiment, as a controller, Lago (2018)'s findings could
potentially be explained with occasional shallow processing. We have
replicated Lago (2018)'s experiment with unambigious head nouns, and we
have found the same agreement attraction effects. However, this may mean
that participants may engage in even more shallow processing than we
imagined. We postulate that participants solely check for the presence
of a \emph{-lAr} morpheme, while largely disregarding the remainder of
the sentence. We utilize an experiment design in which we use a relative
clause with or without plural agreement on the verb in place of the
genitive possessor since both verbal and nominal plural morphemes are
the same in Turkish. If participants did, in fact, adopt a superficial
processing strategy, we would expect to find a number agreement
attraction effect similar in magnitude to Lago (2018)'s. However, if
number attraction is not an artifact of shallow processing strategies,
we should expect to find no number attraction in this experiment.

\vspace{3mm}\hrule

\emph{Keywords}: Turkish, agreement attraction, task effect, shallow
processing

\bleft

\hypertarget{introduction}{%
\section{INTRODUCTION}\label{introduction}}

Attraction errors in production and comprehension of subject-verb
agrrement, in which a verb does not agree with the grammatical agreement
controller, but with a potential attractors, have been the focal point
of many research for quite a long time. In fact, it is still a widely
researched are in psycholinguistic studies. Despite the thorough
research that has been carried out, studies that have been conducted on
agreement attraction in Turkish have been extremely few. In fact, Lago
(2018) has been the only study to look into this phenomenon in Turkish.
Lago (2018)'s study make use of genitive-possessive structures in the
subject position, in which the possessive-marked noun is the head of the
noun phrase which acts as the grammatical agreement controller, and the
genitive noun serves as a potential attractor. In a speeded
acceptability judgment study, they found a significant effect of number
agreement attraction. However, the interpretation of their finding may
be a result of a non-subjecthood cues originating from their use of
morphologically ambiguous forms of possessive. In their possessive form
all head nouns in their stimuli are ambigiuous between possessive and
accusative.

In Turkish, accusative number agreement controllers are extremely rare,
while genitive agreement controllers are very frequent. Thus, Lago
(2018)'s finding could possibly be explained by occasional shallow
processing. When all syntactic relations in the sentence were processed
fully, the possessive noun should have been identified as the
controller. Meanwhile the genitive noun may sometimes have been
erroneously identified as the controller during shallow processing,
because genitives are more likely to act as agreement controllers than
accusatives. A second alternative explanation of Lago (2018)'s finding
may be the fact that participants may engage in even more shallow
processing than outlined above. Participants may have erroneously
responded \emph{Yes} on some trials due to (i) the presence of a plural
morpheme on a noun (attractor or controller) and (ii) the presence of a
plural agreement morpheme on the verb. We speculate that on such trials,
participants would have simply tried to check for the presence of such
morphemes, while largely disregarding the remainder of the sentence.

We first replicated Lago (2018)'s experiment with unambiuous head nouns.
To this end, we have revised the items that were used previously, to
avoid morphological ambiguity between possessive and accusative forms.
The effect found by Lago (2018) replicates with unambiguous nouns as
discused in \S 2.

\S 3 discussses the alternative account that posits even more shallow
processing as mentioned above and offers a pre-registered experiment
using RC attractors with possible outcomes and their indications. Since
both nominal and verbal plural morphemes in Turkish take on the same
form (\emph{-ler} or \emph{-lar} depending on the phonological
environment), we can test this possibility with an experiment, in which
we use relative clause with or without plural agreement on the verb in
the place of the genitive possessors. An agreement attraction effect
similar in magnitude to Lago (2018)'s would mean that participants use
aforementioned strategies.

\S 4 presents a discussion revolving around possible Lastly, \S 5 offers
a brief conclusion and presents topics for future researches.

\hypertarget{replicaton-of-lago}{%
\section{REPLICATON OF Lago (2018)}\label{replicaton-of-lago}}

In their study, Lago (2018) investigated the comprehension of
subject-verb agreement in Turkish-German bilinguals and Turkish
monolinguals. They used speeded acceptability judments for the effects
of number attraction in Turkish. Their sentences makes us of
genitive-possessive constructions in the subject position, where the
genitive is the attractor and the possessive is the head noun. They have
manipulated the grammaticality of the sentence by changing the plural
morphology of the verb, and they also manipulated the plurality of the
attractor noun. In grammatical conditions, subject and the verb both
bears the singular morphology with no overt morpheme. Moreover, in the
ungrammatical conditions the verb bears the overt \emph{-lAr} morpheme
whereas the subject is still singular as exemplified below.

\begin{exe}
\ex
\begin{xlist}
\ex \underline{Grammatical, SG attractor} \label{lago1}
\gll \c{S}ark{\i}c{\i}-n{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}\\
singer-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-$\varnothing$\\
\glt The singer's backup vocalist jumped on the stage non-stop.

\ex \underline{Grammatical, PL attractor} \label{lago2}
\gll \c{S}ark{\i}c{\i}-lar-{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}\\
singer-\textsc{pl}-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-$\varnothing$\\
\glt The singer's backup vocalist jumped on the stage non-stop.

\ex \underline{Ungrammatical, PL attractor} \label{lago3}
\gll \c{S}ark{\i}c{\i}-lar-{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}-lar.\\
singer-\textsc{pl}-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-\textsc{3Pl}\\
\glt The singer's backup vocalist jumped on the stage non-stop.

\ex \underline{Ungrammatical, SG attractor} \label{lago4}
\gll \c{S}ark{\i}c{\i}-n{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}-lar.\\
singer-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-\textsc{3Pl}\\
\glt The singer's backup vocalist jumped on the stage non-stop.
\end{xlist}
\end{exe}

They have found a significant effect of number attraction in Turkish
ranging between 11\%--15\% across monolinguals. As seen from the results
of statistical analysis in Table (\ref{lagomodel}), acceptability
judgments showed an immense effect of grammaticality, and there is also
interaction between grammaticality and attractor number which indicates
an number attraction effect.

\begin{table}[]
\centering
\begin{tabular}{llcccc}
\hline
    &                                        & \multicolumn{4}{l}{Monolingual Speakers}                                               \\ \cline{3-6} 
    &                                        & $\beta$        & SE            & \emph{z} & \emph{p} \\ \hline
\multicolumn{2}{l}{\textbf{Attraction Task}} &                &               &                           &                           \\
    & Grammaticality                         & \textbf{-5.51} & \textbf{0.33} & \textbf{-16.69}           & \textbf{.000}             \\
    & Attractor Number                       & 0.14           & 0.25          & 0.57                      & .571                      \\
    & Grammaticality x Attractor Number      & \textbf{1.69}  & \textbf{0.53} & \textbf{3.19}             & \textbf{.001}             \\
    & Attractor Number: Ungram conditions    & \textbf{0.94}  & \textbf{0.26} & \textbf{3.68}             & \textbf{.000}             \\
    & Attractor Number: Gram conditions      & -0.79          & 0.52          & -1.51                     & .131                      \\ \hline
\end{tabular}
\caption{Model results for the judgments of monolingual cited from @Lago.}
\label{lagomodel}
\end{table}

According to Lago (2018)'s stipulation, Turkish genitive case does not
provide a strong cue against subjecthood since it is extremely common to
see genitive marked subjects in Turkish embedded clauses, as in example
(\ref{gensubj}).

\begin{exe}
\ex \label{gensubj}
\gll k\"{o}y-\"{u} bir haydut-un bas-t{\i}\u{g}-{\i}n-{\i} duy-du-m.\\
village-\textsc{acc} a bandit-\textsc{gen} raid-\textsc{nmlz}-\textsc{3Sg}-\textsc{acc} hear-\textsc{pst}-\textsc{1Sg}\\
\glt I heard that a (certain) robber raided the village. (Adapted from Woolford (2009))
\end{exe}

\hypertarget{motivation}{%
\subsection{Motivation}\label{motivation}}

\hypertarget{modifications}{%
\subsection{Modifications}\label{modifications}}

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

\hypertarget{filler-items}{%
\subsection{Filler Items}\label{filler-items}}

\hypertarget{results-and-discussion}{%
\subsection{Results and Discussion}\label{results-and-discussion}}

\hypertarget{experiment-2-rc-attractor}{%
\section{EXPERIMENT 2: RC ATTRACTOR}\label{experiment-2-rc-attractor}}

\hypertarget{motivation-1}{%
\subsection{Motivation}\label{motivation-1}}

\hypertarget{items-and-fillers}{%
\subsection{Items and Fillers}\label{items-and-fillers}}

\hypertarget{expectations}{%
\subsection{Expectations}\label{expectations}}

\hypertarget{possible-outcomes-and-discussion}{%
\subsection{Possible Outcomes and
Discussion}\label{possible-outcomes-and-discussion}}

\hypertarget{discussion}{%
\section{DISCUSSION}\label{discussion}}

Discuss.

\hypertarget{conclusions}{%
\section{CONCLUSIONS}\label{conclusions}}

Intro and repeat.

\hypertarget{acknowledgements}{%
\section{ACKNOWLEDGEMENTS}\label{acknowledgements}}

We used the statistical language \texttt{R} (R Core Team 2018) for all
our analyses. These were implemented in dynamic rmarkdown documents
using \texttt{knitr} (Xie 2014, 2015, 2018) and \texttt{rmarkdown}
(Allaire et al. 2018, Xie et al. 2018) packages. All graphs have been
done with \texttt{ggplot} (Wickham 2016). Thank the Mine and Kadir for
their student from courses.

\hypertarget{references}{%
\section{REFERENCES}\label{references}}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Allaire_2018}{}%
Allaire, J., Y. Xie, J. McPherson, J. Luraschi, K. Ushey, A. Atkins, H.
Wickham, J. Cheng, W. Chang, and R. Iannone. 2018. Rmarkdown: Dynamic
documents for r.

\leavevmode\hypertarget{ref-Lago}{}%
Lago, S. 2018. Straight from the horse's mouth: agreement attraction
effects with Turkish possessors.

\leavevmode\hypertarget{ref-R_Core_Team_2018}{}%
R Core Team. 2018. R: A language and environment for statistical
computing. R Foundation for Statistical Computing, Vienna, Austria.

\leavevmode\hypertarget{ref-Wickham_2016}{}%
Wickham, H. 2016. Ggplot2: Elegant graphics for data analysis.
Springer-Verlag New York.

\leavevmode\hypertarget{ref-woolford}{}%
Woolford, E. 2009. Differential subject marking at argument structure,
syntax, and pf. Pages 17--40 \emph{in} Differential subject marking.
Springer.

\leavevmode\hypertarget{ref-Xie_2014}{}%
Xie, Y. 2014. Knitr: A comprehensive tool for reproducible research in
R. \emph{in} V. Stodden, F. Leisch, and R. D. Peng, editors.
Implementing reproducible computational research. Chapman; Hall/CRC.

\leavevmode\hypertarget{ref-Xie_2015}{}%
Xie, Y. 2015. Dynamic documents with R and knitr. 2nd editions. Chapman;
Hall/CRC, Boca Raton, Florida.

\leavevmode\hypertarget{ref-Xie_2018}{}%
Xie, Y. 2018. Knitr: A general-purpose package for dynamic report
generation in r.

\leavevmode\hypertarget{ref-Xie_2018a}{}%
Xie, Y., J. Allaire, and G. Grolemund. 2018. R markdown: The definitive
guide. Chapman; Hall/CRC, Boca Raton, Florida.

\eleft

\clearpage

\listoftables

\newpage

\begin{longtable}[]{@{}rrrrl@{}}
\caption{A glimpse of the famous \emph{Iris} dataset.}\tabularnewline
\toprule
Sepal.Length & Sepal.Width & Petal.Length & Petal.Width &
Species\tabularnewline
\midrule
\endfirsthead
\toprule
Sepal.Length & Sepal.Width & Petal.Length & Petal.Width &
Species\tabularnewline
\midrule
\endhead
5.1 & 3.5 & 1.4 & 0.2 & setosa\tabularnewline
4.9 & 3.0 & 1.4 & 0.2 & setosa\tabularnewline
4.7 & 3.2 & 1.3 & 0.2 & setosa\tabularnewline
4.6 & 3.1 & 1.5 & 0.2 & setosa\tabularnewline
5.0 & 3.6 & 1.4 & 0.2 & setosa\tabularnewline
5.4 & 3.9 & 1.7 & 0.4 & setosa\tabularnewline
\bottomrule
\end{longtable}

\newpage

\begin{longtable}[]{@{}lrrrrrrrrrrr@{}}
\caption{Now a subset of mtcars dataset.}\tabularnewline
\toprule
& mpg & cyl & disp & hp & drat & wt & qsec & vs & am & gear &
carb\tabularnewline
\midrule
\endfirsthead
\toprule
& mpg & cyl & disp & hp & drat & wt & qsec & vs & am & gear &
carb\tabularnewline
\midrule
\endhead
Merc 280 & 19.2 & 6 & 167.6 & 123 & 3.92 & 3.440 & 18.30 & 1 & 0 & 4 &
4\tabularnewline
Merc 280C & 17.8 & 6 & 167.6 & 123 & 3.92 & 3.440 & 18.90 & 1 & 0 & 4 &
4\tabularnewline
Merc 450SE & 16.4 & 8 & 275.8 & 180 & 3.07 & 4.070 & 17.40 & 0 & 0 & 3 &
3\tabularnewline
Merc 450SL & 17.3 & 8 & 275.8 & 180 & 3.07 & 3.730 & 17.60 & 0 & 0 & 3 &
3\tabularnewline
Merc 450SLC & 15.2 & 8 & 275.8 & 180 & 3.07 & 3.780 & 18.00 & 0 & 0 & 3
& 3\tabularnewline
Cadillac Fleetwood & 10.4 & 8 & 472.0 & 205 & 2.93 & 5.250 & 17.98 & 0 &
0 & 3 & 4\tabularnewline
Lincoln Continental & 10.4 & 8 & 460.0 & 215 & 3.00 & 5.424 & 17.82 & 0
& 0 & 3 & 4\tabularnewline
\bottomrule
\end{longtable}

\clearpage

\listoffigures

\newpage

\begin{figure}
\centering
\includegraphics{output/figures/Fig1-1.pdf}
\caption{Just my first figure with a very fantastic caption.}
\end{figure}

\newpage

\blandscape

\begin{figure}
\centering
\includegraphics{output/figures/Fig2-1.pdf}
\caption{Second figure in landscape format.}
\end{figure}

\elandscape

\clearpage

\end{document}

### 2019-01-24 Paper/Untitled/Untitled.Rmd
all-update

---
title: 'A template for writing manuscripts in Rmarkdown'

author:

- name: Jeffrey W. Hollister
  affilnum: '1,2'

- name: Francisco Rodriguez-Sanchez 
  affilnum: 3
  email: f.rodriguez.sanc@gmail.com

affiliation:

- affilnum: 1
  affil: US Environmental Protection Agency, Office of Research and Development, National Health and Environmental Effects Research Laboratory, Atlantic Ecology Division, 27 Tarzwell Drive  Narragansett, RI, 02882, USA

- affilnum: 2
  affil: Big Name University, Department of R, City, BN, 01020, USA

- affilnum: 3
  affil: Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain

output:

  pdf_document:
    fig_caption: yes
    fig_width: 7
    fig_height: 7
    keep_tex: yes
    number_sections: no
    template: manuscript.latex
    includes:
      in_header: header.tex

  html_document: null

  word_document: null

documentclass: article
classoption: a4paper
capsize: normalsize
fontsize: 11pt
geometry: margin=1in
linenumbers: yes
spacing: doublespacing
footerdate: yes
bibliography: 
  - references.bib
  - knitcitations.bib
csl: ecology.csl

---

```{r setup, include=FALSE, cache=FALSE, message = FALSE}

library("knitr")

#opts_knit$set(root.dir=normalizePath('../'))

### Chunk options: see http://yihui.name/knitr/options/ ###

## Text results
opts_chunk$set(echo = TRUE, warning = TRUE, message = TRUE, include = TRUE)

## Code decoration
opts_chunk$set(tidy = TRUE, comment = NA, highlight = TRUE)

## Cache
opts_chunk$set(cache = 2, cache.path = "output/cache/")

## Plots
opts_chunk$set(fig.path = "output/figures/")

```

```{r knitcitations, echo=FALSE, cache = FALSE}
library(knitcitations)
cleanbib()   
cite_options(citation_format = "pandoc")
```

\singlespace

\vspace{2mm}\hrule

Write your abstract here.

\vspace{3mm}\hrule

*Keywords*: rmarkdown, reproducible science

\doublespace

\bleft

# INTRODUCTION

Write your introduction here. You can cite bibliography like this [@Yan2011; @Sutherland2011], if you provide a `BibTeX` file with references. See http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html for more information. Or you could also use [knitcitations](https://cran.r-project.org/web/packages/knitcitations/index.html) or [RefManageR](https://cran.r-project.org/web/packages/RefManageR/index.html) to fetch bibliographic metadata automatically from the web. For example, citing a paper can be as easy as providing its DOI `r citep("10.1016/j.tree.2006.03.016")` or even just a few keywords `r citep("Ricklefs 2008 American Naturalist")`. They will then automagically appear in the list of cited references.

You can even specifiy the desired output format for your bibliography by including a style file for a specific journal (e.g. "ecology.csl"). Many different bibliography styles (CSL files) can be obtained at http://citationstyles.org/ or https://github.com/citation-style-language/styles.

# METHODS

## Study Area

We worked in a **beautiful** place with lots of trees, like *Quercus suber* and *Laurus nobilis*.

## Data collection and analysis

```{r read_data, eval = FALSE, echo = FALSE}
dataset <- read.csv("mydata.csv")
```

We applied a linear model where

$$
y_{i} = \alpha + \beta*x_{i} 
$$

```{r model, echo = FALSE, eval = FALSE}
model <- lm(y ~ x)
```

We used the statistical language `R` `r citep(citation())` for all our analyses. These were implemented in dynamic rmarkdown documents using `knitr` `r citep(citation("knitr"))` and `rmarkdown` `r citep(citation("rmarkdown"))` packages. All the multilevel models were fitted with `lme4` `r citep(citation("lme4"))`.

# RESULTS

Trees in forest A grew taller than those in forest B (mean height: `r mean(25, 31, 28)` versus `r mean(13, 19, 16)` m). And many more cool results that get updated dynamically.

# DISCUSSION

Discuss.

# CONCLUSIONS

# ACKNOWLEDGEMENTS

# REFERENCES

```{r write_citations, cache=FALSE, include=FALSE}
write.bibtex(file="knitcitations.bib")
```

<div id = "refs"></div>

\eleft

\clearpage

\listoftables

\newpage

```{r Table1, results='asis', echo=FALSE, cache=FALSE}
kable(head(iris), caption = "A glimpse of the famous *Iris* dataset.")
```

\newpage

```{r Table2, results='asis', echo=FALSE, cache=FALSE}
kable(mtcars[10:16, ], caption = "Now a subset of mtcars dataset.")
```

\clearpage

\listoffigures

\newpage

```{r Fig1, echo=FALSE, fig.cap="Just my first figure with a very fantastic caption.", cache=FALSE}
x <- rnorm(100)
y <- jitter(x, 1000)
plot(x, y)
```

\newpage

\blandscape

```{r Fig2, echo=FALSE, fig.cap="Second figure in landscape format.", cache=FALSE}
a <- sort(rnorm(100))
b <- c(rep("Group Small", 35), rep("Group Big", 65))
boxplot(a ~ b)
```

\elandscape

\clearpage

```{r sessioninfo, echo = FALSE, eval = FALSE}
# set eval = FALSE if you don't want this info (useful for reproducibility) to appear 
sessionInfo()
```

### 2019-01-24 Paper/Untitled/Untitled.tex
all-update

--- 2019-01-24 Paper/AgreementAttraction.tex
@@
             pdfauthor={},
-            pdftitle={Agreement Attraction in Turkish: Effects of Nominal and Verbal Plural Morphemes},
+            pdftitle={A template for writing manuscripts in Rmarkdown},
             colorlinks=true,
@@
 \setlength{\emergencystretch}{3em}  % prevent overfull lines
-\setcounter{secnumdepth}{5}
+\setcounter{secnumdepth}{0}
 
@@
 \usepackage[font=normalsize]{caption}
-  \usepackage[singlespacing]{setspace}
+  \usepackage[doublespacing]{setspace}
 \usepackage{parskip}
@@
 
-\title{Agreement Attraction in Turkish: Effects of Nominal and Verbal Plural
-Morphemes}
+\title{A template for writing manuscripts in Rmarkdown}
 \author{
-Utku Turk
-Pavel Logacev
+Jeffrey W. Hollister
+Francisco Rodriguez-Sanchez
 }
@@
 
-% multicols
-\usepackage{multicol}
-\usepackage{paracol}
-
-% enumerated examples
-\usepackage{enumitem}
-
-% for linguistic examples &  interlinear glosses
-\usepackage{gb4e}
-\exewidth{(10.159)}
-\noautomath
-\let\eachwordone=\it
-
-\usepackage{qtree}
-
 %%Fix tightlist error: https://stackoverflow.com/questions/40438037/tightlist-error-using-pandoc-with-markdown
@@
 \begin{center}
-\huge Agreement Attraction in Turkish: Effects of Nominal and Verbal Plural
-Morphemes
+\huge A template for writing manuscripts in Rmarkdown
 \end{center}
@@
 \large
-Utku Turk \textsuperscript{*} \textsuperscript{1} 
-Pavel Logacev \textsuperscript{1} 
+Jeffrey W. Hollister \textsuperscript{1,2} 
+Francisco Rodriguez-Sanchez \textsuperscript{*} \textsuperscript{3} 
 \end{center}
@@
 \\*
-\textsuperscript{1}Bogazici University, South Campus, John Freely Building, Department of
-Linguistics, 34342, Istanbul, Turkey\\*
+\textsuperscript{1}US Environmental Protection Agency, Office of Research and Development,
+National Health and Environmental Effects Research Laboratory, Atlantic
+Ecology Division, 27 Tarzwell Drive Narragansett, RI, 02882, USA\\*
+\\*
+\textsuperscript{2}Big Name University, Department of R, City, BN, 01020, USA\\*
+\\*
+\textsuperscript{3}Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain\\*
 }
@@
 \fi
-\href{mailto:utku.turk@boun.edu.tr}{\nolinkurl{utku.turk@boun.edu.tr}}
+\href{mailto:f.rodriguez.sanc@gmail.com}{\nolinkurl{f.rodriguez.sanc@gmail.com}}
 \stepcounter{num}
@@
 
+\singlespace
+
 \vspace{2mm}\hrule
 
-In this paper, our objective is to explore the source of agreement
-attraction effects in Turkish found by Lago (2018). The interpretation
-of their finding is complicated by the fact that in their possessive
-form all head nouns in their stimuli are morphologically ambiguous
-between possessive and accusative. Due to the mismatch in the frequency
-of usage of accusative and genitive, which is used as a attractor in
-this experiment, as a controller, Lago (2018)'s findings could
-potentially be explained with occasional shallow processing. We have
-replicated Lago (2018)'s experiment with unambigious head nouns, and we
-have found the same agreement attraction effects. However, this may mean
-that participants may engage in even more shallow processing than we
-imagined. We postulate that participants solely check for the presence
-of a \emph{-lAr} morpheme, while largely disregarding the remainder of
-the sentence. We utilize an experiment design in which we use a relative
-clause with or without plural agreement on the verb in place of the
-genitive possessor since both verbal and nominal plural morphemes are
-the same in Turkish. If participants did, in fact, adopt a superficial
-processing strategy, we would expect to find a number agreement
-attraction effect similar in magnitude to Lago (2018)'s. However, if
-number attraction is not an artifact of shallow processing strategies,
-we should expect to find no number attraction in this experiment.
+Write your abstract here.
 
@@
 
-\emph{Keywords}: Turkish, agreement attraction, task effect, shallow
-processing
+\emph{Keywords}: rmarkdown, reproducible science
+
+\doublespace
 
@@
 
-Attraction errors in production and comprehension of subject-verb
-agrrement, in which a verb does not agree with the grammatical agreement
-controller, but with a potential attractors, have been the focal point
-of many research for quite a long time. In fact, it is still a widely
-researched are in psycholinguistic studies. Despite the thorough
-research that has been carried out, studies that have been conducted on
-agreement attraction in Turkish have been extremely few. In fact, Lago
-(2018) has been the only study to look into this phenomenon in Turkish.
-Lago (2018)'s study make use of genitive-possessive structures in the
-subject position, in which the possessive-marked noun is the head of the
-noun phrase which acts as the grammatical agreement controller, and the
-genitive noun serves as a potential attractor. In a speeded
-acceptability judgment study, they found a significant effect of number
-agreement attraction. However, the interpretation of their finding may
-be a result of a non-subjecthood cues originating from their use of
-morphologically ambiguous forms of possessive. In their possessive form
-all head nouns in their stimuli are ambigiuous between possessive and
-accusative.
+Write your introduction here. You can cite bibliography like this (Yan
+and Gerstein 2011, Sutherland et al. 2011), if you provide a
+\texttt{BibTeX} file with references. See
+\url{http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html}
+for more information. Or you could also use
+\href{https://cran.r-project.org/web/packages/knitcitations/index.html}{knitcitations}
+or
+\href{https://cran.r-project.org/web/packages/RefManageR/index.html}{RefManageR}
+to fetch bibliographic metadata automatically from the web. For example,
+citing a paper can be as easy as providing its DOI (Clark and Gelfand
+2006) or even just a few keywords (Ricklefs 2008). They will then
+automagically appear in the list of cited references.
 
-In Turkish, accusative number agreement controllers are extremely rare,
-while genitive agreement controllers are very frequent. Thus, Lago
-(2018)'s finding could possibly be explained by occasional shallow
-processing. When all syntactic relations in the sentence were processed
-fully, the possessive noun should have been identified as the
-controller. Meanwhile the genitive noun may sometimes have been
-erroneously identified as the controller during shallow processing,
-because genitives are more likely to act as agreement controllers than
-accusatives. A second alternative explanation of Lago (2018)'s finding
-may be the fact that participants may engage in even more shallow
-processing than outlined above. Participants may have erroneously
-responded \emph{Yes} on some trials due to (i) the presence of a plural
-morpheme on a noun (attractor or controller) and (ii) the presence of a
-plural agreement morpheme on the verb. We speculate that on such trials,
-participants would have simply tried to check for the presence of such
-morphemes, while largely disregarding the remainder of the sentence.
+You can even specifiy the desired output format for your bibliography by
+including a style file for a specific journal (e.g.~``ecology.csl'').
+Many different bibliography styles (CSL files) can be obtained at
+\url{http://citationstyles.org/} or
+\url{https://github.com/citation-style-language/styles}.
 
-We first replicated Lago (2018)'s experiment with unambiuous head nouns.
-To this end, we have revised the items that were used previously, to
-avoid morphological ambiguity between possessive and accusative forms.
-The effect found by Lago (2018) replicates with unambiguous nouns as
-discused in \S 2.
+\hypertarget{methods}{%
+\section{METHODS}\label{methods}}
 
-\S 3 discussses the alternative account that posits even more shallow
-processing as mentioned above and offers a pre-registered experiment
-using RC attractors with possible outcomes and their indications. Since
-both nominal and verbal plural morphemes in Turkish take on the same
-form (\emph{-ler} or \emph{-lar} depending on the phonological
-environment), we can test this possibility with an experiment, in which
-we use relative clause with or without plural agreement on the verb in
-the place of the genitive possessors. An agreement attraction effect
-similar in magnitude to Lago (2018)'s would mean that participants use
-aforementioned strategies.
+\hypertarget{study-area}{%
+\subsection{Study Area}\label{study-area}}
 
-\S 4 presents a discussion revolving around possible Lastly, \S 5 offers
-a brief conclusion and presents topics for future researches.
+We worked in a \textbf{beautiful} place with lots of trees, like
+\emph{Quercus suber} and \emph{Laurus nobilis}.
 
-\hypertarget{replicaton-of-lago}{%
-\section{REPLICATON OF Lago (2018)}\label{replicaton-of-lago}}
+\hypertarget{data-collection-and-analysis}{%
+\subsection{Data collection and
+analysis}\label{data-collection-and-analysis}}
 
-In their study, Lago (2018) investigated the comprehension of
-subject-verb agreement in Turkish-German bilinguals and Turkish
-monolinguals. They used speeded acceptability judments for the effects
-of number attraction in Turkish. Their sentences makes us of
-genitive-possessive constructions in the subject position, where the
-genitive is the attractor and the possessive is the head noun. They have
-manipulated the grammaticality of the sentence by changing the plural
-morphology of the verb, and they also manipulated the plurality of the
-attractor noun. In grammatical conditions, subject and the verb both
-bears the singular morphology with no overt morpheme. Moreover, in the
-ungrammatical conditions the verb bears the overt \emph{-lAr} morpheme
-whereas the subject is still singular as exemplified below.
+We applied a linear model where
 
-\begin{exe}
-\ex
-\begin{xlist}
-\ex \underline{Grammatical, SG attractor} \label{lago1}
-\gll \c{S}ark{\i}c{\i}-n{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}\\
-singer-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-$\varnothing$\\
-\glt The singer's backup vocalist jumped on the stage non-stop.
+\[
+y_{i} = \alpha + \beta*x_{i} 
+\]
 
-\ex \underline{Grammatical, PL attractor} \label{lago2}
-\gll \c{S}ark{\i}c{\i}-lar-{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}\\
-singer-\textsc{pl}-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-$\varnothing$\\
-\glt The singer's backup vocalist jumped on the stage non-stop.
+We used the statistical language \texttt{R} (R Core Team 2018) for all
+our analyses. These were implemented in dynamic rmarkdown documents
+using \texttt{knitr} (Xie 2014, 2015, 2018) and \texttt{rmarkdown}
+(Allaire et al. 2018, Xie et al. 2018) packages. All the multilevel
+models were fitted with \texttt{lme4} (Bates et al. 2015).
 
-\ex \underline{Ungrammatical, PL attractor} \label{lago3}
-\gll \c{S}ark{\i}c{\i}-lar-{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}-lar.\\
-singer-\textsc{pl}-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-\textsc{3Pl}\\
-\glt The singer's backup vocalist jumped on the stage non-stop.
+\hypertarget{results}{%
+\section{RESULTS}\label{results}}
 
-\ex \underline{Ungrammatical, SG attractor} \label{lago4}
-\gll \c{S}ark{\i}c{\i}-n{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}-lar.\\
-singer-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-\textsc{3Pl}\\
-\glt The singer's backup vocalist jumped on the stage non-stop.
-\end{xlist}
-\end{exe}
-
-They have found a significant effect of number attraction in Turkish
-ranging between 11\%--15\% across monolinguals. As seen from the results
-of statistical analysis in Table (\ref{lagomodel}), acceptability
-judgments showed an immense effect of grammaticality, and there is also
-interaction between grammaticality and attractor number which indicates
-an number attraction effect.
-
-\begin{table}[]
-\centering
-\begin{tabular}{llcccc}
-\hline
-    &                                        & \multicolumn{4}{l}{Monolingual Speakers}                                               \\ \cline{3-6} 
-    &                                        & $\beta$        & SE            & \emph{z} & \emph{p} \\ \hline
-\multicolumn{2}{l}{\textbf{Attraction Task}} &                &               &                           &                           \\
-    & Grammaticality                         & \textbf{-5.51} & \textbf{0.33} & \textbf{-16.69}           & \textbf{.000}             \\
-    & Attractor Number                       & 0.14           & 0.25          & 0.57                      & .571                      \\
-    & Grammaticality x Attractor Number      & \textbf{1.69}  & \textbf{0.53} & \textbf{3.19}             & \textbf{.001}             \\
-    & Attractor Number: Ungram conditions    & \textbf{0.94}  & \textbf{0.26} & \textbf{3.68}             & \textbf{.000}             \\
-    & Attractor Number: Gram conditions      & -0.79          & 0.52          & -1.51                     & .131                      \\ \hline
-\end{tabular}
-\caption{Model results for the judgments of monolingual cited from @Lago.}
-\label{lagomodel}
-\end{table}
-
-According to Lago (2018)'s stipulation, Turkish genitive case does not
-provide a strong cue against subjecthood since it is extremely common to
-see genitive marked subjects in Turkish embedded clauses, as in example
-(\ref{gensubj}).
-
-\begin{exe}
-\ex \label{gensubj}
-\gll k\"{o}y-\"{u} bir haydut-un bas-t{\i}\u{g}-{\i}n-{\i} duy-du-m.\\
-village-\textsc{acc} a bandit-\textsc{gen} raid-\textsc{nmlz}-\textsc{3Sg}-\textsc{acc} hear-\textsc{pst}-\textsc{1Sg}\\
-\glt I heard that a (certain) robber raided the village. (Adapted from Woolford (2009))
-\end{exe}
-
-\hypertarget{motivation}{%
-\subsection{Motivation}\label{motivation}}
-
-\hypertarget{modifications}{%
-\subsection{Modifications}\label{modifications}}
-
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
-
-\hypertarget{filler-items}{%
-\subsection{Filler Items}\label{filler-items}}
-
-\hypertarget{results-and-discussion}{%
-\subsection{Results and Discussion}\label{results-and-discussion}}
-
-\hypertarget{experiment-2-rc-attractor}{%
-\section{EXPERIMENT 2: RC ATTRACTOR}\label{experiment-2-rc-attractor}}
-
-\hypertarget{motivation-1}{%
-\subsection{Motivation}\label{motivation-1}}
-
-\hypertarget{items-and-fillers}{%
-\subsection{Items and Fillers}\label{items-and-fillers}}
-
-\hypertarget{expectations}{%
-\subsection{Expectations}\label{expectations}}
-
-\hypertarget{possible-outcomes-and-discussion}{%
-\subsection{Possible Outcomes and
-Discussion}\label{possible-outcomes-and-discussion}}
+Trees in forest A grew taller than those in forest B (mean height: 25
+versus 13 m). And many more cool results that get updated dynamically.
 
@@
 
-Intro and repeat.
-
 \hypertarget{acknowledgements}{%
 \section{ACKNOWLEDGEMENTS}\label{acknowledgements}}
-
-We used the statistical language \texttt{R} (R Core Team 2018) for all
-our analyses. These were implemented in dynamic rmarkdown documents
-using \texttt{knitr} (Xie 2014, 2015, 2018) and \texttt{rmarkdown}
-(Allaire et al. 2018, Xie et al. 2018) packages. All graphs have been
-done with \texttt{ggplot} (Wickham 2016). Thank the Mine and Kadir for
-their student from courses.
 
@@
 
-\leavevmode\hypertarget{ref-Lago}{}%
-Lago, S. 2018. Straight from the horse's mouth: agreement attraction
-effects with Turkish possessors.
+\leavevmode\hypertarget{ref-Bates_2015}{}%
+Bates, D., M. Mächler, B. Bolker, and S. Walker. 2015. Fitting linear
+mixed-effects models using lme4. Journal of Statistical Software
+67:1--48.
+
+\leavevmode\hypertarget{ref-Clark_2006}{}%
+Clark, J. S., and A. E. Gelfand. 2006. A future for models and data in
+environmental science. Trends in Ecology \& Evolution 21:375--380.
 
@@
 
-\leavevmode\hypertarget{ref-Wickham_2016}{}%
-Wickham, H. 2016. Ggplot2: Elegant graphics for data analysis.
-Springer-Verlag New York.
+\leavevmode\hypertarget{ref-Ricklefs_2008}{}%
+Ricklefs, R. E. 2008. Disintegration of the ecological community. The
+American Naturalist 172:741--750.
 
-\leavevmode\hypertarget{ref-woolford}{}%
-Woolford, E. 2009. Differential subject marking at argument structure,
-syntax, and pf. Pages 17--40 \emph{in} Differential subject marking.
-Springer.
+\leavevmode\hypertarget{ref-Sutherland2011}{}%
+Sutherland, W. J., D. Goulson, S. G. Potts, and L. V. Dicks. 2011.
+Quantifying the impact and relevance of scientific research. PLoS ONE
+6:e27537.
 
@@
 guide. Chapman; Hall/CRC, Boca Raton, Florida.
+
+\leavevmode\hypertarget{ref-Yan2011}{}%
+Yan, K.-K., and M. Gerstein. 2011. The spread of scientific information:
+Insights from the web usage statistics in plos article-level metrics.
+PLoS ONE 6:e19917.
 

### 2019-01-24 Results and Analysis/playing a bit.R

@@ -1,0 +1,380 @@
+# LIBRARIES & DATA ------
+library(languageR)
+library(tidyverse)
+library(gdata)
+library(MASS)
+library(magrittr)
+library(ggplot2)
+
+# First convert to csv file, using the "_" and "," character as a delimter
+# setwd("C:/Users/utku/Downloads/cormorant_final/results")
+# getwd()
+
+# Then load into R, splitting the csv file on the comma ","
+data <- read.csv('results', 
+                 header = F, 
+                 comment.char = "#", 
+                 encoding = "UTF-8" , 
+                 col.names = paste0("V",seq_len(11)), 
+                 fill = TRUE)
+
+
+# Add column names to dataframe
+colnames(data) = c("Time", "MD5", "ControllerType", "SentenceNoInStimFile", "Element", "Type", "Item", "Sentence", "Question","Answer", "RT")
+
+# Note: Less transparent columns
+# Time: 		When results sent to server
+# MD5: 			Encoding of IP address
+# Controller: 	Presentation type
+
+
+# Cleaning up data
+# What information is there:
+# levels(data$Type)
+# Remove extra information: Should I play with every condition?
+
+
+
+
+
+
+
+# FORM & PRACTICE ------
+# Make Form Entries Columns and left join them, get for unique MD5
+FormEntries <- subset(data, ControllerType != "DashedAcceptabilityJudgment" ) %>% drop.levels(); nrow(data)
+data %<>% subset(ControllerType == "DashedAcceptabilityJudgment")
+
+age <- dplyr::select(FormEntries, MD5,Sentence,Question) %>% 
+  dplyr::filter(Sentence == "age") %>%
+  dplyr::select(MD5, Age = Question)
+
+# Note: The radio buttons on the page returned "male" when participants specified that they were native speakers of Turkish, and "female" otherwise,
+# due to a copy-and-paste error.
+natturk <- dplyr::select(FormEntries, MD5,Sentence,Question) %>% 
+  dplyr::filter(Sentence == "natturk") %>%
+  dplyr::select(MD5, Natturk = Question) %>%
+  mutate(Natturk = Natturk == "male")
+
[…]

### 2019-01-24 Paper/AgreementAttraction.Rmd
paperwriting

@@
 
-```{r outline, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-Introduction
-Recap on what Lago did
-My experiment
-  Reasoning
-  Experiment Details
-    Environments
-    Items
-    Fillers
-    Participants
-    Exclusions
-    Results and Discussions
-  ...
-
-```
-
 ```{r knitcitations, echo=FALSE, cache = FALSE}
@@
 cite_options(citation_format = "pandoc")
+```
+
+```{r init, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+library(languageR)
+library(tidyverse)
+library(gdata)
+library(MASS)
+library(magrittr)
+library(ggplot2)
+
+data <- read.csv('results', 
+                 header = F, 
+                 comment.char = "#", 
+                 encoding = "UTF-8" , 
+                 col.names = paste0("V",seq_len(11)), 
+                 fill = TRUE)
+
+colnames(data) = c("Time", "MD5", "ControllerType", "SentenceNoInStimFile", "Element", "Type", "Item", "Sentence", "Question","Answer", "RT")
+
+FormEntries <- subset(data, ControllerType != "DashedAcceptabilityJudgment" ) %>% drop.levels(); nrow(data)
+data %<>% subset(ControllerType == "DashedAcceptabilityJudgment")
+age <- dplyr::select(FormEntries, MD5,Sentence,Question) %>% 
+  dplyr::filter(Sentence == "age") %>%
+  dplyr::select(MD5, Age = Question)
+natturk <- dplyr::select(FormEntries, MD5,Sentence,Question) %>% 
+  dplyr::filter(Sentence == "natturk") %>%
+  dplyr::select(MD5, Natturk = Question) %>%
+  mutate(Natturk = Natturk == "male")
+dex <- dplyr::select(FormEntries, MD5,Sentence,Question) %>% 
+  dplyr::filter(Sentence == "dex") %>%
+  dplyr::select(MD5, Dex = Question) %>%
+  mutate(Dex = ifelse(Dex == "male", "right-handed", "left-handed"))
+FormPart <- dplyr::left_join(age, natturk, by = "MD5") %>% 
+  dplyr::left_join(., dex , by = "MD5" ) %>% 
+  unique()
+lenForm <- length(levels(factor(FormPart$MD5))); lenForm
+md5form <- levels(factor(FormPart$MD5))
+md5form_subject <- data.frame("MD5" = md5form, "Subject" = sprintf("S[%s]",seq((lenForm))))
+FormPart <- merge(FormPart,md5form_subject, all = T)
+
+stopifnot( nrow(data) %% 2 == 0 )
+rows_stim <- data[c(T,F),]
+rows_resp <- data[c(F,T),]
+
+data <- rows_resp %>% left_join(md5form_subject) %>% dplyr::select(-MD5, -Time, -ControllerType, -Sentence, -Element) %>%
+  dplyr::rename(ResponseCorrect=Answer, Response=Question)
+data %<>% group_by(Subject) %>% mutate(trial_no = seq(Subject))
+data %<>% within({ late_response = (Response == "NULL")
+Response[late_response] = NA
+ResponseCorrect[late_response] = NA
+})
+
+responses <- c(yes="İYİ (P'ye basınız)", no="KÖTÜ (Q'ya basınız)")
+stopifnot( all(data$Response %in% responses | is.na(data$Response) ) )
+
+data$ResponseYes <- ifelse(grepl("P",data$Response) , T, 
+                           ifelse(grepl("Q",data$Response) , F, NA))
+
+data$condition <- 
+  with(data, case_when(Type == "filler" & SentenceNoInStimFile >= 200 ~ "a",
+                       Type == "filler" & SentenceNoInStimFile < 200 ~ "b",
+                       Type == "condition_a" ~ "a",
+                       Type == "condition_b" ~ "b",
+                       Type == "condition_c" ~ "c",
+                       Type == "condition_d" ~ "d",
+                       TRUE ~ as.character(NA)))
+data$experiment <- ifelse(data$Type %in% c("condition_a", "condition_b", "condition_c", "condition_d"), "AgrAttr", as.character(data$Type))
+
+data %>% group_by(experiment, condition) %>% 
+  summarise(perc_yes = mean(ResponseYes, na.rm = T),
+            perc_na = mean(is.na(ResponseYes)))
+
+conditions_info <- data.frame(experiment = c("AgrAttr", "AgrAttr", "AgrAttr", "AgrAttr", "filler", "filler"),
+                              condition = c("a","b","c","d", "a","b"),
+                              grammatical = c("ungram", "gram", "ungram", "gram", "ungram", "gram"),
+                              verb_num = c("sg","pl","sg","pl", "sg","pl"),
+                              attracted = c(T,T,F,F,F,F),
+                              stringsAsFactors = FALSE) 
+data %<>% left_join(conditions_info)
+data %<>% subset(Type != "practice") %>% drop.levels()
+
+dataAv <- data %>% 
+  group_by(experiment, condition, grammatical, verb_num, attracted) %>%
+  summarize(avRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T)) %>% 
+  as.data.frame()
+
+dataAv %>% ggplot(aes(grammatical, p_yes, group = paste(experiment,attracted), color = experiment )) + geom_point() + geom_line(aes(linetype =attracted))
+
+data$trial_group <- Hmisc::cut2(data$trial_no, g=5)
+
+dataAvSplit <- data %>% 
+  group_by(experiment, condition, grammatical, verb_num, attracted, trial_group) %>%
+  summarize(avRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T)) %>% 
+  as.data.frame()
+
+plot_split <- dataAvSplit %>% ggplot(aes(grammatical, p_yes, group = paste(experiment,attracted), color = experiment )) + geom_point() + geom_line(aes(linetype =attracted)) + facet_wrap(~trial_group)
+
+dataAvBySubj <- data %>% 
+  group_by(Subject, experiment, condition, grammatical, verb_num, attracted) %>%
+  summarize(avRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T), N = sum(!is.na(ResponseYes))  )  %>% 
+  as.data.frame()
+head(dataAvBySubj,10)
+
+dataAvBySubjWide = dataAvBySubj %>% mutate(expcond = paste(experiment,condition, sep="_")) %>% dplyr::select(-experiment, -condition, -avRT, -N, -grammatical, -verb_num, -attracted) %>% tidyr::spread(expcond, p_yes)
+dataAvBySubjWide %<>% mutate(delta_dc = AgrAttr_d - AgrAttr_c)
+bad_subjects = subset(dataAvBySubjWide, delta_dc <= 0.25 ) %>% .$Subject
+
+dataAvBySubj %>% subset(Subject %in% bad_subjects) %>% ggplot(aes(grammatical, p_yes, group = paste(experiment,attracted), color = experiment )) + geom_point() + geom_line(aes(linetype =attracted)) + facet_wrap(~Subject)
+
+dataAvClean <- data %>% subset(!Subject %in% bad_subjects)%>% 
+  group_by(experiment, condition, grammatical, verb_num, attracted) %>%
+  summarize(avRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T)) %>% 
+  as.data.frame()
+
+dataAvClean <- slice(dataAvClean, 1:4)
+
+plot_average <- dataAvClean %>% ggplot(aes(grammatical, p_yes, group = paste(experiment,attracted), color = experiment )) + geom_point() + geom_line(aes(linetype =attracted)) #+ facet_wrap(~experiment, scales = "free_y")
+
 ```
@@
 singer-\textsc{pl}-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-$\varnothing$\\
-\glt The singer's backup vocalist jumped on the stage non-stop.
+\glt The singers' backup vocalist jumped on the stage non-stop.
 
@@
 singer-\textsc{pl}-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-\textsc{3Pl}\\
-\glt The singer's backup vocalist jumped on the stage non-stop.
+\glt The singers' backup vocalist jumped on the stage non-stop.
 
@@
 They have found a significant effect of number attraction in Turkish ranging between 11%--15% across monolinguals.
-As seen from the results of statistical analysis in Table (\ref{lagomodel}), acceptability judgments showed an immense effect of grammaticality, and there is also interaction between grammaticality and attractor number which indicates an number attraction effect.
+As seen from the results of statistical analysis in \textsc{Table} (\ref{lagomodel}), acceptability judgments showed an immense effect of grammaticality, and there is also interaction between grammaticality and attractor number which indicates an number attraction effect.
 
-\begin{table}[]
+\begin{table}[!hbt]
 \centering
@@
 
-However, we argue that not only genitive case but also possessive case plays a significant role in delivering the case information.
+However, our first hypothesis was the possibility of participants engaging in a shallow processing, which ends up in a situation where not only genitive case but also possessive case plays a significant role in delivering the case information.
 None of the experimental items in @Lago has a head noun which ends with a vowel; thus, all of the possessive markers are morphologically and phonologically ambiguous between the accusative case and the possessive.
+Unlike genitive case, the accusative case in Turkish is extremely rare to see on the head noun of the subject, which only occurs in the raising predicates as in example (\ref{dsm}).
 
-## Modifications
-## Participants
-## Filler Items
+\begin{exe}
+\ex \label{dsm}
+\gll Ben sen-i git-ti-n san-d{\i}-m\\
+I you-\textsc{acc} go-\textsc{pst}-\textsc{2Sg} suppose-\textsc{pst}-\textsc{1Sg}\\
+\glt I thought you were gone.
+\end{exe}
+
+In order to test this hypothesis, we have replicated the @Lago study with modified items, where the possessive is not ambiguous with the accusative case.
+We have tried to be as faithful as possible to the original sentences while trying to make sentences as plauisable as possible at the same time.
+We keep the semantic relation between the head nound and the controller the same with   A set of sentences are exemplified below.
+
+\begin{exe}
+\ex
+\begin{xlist}
+\ex \underline{Grammatical, SG attractor} \label{exp1}
+\gll Komedyen-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}.\\
+comedian-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}-$\varnothing$\\
+\glt Because of the northeaster, comedian's assistant felt chilly.
+
+\ex \underline{Grammatical, PL attractor} \label{exp2}
+\gll Komedyen-ler-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}.\\
+comedian-\textsc{pl}-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}-$\varnothing$\\
+\glt Because of the northeaster, comedians' assistant felt chilly.
+
+\ex \underline{Ungrammatical, PL attractor} \label{exp3}
+\gll Komedyen-ler-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}-ler.\\
+comedian-\textsc{pl}-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}--\textsc{pl}\\
+\glt Because of the northeaster, comedians' assistant felt chilly.
+
+\ex \underline{Ungrammatical, SG attractor} \label{exp4}
+\gll Komedyen-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}-ler.\\
+comedian-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}-\textsc{pl}\\
+\glt Because of the northeaster, comedian's assistant felt chilly.
+
+\end{xlist}
+\end{exe}
+
+As seen in the examples unlike @Lago's experimental items, all of our items bear the *-sI* possessive marker instead of the ambiguous *-I* one.
+As for the filler items, we could not used or adapt from the original experimentsince the fillers of the original study were not online.
+We have used two types filler sentences: a grammatical ones where the verb bears plural agreement (\ref{fillera}), and an ungrammatical one where verb does not bear plural agreement (\ref{fillerb}).
+We wanted to nullify a possible strategy by the participants where they associate the sentence-final morpheme directly with the acceptability, and disregard other elements in the sentences when answering questions.
+
+\begin{exe}
+\ex
+\begin{xlist}
+\ex \label{fillera}
+\gll Adam-{\i}n anne-si fena-la\c{s}-{\i}nca inek kurban et-ti-ler.\\
+man-\textsc{gen} mother-\textsc{poss} bad-\textsc{vrb}-\textsc{cvb} cow sacrifice do-\textsc{pst}-\textsc{pl}\\
+\glt When his mother got ill, (they) sacrificed a cow.
+\ex \label{fillerb}
+\gll *Pizzac{\i}-n{\i}n kurye-si t\"{o}kezle-yince sos-lar yer-e sa\c{c}-t{\i}.\\
+pizzaria-\textsc{gen} courier-\textsc{poss} trip-\textsc{cvb} sauce-\textsc{pl} floor-\textsc{dat} scatter-\textsc{pst}\\
+\glt Intended: When the pizza boy tripped, sauces scattered around. 
+\end{xlist}
+\end{exe}
+
+All of our data, experimental materials, our experiment design, and as well as our fillers can be found at the Center for Open Science Framework website (https://osf.io/).
+
+## Participants and Procedure
+
+One hundred seven Turkish speakers with mean age of X were recruited from the Bogazici University in {\.I}stanbul.
+We did not collect participants' knowledge of other languages; however, we ensured that Turkish is their native language and they predominantly used in their daily lives.
+In the experiments, participants are asked to judge the experimental and filler sentences whether or not they sound acceptable in Turkish.
+All of the sentences were presented one word at a time in the center area of the screen for 500 ms per word unlike @Lago and @Wagers2009, in which researches used 300 ms visual presentation per word.
+Experiment was run on a web-based platform Ibex Farm, and all of the documentation can be found in our osf and github page.
+
+Before the experiment, they have been instructed to give accurate and quick answers with their own intuition, and they were also notified about the time limit for answering.
+At the start of the experiment they were given 4 practice items with feedbacks.
+
+What to write about analyze?
+
 ## Results and Discussion
+
+In \textsc{Figure} (\ref{fig:replication}), y-axis shows proportion of "acceptable" answers, and x-axis indicates whether or not the sentences in that group is grammatical.
+Moreover, linetypes indicates an attractor noun with overt plural morphology.
+As seen from the figure, `r round(100*dataAvClean[1,7])`% of the sentences with plural attractors and singular verb were accepted by the participants following the findings of @Lago.
+We also see a number attraction rate of `r round(100*(dataAvClean[1,7]-dataAvClean[3,7]))`% which was already shown in @Lago with close results.
+
+In \textsc{Table} (\ref{tab:replication}), ............
+
+\begin{figure}[H]
+  \begin{floatrow}
+    \ffigbox{%
+```{r, fig.align = "right", echo = F}
+print{}
+```
+    }{\caption{A figure}}
+
+    \btabbox{%
+```{r, fig.align = "right", echo = F}
+knitr::kable(head(mtcars[,1:3]), format = "latex")
+```
+    }{\caption{A table}}
+  \end{floatrow}
+\end{figure}
 

### 2019-01-24 Paper/AgreementAttraction.tex
paperwriting

@@
 \usepackage{qtree}
+
+% for figure and table side by side
+\usepackage{floatrow}
+\newfloatcommand{btabbox}{table}
 
@@
 ranging between 11\%--15\% across monolinguals. As seen from the results
-of statistical analysis in Table (\ref{lagomodel}), acceptability
-judgments showed an immense effect of grammaticality, and there is also
-interaction between grammaticality and attractor number which indicates
-an number attraction effect.
+of statistical analysis in \textsc{Table} (\ref{lagomodel}),
+acceptability judgments showed an immense effect of grammaticality, and
+there is also interaction between grammaticality and attractor number
+which indicates an number attraction effect.
 
-\begin{table}[]
+\begin{table}[!hbt]
 \centering
@@
 see genitive marked subjects in Turkish embedded clauses, as in example
-(\ref{gensubj}).
+(\ref{gensubj}). Unlike English, genitive case is compatible with the
+subjecthood in English. Thus, Lago (2018) attributes the robust
+agreement attraction effects to the case information.
 
@@
 
-\hypertarget{motivation}{%
-\subsection{Motivation}\label{motivation}}
+However, our first hypothesis was the possibility of participants
+engaging in a shallow processing, which ends up in a situation where not
+only genitive case but also possessive case plays a significant role in
+delivering the case information. None of the experimental items in Lago
+(2018) has a head noun which ends with a vowel; thus, all of the
+possessive markers are morphologically and phonologically ambiguous
+between the accusative case and the possessive. Unlike genitive case,
+the accusative case in Turkish is extremely rare to see on the head noun
+of the subject, which only occurs in the raising predicates as in
+example (\ref{dsm}).
 
-\hypertarget{modifications}{%
-\subsection{Modifications}\label{modifications}}
+\begin{exe}
+\ex \label{dsm}
+\gll Ben sen-i git-ti-n san-d{\i}-m\\
+I you-\textsc{acc} go-\textsc{pst}-\textsc{2Sg} suppose-\textsc{pst}-\textsc{1Sg}\\
+\glt I thought you were gone.
+\end{exe}
 
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
+In order to test this hypothesis, we have replicated the Lago (2018)
+study with modified items, where the possessive is not ambiguous with
+the accusative case. We have tried to be as faithful as possible to the
+original sentences while trying to make sentences as plauisable as
+possible at the same time. We keep the semantic relation between the
+head nound and the controller the same with A set of sentences are
+exemplified below.
 
-\hypertarget{filler-items}{%
-\subsection{Filler Items}\label{filler-items}}
+\begin{exe}
+\ex
+\begin{xlist}
+\ex \underline{Grammatical, SG attractor} \label{exp1}
+\gll Komedyen-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}.\\
+comedian-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}-$\varnothing$\\
+\glt Because of the northeaster, comedian's assistant felt chilly.
+
+\ex \underline{Grammatical, PL attractor} \label{exp2}
+\gll Komedyen-ler-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}.\\
+comedian-\textsc{pl}-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}-$\varnothing$\\
+\glt Because of the northeaster, comedians' assistant felt chilly.
+
+\ex \underline{Ungrammatical, PL attractor} \label{exp3}
+\gll Komedyen-ler-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}-ler.\\
+comedian-\textsc{pl}-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}--\textsc{pl}\\
+\glt Because of the northeaster, comedians' assistant felt chilly.
+
+\ex \underline{Ungrammatical, SG attractor} \label{exp4}
+\gll Komedyen-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}-ler.\\
+comedian-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}-\textsc{pl}\\
+\glt Because of the northeaster, comedian's assistant felt chilly.
+
+\end{xlist}
+\end{exe}
+
+As seen in the examples unlike Lago (2018)'s experimental items, all of
+our items bear the \emph{-sI} possessive marker instead of the ambiguous
+\emph{-I} one. As for the filler items, we could not used or adapt from
+the original experimentsince the fillers of the original study were not
+online. We have used two types filler sentences: a grammatical ones
+where the verb bears plural agreement (\ref{fillera}), and an
+ungrammatical one where verb does not bear plural agreement
+(\ref{fillerb}). We wanted to nullify a possible strategy by the
+participants where they associate the sentence-final morpheme directly
+with the acceptability, and disregard other elements in the sentences
+when answering questions.
+
+\begin{exe}
+\ex
+\begin{xlist}
+\ex \label{fillera}
+\gll Adam-{\i}n anne-si fena-la\c{s}-{\i}nca inek kurban et-ti-ler.\\
+man-\textsc{gen} mother-\textsc{poss} bad-\textsc{vrb}-\textsc{cvb} cow sacrifice do-\textsc{pst}-\textsc{pl}\\
+\glt When his mother got ill, (they) sacrificed a cow.
+\ex \label{fillerb}
+\gll *Pizzac{\i}-n{\i}n kurye-si t\"{o}kezle-yince sos-lar yer-e sa\c{c}-t{\i}.\\
+pizzaria-\textsc{gen} courier-\textsc{poss} trip-\textsc{cvb} sauce-\textsc{pl} floor-\textsc{dat} scatter-\textsc{pst}\\
+\glt Intended: When the pizza boy tripped, sauces scattered around. 
+\end{xlist}
+\end{exe}
+
+All of our data, experimental materials, our experiment design, and as
+well as our fillers can be found at the Center for Open Science
+Framework website (\url{https://osf.io/}).
+
+\hypertarget{participants-and-procedure}{%
+\subsection{Participants and
+Procedure}\label{participants-and-procedure}}
+
+One hundred seven Turkish speakers with mean age of X were recruited
+from the Bogazici University in \{.I\}stanbul. We did not collect
+participants' knowledge of other languages; however, we ensured that
+Turkish is their native language and they predominantly used in their
+daily lives. In the experiments, participants are asked to judge the
+experimental and filler sentences whether or not they sound acceptable
+in Turkish. All of the sentences were presented one word at a time in
+the center area of the screen for 500 ms per word unlike Lago (2018) and
+Wagers et al. (2009), in which researches used 300 ms visual
+presentation per word. Experiment was run on a web-based platform Ibex
+Farm, and all of the documentation can be found in our osf and github
+page.
+
+Before the experiment, they have been instructed to give accurate and
+quick answers with their own intuition, and they were also notified
+about the time limit for answering. At the start of the experiment they
+were given 4 practice items with feedbacks.
+
+What to write about analyze?
 
@@
 
+In \textsc{Figure} (\ref{fig:replication}), y-axis shows proportion of
+``acceptable'' answers, and x-axis indicates whether or not the
+sentences in that group is grammatical. Moreover, linetypes indicates an
+attractor noun with overt plural morphology. As seen from the figure,
+22\% of the sentences with plural attractors and singular verb were
+accepted by the participants following the findings of Lago (2018). We
+also see a number attraction rate of 10\% which was already shown in
+Lago (2018) with close results.
+
+In \textsc{Table} (\ref{tab:replication}),
+\ldots{}\ldots{}\ldots{}\ldots{}
+
+\begin{figure}[H]
+  \begin{floatrow}
+    \ffigbox{%
+
+\begin{flushright}\includegraphics{output/figures/unnamed-chunk-1-1} \end{flushright}
+    }{\caption{A figure}}
+
+    \btabbox{%
+
+\begin{tabular}{l|r|r|r}
+\hline
+  & mpg & cyl & disp\\
+\hline
+Mazda RX4 & 21.0 & 6 & 160\\
+\hline
+Mazda RX4 Wag & 21.0 & 6 & 160\\
+\hline
+Datsun 710 & 22.8 & 4 & 108\\
+\hline
+Hornet 4 Drive & 21.4 & 6 & 258\\
+\hline
+Hornet Sportabout & 18.7 & 8 & 360\\
+\hline
+Valiant & 18.1 & 6 & 225\\
+\hline
+\end{tabular}
+    }{\caption{A table}}
+  \end{floatrow}
+\end{figure}
+
 \hypertarget{experiment-2-rc-attractor}{%
@@
 
-\hypertarget{motivation-1}{%
-\subsection{Motivation}\label{motivation-1}}
+\hypertarget{motivation}{%
+\subsection{Motivation}\label{motivation}}
 
@@
 computing. R Foundation for Statistical Computing, Vienna, Austria.
+
+\leavevmode\hypertarget{ref-Wagers2009}{}%
+Wagers, M. W., E. F. Lau, and C. Phillips. 2009. Agreement attraction in
+comprehension: Representations and processes. Journal of Memory and
+Language 61:206--237.
 

### 2019-01-24 Results and Analysis/playing a bit.R

@@ -95,7 +95,7 @@ Response[late_response] = NA
 ResponseCorrect[late_response] = NA
 })
 
-responses <- c(yes="ÝYÝ (P'ye basýnýz)", no="KÖTÜ (Q'ya basýnýz)")
+responses <- c(yes="?Y? (P'ye bas?n?z)", no="K?T? (Q'ya bas?n?z)")
 stopifnot( all(data$Response %in% responses | is.na(data$Response) ) )
 
 data$ResponseYes <- ifelse(grepl("P",data$Response) , T, 
@@ -167,6 +167,7 @@ dataAvClean <- data %>% subset(!Subject %in% bad_subjects)%>%
   group_by(experiment, condition, grammatical, verb_num, attracted) %>%
   summarize(avRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T)) %>% 
   as.data.frame()
+dataAvClean <- slice(dataAvClean, 1:4)
 
 dataAvClean %>% ggplot(aes(grammatical, p_yes, group = paste(experiment,attracted), color = experiment )) + geom_point() + geom_line(aes(linetype =attracted)) #+ facet_wrap(~experiment, scales = "free_y")
 

### 2019-01-25 Paper/AgreementAttraction.Rmd
firstdraft of a firstdraft

@@
 
-In this paper, our objective is to explore the source of agreement attraction effects in Turkish found by @Lago.
-The interpretation of their finding is complicated by the fact that in their possessive form all head nouns in their stimuli are morphologically ambiguous between possessive and accusative.
-Due to the mismatch in the frequency of usage of accusative and genitive, which is used as a attractor in this experiment, as a controller, @Lago's findings could potentially be explained with occasional shallow processing.
-We have replicated @Lago's experiment with unambigious head nouns, and we have found the same agreement attraction effects.
-However, this may mean that participants may engage in even more shallow processing than we imagined.
+In this paper, our objective is to explore the source of agreement attraction effects in Turkish discovered by @Lago.
+The interpretation of their finding is complicated by the fact that the possessive form of all head nouns used in their stimuli are morphologically ambiguous between possessive and accusative.
+In Turkish, genitive can be productively used for marking the subject of an embedded clause whereas accusative is rarely used for marking the subject.
+Due to this mismatch in the frequency of usage of accusative and genitive, which is used as a attractor in this experiment, as a controller, @Lago's findings could potentially be explained with occasional shallow processing.
+We have replicated @Lago's experiment with unambigious head nouns, and we have found similar agreement attraction effects.
+However, this may mean that participants engage in even more shallow processing than we imagined.
 We postulate that participants solely check for the presence of a *-lAr* morpheme, while largely disregarding the remainder of the sentence.
-We utilize an experiment design in which we use a relative clause with or without plural agreement on the verb in place of the genitive possessor since both verbal and nominal plural morphemes are the same in Turkish.
-If participants did, in fact, adopt a superficial processing strategy, we would expect to find a number agreement attraction effect similar in magnitude to @Lago's.
-However, if number attraction is not an artifact of shallow processing strategies, we should expect to find no number attraction in this experiment.
+We utilize an experiment design in which we use a relative clause with or without plural agreement on the verb in place of the genitive possessor since both verbal and nominal plural morphemes are the same in Turkish, i.e.
+the exponent of both is *-lAr*.
+If participants did, in fact, adopt a superficial processing strategy, we would expect to find a number agreement attraction effect similar in magnitude to that in @Lago.
+However, if number attraction is not an artifact of shallow processing strategies, we should expect to find no number attraction effects in this experiment.
 
@@
 
-Attraction errors in production and comprehension of subject-verb agrrement, in which a verb does not agree with the grammatical agreement controller, but with a potential attractors, have been the focal point of many research for quite a long time.
-In fact, it is still a widely researched are in psycholinguistic studies.
-Despite the thorough research that has been carried out, studies that have been conducted on agreement attraction in Turkish have been extremely few.
-In fact, @Lago has been the only study to look into this phenomenon in Turkish.
-@Lago's study make use of genitive-possessive structures in the subject position, in which the possessive-marked noun is the head of the noun phrase which acts as the grammatical agreement controller, and the genitive noun serves as a potential attractor.
-In a speeded acceptability judgment study, they found a significant effect of number agreement attraction.
-However, the interpretation of their finding may be a result of a non-subjecthood cues originating from their use of morphologically ambiguous forms of possessive.
-In their possessive form all head nouns in their stimuli are ambigiuous between possessive and accusative.
+Attraction errors in the production and comprehension of subject-verb agreement, in which a verb does not agree with the grammatical agreement controller, but with a potential attractor, have been the main topic of research in many studies for quite a long time.
+In fact, it is still a widely researched area in psycholinguistic studies.
+Despite the comprehensive research that has been carried out, studies that have been conducted on agreement attraction in Turkish have been very limited.
+In fact, @Lago is currently the only study that explores this phenomenon in Turkish.
+@Lago  makes use of genitive-possessive structures in the subject position, in which the possessive-marked noun is the head of the noun phrase which acts as the grammatical agreement controller, and the genitive noun serves as a potential attractor.
+In a speeded acceptability judgment study, @Lago found a significant effect of number agreement attraction.
+However, the interpretation of their findings may be a result of the fact that non-subjecthood cues originate from their use of morphologically ambiguous forms of the possessive.
+In the possessive forms that are used, all the head nouns in their stimuli are ambigiuous between possessive and accusative.
 
 In Turkish, accusative number agreement controllers are extremely rare, while genitive agreement controllers are very frequent.
-Thus, @Lago's finding could possibly be explained by occasional shallow processing.
-When all syntactic relations in the sentence were processed fully, the possessive noun should have been identified as the controller.
-Meanwhile the genitive noun may sometimes have been erroneously identified as the controller during shallow processing, because genitives are more likely to act as agreement controllers than accusatives.
-A second alternative explanation of @Lago's finding may be the fact that participants may engage in even more shallow processing than outlined above.
-Participants may have erroneously responded *Yes* on some trials due to (i) the presence of a plural morpheme on a noun (attractor or controller) and (ii) the presence of a plural agreement morpheme on the verb.
-We speculate that on such trials, participants would have simply tried to check for the presence of such morphemes, while largely disregarding the remainder of the sentence.
+Thus, @Lago's finding could potentially be explained with occasional shallow processing.
+When all syntactic relations in the sentence were processed fully, the possessive noun may have been identified as the controller.
+Meanwhile, the genitive noun may sometimes have been erroneously identified as the controller during shallow processing because genitives are more likely to act as agreement controllers than accusatives (SOURCE).
+A second alternative explanation for @Lago's findings may be the fact that participants may engage in even more shallow processing than outlined above.
+Participants may have erroneously responded *Yes* on some trials for two main reasons: (i) the presence of a plural morpheme on a noun (attractor or controller), and (ii) the presence of a plural agreement morpheme on the verb.
+We speculate that in such trials, participants would have simply tried to check for the presence of such morphemes, while largely disregarding the remainder of the sentence.
 
-We first replicated @Lago's experiment with unambiuous head nouns.
-To this end, we have revised the items that were used previously, to avoid morphological ambiguity between possessive and accusative forms.
-The effect found by @Lago replicates with unambiguous nouns as discused in \S 2.
+We first replicated @Lago's experiment with unambiguous head nouns.
+To this end, we revised the items that were used previously in order to avoid morphological ambiguity between possessive and accusative forms.
+The effect found in @Lago was also observed when unambiguous nouns were used, as will be discussed in \S 2.
 
-\S 3 discussses the alternative account that posits even more shallow processing as mentioned above and offers a pre-registered experiment using RC attractors with possible outcomes and their indications.
-Since both nominal and verbal plural morphemes in Turkish take on the same form (*-ler* or *-lar* depending on the phonological environment), we can test this possibility with an experiment, in which we use relative clause with or without plural agreement on the verb in the place of the genitive possessors.
-An agreement attraction effect similar in magnitude to @Lago's would mean that participants use aforementioned strategies.
+\S 3 discusses the alternative account that posits even more shallow processing as mentioned above and presents a pre-registered experiment using RC attractors with potential outcomes and their indications.
+Since both nominal and verbal plural morphemes in Turkish are expressed with the same form (*-ler* or *-lar* depending on the phonological environment), we can test this possibility with an experiment in which a relative clause with or without plural agreement on the verb in place of the genitive possessors is used.
+An agreement attraction effect similar in magnitude to that observed in @Lago would indicate that participants use the aforementioned strategies.
 
-\S 4 presents a discussion revolving around possible 
-Lastly, \S 5 offers a brief conclusion and presents topics for future researches.
+\S 4 offers a discussion of the issue of number attraction and where this experiments leaves us. Lastly, \S 5 presents a brief conclusion and topics for future research.
 
-# REPLICATON OF @Lago
+# REPLICATON OF LAGO ET AL. (2018)
 
-In their study, @Lago investigated the comprehension of subject-verb agreement in Turkish-German bilinguals and Turkish monolinguals.
-They used speeded acceptability judments for the effects of number attraction in Turkish.
-Their sentences makes us of genitive-possessive constructions in the subject position, where the genitive is the attractor and the possessive is the head noun.
-They have manipulated the grammaticality of the sentence by changing the plural morphology of the verb, and they also manipulated the plurality of the attractor noun.
-In grammatical conditions, subject and the verb both bears the singular morphology with no overt morpheme.
-Moreover, in the ungrammatical conditions the verb bears the overt *-lAr* morpheme whereas the subject is still singular as exemplified below.
+In their study, @Lago investigate the comprehension of subject-verb agreement in Turkish-German bilinguals and Turkish monolinguals.
+They use speeded acceptability judgments for the effects of number attraction in Turkish.
+Their sentences make us of genitive-possessive constructions in the subject position, where the genitive is the attractor and the possessive is the head noun.
+They manipulate the grammaticality of the sentence by changing the plural morphology of the verb, and they also manipulate the plurality of the attractor noun.
+In grammatical conditions, the subject and the verb both bear singular morphology with no overt morpheme.
+Moreover, in the ungrammatical conditions, the verb bears the overt *-lAr* morpheme whereas the subject is still singular as exemplified below.
 
@@
 
-They have found a significant effect of number attraction in Turkish ranging between 11%--15% across monolinguals.
-As seen from the results of statistical analysis in \textsc{Table} (\ref{lagomodel}), acceptability judgments showed an immense effect of grammaticality, and there is also interaction between grammaticality and attractor number which indicates an number attraction effect.
+They found a significant effect of number attraction in Turkish ranging between 11\%--15\% across monolinguals.
+As seen in the results of the statistical analysis in \textsc{Table} (\ref{lagomodel}), the acceptability judgments showed an immense effect of grammaticality, and there is also interaction between grammaticality and attractor number, which indicates the presence of a number attraction effect.
 
@@
 
-According to @Lago's stipulation, Turkish genitive case does not provide a strong cue against subjecthood since it is extremely common to see genitive marked subjects in Turkish embedded clauses, as in example (\ref{gensubj}).
-Unlike English, genitive case is compatible with the subjecthood in English.
-Thus, @Lago attributes the robust agreement attraction effects to the case information.
+@Lago stipulate that the Turkish genitive case does not provide a strong cue against subjecthood since Turkish frequently makes use of genitive marked subjects in embedded clauses, as in example (\ref{gensubj}).
+This is in contrast with English, in which the genitive case is compatible with subjecthood.
+Thus, @Lago argue that this robust agreement attraction effect has been linked to the case information carried by accusative and genitive.
 
@@
 
-However, our first hypothesis was the possibility of participants engaging in a shallow processing, which ends up in a situation where not only genitive case but also possessive case plays a significant role in delivering the case information.
-None of the experimental items in @Lago has a head noun which ends with a vowel; thus, all of the possessive markers are morphologically and phonologically ambiguous between the accusative case and the possessive.
-Unlike genitive case, the accusative case in Turkish is extremely rare to see on the head noun of the subject, which only occurs in the raising predicates as in example (\ref{dsm}).
+However, our initial hypothesis postulates that participants engage in shallow processing, which results in a situation in which not only the genitive case but also the possessive case plays a significant role in delivering the case information.
+None of the experimental items in @Lago have a head noun which ends with a vowel; thus, all of the possessive markers are morphologically and phonologically ambiguous between the accusative case and the possessive.
+Unlike genitive case, it is extremely rare for the accusative case to appear on the head noun of the subject, which only occurs in raising predicates as in example (\ref{dsm}).
 
@@
 
-In order to test this hypothesis, we have replicated the @Lago study with modified items, where the possessive is not ambiguous with the accusative case.
-We have tried to be as faithful as possible to the original sentences while trying to make sentences as plauisable as possible at the same time.
-We keep the semantic relation between the head nound and the controller the same with   A set of sentences are exemplified below.
+In order to test this hypothesis, we have replicated the experiment of @Lago with modified items, in which the possessive is not ambiguous with the accusative case.
+We tried to be as faithful as possible to the original sentences while also trying to make the sentences as plausable as possible.
+We keep the semantic relation between the head noun and the controller the same with what has been described in @Lago's study, which is either a relation regarding profession or a service that is given by the head noun for the possessor.
+A set of sentences are exemplified below.
 
@@
 
-As seen in the examples unlike @Lago's experimental items, all of our items bear the *-sI* possessive marker instead of the ambiguous *-I* one.
-As for the filler items, we could not used or adapt from the original experimentsince the fillers of the original study were not online.
-We have used two types filler sentences: a grammatical ones where the verb bears plural agreement (\ref{fillera}), and an ungrammatical one where verb does not bear plural agreement (\ref{fillerb}).
-We wanted to nullify a possible strategy by the participants where they associate the sentence-final morpheme directly with the acceptability, and disregard other elements in the sentences when answering questions.
+As seen in the examples, unlike @Lago's experimental items, all of our items bear the *-sI* possessive marker instead of the ambiguous *-I* marker.
+As for the filler items, we could not use or modify the original experiment items since the fillers of the original study were not online.
+We have used two types filler sentences: grammatical sentences in which the verb bears plural agreement (\ref{fillera}), and ungrammatical sentences in which the verb does not bear plural agreement (\ref{fillerb}).
+We wanted to nullify a possible strategy by the participants where they associate the sentence-final morpheme directly with the acceptability of the sentence.
+And we also wanted to eliminate the possibility of participants disregarding other elements in the sentences while answering the questions we ask right after the sentence.
 
@@
 
-All of our data, experimental materials, our experiment design, and as well as our fillers can be found at the Center for Open Science Framework website (https://osf.io/).
+All of our data, experimental materials, our experiment design, and our fillers can be found on the website of the Center for Open Science Framework (https://osf.io/).
 
@@
 
-One hundred seven Turkish speakers with mean age of X were recruited from the Bogazici University in {\.I}stanbul.
-We did not collect participants' knowledge of other languages; however, we ensured that Turkish is their native language and they predominantly used in their daily lives.
-In the experiments, participants are asked to judge the experimental and filler sentences whether or not they sound acceptable in Turkish.
-All of the sentences were presented one word at a time in the center area of the screen for 500 ms per word unlike @Lago and @Wagers2009, in which researches used 300 ms visual presentation per word.
-Experiment was run on a web-based platform Ibex Farm, and all of the documentation can be found in our osf and github page.
+One hundred and seven Turkish speakers with a mean age of X were recruited from Bogazici University in İstanbul.
+We did not collect participants' knowledge of other languages; however, we verified that Turkish is their native language and that they predominantly use it in their daily lives.
+In the experiments, participants were asked to judge the acceptability of experimental and filler sentences in Turkish.
+All of the sentences were presented one word at a time in the center of the screen for 500 ms per word unlike @Lago and @Wagers2009, in which the duration was 300 ms per word.
+The experiment was run on a web-based platform titled the Ibex Farm, and all of the documentation can be found on our osf and github page.
 
-Before the experiment, they have been instructed to give accurate and quick answers with their own intuition, and they were also notified about the time limit for answering.
-At the start of the experiment they were given 4 practice items with feedbacks.
+Before the experiment, participants were instructed to give accurate and quick answers based on their own intuitions, and they were also notified about the time limit for answering.
+At the start of the experiment, they were given 4 practice items with feedback.
 
@@
 
-In \textsc{Figure} (\ref{fig:replication}), y-axis shows proportion of "acceptable" answers, and x-axis indicates whether or not the sentences in that group is grammatical.
-Moreover, linetypes indicates an attractor noun with overt plural morphology.
-As seen from the figure, `r round(100*dataAvClean[1,7])`% of the sentences with plural attractors and singular verb were accepted by the participants following the findings of @Lago.
-We also see a number attraction rate of `r round(100*(dataAvClean[1,7]-dataAvClean[3,7]))`% which was already shown in @Lago with close results.
+In \textsc{Figure} (1), the y-axis shows the percentage of "acceptable" answers, and the x-axis indicates whether or not the sentences in that group are grammatical.
+Moreover, the linet ypes indicate an attractor noun with overt plural morphology.
+As seen in the figure, `r round(100*dataAvClean[1,7])`% of the sentences with plural attractors and a singular verb were accepted by the participants, in line with the findings of @Lago.
+We also see a number attraction rate of `r round(100*(dataAvClean[1,7]-dataAvClean[3,7]))`% which was also observed in @Lago with close results.
 
@@
 
+And yes, I plan to beautify the figures.
 \begin{figure}[H]
@@
     \ffigbox{%
-```{r, fig.align = "right", echo = F}
-print{}
+```{r, fig.width = 4 , fig.height = 4 , fig.align = "right", echo = F}
+print(plot_average)
 ```
@@
 ```{r, fig.align = "right", echo = F}
-knitr::kable(head(mtcars[,1:3]), format = "latex")
+
 ```
@@
 # EXPERIMENT 2: RC ATTRACTOR
-## Motivation
-## Items and Fillers
+
+Even though our first hypothesis regarding shallow processing did not hold, we still need to entertain the second possibility we have discussed in this paper.
+Participants may indeed engage in an even shallower process of sentence comprehension, in which they merely match the use of *-lAr*.
+Moreover, we still need to discuss how much it is an effect of case information rather than only a number attraction.
+We have seen that the anti-subjecthood cues of the accusative are not significant since in both cases where the possessive is ambiguous with the accusative and the possessive is clearly marked, we have observed extremely close results in the speeded acceptability judgments.
+
+In order to check both the sole effect of number agreement and the possibility of a task effect, we propose an experiment design in which a head noun is a bare NP, is not marked with any other morpheme and preceded by a relative clause construction.
+This relative clause consists of only a verbal component, which bears an overt plural marker.
+Since Turkish verbal and nominal plural morphemes are identical, we plan to check the participants' strategy with regards to whether or not it is a cue that helps in the reconstruction of the ungrammatical sentence or whether it is merely a task effect in which participants disregard the rest of the sentence and focus the existence of the morpheme *-lAr*.
+
+## Materials
+
+Like genitive-possessive structures, attractors do not intervene between the grammatical agreement controller and the verb in relative clause constructions.
+Turkish relative clauses always precede the head noun, except for in special cases in which they are marked with unique prosody.
+Item (\ref{rcexample}) is an example of a RC structure, and item (\ref{rcexample2}) shows the possibility of using only the verbal component of the relative clause since it is grammatical to drop arguments in Turkish.
+( add a footnote here giving the details of such events, and restrictions.
+)
+
+\begin{exe}
+\ex
+\begin{xlist}
+\ex \label{rcexample}
+\gll On-lar-{\i}n ev-e gel-me-den g\"{o}r-d\"{u}k-ler-i \c{c}ocuk so\u{g}uk-ta \"{u}\c{s}\"{u}-m\"{u}\c{s}-t\"{u}.\\
+they-\textsc{pl}-\textsc{gen} home-\textsc{dat} come-\textsc{neg}-\textsc{abl} see-\textsc{nlmz}-\textsc{pl}-\textsc{poss} kid cold--\textsc{loc} feel.chilly-\textsc{perf}-\textsc{pst}\\
+\glt The kid that they saw right before coming to home was feeling chilly. 
+\ex \label{rcexample2}
+\gll G\"{o}r-d\"{u}k-ler-i \c{c}ocuk so\u{g}uk-ta \"{u}\c{s}\"{u}-m\"{u}\c{s}-t\"{u}.\\
+see-\textsc{nlmz}-\textsc{pl}-\textsc{poss} kid cold--\textsc{loc} feel.chilly-\textsc{perf}-\textsc{pst}\\
+\glt The kid that they saw home was feeling chilly.
+\end{xlist}
+\end{exe}
+
+As for the experimental sentences, we plan to use sentences that are similar to the ones used in @Lago.
+Instead of a genitive controller, we utilize an RC, which we manipulate for its values for bearing the plural morpheme.
+The head noun of the subject is always singular, and it is followed by a 2/3 word adverbial.
+Moreover, the matrix verb of the sentences is also manipulated in terms of plurality, deeming the sentence grammatical or ungrammatical.
+Lastly, the relative clause has to be an object relative clause, since Turkish subject relative clauses never bear a plural morpheme on the embedded verb.
+As in the @Lago's study and our replication, we will have a four condition, where we manipulate the plurality of the attractor (*plural/singular*) and the grammaticality of the sentece by using overt plural morphology (*grammatical/ungrammatical*), which are demonstrated with item (\ref{reg1}), (\ref{reg2}), (\ref{reg3}), and (\ref{reg4})
+
+\begin{exe}
+\ex
+\begin{xlist}
+\ex \underline{Grammatical, SG attractor} \label{reg1}
+\gll D\"{o}v-d\"{u}\u{g}-\"{u} \c{c}ocuk mutfak-ta bayg{\i}n hal-de yat-{\i}yor-du.\\
+beat-\textsc{nmlz}-\textsc{poss} kid kitchen-\textsc{loc} unconscious state-\textsc{loc} lie-\textsc{prog}-\textsc{pst}\\ 
+\glt The kid that he/she beats was laying in the kitchen unconscious.
+\ex \underline{Grammatical, PL attractor} \label{reg2}
+\gll D\"{o}v-d\"{u}k-ler-i \c{c}ocuk mutfak-ta bayg{\i}n hal-de yat-{\i}yor-du.\\
+beat-\textsc{nmlz}-\textsc{pl}-\textsc{poss} kid kitchen-\textsc{loc} unconscious state-\textsc{loc} lie-\textsc{prog}-\textsc{pst}\\
+\glt The kid that they beat was laying in the kitchen unconscious.
+\ex \underline{Ungrammatical, PL attractor} \label{reg3}
+\gll D\"{o}v-d\"{u}k-ler-i \c{c}ocuk mutfak-ta bayg{\i}n hal-de yat-{\i}yor-lar-d{\i}.\\
+beat-\textsc{nmlz}-\textsc{pl}-\textsc{poss} kid kitchen-\textsc{loc} unconscious state-\textsc{loc} lie-\textsc{prog}-\textsc{pl}-\textsc{pst}\\
+\glt Intended: The kid that they beat were laying in the kitchen unconscious.
+\ex \underline{Ungrammatical, SG attractor} \label{reg4}
+\gll D\"{o}v-d\"{u}\u{g}-\"{u} \c{c}ocuk mutfak-ta bayg{\i}n hal-de yat-{\i}yor-lar-d{\i}.\\
+beat-\textsc{nmlz}-\textsc{poss} kid kitchen-\textsc{loc} unconscious state-\textsc{loc} lie-\textsc{prog}-\textsc{pl}-\textsc{pst}\\
+\glt Intended: The kid that he/she beats were laying in the kitchen unconscious.
+\end{xlist}
+\end{exe}
+
+As for the fillers, we need two different set of fillers in order to counterbalance the ever-present grammaticality of singular and plural verbs.
+For grammatical fillers with a plural verb (example (\ref{fillerreg1})) we propose a structure in which the head noun is followed by a converb.
+With this modification, the controller of the experimental sentences becomes a controller for a subclause, and the main verb is saturated with another subject introduced right after the subclause.
+
+For ungrammatical fillers with a singular verb (example (\ref{fillerreg2})), we have used strictly transitive verbs without an overt object.
+By utilizing the same structure with the other type of fillers, we ensure that participants will not come up with a strategy in which they always check the second word for dependency resolution.
+The controller of the fillers and the controller of the experimental items differ in the linear order they are shown in the experiment.
+
+Question: Can we do subject relative clause here? Like durdurulan ogrenci.
+
+\begin{exe}
+\ex
+\begin{xlist}
+\ex \label{fillerreg1}
+\gll Dur-dur-duk-lar-{\i} \"{o}\u{g}renci \c{s}a\c{s}{\i}r-{\i}nca arkada\c{s}-lar-{\i} birden g\"{u}l-d\"{u}-ler.\\
+stop-\textsc{caus}-\textsc{nmlz}-\textsc{pl}-\textsc{poss} student surprise-\textsc{cvb} friend-\textsc{pl}-\textsc{poss} suddenly laugh--\textsc{pst}-\textsc{pl}\\
+\glt When the student which was stopped surprised, his friends burst out laughing.
+\ex \label{fillerreg2}
+\gll *Tut-tuk-lar-{\i} a\c{s}\c{c}{\i} gel-me-yince dan{\i}\c{s}man-lar hala ver-di.\\
+hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss} cook come--\textsc{neg}-\textsc{cvb} advisor-\textsc{pl} still give-\textsc{pst}\\
+\glt Inteded: When the cook that they hired did not come, advisors did not still give. 
+\end{xlist}
+\end{exe}
+
+## Participants and Procedure
+
+We plan to have participants from the undergrad students of Bogazici University, which will be given an extra credit incentive.
+They will again carry out the experiment on an online experiment platform Ibex Farm.
+The experiment process will be exactly the same with the replication of @Lago, including descriptions before the experiment, the layout of the experiment, the time spared for visualization of every word, exclusion criteria, and analysis.
+
 ## Expectations
-## Possible Outcomes and Discussion
+
+(This part is extremely tentative)
+
+Our objective is to explore the number attraction phenomenon without the effects of case information and without the limits of nominal paradigm.
+By doing so, we expect participants to engage with the sentences which are ungrammatical in an extremely shallow fashion.
+We argue that instead of reconstructing the sentence utilizing every detail from the attractor and the controller, participants disregard the information from other sources in the sentence and look for a matching morpheme, i.e.
+*-lAr*.
+
+In the case that there will be a similar attraction effects with the replication of @Lago and @Lago study, we think that...
+what do we think?
+I need to talk about the paper and idea more thoroughly, I guess.
+Because I feel like I am repeating myself.
 
@@
 
-Intro and repeat.
+In this paper, we have entertained the idea of task effect in the so-called Turkish number attraction phenomenon.
+We argue that the findings of the @Lago study is not clear and there are too many variables to account for in the experiment, one of them being the ambiguous morphology that the head noun bears.
+In the first experiment, we have replicated the attraction task of @Lago.
+We have found the similar effects of agreement with a bigger pool of participants.
+Then, for entertaining the other possibility in which we argue that participants do not fully reconstruct the sentence; however, they make us of the direct cue of overt morpheme *-lAr*, we offer an experiment where we use object relative clauses as an attractor.
 
@@
 All graphs have been done with `ggplot` `r citep(citation("ggplot2"))`.
-Thank the Mine and Kadir for their student from courses.
+We also would like to thank Mine Nakipo\u{g}lu and Kadir Gökgöz for giving us the oppurtunity to conduct experiments and having participants from their classes.
 
@@
 
-\newpage
-
-```{r Table1, results='asis', echo=FALSE, cache=FALSE}
-kable(head(iris), caption = "A glimpse of the famous *Iris* dataset.")
-```
-
-\newpage
-
-```{r Table2, results='asis', echo=FALSE, cache=FALSE}
-kable(mtcars[10:16, ], caption = "Now a subset of mtcars dataset.")
-```
-
-\clearpage
-
 \listoffigures
-
-\newpage
-
-```{r Fig1, echo=FALSE, fig.cap="Just my first figure with a very fantastic caption.", cache=FALSE}
-x <- rnorm(100)
-y <- jitter(x, 1000)
-plot(x, y)
-```
-
-\newpage
-
-\blandscape
-
-```{r Fig2, echo=FALSE, fig.cap="Second figure in landscape format.", cache=FALSE}
-a <- sort(rnorm(100))
-b <- c(rep("Group Small", 35), rep("Group Big", 65))
-boxplot(a ~ b)
-```
-
-\elandscape
 

### 2019-01-25 Paper/AgreementAttraction.tex
firstdraft of a firstdraft

--- 2019-01-24 Paper/AgreementAttraction.tex
@@
 \usepackage[margin=1in]{geometry}
-\usepackage{longtable,booktabs}
-\usepackage{graphicx}
-% Redefine \includegraphics so that, unless explicit options are
-% given, the image width will not exceed the width of the page.
-% Images get their normal width if they fit onto the page, but
-% are scaled down if they would overflow the margins.
-\makeatletter
-\def\ScaleIfNeeded{%
-  \ifdim\Gin@nat@width>\linewidth
-    \linewidth
-  \else
-    \Gin@nat@width
-  \fi
-}
-\makeatother
-\let\Oldincludegraphics\includegraphics
-{%
- \catcode`\@=11\relax%
- \gdef\includegraphics{\@ifnextchar[{\Oldincludegraphics}{\Oldincludegraphics[width=\ScaleIfNeeded]}}%
-}%
 \ifxetex
@@
 
+% for figure and table side by side
+\usepackage{floatrow}
+\newfloatcommand{btabbox}{table}
+
 %%Fix tightlist error: https://stackoverflow.com/questions/40438037/tightlist-error-using-pandoc-with-markdown
@@
 In this paper, our objective is to explore the source of agreement
-attraction effects in Turkish found by Lago (2018). The interpretation
-of their finding is complicated by the fact that in their possessive
-form all head nouns in their stimuli are morphologically ambiguous
-between possessive and accusative. Due to the mismatch in the frequency
-of usage of accusative and genitive, which is used as a attractor in
-this experiment, as a controller, Lago (2018)'s findings could
-potentially be explained with occasional shallow processing. We have
-replicated Lago (2018)'s experiment with unambigious head nouns, and we
-have found the same agreement attraction effects. However, this may mean
-that participants may engage in even more shallow processing than we
-imagined. We postulate that participants solely check for the presence
-of a \emph{-lAr} morpheme, while largely disregarding the remainder of
-the sentence. We utilize an experiment design in which we use a relative
-clause with or without plural agreement on the verb in place of the
-genitive possessor since both verbal and nominal plural morphemes are
-the same in Turkish. If participants did, in fact, adopt a superficial
+attraction effects in Turkish discovered by Lago (2018). The
+interpretation of their finding is complicated by the fact that the
+possessive form of all head nouns used in their stimuli are
+morphologically ambiguous between possessive and accusative. In Turkish,
+genitive can be productively used for marking the subject of an embedded
+clause whereas accusative is rarely used for marking the subject. Due to
+this mismatch in the frequency of usage of accusative and genitive,
+which is used as a attractor in this experiment, as a controller, Lago
+(2018)'s findings could potentially be explained with occasional shallow
+processing. We have replicated Lago (2018)'s experiment with unambigious
+head nouns, and we have found similar agreement attraction effects.
+However, this may mean that participants engage in even more shallow
+processing than we imagined. We postulate that participants solely check
+for the presence of a \emph{-lAr} morpheme, while largely disregarding
+the remainder of the sentence. We utilize an experiment design in which
+we use a relative clause with or without plural agreement on the verb in
+place of the genitive possessor since both verbal and nominal plural
+morphemes are the same in Turkish, i.e.~the exponent of both is
+\emph{-lAr}. If participants did, in fact, adopt a superficial
 processing strategy, we would expect to find a number agreement
-attraction effect similar in magnitude to Lago (2018)'s. However, if
-number attraction is not an artifact of shallow processing strategies,
-we should expect to find no number attraction in this experiment.
+attraction effect similar in magnitude to that in Lago (2018). However,
+if number attraction is not an artifact of shallow processing
+strategies, we should expect to find no number attraction effects in
+this experiment.
 
@@
 
-Attraction errors in production and comprehension of subject-verb
-agrrement, in which a verb does not agree with the grammatical agreement
-controller, but with a potential attractors, have been the focal point
-of many research for quite a long time. In fact, it is still a widely
-researched are in psycholinguistic studies. Despite the thorough
-research that has been carried out, studies that have been conducted on
-agreement attraction in Turkish have been extremely few. In fact, Lago
-(2018) has been the only study to look into this phenomenon in Turkish.
-Lago (2018)'s study make use of genitive-possessive structures in the
-subject position, in which the possessive-marked noun is the head of the
-noun phrase which acts as the grammatical agreement controller, and the
-genitive noun serves as a potential attractor. In a speeded
-acceptability judgment study, they found a significant effect of number
-agreement attraction. However, the interpretation of their finding may
-be a result of a non-subjecthood cues originating from their use of
-morphologically ambiguous forms of possessive. In their possessive form
-all head nouns in their stimuli are ambigiuous between possessive and
-accusative.
+Attraction errors in the production and comprehension of subject-verb
+agreement, in which a verb does not agree with the grammatical agreement
+controller, but with a potential attractor, have been the main topic of
+research in many studies for quite a long time. In fact, it is still a
+widely researched area in psycholinguistic studies. Despite the
+comprehensive research that has been carried out, studies that have been
+conducted on agreement attraction in Turkish have been very limited. In
+fact, Lago (2018) is currently the only study that explores this
+phenomenon in Turkish. Lago (2018) makes use of genitive-possessive
+structures in the subject position, in which the possessive-marked noun
+is the head of the noun phrase which acts as the grammatical agreement
+controller, and the genitive noun serves as a potential attractor. In a
+speeded acceptability judgment study, Lago (2018) found a significant
+effect of number agreement attraction. However, the interpretation of
+their findings may be a result of the fact that non-subjecthood cues
+originate from their use of morphologically ambiguous forms of the
+possessive. In the possessive forms that are used, all the head nouns in
+their stimuli are ambigiuous between possessive and accusative.
 
@@
 while genitive agreement controllers are very frequent. Thus, Lago
-(2018)'s finding could possibly be explained by occasional shallow
+(2018)'s finding could potentially be explained with occasional shallow
 processing. When all syntactic relations in the sentence were processed
-fully, the possessive noun should have been identified as the
-controller. Meanwhile the genitive noun may sometimes have been
-erroneously identified as the controller during shallow processing,
-because genitives are more likely to act as agreement controllers than
-accusatives. A second alternative explanation of Lago (2018)'s finding
+fully, the possessive noun may have been identified as the controller.
+Meanwhile, the genitive noun may sometimes have been erroneously
+identified as the controller during shallow processing because genitives
+are more likely to act as agreement controllers than accusatives
+(SOURCE). A second alternative explanation for Lago (2018)'s findings
 may be the fact that participants may engage in even more shallow
 processing than outlined above. Participants may have erroneously
-responded \emph{Yes} on some trials due to (i) the presence of a plural
-morpheme on a noun (attractor or controller) and (ii) the presence of a
-plural agreement morpheme on the verb. We speculate that on such trials,
-participants would have simply tried to check for the presence of such
-morphemes, while largely disregarding the remainder of the sentence.
+responded \emph{Yes} on some trials for two main reasons: (i) the
+presence of a plural morpheme on a noun (attractor or controller), and
+(ii) the presence of a plural agreement morpheme on the verb. We
+speculate that in such trials, participants would have simply tried to
+check for the presence of such morphemes, while largely disregarding the
+remainder of the sentence.
 
-We first replicated Lago (2018)'s experiment with unambiuous head nouns.
-To this end, we have revised the items that were used previously, to
-avoid morphological ambiguity between possessive and accusative forms.
-The effect found by Lago (2018) replicates with unambiguous nouns as
-discused in \S 2.
+We first replicated Lago (2018)'s experiment with unambiguous head
+nouns. To this end, we revised the items that were used previously in
+order to avoid morphological ambiguity between possessive and accusative
+forms. The effect found in Lago (2018) was also observed when
+unambiguous nouns were used, as will be discussed in \S 2.
 
-\S 3 discussses the alternative account that posits even more shallow
-processing as mentioned above and offers a pre-registered experiment
-using RC attractors with possible outcomes and their indications. Since
-both nominal and verbal plural morphemes in Turkish take on the same
-form (\emph{-ler} or \emph{-lar} depending on the phonological
-environment), we can test this possibility with an experiment, in which
-we use relative clause with or without plural agreement on the verb in
-the place of the genitive possessors. An agreement attraction effect
-similar in magnitude to Lago (2018)'s would mean that participants use
-aforementioned strategies.
+\S 3 discusses the alternative account that posits even more shallow
+processing as mentioned above and presents a pre-registered experiment
+using RC attractors with potential outcomes and their indications. Since
+both nominal and verbal plural morphemes in Turkish are expressed with
+the same form (\emph{-ler} or \emph{-lar} depending on the phonological
+environment), we can test this possibility with an experiment in which a
+relative clause with or without plural agreement on the verb in place of
+the genitive possessors is used. An agreement attraction effect similar
+in magnitude to that observed in Lago (2018) would indicate that
+participants use the aforementioned strategies.
 
-\S 4 presents a discussion revolving around possible Lastly, \S 5 offers
-a brief conclusion and presents topics for future researches.
+\S 4 offers a discussion of the issue of number attraction and where
+this experiments leaves us. Lastly, \S 5 presents a brief conclusion and
+topics for future research.
 
-\hypertarget{replicaton-of-lago}{%
-\section{REPLICATON OF Lago (2018)}\label{replicaton-of-lago}}
+\hypertarget{replicaton-of-lago-et-al.-2018}{%
+\section{REPLICATON OF LAGO ET AL.
+(2018)}\label{replicaton-of-lago-et-al.-2018}}
 
-In their study, Lago (2018) investigated the comprehension of
+In their study, Lago (2018) investigate the comprehension of
 subject-verb agreement in Turkish-German bilinguals and Turkish
-monolinguals. They used speeded acceptability judments for the effects
-of number attraction in Turkish. Their sentences makes us of
+monolinguals. They use speeded acceptability judgments for the effects
+of number attraction in Turkish. Their sentences make us of
 genitive-possessive constructions in the subject position, where the
-genitive is the attractor and the possessive is the head noun. They have
-manipulated the grammaticality of the sentence by changing the plural
-morphology of the verb, and they also manipulated the plurality of the
-attractor noun. In grammatical conditions, subject and the verb both
-bears the singular morphology with no overt morpheme. Moreover, in the
-ungrammatical conditions the verb bears the overt \emph{-lAr} morpheme
+genitive is the attractor and the possessive is the head noun. They
+manipulate the grammaticality of the sentence by changing the plural
+morphology of the verb, and they also manipulate the plurality of the
+attractor noun. In grammatical conditions, the subject and the verb both
+bear singular morphology with no overt morpheme. Moreover, in the
+ungrammatical conditions, the verb bears the overt \emph{-lAr} morpheme
 whereas the subject is still singular as exemplified below.
@@
 
-They have found a significant effect of number attraction in Turkish
-ranging between 11\%--15\% across monolinguals. As seen from the results
-of statistical analysis in Table (\ref{lagomodel}), acceptability
-judgments showed an immense effect of grammaticality, and there is also
-interaction between grammaticality and attractor number which indicates
-an number attraction effect.
+They found a significant effect of number attraction in Turkish ranging
+between 11\%--15\% across monolinguals. As seen in the results of the
+statistical analysis in \textsc{Table} (\ref{lagomodel}), the
+acceptability judgments showed an immense effect of grammaticality, and
+there is also interaction between grammaticality and attractor number,
+which indicates the presence of a number attraction effect.
 
-\begin{table}[]
+\begin{table}[!hbt]
 \centering
@@
 
-According to Lago (2018)'s stipulation, Turkish genitive case does not
-provide a strong cue against subjecthood since it is extremely common to
-see genitive marked subjects in Turkish embedded clauses, as in example
-(\ref{gensubj}).
+Lago (2018) stipulate that the Turkish genitive case does not provide a
+strong cue against subjecthood since Turkish frequently makes use of
+genitive marked subjects in embedded clauses, as in example
+(\ref{gensubj}). This is in contrast with English, in which the genitive
+case is compatible with subjecthood. Thus, Lago (2018) argue that this
+robust agreement attraction effect has been linked to the case
+information carried by accusative and genitive.
 
@@
 
-\hypertarget{motivation}{%
-\subsection{Motivation}\label{motivation}}
+However, our initial hypothesis postulates that participants engage in
+shallow processing, which results in a situation in which not only the
+genitive case but also the possessive case plays a significant role in
+delivering the case information. None of the experimental items in Lago
+(2018) have a head noun which ends with a vowel; thus, all of the
+possessive markers are morphologically and phonologically ambiguous
+between the accusative case and the possessive. Unlike genitive case, it
+is extremely rare for the accusative case to appear on the head noun of
+the subject, which only occurs in raising predicates as in example
+(\ref{dsm}).
 
-\hypertarget{modifications}{%
-\subsection{Modifications}\label{modifications}}
+\begin{exe}
+\ex \label{dsm}
+\gll Ben sen-i git-ti-n san-d{\i}-m\\
+I you-\textsc{acc} go-\textsc{pst}-\textsc{2Sg} suppose-\textsc{pst}-\textsc{1Sg}\\
+\glt I thought you were gone.
+\end{exe}
 
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
+In order to test this hypothesis, we have replicated the experiment of
+Lago (2018) with modified items, in which the possessive is not
+ambiguous with the accusative case. We tried to be as faithful as
+possible to the original sentences while also trying to make the
+sentences as plausable as possible. We keep the semantic relation
+between the head noun and the controller the same with what has been
+described in Lago (2018)'s study, which is either a relation regarding
+profession or a service that is given by the head noun for the
+possessor. A set of sentences are exemplified below.
 
-\hypertarget{filler-items}{%
-\subsection{Filler Items}\label{filler-items}}
+\begin{exe}
+\ex
+\begin{xlist}
+\ex \underline{Grammatical, SG attractor} \label{exp1}
+\gll Komedyen-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}.\\
+comedian-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}-$\varnothing$\\
+\glt Because of the northeaster, comedian's assistant felt chilly.
+
+\ex \underline{Grammatical, PL attractor} \label{exp2}
+\gll Komedyen-ler-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}.\\
+comedian-\textsc{pl}-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}-$\varnothing$\\
+\glt Because of the northeaster, comedians' assistant felt chilly.
+
+\ex \underline{Ungrammatical, PL attractor} \label{exp3}
+\gll Komedyen-ler-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}-ler.\\
+comedian-\textsc{pl}-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}--\textsc{pl}\\
+\glt Because of the northeaster, comedians' assistant felt chilly.
+
+\ex \underline{Ungrammatical, SG attractor} \label{exp4}
+\gll Komedyen-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}-ler.\\
+comedian-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}-\textsc{pl}\\
+\glt Because of the northeaster, comedian's assistant felt chilly.
+
+\end{xlist}
+\end{exe}
+
+As seen in the examples, unlike Lago (2018)'s experimental items, all of
+our items bear the \emph{-sI} possessive marker instead of the ambiguous
+\emph{-I} marker. As for the filler items, we could not use or modify
+the original experiment items since the fillers of the original study
+were not online. We have used two types filler sentences: grammatical
+sentences in which the verb bears plural agreement (\ref{fillera}), and
+ungrammatical sentences in which the verb does not bear plural agreement
+(\ref{fillerb}). We wanted to nullify a possible strategy by the
+participants where they associate the sentence-final morpheme directly
+with the acceptability of the sentence. And we also wanted to eliminate
+the possibility of participants disregarding other elements in the
+sentences while answering the questions we ask right after the sentence.
+
+\begin{exe}
+\ex
+\begin{xlist}
+\ex \label{fillera}
+\gll Adam-{\i}n anne-si fena-la\c{s}-{\i}nca inek kurban et-ti-ler.\\
+man-\textsc{gen} mother-\textsc{poss} bad-\textsc{vrb}-\textsc{cvb} cow sacrifice do-\textsc{pst}-\textsc{pl}\\
+\glt When his mother got ill, (they) sacrificed a cow.
+\ex \label{fillerb}
+\gll *Pizzac{\i}-n{\i}n kurye-si t\"{o}kezle-yince sos-lar yer-e sa\c{c}-t{\i}.\\
+pizzaria-\textsc{gen} courier-\textsc{poss} trip-\textsc{cvb} sauce-\textsc{pl} floor-\textsc{dat} scatter-\textsc{pst}\\
+\glt Intended: When the pizza boy tripped, sauces scattered around. 
+\end{xlist}
+\end{exe}
+
+All of our data, experimental materials, our experiment design, and our
+fillers can be found on the website of the Center for Open Science
+Framework (\url{https://osf.io/}).
+
+\hypertarget{participants-and-procedure}{%
+\subsection{Participants and
+Procedure}\label{participants-and-procedure}}
+
+One hundred and seven Turkish speakers with a mean age of X were
+recruited from Bogazici University in İstanbul. We did not collect
+participants' knowledge of other languages; however, we verified that
+Turkish is their native language and that they predominantly use it in
+their daily lives. In the experiments, participants were asked to judge
+the acceptability of experimental and filler sentences in Turkish. All
+of the sentences were presented one word at a time in the center of the
+screen for 500 ms per word unlike Lago (2018) and Wagers et al. (2009),
+in which the duration was 300 ms per word. The experiment was run on a
+web-based platform titled the Ibex Farm, and all of the documentation
+can be found on our osf and github page.
+
+Before the experiment, participants were instructed to give accurate and
+quick answers based on their own intuitions, and they were also notified
+about the time limit for answering. At the start of the experiment, they
+were given 4 practice items with feedback.
+
+What to write about analyze?
 
@@
 
+In \textsc{Figure} (1), the y-axis shows the percentage of
+``acceptable'' answers, and the x-axis indicates whether or not the
+sentences in that group are grammatical. Moreover, the linet ypes
+indicate an attractor noun with overt plural morphology. As seen in the
+figure, 22\% of the sentences with plural attractors and a singular verb
+were accepted by the participants, in line with the findings of Lago
+(2018). We also see a number attraction rate of 10\% which was also
+observed in Lago (2018) with close results.
+
+In \textsc{Table} (\ref{tab:replication}),
+\ldots{}\ldots{}\ldots{}\ldots{}
+
+And yes, I plan to beautify the figures.
+
+\begin{figure}[H]
+  \begin{floatrow}
+    \ffigbox{%
+
+\begin{flushright}\includegraphics{output/figures/unnamed-chunk-1-1} \end{flushright}
+    }{\caption{A figure}}
+
+    \btabbox{%
+
+    }{\caption{A table}}
+  \end{floatrow}
+\end{figure}
+
 \hypertarget{experiment-2-rc-attractor}{%
@@
 
-\hypertarget{motivation-1}{%
-\subsection{Motivation}\label{motivation-1}}
+Even though our first hypothesis regarding shallow processing did not
+hold, we still need to entertain the second possibility we have
+discussed in this paper. Participants may indeed engage in an even
+shallower process of sentence comprehension, in which they merely match
+the use of \emph{-lAr}. Moreover, we still need to discuss how much it
+is an effect of case information rather than only a number attraction.
+We have seen that the anti-subjecthood cues of the accusative are not
+significant since in both cases where the possessive is ambiguous with
+the accusative and the possessive is clearly marked, we have observed
+extremely close results in the speeded acceptability judgments.
 
-\hypertarget{items-and-fillers}{%
-\subsection{Items and Fillers}\label{items-and-fillers}}
+In order to check both the sole effect of number agreement and the
+possibility of a task effect, we propose an experiment design in which a
+head noun is a bare NP, is not marked with any other morpheme and
+preceded by a relative clause construction. This relative clause
+consists of only a verbal component, which bears an overt plural marker.
+Since Turkish verbal and nominal plural morphemes are identical, we plan
+to check the participants' strategy with regards to whether or not it is
+a cue that helps in the reconstruction of the ungrammatical sentence or
+whether it is merely a task effect in which participants disregard the
+rest of the sentence and focus the existence of the morpheme
+\emph{-lAr}.
+
+\hypertarget{materials}{%
+\subsection{Materials}\label{materials}}
+
+Like genitive-possessive structures, attractors do not intervene between
+the grammatical agreement controller and the verb in relative clause
+constructions. Turkish relative clauses always precede the head noun,
+except for in special cases in which they are marked with unique
+prosody. Item (\ref{rcexample}) is an example of a RC structure, and
+item (\ref{rcexample2}) shows the possibility of using only the verbal
+component of the relative clause since it is grammatical to drop
+arguments in Turkish. ( add a footnote here giving the details of such
+events, and restrictions. )
+
+\begin{exe}
+\ex
+\begin{xlist}
+\ex \label{rcexample}
+\gll On-lar-{\i}n ev-e gel-me-den g\"{o}r-d\"{u}k-ler-i \c{c}ocuk so\u{g}uk-ta \"{u}\c{s}\"{u}-m\"{u}\c{s}-t\"{u}.\\
+they-\textsc{pl}-\textsc{gen} home-\textsc{dat} come-\textsc{neg}-\textsc{abl} see-\textsc{nlmz}-\textsc{pl}-\textsc{poss} kid cold--\textsc{loc} feel.chilly-\textsc{perf}-\textsc{pst}\\
+\glt The kid that they saw right before coming to home was feeling chilly. 
+\ex \label{rcexample2}
+\gll G\"{o}r-d\"{u}k-ler-i \c{c}ocuk so\u{g}uk-ta \"{u}\c{s}\"{u}-m\"{u}\c{s}-t\"{u}.\\
+see-\textsc{nlmz}-\textsc{pl}-\textsc{poss} kid cold--\textsc{loc} feel.chilly-\textsc{perf}-\textsc{pst}\\
+\glt The kid that they saw home was feeling chilly.
+\end{xlist}
+\end{exe}
+
+As for the experimental sentences, we plan to use sentences that are
+similar to the ones used in Lago (2018). Instead of a genitive
+controller, we utilize an RC, which we manipulate for its values for
+bearing the plural morpheme. The head noun of the subject is always
+singular, and it is followed by a 2/3 word adverbial. Moreover, the
+matrix verb of the sentences is also manipulated in terms of plurality,
+deeming the sentence grammatical or ungrammatical. Lastly, the relative
+clause has to be an object relative clause, since Turkish subject
+relative clauses never bear a plural morpheme on the embedded verb. As
+in the Lago (2018)'s study and our replication, we will have a four
+condition, where we manipulate the plurality of the attractor
+(\emph{plural/singular}) and the grammaticality of the sentece by using
+overt plural morphology (\emph{grammatical/ungrammatical}), which are
+demonstrated with item (\ref{reg1}), (\ref{reg2}), (\ref{reg3}), and
+(\ref{reg4})
+
+\begin{exe}
+\ex
+\begin{xlist}
+\ex \underline{Grammatical, SG attractor} \label{reg1}
+\gll D\"{o}v-d\"{u}\u{g}-\"{u} \c{c}ocuk mutfak-ta bayg{\i}n hal-de yat-{\i}yor-du.\\
+beat-\textsc{nmlz}-\textsc{poss} kid kitchen-\textsc{loc} unconscious state-\textsc{loc} lie-\textsc{prog}-\textsc{pst}\\ 
+\glt The kid that he/she beats was laying in the kitchen unconscious.
+\ex \underline{Grammatical, PL attractor} \label{reg2}
+\gll D\"{o}v-d\"{u}k-ler-i \c{c}ocuk mutfak-ta bayg{\i}n hal-de yat-{\i}yor-du.\\
+beat-\textsc{nmlz}-\textsc{pl}-\textsc{poss} kid kitchen-\textsc{loc} unconscious state-\textsc{loc} lie-\textsc{prog}-\textsc{pst}\\
+\glt The kid that they beat was laying in the kitchen unconscious.
+\ex \underline{Ungrammatical, PL attractor} \label{reg3}
+\gll D\"{o}v-d\"{u}k-ler-i \c{c}ocuk mutfak-ta bayg{\i}n hal-de yat-{\i}yor-lar-d{\i}.\\
+beat-\textsc{nmlz}-\textsc{pl}-\textsc{poss} kid kitchen-\textsc{loc} unconscious state-\textsc{loc} lie-\textsc{prog}-\textsc{pl}-\textsc{pst}\\
+\glt Intended: The kid that they beat were laying in the kitchen unconscious.
+\ex \underline{Ungrammatical, SG attractor} \label{reg4}
+\gll D\"{o}v-d\"{u}\u{g}-\"{u} \c{c}ocuk mutfak-ta bayg{\i}n hal-de yat-{\i}yor-lar-d{\i}.\\
+beat-\textsc{nmlz}-\textsc{poss} kid kitchen-\textsc{loc} unconscious state-\textsc{loc} lie-\textsc{prog}-\textsc{pl}-\textsc{pst}\\
+\glt Intended: The kid that he/she beats were laying in the kitchen unconscious.
+\end{xlist}
+\end{exe}
+
+As for the fillers, we need two different set of fillers in order to
+counterbalance the ever-present grammaticality of singular and plural
+verbs. For grammatical fillers with a plural verb (example
+(\ref{fillerreg1})) we propose a structure in which the head noun is
+followed by a converb. With this modification, the controller of the
+experimental sentences becomes a controller for a subclause, and the
+main verb is saturated with another subject introduced right after the
+subclause.
+
+For ungrammatical fillers with a singular verb (example
+(\ref{fillerreg2})), we have used strictly transitive verbs without an
+overt object. By utilizing the same structure with the other type of
+fillers, we ensure that participants will not come up with a strategy in
+which they always check the second word for dependency resolution. The
+controller of the fillers and the controller of the experimental items
+differ in the linear order they are shown in the experiment.
+
+Question: Can we do subject relative clause here? Like durdurulan
+ogrenci.
+
+\begin{exe}
+\ex
+\begin{xlist}
+\ex \label{fillerreg1}
+\gll Dur-dur-duk-lar-{\i} \"{o}\u{g}renci \c{s}a\c{s}{\i}r-{\i}nca arkada\c{s}-lar-{\i} birden g\"{u}l-d\"{u}-ler.\\
+stop-\textsc{caus}-\textsc{nmlz}-\textsc{pl}-\textsc{poss} student surprise-\textsc{cvb} friend-\textsc{pl}-\textsc{poss} suddenly laugh--\textsc{pst}-\textsc{pl}\\
+\glt When the student which was stopped surprised, his friends burst out laughing.
+\ex \label{fillerreg2}
+\gll *Tut-tuk-lar-{\i} a\c{s}\c{c}{\i} gel-me-yince dan{\i}\c{s}man-lar hala ver-di.\\
+hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss} cook come--\textsc{neg}-\textsc{cvb} advisor-\textsc{pl} still give-\textsc{pst}\\
+\glt Inteded: When the cook that they hired did not come, advisors did not still give. 
+\end{xlist}
+\end{exe}
+
+\hypertarget{participants-and-procedure-1}{%
+\subsection{Participants and
+Procedure}\label{participants-and-procedure-1}}
+
+We plan to have participants from the undergrad students of Bogazici
+University, which will be given an extra credit incentive. They will
+again carry out the experiment on an online experiment platform Ibex
+Farm. The experiment process will be exactly the same with the
+replication of Lago (2018), including descriptions before the
+experiment, the layout of the experiment, the time spared for
+visualization of every word, exclusion criteria, and analysis.
 
@@
 
-\hypertarget{possible-outcomes-and-discussion}{%
-\subsection{Possible Outcomes and
-Discussion}\label{possible-outcomes-and-discussion}}
+(This part is extremely tentative)
+
+Our objective is to explore the number attraction phenomenon without the
+effects of case information and without the limits of nominal paradigm.
+By doing so, we expect participants to engage with the sentences which
+are ungrammatical in an extremely shallow fashion. We argue that instead
+of reconstructing the sentence utilizing every detail from the attractor
+and the controller, participants disregard the information from other
+sources in the sentence and look for a matching morpheme,
+i.e.~\emph{-lAr}.
+
+In the case that there will be a similar attraction effects with the
+replication of Lago (2018) and Lago (2018) study, we think that\ldots{}
+what do we think? I need to talk about the paper and idea more
+thoroughly, I guess. Because I feel like I am repeating myself.
 
@@
 
-Intro and repeat.
+In this paper, we have entertained the idea of task effect in the
+so-called Turkish number attraction phenomenon. We argue that the
+findings of the Lago (2018) study is not clear and there are too many
+variables to account for in the experiment, one of them being the
+ambiguous morphology that the head noun bears. In the first experiment,
+we have replicated the attraction task of Lago (2018). We have found the
+similar effects of agreement with a bigger pool of participants. Then,
+for entertaining the other possibility in which we argue that
+participants do not fully reconstruct the sentence; however, they make
+us of the direct cue of overt morpheme \emph{-lAr}, we offer an
+experiment where we use object relative clauses as an attractor.
 
@@
 (Allaire et al. 2018, Xie et al. 2018) packages. All graphs have been
-done with \texttt{ggplot} (Wickham 2016). Thank the Mine and Kadir for
-their student from courses.
+done with \texttt{ggplot} (Wickham 2016). We also would like to thank
+Mine Nakipo\u{g}lu and Kadir Gökgöz for giving us the oppurtunity to
+conduct experiments and having participants from their classes.
 
@@
 
-\newpage
-
-\begin{longtable}[]{@{}rrrrl@{}}
-\caption{A glimpse of the famous \emph{Iris} dataset.}\tabularnewline
-\toprule
-Sepal.Length & Sepal.Width & Petal.Length & Petal.Width &
-Species\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-Sepal.Length & Sepal.Width & Petal.Length & Petal.Width &
-Species\tabularnewline
-\midrule
-\endhead
-5.1 & 3.5 & 1.4 & 0.2 & setosa\tabularnewline
-4.9 & 3.0 & 1.4 & 0.2 & setosa\tabularnewline
-4.7 & 3.2 & 1.3 & 0.2 & setosa\tabularnewline
-4.6 & 3.1 & 1.5 & 0.2 & setosa\tabularnewline
-5.0 & 3.6 & 1.4 & 0.2 & setosa\tabularnewline
-5.4 & 3.9 & 1.7 & 0.4 & setosa\tabularnewline
-\bottomrule
-\end{longtable}
-
-\newpage
-
-\begin{longtable}[]{@{}lrrrrrrrrrrr@{}}
-\caption{Now a subset of mtcars dataset.}\tabularnewline
-\toprule
-& mpg & cyl & disp & hp & drat & wt & qsec & vs & am & gear &
-carb\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-& mpg & cyl & disp & hp & drat & wt & qsec & vs & am & gear &
-carb\tabularnewline
-\midrule
-\endhead
-Merc 280 & 19.2 & 6 & 167.6 & 123 & 3.92 & 3.440 & 18.30 & 1 & 0 & 4 &
-4\tabularnewline
-Merc 280C & 17.8 & 6 & 167.6 & 123 & 3.92 & 3.440 & 18.90 & 1 & 0 & 4 &
-4\tabularnewline
-Merc 450SE & 16.4 & 8 & 275.8 & 180 & 3.07 & 4.070 & 17.40 & 0 & 0 & 3 &
-3\tabularnewline
-Merc 450SL & 17.3 & 8 & 275.8 & 180 & 3.07 & 3.730 & 17.60 & 0 & 0 & 3 &
-3\tabularnewline
-Merc 450SLC & 15.2 & 8 & 275.8 & 180 & 3.07 & 3.780 & 18.00 & 0 & 0 & 3
-& 3\tabularnewline
-Cadillac Fleetwood & 10.4 & 8 & 472.0 & 205 & 2.93 & 5.250 & 17.98 & 0 &
-0 & 3 & 4\tabularnewline
-Lincoln Continental & 10.4 & 8 & 460.0 & 215 & 3.00 & 5.424 & 17.82 & 0
-& 0 & 3 & 4\tabularnewline
-\bottomrule
-\end{longtable}
-
-\clearpage
-
 \listoffigures
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{output/figures/Fig1-1.pdf}
-\caption{Just my first figure with a very fantastic caption.}
-\end{figure}
-
-\newpage
-
-\blandscape
-
-\begin{figure}
-\centering
-\includegraphics{output/figures/Fig2-1.pdf}
-\caption{Second figure in landscape format.}
-\end{figure}
-
-\elandscape
 

### 2019-01-29 Paper/AgreementAttraction.Rmd

@@
 - affilnum: 1
-  affil: Bogazici University, South Campus, John Freely Building, Department of Linguistics, 34342, Istanbul, Turkey
+  affil: Bogazici University, Department of Linguistics, Istanbul, Turkey
 
@@
 geometry: margin=1in
-linenumbers: yes
+linenumbers: no
 spacing: singlespacing

### 2019-01-29 Paper/AgreementAttraction.tex

@@
 \usepackage{lineno} % add 
-  \linenumbers % turns line numbering on 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \\*
-\textsuperscript{1}Bogazici University, South Campus, John Freely Building, Department of
-Linguistics, 34342, Istanbul, Turkey\\*
+\textsuperscript{1}Bogazici University, Department of Linguistics, Istanbul, Turkey\\*
 }
@@
 
-\hypertarget{introduction}{%
-\section{INTRODUCTION}\label{introduction}}
+\section{INTRODUCTION}\label{introduction}
 
@@
 
-\hypertarget{replicaton-of-lago-et-al.-2018}{%
 \section{REPLICATON OF LAGO ET AL.
-(2018)}\label{replicaton-of-lago-et-al.-2018}}
+(2018)}\label{replicaton-of-lago-et-al.-2018}
 
@@
 
-\hypertarget{participants-and-procedure}{%
 \subsection{Participants and
-Procedure}\label{participants-and-procedure}}
+Procedure}\label{participants-and-procedure}
 
@@
 
-\hypertarget{results-and-discussion}{%
-\subsection{Results and Discussion}\label{results-and-discussion}}
+\subsection{Results and Discussion}\label{results-and-discussion}
 
@@
 
-\hypertarget{experiment-2-rc-attractor}{%
-\section{EXPERIMENT 2: RC ATTRACTOR}\label{experiment-2-rc-attractor}}
+\section{EXPERIMENT 2: RC ATTRACTOR}\label{experiment-2-rc-attractor}
 
@@
 
-\hypertarget{materials}{%
-\subsection{Materials}\label{materials}}
+\subsection{Materials}\label{materials}
 
@@
 
-\hypertarget{participants-and-procedure-1}{%
 \subsection{Participants and
-Procedure}\label{participants-and-procedure-1}}
+Procedure}\label{participants-and-procedure-1}
 
@@
 
-\hypertarget{expectations}{%
-\subsection{Expectations}\label{expectations}}
+\subsection{Expectations}\label{expectations}
 
@@
 and the controller, participants disregard the information from other
-sources in the sentence and look for a matching morpheme,
-i.e.~\emph{-lAr}.
+sources in the sentence and look for a matching morpheme, i.e.
+\emph{-lAr}.
 
@@
 
-\hypertarget{discussion}{%
-\section{DISCUSSION}\label{discussion}}
+\section{DISCUSSION}\label{discussion}
 
@@
 
-\hypertarget{conclusions}{%
-\section{CONCLUSIONS}\label{conclusions}}
+\section{CONCLUSIONS}\label{conclusions}
 
@@
 
-\hypertarget{acknowledgements}{%
-\section{ACKNOWLEDGEMENTS}\label{acknowledgements}}
+\section{ACKNOWLEDGEMENTS}\label{acknowledgements}
 
@@
 
-\hypertarget{references}{%
-\section{REFERENCES}\label{references}}
+\section{REFERENCES}\label{references}
 
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-Allaire_2018}{}%
+\hypertarget{ref-Allaire_2018}{}
 Allaire, J., Y. Xie, J. McPherson, J. Luraschi, K. Ushey, A. Atkins, H.
@@
 
-\leavevmode\hypertarget{ref-Lago}{}%
+\hypertarget{ref-Lago}{}
 Lago, S. 2018. Straight from the horse's mouth: agreement attraction
@@
 
-\leavevmode\hypertarget{ref-R_Core_Team_2018}{}%
+\hypertarget{ref-R_Core_Team_2018}{}
 R Core Team. 2018. R: A language and environment for statistical
@@
 
-\leavevmode\hypertarget{ref-Wagers2009}{}%
+\hypertarget{ref-Wagers2009}{}
 Wagers, M. W., E. F. Lau, and C. Phillips. 2009. Agreement attraction in
@@
 
-\leavevmode\hypertarget{ref-Wickham_2016}{}%
+\hypertarget{ref-Wickham_2016}{}
 Wickham, H. 2016. Ggplot2: Elegant graphics for data analysis.
@@
 
-\leavevmode\hypertarget{ref-woolford}{}%
+\hypertarget{ref-woolford}{}
 Woolford, E. 2009. Differential subject marking at argument structure,
@@
 
-\leavevmode\hypertarget{ref-Xie_2014}{}%
+\hypertarget{ref-Xie_2014}{}
 Xie, Y. 2014. Knitr: A comprehensive tool for reproducible research in
@@
 
-\leavevmode\hypertarget{ref-Xie_2015}{}%
+\hypertarget{ref-Xie_2015}{}
 Xie, Y. 2015. Dynamic documents with R and knitr. 2nd editions. Chapman;
@@
 
-\leavevmode\hypertarget{ref-Xie_2018}{}%
+\hypertarget{ref-Xie_2018}{}
 Xie, Y. 2018. Knitr: A general-purpose package for dynamic report
@@
 
-\leavevmode\hypertarget{ref-Xie_2018a}{}%
+\hypertarget{ref-Xie_2018a}{}
 Xie, Y., J. Allaire, and G. Grolemund. 2018. R markdown: The definitive

### 2019-02-13 Paper/AgreementAttraction.Rmd
First model, and major restructuring of the directory structure.

@@
 author: 
+  - name          : "Utku Türk"
+    affiliation   : "1"
+    corresponding : yes    # Define only one corresponding author
+    address       : "Postal address"
+    email         : "utku.turk@boun.edu.tr"
+  - name          :  "Pavel Logačev"
+    affiliation   : "1"
+affiliation       :
+  - id            : "1"
+    institution   : "Boğaziçi University University, Istanbul, Turkey"
 
-- name: Utku Turk
-  affilnum: 1
-  email: utku.turk@boun.edu.tr
+authornote: |
+  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+  Enter author note here.
+shorttitle: Why Utku is the best
+abstract: |
+  This paper deals with agreement attraction because it's more important than literally anything else.
+  Recently, Lago et al.
+(2018) demonstrated agreement attraction effects in comprension in Turkish, which is super-interesting because this finding allows us to make a lot of money.
+However, there is an alternative explanation for their findings: dark sorcery.
+In this paper we tested the predictions of these alternative accounts.
+In Experiment 1, we found that a particular kind of dark sorcery was not involved.
+In Experiment 2, we shall find ...
 
-- name: Pavel Logacev 
-  affilnum: 1
-
-affiliation:
-
-- affilnum: 1
-  affil: Bogazici University, Department of Linguistics, Istanbul, Turkey
-
-output:
-
-  pdf_document:
-    fig_caption: yes
-    fig_width: 7
-    fig_height: 7
-    keep_tex: yes
-    number_sections: yes
-    template: manuscript.latex
+keywords          : "keywords"
+wordcount         : "X"
+bibliography      : ["myreferences.bib", "references.bib"]
+floatsintext      : no
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+linenumbers       : no
+mask              : no
+draft             : no
+documentclass     : "apa6"
+classoption       : "doc"
+output            : 
+  papaja::apa6_pdf:
     includes:
         in_header: header.tex
-
-  html_document: null
-
-  word_document: null
-
-documentclass: article
-classoption: a4paper
-capsize: normalsize
-fontsize: 11pt
-geometry: margin=1in
-linenumbers: no
-spacing: singlespacing
-footerdate: yes
-bibliography: 
-  - references.bib
-  - knitcitations.bib
-csl: ecology.csl
-
+editor_options: 
+  chunk_output_type: console
 ---
 
-```{r setup, include=FALSE, cache=FALSE, message = FALSE}
+<!--  - knitcitations.bib
 
-library("knitr")
+-->
 
-#opts_knit$set(root.dir=normalizePath('../'))
+```{r setup, eval =T, include = FALSE, message=FALSE, warning=FALSE}
+library("papaja")
+library(knitcitations)
+library(tidyverse)
+library(magrittr)
+library(ggplot2)
+theme_set(theme_bw())
 
-### Chunk options: see http://yihui.name/knitr/options/ ###
+library(car, warn.conflicts = FALSE)
+library(MASS)
+library(brms)
+library(xtable)
+library(ggpubr)
 
-## Text results
-opts_chunk$set(echo = TRUE, warning = TRUE, message = TRUE, include = TRUE)
-
-## Code decoration
-opts_chunk$set(tidy = TRUE, comment = NA, highlight = TRUE)
-
-## Cache
-opts_chunk$set(cache = 2, cache.path = "output/cache/")
-
-## Plots
-opts_chunk$set(fig.path = "output/figures/")
-
-```
-
-```{r knitcitations, echo=FALSE, cache = FALSE}
-library(knitcitations)
-cleanbib()   
-cite_options(citation_format = "pandoc")
-```
-
-```{r init, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
 library(languageR)
@@
 
-data <- read.csv('results', 
-                 header = F, 
-                 comment.char = "#", 
-                 encoding = "UTF-8" , 
-                 col.names = paste0("V",seq_len(11)), 
-                 fill = TRUE)
-
-colnames(data) = c("Time", "MD5", "ControllerType", "SentenceNoInStimFile", "Element", "Type", "Item", "Sentence", "Question","Answer", "RT")
-
-FormEntries <- subset(data, ControllerType != "DashedAcceptabilityJudgment" ) %>% drop.levels(); nrow(data)
-data %<>% subset(ControllerType == "DashedAcceptabilityJudgment")
-age <- dplyr::select(FormEntries, MD5,Sentence,Question) %>% 
-  dplyr::filter(Sentence == "age") %>%
-  dplyr::select(MD5, Age = Question)
-natturk <- dplyr::select(FormEntries, MD5,Sentence,Question) %>% 
-  dplyr::filter(Sentence == "natturk") %>%
-  dplyr::select(MD5, Natturk = Question) %>%
-  mutate(Natturk = Natturk == "male")
-dex <- dplyr::select(FormEntries, MD5,Sentence,Question) %>% 
-  dplyr::filter(Sentence == "dex") %>%
-  dplyr::select(MD5, Dex = Question) %>%
-  mutate(Dex = ifelse(Dex == "male", "right-handed", "left-handed"))
-FormPart <- dplyr::left_join(age, natturk, by = "MD5") %>% 
-  dplyr::left_join(., dex , by = "MD5" ) %>% 
-  unique()
-lenForm <- length(levels(factor(FormPart$MD5))); lenForm
-md5form <- levels(factor(FormPart$MD5))
-md5form_subject <- data.frame("MD5" = md5form, "Subject" = sprintf("S[%s]",seq((lenForm))))
-FormPart <- merge(FormPart,md5form_subject, all = T)
-
-stopifnot( nrow(data) %% 2 == 0 )
-rows_stim <- data[c(T,F),]
-rows_resp <- data[c(F,T),]
-
-data <- rows_resp %>% left_join(md5form_subject) %>% dplyr::select(-MD5, -Time, -ControllerType, -Sentence, -Element) %>%
-  dplyr::rename(ResponseCorrect=Answer, Response=Question)
-data %<>% group_by(Subject) %>% mutate(trial_no = seq(Subject))
-data %<>% within({ late_response = (Response == "NULL")
-Response[late_response] = NA
-ResponseCorrect[late_response] = NA
-})
-
-responses <- c(yes="İYİ (P'ye basınız)", no="KÖTÜ (Q'ya basınız)")
-stopifnot( all(data$Response %in% responses | is.na(data$Response) ) )
-
-data$ResponseYes <- ifelse(grepl("P",data$Response) , T, 
-                           ifelse(grepl("Q",data$Response) , F, NA))
-
-data$condition <- 
-  with(data, case_when(Type == "filler" & SentenceNoInStimFile >= 200 ~ "a",
-                       Type == "filler" & SentenceNoInStimFile < 200 ~ "b",
-                       Type == "condition_a" ~ "a",
-                       Type == "condition_b" ~ "b",
-                       Type == "condition_c" ~ "c",
-                       Type == "condition_d" ~ "d",
-                       TRUE ~ as.character(NA)))
-data$experiment <- ifelse(data$Type %in% c("condition_a", "condition_b", "condition_c", "condition_d"), "AgrAttr", as.character(data$Type))
-
-data %>% group_by(experiment, condition) %>% 
-  summarise(perc_yes = mean(ResponseYes, na.rm = T),
-            perc_na = mean(is.na(ResponseYes)))
-
-conditions_info <- data.frame(experiment = c("AgrAttr", "AgrAttr", "AgrAttr", "AgrAttr", "filler", "filler"),
-                              condition = c("a","b","c","d", "a","b"),
-                              grammatical = c("ungram", "gram", "ungram", "gram", "ungram", "gram"),
-                              verb_num = c("sg","pl","sg","pl", "sg","pl"),
-                              attracted = c(T,T,F,F,F,F),
-                              stringsAsFactors = FALSE) 
-data %<>% left_join(conditions_info)
-data %<>% subset(Type != "practice") %>% drop.levels()
-
-dataAv <- data %>% 
-  group_by(experiment, condition, grammatical, verb_num, attracted) %>%
-  summarize(avRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T)) %>% 
-  as.data.frame()
-
-dataAv %>% ggplot(aes(grammatical, p_yes, group = paste(experiment,attracted), color = experiment )) + geom_point() + geom_line(aes(linetype =attracted))
-
-data$trial_group <- Hmisc::cut2(data$trial_no, g=5)
-
-dataAvSplit <- data %>% 
-  group_by(experiment, condition, grammatical, verb_num, attracted, trial_group) %>%
-  summarize(avRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T)) %>% 
-  as.data.frame()
-
-plot_split <- dataAvSplit %>% ggplot(aes(grammatical, p_yes, group = paste(experiment,attracted), color = experiment )) + geom_point() + geom_line(aes(linetype =attracted)) + facet_wrap(~trial_group)
-
-dataAvBySubj <- data %>% 
-  group_by(Subject, experiment, condition, grammatical, verb_num, attracted) %>%
-  summarize(avRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T), N = sum(!is.na(ResponseYes))  )  %>% 
-  as.data.frame()
-head(dataAvBySubj,10)
-
-dataAvBySubjWide = dataAvBySubj %>% mutate(expcond = paste(experiment,condition, sep="_")) %>% dplyr::select(-experiment, -condition, -avRT, -N, -grammatical, -verb_num, -attracted) %>% tidyr::spread(expcond, p_yes)
-dataAvBySubjWide %<>% mutate(delta_dc = AgrAttr_d - AgrAttr_c)
-bad_subjects = subset(dataAvBySubjWide, delta_dc <= 0.25 ) %>% .$Subject
-
-dataAvBySubj %>% subset(Subject %in% bad_subjects) %>% ggplot(aes(grammatical, p_yes, group = paste(experiment,attracted), color = experiment )) + geom_point() + geom_line(aes(linetype =attracted)) + facet_wrap(~Subject)
-
-dataAvClean <- data %>% subset(!Subject %in% bad_subjects)%>% 
-  group_by(experiment, condition, grammatical, verb_num, attracted) %>%
-  summarize(avRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T)) %>% 
-  as.data.frame()
-
-dataAvClean <- slice(dataAvClean, 1:4)
-
-plot_average <- dataAvClean %>% ggplot(aes(grammatical, p_yes, group = paste(experiment,attracted), color = experiment )) + geom_point() + geom_line(aes(linetype =attracted)) #+ facet_wrap(~experiment, scales = "free_y")
+source("../scripts/misc.R")
 
@@
 
+```{r analysis-preferences, eval =T, message=FALSE, warning=FALSE}
+# Seed for random number generation
+set.seed(42)
+knitr::opts_chunk$set(encoding = 'UTF-8',
+                      cache.extra = knitr::rand_seed,
+                      echo = FALSE,
+                      results = 'hide')
+options("citation_format" = "pandoc")
+
+```
+
+<!--
 \vspace{2mm}\hrule
@@
 
-\bleft
-
 ---
@@
 ...
+
+-->
 
@@
 
-# REPLICATON OF LAGO ET AL. (2018)
+# Experiment 1
 
-In their study, @Lago investigate the comprehension of subject-verb agreement in Turkish-German bilinguals and Turkish monolinguals.
+```{r loadDataExp1, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+
+fname_data <- "../workspace_exp1/exp_data.rds"
+data <- readRDS(file = fname_data)
+
+# compute by-subject percentages of 'yes' responses, and average RTs 
+avg_by_subj <- data %>%
+                group_by(subject, experiment, condition, 
+                         grammatical, verb_num, attractor_num) %>%
+                summarize(avRT = mean(RT), 
+                          p_yes = mean(ResponseYes, na.rm = T), 
+                          N = sum(!is.na(ResponseYes))  )
+
+# reformat by-subject averages to a wide format
+avg_by_subj_wide <- avg_by_subj %>% 
+                      mutate(expcond = paste(experiment, condition, sep="_")) %>% 
+                      ungroup() %>%
+                      dplyr::select(-experiment, -condition, -avRT, -N,
+                                    -grammatical, -verb_num, -attractor_num) %>%
+                      tidyr::spread(expcond, p_yes) %>% 
+                      mutate(delta_dc = AgrAttr_d - AgrAttr_c)
+
+```
+
+```{r loadDataLago, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+
+# Load Lago et al.'s monolingual data
+fname_lagoetal <- "../Data/Lago_et_al/Lago_data.csv"
+df_lagoetal <- read.csv(fname_lagoetal, encoding = "UTF-8", as.is = T)
+df_lagoetal %<>% subset(Group == "monolingual")
+df_lagoetal %<>% dplyr::select(-Accuracy, -L1:-Group, -List:-SelfRateGerman)
+
+# Note: All rows with Experiment == "offline" also seem to be for 
+#       the UNP task ('Grammatical' is NA). I wonder if these were
+#       the same subjects, or if the subject labels were simply the same
+#       for the two experiments.
+with(df_lagoetal, stopifnot( is.na(Grammatical) == (Experiment == "offline") ))
+
+df_lagoetal_unp <- df_lagoetal %>% 
+                    subset(is.na(Grammatical)) %>%
+                    dplyr::select(-Grammatical:-Label)
+df_lagoetal_attr <- df_lagoetal %>% 
+                  subset(!is.na(Grammatical)) %>%
+                  dplyr::select(-Distance:-NewCond)
+
+```
+
+In their study, @Lago investigates the comprehension of subject-verb agreement  Turkish monolinguals.
 They use speeded acceptability judgments for the effects of number attraction in Turkish.
@@
 \begin{xlist}
-\ex \underline{Grammatical, SG attractor} \label{lago1}
+
+\ex \textsc{Ungrammatical, SG attractor} \label{lago4}
+\gll \c{S}ark{\i}c{\i}-n{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}-lar.\\
+singer-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-\textsc{3Pl}\\
+\glt The singer's backup vocalist jumped on the stage non-stop.
+
+\ex \textsc{Grammatical, PL attractor} \label{lago2}
+\gll \c{S}ark{\i}c{\i}-lar-{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}\\
+singer-\textsc{pl}-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-$\varnothing$\\
+\glt The singers' backup vocalist jumped on the stage non-stop.
+
+\ex \textsc{Ungrammatical, PL attractor} \label{lago3}
+\gll \c{S}ark{\i}c{\i}-lar-{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}-lar.\\
+singer-\textsc{pl}-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-\textsc{3Pl}\\
+\glt The singers' backup vocalist jumped on the stage non-stop.
+
+\ex \textsc{Grammatical, SG attractor} \label{lago1}
 \gll \c{S}ark{\i}c{\i}-n{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}\\
@@
 
-\ex \underline{Grammatical, PL attractor} \label{lago2}
-\gll \c{S}ark{\i}c{\i}-lar-{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}\\
-singer-\textsc{pl}-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-$\varnothing$\\
-\glt The singers' backup vocalist jumped on the stage non-stop.
-
-\ex \underline{Ungrammatical, PL attractor} \label{lago3}
-\gll \c{S}ark{\i}c{\i}-lar-{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}-lar.\\
-singer-\textsc{pl}-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-\textsc{3Pl}\\
-\glt The singers' backup vocalist jumped on the stage non-stop.
-
-\ex \underline{Ungrammatical, SG attractor} \label{lago4}
-\gll \c{S}ark{\i}c{\i}-n{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}-lar.\\
-singer-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-\textsc{3Pl}\\
-\glt The singer's backup vocalist jumped on the stage non-stop.
 \end{xlist}
@@
   \begin{xlist}
-\ex \underline{Grammatical, SG attractor} \label{exp1}
-\gll Komedyen-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}.\\
-comedian-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}-$\varnothing$\\
-\glt Because of the northeaster, comedian's assistant felt chilly.
+  \ex \underline{Ungrammatical, PL attractor} \label{exp3}
+      \gll Komedyen-ler-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}-ler.\\
+  comedian-\textsc{pl}-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}--\textsc{pl}\\
+      \glt Because of the northeaster, comedians' assistant felt chilly.
 
@@
 
-\ex \underline{Ungrammatical, PL attractor} \label{exp3}
-\gll Komedyen-ler-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}-ler.\\
-comedian-\textsc{pl}-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}--\textsc{pl}\\
-\glt Because of the northeaster, comedians' assistant felt chilly.
-
   \ex \underline{Ungrammatical, SG attractor} \label{exp4}
@@
   comedian-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}-\textsc{pl}\\
+      \glt Because of the northeaster, comedian's assistant felt chilly.
+
+  \ex \underline{Grammatical, SG attractor} \label{exp1}
+      \gll Komedyen-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}.\\
+  comedian-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}-$\varnothing$\\
       \glt Because of the northeaster, comedian's assistant felt chilly.
@@
 
+```{r identifyBadSubjects, eval =T, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+
+# identify participants 
+bad_subjects <- subset(avg_by_subj_wide, delta_dc <= 0.25 ) %>% .$subject
+
+#dataAvBySubj %>% subset(subject %in% bad_subjects) %>% ggplot(aes(grammatical, p_yes, group = paste(experiment,attracted), color = experiment )) + geom_point() + geom_line(aes(linetype =attracted)) + facet_wrap(~subject)
+
+data_clean <- data %>% subset(!subject %in% bad_subjects)
+
+```
+
 In \textsc{Figure} (1), the y-axis shows the percentage of "acceptable" answers, and the x-axis indicates whether or not the sentences in that group are grammatical.
 Moreover, the linet ypes indicate an attractor noun with overt plural morphology.
-As seen in the figure, `r round(100*dataAvClean[1,7])`% of the sentences with plural attractors and a singular verb were accepted by the participants, in line with the findings of @Lago.
-We also see a number attraction rate of `r round(100*(dataAvClean[1,7]-dataAvClean[3,7]))`% which was also observed in @Lago with close results.
+As seen in the figure, `r 1`% of the sentences with plural attractors and a singular verb were accepted by the participants, in line with the findings of @Lago.
+We also see a number attraction rate of `r 2`% which was also observed in @Lago with close results.
 
@@
 
-And yes, I plan to beautify the figures.
-\begin{figure}[H]
-  \begin{floatrow}
-    \ffigbox{%
-```{r, fig.width = 4 , fig.height = 4 , fig.align = "right", echo = F}
-print(plot_average)
+```{r mergeData, eval =T, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+
+df_merge_exp1 <- data_clean %>% ungroup() %>% 
+                      dplyr::select(source=experiment, grammatical, attractor_num, # condition,
+                                    subject, item=Item,
+                                    ResponseYes, RT)
+df_merge_exp1$experiment <- "Experiment 1"
+df_merge_exp1$grammatical <- with(df_merge_exp1, ifelse(grammatical == "gram", 
+                                                        "grammatical",
+                                                        "ungrammatical"))
+df_merge_exp1$attractor_num <- with(df_merge_exp1, ifelse(attractor_num == "pl", 
+                                                          "plural", 
+                                                          "singular"))
+df_merge_exp1$item %<>% as.integer()
+df_merge_exp1$subject %<>% as.character()
+
+df_lagoetal_attr %<>% mutate(ResponseYes = (Response == "yes") )
+df_merge_lago <- df_lagoetal_attr %>% ungroup() %>% 
+                      dplyr::select(grammatical=Grammatical, attractor_num=Attractor, #condition=Condition, 
+                                    subject=Participant, item=Item,
+                                    ResponseYes, RT)
+df_merge_lago$experiment <- "Lago et al. (2018)" 
+df_merge_lago$source <- NA
+df_merge_lago$item %<>% add(1000)
+
+df_merged <- dplyr::bind_rows(df_merge_exp1, df_merge_lago)
+df_merged$subject %<>% as.factor()
+df_merged$item %<>% as.factor()
 ```
-    }{\caption{A figure}}
 
-    \btabbox{%
-```{r, fig.align = "right", echo = F}
+```{r computeAverages, eval =T, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+
+avg_clean <- df_merged %>%
+                group_by(experiment, source, grammatical, attractor_num) %>%
+                summarize(avgRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T))
+```
+
+## Responses
+
+```{r exp1AvgResponse, fig.height = 2.5, fig.width = 6, fig.cap="Estimates and 95% credible intervals for the analysis of the probability of a 'yes' response."}
+
+avg_exp <- avg_clean %>% subset(is.na(source) | source != "filler")
+avg_fillers <- avg_clean %>% subset(source == "filler")
+
+p_avg_resp <- ggplot(avg_exp, 
+                     aes(grammatical, p_yes, #linetype = attractor_num, 
+                         color = attractor_num, group = attractor_num)) + 
+                geom_point() + geom_line() + 
+                facet_wrap(~experiment)
+
+p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) + geom_point(data = avg_fillers)
+
+print(p_avg_resp)
 
 ```
-    }{\caption{A table}}
-  \end{floatrow}
-\end{figure}
+
+```{r exp1ModelResponse, eval = F}
+
+# # TODO: the following subjects have too much data: 11, 28, 36, 42, 55, 65, 73, 84, 92, 
+# #
+# x <- df_merged %>% subset(experiment == "Experiment 1") %>% group_by(subject) %>% dplyr::summarize(F = sum(is.na(attractor_num)),
+#                                                           N = length(is.na(attractor_num)) )
+# x %>% as.data.frame()
+# 
+# x$N %>% sum()
+# x$F %>% sum()
+
+#summary(as.factor(df_merged$attractor_num))
+
+df_merged %<>% within(., {
+  cGrammatical <- ifelse(grammatical == "grammatical", .5, -.5)
+  cUngrammatical <- ifelse(grammatical == "ungrammatical", .5, -.5)
+  cAttractorPlural <- ifelse(attractor_num == "plural", .5, -.5)
+  cEndsInVowel <- ifelse(experiment == "Experiment 1", .5, -.5)
+})
+df_merged_nofillers <- df_merged %>% subset(is.na(source) | source != "filler")
+
+# ## test model parameterization using a simple GLM first
+# m <- glm(ResponseYes ~ cEndsInVowel * cUngrammatical * cAttractorPlural,
+#          data = df_merged_nofillers,
+#          family = binomial("probit"))
+# summary(m)
+
+n_chains <- 4
+n_cores <- 4
+n_iter <- 5000
+
+fname_exp1_responses <- "../workspace_exp1/model_responses"
+
+library(brms)
+
+m_responses <- brm(ResponseYes ~ cEndsInVowel * cUngrammatical * cAttractorPlural + 
+                                 (cUngrammatical * cAttractorPlural + 1| subject) +
+                                 (cUngrammatical * cAttractorPlural + 1| item),
+                   data = df_merged_nofillers,
+                   family = bernoulli("probit"),
+                   file = fname_exp1_responses, 
+                   chains = n_chains, cores = n_cores, iter = n_iter)
+
+```
+
+```{r exp1ResponseModelPlot, eval = F, fig.height= 1.5, message=FALSE, warning=FALSE, fig.cap="Estimates and 95% credible intervals for the analysis of the probability of a 'yes' response."}
+
+contrast_names <- c("cUngrammatical" = "Ungrammaticality",
+                    "cAttractorMatch" = "Attactor Match",
+                    "cUngrammatical:cAttractorMatch" = "Ungrammaticality * Attractor Match")
+
+p_m_response <- create_model_coefs_plot(m_responses, map_names = contrast_names)
+p_m_response <- p_m_response + xlab("Estimate (log-odds)")
+print(p_m_response)
+
+```
+
+## Response Times
+
+```{r exp1AvgRTs, fig.height=2.5, fig.width = 6 }
+
+p_avg_rt <- ggplot(avg_clean, aes(grammatical, avgRT, linetype = attractor_num, color = experiment, group = paste(experiment, attractor_num))) + geom_point() + geom_line()
+
+print(p_avg_rt)
+
+```
+
+\clearpage
 
@@
 Then, for entertaining the other possibility in which we argue that participants do not fully reconstruct the sentence; however, they make us of the direct cue of overt morpheme *-lAr*, we offer an experiment where we use object relative clauses as an attractor.
+-
 
@@
 We used the statistical language `R` `r citep(citation())` for all our analyses.
-These were implemented in dynamic rmarkdown documents using `knitr` `r citep(citation("knitr"))` and `rmarkdown` `r citep(citation("rmarkdown"))` packages.
+These were implemented in dynamic rmarkdown documents using `knitr` `r citep(citation("knitr")[1])` and `rmarkdown` `r citep(citation("rmarkdown")[2])` packages.
 All graphs have been done with `ggplot` `r citep(citation("ggplot2"))`.
-We also would like to thank Mine Nakipo\u{g}lu and Kadir Gökgöz for giving us the oppurtunity to conduct experiments and having participants from their classes.
 
@@
 
-```{r write_citations, cache=FALSE, include=FALSE}
-write.bibtex(file="knitcitations.bib")
+```{r write_citations, eval =T, cache=FALSE, include=FALSE}
+write.bibtex(file="references.bib")
 ```
-
-<div id = "refs"></div>
-
-\eleft
-
-\clearpage
-
-\listoftables
-
-\listoffigures
-
-\clearpage
-
-```{r sessioninfo, echo = FALSE, eval = FALSE}
-# set eval = FALSE if you don't want this info (useful for reproducibility) to appear 
-sessionInfo()
-```

### 2019-02-13 Paper/AgreementAttraction.tex
First model, and major restructuring of the directory structure.

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Original default rstudio/pandoc latex file
-%% upated by @jhollist 09/15/2014
-%% inspired by @cboetting https://github.com/cboettig/template and
-%% @rmflight blog posts:
-%% http://rmflight.github.io/posts/2014/07/analyses_as_packages.html 
-%% http://rmflight.github.io/posts/2014/07/vignetteAnalysis.html).  
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\documentclass[11pt,a4paper]{article}
-\usepackage[T1]{fontenc}
+\documentclass[doc]{apa6}
 \usepackage{lmodern}
@@
 \usepackage{fixltx2e} % provides \textsubscript
-% use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
   \usepackage[utf8]{inputenc}
@@
     \usepackage{mathspec}
-    \usepackage{xltxtra,xunicode}
   \else
@@
   \fi
-  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
-  \newcommand{\euro}{€}
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
 \fi
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 % use microtype if available
-\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
-\usepackage[margin=1in]{geometry}
-\ifxetex
-  \usepackage[setpagesize=false, % page size defined by xetex
-              unicode=false, % unicode breaks when used with xetex
-              xetex]{hyperref}
-\else
-  \usepackage[unicode=true]{hyperref}
-\fi
-\hypersetup{breaklinks=true,
-            bookmarks=true,
-            pdfauthor={},
+\IfFileExists{microtype.sty}{%
+\usepackage{microtype}
+\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\usepackage{hyperref}
+\hypersetup{unicode=true,
             pdftitle={Agreement Attraction in Turkish: Effects of Nominal and Verbal Plural Morphemes},
-            colorlinks=true,
-            citecolor=blue,
-            urlcolor=blue,
-            linkcolor=magenta,
-            pdfborder={0 0 0}}
+            pdfauthor={Utku Türk~\& Pavel Logačev},
+            pdfkeywords={keywords},
+            pdfborder={0 0 0},
+            breaklinks=true}
 \urlstyle{same}  % don't use monospace font for urls
+\usepackage{graphicx,grffile}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
 \setlength{\parindent}{0pt}
 \setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
 \setlength{\emergencystretch}{3em}  % prevent overfull lines
-\setcounter{secnumdepth}{5}
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{0}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Changes borrowed from @cboettig, added by @jhollist 
-% A modified page layout 
-\textwidth 6.75in
-\oddsidemargin -0.15in
-\evensidemargin -0.15in
-\textheight 9in
-\topmargin -0.5in
-\usepackage{lineno} % add 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%Packages and layout changes by @jhollist 09/15/2014
-\usepackage{ragged2e}
-\usepackage[font=normalsize]{caption}
-  \usepackage[singlespacing]{setspace}
-\usepackage{parskip}
-\usepackage{fancyhdr}
-\pagestyle{fancy}
-\fancyhf{}
-\renewcommand{\headrulewidth}{0pt}
-  \rfoot{\today}
-\lfoot{\thepage}
-%%Changed default abstract width and added lines
-\renewenvironment{abstract}{
-  \hfill\begin{minipage}{1\textwidth}
-  \rule{\textwidth}{1pt}\vspace{5pt}
-  \normalsize
-  \begin{justify}
-  \bfseries\abstractname\vspace{5pt}
-  \end{justify}}
-  {\par\noindent\rule{\textwidth}{1pt}\end{minipage}
-}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%% Use protect on footnotes to avoid problems with footnotes in titles
+\let\rmarkdownfootnote\footnote%
+\def\footnote{\protect\rmarkdownfootnote}
 
@@
 Morphemes}
-\author{
-Utku Turk
-Pavel Logacev
+    \author{Utku Türk\textsuperscript{1}~\& Pavel Logačev\textsuperscript{1}}
+    \date{}
+
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+
+\usepackage{xcolor}
+\usepackage{hhline}
+\usepackage{mathtools}
+\usepackage{gb4e}\noautomath
+
+\authornote{Add complete departmental affiliations for each
+author here. Each new line herein must be indented, like this line.
+Enter author note here.
+
+Correspondence concerning this article should be addressed to Utku Türk,
+Postal address. E-mail:
+\href{mailto:utku.turk@boun.edu.tr}{\nolinkurl{utku.turk@boun.edu.tr}}}
+
+\abstract{
+This paper deals with agreement attraction because it's more important
+than literally anything else. Recently, Lago et al. (2018) demonstrated
+agreement attraction effects in comprension in Turkish, which is
+super-interesting because this finding allows us to make a lot of money.
+However, there is an alternative explanation for their findings: dark
+sorcery. In this paper we tested the predictions of these alternative
+accounts. In Experiment 1, we found that a particular kind of dark
+sorcery was not involved. In Experiment 2, we shall find \ldots{}
+
 }
-\date{}
-% Allowing for landscape pages
-\usepackage{lscape}
-\newcommand{\blandscape}{\begin{landscape}}
-\newcommand{\elandscape}{\end{landscape}}
-
-% Left justification of the text: see https://www.sharelatex.com/learn/Text_alignment
-% \usepackage[document]{ragged2e} % already in the latex template
-\newcommand{\bleft}{\begin{flushleft}}
-\newcommand{\eleft}{\end{flushleft}}
-
-% multicols
-\usepackage{multicol}
-\usepackage{paracol}
-
-% enumerated examples
-\usepackage{enumitem}
-
-% for linguistic examples &  interlinear glosses
-\usepackage{gb4e}
-\exewidth{(10.159)}
-\noautomath
-\let\eachwordone=\it
-
-\usepackage{qtree}
-
-% for figure and table side by side
-\usepackage{floatrow}
-\newfloatcommand{btabbox}{table}
-
-%%Fix tightlist error: https://stackoverflow.com/questions/40438037/tightlist-error-using-pandoc-with-markdown
-%%Added 2018-03-26 
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-%%%
 
 \begin{document}
-%%Edited by @jhollist 09/15/2014
-%%Adds title from YAML
-\begin{singlespace}
-\begin{center}
-\huge Agreement Attraction in Turkish: Effects of Nominal and Verbal Plural
-Morphemes
-\end{center}
-%%Adds Author, correspond email asterisk, and affilnum from YAML
-\begin{center}
-\large
-Utku Turk \textsuperscript{*} \textsuperscript{1} 
-Pavel Logacev \textsuperscript{1} 
-\end{center}
-%%Adds affiliations from YAML
-\begin{justify}
-\footnotesize \emph{ 
-\\*
-\textsuperscript{1}Bogazici University, Department of Linguistics, Istanbul, Turkey\\*
-}
-%%Adds corresponding author email(s) from YAML
-\newcounter{num}
-\setcounter{num}{1}
-\\[0.1cm]
-\footnotesize \emph{ 
-\ifnum\value{num}=1%
-\textsuperscript{*} corresponding author:
-\fi
-\href{mailto:utku.turk@boun.edu.tr}{\nolinkurl{utku.turk@boun.edu.tr}}
-\stepcounter{num}
-}
-\end{justify}
-%%Adds date from YAML
-\normalsize
-
-\end{singlespace}
-
-\vspace{2mm}\hrule
-
-In this paper, our objective is to explore the source of agreement
-attraction effects in Turkish discovered by Lago (2018). The
-interpretation of their finding is complicated by the fact that the
-possessive form of all head nouns used in their stimuli are
-morphologically ambiguous between possessive and accusative. In Turkish,
-genitive can be productively used for marking the subject of an embedded
-clause whereas accusative is rarely used for marking the subject. Due to
-this mismatch in the frequency of usage of accusative and genitive,
-which is used as a attractor in this experiment, as a controller, Lago
-(2018)'s findings could potentially be explained with occasional shallow
-processing. We have replicated Lago (2018)'s experiment with unambigious
-head nouns, and we have found similar agreement attraction effects.
-However, this may mean that participants engage in even more shallow
-processing than we imagined. We postulate that participants solely check
-for the presence of a \emph{-lAr} morpheme, while largely disregarding
-the remainder of the sentence. We utilize an experiment design in which
-we use a relative clause with or without plural agreement on the verb in
-place of the genitive possessor since both verbal and nominal plural
-morphemes are the same in Turkish, i.e.~the exponent of both is
-\emph{-lAr}. If participants did, in fact, adopt a superficial
-processing strategy, we would expect to find a number agreement
-attraction effect similar in magnitude to that in Lago (2018). However,
-if number attraction is not an artifact of shallow processing
-strategies, we should expect to find no number attraction effects in
-this experiment.
-
-\vspace{3mm}\hrule
-
-\emph{Keywords}: Turkish, agreement attraction, task effect, shallow
-processing
-
-\bleft
+\maketitle
 
@@
 
-\section{REPLICATON OF LAGO ET AL.
-(2018)}\label{replicaton-of-lago-et-al.-2018}
+\section{Experiment 1}\label{experiment-1}
 
-In their study, Lago (2018) investigate the comprehension of
-subject-verb agreement in Turkish-German bilinguals and Turkish
-monolinguals. They use speeded acceptability judgments for the effects
-of number attraction in Turkish. Their sentences make us of
-genitive-possessive constructions in the subject position, where the
-genitive is the attractor and the possessive is the head noun. They
-manipulate the grammaticality of the sentence by changing the plural
-morphology of the verb, and they also manipulate the plurality of the
-attractor noun. In grammatical conditions, the subject and the verb both
-bear singular morphology with no overt morpheme. Moreover, in the
-ungrammatical conditions, the verb bears the overt \emph{-lAr} morpheme
-whereas the subject is still singular as exemplified below.
+In their study, Lago (2018) investigates the comprehension of
+subject-verb agreement Turkish monolinguals. They use speeded
+acceptability judgments for the effects of number attraction in Turkish.
+Their sentences make us of genitive-possessive constructions in the
+subject position, where the genitive is the attractor and the possessive
+is the head noun. They manipulate the grammaticality of the sentence by
+changing the plural morphology of the verb, and they also manipulate the
+plurality of the attractor noun. In grammatical conditions, the subject
+and the verb both bear singular morphology with no overt morpheme.
+Moreover, in the ungrammatical conditions, the verb bears the overt
+\emph{-lAr} morpheme whereas the subject is still singular as
+exemplified below.
 
@@
 of the sentences were presented one word at a time in the center of the
-screen for 500 ms per word unlike Lago (2018) and Wagers et al. (2009),
-in which the duration was 300 ms per word. The experiment was run on a
-web-based platform titled the Ibex Farm, and all of the documentation
-can be found on our osf and github page.
+screen for 500 ms per word unlike Lago (2018) and Wagers, Lau, and
+Phillips (2009), in which the duration was 300 ms per word. The
+experiment was run on a web-based platform titled the Ibex Farm, and all
+of the documentation can be found on our osf and github page.
 
@@
 indicate an attractor noun with overt plural morphology. As seen in the
-figure, 22\% of the sentences with plural attractors and a singular verb
+figure, 1\% of the sentences with plural attractors and a singular verb
 were accepted by the participants, in line with the findings of Lago
-(2018). We also see a number attraction rate of 10\% which was also
+(2018). We also see a number attraction rate of 2\% which was also
 observed in Lago (2018) with close results.
@@
 
-And yes, I plan to beautify the figures.
+\subsection{Responses}\label{responses}
 
-\begin{figure}[H]
-  \begin{floatrow}
-    \ffigbox{%
+\begin{figure}
+\centering
+\includegraphics{AgreementAttraction_files/figure-latex/exp1AvgResponse-1.pdf}
+\caption{\label{fig:exp1AvgResponse}Estimates and 95\% credible intervals
+for the analysis of the probability of a `yes' response.}
+\end{figure}
 
-\begin{flushright}\includegraphics{output/figures/unnamed-chunk-1-1} \end{flushright}
-    }{\caption{A figure}}
+\begin{figure}
+\centering
+\includegraphics{AgreementAttraction_files/figure-latex/exp1AvgResponseLagoEtAl-1.pdf}
+\caption{\label{fig:exp1AvgResponseLagoEtAl}Estimates and 95\% credible
+intervals for the analysis of the probability of a `yes' response.}
+\end{figure}
 
-    \btabbox{%
+\subsection{Response Times}\label{response-times}
 
-    }{\caption{A table}}
-  \end{floatrow}
+\begin{figure}
+\centering
+\includegraphics{AgreementAttraction_files/figure-latex/exp1AvgRTs-1.pdf}
+\caption{}
 \end{figure}
+
+\clearpage
 
@@
 
-In this paper, we have entertained the idea of task effect in the
-so-called Turkish number attraction phenomenon. We argue that the
-findings of the Lago (2018) study is not clear and there are too many
-variables to account for in the experiment, one of them being the
-ambiguous morphology that the head noun bears. In the first experiment,
-we have replicated the attraction task of Lago (2018). We have found the
-similar effects of agreement with a bigger pool of participants. Then,
-for entertaining the other possibility in which we argue that
-participants do not fully reconstruct the sentence; however, they make
-us of the direct cue of overt morpheme \emph{-lAr}, we offer an
-experiment where we use object relative clauses as an attractor.
+\subsection{\texorpdfstring{In this paper, we have entertained the idea
+of task effect in the so-called Turkish number attraction phenomenon. We
+argue that the findings of the Lago (2018) study is not clear and there
+are too many variables to account for in the experiment, one of them
+being the ambiguous morphology that the head noun bears. In the first
+experiment, we have replicated the attraction task of Lago (2018). We
+have found the similar effects of agreement with a bigger pool of
+participants. Then, for entertaining the other possibility in which we
+argue that participants do not fully reconstruct the sentence; however,
+they make us of the direct cue of overt morpheme \emph{-lAr}, we offer
+an experiment where we use object relative clauses as an
+attractor.}{In this paper, we have entertained the idea of task effect in the so-called Turkish number attraction phenomenon.
+We argue that the findings of the Lago (2018) study is not clear and there are too many variables to account for in the experiment, one of them being the ambiguous morphology that the head noun bears.
+In the first experiment, we have replicated the attraction task of Lago (2018).
+We have found the similar effects of agreement with a bigger pool of participants.
+Then, for entertaining the other possibility in which we argue that participants do not fully reconstruct the sentence; however, they make us of the direct cue of overt morpheme -lAr, we offer an experiment where we use object relative clauses as an attractor.}}\label{in-this-paper-we-have-entertained-the-idea-of-task-effect-in-the-so-called-turkish-number-attraction-phenomenon.-we-argue-that-the-findings-of-the-lago-study-is-not-clear-and-there-are-too-many-variables-to-account-for-in-the-experiment-one-of-them-being-the-ambiguous-morphology-that-the-head-noun-bears.-in-the-first-experiment-we-have-replicated-the-attraction-task-of-lago.-we-have-found-the-similar-effects-of-agreement-with-a-bigger-pool-of-participants.-then-for-entertaining-the-other-possibility-in-which-we-argue-that-participants-do-not-fully-reconstruct-the-sentence-however-they-make-us-of-the-direct-cue-of-overt-morpheme--lar-we-offer-an-experiment-where-we-use-object-relative-clauses-as-an-attractor.}
 
@@
 
-We used the statistical language \texttt{R} (R Core Team 2018) for all
+We used the statistical language \texttt{R} (R Core Team, 2018) for all
 our analyses. These were implemented in dynamic rmarkdown documents
-using \texttt{knitr} (Xie 2014, 2015, 2018) and \texttt{rmarkdown}
-(Allaire et al. 2018, Xie et al. 2018) packages. All graphs have been
-done with \texttt{ggplot} (Wickham 2016). We also would like to thank
-Mine Nakipo\u{g}lu and Kadir Gökgöz for giving us the oppurtunity to
-conduct experiments and having participants from their classes.
+using \texttt{knitr} (Xie, 2018) and \texttt{rmarkdown} (Xie, Allaire,
+\& Grolemund, 2018) packages. All graphs have been done with
+\texttt{ggplot} (Wickham, 2016).
 
-\section{REFERENCES}\label{references}
+\section*{REFERENCES}\label{references}
+\addcontentsline{toc}{section}{REFERENCES}
 
 \hypertarget{refs}{}
-\hypertarget{ref-Allaire_2018}{}
-Allaire, J., Y. Xie, J. McPherson, J. Luraschi, K. Ushey, A. Atkins, H.
-Wickham, J. Cheng, W. Chang, and R. Iannone. 2018. Rmarkdown: Dynamic
-documents for r.
-
 \hypertarget{ref-Lago}{}
-Lago, S. 2018. Straight from the horse's mouth: agreement attraction
-effects with Turkish possessors.
+Lago, S. (2018). Straight from the horse's mouth: agreement attraction
+effects with Turkish possessors. doi:\href{https://doi.org/none}{none}
 
 \hypertarget{ref-R_Core_Team_2018}{}
-R Core Team. 2018. R: A language and environment for statistical
-computing. R Foundation for Statistical Computing, Vienna, Austria.
+R Core Team. (2018). \emph{R: A language and environment for statistical
+computing}. Vienna, Austria: R Foundation for Statistical Computing.
+Retrieved from \url{https://www.R-project.org/}
 
 \hypertarget{ref-Wagers2009}{}
-Wagers, M. W., E. F. Lau, and C. Phillips. 2009. Agreement attraction in
-comprehension: Representations and processes. Journal of Memory and
-Language 61:206--237.
+Wagers, M. W., Lau, E. F., \& Phillips, C. (2009). Agreement attraction
+in comprehension: Representations and processes. \emph{Journal of Memory
+and Language}, \emph{61}(2), 206--237.
+doi:\href{https://doi.org/10.1016/j.jml.2009.04.002}{10.1016/j.jml.2009.04.002}
 
 \hypertarget{ref-Wickham_2016}{}
-Wickham, H. 2016. Ggplot2: Elegant graphics for data analysis.
-Springer-Verlag New York.
-
-\hypertarget{ref-woolford}{}
-Woolford, E. 2009. Differential subject marking at argument structure,
-syntax, and pf. Pages 17--40 \emph{in} Differential subject marking.
-Springer.
-
-\hypertarget{ref-Xie_2014}{}
-Xie, Y. 2014. Knitr: A comprehensive tool for reproducible research in
-R. \emph{in} V. Stodden, F. Leisch, and R. D. Peng, editors.
-Implementing reproducible computational research. Chapman; Hall/CRC.
-
-\hypertarget{ref-Xie_2015}{}
-Xie, Y. 2015. Dynamic documents with R and knitr. 2nd editions. Chapman;
-Hall/CRC, Boca Raton, Florida.
+Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}.
+Springer-Verlag New York. Retrieved from \url{http://ggplot2.org}
 
 \hypertarget{ref-Xie_2018}{}
-Xie, Y. 2018. Knitr: A general-purpose package for dynamic report
-generation in r.
+Xie, Y. (2018). \emph{Knitr: A general-purpose package for dynamic
+report generation in r}. Retrieved from \url{https://yihui.name/knitr/}
 
 \hypertarget{ref-Xie_2018a}{}
-Xie, Y., J. Allaire, and G. Grolemund. 2018. R markdown: The definitive
-guide. Chapman; Hall/CRC, Boca Raton, Florida.
-
-\eleft
-
-\clearpage
-
-\listoftables
-
-\listoffigures
-
-\clearpage
+Xie, Y., Allaire, J., \& Grolemund, G. (2018). \emph{R markdown: The
+definitive guide}. Boca Raton, Florida: Chapman; Hall/CRC. Retrieved
+from \url{https://bookdown.org/yihui/rmarkdown}
 

### 2019-02-13 Results and Analysis/playing a bit.R

@@ -1,381 +1,0 @@
-# LIBRARIES & DATA ------
-library(languageR)
-library(tidyverse)
-library(gdata)
-library(MASS)
-library(magrittr)
-library(ggplot2)
-
-# First convert to csv file, using the "_" and "," character as a delimter
-# setwd("C:/Users/utku/Downloads/cormorant_final/results")
-# getwd()
-
-# Then load into R, splitting the csv file on the comma ","
-data <- read.csv('results', 
-                 header = F, 
-                 comment.char = "#", 
-                 encoding = "UTF-8" , 
-                 col.names = paste0("V",seq_len(11)), 
-                 fill = TRUE)
-
-
-# Add column names to dataframe
-colnames(data) = c("Time", "MD5", "ControllerType", "SentenceNoInStimFile", "Element", "Type", "Item", "Sentence", "Question","Answer", "RT")
-
-# Note: Less transparent columns
-# Time: 		When results sent to server
-# MD5: 			Encoding of IP address
-# Controller: 	Presentation type
-
-
-# Cleaning up data
-# What information is there:
-# levels(data$Type)
-# Remove extra information: Should I play with every condition?
-
-
-
-
-
-
-
-# FORM & PRACTICE ------
-# Make Form Entries Columns and left join them, get for unique MD5
-FormEntries <- subset(data, ControllerType != "DashedAcceptabilityJudgment" ) %>% drop.levels(); nrow(data)
-data %<>% subset(ControllerType == "DashedAcceptabilityJudgment")
-
-age <- dplyr::select(FormEntries, MD5,Sentence,Question) %>% 
-  dplyr::filter(Sentence == "age") %>%
-  dplyr::select(MD5, Age = Question)
-
-# Note: The radio buttons on the page returned "male" when participants specified that they were native speakers of Turkish, and "female" otherwise,
-# due to a copy-and-paste error.
-natturk <- dplyr::select(FormEntries, MD5,Sentence,Question) %>% 
-  dplyr::filter(Sentence == "natturk") %>%
-  dplyr::select(MD5, Natturk = Question) %>%
-  mutate(Natturk = Natturk == "male")
-
[…]

### 2019-02-13 scripts/experiment1_eda.R

@@ -1,0 +1,30 @@
+library(languageR)
+library(tidyverse)
+library(gdata)
+library(MASS)
+library(magrittr)
+library(ggplot2)
+
+fname_data <- "../workspace1/exp_data.rds"
+
+
+dataAv <- data %>% 
+  group_by(experiment, condition, grammatical, verb_num, attracted) %>%
+  summarize(avRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T)) %>% 
+  as.data.frame()
+
+dataAv %>% ggplot(aes(grammatical, p_yes, group = paste(experiment,attracted), color = experiment )) + geom_point() + geom_line(aes(linetype =attracted)) 
+
+data$trial_group <- Hmisc::cut2(data$trial_no, g=5)
+
+dataAvSplit <- data %>% 
+  group_by(experiment, condition, grammatical, verb_num, attracted, trial_group) %>%
+  summarize(avRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T)) %>% 
+  as.data.frame()
+
+plot_split <- dataAvSplit %>% ggplot(aes(grammatical, p_yes, group = paste(experiment,attracted), color = experiment )) + geom_point() + geom_line(aes(linetype =attracted)) + facet_wrap(~trial_group)
+
+
+dataAvClean <- slice(dataAvClean, 1:4)
+
+plot_average <- dataAvClean %>% ggplot(aes(grammatical, p_yes, group = paste(experiment,attracted), color = experiment )) + geom_point() + geom_line(aes(linetype =attracted)) #+ facet_wrap(~experiment, scales = "free_y")

### 2019-02-13 scripts/experiment1_prepare.R

@@ -1,0 +1,80 @@
+library(languageR)
+library(tidyverse)
+library(gdata)
+library(MASS)
+library(magrittr)
+library(ggplot2)
+
+fname_data <- "../Data/Experiment1/results/results"
+fname_data_out <- "../workspace_exp1/exp_data.rds"
+
+data <- read.csv(fname_data, 
+                 header = F, 
+                 comment.char = "#", 
+                 encoding = "UTF-8" , 
+                 col.names = paste0("V",seq_len(11)), 
+                 fill = TRUE)
+colnames(data) = c("Time", "MD5", "ControllerType", "SentenceNoInStimFile", "Element", "Type", "Item", "Sentence", "Question","Answer", "RT")
+
+FormEntries <- subset(data, ControllerType != "DashedAcceptabilityJudgment" ) %>% drop.levels(); nrow(data)
+data %<>% subset(ControllerType == "DashedAcceptabilityJudgment")
+age <- dplyr::select(FormEntries, MD5,Sentence,Question) %>% 
+          dplyr::filter(Sentence == "age") %>%
+          dplyr::select(MD5, Age = Question)
+natturk <- dplyr::select(FormEntries, MD5,Sentence,Question) %>% 
+          dplyr::filter(Sentence == "natturk") %>%
+          dplyr::select(MD5, Natturk = Question) %>%
+          mutate(Natturk = Natturk == "male")
+dex <- dplyr::select(FormEntries, MD5,Sentence,Question) %>% 
+          dplyr::filter(Sentence == "dex") %>%
+          dplyr::select(MD5, Dex = Question) %>%
+          mutate(Dex = ifelse(Dex == "male", "right-handed", "left-handed"))
+FormPart <- dplyr::left_join(age, natturk, by = "MD5") %>% 
+        dplyr::left_join(., dex , by = "MD5" ) %>% 
+        unique()
+lenForm <- length(levels(factor(FormPart$MD5))); lenForm
+md5form <- levels(factor(FormPart$MD5))
+md5form_subject <- data.frame("MD5" = md5form, "subject" = sprintf("S[%s]",seq((lenForm))))
+FormPart <- merge(FormPart,md5form_subject, all = T)
+
+stopifnot( nrow(data) %% 2 == 0 )
+rows_stim <- data[c(T,F),]
+rows_resp <- data[c(F,T),]
+
[…]

### 2019-02-13 scripts/misc.R

@@ -1,0 +1,260 @@
+
+# TODO: Figure out how to treat missing data in this function
+se_cousineau <- function(df, n_conditions, subject, DV, group, is_proportion = NULL)
+{
+  stopifnot(!"avgDV" %in% colnames(df))
+  subject <- substitute(subject) %>% deparse()
+  DV <- substitute(DV) %>% deparse()
+  
+  subj_means <- df %>% group_by_(subject) %>% dplyr::summarize_(avgDV = sprintf("mean(%s, na.rm = T)", DV))
+  GM <- mean(subj_means$avgDV)
+  df %<>% group_by_(subject) %>% mutate_(nDV = sprintf("%s - mean(%s, na.rm = T) + GM", DV, DV) )
+  
+  if (is.null(is_proportion)) {
+    dv <- df[[DV]]
+    dv_unique <- unique(dv)
+    if ( is.logical(dv) || (length(dv_unique) == 2 && all(dv_unique %in% c(0,1))) ) {
+      is_proportion <- TRUE
+    } else {
+      is_proportion <- FALSE
+    }
+  }
+  
+  var_correction_factor <- n_conditions/(n_conditions-1)
+  df %>% group_by_(.dots = group) %>% 
+    dplyr::summarize(M = mean(nDV, na.rm = T),
+                     #Var = ifelse(is_proportion, M*(1-M), var(x)) * var_correction_factor,
+                     Var = var(nDV, na.rm = T) * var_correction_factor,
+                     N = sum(!is.na(nDV)),
+                     SE = sqrt(Var/N) )
+}
+
+
+
+
+nunique <- function(x) length(unique(x))
+
+
+read_file <- function(fname) { readChar(fname, file.info(fname)$size) }
+
+
+
+
+lognormalParamMeanSigma <- custom_family(
+  "lognormalParamMeanSigma", dpars = c("mu", "sigma"),
+  links = c("identity", "log"), lb = c(0, 0),
+  type = "real"
+)
+
+stan_funs_lognormalParamMeanSigma <- "
+real lognormalmean2mu(real mean, real sigma) {
+  real mu;
+  if (mean < 25) {
+    mu = log( mean + (exp(mean)-mean)/(exp(2*mean) + 1) ) - sigma^2/2;
+  } else {
+    mu = log( mean ) - sigma^2/2;
+  }
+  return mu;
+}
+real lognormalParamMeanSigma_lpdf(real y, real mean, real sigma) {
[…]

### 2019-06-10 Paper/AgreementAttraction.Rmd
almost a mediocre paper

@@
 ---
-title: 'Agreement Attraction in Turkish: Effects of Nominal and Verbal Plural Morphemes'
-
+title             : "Agreement Attraction"
+shorttitle        : "Agreement Attraction in Turkish"
 author: 
@@
     corresponding : yes    # Define only one corresponding author
-    address       : "Postal address"
+    address       : ""
     email         : "utku.turk@boun.edu.tr"
-  - name          :  "Pavel Logačev"
+  - name          : "Pavel Logacev"
     affiliation   : "1"
-affiliation       :
+
+affiliation:
   - id            : "1"
-    institution   : "Boğaziçi University University, Istanbul, Turkey"
+    institution   : "Boğaziçi University"
 
-authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-  Enter author note here.
-shorttitle: Why Utku is the best
+#authornote: |
+#  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+#
+#   Enter author note here.
+
 abstract: |
-  This paper deals with agreement attraction because it's more important than literally anything else.
-  Recently, Lago et al.
-(2018) demonstrated agreement attraction effects in comprension in Turkish, which is super-interesting because this finding allows us to make a lot of money.
-However, there is an alternative explanation for their findings: dark sorcery.
-In this paper we tested the predictions of these alternative accounts.
-In Experiment 1, we found that a particular kind of dark sorcery was not involved.
-In Experiment 2, we shall find ...
+    The comprehension of agreement within the elements of a sentence is known to fail.
+One of these comprehension errors is known as agreement attraction.
+Speakers may erroneously find a sentence in which the "attractor" agrees with the verb instead of the "head" of the subject.
+Data from typologically different languages and explanations from different frameworks shows that we are far from understanding by what the attraction is modulated.
+Some theories refer this phenomenon as a faulty representation of the number on the head of the subject phase whereas other theories argues that the attraction is due to an error in the access to the number of the subject.
+In this paper, we report two experiments exploring a possible explanation for agreement attraction: an extremely shallow processing.
+The first experiment is a replication of @Lago2018 where we changed the head of the subject in order to differentiate between the accusative case *-I*.
+In the second experiment, we have used a relative clause which only consists of a plural marked verb as a distractor.
+Our results show that while people do indeed care more than just "matching" the forms of plural verbal.
+Either comprehenders have some sort of restriction to not use cues from verbs upon accessing the number of the plural morpheme or there is a syntactic reason for the number feature of plural morpheme to not "percolate."
 
-keywords          : "keywords"
-wordcount         : "X"
-bibliography      : ["myreferences.bib", "references.bib"]
+# keywords          : "keywords"
+# wordcount         : "X"
+
+bibliography      : ["myreferences.bib","r-references.bib"]
+
 floatsintext      : no
@@
 draft             : no
+header-includes   :
+  - \usepackage[utf8]{inputenc}
+  - \usepackage[T1]{fontenc}
+  - \usepackage{xcolor}
+  - \usepackage{hhline}
+  - \usepackage{mathtools}
+  - \linespread{1}
+  - \usepackage{gb4e}
+  - \noautomath #trying to see why shorttitle does not appear in the other paper. when done like this it appears.
+  - \usepackage{setspace}
+  - \makeatletter
+  - \apptocmd{\@exe}{\singlespacing}{}{}
+  - \makeatother
+  - \usepackage{sectsty}
+  - \allsectionsfont{\large}
+  - \usepackage{color}
+  - \usepackage{hyperref}
+  - \hypersetup{colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue} 
+  - \usepackage[english]{babel}
+  - \addto\extrasenglish{\renewcommand{\itemautorefname}{Item}}
+  - \renewcommand*{\nameyeardelim}{\addcomma\space}
+  - \usepackage{tikz}
+  - \usepackage{tikz-qtree}
+#  - \usepackage[mcolblock]{leipzig}
+#  - \makeglossaries
+  - \let\eachwordone=\textit
+#  - \renewcommand{\eachwordone}{\footnotesize\textit}
+#  - \let\eachwordtwo=\footnotesize
+
 documentclass     : "apa6"
 classoption       : "doc"
-output            : 
+output:
   papaja::apa6_pdf:
-    includes:
-        in_header: header.tex
-editor_options: 
-  chunk_output_type: console
+    number_sections: true
+    citation_package: biblatex
+keep_tex: TRUE
+biblatexoptions: [maxbibnames=999]
 ---
-
-<!--  - knitcitations.bib
-
--->
 
@@
 
-<!--
-\vspace{2mm}\hrule
+# Introduction
 
-In this paper, our objective is to explore the source of agreement attraction effects in Turkish discovered by @Lago.
-The interpretation of their finding is complicated by the fact that the possessive form of all head nouns used in their stimuli are morphologically ambiguous between possessive and accusative.
-In Turkish, genitive can be productively used for marking the subject of an embedded clause whereas accusative is rarely used for marking the subject.
-Due to this mismatch in the frequency of usage of accusative and genitive, which is used as a attractor in this experiment, as a controller, @Lago's findings could potentially be explained with occasional shallow processing.
-We have replicated @Lago's experiment with unambigious head nouns, and we have found similar agreement attraction effects.
-However, this may mean that participants engage in even more shallow processing than we imagined.
-We postulate that participants solely check for the presence of a *-lAr* morpheme, while largely disregarding the remainder of the sentence.
-We utilize an experiment design in which we use a relative clause with or without plural agreement on the verb in place of the genitive possessor since both verbal and nominal plural morphemes are the same in Turkish, i.e.
-the exponent of both is *-lAr*.
-If participants did, in fact, adopt a superficial processing strategy, we would expect to find a number agreement attraction effect similar in magnitude to that in @Lago.
-However, if number attraction is not an artifact of shallow processing strategies, we should expect to find no number attraction effects in this experiment.
+# Literature
 
-\vspace{3mm}\hrule
+## Theories of attraction
 
-*Keywords*: Turkish, agreement attraction, task effect, shallow processing
+Agreement attractions are defined as instances of incorrect agreements of an element with a distractor that is not its grammatical controller.
+As in \autoref{E1}, the target of the agreement is the verb *are*, the attracting distractor is *bottles*, and the feature erroneously assesed is the number feature of the grammatical controller *label*.
 
----
-nocite: | 
-  @woolford
-...
+\begin{exe}
+\ex[*]{The label on the bottles \textit{are} wrong.\footnotemark}
+\label{E1}
+\end{exe}
 
--->
+\footnotetext{The convention of using $\ast$ is to show the ungrammaticality of the sentencee.}
 
-# INTRODUCTION
+This type of attraction, called number attraction in subject-verb agreement, first theorized by @Quirk1972 and attested experimentally by @Bock1991 in language production.
+One of the theoretical attempts to explain such phenomenon was Marking and Morphing Theories [@Bock2001; @Eberhard2005 among others].
+The reason it is called *Marking* and *Morphing* is because there is two possible explanation within the framework with regards to where and when the attraction occurs.
+First possibility is speaker (and/or comprehender) can erroneously create a semantic representation of the head with wrong number feature in the marking process in the marking process.
+Another possibility is that the attraction may arise from an interfering number feature of the attractor with the number feature of the highest noun phrase node in morphing process.
+During the this process, the speaker forms a final number value of the subject phrase, which is determined by each morpheme within the same phrase and their number information with particular weight.
+In morphing process, these other morphemes with number information may contaminate the final number value with perculation mechanism, which depends on the depth of the syntactic embedding.
+As the prediction goes, the more embedded an attractor is, the less attraction they trigger as shown in @Bock1992 in which authors shown that attractors within a relative clause trigger less agreement attraction in the production.
 
-Attraction errors in the production and comprehension of subject-verb agreement, in which a verb does not agree with the grammatical agreement controller, but with a potential attractor, have been the main topic of research in many studies for quite a long time.
-In fact, it is still a widely researched area in psycholinguistic studies.
-Despite the comprehensive research that has been carried out, studies that have been conducted on agreement attraction in Turkish have been very limited.
-In fact, @Lago is currently the only study that explores this phenomenon in Turkish.
-@Lago  makes use of genitive-possessive structures in the subject position, in which the possessive-marked noun is the head of the noun phrase which acts as the grammatical agreement controller, and the genitive noun serves as a potential attractor.
-In a speeded acceptability judgment study, @Lago found a significant effect of number agreement attraction.
+However, other studies shown that other preverbal elements, such as objects, object relative clauses, object clefts, and object questions, may trigger agreement attraction [@Kimball1971; @Hartsuiker2001; @Franck2006; @Franck2015 among others].
+In sentences like \autoref{E2}, the pronominal object *hen* triggers and agreement attraction without being a part of the subject.
+
+\begin{exe}
+\ex[*]{
+\gll Theo denkt dat de knecht hen roep.\\
+Theo thinks that the servant them call.\textsc{Pl}.\\
+\trans  `Theo thinks that the servant \textit{call} them'}
+\label{E2}
+\end{exe}
+
+Since the Marking and Morphing theories put the source of the agreement attraction on the probe, i.e.
+subject phrase, they cannot explain agreement attraction effects that are triggered by an distractor outside of the syntactic scope of the subject.
+Regardless, these effects can be explained in a framework where the source of the agreement attraction can placed on the trigger, i.e.
+verb.
+@Badecker2007 suggests that a process where the subject is retrieved from the memory plays a role in agreement attraction effects as well [see as well @Wagers2009].
+Building on the work in cue-based retrieval mechanism [@Gordon2001; @Lewis2005; @Lewis2006 among others], they argued that when spakers reach the verb, they try to retrieve the subject using certain features (cues) that essentially marks the *subjecthood*.
+Thus, any element that matches (or partially mathces) with the cues in use may cause agreement attraction regardless of their position or syntactic relation to the subject.
+Going back to \autoref{E2}, it is expected, then, for an object which shares features like being preverbal, being a noun phrase, ability to bear agreement with a subject to trigger agreement attraction.
+
+Another challenge for the Marking and Morphing model was the grammaticality asymmetry.
+Due to the spreading activation formula utilized in the Marking and Morphing model [see @Dell1986], this model overgeneralizes the attraction effects to both ungrammatical and grammatical sentences and predicts both \autoref{E1} and \autoref{E3} to be present empirically, which is not the case [@Wagers2009].
+
+\begin{exe}
+\ex[*]{The labels on the bottle \textit{is} wrong.}
+\label{E3}
+\end{exe}
+
+On the other hand, cue-based retrieval models successfully predicts the the grammaticality asymmetry as shown by @Dillon2013 in an ACT-R simulation as well as numerous studies in self-paced reading, eye-tracking, and ERP studies [@Wagers2009; @Tucker2010; @Tanner2014; @Lago2015 among others].
+This success was due to their replacement of source of the attraction.
+According to cue-based retrieval models, the probe, verb, presents certain cues to retrieve an NP with matching features in agreement.
+When features of the grammatical controller of the verb does not *fully* match with the cues, no single NP will be satisfying the *agreement*.
+Thus, another NP in the clause can match with cues presented by the VP, such as its case, syntactic position, grammatical number.
+Thus, if there is no *retrieval cue* in the first place, i.e.
+the verb is nor marked plural, there will be no need for partial match.
+
+## Turkish relative clauses and plural marking
+
+Before discussing the experiments, we will touch upon the mechanisms that we utilize in the experiments: optional plural agreement, relative clause structure, and syncretism between possessive and accusative.
+
+Turkish plural agreement is quite similar with regards to the subject-verb number agreement in the first and second plural person.
+However, Turkish plural agreement is optional in third person plurals as shown in \autoref{TB1} and \autoref{TB2}.
+The other characteristics of Turkish plural agreement is that, the nominal and verbal plural marking is done by the same morpheme *-lAr*\footnote{The convention of using an uppercase A is to show that the morpheme can surface as either \textit{-ler} or \textit{-lar} according to the previous vowel due to the vowel harmony reasons.}.
+
+\begin{exe}
+\ex \label{TB1} Dün çocuk-\textsc{Lar} okul-a git-ti-\textsc{Ler} mi?
+\ex 
+\gll Dün çocuk-LAR okul-a git-ti mi?\\
+yesterday child-\textsc{Pl} school-\textsc{Dat} go-\textsc{Pst}(-\textsc{Pl}) Q\\
+\trans ``Did the children go to school yesterday?''
+\label{TB2}
+\end{exe}
+
+As for Turkish relative clauses, they always precede the external head noun [@Goksel2004; @Taylan2015] and they use either *-An* or *-dIk* nomilizers to show the referentiality of the subject within the relative clause as shown in \autoref{TB3} and \autoref{TB4} [@Haig1997].
+Moreover, due to pro-drop and null object properties of the Turkish [see @Ozturk2005], relative clauses can consist of only the verb itself in Turkish as in \autoref{TB5}.
+
+\begin{exe}
+\ex \label{TB3}
+\gll Kazı-lar-ın yap-ıl-dığ-ı alan ... \\
+excavation-\textsc{Pl}-\textsc{Gen} do-\textsc{Pass}-\textsc{Nmlz}-\textsc{Poss} area ... \\
+\glt ``The place where the excavations are done ...''
+\ex \label{TB4}
+\gll Kazı-lar yap-ıl-an alan ... \\
+excavation-\textsc{Pl} do-\textsc{Pass}-\textsc{Nmlz} area ... \\
+\glt ``A place where some excavations are done ...''
+\ex \label{TB5}
+\gll Gör-düğ-ü kuş çok güzel-di.\\
+see-\textsc{Nmlz}-\textsc{Poss} bird very pretty-\textsc{Pst}\\
+\glt ``The bird that he/she saw was very pretty.''
+\end{exe}
+
+Final characteristics that interests us in this paper is the morphological syncretism between the accusative case and possessive suffix in Turkish.
+When the possessive case is attached to a nominal stem that ends with a consonant, it is pronounced as \textit{-I}, which is exactly how accusative case is also pronounced in the same environment in Turkish.
+However, the ambiguity is immediately resolved when they follow a nominal stem that ends with a vowel.
+In the latter environment, the accussative case surfaces as *-yI* whereas the possessive surfaces as *-sI(n)*\footnote{The final \textit{n} is only surfaces when any other morphemes follows the possessive suffix.
+Otherwise, it surfaces as \textit{-sI}} as shown in \autoref{TB6}-\autoref{TB9}.
+
+\begin{exe}
+\ex
+\begin{xlist}
+\ex \label{TB6}
+\gll Kuş-\textbf{u} beğen-di-m.\\
+bird-\textsc{Acc} like-\textsc{Pst}-\textsc{1Sg}\\
+\glt ``I liked the bird.''
+\ex \label{TB7}
+\gll Emin'in kuş-\textbf{u} güzel-miş.\\
+Emin-\textsc{Gen} bird-\textsc{Poss} pretty-\textsc{Evd}\\
+\glt ``Emin's bird was pretty.''
+\ex \label{TB8}
+\gll Kedi-\textbf{yi} beğen-di-m.\\
+cat-\textsc{Acc} like-\textsc{Pst}-\textsc{1Sg}\\
+\glt ``I liked the cat.''
+\ex \label{TB9}
+\gll Emin'in kedi-\textbf{si} güzel-miş.\\
+Emin-\textsc{Gen} cat-\textsc{Poss} pretty-\textsc{Evd}\\
+\glt ``Emin's cat was pretty.''
+\end{xlist}
+\end{exe}
+
+# The Current Study
+
+In this study, we examine the question of whether agreement attraction is due to the shallow parsing that mainly depends on the memory of plural morpheme *-lAr* and matching the verbal plural morpheme with the nominal plural morpheme.
+
+First of all, we investigate the effects of ambiguous suffix with Experiment 1, which is a replication of @Lago2018.
+@Lago2018 makes use of genitive-possessive structures in the subject position, in which the possessive-marked noun is the head of the noun phrase which acts as the grammatical agreement controller, and the genitive noun serves as a potential attractor as in \autoref{Lagoitem}.
+In a speeded acceptability judgment study, @Lago2018 found a significant effect of number agreement attraction.
 However, the interpretation of their findings may be a result of the fact that non-subjecthood cues originate from their use of morphologically ambiguous forms of the possessive.
@@
 
+\begin{exe}
+\ex \label{Lagoitem}
+\gll \c{S}ark{\i}c{\i}-n{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}-lar.\\
+singer-\textsc{Gen} vocalist-\textsc{Poss} stage-\textsc{Loc} non-stop jump-\textsc{Pst}-\textsc{3Pl}\\
+\glt The singer's backup vocalist jumped on the stage non-stop.
+\end{exe}
+
 In Turkish, accusative number agreement controllers are extremely rare, while genitive agreement controllers are very frequent.
-Thus, @Lago's finding could potentially be explained with occasional shallow processing.
+Thus, @Lago2018's finding could potentially be explained with occasional shallow processing.
 When all syntactic relations in the sentence were processed fully, the possessive noun may have been identified as the controller.
-Meanwhile, the genitive noun may sometimes have been erroneously identified as the controller during shallow processing because genitives are more likely to act as agreement controllers than accusatives (SOURCE).
-A second alternative explanation for @Lago's findings may be the fact that participants may engage in even more shallow processing than outlined above.
-Participants may have erroneously responded *Yes* on some trials for two main reasons: (i) the presence of a plural morpheme on a noun (attractor or controller), and (ii) the presence of a plural agreement morpheme on the verb.
-We speculate that in such trials, participants would have simply tried to check for the presence of such morphemes, while largely disregarding the remainder of the sentence.
+Meanwhile, the genitive noun may sometimes have been erroneously identified as the controller during shallow processing because genitives are more likely to act as agreement controllers than accusatives.
+In order to check this effect, we have replicated @Lago2018 in Experiment 1.
+We have used different head nouns which ends with a vowel to differentiate between the accusative case and the possessive suffix, i.e.
+*taksici* (taxi driver) instead of *vokalist* in \autoref{Lagoitem}.
 
-We first replicated @Lago's experiment with unambiguous head nouns.
-To this end, we revised the items that were used previously in order to avoid morphological ambiguity between possessive and accusative forms.
-The effect found in @Lago was also observed when unambiguous nouns were used, as will be discussed in \S 2.
+With regards to percolation theories, this replication should yield no difference from @Lago2018.
+The syntactic depth has not changed, the number information of the head and distractor have not changed.
+Slight differences may be expected since we have changed some items which can be found in Appendix 1, and this situation can create a erroneous number information to be used in the marking process.
 
-\S 3 discusses the alternative account that posits even more shallow processing as mentioned above and presents a pre-registered experiment using RC attractors with potential outcomes and their indications.
-Since both nominal and verbal plural morphemes in Turkish are expressed with the same form (*-ler* or *-lar* depending on the phonological environment), we can test this possibility with an experiment in which a relative clause with or without plural agreement on the verb in place of the genitive possessors is used.
-An agreement attraction effect similar in magnitude to that observed in @Lago would indicate that participants use the aforementioned strategies.
+As for cue-based retrieval models, we should expect a lower agreement attraction effect in this replication.
+This predictions stems from the fact that possibility of erroneous representation of features of head noun is now lower due to our efforts to differentiate between the accusative case and the possessive marking.
+@Lago2018 argues that due to the subjecthood information provided by genitive case, there is an effect of agreement attraction.
+We eliminate the possibility of possible non-subjecthood clues given by the form that is shared by the accusative case and the posessive suffix.
 
-\S 4 offers a discussion of the issue of number attraction and where this experiments leaves us. Lastly, \S 5 presents a brief conclusion and topics for future research.
+Within the shallow processing model, we would also expect a no change in the status of agreement attraction.
+In our account of shallow processing, we argue that when the comprehenders reach the verb and saw plural morpheme, they engage in matching mechanism where they try to match the verbal plural morpheme with a previous nomimal plural morpheme.
+An agreement attraction, then, is not a result of a partial matching or a representational error of number feature; instead, it is the result of a state of memory in which comprehenders misremember either the existence of the nominal plural morpheme or the place of the nominal plural morpheme as stated in the MPT model of the agreement attraction within shallow processor within \autoref{model1}, \autoref{model2}, \autoref{model3}\footnote{Author here wishes he knew more latex to do the MPT tree more neat.}.
 
-# Experiment 1
+\begin{figure}[htb!]
+\centering
+\begin{tikzpicture}[
+    sibling distance        = 0.5em,
+    level distance          = 5em,
+    edge from parent/.style = {draw, -latex},
+    every node/.style       = {font=\scriptsize},
+    sloped
+  ]
+\Tree [.{\ }
+        \edge node[auto=left]{f}; [.\node[draw,rounded corners=.8ex]{generic failure};
+                                     \node[draw]{Ungrammatical};]
+        \edge node[auto=left]{1-f};
+        [.\node[draw,rounded corners=.8ex]{no failure};
+          \edge[dashed]; [.\node[]{Plural Verbs}; 
+                           \edge[dashed]; \node[]{With Distractor};
+                           \edge[dashed]; \node[]{Without Distractor};
+                         ] 
+          \edge[dashed]; [.\node[]{Singular Verbs}; 
+                          \edge[dashed]; [.\node[draw,rounded corners=.8ex]{No checking};
+                                           \node[draw]{Grammatical};]
+                         ] 
+        ] 
+      ]
+\end{tikzpicture}
+\caption{xd}
+\label{model1}
+\end{figure}
+
+\begin{figure}[htb!]
+\centering
+\begin{tikzpicture}[
+    sibling distance        = 0.5em,
+    level distance          = 5em,
+    edge from parent/.style = {draw, -latex},
+    every node/.style       = {font=\scriptsize},
+    sloped
+  ]
+\Tree [.\node[]{Without Distractor}; 
+                                          \edge node[auto=left]{m$_2$}; [.\node[draw,rounded corners=.8ex]{No Memory of -lAr};
+                                                                        \edge node[auto=left]{g}; \node[draw]{Grammatical};
+                                                                        \edge node[auto=left]{1-g}; \node[draw]{Ungrammatical};]
+                                          \edge node[auto=left]{1-m$_2$}; [.\node[draw,rounded corners=.8ex]{Memory of -lAr}; 
+                                          \edge node[auto=left]{1-p$_2$}; [.\node[draw,rounded corners=.8ex]{No Place of -lAr};
+                                                                        \edge node[auto=left]{g}; \node[draw]{Grammatical};
+                                                                        \edge node[auto=left]{1-g}; \node[draw]{Ungrammatical};]
+                                          \edge node[auto=left]{p$_2$}; [.\node[draw,rounded corners=.8ex]{Misrepresented place of -lAr};
+                                                                        \node[draw]{Ungrammatical};]]]
+
+\end{tikzpicture}
+\caption{xd}
+\label{model2}
+\end{figure}
+\begin{figure}[htb!]
+\centering
+\begin{tikzpicture}[
+    sibling distance        = 0.5em,
+    level distance          = 5em,
+    edge from parent/.style = {draw, -latex},
+    every node/.style       = {font=\scriptsize},
+    sloped
+  ]
+\Tree [.\node[]{With Distractor}; 
+                                          \edge node[auto=left]{m$_1$}; [.\node[draw,rounded corners=.8ex]{No Memory of -lAr};
+                                                                        \edge node[auto=left]{g}; \node[draw]{Grammatical};
+                                                                        \edge node[auto=left]{1-g}; \node[draw]{Ungrammatical};]
+                                          \edge node[auto=left]{1-m$_1$}; [.\node[draw,rounded corners=.8ex]{Memory of -lAr}; 
+                                          \edge node[auto=left]{1-p$_1$}; [.\node[draw,rounded corners=.8ex]{No Place of -lAr};
+                                                                        \edge node[auto=left]{g}; \node[draw]{Grammatical};
+                                                                        \edge node[auto=left]{1-g}; \node[draw]{Ungrammatical};]
+                                          \edge node[auto=left]{p$_1$}; [.\node[draw,rounded corners=.8ex]{Memory of place of -lAr};
+                                                                        \node[draw]{Grammatical};]]]
+
+\end{tikzpicture}
+\caption{xd}
+\label{model3}
+\end{figure}
+
+In our second experiment, we investigate the predictions made from our model using a verbal plural morpheme within a distractor relative clause.
+As mentioned earlier, the verbal plural morpheme in Turkish is exactly the same with the nominal plural with regards to its stress, its behaviour, and its form: *-lAr*.
+Since Turkish relative clauses are essentially nominals due the nomilization process, they behave exactly like other nominals within the sentence [@Goksel2004; @Taylan2015].
+They can be marked with cases, plural agreement and they can have postpositions that any nominal also can.
+This syntactic formation enables us to question how shallow people process, how much syntactic information is relevant, or how perfectly people encode the features of the elements of the sentence.
+In our experiment 2, we have used items in which the referential head noun of the subject is modified with a single-word relative clause as in \autoref{ouritem1}.
+
+\begin{exe}
+  \ex \label{ouritem1}
+      \gll D\"{o}v-d\"{u}k-(\textbf{ler})-i \c{c}ocuk mutfak-ta bayg{\i}n hal-de yat-{\i}yor-(\textbf{lar})-d{\i}.\\
+  beat-\textsc{Nmlz}-(\textsc{Pl})-\textsc{Poss} kid kitchen-\textsc{Loc} unconscious state-\textsc{Loc} lie-\textsc{Prog}-(\textsc{Pl})-\textsc{Pst}\\
+      \glt Intended: The kid that they beat were laying in the kitchen unconscious.
+\end{exe}
+
+Within the framework of percolation theories, we expect a harsh decline in the agreement attraction effects\footnote{Discussion regarding to the how and where relative clauses adjoined is omited due to the scope of the paper.
+However, it should be clear that a late insertion analysis where the relative clauses are actually above the head noun would yield different results.
+In this paper, I assume that modifiers like relative clauses are within the noun phrase, which deems them \textit{syntactically} deeper placed in the hierarchical three than the possessee.}.
+The reason for this expected decline is the fact that relative clauses being relative *deeper* in the hierarchical structure than the possessee of genitive-posessive structure.
+
+As for cue-based retrieval models, we would expect an agreement attraction quite similar to the one that we originally have in @Lago2018.
+The reason for this expected agreement attraction is the fact that apart from having a verbal root, the relative clauses and nomials are behave exactly the same in terms of *nounnness*.
+Like nominals, nominalized structures first marked with plural and then with the case or possessive suffix.
+From this aspective, it seems like there should be no difference.
+However, one may argue that the features related to the verbal and nominal can be encoded differently.
+Thus, there will no partial match at any time given due to the fact that verbal plural morpheme at the main verb does specify cues for specific type of plural marking.
+One other question that may arise from this structure is that whether or not the parts of already-formed dependencies can feed the following dependency resolution.
+In other words, the verbal plural morpheme *-lar* on *dövdükleri* in \autoref{ouritem1} is already a trigger of a cue retrieval process.
+And, when it is merged with the nominal head *çocuk*, there is a formed semantic meaning that is  "a group of people have beaten a kid."  However, this *suggesstion* assumes that relative clauses are formed at the very moment.
+Moreover, we also need to assume that after forming a relative clause they are unreachable, meaning that they do not contribute to the processing of the sentnece, anymore.
+
+Lastly in our extremely shallow processing model, we would expect a significant effect of agreement attraction.
+Due to one of the writers inability to *run the numbers* and *form the mpt trees in time*, this part unfortunately does not go beyond than a verbal argumentation.
+The reason we wait a significant effect of agreement is due to the fact that upon the agreement process is driven by the faulty memory of the place of the plural morpheme and uneducated guessing.
+Since the parsing is shallow, comprehenders do not engage in perfect attribution of the features, thus having a somewhat blurry representation behind.
+We expect for this behaviour to be omnipresent in other agreement attraction phenomenon that has been showed, as well as in @Lago2018 and in our replication of it.
+Therefore, there is no reason to have to anything to be different in experiment 2.
+
+## Experiment 1
 
@@
 
-In their study, @Lago investigates the comprehension of subject-verb agreement  Turkish monolinguals.
+In their study, @Lago2018 investigates the comprehension of subject-verb agreement  Turkish monolinguals.
 They use speeded acceptability judgments for the effects of number attraction in Turkish.
@@
 They found a significant effect of number attraction in Turkish ranging between 11\%--15\% across monolinguals.
-As seen in the results of the statistical analysis in \textsc{Table} (\ref{lagomodel}), the acceptability judgments showed an immense effect of grammaticality, and there is also interaction between grammaticality and attractor number, which indicates the presence of a number attraction effect.
-
-\begin{table}[!hbt]
-\centering
-\begin{tabular}{llcccc}
-\hline
-    &                                        & \multicolumn{4}{l}{Monolingual Speakers}                                               \\ \cline{3-6} 
-    &                                        & $\beta$        & SE            & \emph{z} & \emph{p} \\ \hline
-\multicolumn{2}{l}{\textbf{Attraction Task}} &                &               &                           &                           \\
-    & Grammaticality                         & \textbf{-5.51} & \textbf{0.33} & \textbf{-16.69}           & \textbf{.000}             \\
-    & Attractor Number                       & 0.14           & 0.25          & 0.57                      & .571                      \\
-    & Grammaticality x Attractor Number      & \textbf{1.69}  & \textbf{0.53} & \textbf{3.19}             & \textbf{.001}             \\
-    & Attractor Number: Ungram conditions    & \textbf{0.94}  & \textbf{0.26} & \textbf{3.68}             & \textbf{.000}             \\
-    & Attractor Number: Gram conditions      & -0.79          & 0.52          & -1.51                     & .131                      \\ \hline
-\end{tabular}
-\caption{Model results for the judgments of monolingual cited from @Lago.}
-\label{lagomodel}
-\end{table}
-
-@Lago stipulate that the Turkish genitive case does not provide a strong cue against subjecthood since Turkish frequently makes use of genitive marked subjects in embedded clauses, as in example (\ref{gensubj}).
+@Lago2018 stipulate that the Turkish genitive case does not provide a strong cue against subjecthood since Turkish frequently makes use of genitive marked subjects in embedded clauses, as in \autoref{gensubj}.
 This is in contrast with English, in which the genitive case is compatible with subjecthood.
-Thus, @Lago argue that this robust agreement attraction effect has been linked to the case information carried by accusative and genitive.
+Thus, @Lago2018 argue that this robust agreement attraction effect has been linked to the case information carried by accusative and genitive.
 
@@
 However, our initial hypothesis postulates that participants engage in shallow processing, which results in a situation in which not only the genitive case but also the possessive case plays a significant role in delivering the case information.
-None of the experimental items in @Lago have a head noun which ends with a vowel; thus, all of the possessive markers are morphologically and phonologically ambiguous between the accusative case and the possessive.
-Unlike genitive case, it is extremely rare for the accusative case to appear on the head noun of the subject, which only occurs in raising predicates as in example (\ref{dsm}).
+None of the experimental items in @Lago2018 have a head noun which ends with a vowel; thus, all of the possessive markers are morphologically and phonologically ambiguous between the accusative case and the possessive.
+Unlike genitive case, it is extremely rare for the accusative case to appear on the head noun of the subject, which only occurs in raising predicates as in \autoref{dsm}.
 
@@
 
-In order to test this hypothesis, we have replicated the experiment of @Lago with modified items, in which the possessive is not ambiguous with the accusative case.
+In order to test this hypothesis, we have replicated the experiment of @Lago2018 with modified items, in which the possessive is not ambiguous with the accusative case.
 We tried to be as faithful as possible to the original sentences while also trying to make the sentences as plausable as possible.
-We keep the semantic relation between the head noun and the controller the same with what has been described in @Lago's study, which is either a relation regarding profession or a service that is given by the head noun for the possessor.
+We keep the semantic relation between the head noun and the controller the same with what has been described in @Lago2018, which is either a relation regarding profession or a service that is given by the head noun for the possessor.
 A set of sentences are exemplified below.
@@
 
-As seen in the examples, unlike @Lago's experimental items, all of our items bear the *-sI* possessive marker instead of the ambiguous *-I* marker.
+As seen in the examples, unlike @Lago2018's experimental items, all of our items bear the *-sI* possessive marker instead of the ambiguous *-I* marker.
 As for the filler items, we could not use or modify the original experiment items since the fillers of the original study were not online.
-We have used two types filler sentences: grammatical sentences in which the verb bears plural agreement (\ref{fillera}), and ungrammatical sentences in which the verb does not bear plural agreement (\ref{fillerb}).
+We have used two types filler sentences: grammatical sentences in which the verb bears plural agreement (\autoref{fillera}), and ungrammatical sentences in which the verb does not bear plural agreement (\autoref{fillerb}).
 We wanted to nullify a possible strategy by the participants where they associate the sentence-final morpheme directly with the acceptability of the sentence.
@@
 
-All of our data, experimental materials, our experiment design, and our fillers can be found on the website of the Center for Open Science Framework (https://osf.io/).
+### Participants and Procedure
 
-## Participants and Procedure
-
-One hundred and seven Turkish speakers with a mean age of X were recruited from Bogazici University in İstanbul.
+One hundred and seven Turkish speakers were recruited from Bogazici University in İstanbul.
 We did not collect participants' knowledge of other languages; however, we verified that Turkish is their native language and that they predominantly use it in their daily lives.
 In the experiments, participants were asked to judge the acceptability of experimental and filler sentences in Turkish.
-All of the sentences were presented one word at a time in the center of the screen for 500 ms per word unlike @Lago and @Wagers2009, in which the duration was 300 ms per word.
-The experiment was run on a web-based platform titled the Ibex Farm, and all of the documentation can be found on our osf and github page.
+All of the sentences were presented one word at a time in the center of the screen for 500 ms per word unlike @Lago2018 and @Wagers2009, in which the duration was 300 ms per word.
+The experiment was run on a web-based platform titled the Ibex Farm, and all of the documentation can be found on our github page.
 
@@
 At the start of the experiment, they were given 4 practice items with feedback.
+Each trial after the practice items started with a blank screen, followed by a flash of single words in the middle of the screen.
+After the sentence, they were asked a grammaticality judgment questins (Was the sentence you read was natural to you?) where they need to press P for *no* and press Q for *yes*.
+In the experiment, every participant saw 40 experimental item that is latin-squared and 40 fillers.
 
-What to write about analyze?
+### Analysis
 
-## Results and Discussion
+Every experimental item from both experiments (Experiment 1 and @Lago2018) is included in the analysis.
+Participants that could not exceed the threshold of 0.25 difference in *yes* answer between the condition (c) and (d), namely Ungrammatical, SG attractor and Grammatical, SG attractor, were excluded.
+We performed an analysis by fitting linear mixed-effect modelts to our data, controlling for vowel ending, plural attractor, grammaticality and their interactions.
+Models were fit using bernoulli distribution with probit link function and 95\% confidence intervals.
+
+### Results
 
@@
 ```
-
-In \textsc{Figure} (1), the y-axis shows the percentage of "acceptable" answers, and the x-axis indicates whether or not the sentences in that group are grammatical.
-Moreover, the linet ypes indicate an attractor noun with overt plural morphology.
-As seen in the figure, `r 1`% of the sentences with plural attractors and a singular verb were accepted by the participants, in line with the findings of @Lago.
-We also see a number attraction rate of `r 2`% which was also observed in @Lago with close results.
-
-In \textsc{Table} (\ref{tab:replication}), ............
 
@@
 
-## Responses
-
 ```{r exp1AvgResponse, fig.height = 2.5, fig.width = 6, fig.cap="Estimates and 95% credible intervals for the analysis of the probability of a 'yes' response."}
@@
 
-```{r exp1ModelResponse, eval = F}
+In Figure \@ref(fig:exp1AvgResponse), the y-axis shows the percentage of "acceptable" answers, and the x-axis indicates whether or not the sentences in that group are grammatical.
+As seen in the figure, `r round(as.numeric(avg_exp[3,6]), digits = 2)`% of the sentences with plural attractors and a singular verb were accepted by the participants, in line with the findings of @Lago2018.
+We also see a number attraction rate of `r round(as.numeric(avg_exp[3,6]), digits = 2)-round(as.numeric(avg_exp[4,6]), digits = 2)`% which was also observed in @Lago2018 with close results.
+
+In Figure \@ref(fig:exp1ResponseModelPlot), we clearly see the effects of ungrammaticality and the interaction between the ungrammaticality and plural attractor.
+We see that, vowel ending is not significant even though it has negative effect.
+Thus, we may say that differentiating between the accusative case and the possessive suffix has cause a reduction in the effect of the agreement attraction.
+The results also shows that when the attractor is plural, people have a high tendency to find the sentence grammatical.
+
+```{r exp1ModelResponse, include=FALSE}
 
@@
 
-n_chains <- 4
-n_cores <- 4
+n_chains <- 6
+n_cores <- 6
 n_iter <- 5000
@@
 
-```{r exp1ResponseModelPlot, eval = F, fig.height= 1.5, message=FALSE, warning=FALSE, fig.cap="Estimates and 95% credible intervals for the analysis of the probability of a 'yes' response."}
+```{r exp1ResponseModelPlot, fig.height = 2.5, fig.width = 6, fig.cap="log-odd Estimates and 95% credible intervals for the regression coefficients."}
 
 contrast_names <- c("cUngrammatical" = "Ungrammaticality",
-                    "cAttractorMatch" = "Attactor Match",
-                    "cUngrammatical:cAttractorMatch" = "Ungrammaticality * Attractor Match")
+                    "cAttractorPlural" = "Plural Attactor",
+                    "cUngrammatical:cAttractorPlural" = "Ungrammaticality * Plural Attractor",
+                    "cEndsInVowel" = "Vowel Ending",
+                    "cEndsInVowel:cUngrammatical" = "Ungrammaticality * Vowel Ending",
+                    "cEndsInVowel:cAttractorPlural" = "Vowel Ending * Plural Attractor",
+                    "cEndsInVowel:cUngrammatical:cAttractorPlural" = "Vowel Ending * Ungrammaticality * Plural Attractor")
 
@@
 
-## Response Times
+In Figure \@ref(fig:exp1AvgRTs), we see that average response times are significantly higher than the those of @Lago2018.
+Again, these results shows the effect of disambiguation of the possessive suffix from the accusative case has surfaced as the difficuilty in response and memory retrieval time.
 
-```{r exp1AvgRTs, fig.height=2.5, fig.width = 6 }
+```{r exp1AvgRTs, fig.height=2.5, fig.width = 6, fig.cap="Average response times for our replication and Lago et. al. (2018)"}
 
@@
 
-\clearpage
+### Discussion
 
-# EXPERIMENT 2: RC ATTRACTOR
+The results follow from what a cue-based model would predict: slightly lower agreement attraction.
+However, these results can also be a result of a badly formed filler sentences which are shown with purple line.
+Participants may be biased towards saying no since most of the experimental items being ungramatical.
+However, this can also be statistical *miss* since we may accidentally have a group such as this one.
+However, the visible effect of vowel ending and response time suggest that people do indeed care more than only the retrieval of plural morpheme *-lar* and its place.
+This results go against what we have predicted for the Marking and Morphing model and our shallow processing model.
+However, the existence of extremely close degree of agremeent attraction effects and non-significant nature of the effect of the vowel ending indicate that we cannot readily discard other explanations.
 
-Even though our first hypothesis regarding shallow processing did not hold, we still need to entertain the second possibility we have discussed in this paper.
-Participants may indeed engage in an even shallower process of sentence comprehension, in which they merely match the use of *-lAr*.
-Moreover, we still need to discuss how much it is an effect of case information rather than only a number attraction.
-We have seen that the anti-subjecthood cues of the accusative are not significant since in both cases where the possessive is ambiguous with the accusative and the possessive is clearly marked, we have observed extremely close results in the speeded acceptability judgments.
+## Experiment 2
 
-In order to check both the sole effect of number agreement and the possibility of a task effect, we propose an experiment design in which a head noun is a bare NP, is not marked with any other morpheme and preceded by a relative clause construction.
-This relative clause consists of only a verbal component, which bears an overt plural marker.
-Since Turkish verbal and nominal plural morphemes are identical, we plan to check the participants' strategy with regards to whether or not it is a cue that helps in the reconstruction of the ungrammatical sentence or whether it is merely a task effect in which participants disregard the rest of the sentence and focus the existence of the morpheme *-lAr*.
+```{r loadDataExp2, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
 
-## Materials
+fname_data2 <- "../workspace_exp2/exp_data.rds"
+data2 <- readRDS(file = fname_data2)
 
-Like genitive-possessive structures, attractors do not intervene between the grammatical agreement controller and the verb in relative clause constructions.
-Turkish relative clauses always precede the head noun, except for in special cases in which they are marked with unique prosody.
-Item (\ref{rcexample}) is an example of a RC structure, and item (\ref{rcexample2}) shows the possibility of using only the verbal component of the relative clause since it is grammatical to drop arguments in Turkish.
-( add a footnote here giving the details of such events, and restrictions.
-)
+# compute by-subject percentages of 'yes' responses, and average RTs 
+avg_by_subj2 <- data2 %>%
+                group_by(subject, experiment, condition, 
+                         grammatical, verb_num, attractor_num) %>%
+                summarize(avRT = mean(RT), 
+                          p_yes = mean(ResponseYes, na.rm = T), 
+                          N = sum(!is.na(ResponseYes))  )
+
+# reformat by-subject averages to a wide format
+avg_by_subj_wide2 <- avg_by_subj2 %>% 
+                      mutate(expcond = paste(experiment, condition, sep="_")) %>% 
+                      ungroup() %>%
+                      dplyr::select(-experiment, -condition, -avRT, -N,
+                                    -grammatical, -verb_num, -attractor_num) %>%
+                      tidyr::spread(expcond, p_yes) %>% 
+                      mutate(delta_dc = AgrAttr_d - AgrAttr_c)
+
+```
+
+```{r identifyBadSubjects2, eval =T, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+
+# identify participants 
+bad_subjects2 <- subset(avg_by_subj_wide2, delta_dc <= 0.25 ) %>% .$subject
+
+#dataAvBySubj %>% subset(subject %in% bad_subjects) %>% ggplot(aes(grammatical, p_yes, group = paste(experiment,attracted), color = experiment )) + geom_point() + geom_line(aes(linetype =attracted)) + facet_wrap(~subject)
+
+data_clean2 <- data2 %>% subset(!subject %in% bad_subjects)
+
+```
+
+```{r mergeData2, eval =T, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+
+df_merge_exp2 <- data_clean2 %>% ungroup() %>% 
+                      dplyr::select(source=experiment, grammatical, attractor_num, # condition,
+                                    subject, item=Item,
+                                    ResponseYes, RT)
+df_merge_exp2$experiment <- "Experiment 2"
+df_merge_exp2$grammatical <- with(df_merge_exp2, ifelse(grammatical == "gram", 
+                                                        "grammatical",
+                                                        "ungrammatical"))
+df_merge_exp2$attractor_num <- with(df_merge_exp2, ifelse(attractor_num == "pl", 
+                                                          "plural", 
+                                                          "singular"))
+df_merge_exp2$item %<>% as.integer()
+df_merge_exp2$subject %<>% as.character()
+
+df_merged2 <- dplyr::bind_rows(df_merge_exp1, df_merge_exp2)
+df_merged2$subject %<>% as.factor()
+df_merged2$item %<>% as.factor()
+```
+
+```{r computeAverages2, eval =T, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+
+avg_clean2 <- df_merged2 %>%
+                group_by(experiment, source, grammatical, attractor_num) %>%
+                summarize(avgRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T))
+```
+
+Having discussed the replication study of @Lago2018, we have shown that results favor the cue-based models, especially with the effect of disambiguated possessive suffix on response times.
+However, due to the extremely similar effects on agreement attraction we can still entartain shallow processing mechanism as explained in \autoref{model1}, \autoref{model2}, and \autoref{model3}.
+Since we argue that the agreement attraction is a product of memory state in which comprehenders do not have an exact memory of the place of the plural morpheme mainly, we conducted an experiment where the distractor with the plural morpheme in on the relative clause.
+
+The study consists of an speeded acceptability judgment experiment in the web-based platform Ibex Farm.
+In the experiment, we test whether or not speakers utilize even more shallow parser than what is stipulated by @Lago2018 and our replication of @Lago2018 Experiment 2.
+This was investigated using syntactic structures similar to @Lago2018 materials, in which we have opted out the Genitive Constructuion (GC) for Relative Clause construction (RCC) as a distractor.
+In Turkish, like GC, relative clause in RCC precedes the head noun, and length-wise Turkish relative clauses can consist of only one word and the rest can be dropped.
+Turkish allows us to use RCCs as distractors in the same place because Turkish plural morpheme in verbal domain and nominal domain are the same: *-lAr*.
+Both of them react similarly in the same phonological environments, and they also exhibit same stress patterns.
+
+In the experimental items, the distractor RC and the matrix verb had four configurations in which the number morpheme on the RCC (*plural* vs.
+*singular* marked RC verb) and matrix verb (*grammatical* vs.
+*ungrammatical*) as in \autoref{prereg1}.
 
 \begin{exe}
-\ex
-  \begin{xlist}
-    \ex \label{rcexample}
-    \gll On-lar-{\i}n ev-e gel-me-den g\"{o}r-d\"{u}k-ler-i \c{c}ocuk so\u{g}uk-ta \"{u}\c{s}\"{u}-m\"{u}\c{s}-t\"{u}.\\
-    they-\textsc{pl}-\textsc{gen} home-\textsc{dat} come-\textsc{neg}-\textsc{abl} see-\textsc{nlmz}-\textsc{pl}-\textsc{poss} kid cold--\textsc{loc} feel.chilly-\textsc{perf}-\textsc{pst}\\
-    \glt The kid that they saw right before coming to home was feeling chilly. 
-    \ex \label{rcexample2}
-    \gll G\"{o}r-d\"{u}k-ler-i \c{c}ocuk so\u{g}uk-ta \"{u}\c{s}\"{u}-m\"{u}\c{s}-t\"{u}.\\
-    see-\textsc{nlmz}-\textsc{pl}-\textsc{poss} kid cold--\textsc{loc} feel.chilly-\textsc{perf}-\textsc{pst}\\
-    \glt The kid that they saw home was feeling chilly.
-  \end{xlist}
-\end{exe}
-
-As for the experimental sentences, we plan to use sentences that are similar to the ones used in @Lago.
-Instead of a genitive controller, we utilize an RC, which we manipulate for its values for bearing the plural morpheme.
-The head noun of the subject is always singular, and it is followed by a 2/3 word adverbial.
-Moreover, the matrix verb of the sentences is also manipulated in terms of plurality, deeming the sentence grammatical or ungrammatical.
-Lastly, the relative clause has to be an object relative clause, since Turkish subject relative clauses never bear a plural morpheme on the embedded verb.
-As in the @Lago's study and our replication, we will have a four condition, where we manipulate the plurality of the attractor (*plural/singular*) and the grammaticality of the sentece by using overt plural morphology (*grammatical/ungrammatical*), which are demonstrated with item (\ref{reg1}), (\ref{reg2}), (\ref{reg3}), and (\ref{reg4})
-
-\begin{exe}
-\ex
+\ex \label{prereg1}
   \begin{xlist}
   \ex \underline{Grammatical, SG attractor} \label{reg1}
-      \gll D\"{o}v-d\"{u}\u{g}-\"{u} \c{c}ocuk mutfak-ta bayg{\i}n hal-de yat-{\i}yor-du.\\
-  beat-\textsc{nmlz}-\textsc{poss} kid kitchen-\textsc{loc} unconscious state-\textsc{loc} lie-\textsc{prog}-\textsc{pst}\\ 
+      \gll D\"{o}v-d\"{u}\u{g}-\"{u} \c{c}ocuk okul-a yorgun arg?n gel-di.\\
+  beat-\textsc{nmlz}-\textsc{poss} kid school-\textsc{dat} unconscious state-\textsc{loc} lie-\textsc{prog}-\textsc{pst}\\ 
       \glt The kid that he/she beats was laying in the kitchen unconscious.
@@
 
-As for the fillers, we need two different set of fillers in order to counterbalance the ever-present grammaticality of singular and plural verbs.
-For grammatical fillers with a plural verb (example (\ref{fillerreg1})) we propose a structure in which the head noun is followed by a converb.
-With this modification, the controller of the experimental sentences becomes a controller for a subclause, and the main verb is saturated with another subject introduced right after the subclause.
-
-For ungrammatical fillers with a singular verb (example (\ref{fillerreg2})), we have used strictly transitive verbs without an overt object.
-By utilizing the same structure with the other type of fillers, we ensure that participants will not come up with a strategy in which they always check the second word for dependency resolution.
-The controller of the fillers and the controller of the experimental items differ in the linear order they are shown in the experiment.
-
-Question: Can we do subject relative clause here? Like durdurulan ogrenci.
+As for the experiment, we have used same type of fillers with the Experiment 1 in order to tackle with two possible strategies that can be utilized by the participants: (i) deeming the sentence acceptable when the matrix verb is singular and (ii) deeming most of the sentences unacceptable when the matrix verb is plural.
+To tackle with the first type of strategy, we have used a sentence where the object is not marked with accusative and it is not in immediately pre-verbal position as in \autoref{filler1a}.
+The idea was to have a singular matrix verb in an ungrammtical sentence where the ungrammaticality does not stem from the local elements.
+As for the other strategy we have used pro-drop charactheristics of Turkish and made the first noun phrase with a relative clause an object as in \autoref{filler1b}.
+The idea behind is that the plural agreement on the matrix verb is resolved with a dropped subject instead of the first noun phrase with a relative clause.
+Every participant saw 40 experimental item that is latin-squared and 40 fillers.
 
@@
 \begin{xlist}
-\ex \label{fillerreg1}
-\gll Dur-dur-duk-lar-{\i} \"{o}\u{g}renci \c{s}a\c{s}{\i}r-{\i}nca arkada\c{s}-lar-{\i} birden g\"{u}l-d\"{u}-ler.\\
-stop-\textsc{caus}-\textsc{nmlz}-\textsc{pl}-\textsc{poss} student surprise-\textsc{cvb} friend-\textsc{pl}-\textsc{poss} suddenly laugh--\textsc{pst}-\textsc{pl}\\
-\glt When the student which was stopped surprised, his friends burst out laughing.
-\ex \label{fillerreg2}
-\gll *Tut-tuk-lar-{\i} a\c{s}\c{c}{\i} gel-me-yince dan{\i}\c{s}man-lar hala ver-di.\\
-hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss} cook come--\textsc{neg}-\textsc{cvb} advisor-\textsc{pl} still give-\textsc{pst}\\
-\glt Inteded: When the cook that they hired did not come, advisors did not still give. 
+\ex \label{filler1a}
+\gll * Haberleş-tiğ-i çevirmen ara-ma-yınca metin keyfince bitir-di.\\
+{\ } communicate-\textsc{Nmlz}-\textsc{Poss} translator call-\textsc{Neg}-\textsc{Nmlz} text as.he.wished finis-\textsc{Pst}\\
+\glt Intended: ``When the translator that he spoke with did not call, he finished the text as he wished.''
+\ex \label{filler1b}
+\gll Sev-dik-ler-i öğretmen emekli ol-unca saatlerce ağla-dı-lar.\\
+love-\textsc{Nmlz}-\textsc{Pl}-\textsc{Poss} teacher retired be-\textsc{Nmlz} for.hours cry-\textsc{Pst}-\textsc{Pl}\\
+\glt ``When the teacher they loved retired, they cried for hours.''
 \end{xlist}
@@
 
-## Participants and Procedure
+### Participants and Procedure
 
-We plan to have participants from the undergrad students of Bogazici University, which will be given an extra credit incentive.
-They will again carry out the experiment on an online experiment platform Ibex Farm.
-The experiment process will be exactly the same with the replication of @Lago, including descriptions before the experiment, the layout of the experiment, the time spared for visualization of every word, exclusion criteria, and analysis.
+Eighty Turkish speakers were recruited from Bogazici University in İstanbul.
+The procedure was exatcly the same as the Experiment 1.
+The participants in this experiment were completely different than the Experiment one.
 
-## Expectations
+### Analysis
 
-(This part is extremely tentative)
+Every experimental item from both experiments (this experiment and the Experiment 1) is included in the analysis.
+Participants that could not exceed the threshold of 0.25 difference in *yes* answer between the condition (c) and (d), namely Ungrammatical, SG attractor and Grammatical, SG attractor, were excluded.
+We performed an analysis by fitting linear mixed-effect modelts to our data, controlling for vowel ending, plural attractor, grammaticality and their interactions.
+Models were fit using bernoulli ditribution with probit link function and 95\% confidence intervals.
 
-Our objective is to explore the number attraction phenomenon without the effects of case information and without the limits of nominal paradigm.
-By doing so, we expect participants to engage with the sentences which are ungrammatical in an extremely shallow fashion.
-We argue that instead of reconstructing the sentence utilizing every detail from the attractor and the controller, participants disregard the information from other sources in the sentence and look for a matching morpheme, i.e.
-*-lAr*.
+### Results
 
-In the case that there will be a similar attraction effects with the replication of @Lago and @Lago study, we think that...
-what do we think?
-I need to talk about the paper and idea more thoroughly, I guess.
-Because I feel like I am repeating myself.
+```{r exp2AvgResponse, fig.height = 2.5, fig.width = 6, fig.cap="Estimates and 95% credible intervals for the analysis of the probability of a 'yes' response."}
 
-# DISCUSSION
+avg_exp2 <- avg_clean2 %>% subset(is.na(source) | source != "filler")
+avg_fillers2 <- avg_clean2 %>% subset(source == "filler")
 
-Discuss.
+p_avg_resp2 <- ggplot(avg_exp2, 
+                     aes(grammatical, p_yes, #linetype = attractor_num, 
+                         color = attractor_num, group = attractor_num)) + 
+                geom_point() + geom_line() + 
+                facet_wrap(~experiment)
 
-# CONCLUSIONS
+p_avg_resp2 <- p_avg_resp2 + geom_line(data = avg_fillers) + geom_point(data = avg_fillers2)
 
-In this paper, we have entertained the idea of task effect in the so-called Turkish number attraction phenomenon.
-We argue that the findings of the @Lago study is not clear and there are too many variables to account for in the experiment, one of them being the ambiguous morphology that the head noun bears.
-In the first experiment, we have replicated the attraction task of @Lago.
-We have found the similar effects of agreement with a bigger pool of participants.
-Then, for entertaining the other possibility in which we argue that participants do not fully reconstruct the sentence; however, they make us of the direct cue of overt morpheme *-lAr*, we offer an experiment where we use object relative clauses as an attractor.
--
+print(p_avg_resp2)
 
-# ACKNOWLEDGEMENTS
-We used the statistical language `R` `r citep(citation())` for all our analyses.
-These were implemented in dynamic rmarkdown documents using `knitr` `r citep(citation("knitr")[1])` and `rmarkdown` `r citep(citation("rmarkdown")[2])` packages.
-All graphs have been done with `ggplot` `r citep(citation("ggplot2"))`.
+```
 
-# REFERENCES
+It is clear from Figure \@ref(fig:exp2AvgResponse) that in the condition (c) where we expect an agreement attraction, participants find as unacceptable as the condition (d) with singular attractor, singular head noun, and plural matrix verb.
+While we do not see any agreement attraction (`r round(as.numeric(avg_exp2[7,6]), digits = 2)`%), we also see a more firm analysis of the ungrammatical sentence with singular matrix verb ((`r round(as.numeric(avg_exp2[7,6]), digits = 3)`%)).
 
-```{r write_citations, eval =T, cache=FALSE, include=FALSE}
-write.bibtex(file="references.bib")
+```{r exp2ModelResponse, include=FALSE}
+
+# # TODO: the following subjects have too much data: 11, 28, 36, 42, 55, 65, 73, 84, 92, 
+# #
+# x <- df_merged %>% subset(experiment == "Experiment 1") %>% group_by(subject) %>% dplyr::summarize(F = sum(is.na(attractor_num)),
+#                                                           N = length(is.na(attractor_num)) )
+# x %>% as.data.frame()
+# 
+# x$N %>% sum()
+# x$F %>% sum()
+
+#summary(as.factor(df_merged$attractor_num))
+
+df_merged2 %<>% within(., {
+  cGrammatical <- ifelse(grammatical == "grammatical", .5, -.5)
+  cUngrammatical <- ifelse(grammatical == "ungrammatical", .5, -.5)
+  cAttractorPlural <- ifelse(attractor_num == "plural", .5, -.5)
+  cVerbalPlural <- ifelse(experiment == "Experiment 2", .5, -.5)
+})
+df_merged_nofillers2 <- df_merged2 %>% subset(is.na(source) | source != "filler")
+
+# ## test model parameterization using a simple GLM first
+# m <- glm(ResponseYes ~ cEndsInVowel * cUngrammatical * cAttractorPlural,
+#          data = df_merged_nofillers,
+#          family = binomial("probit"))
+# summary(m)
+
+n_chains <- 6
+n_cores <- 6
+n_iter <- 5000
+
+fname_exp2_responses <- "../workspace_exp2/model_responses"
+
+library(brms)
+
+m_responses2 <- brm(ResponseYes ~ cVerbalPlural * cUngrammatical * cAttractorPlural + 
+                                 (cUngrammatical * cAttractorPlural + 1| subject) +
+                                 (cUngrammatical * cAttractorPlural + 1| item),
+                   data = df_merged_nofillers2,
+                   family = bernoulli("probit"),
+                   file = fname_exp2_responses, 
+                   chains = n_chains, cores = n_cores, iter = n_iter)
+
 ```
+
+As for the estimates of coefficients in \@ref(fig:exp2ResponseModelPlot), we can conclude that there is a significant negative effect of plural morpheme on the relative clause, which means that it does not cause any agreement affects.
+Again, the effect of ungrammaticality that stems from the existence of plural morpeheme on the matrix verb is visible.
+The interaction between the plural morpheme on the attractor RC and the matrix verb is even higher than the sole effect of plural morpheme on the attractor RC.
+
+```{r exp2ResponseModelPlot, fig.height = 2.5, fig.width = 6, fig.cap="log-odd Estimates and 95% credible intervals for the regression coefficients."}
+
+contrast_names2 <- c("cUngrammatical" = "Ungrammaticality",
+                    "cAttractorPlural" = "Plural Attactor",
+                    "cUngrammatical:cAttractorPlural" = "Ungrammaticality * Plural Attractor",
+                    "cVerbalPlural" = "Verbal Plural",
+                    "cVerbalPlural:cUngrammatical" = "Ungrammaticality * Verbal Plural",
+                    "cVerbalPlural:cAttractorPlural" = "Verbal Plural * Plural Attractor",
+                    "cVerbalPlural:cUngrammatical:cAttractorPlural" = "Verbal Plural * Ungrammaticality * Plural Attractor")
+
+p_m_response2 <- create_model_coefs_plot(m_responses2, map_names = contrast_names2)
+p_m_response2 <- p_m_response2 + xlab("Estimate (log-odds)")
+print(p_m_response2)
+
+```
+
+```{r exp2AvgRTs, fig.height=2.5, fig.width = 6 ,fig.cap="Average response times for our replication and Experiment2"}
+
+p_avg_rt2 <- ggplot(avg_clean2, aes(grammatical, avgRT, linetype = attractor_num, color = experiment, group = paste(experiment, attractor_num))) + geom_point() + geom_line()
+
+print(p_avg_rt2)
+
+```
+
+Finally, the response times of the Experiment 2 is significantly lower than the Experiment 1 as seen from Figure \@ref(fig:exp2AvgRTs).
+The even lower response time in ungrammatical plural (condition c) shows that participants were extremely confident with their decision and did not had any issue with the dependency resolution.
+
+### Discussion
+
+These findings indicate that our hypothesis regarding the matching of the forms is not supported by the empirical evidence.
+However, results in Experiment 2 points in a direction where the Marking and Morphing studies predicted in the first place.
+Due to the deeper syntactic embedding, the numeral feature cannot percolate as freely as it can in genitive possessive structure and cannot affect the final number of the subject root node.
+
+However, with the right prediction with regards to which features are stored and can be cued for, cue-based retrieval mechanisms can also explain the findings in Experiment 2.
+
+# Conclusion
+
+We have shown that the agreement attraction effects cannot be explained by the extremely shallow processing mechanisms, at least with the implementaion we have proposed here.
+However, we also shown that findings from Experiment 1 and 2 was not enought the differentiate between two models that can explain agreement attraction: the Marking and Morphing and cue-based retrieval models.
+While the findings of Experiment 1 favors the cue-based retrieval mechanism, Experiment 2 with the harsh decline in the effects of agreement attraction points to another horizon.
+
+Another take on the results may follow from the redefinition of the *shallowness* concept.
+Experiments show that it is not only dependent on the form.
+However, it can be an issue related to already-formed dependencies inability to be used in the memory process.
+One can argue that once the dependencies are formed and resolved, participants does not go back to them when another cue is set out.
+
+# References
+```{r create_r-references}
+r_refs(file = "r-references.bib")
+```
+
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+
+<div id = "refs"></div>
+\endgroup

### 2019-06-10 Paper/AgreementAttraction.tex
almost a mediocre paper

@@
 \hypersetup{unicode=true,
-            pdftitle={Agreement Attraction in Turkish: Effects of Nominal and Verbal Plural Morphemes},
-            pdfauthor={Utku Türk~\& Pavel Logačev},
-            pdfkeywords={keywords},
+            pdftitle={Agreement Attraction},
+            pdfauthor={Utku Türk~\& Pavel Logacev},
             pdfborder={0 0 0},
@@
 \urlstyle{same}  % don't use monospace font for urls
+\usepackage{biblatex}
+\ExecuteBibliographyOptions{maxbibnames=999}
+\addbibresource{myreferences.bib}
+\addbibresource{r-references.bib}
 \usepackage{graphicx,grffile}
@@
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{0}
+\setcounter{secnumdepth}{5}
 % Redefines (sub)paragraphs to behave more like sections
@@
 
-  \title{Agreement Attraction in Turkish: Effects of Nominal and Verbal Plural
-Morphemes}
-    \author{Utku Türk\textsuperscript{1}~\& Pavel Logačev\textsuperscript{1}}
+  \title{Agreement Attraction}
+    \author{Utku Türk\textsuperscript{1}~\& Pavel Logacev\textsuperscript{1}}
     \date{}
 
+\shorttitle{Agreement Attraction in Turkish}
+\affiliation{
+\vspace{0.5cm}
+\textsuperscript{1} Boğaziçi University}
+\usepackage{csquotes}
+\usepackage{upgreek}
+\captionsetup{font=singlespacing,justification=justified}
+
+\usepackage{longtable}
+\usepackage{lscape}
+\usepackage{multirow}
+\usepackage{tabularx}
+\usepackage[flushleft]{threeparttable}
+\usepackage{threeparttablex}
+
+\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
+
+\makeatletter
+\newcommand\LastLTentrywidth{1em}
+\newlength\longtablewidth
+\setlength{\longtablewidth}{1in}
+\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
 \usepackage[utf8]{inputenc}
 \usepackage[T1]{fontenc}
-
 \usepackage{xcolor}
@@
 \usepackage{mathtools}
-\usepackage{gb4e}\noautomath
+\linespread{1}
+\usepackage{gb4e}
+\noautomath
+\usepackage{setspace}
+\makeatletter
+\apptocmd{\@exe}{\singlespacing}{}{}
+\makeatother
+\usepackage{sectsty}
+\allsectionsfont{\large}
+\usepackage{color}
+\usepackage{hyperref}
+\hypersetup{colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue}
+\usepackage[english]{babel}
+\addto\extrasenglish{\renewcommand{\itemautorefname}{Item}}
+\renewcommand*{\nameyeardelim}{\addcomma\space}
+\usepackage{tikz}
+\usepackage{tikz-qtree}
+\let\eachwordone=\textit
 
-\authornote{Add complete departmental affiliations for each
-author here. Each new line herein must be indented, like this line.
-Enter author note here.
+\authornote{
 
-Correspondence concerning this article should be addressed to Utku Türk,
-Postal address. E-mail:
-\href{mailto:utku.turk@boun.edu.tr}{\nolinkurl{utku.turk@boun.edu.tr}}}
+Correspondence concerning this article should be addressed to Utku Türk, . E-mail: \href{mailto:utku.turk@boun.edu.tr}{\nolinkurl{utku.turk@boun.edu.tr}}}
 
 \abstract{
-This paper deals with agreement attraction because it's more important
-than literally anything else. Recently, Lago et al. (2018) demonstrated
-agreement attraction effects in comprension in Turkish, which is
-super-interesting because this finding allows us to make a lot of money.
-However, there is an alternative explanation for their findings: dark
-sorcery. In this paper we tested the predictions of these alternative
-accounts. In Experiment 1, we found that a particular kind of dark
-sorcery was not involved. In Experiment 2, we shall find \ldots{}
+The comprehension of agreement within the elements of a sentence is known to fail.
+One of these comprehension errors is known as agreement attraction.
+Speakers may erroneously find a sentence in which the ``attractor'' agrees with the verb instead of the ``head'' of the subject.
+Data from typologically different languages and explanations from different frameworks shows that we are far from understanding by what the attraction is modulated.
+Some theories refer this phenomenon as a faulty representation of the number on the head of the subject phase whereas other theories argues that the attraction is due to an error in the access to the number of the subject.
+In this paper, we report two experiments exploring a possible explanation for agreement attraction: an extremely shallow processing.
+The first experiment is a replication of \textcite{Lago2018} where we changed the head of the subject in order to differentiate between the accusative case \emph{-I}.
+In the second experiment, we have used a relative clause which only consists of a plural marked verb as a distractor.
+Our results show that while people do indeed care more than just ``matching'' the forms of plural verbal.
+Either comprehenders have some sort of restriction to not use cues from verbs upon accessing the number of the plural morpheme or there is a syntactic reason for the number feature of plural morpheme to not ``percolate.''
 
@@
 
-\section{INTRODUCTION}\label{introduction}
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
-Attraction errors in the production and comprehension of subject-verb
-agreement, in which a verb does not agree with the grammatical agreement
-controller, but with a potential attractor, have been the main topic of
-research in many studies for quite a long time. In fact, it is still a
-widely researched area in psycholinguistic studies. Despite the
-comprehensive research that has been carried out, studies that have been
-conducted on agreement attraction in Turkish have been very limited. In
-fact, Lago (2018) is currently the only study that explores this
-phenomenon in Turkish. Lago (2018) makes use of genitive-possessive
-structures in the subject position, in which the possessive-marked noun
-is the head of the noun phrase which acts as the grammatical agreement
-controller, and the genitive noun serves as a potential attractor. In a
-speeded acceptability judgment study, Lago (2018) found a significant
-effect of number agreement attraction. However, the interpretation of
-their findings may be a result of the fact that non-subjecthood cues
-originate from their use of morphologically ambiguous forms of the
-possessive. In the possessive forms that are used, all the head nouns in
-their stimuli are ambigiuous between possessive and accusative.
+\hypertarget{literature}{%
+\section{Literature}\label{literature}}
 
-In Turkish, accusative number agreement controllers are extremely rare,
-while genitive agreement controllers are very frequent. Thus, Lago
-(2018)'s finding could potentially be explained with occasional shallow
-processing. When all syntactic relations in the sentence were processed
-fully, the possessive noun may have been identified as the controller.
-Meanwhile, the genitive noun may sometimes have been erroneously
-identified as the controller during shallow processing because genitives
-are more likely to act as agreement controllers than accusatives
-(SOURCE). A second alternative explanation for Lago (2018)'s findings
-may be the fact that participants may engage in even more shallow
-processing than outlined above. Participants may have erroneously
-responded \emph{Yes} on some trials for two main reasons: (i) the
-presence of a plural morpheme on a noun (attractor or controller), and
-(ii) the presence of a plural agreement morpheme on the verb. We
-speculate that in such trials, participants would have simply tried to
-check for the presence of such morphemes, while largely disregarding the
-remainder of the sentence.
+\hypertarget{theories-of-attraction}{%
+\subsection{Theories of attraction}\label{theories-of-attraction}}
 
-We first replicated Lago (2018)'s experiment with unambiguous head
-nouns. To this end, we revised the items that were used previously in
-order to avoid morphological ambiguity between possessive and accusative
-forms. The effect found in Lago (2018) was also observed when
-unambiguous nouns were used, as will be discussed in \S 2.
+Agreement attractions are defined as instances of incorrect agreements of an element with a distractor that is not its grammatical controller.
+As in \autoref{E1}, the target of the agreement is the verb \emph{are}, the attracting distractor is \emph{bottles}, and the feature erroneously assesed is the number feature of the grammatical controller \emph{label}.
 
-\S 3 discusses the alternative account that posits even more shallow
-processing as mentioned above and presents a pre-registered experiment
-using RC attractors with potential outcomes and their indications. Since
-both nominal and verbal plural morphemes in Turkish are expressed with
-the same form (\emph{-ler} or \emph{-lar} depending on the phonological
-environment), we can test this possibility with an experiment in which a
-relative clause with or without plural agreement on the verb in place of
-the genitive possessors is used. An agreement attraction effect similar
-in magnitude to that observed in Lago (2018) would indicate that
-participants use the aforementioned strategies.
+\begin{exe}
+\ex[*]{The label on the bottles \textit{are} wrong.\footnotemark}
+\label{E1}
+\end{exe}
 
-\S 4 offers a discussion of the issue of number attraction and where
-this experiments leaves us. Lastly, \S 5 presents a brief conclusion and
-topics for future research.
+\footnotetext{The convention of using $\ast$ is to show the ungrammaticality of the sentencee.}
 
-\section{Experiment 1}\label{experiment-1}
+This type of attraction, called number attraction in subject-verb agreement, first theorized by \textcite{Quirk1972} and attested experimentally by \textcite{Bock1991} in language production.
+One of the theoretical attempts to explain such phenomenon was Marking and Morphing Theories \autocites{Bock2001}[ among others]{Eberhard2005}.
+The reason it is called \emph{Marking} and \emph{Morphing} is because there is two possible explanation within the framework with regards to where and when the attraction occurs.
+First possibility is speaker (and/or comprehender) can erroneously create a semantic representation of the head with wrong number feature in the marking process in the marking process.
+Another possibility is that the attraction may arise from an interfering number feature of the attractor with the number feature of the highest noun phrase node in morphing process.
+During the this process, the speaker forms a final number value of the subject phrase, which is determined by each morpheme within the same phrase and their number information with particular weight.
+In morphing process, these other morphemes with number information may contaminate the final number value with perculation mechanism, which depends on the depth of the syntactic embedding.
+As the prediction goes, the more embedded an attractor is, the less attraction they trigger as shown in \textcite{Bock1992} in which authors shown that attractors within a relative clause trigger less agreement attraction in the production.
 
-In their study, Lago (2018) investigates the comprehension of
-subject-verb agreement Turkish monolinguals. They use speeded
-acceptability judgments for the effects of number attraction in Turkish.
-Their sentences make us of genitive-possessive constructions in the
-subject position, where the genitive is the attractor and the possessive
-is the head noun. They manipulate the grammaticality of the sentence by
-changing the plural morphology of the verb, and they also manipulate the
-plurality of the attractor noun. In grammatical conditions, the subject
-and the verb both bear singular morphology with no overt morpheme.
-Moreover, in the ungrammatical conditions, the verb bears the overt
-\emph{-lAr} morpheme whereas the subject is still singular as
-exemplified below.
+However, other studies shown that other preverbal elements, such as objects, object relative clauses, object clefts, and object questions, may trigger agreement attraction \autocites{Kimball1971}{Hartsuiker2001}{Franck2006}[ among others]{Franck2015}.
+In sentences like \autoref{E2}, the pronominal object \emph{hen} triggers and agreement attraction without being a part of the subject.
+
+\begin{exe}
+\ex[*]{
+\gll Theo denkt dat de knecht hen roep.\\
+Theo thinks that the servant them call.\textsc{Pl}.\\
+\trans  `Theo thinks that the servant \textit{call} them'}
+\label{E2}
+\end{exe}
+
+Since the Marking and Morphing theories put the source of the agreement attraction on the probe, i.e.~subject phrase, they cannot explain agreement attraction effects that are triggered by an distractor outside of the syntactic scope of the subject.
+Regardless, these effects can be explained in a framework where the source of the agreement attraction can placed on the trigger, i.e.~verb.
+\textcite{Badecker2007} suggests that a process where the subject is retrieved from the memory plays a role in agreement attraction effects as well \autocite[see as well][]{Wagers2009}.
+Building on the work in cue-based retrieval mechanism \autocites{Gordon2001}{Lewis2005}[ among others]{Lewis2006}, they argued that when spakers reach the verb, they try to retrieve the subject using certain features (cues) that essentially marks the \emph{subjecthood}.
+Thus, any element that matches (or partially mathces) with the cues in use may cause agreement attraction regardless of their position or syntactic relation to the subject.
+Going back to \autoref{E2}, it is expected, then, for an object which shares features like being preverbal, being a noun phrase, ability to bear agreement with a subject to trigger agreement attraction.
+
+Another challenge for the Marking and Morphing model was the grammaticality asymmetry.
+Due to the spreading activation formula utilized in the Marking and Morphing model \autocite[see][]{Dell1986}, this model overgeneralizes the attraction effects to both ungrammatical and grammatical sentences and predicts both \autoref{E1} and \autoref{E3} to be present empirically, which is not the case \autocite{Wagers2009}.
+
+\begin{exe}
+\ex[*]{The labels on the bottle \textit{is} wrong.}
+\label{E3}
+\end{exe}
+
+On the other hand, cue-based retrieval models successfully predicts the the grammaticality asymmetry as shown by \textcite{Dillon2013} in an ACT-R simulation as well as numerous studies in self-paced reading, eye-tracking, and ERP studies \autocites{Wagers2009}{Tucker2010}{Tanner2014}[ among others]{Lago2015}.
+This success was due to their replacement of source of the attraction.
+According to cue-based retrieval models, the probe, verb, presents certain cues to retrieve an NP with matching features in agreement.
+When features of the grammatical controller of the verb does not \emph{fully} match with the cues, no single NP will be satisfying the \emph{agreement}.
+Thus, another NP in the clause can match with cues presented by the VP, such as its case, syntactic position, grammatical number.
+Thus, if there is no \emph{retrieval cue} in the first place, i.e.~the verb is nor marked plural, there will be no need for partial match.
+
+\hypertarget{turkish-relative-clauses-and-plural-marking}{%
+\subsection{Turkish relative clauses and plural marking}\label{turkish-relative-clauses-and-plural-marking}}
+
+Before discussing the experiments, we will touch upon the mechanisms that we utilize in the experiments: optional plural agreement, relative clause structure, and syncretism between possessive and accusative.
+
+Turkish plural agreement is quite similar with regards to the subject-verb number agreement in the first and second plural person.
+However, Turkish plural agreement is optional in third person plurals as shown in \autoref{TB1} and \autoref{TB2}.
+The other characteristics of Turkish plural agreement is that, the nominal and verbal plural marking is done by the same morpheme \emph{-lAr}\footnote{The convention of using an uppercase A is to show that the morpheme can surface as either \textit{-ler} or \textit{-lar} according to the previous vowel due to the vowel harmony reasons.}.
+
+\begin{exe}
+\ex \label{TB1} Dün çocuk-\textsc{Lar} okul-a git-ti-\textsc{Ler} mi?
+\ex 
+\gll Dün çocuk-LAR okul-a git-ti mi?\\
+yesterday child-\textsc{Pl} school-\textsc{Dat} go-\textsc{Pst}(-\textsc{Pl}) Q\\
+\trans ``Did the children go to school yesterday?''
+\label{TB2}
+\end{exe}
+
+As for Turkish relative clauses, they always precede the external head noun \autocites{Goksel2004}{Taylan2015} and they use either \emph{-An} or \emph{-dIk} nomilizers to show the referentiality of the subject within the relative clause as shown in \autoref{TB3} and \autoref{TB4} \autocite{Haig1997}.
+Moreover, due to pro-drop and null object properties of the Turkish \autocite[see][]{Ozturk2005}, relative clauses can consist of only the verb itself in Turkish as in \autoref{TB5}.
+
+\begin{exe}
+\ex \label{TB3}
+\gll Kazı-lar-ın yap-ıl-dığ-ı alan ... \\
+excavation-\textsc{Pl}-\textsc{Gen} do-\textsc{Pass}-\textsc{Nmlz}-\textsc{Poss} area ... \\
+\glt ``The place where the excavations are done ...''
+\ex \label{TB4}
+\gll Kazı-lar yap-ıl-an alan ... \\
+excavation-\textsc{Pl} do-\textsc{Pass}-\textsc{Nmlz} area ... \\
+\glt ``A place where some excavations are done ...''
+\ex \label{TB5}
+\gll Gör-düğ-ü kuş çok güzel-di.\\
+see-\textsc{Nmlz}-\textsc{Poss} bird very pretty-\textsc{Pst}\\
+\glt ``The bird that he/she saw was very pretty.''
+\end{exe}
+
+Final characteristics that interests us in this paper is the morphological syncretism between the accusative case and possessive suffix in Turkish.
+When the possessive case is attached to a nominal stem that ends with a consonant, it is pronounced as \textit{-I}, which is exactly how accusative case is also pronounced in the same environment in Turkish.
+However, the ambiguity is immediately resolved when they follow a nominal stem that ends with a vowel.
+In the latter environment, the accussative case surfaces as \emph{-yI} whereas the possessive surfaces as \emph{-sI(n)}\footnote{The final \textit{n} is only surfaces when any other morphemes follows the possessive suffix.
+Otherwise, it surfaces as \textit{-sI}} as shown in \autoref{TB6}-\autoref{TB9}.
+
+\begin{exe}
+\ex
+\begin{xlist}
+\ex \label{TB6}
+\gll Kuş-\textbf{u} beğen-di-m.\\
+bird-\textsc{Acc} like-\textsc{Pst}-\textsc{1Sg}\\
+\glt ``I liked the bird.''
+\ex \label{TB7}
+\gll Emin'in kuş-\textbf{u} güzel-miş.\\
+Emin-\textsc{Gen} bird-\textsc{Poss} pretty-\textsc{Evd}\\
+\glt ``Emin's bird was pretty.''
+\ex \label{TB8}
+\gll Kedi-\textbf{yi} beğen-di-m.\\
+cat-\textsc{Acc} like-\textsc{Pst}-\textsc{1Sg}\\
+\glt ``I liked the cat.''
+\ex \label{TB9}
+\gll Emin'in kedi-\textbf{si} güzel-miş.\\
+Emin-\textsc{Gen} cat-\textsc{Poss} pretty-\textsc{Evd}\\
+\glt ``Emin's cat was pretty.''
+\end{xlist}
+\end{exe}
+
+\hypertarget{the-current-study}{%
+\section{The Current Study}\label{the-current-study}}
+
+In this study, we examine the question of whether agreement attraction is due to the shallow parsing that mainly depends on the memory of plural morpheme \emph{-lAr} and matching the verbal plural morpheme with the nominal plural morpheme.
+
+First of all, we investigate the effects of ambiguous suffix with Experiment 1, which is a replication of \textcite{Lago2018}.
+\textcite{Lago2018} makes use of genitive-possessive structures in the subject position, in which the possessive-marked noun is the head of the noun phrase which acts as the grammatical agreement controller, and the genitive noun serves as a potential attractor as in \autoref{Lagoitem}.
+In a speeded acceptability judgment study, \textcite{Lago2018} found a significant effect of number agreement attraction.
+However, the interpretation of their findings may be a result of the fact that non-subjecthood cues originate from their use of morphologically ambiguous forms of the possessive.
+In the possessive forms that are used, all the head nouns in their stimuli are ambigiuous between possessive and accusative.
+
+\begin{exe}
+\ex \label{Lagoitem}
+\gll \c{S}ark{\i}c{\i}-n{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}-lar.\\
+singer-\textsc{Gen} vocalist-\textsc{Poss} stage-\textsc{Loc} non-stop jump-\textsc{Pst}-\textsc{3Pl}\\
+\glt The singer's backup vocalist jumped on the stage non-stop.
+\end{exe}
+
+In Turkish, accusative number agreement controllers are extremely rare, while genitive agreement controllers are very frequent.
+Thus, \textcite{Lago2018}'s finding could potentially be explained with occasional shallow processing.
+When all syntactic relations in the sentence were processed fully, the possessive noun may have been identified as the controller.
+Meanwhile, the genitive noun may sometimes have been erroneously identified as the controller during shallow processing because genitives are more likely to act as agreement controllers than accusatives.
+In order to check this effect, we have replicated \textcite{Lago2018} in Experiment 1.
+We have used different head nouns which ends with a vowel to differentiate between the accusative case and the possessive suffix, i.e.
+\emph{taksici} (taxi driver) instead of \emph{vokalist} in \autoref{Lagoitem}.
+
+With regards to percolation theories, this replication should yield no difference from \textcite{Lago2018}.
+The syntactic depth has not changed, the number information of the head and distractor have not changed.
+Slight differences may be expected since we have changed some items which can be found in Appendix 1, and this situation can create a erroneous number information to be used in the marking process.
+
+As for cue-based retrieval models, we should expect a lower agreement attraction effect in this replication.
+This predictions stems from the fact that possibility of erroneous representation of features of head noun is now lower due to our efforts to differentiate between the accusative case and the possessive marking.
+\textcite{Lago2018} argues that due to the subjecthood information provided by genitive case, there is an effect of agreement attraction.
+We eliminate the possibility of possible non-subjecthood clues given by the form that is shared by the accusative case and the posessive suffix.
+
+Within the shallow processing model, we would also expect a no change in the status of agreement attraction.
+In our account of shallow processing, we argue that when the comprehenders reach the verb and saw plural morpheme, they engage in matching mechanism where they try to match the verbal plural morpheme with a previous nomimal plural morpheme.
+An agreement attraction, then, is not a result of a partial matching or a representational error of number feature; instead, it is the result of a state of memory in which comprehenders misremember either the existence of the nominal plural morpheme or the place of the nominal plural morpheme as stated in the MPT model of the agreement attraction within shallow processor within \autoref{model1}, \autoref{model2}, \autoref{model3}\footnote{Author here wishes he knew more latex to do the MPT tree more neat.}.
+
+\begin{figure}[htb!]
+\centering
+\begin{tikzpicture}[
+    sibling distance        = 0.5em,
+    level distance          = 5em,
+    edge from parent/.style = {draw, -latex},
+    every node/.style       = {font=\scriptsize},
+    sloped
+  ]
+\Tree [.{\ }
+        \edge node[auto=left]{f}; [.\node[draw,rounded corners=.8ex]{generic failure};
+                                     \node[draw]{Ungrammatical};]
+        \edge node[auto=left]{1-f};
+        [.\node[draw,rounded corners=.8ex]{no failure};
+          \edge[dashed]; [.\node[]{Plural Verbs}; 
+                           \edge[dashed]; \node[]{With Distractor};
+                           \edge[dashed]; \node[]{Without Distractor};
+                         ] 
+          \edge[dashed]; [.\node[]{Singular Verbs}; 
+                          \edge[dashed]; [.\node[draw,rounded corners=.8ex]{No checking};
+                                           \node[draw]{Grammatical};]
+                         ] 
+        ] 
+      ]
+\end{tikzpicture}
+\caption{xd}
+\label{model1}
+\end{figure}
+
+\begin{figure}[htb!]
+\centering
+\begin{tikzpicture}[
+    sibling distance        = 0.5em,
+    level distance          = 5em,
+    edge from parent/.style = {draw, -latex},
+    every node/.style       = {font=\scriptsize},
+    sloped
+  ]
+\Tree [.\node[]{Without Distractor}; 
+                                          \edge node[auto=left]{m$_2$}; [.\node[draw,rounded corners=.8ex]{No Memory of -lAr};
+                                                                        \edge node[auto=left]{g}; \node[draw]{Grammatical};
+                                                                        \edge node[auto=left]{1-g}; \node[draw]{Ungrammatical};]
+                                          \edge node[auto=left]{1-m$_2$}; [.\node[draw,rounded corners=.8ex]{Memory of -lAr}; 
+                                          \edge node[auto=left]{1-p$_2$}; [.\node[draw,rounded corners=.8ex]{No Place of -lAr};
+                                                                        \edge node[auto=left]{g}; \node[draw]{Grammatical};
+                                                                        \edge node[auto=left]{1-g}; \node[draw]{Ungrammatical};]
+                                          \edge node[auto=left]{p$_2$}; [.\node[draw,rounded corners=.8ex]{Misrepresented place of -lAr};
+                                                                        \node[draw]{Ungrammatical};]]]
+
+\end{tikzpicture}
+\caption{xd}
+\label{model2}
+\end{figure}
+\begin{figure}[htb!]
+\centering
+\begin{tikzpicture}[
+    sibling distance        = 0.5em,
+    level distance          = 5em,
+    edge from parent/.style = {draw, -latex},
+    every node/.style       = {font=\scriptsize},
+    sloped
+  ]
+\Tree [.\node[]{With Distractor}; 
+                                          \edge node[auto=left]{m$_1$}; [.\node[draw,rounded corners=.8ex]{No Memory of -lAr};
+                                                                        \edge node[auto=left]{g}; \node[draw]{Grammatical};
+                                                                        \edge node[auto=left]{1-g}; \node[draw]{Ungrammatical};]
+                                          \edge node[auto=left]{1-m$_1$}; [.\node[draw,rounded corners=.8ex]{Memory of -lAr}; 
+                                          \edge node[auto=left]{1-p$_1$}; [.\node[draw,rounded corners=.8ex]{No Place of -lAr};
+                                                                        \edge node[auto=left]{g}; \node[draw]{Grammatical};
+                                                                        \edge node[auto=left]{1-g}; \node[draw]{Ungrammatical};]
+                                          \edge node[auto=left]{p$_1$}; [.\node[draw,rounded corners=.8ex]{Memory of place of -lAr};
+                                                                        \node[draw]{Grammatical};]]]
+
+\end{tikzpicture}
+\caption{xd}
+\label{model3}
+\end{figure}
+
+In our second experiment, we investigate the predictions made from our model using a verbal plural morpheme within a distractor relative clause.
+As mentioned earlier, the verbal plural morpheme in Turkish is exactly the same with the nominal plural with regards to its stress, its behaviour, and its form: \emph{-lAr}.
+Since Turkish relative clauses are essentially nominals due the nomilization process, they behave exactly like other nominals within the sentence \autocites{Goksel2004}{Taylan2015}.
+They can be marked with cases, plural agreement and they can have postpositions that any nominal also can.
+This syntactic formation enables us to question how shallow people process, how much syntactic information is relevant, or how perfectly people encode the features of the elements of the sentence.
+In our experiment 2, we have used items in which the referential head noun of the subject is modified with a single-word relative clause as in \autoref{ouritem1}.
+
+\begin{exe}
+  \ex \label{ouritem1}
+      \gll D\"{o}v-d\"{u}k-(\textbf{ler})-i \c{c}ocuk mutfak-ta bayg{\i}n hal-de yat-{\i}yor-(\textbf{lar})-d{\i}.\\
+  beat-\textsc{Nmlz}-(\textsc{Pl})-\textsc{Poss} kid kitchen-\textsc{Loc} unconscious state-\textsc{Loc} lie-\textsc{Prog}-(\textsc{Pl})-\textsc{Pst}\\
+      \glt Intended: The kid that they beat were laying in the kitchen unconscious.
+\end{exe}
+
+Within the framework of percolation theories, we expect a harsh decline in the agreement attraction effects\footnote{Discussion regarding to the how and where relative clauses adjoined is omited due to the scope of the paper.
+However, it should be clear that a late insertion analysis where the relative clauses are actually above the head noun would yield different results.
+In this paper, I assume that modifiers like relative clauses are within the noun phrase, which deems them \textit{syntactically} deeper placed in the hierarchical three than the possessee.}.
+The reason for this expected decline is the fact that relative clauses being relative \emph{deeper} in the hierarchical structure than the possessee of genitive-posessive structure.
+
+As for cue-based retrieval models, we would expect an agreement attraction quite similar to the one that we originally have in \textcite{Lago2018}.
+The reason for this expected agreement attraction is the fact that apart from having a verbal root, the relative clauses and nomials are behave exactly the same in terms of \emph{nounnness}.
+Like nominals, nominalized structures first marked with plural and then with the case or possessive suffix.
+From this aspective, it seems like there should be no difference.
+However, one may argue that the features related to the verbal and nominal can be encoded differently.
+Thus, there will no partial match at any time given due to the fact that verbal plural morpheme at the main verb does specify cues for specific type of plural marking.
+One other question that may arise from this structure is that whether or not the parts of already-formed dependencies can feed the following dependency resolution.
+In other words, the verbal plural morpheme \emph{-lar} on \emph{dövdükleri} in \autoref{ouritem1} is already a trigger of a cue retrieval process.
+And, when it is merged with the nominal head \emph{çocuk}, there is a formed semantic meaning that is \enquote{a group of people have beaten a kid.} However, this \emph{suggesstion} assumes that relative clauses are formed at the very moment.
+Moreover, we also need to assume that after forming a relative clause they are unreachable, meaning that they do not contribute to the processing of the sentnece, anymore.
+
+Lastly in our extremely shallow processing model, we would expect a significant effect of agreement attraction.
+Due to one of the writers inability to \emph{run the numbers} and \emph{form the mpt trees in time}, this part unfortunately does not go beyond than a verbal argumentation.
+The reason we wait a significant effect of agreement is due to the fact that upon the agreement process is driven by the faulty memory of the place of the plural morpheme and uneducated guessing.
+Since the parsing is shallow, comprehenders do not engage in perfect attribution of the features, thus having a somewhat blurry representation behind.
+We expect for this behaviour to be omnipresent in other agreement attraction phenomenon that has been showed, as well as in \textcite{Lago2018} and in our replication of it.
+Therefore, there is no reason to have to anything to be different in experiment 2.
+
+\hypertarget{experiment-1}{%
+\subsection{Experiment 1}\label{experiment-1}}
+
+In their study, \textcite{Lago2018} investigates the comprehension of subject-verb agreement Turkish monolinguals.
+They use speeded acceptability judgments for the effects of number attraction in Turkish.
+Their sentences make us of genitive-possessive constructions in the subject position, where the genitive is the attractor and the possessive is the head noun.
+They manipulate the grammaticality of the sentence by changing the plural morphology of the verb, and they also manipulate the plurality of the attractor noun.
+In grammatical conditions, the subject and the verb both bear singular morphology with no overt morpheme.
+Moreover, in the ungrammatical conditions, the verb bears the overt \emph{-lAr} morpheme whereas the subject is still singular as exemplified below.
 
@@
 
-They found a significant effect of number attraction in Turkish ranging
-between 11\%--15\% across monolinguals. As seen in the results of the
-statistical analysis in \textsc{Table} (\ref{lagomodel}), the
-acceptability judgments showed an immense effect of grammaticality, and
-there is also interaction between grammaticality and attractor number,
-which indicates the presence of a number attraction effect.
-
-\begin{table}[!hbt]
-\centering
-\begin{tabular}{llcccc}
-\hline
-    &                                        & \multicolumn{4}{l}{Monolingual Speakers}                                               \\ \cline{3-6} 
-    &                                        & $\beta$        & SE            & \emph{z} & \emph{p} \\ \hline
-\multicolumn{2}{l}{\textbf{Attraction Task}} &                &               &                           &                           \\
-    & Grammaticality                         & \textbf{-5.51} & \textbf{0.33} & \textbf{-16.69}           & \textbf{.000}             \\
-    & Attractor Number                       & 0.14           & 0.25          & 0.57                      & .571                      \\
-    & Grammaticality x Attractor Number      & \textbf{1.69}  & \textbf{0.53} & \textbf{3.19}             & \textbf{.001}             \\
-    & Attractor Number: Ungram conditions    & \textbf{0.94}  & \textbf{0.26} & \textbf{3.68}             & \textbf{.000}             \\
-    & Attractor Number: Gram conditions      & -0.79          & 0.52          & -1.51                     & .131                      \\ \hline
-\end{tabular}
-\caption{Model results for the judgments of monolingual cited from @Lago.}
-\label{lagomodel}
-\end{table}
-
-Lago (2018) stipulate that the Turkish genitive case does not provide a
-strong cue against subjecthood since Turkish frequently makes use of
-genitive marked subjects in embedded clauses, as in example
-(\ref{gensubj}). This is in contrast with English, in which the genitive
-case is compatible with subjecthood. Thus, Lago (2018) argue that this
-robust agreement attraction effect has been linked to the case
-information carried by accusative and genitive.
+They found a significant effect of number attraction in Turkish ranging between 11\%--15\% across monolinguals.
+\textcite{Lago2018} stipulate that the Turkish genitive case does not provide a strong cue against subjecthood since Turkish frequently makes use of genitive marked subjects in embedded clauses, as in \autoref{gensubj}.
+This is in contrast with English, in which the genitive case is compatible with subjecthood.
+Thus, \textcite{Lago2018} argue that this robust agreement attraction effect has been linked to the case information carried by accusative and genitive.
 
@@
 
-However, our initial hypothesis postulates that participants engage in
-shallow processing, which results in a situation in which not only the
-genitive case but also the possessive case plays a significant role in
-delivering the case information. None of the experimental items in Lago
-(2018) have a head noun which ends with a vowel; thus, all of the
-possessive markers are morphologically and phonologically ambiguous
-between the accusative case and the possessive. Unlike genitive case, it
-is extremely rare for the accusative case to appear on the head noun of
-the subject, which only occurs in raising predicates as in example
-(\ref{dsm}).
+However, our initial hypothesis postulates that participants engage in shallow processing, which results in a situation in which not only the genitive case but also the possessive case plays a significant role in delivering the case information.
+None of the experimental items in \textcite{Lago2018} have a head noun which ends with a vowel; thus, all of the possessive markers are morphologically and phonologically ambiguous between the accusative case and the possessive.
+Unlike genitive case, it is extremely rare for the accusative case to appear on the head noun of the subject, which only occurs in raising predicates as in \autoref{dsm}.
 
@@
 
-In order to test this hypothesis, we have replicated the experiment of
-Lago (2018) with modified items, in which the possessive is not
-ambiguous with the accusative case. We tried to be as faithful as
-possible to the original sentences while also trying to make the
-sentences as plausable as possible. We keep the semantic relation
-between the head noun and the controller the same with what has been
-described in Lago (2018)'s study, which is either a relation regarding
-profession or a service that is given by the head noun for the
-possessor. A set of sentences are exemplified below.
+In order to test this hypothesis, we have replicated the experiment of \textcite{Lago2018} with modified items, in which the possessive is not ambiguous with the accusative case.
+We tried to be as faithful as possible to the original sentences while also trying to make the sentences as plausable as possible.
+We keep the semantic relation between the head noun and the controller the same with what has been described in \textcite{Lago2018}, which is either a relation regarding profession or a service that is given by the head noun for the possessor.
+A set of sentences are exemplified below.
 
@@
 
-As seen in the examples, unlike Lago (2018)'s experimental items, all of
-our items bear the \emph{-sI} possessive marker instead of the ambiguous
-\emph{-I} marker. As for the filler items, we could not use or modify
-the original experiment items since the fillers of the original study
-were not online. We have used two types filler sentences: grammatical
-sentences in which the verb bears plural agreement (\ref{fillera}), and
-ungrammatical sentences in which the verb does not bear plural agreement
-(\ref{fillerb}). We wanted to nullify a possible strategy by the
-participants where they associate the sentence-final morpheme directly
-with the acceptability of the sentence. And we also wanted to eliminate
-the possibility of participants disregarding other elements in the
-sentences while answering the questions we ask right after the sentence.
+As seen in the examples, unlike \textcite{Lago2018}'s experimental items, all of our items bear the \emph{-sI} possessive marker instead of the ambiguous \emph{-I} marker.
+As for the filler items, we could not use or modify the original experiment items since the fillers of the original study were not online.
+We have used two types filler sentences: grammatical sentences in which the verb bears plural agreement (\autoref{fillera}), and ungrammatical sentences in which the verb does not bear plural agreement (\autoref{fillerb}).
+We wanted to nullify a possible strategy by the participants where they associate the sentence-final morpheme directly with the acceptability of the sentence.
+And we also wanted to eliminate the possibility of participants disregarding other elements in the sentences while answering the questions we ask right after the sentence.
 
@@
 
-All of our data, experimental materials, our experiment design, and our
-fillers can be found on the website of the Center for Open Science
-Framework (\url{https://osf.io/}).
+\hypertarget{participants-and-procedure}{%
+\subsubsection{Participants and Procedure}\label{participants-and-procedure}}
 
-\subsection{Participants and
-Procedure}\label{participants-and-procedure}
+One hundred and seven Turkish speakers were recruited from Bogazici University in İstanbul.
+We did not collect participants' knowledge of other languages; however, we verified that Turkish is their native language and that they predominantly use it in their daily lives.
+In the experiments, participants were asked to judge the acceptability of experimental and filler sentences in Turkish.
+All of the sentences were presented one word at a time in the center of the screen for 500 ms per word unlike \textcite{Lago2018} and \textcite{Wagers2009}, in which the duration was 300 ms per word.
+The experiment was run on a web-based platform titled the Ibex Farm, and all of the documentation can be found on our github page.
 
-One hundred and seven Turkish speakers with a mean age of X were
-recruited from Bogazici University in İstanbul. We did not collect
-participants' knowledge of other languages; however, we verified that
-Turkish is their native language and that they predominantly use it in
-their daily lives. In the experiments, participants were asked to judge
-the acceptability of experimental and filler sentences in Turkish. All
-of the sentences were presented one word at a time in the center of the
-screen for 500 ms per word unlike Lago (2018) and Wagers, Lau, and
-Phillips (2009), in which the duration was 300 ms per word. The
-experiment was run on a web-based platform titled the Ibex Farm, and all
-of the documentation can be found on our osf and github page.
+Before the experiment, participants were instructed to give accurate and quick answers based on their own intuitions, and they were also notified about the time limit for answering.
+At the start of the experiment, they were given 4 practice items with feedback.
+Each trial after the practice items started with a blank screen, followed by a flash of single words in the middle of the screen.
+After the sentence, they were asked a grammaticality judgment questins (Was the sentence you read was natural to you?) where they need to press P for \emph{no} and press Q for \emph{yes}.
+In the experiment, every participant saw 40 experimental item that is latin-squared and 40 fillers.
 
-Before the experiment, participants were instructed to give accurate and
-quick answers based on their own intuitions, and they were also notified
-about the time limit for answering. At the start of the experiment, they
-were given 4 practice items with feedback.
+\hypertarget{analysis}{%
+\subsubsection{Analysis}\label{analysis}}
 
-What to write about analyze?
+Every experimental item from both experiments (Experiment 1 and \textcite{Lago2018}) is included in the analysis.
+Participants that could not exceed the threshold of 0.25 difference in \emph{yes} answer between the condition (c) and (d), namely Ungrammatical, SG attractor and Grammatical, SG attractor, were excluded.
+We performed an analysis by fitting linear mixed-effect modelts to our data, controlling for vowel ending, plural attractor, grammaticality and their interactions.
+Models were fit using bernoulli distribution with probit link function and 95\% confidence intervals.
 
-\subsection{Results and Discussion}\label{results-and-discussion}
-
-In \textsc{Figure} (1), the y-axis shows the percentage of
-``acceptable'' answers, and the x-axis indicates whether or not the
-sentences in that group are grammatical. Moreover, the linet ypes
-indicate an attractor noun with overt plural morphology. As seen in the
-figure, 1\% of the sentences with plural attractors and a singular verb
-were accepted by the participants, in line with the findings of Lago
-(2018). We also see a number attraction rate of 2\% which was also
-observed in Lago (2018) with close results.
-
-In \textsc{Table} (\ref{tab:replication}),
-\ldots{}\ldots{}\ldots{}\ldots{}
-
-\subsection{Responses}\label{responses}
+\hypertarget{results}{%
+\subsubsection{Results}\label{results}}
 
@@
 \includegraphics{AgreementAttraction_files/figure-latex/exp1AvgResponse-1.pdf}
-\caption{\label{fig:exp1AvgResponse}Estimates and 95\% credible intervals
-for the analysis of the probability of a `yes' response.}
+\caption{\label{fig:exp1AvgResponse}Estimates and 95\% credible intervals for the analysis of the probability of a \enquote{yes} response.}
 \end{figure}
+
+In Figure \ref{fig:exp1AvgResponse}, the y-axis shows the percentage of \enquote{acceptable} answers, and the x-axis indicates whether or not the sentences in that group are grammatical.
+As seen in the figure, 0.22\% of the sentences with plural attractors and a singular verb were accepted by the participants, in line with the findings of \textcite{Lago2018}.
+We also see a number attraction rate of 0.11\% which was also observed in \textcite{Lago2018} with close results.
+
+In Figure \ref{fig:exp1ResponseModelPlot}, we clearly see the effects of ungrammaticality and the interaction between the ungrammaticality and plural attractor.
+We see that, vowel ending is not significant even though it has negative effect.
+Thus, we may say that differentiating between the accusative case and the possessive suffix has cause a reduction in the effect of the agreement attraction.
+The results also shows that when the attractor is plural, people have a high tendency to find the sentence grammatical.
 
@@
 \centering
-\includegraphics{AgreementAttraction_files/figure-latex/exp1AvgResponseLagoEtAl-1.pdf}
-\caption{\label{fig:exp1AvgResponseLagoEtAl}Estimates and 95\% credible
-intervals for the analysis of the probability of a `yes' response.}
+\includegraphics{AgreementAttraction_files/figure-latex/exp1ResponseModelPlot-1.pdf}
+\caption{\label{fig:exp1ResponseModelPlot}log-odd Estimates and 95\% credible intervals for the regression coefficients.}
 \end{figure}
 
-\subsection{Response Times}\label{response-times}
+In Figure \ref{fig:exp1AvgRTs}, we see that average response times are significantly higher than the those of \textcite{Lago2018}.
+Again, these results shows the effect of disambiguation of the possessive suffix from the accusative case has surfaced as the difficuilty in response and memory retrieval time.
 
@@
 \includegraphics{AgreementAttraction_files/figure-latex/exp1AvgRTs-1.pdf}
-\caption{}
+\caption{\label{fig:exp1AvgRTs}Average response times for our replication and Lago et. al. (2018)}
 \end{figure}
 
-\clearpage
+\hypertarget{discussion}{%
+\subsubsection{Discussion}\label{discussion}}
 
-\section{EXPERIMENT 2: RC ATTRACTOR}\label{experiment-2-rc-attractor}
+The results follow from what a cue-based model would predict: slightly lower agreement attraction.
+However, these results can also be a result of a badly formed filler sentences which are shown with purple line.
+Participants may be biased towards saying no since most of the experimental items being ungramatical.
+However, this can also be statistical \emph{miss} since we may accidentally have a group such as this one.
+However, the visible effect of vowel ending and response time suggest that people do indeed care more than only the retrieval of plural morpheme \emph{-lar} and its place.
+This results go against what we have predicted for the Marking and Morphing model and our shallow processing model.
+However, the existence of extremely close degree of agremeent attraction effects and non-significant nature of the effect of the vowel ending indicate that we cannot readily discard other explanations.
 
-Even though our first hypothesis regarding shallow processing did not
-hold, we still need to entertain the second possibility we have
-discussed in this paper. Participants may indeed engage in an even
-shallower process of sentence comprehension, in which they merely match
-the use of \emph{-lAr}. Moreover, we still need to discuss how much it
-is an effect of case information rather than only a number attraction.
-We have seen that the anti-subjecthood cues of the accusative are not
-significant since in both cases where the possessive is ambiguous with
-the accusative and the possessive is clearly marked, we have observed
-extremely close results in the speeded acceptability judgments.
+\hypertarget{experiment-2}{%
+\subsection{Experiment 2}\label{experiment-2}}
 
-In order to check both the sole effect of number agreement and the
-possibility of a task effect, we propose an experiment design in which a
-head noun is a bare NP, is not marked with any other morpheme and
-preceded by a relative clause construction. This relative clause
-consists of only a verbal component, which bears an overt plural marker.
-Since Turkish verbal and nominal plural morphemes are identical, we plan
-to check the participants' strategy with regards to whether or not it is
-a cue that helps in the reconstruction of the ungrammatical sentence or
-whether it is merely a task effect in which participants disregard the
-rest of the sentence and focus the existence of the morpheme
-\emph{-lAr}.
+Having discussed the replication study of \textcite{Lago2018}, we have shown that results favor the cue-based models, especially with the effect of disambiguated possessive suffix on response times.
+However, due to the extremely similar effects on agreement attraction we can still entartain shallow processing mechanism as explained in \autoref{model1}, \autoref{model2}, and \autoref{model3}.
+Since we argue that the agreement attraction is a product of memory state in which comprehenders do not have an exact memory of the place of the plural morpheme mainly, we conducted an experiment where the distractor with the plural morpheme in on the relative clause.
 
-\subsection{Materials}\label{materials}
+The study consists of an speeded acceptability judgment experiment in the web-based platform Ibex Farm.
+In the experiment, we test whether or not speakers utilize even more shallow parser than what is stipulated by \textcite{Lago2018} and our replication of \textcite{Lago2018} Experiment 2.
+This was investigated using syntactic structures similar to \textcite{Lago2018} materials, in which we have opted out the Genitive Constructuion (GC) for Relative Clause construction (RCC) as a distractor.
+In Turkish, like GC, relative clause in RCC precedes the head noun, and length-wise Turkish relative clauses can consist of only one word and the rest can be dropped.
+Turkish allows us to use RCCs as distractors in the same place because Turkish plural morpheme in verbal domain and nominal domain are the same: \emph{-lAr}.
+Both of them react similarly in the same phonological environments, and they also exhibit same stress patterns.
 
-Like genitive-possessive structures, attractors do not intervene between
-the grammatical agreement controller and the verb in relative clause
-constructions. Turkish relative clauses always precede the head noun,
-except for in special cases in which they are marked with unique
-prosody. Item (\ref{rcexample}) is an example of a RC structure, and
-item (\ref{rcexample2}) shows the possibility of using only the verbal
-component of the relative clause since it is grammatical to drop
-arguments in Turkish. ( add a footnote here giving the details of such
-events, and restrictions. )
+In the experimental items, the distractor RC and the matrix verb had four configurations in which the number morpheme on the RCC (\emph{plural} vs.
+\emph{singular} marked RC verb) and matrix verb (\emph{grammatical} vs.
+\emph{ungrammatical}) as in \autoref{prereg1}.
 
 \begin{exe}
-\ex
-  \begin{xlist}
-    \ex \label{rcexample}
-    \gll On-lar-{\i}n ev-e gel-me-den g\"{o}r-d\"{u}k-ler-i \c{c}ocuk so\u{g}uk-ta \"{u}\c{s}\"{u}-m\"{u}\c{s}-t\"{u}.\\
-    they-\textsc{pl}-\textsc{gen} home-\textsc{dat} come-\textsc{neg}-\textsc{abl} see-\textsc{nlmz}-\textsc{pl}-\textsc{poss} kid cold--\textsc{loc} feel.chilly-\textsc{perf}-\textsc{pst}\\
-    \glt The kid that they saw right before coming to home was feeling chilly. 
-    \ex \label{rcexample2}
-    \gll G\"{o}r-d\"{u}k-ler-i \c{c}ocuk so\u{g}uk-ta \"{u}\c{s}\"{u}-m\"{u}\c{s}-t\"{u}.\\
-    see-\textsc{nlmz}-\textsc{pl}-\textsc{poss} kid cold--\textsc{loc} feel.chilly-\textsc{perf}-\textsc{pst}\\
-    \glt The kid that they saw home was feeling chilly.
-  \end{xlist}
-\end{exe}
-
-As for the experimental sentences, we plan to use sentences that are
-similar to the ones used in Lago (2018). Instead of a genitive
-controller, we utilize an RC, which we manipulate for its values for
-bearing the plural morpheme. The head noun of the subject is always
-singular, and it is followed by a 2/3 word adverbial. Moreover, the
-matrix verb of the sentences is also manipulated in terms of plurality,
-deeming the sentence grammatical or ungrammatical. Lastly, the relative
-clause has to be an object relative clause, since Turkish subject
-relative clauses never bear a plural morpheme on the embedded verb. As
-in the Lago (2018)'s study and our replication, we will have a four
-condition, where we manipulate the plurality of the attractor
-(\emph{plural/singular}) and the grammaticality of the sentece by using
-overt plural morphology (\emph{grammatical/ungrammatical}), which are
-demonstrated with item (\ref{reg1}), (\ref{reg2}), (\ref{reg3}), and
-(\ref{reg4})
-
-\begin{exe}
-\ex
+\ex \label{prereg1}
   \begin{xlist}
   \ex \underline{Grammatical, SG attractor} \label{reg1}
-      \gll D\"{o}v-d\"{u}\u{g}-\"{u} \c{c}ocuk mutfak-ta bayg{\i}n hal-de yat-{\i}yor-du.\\
-  beat-\textsc{nmlz}-\textsc{poss} kid kitchen-\textsc{loc} unconscious state-\textsc{loc} lie-\textsc{prog}-\textsc{pst}\\ 
+      \gll D\"{o}v-d\"{u}\u{g}-\"{u} \c{c}ocuk okul-a yorgun arg?n gel-di.\\
+  beat-\textsc{nmlz}-\textsc{poss} kid school-\textsc{dat} unconscious state-\textsc{loc} lie-\textsc{prog}-\textsc{pst}\\ 
       \glt The kid that he/she beats was laying in the kitchen unconscious.
@@
 
-As for the fillers, we need two different set of fillers in order to
-counterbalance the ever-present grammaticality of singular and plural
-verbs. For grammatical fillers with a plural verb (example
-(\ref{fillerreg1})) we propose a structure in which the head noun is
-followed by a converb. With this modification, the controller of the
-experimental sentences becomes a controller for a subclause, and the
-main verb is saturated with another subject introduced right after the
-subclause.
-
-For ungrammatical fillers with a singular verb (example
-(\ref{fillerreg2})), we have used strictly transitive verbs without an
-overt object. By utilizing the same structure with the other type of
-fillers, we ensure that participants will not come up with a strategy in
-which they always check the second word for dependency resolution. The
-controller of the fillers and the controller of the experimental items
-differ in the linear order they are shown in the experiment.
-
-Question: Can we do subject relative clause here? Like durdurulan
-ogrenci.
+As for the experiment, we have used same type of fillers with the Experiment 1 in order to tackle with two possible strategies that can be utilized by the participants: (i) deeming the sentence acceptable when the matrix verb is singular and (ii) deeming most of the sentences unacceptable when the matrix verb is plural.
+To tackle with the first type of strategy, we have used a sentence where the object is not marked with accusative and it is not in immediately pre-verbal position as in \autoref{filler1a}.
+The idea was to have a singular matrix verb in an ungrammtical sentence where the ungrammaticality does not stem from the local elements.
+As for the other strategy we have used pro-drop charactheristics of Turkish and made the first noun phrase with a relative clause an object as in \autoref{filler1b}.
+The idea behind is that the plural agreement on the matrix verb is resolved with a dropped subject instead of the first noun phrase with a relative clause.
+Every participant saw 40 experimental item that is latin-squared and 40 fillers.
 
@@
 
-\subsection{Participants and
-Procedure}\label{participants-and-procedure-1}
+\hypertarget{participants-and-procedure-1}{%
+\subsubsection{Participants and Procedure}\label{participants-and-procedure-1}}
 
-We plan to have participants from the undergrad students of Bogazici
-University, which will be given an extra credit incentive. They will
-again carry out the experiment on an online experiment platform Ibex
-Farm. The experiment process will be exactly the same with the
-replication of Lago (2018), including descriptions before the
-experiment, the layout of the experiment, the time spared for
-visualization of every word, exclusion criteria, and analysis.
+Eighty Turkish speakers were recruited from Bogazici University in İstanbul.
+The procedure was exatcly the same as the Experiment 1.
+The participants in this experiment were completely different than the Experiment one.
 
-\subsection{Expectations}\label{expectations}
+\hypertarget{analysis-1}{%
+\subsubsection{Analysis}\label{analysis-1}}
 
-(This part is extremely tentative)
+Every experimental item from both experiments (this experiment and the Experiment 1) is included in the analysis.
+Participants that could not exceed the threshold of 0.25 difference in \emph{yes} answer between the condition (c) and (d), namely Ungrammatical, SG attractor and Grammatical, SG attractor, were excluded.
+We performed an analysis by fitting linear mixed-effect modelts to our data, controlling for vowel ending, plural attractor, grammaticality and their interactions.
+Models were fit using bernoulli ditribution with probit link function and 95\% confidence intervals.
 
-Our objective is to explore the number attraction phenomenon without the
-effects of case information and without the limits of nominal paradigm.
-By doing so, we expect participants to engage with the sentences which
-are ungrammatical in an extremely shallow fashion. We argue that instead
-of reconstructing the sentence utilizing every detail from the attractor
-and the controller, participants disregard the information from other
-sources in the sentence and look for a matching morpheme, i.e.
-\emph{-lAr}.
+\hypertarget{results-1}{%
+\subsubsection{Results}\label{results-1}}
 
-In the case that there will be a similar attraction effects with the
-replication of Lago (2018) and Lago (2018) study, we think that\ldots{}
-what do we think? I need to talk about the paper and idea more
-thoroughly, I guess. Because I feel like I am repeating myself.
+\begin{figure}
+\centering
+\includegraphics{AgreementAttraction_files/figure-latex/exp2AvgResponse-1.pdf}
+\caption{\label{fig:exp2AvgResponse}Estimates and 95\% credible intervals for the analysis of the probability of a \enquote{yes} response.}
+\end{figure}
 
-\section{DISCUSSION}\label{discussion}
+It is clear from Figure \ref{fig:exp2AvgResponse} that in the condition (c) where we expect an agreement attraction, participants find as unacceptable as the condition (d) with singular attractor, singular head noun, and plural matrix verb.
+While we do not see any agreement attraction (0.07\%), we also see a more firm analysis of the ungrammatical sentence with singular matrix verb ((0.07\%)).
 
-Discuss.
+As for the estimates of coefficients in \ref{fig:exp2ResponseModelPlot}, we can conclude that there is a significant negative effect of plural morpheme on the relative clause, which means that it does not cause any agreement affects.
+Again, the effect of ungrammaticality that stems from the existence of plural morpeheme on the matrix verb is visible.
+The interaction between the plural morpheme on the attractor RC and the matrix verb is even higher than the sole effect of plural morpheme on the attractor RC.
 
-\section{CONCLUSIONS}\label{conclusions}
+\begin{figure}
+\centering
+\includegraphics{AgreementAttraction_files/figure-latex/exp2ResponseModelPlot-1.pdf}
+\caption{\label{fig:exp2ResponseModelPlot}log-odd Estimates and 95\% credible intervals for the regression coefficients.}
+\end{figure}
 
-\subsection{\texorpdfstring{In this paper, we have entertained the idea
-of task effect in the so-called Turkish number attraction phenomenon. We
-argue that the findings of the Lago (2018) study is not clear and there
-are too many variables to account for in the experiment, one of them
-being the ambiguous morphology that the head noun bears. In the first
-experiment, we have replicated the attraction task of Lago (2018). We
-have found the similar effects of agreement with a bigger pool of
-participants. Then, for entertaining the other possibility in which we
-argue that participants do not fully reconstruct the sentence; however,
-they make us of the direct cue of overt morpheme \emph{-lAr}, we offer
-an experiment where we use object relative clauses as an
-attractor.}{In this paper, we have entertained the idea of task effect in the so-called Turkish number attraction phenomenon.
-We argue that the findings of the Lago (2018) study is not clear and there are too many variables to account for in the experiment, one of them being the ambiguous morphology that the head noun bears.
-In the first experiment, we have replicated the attraction task of Lago (2018).
-We have found the similar effects of agreement with a bigger pool of participants.
-Then, for entertaining the other possibility in which we argue that participants do not fully reconstruct the sentence; however, they make us of the direct cue of overt morpheme -lAr, we offer an experiment where we use object relative clauses as an attractor.}}\label{in-this-paper-we-have-entertained-the-idea-of-task-effect-in-the-so-called-turkish-number-attraction-phenomenon.-we-argue-that-the-findings-of-the-lago-study-is-not-clear-and-there-are-too-many-variables-to-account-for-in-the-experiment-one-of-them-being-the-ambiguous-morphology-that-the-head-noun-bears.-in-the-first-experiment-we-have-replicated-the-attraction-task-of-lago.-we-have-found-the-similar-effects-of-agreement-with-a-bigger-pool-of-participants.-then-for-entertaining-the-other-possibility-in-which-we-argue-that-participants-do-not-fully-reconstruct-the-sentence-however-they-make-us-of-the-direct-cue-of-overt-morpheme--lar-we-offer-an-experiment-where-we-use-object-relative-clauses-as-an-attractor.}
+\begin{figure}
+\centering
+\includegraphics{AgreementAttraction_files/figure-latex/exp2AvgRTs-1.pdf}
+\caption{\label{fig:exp2AvgRTs}Average response times for our replication and Experiment2}
+\end{figure}
 
-\section{ACKNOWLEDGEMENTS}\label{acknowledgements}
+Finally, the response times of the Experiment 2 is significantly lower than the Experiment 1 as seen from Figure \ref{fig:exp2AvgRTs}.
+The even lower response time in ungrammatical plural (condition c) shows that participants were extremely confident with their decision and did not had any issue with the dependency resolution.
 
-We used the statistical language \texttt{R} (R Core Team, 2018) for all
-our analyses. These were implemented in dynamic rmarkdown documents
-using \texttt{knitr} (Xie, 2018) and \texttt{rmarkdown} (Xie, Allaire,
-\& Grolemund, 2018) packages. All graphs have been done with
-\texttt{ggplot} (Wickham, 2016).
+\hypertarget{discussion-1}{%
+\subsubsection{Discussion}\label{discussion-1}}
 
-\section*{REFERENCES}\label{references}
-\addcontentsline{toc}{section}{REFERENCES}
+These findings indicate that our hypothesis regarding the matching of the forms is not supported by the empirical evidence.
+However, results in Experiment 2 points in a direction where the Marking and Morphing studies predicted in the first place.
+Due to the deeper syntactic embedding, the numeral feature cannot percolate as freely as it can in genitive possessive structure and cannot affect the final number of the subject root node.
+
+However, with the right prediction with regards to which features are stored and can be cued for, cue-based retrieval mechanisms can also explain the findings in Experiment 2.
+
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
+
+We have shown that the agreement attraction effects cannot be explained by the extremely shallow processing mechanisms, at least with the implementaion we have proposed here.
+However, we also shown that findings from Experiment 1 and 2 was not enought the differentiate between two models that can explain agreement attraction: the Marking and Morphing and cue-based retrieval models.
+While the findings of Experiment 1 favors the cue-based retrieval mechanism, Experiment 2 with the harsh decline in the effects of agreement attraction points to another horizon.
+
+Another take on the results may follow from the redefinition of the \emph{shallowness} concept.
+Experiments show that it is not only dependent on the form.
+However, it can be an issue related to already-formed dependencies inability to be used in the memory process.
+One can argue that once the dependencies are formed and resolved, participants does not go back to them when another cue is set out.
+
+\hypertarget{references}{%
+\section{References}\label{references}}
+
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
 
 \hypertarget{refs}{}
-\hypertarget{ref-Lago}{}
-Lago, S. (2018). Straight from the horse's mouth: agreement attraction
-effects with Turkish possessors. doi:\href{https://doi.org/none}{none}
 
-\hypertarget{ref-R_Core_Team_2018}{}
-R Core Team. (2018). \emph{R: A language and environment for statistical
-computing}. Vienna, Austria: R Foundation for Statistical Computing.
-Retrieved from \url{https://www.R-project.org/}
+\endgroup
 
-\hypertarget{ref-Wagers2009}{}
-Wagers, M. W., Lau, E. F., \& Phillips, C. (2009). Agreement attraction
-in comprehension: Representations and processes. \emph{Journal of Memory
-and Language}, \emph{61}(2), 206--237.
-doi:\href{https://doi.org/10.1016/j.jml.2009.04.002}{10.1016/j.jml.2009.04.002}
-
-\hypertarget{ref-Wickham_2016}{}
-Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}.
-Springer-Verlag New York. Retrieved from \url{http://ggplot2.org}
-
-\hypertarget{ref-Xie_2018}{}
-Xie, Y. (2018). \emph{Knitr: A general-purpose package for dynamic
-report generation in r}. Retrieved from \url{https://yihui.name/knitr/}
-
-\hypertarget{ref-Xie_2018a}{}
-Xie, Y., Allaire, J., \& Grolemund, G. (2018). \emph{R markdown: The
-definitive guide}. Boca Raton, Florida: Chapman; Hall/CRC. Retrieved
-from \url{https://bookdown.org/yihui/rmarkdown}
+\printbibliography
 

### 2019-06-14 Paper/AgreementAttraction.Rmd
without
proper mpt, with second experiment

@@
 ---
-title             : "Agreement Attraction"
+title             : "Agreement Attraction in Turkish: Who let the -lAr out?"
 shorttitle        : "Agreement Attraction in Turkish"
@@
   - name          : "Utku Türk"
-    affiliation   : "1"
+    affiliation   : ""
     corresponding : yes    # Define only one corresponding author
@@
     email         : "utku.turk@boun.edu.tr"
-  - name          : "Pavel Logacev"
-    affiliation   : "1"
 
 affiliation:
-  - id            : "1"
+  - id            : ""
     institution   : "Boğaziçi University"
@@
 abstract: |
-    The comprehension of agreement within the elements of a sentence is known to fail.
-One of these comprehension errors is known as agreement attraction.
-Speakers may erroneously find a sentence in which the "attractor" agrees with the verb instead of the "head" of the subject.
-Data from typologically different languages and explanations from different frameworks shows that we are far from understanding by what the attraction is modulated.
-Some theories refer this phenomenon as a faulty representation of the number on the head of the subject phase whereas other theories argues that the attraction is due to an error in the access to the number of the subject.
-In this paper, we report two experiments exploring a possible explanation for agreement attraction: an extremely shallow processing.
-The first experiment is a replication of @Lago2018 where we changed the head of the subject in order to differentiate between the accusative case *-I*.
-In the second experiment, we have used a relative clause which only consists of a plural marked verb as a distractor.
-Our results show that while people do indeed care more than just "matching" the forms of plural verbal.
-Either comprehenders have some sort of restriction to not use cues from verbs upon accessing the number of the plural morpheme or there is a syntactic reason for the number feature of plural morpheme to not "percolate."
 
@@
 #  - \let\eachwordtwo=\footnotesize
+  - \usepackage{geometry}
+  - \geometry{margin=2cm}
+  - \usepackage{libertine}
+  - \usepackage{libertinust1math}
+  - \usepackage[T1]{fontenc}
+  - \usepackage{fancyhdr}
+  - \pagestyle{fancy}
+  - \fancyhf{}
+  - \rhead{Türk}
+  - \lhead{Agreement Attraction in Turkish}
+  - \rfoot{\thepage}
 
@@
 
-# Introduction
+\section*{Introduction}
+
+It has been observed that speakers generally fail to accurately comprehend agreement between elements in a sentence.
+One such comprehension error that is made has been deemed agreement attraction.
+Speakers may erroneously find a sentence in which the "attractor" agrees with the verb instead of the "head" of the subject.
+Data from typologically different languages and explanations from different frameworks show that I am far from understanding by what the attraction is modulated.
+Some theories refer this phenomenon as a faulty representation of the number on the head of the subject phase whereas other theories argue that the attraction is due to an error in the access to the number of the subject.
+In this paper, I report two experiments exploring another possible explanation for agreement attraction: an extreme shallow processing.
+The first experiment is a replication of @Lago2018 where I changed the head of the subject in order to differentiate between the accusative case *-I*.
+In the second experiment, I have used a relative clause which only consists of a plural marked verb as a distractor.
+my results show that while people do indeed care more than just "matching" the forms of plural verbal.
+either comprehenders have some sort of restriction to not use cues from verbs upon accessing the number of the plural morpheme or there is a syntactic reason for the number feature of the plural morpheme to not "percolate."
 
@@
 Agreement attractions are defined as instances of incorrect agreements of an element with a distractor that is not its grammatical controller.
-As in \autoref{E1}, the target of the agreement is the verb *are*, the attracting distractor is *bottles*, and the feature erroneously assesed is the number feature of the grammatical controller *label*.
+As in \autoref{E1}, the target of the agreement is the verb *are*, the attracting distractor is *bottles*, and the feature erroneously assessed is the number feature of the grammatical controller *label*.
 
@@
 One of the theoretical attempts to explain such phenomenon was Marking and Morphing Theories [@Bock2001; @Eberhard2005 among others].
-The reason it is called *Marking* and *Morphing* is because there is two possible explanation within the framework with regards to where and when the attraction occurs.
-First possibility is speaker (and/or comprehender) can erroneously create a semantic representation of the head with wrong number feature in the marking process in the marking process.
-Another possibility is that the attraction may arise from an interfering number feature of the attractor with the number feature of the highest noun phrase node in morphing process.
-During the this process, the speaker forms a final number value of the subject phrase, which is determined by each morpheme within the same phrase and their number information with particular weight.
-In morphing process, these other morphemes with number information may contaminate the final number value with perculation mechanism, which depends on the depth of the syntactic embedding.
-As the prediction goes, the more embedded an attractor is, the less attraction they trigger as shown in @Bock1992 in which authors shown that attractors within a relative clause trigger less agreement attraction in the production.
-
-However, other studies shown that other preverbal elements, such as objects, object relative clauses, object clefts, and object questions, may trigger agreement attraction [@Kimball1971; @Hartsuiker2001; @Franck2006; @Franck2015 among others].
+The reason it is called *Marking* and *Morphing* is because there are two possible explanations within the framework with regards to where and when the attraction occurs.
+The first possibility is the speaker can erroneously create a semantic representation of the head with the wrong number feature in the marking process in the marking process.
+Another possibility is that the attraction may arise from an interfering number feature of the attractor with the number feature of the highest noun phrase node in the morphing process.
+During this process, the speaker forms a final number value of the subject phrase, which is determined by each morpheme within the same phrase and their number information with a particular weight.
+In the morphing process, these other morphemes with number information may contaminate the final number value with the percolation mechanism, which depends on the depth of the syntactic embedding.
+As the prediction goes, the more embedded an attractor is, the less attraction they trigger as shown in @Bock1992 in which authors show that attractors within a relative clause trigger less agreement attraction in the production.
+
+However, other studies have shown that other preverbal elements, such as objects, object relative clauses, object clefts, and object questions, may trigger agreement attraction [@Kimball1971; @Hartsuiker2001; @Franck2006; @Franck2015 among others].
 In sentences like \autoref{E2}, the pronominal object *hen* triggers and agreement attraction without being a part of the subject.
@@
 Since the Marking and Morphing theories put the source of the agreement attraction on the probe, i.e.
-subject phrase, they cannot explain agreement attraction effects that are triggered by an distractor outside of the syntactic scope of the subject.
-Regardless, these effects can be explained in a framework where the source of the agreement attraction can placed on the trigger, i.e.
+subject phrase, they cannot explain agreement attraction effects that are triggered by a distractor outside of the syntactic scope of the subject.
+Regardless, these effects may be explained in a framework where the source of the agreement attraction is placed on the trigger, i.e.
 verb.
 @Badecker2007 suggests that a process where the subject is retrieved from the memory plays a role in agreement attraction effects as well [see as well @Wagers2009].
-Building on the work in cue-based retrieval mechanism [@Gordon2001; @Lewis2005; @Lewis2006 among others], they argued that when spakers reach the verb, they try to retrieve the subject using certain features (cues) that essentially marks the *subjecthood*.
-Thus, any element that matches (or partially mathces) with the cues in use may cause agreement attraction regardless of their position or syntactic relation to the subject.
+Building on the work in cue-based retrieval mechanism [@Gordon2001; @Lewis2005; @Lewis2006 among others], they argued that when speakers reach the verb, they try to retrieve the subject using certain features (cues) that essentially marks the *subjecthood*.
+Thus, any element that matches (or partially matches) with the cues in use may cause agreement attraction regardless of their position or syntactic relation to the subject.
 Going back to \autoref{E2}, it is expected, then, for an object which shares features like being preverbal, being a noun phrase, ability to bear agreement with a subject to trigger agreement attraction.
@@
 
-On the other hand, cue-based retrieval models successfully predicts the the grammaticality asymmetry as shown by @Dillon2013 in an ACT-R simulation as well as numerous studies in self-paced reading, eye-tracking, and ERP studies [@Wagers2009; @Tucker2010; @Tanner2014; @Lago2015 among others].
+On the other hand, cue-based retrieval models successfully predict the grammaticality asymmetry as shown by @Dillon2013 in an ACT-R simulation as well as numerous studies in self-paced reading, eye-tracking, and ERP studies [@Wagers2009; @Tucker2010; @Tanner2014; @Lago2015 among others].
 This success was due to their replacement of source of the attraction.
-According to cue-based retrieval models, the probe, verb, presents certain cues to retrieve an NP with matching features in agreement.
-When features of the grammatical controller of the verb does not *fully* match with the cues, no single NP will be satisfying the *agreement*.
+According to cue-based retrieval models, the probe, verb, present certain cues to retrieve an NP with matching features in agreement.
+When features of the grammatical controller of the verb do not *fully* match with the cues, no single NP will be satisfying the *agreement*.
 Thus, another NP in the clause can match with cues presented by the VP, such as its case, syntactic position, grammatical number.
 Thus, if there is no *retrieval cue* in the first place, i.e.
-the verb is nor marked plural, there will be no need for partial match.
+the verb is not marked plural, there will be no need for partial match.
 
@@
 
-Before discussing the experiments, we will touch upon the mechanisms that we utilize in the experiments: optional plural agreement, relative clause structure, and syncretism between possessive and accusative.
+Before discussing the experiments, I will touch upon the mechanisms that I utilize in the experiments: optional plural agreement, relative clause structure, and syncretism between possessive and accusative.
 
@@
 However, Turkish plural agreement is optional in third person plurals as shown in \autoref{TB1} and \autoref{TB2}.
-The other characteristics of Turkish plural agreement is that, the nominal and verbal plural marking is done by the same morpheme *-lAr*\footnote{The convention of using an uppercase A is to show that the morpheme can surface as either \textit{-ler} or \textit{-lar} according to the previous vowel due to the vowel harmony reasons.}.
+The other important characteristicc of Turkish plural agreement is the fact that the nominal and verbal plural marking is done by the same morpheme *-lAr*\footnote{The convention of using an uppercase A is to show that the morpheme can surface as either \textit{-ler} or \textit{-lar} according to the previous vowel due to the vowel harmony reasons.}.
 
@@
 
-Final characteristics that interests us in this paper is the morphological syncretism between the accusative case and possessive suffix in Turkish.
-When the possessive case is attached to a nominal stem that ends with a consonant, it is pronounced as \textit{-I}, which is exactly how accusative case is also pronounced in the same environment in Turkish.
+Final characteristics that interest us in this paper is the morphological syncretism between the accusative case and possessive suffix in Turkish.
+When the possessive case is attached to a nominal stem that ends with a consonant, it is pronounced as \textit{-I}, which is exactly how the accusative case is also pronounced in the same environment in Turkish.
 However, the ambiguity is immediately resolved when they follow a nominal stem that ends with a vowel.
-In the latter environment, the accussative case surfaces as *-yI* whereas the possessive surfaces as *-sI(n)*\footnote{The final \textit{n} is only surfaces when any other morphemes follows the possessive suffix.
+In the latter environment, the accusative case surfaces as *-yI* whereas the possessive surfaces as *-sI(n)*\footnote{The final \textit{n} only surfaces when any other morphemes follow the possessive suffix.
 Otherwise, it surfaces as \textit{-sI}} as shown in \autoref{TB6}-\autoref{TB9}.
@@
 
-In this study, we examine the question of whether agreement attraction is due to the shallow parsing that mainly depends on the memory of plural morpheme *-lAr* and matching the verbal plural morpheme with the nominal plural morpheme.
-
-First of all, we investigate the effects of ambiguous suffix with Experiment 1, which is a replication of @Lago2018.
+In this study, I examine the question of whether agreement attraction is due to the shallow parsing that mainly depends on the memory of plural morpheme *-lAr* and matching the verbal plural morpheme with the nominal plural morpheme.
+
+First of all, I investigate the effects of ambiguous suffix with Experiment 1, which is a replication of @Lago2018.
 @Lago2018 makes use of genitive-possessive structures in the subject position, in which the possessive-marked noun is the head of the noun phrase which acts as the grammatical agreement controller, and the genitive noun serves as a potential attractor as in \autoref{Lagoitem}.
@@
 However, the interpretation of their findings may be a result of the fact that non-subjecthood cues originate from their use of morphologically ambiguous forms of the possessive.
-In the possessive forms that are used, all the head nouns in their stimuli are ambigiuous between possessive and accusative.
+In the possessive forms that are used, all the head nouns in their stimuli are ambiguous between possessive and accusative.
 
@@
 Meanwhile, the genitive noun may sometimes have been erroneously identified as the controller during shallow processing because genitives are more likely to act as agreement controllers than accusatives.
-In order to check this effect, we have replicated @Lago2018 in Experiment 1.
-We have used different head nouns which ends with a vowel to differentiate between the accusative case and the possessive suffix, i.e.
+In order to check this effect, I have replicated @Lago2018 in Experiment 1.
+I have used different head nouns which ends with a vowel to differentiate between the accusative case and the possessive suffix, i.e.
 *taksici* (taxi driver) instead of *vokalist* in \autoref{Lagoitem}.
@@
 The syntactic depth has not changed, the number information of the head and distractor have not changed.
-Slight differences may be expected since we have changed some items which can be found in Appendix 1, and this situation can create a erroneous number information to be used in the marking process.
-
-As for cue-based retrieval models, we should expect a lower agreement attraction effect in this replication.
-This predictions stems from the fact that possibility of erroneous representation of features of head noun is now lower due to our efforts to differentiate between the accusative case and the possessive marking.
-@Lago2018 argues that due to the subjecthood information provided by genitive case, there is an effect of agreement attraction.
-We eliminate the possibility of possible non-subjecthood clues given by the form that is shared by the accusative case and the posessive suffix.
-
-Within the shallow processing model, we would also expect a no change in the status of agreement attraction.
-In our account of shallow processing, we argue that when the comprehenders reach the verb and saw plural morpheme, they engage in matching mechanism where they try to match the verbal plural morpheme with a previous nomimal plural morpheme.
+Slight differences may be expected since I have changed some items which can be found in Appendix 1, and this situation can create erroneous number information to be used in the marking process.
+
+As for cue-based retrieval models, I should expect a lower agreement attraction effect in this replication.
+This prediction stems from the fact that the possibility of erroneous representation of features of the head noun is now lower due to  my efforts to differentiate between the accusative case and the possessive marking.
+@Lago2018 argues that due to the subjecthood information provided by the genitive case, there is an effect of agreement attraction.
+I eliminate the possibility of possible non-subjecthood clues given by the form that is shared by the accusative case and the possessive suffix.
+
+Within the shallow processing model, I would also expect a no change in the status of agreement attraction.
+In  my account of shallow processing, I argue that when the comprehenders reach the verb and saw plural morpheme, they engage in a matching mechanism where they try to match the verbal plural morpheme with a previous nominal plural morpheme.
 An agreement attraction, then, is not a result of a partial matching or a representational error of number feature; instead, it is the result of a state of memory in which comprehenders misremember either the existence of the nominal plural morpheme or the place of the nominal plural morpheme as stated in the MPT model of the agreement attraction within shallow processor within \autoref{model1}, \autoref{model2}, \autoref{model3}\footnote{Author here wishes he knew more latex to do the MPT tree more neat.}.
@@
 \end{tikzpicture}
-\caption{xd}
+\caption{Proposed multinomial processing tree of how people judge sentences in a agreement attraction task}
 \label{model1}
@@
 \end{tikzpicture}
-\caption{xd}
+\caption{The Continuation of the proposed MPT with regards to the items which do not have an attractors with overt plural morphology but do have a plural marked verbs.}
 \label{model2}
@@
 \end{tikzpicture}
-\caption{xd}
+\caption{The Continuation of the proposed MPT with regards to the items who have attractors with overt plural morphology and  plural marked verbs.}
 \label{model3}
@@
 
-In our second experiment, we investigate the predictions made from our model using a verbal plural morpheme within a distractor relative clause.
-As mentioned earlier, the verbal plural morpheme in Turkish is exactly the same with the nominal plural with regards to its stress, its behaviour, and its form: *-lAr*.
-Since Turkish relative clauses are essentially nominals due the nomilization process, they behave exactly like other nominals within the sentence [@Goksel2004; @Taylan2015].
+In  my second experiment, I investigate the predictions made from  my model using a verbal plural morpheme within a distractor relative clause.
+As mentioned earlier, the verbal plural morpheme in Turkish is exactly the same as the nominal plural with regards to its stress, its behavior, and its form: *-lAr*.
+Since Turkish relative clauses are essentially nominals due to the nominalization process, they behave exactly like other nominals within the sentence [@Goksel2004; @Taylan2015].
 They can be marked with cases, plural agreement and they can have postpositions that any nominal also can.
 This syntactic formation enables us to question how shallow people process, how much syntactic information is relevant, or how perfectly people encode the features of the elements of the sentence.
-In our experiment 2, we have used items in which the referential head noun of the subject is modified with a single-word relative clause as in \autoref{ouritem1}.
+In  my experiment 2, I have used items in which the referential head noun of the subject is modified with a single-word relative clause as in \autoref{ouritem1}.
 
@@
 
-Within the framework of percolation theories, we expect a harsh decline in the agreement attraction effects\footnote{Discussion regarding to the how and where relative clauses adjoined is omited due to the scope of the paper.
+Within the framework of percolation theories, I expect a harsh decline in the agreement attraction effects\footnote{Discussion with regards to how and where relative clauses adjoined is omitted due to the scope of the paper.
 However, it should be clear that a late insertion analysis where the relative clauses are actually above the head noun would yield different results.
 In this paper, I assume that modifiers like relative clauses are within the noun phrase, which deems them \textit{syntactically} deeper placed in the hierarchical three than the possessee.}.
-The reason for this expected decline is the fact that relative clauses being relative *deeper* in the hierarchical structure than the possessee of genitive-posessive structure.
-
-As for cue-based retrieval models, we would expect an agreement attraction quite similar to the one that we originally have in @Lago2018.
-The reason for this expected agreement attraction is the fact that apart from having a verbal root, the relative clauses and nomials are behave exactly the same in terms of *nounnness*.
+The reason for this expected decline is the fact that relative clauses being relative *deeper* in the hierarchical structure than the possessee of genitive-possessive structure.
+
+As for cue-based retrieval models, I would expect an agreement attraction quite similar to the one that I originally have in @Lago2018.
+The reason for this expected agreement attraction is the fact that apart from having a verbal root, the relative clauses and nominals behave exactly the same in terms of *nounness*.
 Like nominals, nominalized structures first marked with plural and then with the case or possessive suffix.
-From this aspective, it seems like there should be no difference.
+From this perspective, it seems like there should be no difference.
 However, one may argue that the features related to the verbal and nominal can be encoded differently.
-Thus, there will no partial match at any time given due to the fact that verbal plural morpheme at the main verb does specify cues for specific type of plural marking.
+Thus, there will no partial match at any time given due to the fact that verbal plural morpheme at the main verb does specify cues for a specific type of plural marking.
 One other question that may arise from this structure is that whether or not the parts of already-formed dependencies can feed the following dependency resolution.
 In other words, the verbal plural morpheme *-lar* on *dövdükleri* in \autoref{ouritem1} is already a trigger of a cue retrieval process.
-And, when it is merged with the nominal head *çocuk*, there is a formed semantic meaning that is  "a group of people have beaten a kid."  However, this *suggesstion* assumes that relative clauses are formed at the very moment.
-Moreover, we also need to assume that after forming a relative clause they are unreachable, meaning that they do not contribute to the processing of the sentnece, anymore.
-
-Lastly in our extremely shallow processing model, we would expect a significant effect of agreement attraction.
-Due to one of the writers inability to *run the numbers* and *form the mpt trees in time*, this part unfortunately does not go beyond than a verbal argumentation.
-The reason we wait a significant effect of agreement is due to the fact that upon the agreement process is driven by the faulty memory of the place of the plural morpheme and uneducated guessing.
+And, when it is merged with the nominal head *çocuk*, there is a formed semantic meaning that is  "a group of people has beaten a kid."  However, this *suggestion* assumes that relative clauses are formed at the very moment.
+Moreover, I also need to assume that after forming a relative clause they are unreachable, meaning that they do not contribute to the processing of the sentence, anymore.
+
+Lastly, in  my extremely shallow processing model, I would expect a significant effect of agreement attraction.
+Due to one of the writers' inability to *run the numbers* and *form the mpt trees in time*, this part---unfortunately---does not go beyond than a verbal argumentation.
+The reason I expect a significant effect of the agreement attraction is due to the fact that upon the agreement process is driven by the faulty memory of the place of the plural morpheme and uneducated guessing.
 Since the parsing is shallow, comprehenders do not engage in perfect attribution of the features, thus having a somewhat blurry representation behind.
-We expect for this behaviour to be omnipresent in other agreement attraction phenomenon that has been showed, as well as in @Lago2018 and in our replication of it.
-Therefore, there is no reason to have to anything to be different in experiment 2.
+I expect this behavior to be omnipresent in other agreement attraction phenomenon that has been shown, as well as in @Lago2018 and in  my replication of it.
+Therefore, there is no reason to have anything to be different in experiment 2.
 
@@
 
-However, our initial hypothesis postulates that participants engage in shallow processing, which results in a situation in which not only the genitive case but also the possessive case plays a significant role in delivering the case information.
+However,  my initial hypothesis postulates that participants engage in shallow processing, which results in a situation in which not only the genitive case but also the possessive case plays a significant role in delivering the case information.
 None of the experimental items in @Lago2018 have a head noun which ends with a vowel; thus, all of the possessive markers are morphologically and phonologically ambiguous between the accusative case and the possessive.
-Unlike genitive case, it is extremely rare for the accusative case to appear on the head noun of the subject, which only occurs in raising predicates as in \autoref{dsm}.
+Unlike the genitive case, it is extremely rare for the accusative case to appear on the head noun of the subject, which only occurs in raising predicates as in \autoref{dsm}.
 
@@
 
-In order to test this hypothesis, we have replicated the experiment of @Lago2018 with modified items, in which the possessive is not ambiguous with the accusative case.
-We tried to be as faithful as possible to the original sentences while also trying to make the sentences as plausable as possible.
-We keep the semantic relation between the head noun and the controller the same with what has been described in @Lago2018, which is either a relation regarding profession or a service that is given by the head noun for the possessor.
+In order to test this hypothesis, I have replicated the experiment of @Lago2018 with modified items, in which the possessive is not ambiguous with the accusative case.
+I tried to be as faithful as possible to the original sentences while also trying to make the sentences as plausible as possible.
+I keep the semantic relation between the head noun and the controller the same with what has been described in @Lago2018, which is either a relation regarding profession or a service that is given by the head noun for the possessor.
 A set of sentences are exemplified below.
@@
 
-As seen in the examples, unlike @Lago2018's experimental items, all of our items bear the *-sI* possessive marker instead of the ambiguous *-I* marker.
-As for the filler items, we could not use or modify the original experiment items since the fillers of the original study were not online.
-We have used two types filler sentences: grammatical sentences in which the verb bears plural agreement (\autoref{fillera}), and ungrammatical sentences in which the verb does not bear plural agreement (\autoref{fillerb}).
-We wanted to nullify a possible strategy by the participants where they associate the sentence-final morpheme directly with the acceptability of the sentence.
-And we also wanted to eliminate the possibility of participants disregarding other elements in the sentences while answering the questions we ask right after the sentence.
+As seen in the examples, unlike @Lago2018's experimental items, all of  my items bear the *-sI* possessive marker instead of the ambiguous *-I* marker.
+As for the filler items, I could not use or modify the original experiment items since the fillers of the original study were not online.
+I have used two types of filler sentences: grammatical sentences in which the verb bears plural agreement (\autoref{fillera}), and ungrammatical sentences in which the verb does not bear plural agreement (\autoref{fillerb}).
+I wanted to nullify a possible strategy by the participants where they associate the sentence-final morpheme directly with the acceptability of the sentence.
+And I also wanted to eliminate the possibility of participants disregarding other elements in the sentences while answering the questions I ask right after the sentence.
 
@@
 One hundred and seven Turkish speakers were recruited from Bogazici University in İstanbul.
-We did not collect participants' knowledge of other languages; however, we verified that Turkish is their native language and that they predominantly use it in their daily lives.
+I did not collect participants' knowledge of other languages; however, I verified that Turkish is their native language and that they predominantly use it in their daily lives.
 In the experiments, participants were asked to judge the acceptability of experimental and filler sentences in Turkish.
 All of the sentences were presented one word at a time in the center of the screen for 500 ms per word unlike @Lago2018 and @Wagers2009, in which the duration was 300 ms per word.
-The experiment was run on a web-based platform titled the Ibex Farm, and all of the documentation can be found on our github page.
+The experiment was run on a web-based platform titled the Ibex Farm, and all of the documentation can be found on  my Github page:\url{https://github.com/utkuturk/AgreementAttraction_Experiment}.
 
@@
 Each trial after the practice items started with a blank screen, followed by a flash of single words in the middle of the screen.
-After the sentence, they were asked a grammaticality judgment questins (Was the sentence you read was natural to you?) where they need to press P for *no* and press Q for *yes*.
-In the experiment, every participant saw 40 experimental item that is latin-squared and 40 fillers.
+After the sentence, they were asked a grammaticality judgment questions (Was the sentence you read was natural to you?) where they need to press P for *no* and press Q for *yes*.
+In the experiment, every participant saw 40 experimental item that is Latin-squared and 40 fillers.
 
@@
 Participants that could not exceed the threshold of 0.25 difference in *yes* answer between the condition (c) and (d), namely Ungrammatical, SG attractor and Grammatical, SG attractor, were excluded.
-We performed an analysis by fitting linear mixed-effect modelts to our data, controlling for vowel ending, plural attractor, grammaticality and their interactions.
-Models were fit using bernoulli distribution with probit link function and 95\% confidence intervals.
+I performed an analysis by fitting linear mixed-effect models to  my data, controlling for vowel ending, plural attractor, grammaticality and their interactions.
+Models for responses were fit using Bernoulli distribution with probit link function and 95\% confidence intervals.
+Models for response times were fit using Lognormal distribution.
 
@@
 As seen in the figure, `r round(as.numeric(avg_exp[3,6]), digits = 2)`% of the sentences with plural attractors and a singular verb were accepted by the participants, in line with the findings of @Lago2018.
-We also see a number attraction rate of `r round(as.numeric(avg_exp[3,6]), digits = 2)-round(as.numeric(avg_exp[4,6]), digits = 2)`% which was also observed in @Lago2018 with close results.
-
-In Figure \@ref(fig:exp1ResponseModelPlot), we clearly see the effects of ungrammaticality and the interaction between the ungrammaticality and plural attractor.
-We see that, vowel ending is not significant even though it has negative effect.
-Thus, we may say that differentiating between the accusative case and the possessive suffix has cause a reduction in the effect of the agreement attraction.
-The results also shows that when the attractor is plural, people have a high tendency to find the sentence grammatical.
+I also see a number attraction rate of `r round(as.numeric(avg_exp[3,6]), digits = 2)-round(as.numeric(avg_exp[4,6]), digits = 2)`% which was also observed in @Lago2018 with close results.
+
+In Figure \@ref(fig:exp1ResponseModelPlot), I clearly see the effects of ungrammaticality and the interaction between the ungrammaticality and plural attractor.
+I see that the vowel ending is not significant even though it has a negative effect.
+Thus, I may say that differentiating between the accusative case and the possessive suffix has caused a reduction in the effect of the agreement attraction.
+The results also show that when the attractor is plural, people have a high tendency to find the sentence grammatical.
 
@@
 
-```
-
-```{r exp1ResponseModelPlot, fig.height = 2.5, fig.width = 6, fig.cap="log-odd Estimates and 95% credible intervals for the regression coefficients."}
+fname_exp3_responses <- "../workspace_exp1/model_responses_rt"
+
+m_rts <- brm(RT ~ cEndsInVowel * cUngrammatical * cAttractorPlural + 
+                                 (cUngrammatical * cAttractorPlural + 1| subject) +
+                                 (cUngrammatical * cAttractorPlural + 1| item),
+                   data = df_merged_nofillers,
+                   family = lognormal(),
+                   file = fname_exp3_responses, 
+                   chains = n_chains, cores = n_cores, iter = n_iter)
+
+```
+
+```{r exp1ResponseModelPlot, fig.height = 2.5, fig.width = 6, fig.cap="log-odd Estimates and 95% credible intervals for the regression coefficients in Accuracy."}
 
@@
 
-p_m_response <- create_model_coefs_plot(m_responses, map_names = contrast_names)
+p_m_response <- stanplot(m_responses, pars = "^b_c" , type="areas")
 p_m_response <- p_m_response + xlab("Estimate (log-odds)")
@@
 
-In Figure \@ref(fig:exp1AvgRTs), we see that average response times are significantly higher than the those of @Lago2018.
-Again, these results shows the effect of disambiguation of the possessive suffix from the accusative case has surfaced as the difficuilty in response and memory retrieval time.
-
-```{r exp1AvgRTs, fig.height=2.5, fig.width = 6, fig.cap="Average response times for our replication and Lago et. al. (2018)"}
+```{r exp1ResponseTimeModelPlot, fig.height = 2.5, fig.width = 6, fig.cap="log-odd Estimates and 95% credible intervals for the regression coefficients in Reading Times."}
+
+p_m_rt <- stanplot(m_rts, pars = "^b_c" , type="areas")
+p_m_rt <- p_m_rt + xlab("Estimate (log-odds)")
+print(p_m_rt)
+
+```
+
+In Figure \@ref(fig:exp1AvgRTs), I see that average response times are significantly higher than the those of @Lago2018.
+I also see it in \@ref(exp1ResponseTimeModelPlot), since **b_cEndsinVowel** indicates whether or not it is Experiment 1 or Experiment from @Lago2018, i.e.
+distractors in items in @Lago2018 ends with a consonant, while ours ends in a vowel.
+Again, these results show the effect of disambiguation of the possessive suffix from the accusative case has surfaced as the difficulty in response and memory retrieval time.
+
+```{r exp1AvgRTs, fig.height=2.5, fig.width = 6, fig.cap="Average response times for  my replication and Lago et. al. (2018)"}
 
@@
 
-The results follow from what a cue-based model would predict: slightly lower agreement attraction.
-However, these results can also be a result of a badly formed filler sentences which are shown with purple line.
-Participants may be biased towards saying no since most of the experimental items being ungramatical.
-However, this can also be statistical *miss* since we may accidentally have a group such as this one.
+Experiment 1 found number attraction effects, like also attested in @Lago2018, and also found a significant effect of form ambiguity of possessive and an interaction of plural attractor with ungrammaticality in response times.
+Illusionary agreement of the verb with the plural attractor was more than the singular attractor.
+In addition to what has been discussed by @Avetisyan2019.
+this results also show that not only the case itself but also the form of the case can affect the response times.
+
+In the previous sections, I have predicted that with an assumed mechanism where people do take the clues from the form of the plural morpheme itself and have a strategy based on matching the plural morphemes, I would expect no change with regards to the agreement attraction effects.
+I also should not expect increasing response times when an irrelevant morpheme for the mechanism I assume.
+
+However, I see that response times have changed drastically when the suffixes are dismabiguated.
+It is clear from the Figure \@ref(fig:exp1AvgRTs), when people are prompted to judge the sentence, they have difficulty in resolving and back-tracking the dependencies of the sentence even though nothing relevant to the plural morpheme and its host word has changed.
+
+The results follow from what a cue-based model would predict: slightly lower agreement attraction and increased response time.
+Due to the disambiguation between the accusative case and the possessive suffix, I speculated that the features related to the *non-subjecthood* of the head of the subject would not surface falsely in  my replication.
+With more clearly formed genitive-possessive structures, participants do not have an easy time to partially match the cues with the phrases.
+This situation stems from the idea proposed by @Lago2018 with regards to the effects of the cases on numeral agreement attraction.
+She argues that the frequency of the case being used in the subject position affects the agreement attraction effects in a positive manner.
+Since the accusative case is rarely used in Turkish, I have argued that it may give *wrong* clues an enable the distractors to even distract more.
+Yet, with clearly marked possessive suffix, I see that these enabling nature of the genitive possessive structure is eliminated, which is also shown in @Avetisyan2019.
+
+However, these results can also be a result of badly formed filler sentences which are shown with a purple line.
+Participants may be biased towards saying no since most of the experimental items being ungrammatical.
+However, this can also be statistical *miss* since I may accidentally have a group such as this one.
 However, the visible effect of vowel ending and response time suggest that people do indeed care more than only the retrieval of plural morpheme *-lar* and its place.
-This results go against what we have predicted for the Marking and Morphing model and our shallow processing model.
-However, the existence of extremely close degree of agremeent attraction effects and non-significant nature of the effect of the vowel ending indicate that we cannot readily discard other explanations.
+
+These results go against what I have predicted for the Marking and Morphing model as well.
+Due to the no extreme semantic change in the experimental (*Marking*) and no change in the structural relations among the genitive-possessive constructions (*Morphing*), there should be no difference in agreement attraction.
+
+However, the existence of an extremely close degree of agreement attraction effects and non-significant nature of the effect of the vowel ending indicates that I cannot readily discard other explanations.
+Another reason for not jumping to the conclusion with percolation models can be related to the number of participants @Lago2018 have included in their study [see @Vasishth2018].
 
@@
 
-Having discussed the replication study of @Lago2018, we have shown that results favor the cue-based models, especially with the effect of disambiguated possessive suffix on response times.
-However, due to the extremely similar effects on agreement attraction we can still entartain shallow processing mechanism as explained in \autoref{model1}, \autoref{model2}, and \autoref{model3}.
-Since we argue that the agreement attraction is a product of memory state in which comprehenders do not have an exact memory of the place of the plural morpheme mainly, we conducted an experiment where the distractor with the plural morpheme in on the relative clause.
-
-The study consists of an speeded acceptability judgment experiment in the web-based platform Ibex Farm.
-In the experiment, we test whether or not speakers utilize even more shallow parser than what is stipulated by @Lago2018 and our replication of @Lago2018 Experiment 2.
-This was investigated using syntactic structures similar to @Lago2018 materials, in which we have opted out the Genitive Constructuion (GC) for Relative Clause construction (RCC) as a distractor.
-In Turkish, like GC, relative clause in RCC precedes the head noun, and length-wise Turkish relative clauses can consist of only one word and the rest can be dropped.
-Turkish allows us to use RCCs as distractors in the same place because Turkish plural morpheme in verbal domain and nominal domain are the same: *-lAr*.
-Both of them react similarly in the same phonological environments, and they also exhibit same stress patterns.
-
-In the experimental items, the distractor RC and the matrix verb had four configurations in which the number morpheme on the RCC (*plural* vs.
+Having discussed the replication study of @Lago2018, I have shown that results favor the cue-based models, especially with the effect of disambiguated possessive suffix on response times.
+However, due to the extremely similar effects on agreement attraction, I can still entertain shallow processing mechanism as explained in \autoref{model1}, \autoref{model2}, and \autoref{model3}.
+Since I argue that the agreement attraction is a product of memory state in which comprehenders do not have an exact memory of the place of the plural morpheme mainly, I conducted an experiment where the distractor with the plural morpheme in on the relative clause.
+
+The study consists of a speeded acceptability judgment experiment in the web-based platform Ibex Farm.
+In the experiment, I test whether or not speakers utilize even more shallow parser than what is stipulated by @Lago2018 and  my replication of @Lago2018 Experiment 2.
+This was investigated using syntactic structures similar to @Lago2018 materials, in which I have opted out the Genitive Construction (GC) for Relative Clause construction (RCC) as a distractor.
+In Turkish, like GC, the relative clause in RCC precedes the head noun, and length-wise Turkish relative clauses can consist of only one word and the rest can be dropped.
+Turkish allows us to use RCCs as distractors in the same place because Turkish plural morpheme in the verbal domain and nominal domain are the same: *-lAr*.
+Both of them react similarly in the same phonological environments, and they also exhibit the same stress patterns.
+
+In the experimental items, the distractor RC and the matrix verb had f my configurations in which the number morpheme on the RCC (*plural* vs.
 *singular* marked RC verb) and matrix verb (*grammatical* vs.
@@
 
-As for the experiment, we have used same type of fillers with the Experiment 1 in order to tackle with two possible strategies that can be utilized by the participants: (i) deeming the sentence acceptable when the matrix verb is singular and (ii) deeming most of the sentences unacceptable when the matrix verb is plural.
-To tackle with the first type of strategy, we have used a sentence where the object is not marked with accusative and it is not in immediately pre-verbal position as in \autoref{filler1a}.
-The idea was to have a singular matrix verb in an ungrammtical sentence where the ungrammaticality does not stem from the local elements.
-As for the other strategy we have used pro-drop charactheristics of Turkish and made the first noun phrase with a relative clause an object as in \autoref{filler1b}.
+As for the experiment, I have used the same type of fillers with the Experiment 1 in order to tackle with two possible strategies that can be utilized by the participants: (i) deeming the sentence acceptable when the matrix verb is singular and (ii) deeming most of the sentences unacceptable when the matrix verb is plural.
+To tackle with the first type of strategy, I have used a sentence where the object is not marked with accusative and it is not in an immediately pre-verbal position as in \autoref{filler1a}.
+The idea was to have a singular matrix verb in an ungrammatical sentence where the ungrammaticality does not stem from the local elements.
+As for the other strategy I have used pro-drop characteristics of Turkish and made the first noun phrase with a relative clause an object as in \autoref{filler1b}.
 The idea behind is that the plural agreement on the matrix verb is resolved with a dropped subject instead of the first noun phrase with a relative clause.
-Every participant saw 40 experimental item that is latin-squared and 40 fillers.
+Every participant saw 40 experimental item that is Latin-squared and 40 fillers.
 
@@
 Eighty Turkish speakers were recruited from Bogazici University in İstanbul.
-The procedure was exatcly the same as the Experiment 1.
-The participants in this experiment were completely different than the Experiment one.
+The procedure was exactly the same as Experiment 1.
+The participants in this experiment were completely different from Experiment 1.
 
@@
 
-Every experimental item from both experiments (this experiment and the Experiment 1) is included in the analysis.
+Every experimental item from both experiments (this experiment and Experiment (1) is included in the analysis.
 Participants that could not exceed the threshold of 0.25 difference in *yes* answer between the condition (c) and (d), namely Ungrammatical, SG attractor and Grammatical, SG attractor, were excluded.
-We performed an analysis by fitting linear mixed-effect modelts to our data, controlling for vowel ending, plural attractor, grammaticality and their interactions.
-Models were fit using bernoulli ditribution with probit link function and 95\% confidence intervals.
+I performed an analysis by fitting linear mixed-effect models to  my data, controlling for vowel ending, plural attractor, grammaticality and their interactions.
+Models were fit using Bernoulli distribution with probit link function and 95\% confidence intervals.
 
@@
 
-It is clear from Figure \@ref(fig:exp2AvgResponse) that in the condition (c) where we expect an agreement attraction, participants find as unacceptable as the condition (d) with singular attractor, singular head noun, and plural matrix verb.
-While we do not see any agreement attraction (`r round(as.numeric(avg_exp2[7,6]), digits = 2)`%), we also see a more firm analysis of the ungrammatical sentence with singular matrix verb ((`r round(as.numeric(avg_exp2[7,6]), digits = 3)`%)).
+It is clear from Figure \@ref(fig:exp2AvgResponse) that in the condition (c) where I expect an agreement attraction, participants find as unacceptable as the condition (d) with singular attractor, singular head noun, and plural matrix verb.
+While I do not see any agreement attraction (`r round(as.numeric(avg_exp2[7,6]), digits = 2)`%), I also see a more firm analysis of the ungrammatical sentence with singular matrix verb ((`r round(as.numeric(avg_exp2[7,6]), digits = 3)`%)).
 
@@
 
-As for the estimates of coefficients in \@ref(fig:exp2ResponseModelPlot), we can conclude that there is a significant negative effect of plural morpheme on the relative clause, which means that it does not cause any agreement affects.
-Again, the effect of ungrammaticality that stems from the existence of plural morpeheme on the matrix verb is visible.
+As for the estimates of coefficients in \@ref(fig:exp2ResponseModelPlot), I can conclude that there is a significant negative effect of plural morpheme on the relative clause, which means that it does not cause any agreement affects.
+Again, the effect of ungrammaticality that stems from the existence of plural morpheme on the matrix verb is visible.
 The interaction between the plural morpheme on the attractor RC and the matrix verb is even higher than the sole effect of plural morpheme on the attractor RC.
@@
 
-```{r exp2AvgRTs, fig.height=2.5, fig.width = 6 ,fig.cap="Average response times for our replication and Experiment2"}
+```{r exp2AvgRTs, fig.height=2.5, fig.width = 6 ,fig.cap="Average response times for  my replication and Experiment2"}
 
@@
 
-Finally, the response times of the Experiment 2 is significantly lower than the Experiment 1 as seen from Figure \@ref(fig:exp2AvgRTs).
-The even lower response time in ungrammatical plural (condition c) shows that participants were extremely confident with their decision and did not had any issue with the dependency resolution.
+Finally, the response times of Experiment 2 is significantly lower than the Experiment 1 as seen from Figure \@ref(fig:exp2AvgRTs).
+The even lower response time in ungrammatical plural (condition c) shows that participants were extremely confident with their decision and did not have any issue with the dependency resolution.
 
@@
 
-These findings indicate that our hypothesis regarding the matching of the forms is not supported by the empirical evidence.
+These findings indicate that  my hypothesis regarding the matching of the forms is not supported by the empirical evidence.
 However, results in Experiment 2 points in a direction where the Marking and Morphing studies predicted in the first place.
@@
 
-We have shown that the agreement attraction effects cannot be explained by the extremely shallow processing mechanisms, at least with the implementaion we have proposed here.
-However, we also shown that findings from Experiment 1 and 2 was not enought the differentiate between two models that can explain agreement attraction: the Marking and Morphing and cue-based retrieval models.
+We have shown that the agreement attraction effects cannot be explained by the extremely shallow processing mechanisms, at least with the implementation I have proposed here.
+However, I also show that findings from Experiment 1 and 2 were not enough to differentiate between two models that can explain agreement attraction: the Marking and Morphing and cue-based retrieval models.
 While the findings of Experiment 1 favors the cue-based retrieval mechanism, Experiment 2 with the harsh decline in the effects of agreement attraction points to another horizon.
@@
 However, it can be an issue related to already-formed dependencies inability to be used in the memory process.
-One can argue that once the dependencies are formed and resolved, participants does not go back to them when another cue is set out.
+One can argue that once the dependencies are formed and resolved, participants do not go back to them when another cue is set out.
 

### 2019-06-14 Paper/AgreementAttraction.tex
without
proper mpt, with second experiment

@@
 \hypersetup{unicode=true,
-            pdftitle={Agreement Attraction},
-            pdfauthor={Utku Türk~\& Pavel Logacev},
+            pdftitle={Agreement Attraction in Turkish: Who let the -lAr out?},
+            pdfauthor={Utku Türk},
             pdfborder={0 0 0},
@@
 
-  \title{Agreement Attraction}
-    \author{Utku Türk\textsuperscript{1}~\& Pavel Logacev\textsuperscript{1}}
+  \title{Agreement Attraction in Turkish: Who let the -lAr out?}
+    \author{Utku Türk\textsuperscript{}}
     \date{}
@@
 \vspace{0.5cm}
-\textsuperscript{1} Boğaziçi University}
+\textsuperscript{} Boğaziçi University}
 \usepackage{csquotes}
@@
 \let\eachwordone=\textit
+\usepackage{geometry}
+\geometry{margin=2cm}
+\usepackage{libertine}
+\usepackage{libertinust1math}
+\usepackage[T1]{fontenc}
+\usepackage{fancyhdr}
+\pagestyle{fancy}
+\fancyhf{}
+\rhead{Türk}
+\lhead{Agreement Attraction in Turkish}
+\rfoot{\thepage}
 
@@
 
-\abstract{
-The comprehension of agreement within the elements of a sentence is known to fail.
-One of these comprehension errors is known as agreement attraction.
-Speakers may erroneously find a sentence in which the ``attractor'' agrees with the verb instead of the ``head'' of the subject.
-Data from typologically different languages and explanations from different frameworks shows that we are far from understanding by what the attraction is modulated.
-Some theories refer this phenomenon as a faulty representation of the number on the head of the subject phase whereas other theories argues that the attraction is due to an error in the access to the number of the subject.
-In this paper, we report two experiments exploring a possible explanation for agreement attraction: an extremely shallow processing.
-The first experiment is a replication of \textcite{Lago2018} where we changed the head of the subject in order to differentiate between the accusative case \emph{-I}.
-In the second experiment, we have used a relative clause which only consists of a plural marked verb as a distractor.
-Our results show that while people do indeed care more than just ``matching'' the forms of plural verbal.
-Either comprehenders have some sort of restriction to not use cues from verbs upon accessing the number of the plural morpheme or there is a syntactic reason for the number feature of plural morpheme to not ``percolate.''
-
-}
-
 \begin{document}
@@
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+\section*{Introduction}
+
+It has been observed that speakers generally fail to accurately comprehend agreement between elements in a sentence.
+One such comprehension error that is made has been deemed agreement attraction.
+Speakers may erroneously find a sentence in which the \enquote{attractor} agrees with the verb instead of the \enquote{head} of the subject.
+Data from typologically different languages and explanations from different frameworks show that I am far from understanding by what the attraction is modulated.
+Some theories refer this phenomenon as a faulty representation of the number on the head of the subject phase whereas other theories argue that the attraction is due to an error in the access to the number of the subject.
+In this paper, I report two experiments exploring another possible explanation for agreement attraction: an extreme shallow processing.
+The first experiment is a replication of \textcite{Lago2018} where I changed the head of the subject in order to differentiate between the accusative case \emph{-I}.
+In the second experiment, I have used a relative clause which only consists of a plural marked verb as a distractor.
+my results show that while people do indeed care more than just \enquote{matching} the forms of plural verbal.
+either comprehenders have some sort of restriction to not use cues from verbs upon accessing the number of the plural morpheme or there is a syntactic reason for the number feature of the plural morpheme to not \enquote{percolate.}
 
@@
 Agreement attractions are defined as instances of incorrect agreements of an element with a distractor that is not its grammatical controller.
-As in \autoref{E1}, the target of the agreement is the verb \emph{are}, the attracting distractor is \emph{bottles}, and the feature erroneously assesed is the number feature of the grammatical controller \emph{label}.
+As in \autoref{E1}, the target of the agreement is the verb \emph{are}, the attracting distractor is \emph{bottles}, and the feature erroneously assessed is the number feature of the grammatical controller \emph{label}.
 
@@
 One of the theoretical attempts to explain such phenomenon was Marking and Morphing Theories \autocites{Bock2001}[ among others]{Eberhard2005}.
-The reason it is called \emph{Marking} and \emph{Morphing} is because there is two possible explanation within the framework with regards to where and when the attraction occurs.
-First possibility is speaker (and/or comprehender) can erroneously create a semantic representation of the head with wrong number feature in the marking process in the marking process.
-Another possibility is that the attraction may arise from an interfering number feature of the attractor with the number feature of the highest noun phrase node in morphing process.
-During the this process, the speaker forms a final number value of the subject phrase, which is determined by each morpheme within the same phrase and their number information with particular weight.
-In morphing process, these other morphemes with number information may contaminate the final number value with perculation mechanism, which depends on the depth of the syntactic embedding.
-As the prediction goes, the more embedded an attractor is, the less attraction they trigger as shown in \textcite{Bock1992} in which authors shown that attractors within a relative clause trigger less agreement attraction in the production.
+The reason it is called \emph{Marking} and \emph{Morphing} is because there are two possible explanations within the framework with regards to where and when the attraction occurs.
+The first possibility is the speaker can erroneously create a semantic representation of the head with the wrong number feature in the marking process in the marking process.
+Another possibility is that the attraction may arise from an interfering number feature of the attractor with the number feature of the highest noun phrase node in the morphing process.
+During this process, the speaker forms a final number value of the subject phrase, which is determined by each morpheme within the same phrase and their number information with a particular weight.
+In the morphing process, these other morphemes with number information may contaminate the final number value with the percolation mechanism, which depends on the depth of the syntactic embedding.
+As the prediction goes, the more embedded an attractor is, the less attraction they trigger as shown in \textcite{Bock1992} in which authors show that attractors within a relative clause trigger less agreement attraction in the production.
 
-However, other studies shown that other preverbal elements, such as objects, object relative clauses, object clefts, and object questions, may trigger agreement attraction \autocites{Kimball1971}{Hartsuiker2001}{Franck2006}[ among others]{Franck2015}.
+However, other studies have shown that other preverbal elements, such as objects, object relative clauses, object clefts, and object questions, may trigger agreement attraction \autocites{Kimball1971}{Hartsuiker2001}{Franck2006}[ among others]{Franck2015}.
 In sentences like \autoref{E2}, the pronominal object \emph{hen} triggers and agreement attraction without being a part of the subject.
@@
 
-Since the Marking and Morphing theories put the source of the agreement attraction on the probe, i.e.~subject phrase, they cannot explain agreement attraction effects that are triggered by an distractor outside of the syntactic scope of the subject.
-Regardless, these effects can be explained in a framework where the source of the agreement attraction can placed on the trigger, i.e.~verb.
+Since the Marking and Morphing theories put the source of the agreement attraction on the probe, i.e.~subject phrase, they cannot explain agreement attraction effects that are triggered by a distractor outside of the syntactic scope of the subject.
+Regardless, these effects may be explained in a framework where the source of the agreement attraction is placed on the trigger, i.e.~verb.
 \textcite{Badecker2007} suggests that a process where the subject is retrieved from the memory plays a role in agreement attraction effects as well \autocite[see as well][]{Wagers2009}.
-Building on the work in cue-based retrieval mechanism \autocites{Gordon2001}{Lewis2005}[ among others]{Lewis2006}, they argued that when spakers reach the verb, they try to retrieve the subject using certain features (cues) that essentially marks the \emph{subjecthood}.
-Thus, any element that matches (or partially mathces) with the cues in use may cause agreement attraction regardless of their position or syntactic relation to the subject.
+Building on the work in cue-based retrieval mechanism \autocites{Gordon2001}{Lewis2005}[ among others]{Lewis2006}, they argued that when speakers reach the verb, they try to retrieve the subject using certain features (cues) that essentially marks the \emph{subjecthood}.
+Thus, any element that matches (or partially matches) with the cues in use may cause agreement attraction regardless of their position or syntactic relation to the subject.
 Going back to \autoref{E2}, it is expected, then, for an object which shares features like being preverbal, being a noun phrase, ability to bear agreement with a subject to trigger agreement attraction.
@@
 
-On the other hand, cue-based retrieval models successfully predicts the the grammaticality asymmetry as shown by \textcite{Dillon2013} in an ACT-R simulation as well as numerous studies in self-paced reading, eye-tracking, and ERP studies \autocites{Wagers2009}{Tucker2010}{Tanner2014}[ among others]{Lago2015}.
+On the other hand, cue-based retrieval models successfully predict the grammaticality asymmetry as shown by \textcite{Dillon2013} in an ACT-R simulation as well as numerous studies in self-paced reading, eye-tracking, and ERP studies \autocites{Wagers2009}{Tucker2010}{Tanner2014}[ among others]{Lago2015}.
 This success was due to their replacement of source of the attraction.
-According to cue-based retrieval models, the probe, verb, presents certain cues to retrieve an NP with matching features in agreement.
-When features of the grammatical controller of the verb does not \emph{fully} match with the cues, no single NP will be satisfying the \emph{agreement}.
+According to cue-based retrieval models, the probe, verb, present certain cues to retrieve an NP with matching features in agreement.
+When features of the grammatical controller of the verb do not \emph{fully} match with the cues, no single NP will be satisfying the \emph{agreement}.
 Thus, another NP in the clause can match with cues presented by the VP, such as its case, syntactic position, grammatical number.
-Thus, if there is no \emph{retrieval cue} in the first place, i.e.~the verb is nor marked plural, there will be no need for partial match.
+Thus, if there is no \emph{retrieval cue} in the first place, i.e.~the verb is not marked plural, there will be no need for partial match.
 
@@
 However, Turkish plural agreement is optional in third person plurals as shown in \autoref{TB1} and \autoref{TB2}.
-The other characteristics of Turkish plural agreement is that, the nominal and verbal plural marking is done by the same morpheme \emph{-lAr}\footnote{The convention of using an uppercase A is to show that the morpheme can surface as either \textit{-ler} or \textit{-lar} according to the previous vowel due to the vowel harmony reasons.}.
+The other important characteristicc of Turkish plural agreement is the fact that the nominal and verbal plural marking is done by the same morpheme \emph{-lAr}\footnote{The convention of using an uppercase A is to show that the morpheme can surface as either \textit{-ler} or \textit{-lar} according to the previous vowel due to the vowel harmony reasons.}.
 
@@
 
-Final characteristics that interests us in this paper is the morphological syncretism between the accusative case and possessive suffix in Turkish.
-When the possessive case is attached to a nominal stem that ends with a consonant, it is pronounced as \textit{-I}, which is exactly how accusative case is also pronounced in the same environment in Turkish.
+Final characteristics that interest us in this paper is the morphological syncretism between the accusative case and possessive suffix in Turkish.
+When the possessive case is attached to a nominal stem that ends with a consonant, it is pronounced as \textit{-I}, which is exactly how the accusative case is also pronounced in the same environment in Turkish.
 However, the ambiguity is immediately resolved when they follow a nominal stem that ends with a vowel.
-In the latter environment, the accussative case surfaces as \emph{-yI} whereas the possessive surfaces as \emph{-sI(n)}\footnote{The final \textit{n} is only surfaces when any other morphemes follows the possessive suffix.
+In the latter environment, the accusative case surfaces as \emph{-yI} whereas the possessive surfaces as \emph{-sI(n)}\footnote{The final \textit{n} only surfaces when any other morphemes follow the possessive suffix.
 Otherwise, it surfaces as \textit{-sI}} as shown in \autoref{TB6}-\autoref{TB9}.
@@
 
-In this study, we examine the question of whether agreement attraction is due to the shallow parsing that mainly depends on the memory of plural morpheme \emph{-lAr} and matching the verbal plural morpheme with the nominal plural morpheme.
+In this study, I examine the question of whether agreement attraction is due to the shallow parsing that mainly depends on the memory of plural morpheme \emph{-lAr} and matching the verbal plural morpheme with the nominal plural morpheme.
 
-First of all, we investigate the effects of ambiguous suffix with Experiment 1, which is a replication of \textcite{Lago2018}.
+First of all, I investigate the effects of ambiguous suffix with Experiment 1, which is a replication of \textcite{Lago2018}.
 \textcite{Lago2018} makes use of genitive-possessive structures in the subject position, in which the possessive-marked noun is the head of the noun phrase which acts as the grammatical agreement controller, and the genitive noun serves as a potential attractor as in \autoref{Lagoitem}.
@@
 Meanwhile, the genitive noun may sometimes have been erroneously identified as the controller during shallow processing because genitives are more likely to act as agreement controllers than accusatives.
-In order to check this effect, we have replicated \textcite{Lago2018} in Experiment 1.
-We have used different head nouns which ends with a vowel to differentiate between the accusative case and the possessive suffix, i.e.
+In order to check this effect, I have replicated \textcite{Lago2018} in Experiment 1.
+I have used different head nouns which ends with a vowel to differentiate between the accusative case and the possessive suffix, i.e.
 \emph{taksici} (taxi driver) instead of \emph{vokalist} in \autoref{Lagoitem}.
@@
 The syntactic depth has not changed, the number information of the head and distractor have not changed.
-Slight differences may be expected since we have changed some items which can be found in Appendix 1, and this situation can create a erroneous number information to be used in the marking process.
+Slight differences may be expected since I have changed some items which can be found in Appendix 1, and this situation can create erroneous number information to be used in the marking process.
 
-As for cue-based retrieval models, we should expect a lower agreement attraction effect in this replication.
-This predictions stems from the fact that possibility of erroneous representation of features of head noun is now lower due to our efforts to differentiate between the accusative case and the possessive marking.
-\textcite{Lago2018} argues that due to the subjecthood information provided by genitive case, there is an effect of agreement attraction.
-We eliminate the possibility of possible non-subjecthood clues given by the form that is shared by the accusative case and the posessive suffix.
+As for cue-based retrieval models, I should expect a lower agreement attraction effect in this replication.
+This prediction stems from the fact that the possibility of erroneous representation of features of the head noun is now lower due to my efforts to differentiate between the accusative case and the possessive marking.
+\textcite{Lago2018} argues that due to the subjecthood information provided by the genitive case, there is an effect of agreement attraction.
+I eliminate the possibility of possible non-subjecthood clues given by the form that is shared by the accusative case and the possessive suffix.
 
-Within the shallow processing model, we would also expect a no change in the status of agreement attraction.
-In our account of shallow processing, we argue that when the comprehenders reach the verb and saw plural morpheme, they engage in matching mechanism where they try to match the verbal plural morpheme with a previous nomimal plural morpheme.
+Within the shallow processing model, I would also expect a no change in the status of agreement attraction.
+In my account of shallow processing, I argue that when the comprehenders reach the verb and saw plural morpheme, they engage in a matching mechanism where they try to match the verbal plural morpheme with a previous nominal plural morpheme.
 An agreement attraction, then, is not a result of a partial matching or a representational error of number feature; instead, it is the result of a state of memory in which comprehenders misremember either the existence of the nominal plural morpheme or the place of the nominal plural morpheme as stated in the MPT model of the agreement attraction within shallow processor within \autoref{model1}, \autoref{model2}, \autoref{model3}\footnote{Author here wishes he knew more latex to do the MPT tree more neat.}.
@@
 
-In our second experiment, we investigate the predictions made from our model using a verbal plural morpheme within a distractor relative clause.
-As mentioned earlier, the verbal plural morpheme in Turkish is exactly the same with the nominal plural with regards to its stress, its behaviour, and its form: \emph{-lAr}.
-Since Turkish relative clauses are essentially nominals due the nomilization process, they behave exactly like other nominals within the sentence \autocites{Goksel2004}{Taylan2015}.
+In my second experiment, I investigate the predictions made from my model using a verbal plural morpheme within a distractor relative clause.
+As mentioned earlier, the verbal plural morpheme in Turkish is exactly the same as the nominal plural with regards to its stress, its behavior, and its form: \emph{-lAr}.
+Since Turkish relative clauses are essentially nominals due to the nominalization process, they behave exactly like other nominals within the sentence \autocites{Goksel2004}{Taylan2015}.
 They can be marked with cases, plural agreement and they can have postpositions that any nominal also can.
 This syntactic formation enables us to question how shallow people process, how much syntactic information is relevant, or how perfectly people encode the features of the elements of the sentence.
-In our experiment 2, we have used items in which the referential head noun of the subject is modified with a single-word relative clause as in \autoref{ouritem1}.
+In my experiment 2, I have used items in which the referential head noun of the subject is modified with a single-word relative clause as in \autoref{ouritem1}.
 
@@
 
-Within the framework of percolation theories, we expect a harsh decline in the agreement attraction effects\footnote{Discussion regarding to the how and where relative clauses adjoined is omited due to the scope of the paper.
+Within the framework of percolation theories, I expect a harsh decline in the agreement attraction effects\footnote{Discussion with regards to how and where relative clauses adjoined is omitted due to the scope of the paper.
 However, it should be clear that a late insertion analysis where the relative clauses are actually above the head noun would yield different results.
 In this paper, I assume that modifiers like relative clauses are within the noun phrase, which deems them \textit{syntactically} deeper placed in the hierarchical three than the possessee.}.
-The reason for this expected decline is the fact that relative clauses being relative \emph{deeper} in the hierarchical structure than the possessee of genitive-posessive structure.
+The reason for this expected decline is the fact that relative clauses being relative \emph{deeper} in the hierarchical structure than the possessee of genitive-possessive structure.
 
-As for cue-based retrieval models, we would expect an agreement attraction quite similar to the one that we originally have in \textcite{Lago2018}.
-The reason for this expected agreement attraction is the fact that apart from having a verbal root, the relative clauses and nomials are behave exactly the same in terms of \emph{nounnness}.
+As for cue-based retrieval models, I would expect an agreement attraction quite similar to the one that I originally have in \textcite{Lago2018}.
+The reason for this expected agreement attraction is the fact that apart from having a verbal root, the relative clauses and nominals behave exactly the same in terms of \emph{nounness}.
 Like nominals, nominalized structures first marked with plural and then with the case or possessive suffix.
-From this aspective, it seems like there should be no difference.
+From this perspective, it seems like there should be no difference.
 However, one may argue that the features related to the verbal and nominal can be encoded differently.
-Thus, there will no partial match at any time given due to the fact that verbal plural morpheme at the main verb does specify cues for specific type of plural marking.
+Thus, there will no partial match at any time given due to the fact that verbal plural morpheme at the main verb does specify cues for a specific type of plural marking.
 One other question that may arise from this structure is that whether or not the parts of already-formed dependencies can feed the following dependency resolution.
 In other words, the verbal plural morpheme \emph{-lar} on \emph{dövdükleri} in \autoref{ouritem1} is already a trigger of a cue retrieval process.
-And, when it is merged with the nominal head \emph{çocuk}, there is a formed semantic meaning that is \enquote{a group of people have beaten a kid.} However, this \emph{suggesstion} assumes that relative clauses are formed at the very moment.
-Moreover, we also need to assume that after forming a relative clause they are unreachable, meaning that they do not contribute to the processing of the sentnece, anymore.
+And, when it is merged with the nominal head \emph{çocuk}, there is a formed semantic meaning that is \enquote{a group of people has beaten a kid.} However, this \emph{suggestion} assumes that relative clauses are formed at the very moment.
+Moreover, I also need to assume that after forming a relative clause they are unreachable, meaning that they do not contribute to the processing of the sentence, anymore.
 
-Lastly in our extremely shallow processing model, we would expect a significant effect of agreement attraction.
-Due to one of the writers inability to \emph{run the numbers} and \emph{form the mpt trees in time}, this part unfortunately does not go beyond than a verbal argumentation.
-The reason we wait a significant effect of agreement is due to the fact that upon the agreement process is driven by the faulty memory of the place of the plural morpheme and uneducated guessing.
+Lastly, in my extremely shallow processing model, I would expect a significant effect of agreement attraction.
+Due to one of the writers' inability to \emph{run the numbers} and \emph{form the mpt trees in time}, this part---unfortunately---does not go beyond than a verbal argumentation.
+The reason I expect a significant effect of the agreement attraction is due to the fact that upon the agreement process is driven by the faulty memory of the place of the plural morpheme and uneducated guessing.
 Since the parsing is shallow, comprehenders do not engage in perfect attribution of the features, thus having a somewhat blurry representation behind.
-We expect for this behaviour to be omnipresent in other agreement attraction phenomenon that has been showed, as well as in \textcite{Lago2018} and in our replication of it.
-Therefore, there is no reason to have to anything to be different in experiment 2.
+I expect this behavior to be omnipresent in other agreement attraction phenomenon that has been shown, as well as in \textcite{Lago2018} and in my replication of it.
+Therefore, there is no reason to have anything to be different in experiment 2.
 
@@
 
-However, our initial hypothesis postulates that participants engage in shallow processing, which results in a situation in which not only the genitive case but also the possessive case plays a significant role in delivering the case information.
+However, my initial hypothesis postulates that participants engage in shallow processing, which results in a situation in which not only the genitive case but also the possessive case plays a significant role in delivering the case information.
 None of the experimental items in \textcite{Lago2018} have a head noun which ends with a vowel; thus, all of the possessive markers are morphologically and phonologically ambiguous between the accusative case and the possessive.
-Unlike genitive case, it is extremely rare for the accusative case to appear on the head noun of the subject, which only occurs in raising predicates as in \autoref{dsm}.
+Unlike the genitive case, it is extremely rare for the accusative case to appear on the head noun of the subject, which only occurs in raising predicates as in \autoref{dsm}.
 
@@
 
-In order to test this hypothesis, we have replicated the experiment of \textcite{Lago2018} with modified items, in which the possessive is not ambiguous with the accusative case.
-We tried to be as faithful as possible to the original sentences while also trying to make the sentences as plausable as possible.
-We keep the semantic relation between the head noun and the controller the same with what has been described in \textcite{Lago2018}, which is either a relation regarding profession or a service that is given by the head noun for the possessor.
+In order to test this hypothesis, I have replicated the experiment of \textcite{Lago2018} with modified items, in which the possessive is not ambiguous with the accusative case.
+I tried to be as faithful as possible to the original sentences while also trying to make the sentences as plausible as possible.
+I keep the semantic relation between the head noun and the controller the same with what has been described in \textcite{Lago2018}, which is either a relation regarding profession or a service that is given by the head noun for the possessor.
 A set of sentences are exemplified below.
@@
 
-As seen in the examples, unlike \textcite{Lago2018}'s experimental items, all of our items bear the \emph{-sI} possessive marker instead of the ambiguous \emph{-I} marker.
-As for the filler items, we could not use or modify the original experiment items since the fillers of the original study were not online.
-We have used two types filler sentences: grammatical sentences in which the verb bears plural agreement (\autoref{fillera}), and ungrammatical sentences in which the verb does not bear plural agreement (\autoref{fillerb}).
-We wanted to nullify a possible strategy by the participants where they associate the sentence-final morpheme directly with the acceptability of the sentence.
-And we also wanted to eliminate the possibility of participants disregarding other elements in the sentences while answering the questions we ask right after the sentence.
+As seen in the examples, unlike \textcite{Lago2018}'s experimental items, all of my items bear the \emph{-sI} possessive marker instead of the ambiguous \emph{-I} marker.
+As for the filler items, I could not use or modify the original experiment items since the fillers of the original study were not online.
+I have used two types of filler sentences: grammatical sentences in which the verb bears plural agreement (\autoref{fillera}), and ungrammatical sentences in which the verb does not bear plural agreement (\autoref{fillerb}).
+I wanted to nullify a possible strategy by the participants where they associate the sentence-final morpheme directly with the acceptability of the sentence.
+And I also wanted to eliminate the possibility of participants disregarding other elements in the sentences while answering the questions I ask right after the sentence.
 
@@
 One hundred and seven Turkish speakers were recruited from Bogazici University in İstanbul.
-We did not collect participants' knowledge of other languages; however, we verified that Turkish is their native language and that they predominantly use it in their daily lives.
+I did not collect participants' knowledge of other languages; however, I verified that Turkish is their native language and that they predominantly use it in their daily lives.
 In the experiments, participants were asked to judge the acceptability of experimental and filler sentences in Turkish.
 All of the sentences were presented one word at a time in the center of the screen for 500 ms per word unlike \textcite{Lago2018} and \textcite{Wagers2009}, in which the duration was 300 ms per word.
-The experiment was run on a web-based platform titled the Ibex Farm, and all of the documentation can be found on our github page.
+The experiment was run on a web-based platform titled the Ibex Farm, and all of the documentation can be found on my Github page:\url{https://github.com/utkuturk/AgreementAttraction_Experiment}.
 
@@
 Each trial after the practice items started with a blank screen, followed by a flash of single words in the middle of the screen.
-After the sentence, they were asked a grammaticality judgment questins (Was the sentence you read was natural to you?) where they need to press P for \emph{no} and press Q for \emph{yes}.
-In the experiment, every participant saw 40 experimental item that is latin-squared and 40 fillers.
+After the sentence, they were asked a grammaticality judgment questions (Was the sentence you read was natural to you?) where they need to press P for \emph{no} and press Q for \emph{yes}.
+In the experiment, every participant saw 40 experimental item that is Latin-squared and 40 fillers.
 
@@
 Participants that could not exceed the threshold of 0.25 difference in \emph{yes} answer between the condition (c) and (d), namely Ungrammatical, SG attractor and Grammatical, SG attractor, were excluded.
-We performed an analysis by fitting linear mixed-effect modelts to our data, controlling for vowel ending, plural attractor, grammaticality and their interactions.
-Models were fit using bernoulli distribution with probit link function and 95\% confidence intervals.
+I performed an analysis by fitting linear mixed-effect models to my data, controlling for vowel ending, plural attractor, grammaticality and their interactions.
+Models for responses were fit using Bernoulli distribution with probit link function and 95\% confidence intervals.
+Models for response times were fit using Lognormal distribution.
 
@@
 As seen in the figure, 0.22\% of the sentences with plural attractors and a singular verb were accepted by the participants, in line with the findings of \textcite{Lago2018}.
-We also see a number attraction rate of 0.11\% which was also observed in \textcite{Lago2018} with close results.
+I also see a number attraction rate of 0.11\% which was also observed in \textcite{Lago2018} with close results.
 
-In Figure \ref{fig:exp1ResponseModelPlot}, we clearly see the effects of ungrammaticality and the interaction between the ungrammaticality and plural attractor.
-We see that, vowel ending is not significant even though it has negative effect.
-Thus, we may say that differentiating between the accusative case and the possessive suffix has cause a reduction in the effect of the agreement attraction.
-The results also shows that when the attractor is plural, people have a high tendency to find the sentence grammatical.
+In Figure \ref{fig:exp1ResponseModelPlot}, I clearly see the effects of ungrammaticality and the interaction between the ungrammaticality and plural attractor.
+I see that the vowel ending is not significant even though it has a negative effect.
+Thus, I may say that differentiating between the accusative case and the possessive suffix has caused a reduction in the effect of the agreement attraction.
+The results also show that when the attractor is plural, people have a high tendency to find the sentence grammatical.
 
@@
 \includegraphics{AgreementAttraction_files/figure-latex/exp1ResponseModelPlot-1.pdf}
-\caption{\label{fig:exp1ResponseModelPlot}log-odd Estimates and 95\% credible intervals for the regression coefficients.}
+\caption{\label{fig:exp1ResponseModelPlot}log-odd Estimates and 95\% credible intervals for the regression coefficients in Accuracy.}
 \end{figure}
 
-In Figure \ref{fig:exp1AvgRTs}, we see that average response times are significantly higher than the those of \textcite{Lago2018}.
-Again, these results shows the effect of disambiguation of the possessive suffix from the accusative case has surfaced as the difficuilty in response and memory retrieval time.
+\begin{figure}
+\centering
+\includegraphics{AgreementAttraction_files/figure-latex/exp1ResponseTimeModelPlot-1.pdf}
+\caption{\label{fig:exp1ResponseTimeModelPlot}log-odd Estimates and 95\% credible intervals for the regression coefficients in Reading Times.}
+\end{figure}
+
+In Figure \ref{fig:exp1AvgRTs}, I see that average response times are significantly higher than the those of \textcite{Lago2018}.
+I also see it in \ref{exp1ResponseTimeModelPlot}, since \textbf{b\_cEndsinVowel} indicates whether or not it is Experiment 1 or Experiment from \textcite{Lago2018}, i.e.~distractors in items in \textcite{Lago2018} ends with a consonant, while ours ends in a vowel.
+Again, these results show the effect of disambiguation of the possessive suffix from the accusative case has surfaced as the difficulty in response and memory retrieval time.
 
@@
 \includegraphics{AgreementAttraction_files/figure-latex/exp1AvgRTs-1.pdf}
-\caption{\label{fig:exp1AvgRTs}Average response times for our replication and Lago et. al. (2018)}
+\caption{\label{fig:exp1AvgRTs}Average response times for my replication and Lago et. al. (2018)}
 \end{figure}
@@
 
-The results follow from what a cue-based model would predict: slightly lower agreement attraction.
-However, these results can also be a result of a badly formed filler sentences which are shown with purple line.
-Participants may be biased towards saying no since most of the experimental items being ungramatical.
-However, this can also be statistical \emph{miss} since we may accidentally have a group such as this one.
+Experiment 1 found number attraction effects, like also attested in \textcite{Lago2018}, and also found a significant effect of form ambiguity of possessive and an interaction of plural attractor with ungrammaticality in response times.
+Illusionary agreement of the verb with the plural attractor was more than the singular attractor.
+In addition to what has been discussed by \textcite{Avetisyan2019}.
+this results also show that not only the case itself but also the form of the case can affect the response times.
+
+In the previous sections, I have predicted that with an assumed mechanism where people do take the clues from the form of the plural morpheme itself and have a strategy based on matching the plural morphemes, I would expect no change with regards to the agreement attraction effects.
+I also should not expect increasing response times when an irrelevant morpheme for the mechanism I assume.
+
+However, I see that response times have changed drastically when the suffixes are dismabiguated.
+It is clear from the Figure \ref{fig:exp1AvgRTs}, when people are prompted to judge the sentence, they have difficulty in resolving and back-tracking the dependencies of the sentence even though nothing relevant to the plural morpheme and its host word has changed.
+
+The results follow from what a cue-based model would predict: slightly lower agreement attraction and increased response time.
+Due to the disambiguation between the accusative case and the possessive suffix, I speculated that the features related to the \emph{non-subjecthood} of the head of the subject would not surface falsely in my replication.
+With more clearly formed genitive-possessive structures, participants do not have an easy time to partially match the cues with the phrases.
+This situation stems from the idea proposed by \textcite{Lago2018} with regards to the effects of the cases on numeral agreement attraction.
+She argues that the frequency of the case being used in the subject position affects the agreement attraction effects in a positive manner.
+Since the accusative case is rarely used in Turkish, I have argued that it may give \emph{wrong} clues an enable the distractors to even distract more.
+Yet, with clearly marked possessive suffix, I see that these enabling nature of the genitive possessive structure is eliminated, which is also shown in \textcite{Avetisyan2019}.
+
+However, these results can also be a result of badly formed filler sentences which are shown with a purple line.
+Participants may be biased towards saying no since most of the experimental items being ungrammatical.
+However, this can also be statistical \emph{miss} since I may accidentally have a group such as this one.
 However, the visible effect of vowel ending and response time suggest that people do indeed care more than only the retrieval of plural morpheme \emph{-lar} and its place.
-This results go against what we have predicted for the Marking and Morphing model and our shallow processing model.
-However, the existence of extremely close degree of agremeent attraction effects and non-significant nature of the effect of the vowel ending indicate that we cannot readily discard other explanations.
+
+These results go against what I have predicted for the Marking and Morphing model as well.
+Due to the no extreme semantic change in the experimental (\emph{Marking}) and no change in the structural relations among the genitive-possessive constructions (\emph{Morphing}), there should be no difference in agreement attraction.
+
+However, the existence of an extremely close degree of agreement attraction effects and non-significant nature of the effect of the vowel ending indicates that I cannot readily discard other explanations.
+Another reason for not jumping to the conclusion with percolation models can be related to the number of participants \textcite{Lago2018} have included in their study \autocite[see][]{Vasishth2018}.
 
@@
 
-Having discussed the replication study of \textcite{Lago2018}, we have shown that results favor the cue-based models, especially with the effect of disambiguated possessive suffix on response times.
-However, due to the extremely similar effects on agreement attraction we can still entartain shallow processing mechanism as explained in \autoref{model1}, \autoref{model2}, and \autoref{model3}.
-Since we argue that the agreement attraction is a product of memory state in which comprehenders do not have an exact memory of the place of the plural morpheme mainly, we conducted an experiment where the distractor with the plural morpheme in on the relative clause.
+Having discussed the replication study of \textcite{Lago2018}, I have shown that results favor the cue-based models, especially with the effect of disambiguated possessive suffix on response times.
+However, due to the extremely similar effects on agreement attraction, I can still entertain shallow processing mechanism as explained in \autoref{model1}, \autoref{model2}, and \autoref{model3}.
+Since I argue that the agreement attraction is a product of memory state in which comprehenders do not have an exact memory of the place of the plural morpheme mainly, I conducted an experiment where the distractor with the plural morpheme in on the relative clause.
 
-The study consists of an speeded acceptability judgment experiment in the web-based platform Ibex Farm.
-In the experiment, we test whether or not speakers utilize even more shallow parser than what is stipulated by \textcite{Lago2018} and our replication of \textcite{Lago2018} Experiment 2.
-This was investigated using syntactic structures similar to \textcite{Lago2018} materials, in which we have opted out the Genitive Constructuion (GC) for Relative Clause construction (RCC) as a distractor.
-In Turkish, like GC, relative clause in RCC precedes the head noun, and length-wise Turkish relative clauses can consist of only one word and the rest can be dropped.
-Turkish allows us to use RCCs as distractors in the same place because Turkish plural morpheme in verbal domain and nominal domain are the same: \emph{-lAr}.
-Both of them react similarly in the same phonological environments, and they also exhibit same stress patterns.
+The study consists of a speeded acceptability judgment experiment in the web-based platform Ibex Farm.
+In the experiment, I test whether or not speakers utilize even more shallow parser than what is stipulated by \textcite{Lago2018} and my replication of \textcite{Lago2018} Experiment 2.
+This was investigated using syntactic structures similar to \textcite{Lago2018} materials, in which I have opted out the Genitive Construction (GC) for Relative Clause construction (RCC) as a distractor.
+In Turkish, like GC, the relative clause in RCC precedes the head noun, and length-wise Turkish relative clauses can consist of only one word and the rest can be dropped.
+Turkish allows us to use RCCs as distractors in the same place because Turkish plural morpheme in the verbal domain and nominal domain are the same: \emph{-lAr}.
+Both of them react similarly in the same phonological environments, and they also exhibit the same stress patterns.
 
-In the experimental items, the distractor RC and the matrix verb had four configurations in which the number morpheme on the RCC (\emph{plural} vs.
+In the experimental items, the distractor RC and the matrix verb had f my configurations in which the number morpheme on the RCC (\emph{plural} vs.
 \emph{singular} marked RC verb) and matrix verb (\emph{grammatical} vs.
@@
 
-Every experimental item from both experiments (this experiment and the Experiment 1) is included in the analysis.
+Every experimental item from both experiments (this experiment and Experiment (1) is included in the analysis.
 Participants that could not exceed the threshold of 0.25 difference in \emph{yes} answer between the condition (c) and (d), namely Ungrammatical, SG attractor and Grammatical, SG attractor, were excluded.
-We performed an analysis by fitting linear mixed-effect modelts to our data, controlling for vowel ending, plural attractor, grammaticality and their interactions.
-Models were fit using bernoulli ditribution with probit link function and 95\% confidence intervals.
+I performed an analysis by fitting linear mixed-effect models to my data, controlling for vowel ending, plural attractor, grammaticality and their interactions.
+Models were fit using Bernoulli distribution with probit link function and 95\% confidence intervals.
 
@@
 
-It is clear from Figure \ref{fig:exp2AvgResponse} that in the condition (c) where we expect an agreement attraction, participants find as unacceptable as the condition (d) with singular attractor, singular head noun, and plural matrix verb.
-While we do not see any agreement attraction (0.07\%), we also see a more firm analysis of the ungrammatical sentence with singular matrix verb ((0.07\%)).
+It is clear from Figure \ref{fig:exp2AvgResponse} that in the condition (c) where I expect an agreement attraction, participants find as unacceptable as the condition (d) with singular attractor, singular head noun, and plural matrix verb.
+While I do not see any agreement attraction (0.07\%), I also see a more firm analysis of the ungrammatical sentence with singular matrix verb ((0.07\%)).
 
-As for the estimates of coefficients in \ref{fig:exp2ResponseModelPlot}, we can conclude that there is a significant negative effect of plural morpheme on the relative clause, which means that it does not cause any agreement affects.
-Again, the effect of ungrammaticality that stems from the existence of plural morpeheme on the matrix verb is visible.
+As for the estimates of coefficients in \ref{fig:exp2ResponseModelPlot}, I can conclude that there is a significant negative effect of plural morpheme on the relative clause, which means that it does not cause any agreement affects.
+Again, the effect of ungrammaticality that stems from the existence of plural morpheme on the matrix verb is visible.
 The interaction between the plural morpheme on the attractor RC and the matrix verb is even higher than the sole effect of plural morpheme on the attractor RC.
@@
 \includegraphics{AgreementAttraction_files/figure-latex/exp2AvgRTs-1.pdf}
-\caption{\label{fig:exp2AvgRTs}Average response times for our replication and Experiment2}
+\caption{\label{fig:exp2AvgRTs}Average response times for my replication and Experiment2}
 \end{figure}
 
-Finally, the response times of the Experiment 2 is significantly lower than the Experiment 1 as seen from Figure \ref{fig:exp2AvgRTs}.
-The even lower response time in ungrammatical plural (condition c) shows that participants were extremely confident with their decision and did not had any issue with the dependency resolution.
+Finally, the response times of Experiment 2 is significantly lower than the Experiment 1 as seen from Figure \ref{fig:exp2AvgRTs}.
+The even lower response time in ungrammatical plural (condition c) shows that participants were extremely confident with their decision and did not have any issue with the dependency resolution.
 
@@
 
-These findings indicate that our hypothesis regarding the matching of the forms is not supported by the empirical evidence.
+These findings indicate that my hypothesis regarding the matching of the forms is not supported by the empirical evidence.
 However, results in Experiment 2 points in a direction where the Marking and Morphing studies predicted in the first place.

### 2019-07-03 Paper/AgreementAttraction.Rmd
Some stuff. I don't remember.

--- 2019-02-13 Paper/AgreementAttraction.Rmd
@@
 
-Attraction errors in the production and comprehension of subject-verb agreement, in which a verb does not agree with the grammatical agreement controller, but with a potential attractor, have been the main topic of research in many studies for quite a long time.
+Attraction attraction in the processing of subject-verb agreement have been an illuminating with regard to \ldots.
+
+<!--
+Introduction:
+ - Review of the key attraction findings: 
+        * English. 
+      * German: @ReifegersteEtAl:2016
+      * Definitely Russian (Sliosar on gender). [@SlioussarMalko:2016]
+      * Arabic: @TuckerEtAl:2015
+      * Spanish: @LagoEtAl:2015
+      * Turkish: @LagoEtAl:2018
+      * Hammerly 2018 [@HammerlyEtAl:2018]
+      * @LinzenLeonard:2018
+      * @SmithFranck:2018
+      * @ParkerPhillips:2017
+      * @VasishthEtAl:2017
+      * @ReifegersteEtAl:2016
+      * @KwonSturt:2016
+      * @RisticMolinaroMancini:2016
+      * @SlevcMartin:2016
+      * @PatsonHusband:2015
+      * @Enochson:2015
+      * @FranckColonnaRizzi:2015
+      * @WagersEtAl:2009
+      * Slovak: @BadeckerKuminiak:2007
+      * @BockEtAl:2001
+      * @FiederEtAl:2014
+      * @Staub:2009
+      * @TannerNicolBrehm:2014
+      * @XiangEtAl:2013
+      * @NicenboimEtAl:2018
+
+      @TannerBulkes:2015
+      @Staub:2010
+      @DankEtAl:2014
+      @PearlmutterGarnseyBock:1999
+      @FooteBock:2012
+      @DillonEtAl:2013
+
+  - Accounts of 
+-->
+
+errors in the production and comprehension of subject-verb agreement,
+
+in which a verb does not agree with the grammatical agreement controller, but with a potential attractor, have been the main topic of research in many studies for quite a long time.
 In fact, it is still a widely researched area in psycholinguistic studies.
@@
                   dplyr::select(-Distance:-NewCond)
-
 ```
@@
 
+```{r loadFrequencies, eval =T, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+
+word_freq <- readxl::read_excel("../Data/freq.xlsx", sheet = 1)
+word_freq$freq_percentage %<>% as.numeric()
+word_freq %<>% dplyr::select(-freq_standardized, -freq_percentage, -word)
+word_freq %<>% tidyr::spread(place, freq_count)
+
+word_freq %<>% dplyr::group_by(exp) %>% 
+               dplyr::mutate( cat_n1 = ifelse(n1 > median(n1), "high", "low"),
+                              cat_n2 = ifelse(n2 > median(n2), "high", "low"),
+                              freqlog_n1 = scale(log(n1)),
+                              freqlog_n2 = scale(log(n2)),
+                              freqlog_n1n2 = log(n1) - log(n2)
+                            ) %>% 
+                ungroup()
+word_freq$cat_n1 %<>% as.factor()
+word_freq$cat_n2 %<>% as.factor()
+
+word_freq_exp1 <- word_freq %>% 
+                    subset(exp == "up") %>% 
+                    dplyr::select(-exp)
+word_freq_lago <- word_freq %>% 
+                    subset(exp == "lago") %>% 
+                    dplyr::select(-exp)
+
+```
+
 ```{r mergeData, eval =T, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
@@
 df_merge_exp1 <- data_clean %>% ungroup() %>% 
-                      dplyr::select(source=experiment, grammatical, attractor_num, # condition,
+                      dplyr::select(source=experiment, 
+                                    grammatical, attractor_num,
+                                    # condition,
                                     subject, item=Item,
@@
 df_merge_exp1$experiment <- "Experiment 1"
-df_merge_exp1$grammatical <- with(df_merge_exp1, ifelse(grammatical == "gram", 
+df_merge_exp1$grammatical <- with(df_merge_exp1, 
+                                  ifelse(grammatical == "gram", 
                                           "grammatical",
                                           "ungrammatical"))
-df_merge_exp1$attractor_num <- with(df_merge_exp1, ifelse(attractor_num == "pl", 
+df_merge_exp1$attractor_num <- with(df_merge_exp1, 
+                                    ifelse(attractor_num == "pl",
                                            "plural", 
@@
 df_merge_exp1$subject %<>% as.character()
+df_merge_exp1 %<>% left_join(word_freq_exp1, by = "item")
 
@@
 df_merge_lago <- df_lagoetal_attr %>% ungroup() %>% 
-                      dplyr::select(grammatical=Grammatical, attractor_num=Attractor, #condition=Condition, 
-                                    subject=Participant, item=Item,
+                      dplyr::select(grammatical=Grammatical,
+                                    attractor_num=Attractor,
+                                    #condition=Condition, 
+                                    subject=Participant, 
+                                    item=Item,
                                     ResponseYes, RT)
+df_merge_lago %<>% left_join(word_freq_lago, by = "item")
 df_merge_lago$experiment <- "Lago et al. (2018)" 
@@
 
-avg_clean <- df_merged %>%
+avg_clean <- 
+  df_merged %>%
      group_by(experiment, source, grammatical, attractor_num) %>%
      summarize(avgRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T))
+
+# ##
+# avg_clean1 <- df_merged %>%
+#                 group_by(experiment, source, grammatical, attractor_num, cat_n1) %>%
+#                 summarize(avgRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T))
+# 
+# p_avg_resp1 <- ggplot(avg_clean1 %>% subset(is.na(source) | source != "filler"), 
+#                      aes(grammatical, p_yes, #linetype = attractor_num, 
+#                          color = attractor_num, linetype = cat_n1, 
+#                          group = paste(attractor_num,cat_n1) )) + 
+#                 geom_point() + geom_line() + 
+#                 facet_wrap(cat_n1~experiment)
+# p_avg_resp1
+# 
+# ##
+# ##
+# 
+# avg_clean2 <- df_merged %>%
+#                 group_by(experiment, source, grammatical, attractor_num, cat_n2) %>%
+#                 summarize(avgRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T))
+# 
+# p_avg_resp2 <- ggplot(avg_clean2 %>% subset(is.na(source) | source != "filler"), 
+#                      aes(grammatical, p_yes, #linetype = attractor_num, 
+#                          color = attractor_num, linetype = cat_n2, 
+#                          group = paste(attractor_num,cat_n2) )) + 
+#                 geom_point() + geom_line() + 
+#                 facet_wrap(cat_n2~experiment)
+# p_avg_resp2
+# 
+# ##
+# ##
+# 
+# avg_clean3 <- df_merged %>%
+#                 group_by(experiment, source, grammatical, attractor_num, cat_n1n2) %>%
+#                 summarize(avgRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T))
+# 
+# p_avg_resp3 <- ggplot(avg_clean3 %>% subset(is.na(source) | source != "filler"), 
+#                      aes(grammatical, p_yes, #linetype = attractor_num, 
+#                          color = attractor_num, linetype = cat_n1n2, 
+#                          group = paste(attractor_num,cat_n1n2) )) + 
+#                 geom_point() + geom_line() + 
+#                 facet_wrap(~experiment)
+# p_avg_resp3
+# 
+# ##
+
 ```
@@
 
-```{r exp1ModelResponse, eval = F}
+```{r exp1ModelResponse, eval = T}
 
@@
   cEndsInVowel <- ifelse(experiment == "Experiment 1", .5, -.5)
+  cFreqlog_n1n2 <- scale(freqlog_n1n2)
+  cFreqlog_n1 <- scale(freqlog_n1)
+  cFreqlog_n2 <- scale(freqlog_n2)
 })
@@
 # ## test model parameterization using a simple GLM first
-# m <- glm(ResponseYes ~ cEndsInVowel * cUngrammatical * cAttractorPlural,
+# m <- glm(ResponseYes ~ (cFreqlog_n1 + cFreqlog_n2) *
+#            cEndsInVowel * cUngrammatical * cAttractorPlural,
 #          data = df_merged_nofillers,
@@
 
-m_responses <- brm(ResponseYes ~ cEndsInVowel * cUngrammatical * cAttractorPlural + 
-                                 (cUngrammatical * cAttractorPlural + 1| subject) +
+#with(df_merged_nofillers, cor(cFreqlog_n1, cFreqlog_n2))
+#with(df_merged_nofillers, cor(cFreqlog_n1, cFreqlog_n1n2))
+#with(df_merged_nofillers, cor(cFreqlog_n2, cFreqlog_n1n2))
+#
+# m <- glm(ResponseYes ~ (cFreqlog_n1n2) * #+ cFreqlog_n1n2
+#                         cEndsInVowel * cUngrammatical * cAttractorPlural,
+#                    data = df_merged_nofillers,
+#                    family = "binomial")
+# summary(m)
+
+# + cFreqlog_n1n2
+m_responses <- brm(ResponseYes ~ (cFreqlog_n1 + cFreqlog_n2) *
+                                  cEndsInVowel * cUngrammatical * cAttractorPlural + 
+                                 ((cFreqlog_n1 + cFreqlog_n2) * cUngrammatical * cAttractorPlural + 1| subject) +
                                  (cUngrammatical * cAttractorPlural + 1| item),
                    data = df_merged_nofillers,
+                   init = "0",
                    family = bernoulli("probit"),
@@
 
+# + 
+m_responses2 <- brm(ResponseYes ~ (cFreqlog_n1n2) *
+                                  cEndsInVowel * cUngrammatical * cAttractorPlural + 
+                                 ((cFreqlog_n1n2) * cUngrammatical * cAttractorPlural + 1| subject) +
+                                 (cUngrammatical * cAttractorPlural + 1| item),
+                   data = df_merged_nofillers,
+                   init = "0",
+                   family = bernoulli("probit"),
+                   file = paste0(fname_exp1_responses, "2"), 
+                   chains = n_chains, cores = n_cores, iter = n_iter)
+
 ```
 
-```{r exp1ResponseModelPlot, eval = F, fig.height= 1.5, message=FALSE, warning=FALSE, fig.cap="Estimates and 95% credible intervals for the analysis of the probability of a 'yes' response."}
+```{r exp1ResponseModelPlot, eval = T, fig.height= 2, message=FALSE, warning=FALSE, fig.cap="Estimates and 95% credible intervals for the analysis of the probability of a 'yes' response."}
 
 contrast_names <- c("cUngrammatical" = "Ungrammaticality",
-                    "cAttractorMatch" = "Attactor Match",
-                    "cUngrammatical:cAttractorMatch" = "Ungrammaticality * Attractor Match")
+                    "cAttractorPlural" = "Plural Attactor",
+                    "cEndsInVowel"="Vowel-ending",
+                    "cUngrammatical:cAttractorPlural" = "Ungrammaticality * Plural Attactor",
+                    "cEndsInVowel:cUngrammatical"="Vowel-ending * Ungrammaticality",
+                    "cEndsInVowel:cAttractorPlural"="Vowel-ending * Plural Attactor",
+                    "cEndsInVowel:cUngrammatical:cAttractorPlural"="Vowel-ending * Ungrammaticality * Plural Attactor"
+                    )
 

### 2019-07-03 Paper/AgreementAttraction.tex
Some stuff. I don't remember.

--- 2019-02-13 Paper/AgreementAttraction.tex
@@
 \centering
-\includegraphics{AgreementAttraction_files/figure-latex/exp1AvgResponseLagoEtAl-1.pdf}
-\caption{\label{fig:exp1AvgResponseLagoEtAl}Estimates and 95\% credible
+\includegraphics{AgreementAttraction_files/figure-latex/exp1ResponseModelPlot-1.pdf}
+\caption{\label{fig:exp1ResponseModelPlot}Estimates and 95\% credible
 intervals for the analysis of the probability of a `yes' response.}

### 2019-07-03 scripts/experiment1_prepare.R

@@ -14,39 +14,48 @@ data <- read.csv(fname_data,
                  encoding = "UTF-8" , 
                  col.names = paste0("V",seq_len(11)), 
                  fill = TRUE)
-colnames(data) = c("Time", "MD5", "ControllerType", "SentenceNoInStimFile", "Element", "Type", "Item", "Sentence", "Question","Answer", "RT")
+colnames(data) = c("Timestamp", "MD5", "ControllerType", "SentenceNoInStimFile", "Element", "Type", "Item", "Sentence", "Question","Answer", "RT")
+data %<>% dplyr::select(-MD5)
 
-FormEntries <- subset(data, ControllerType != "DashedAcceptabilityJudgment" ) %>% drop.levels(); nrow(data)
+FormEntries <- subset(data, ControllerType != "DashedAcceptabilityJudgment" ) %>% 
+                      drop.levels(); 
+nrow(data)
 data %<>% subset(ControllerType == "DashedAcceptabilityJudgment")
-age <- dplyr::select(FormEntries, MD5,Sentence,Question) %>% 
+age <- dplyr::select(FormEntries, Timestamp,Sentence,Question) %>% 
           dplyr::filter(Sentence == "age") %>%
-          dplyr::select(MD5, Age = Question)
-natturk <- dplyr::select(FormEntries, MD5,Sentence,Question) %>% 
+          dplyr::select(Timestamp, Age = Question)
+natturk <- dplyr::select(FormEntries, Timestamp,Sentence,Question) %>% 
           dplyr::filter(Sentence == "natturk") %>%
-          dplyr::select(MD5, Natturk = Question) %>%
+          dplyr::select(Timestamp, Natturk = Question) %>%
           mutate(Natturk = Natturk == "male")
-dex <- dplyr::select(FormEntries, MD5,Sentence,Question) %>% 
+dex <- dplyr::select(FormEntries, Timestamp,Sentence,Question) %>% 
           dplyr::filter(Sentence == "dex") %>%
-          dplyr::select(MD5, Dex = Question) %>%
+          dplyr::select(Timestamp, Dex = Question) %>%
           mutate(Dex = ifelse(Dex == "male", "right-handed", "left-handed"))
-FormPart <- dplyr::left_join(age, natturk, by = "MD5") %>% 
-        dplyr::left_join(., dex , by = "MD5" ) %>% 
-        unique()
[…]

### 2019-07-03 Paper/AgreementAttraction.Rmd

--- 2019-06-14 Paper/AgreementAttraction.Rmd
@@
 
+<!--
+Introduction:
+ - Review of the key attraction findings: 
+        * English. 
+      * German: @ReifegersteEtAl:2016
+      * Definitely Russian (Sliosar on gender). [@SlioussarMalko:2016]
+      * Arabic: @TuckerEtAl:2015
+      * Spanish: @LagoEtAl:2015
+      * Turkish: @LagoEtAl:2018
+      * Hammerly 2018 [@HammerlyEtAl:2018]
+      * @LinzenLeonard:2018
+      * @SmithFranck:2018
+      * @ParkerPhillips:2017
+      * @VasishthEtAl:2017
+      * @ReifegersteEtAl:2016
+      * @KwonSturt:2016
+      * @RisticMolinaroMancini:2016
+      * @SlevcMartin:2016
+      * @PatsonHusband:2015
+      * @Enochson:2015
+      * @FranckColonnaRizzi:2015
+      * @WagersEtAl:2009
+      * Slovak: @BadeckerKuminiak:2007
+      * @BockEtAl:2001
+      * @FiederEtAl:2014
+      * @Staub:2009
+      * @TannerNicolBrehm:2014
+      * @XiangEtAl:2013
+      * @NicenboimEtAl:2018
+
+      @TannerBulkes:2015
+      @Staub:2010
+      @DankEtAl:2014
+      @PearlmutterGarnseyBock:1999
+      @FooteBock:2012
+      @DillonEtAl:2013
+
+Attraction attraction in the processing of subject-verb agreement have been an illuminating with regard to \ldots.
+
+errors in the production and comprehension of subject-verb agreement,
+
+in which a verb does not agree with the grammatical agreement controller, but with a potential attractor, have been the main topic of research in many studies for quite a long time.
+In fact, it is still a widely researched area in psycholinguistic studies.
+Despite the comprehensive research that has been carried out, studies that have been conducted on agreement attraction in Turkish have been very limited.
+In fact, @Lago is currently the only study that explores this phenomenon in Turkish.
+@Lago  makes use of genitive-possessive structures in the subject position, in which the possessive-marked noun is the head of the noun phrase which acts as the grammatical agreement controller, and the genitive noun serves as a potential attractor.
+In a speeded acceptability judgment study, @Lago found a significant effect of number agreement attraction.
+However, the interpretation of their findings may be a result of the fact that non-subjecthood cues originate from their use of morphologically ambiguous forms of the possessive.
+In the possessive forms that are used, all the head nouns in their stimuli are ambigiuous between possessive and accusative.
+-->
+
 ```{r setup, eval =T, include = FALSE, message=FALSE, warning=FALSE}

### 2019-07-03 Paper/AgreementAttraction.Rmd
the ones I miss

@@
       * @ParkerPhillips:2017
-      * @VasishthEtAl:2017
+      * @VasishthEtAl:2017 **
       * @ReifegersteEtAl:2016
@@
       * @PatsonHusband:2015
-      * @Enochson:2015
+      * @Enochson:2015 **
       * @FranckColonnaRizzi:2015
@@
       * @BockEtAl:2001
-      * @FiederEtAl:2014
+      * @FiederEtAl:2014 **
       * @Staub:2009
@@
       @Staub:2010
-      @DankEtAl:2014
+      @DankEtAl:2014 **
       @PearlmutterGarnseyBock:1999

### 2019-08-06 Paper/paper_draft.rmd
Started working on the paper. [PL]

--- 2019-07-03 Paper/AgreementAttraction.Rmd
@@
 
-      @TannerBulkes:2015
-      @Staub:2010
-      @DankEtAl:2014 **
-      @PearlmutterGarnseyBock:1999
-      @FooteBock:2012
-      @DillonEtAl:2013
+      * @TannerBulkes:2015
+      * @Staub:2010
+      * @DankEtAl:2014 **
+      * @PearlmutterGarnseyBock:1999
+      * @FooteBock:2012
+      * @DillonEtAl:2013
+      - Shravan et al.'s new paper on Armenian
 
@@
 
-It has been observed that speakers generally fail to accurately comprehend agreement between elements in a sentence.
-One such comprehension error that is made has been deemed agreement attraction.
-Speakers may erroneously find a sentence in which the "attractor" agrees with the verb instead of the "head" of the subject.
-Data from typologically different languages and explanations from different frameworks show that I am far from understanding by what the attraction is modulated.
-Some theories refer this phenomenon as a faulty representation of the number on the head of the subject phase whereas other theories argue that the attraction is due to an error in the access to the number of the subject.
-In this paper, I report two experiments exploring another possible explanation for agreement attraction: an extreme shallow processing.
-The first experiment is a replication of @Lago2018 where I changed the head of the subject in order to differentiate between the accusative case *-I*.
-In the second experiment, I have used a relative clause which only consists of a plural marked verb as a distractor.
-my results show that while people do indeed care more than just "matching" the forms of plural verbal.
+It has been observed that speakers often fail to accurately process grammatical dependencies between the parts of a sentence. 
+For example, \ldots illusory npi licensing, agreement attraction \ldots
+One such comprehension error that is made has been dubbed agreement attraction (cite): Speakers may erroneously find sentences acceptable, in which the the verb erroneously agrees with an unreated noun phrase (*the attractor*) instead of the subject (*the agreement controller*).
+
+Some theories (cite) explain this phenomenon by means of a faulty representation of the number on the head of the agreement controller whereas other theories assume that the attraction is due to an error in the access to the number of the subject.
+
+In this paper, we report two experiments exploring another possible explanation for agreement attraction: shallow processing.
+The first experiment is a replication of @Lago2018 in which a potentially confounding variable is controlled.
+In the second experiment, we explore whether verbs with plural agreement can serve as as potential attractors.
+The results show that
+<!--
+pvl: no idea what the text below means
+while people do indeed care more than just "matching" the forms of plural verbal.
 either comprehenders have some sort of restriction to not use cues from verbs upon accessing the number of the plural morpheme or there is a syntactic reason for the number feature of the plural morpheme to not "percolate."
-
-# Literature
-
-## Theories of attraction
-
-Agreement attractions are defined as instances of incorrect agreements of an element with a distractor that is not its grammatical controller.
+-->
+
+# Theories of attraction
+
+Agreement attraction are defined as instances of incorrect agreements of an element with a distractor that is not its grammatical controller.
 As in \autoref{E1}, the target of the agreement is the verb *are*, the attracting distractor is *bottles*, and the feature erroneously assessed is the number feature of the grammatical controller *label*.
@@
 \begin{exe}
-\ex[*]{The label on the bottles \textit{are} wrong.\footnotemark}
+\ex[*]{The key to the cabinets \textit{are} \ldots }
 \label{E1}
 \end{exe}
-
-\footnotetext{The convention of using $\ast$ is to show the ungrammaticality of the sentencee.}
 
@@
 
-In their study, @Lago2018 investigates the comprehension of subject-verb agreement  Turkish monolinguals.
+In their study, @Lago2018 investigate the comprehension of subject-verb agreement  Turkish monolinguals.
 They use speeded acceptability judgments for the effects of number attraction in Turkish.
@@
 
-\ex \textsc{Ungrammatical, SG attractor} \label{lago4}
+\ex \textsc{ungrammatical, sg attractor} \label{lago4}
 \gll \c{S}ark{\i}c{\i}-n{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}-lar.\\
@@
 
-\ex \textsc{Grammatical, PL attractor} \label{lago2}
+\ex \textsc{grammatical, pl attractor} \label{lago2}
 \gll \c{S}ark{\i}c{\i}-lar-{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}\\
@@
 
-\ex \textsc{Ungrammatical, PL attractor} \label{lago3}
+\ex \textsc{ungrammatical, sg attractor} \label{lago3}
 \gll \c{S}ark{\i}c{\i}-lar-{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}-lar.\\
@@
 
-\ex \textsc{Grammatical, SG attractor} \label{lago1}
+\ex \textsc{grammatical, pl attractor} \label{lago1}
 \gll \c{S}ark{\i}c{\i}-n{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}\\
@@
   \begin{xlist}
-  \ex \underline{Ungrammatical, PL attractor} \label{exp3}
+  \ex \underline{ungrammatical, pl attractor} \label{exp3}
       \gll Komedyen-ler-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}-ler.\\
@@
 
-  \ex \underline{Grammatical, PL attractor} \label{exp2}
+  \ex \underline{grammatical, pl attractor} \label{exp2}
       \gll Komedyen-ler-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}.\\
@@
 
-  \ex \underline{Ungrammatical, SG attractor} \label{exp4}
+  \ex \underline{ungrammatical, sg attractor} \label{exp4}
       \gll Komedyen-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}-ler.\\
@@
 
-  \ex \underline{Grammatical, SG attractor} \label{exp1}
+  \ex \underline{grammatical, sg attractor} \label{exp1}
       \gll Komedyen-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}.\\
@@
 One hundred and seven Turkish speakers were recruited from Bogazici University in İstanbul.
-I did not collect participants' knowledge of other languages; however, I verified that Turkish is their native language and that they predominantly use it in their daily lives.
-In the experiments, participants were asked to judge the acceptability of experimental and filler sentences in Turkish.
-All of the sentences were presented one word at a time in the center of the screen for 500 ms per word unlike @Lago2018 and @Wagers2009, in which the duration was 300 ms per word.
-The experiment was run on a web-based platform titled the Ibex Farm, and all of the documentation can be found on  my Github page:\url{https://github.com/utkuturk/AgreementAttraction_Experiment}.
-
-Before the experiment, participants were instructed to give accurate and quick answers based on their own intuitions, and they were also notified about the time limit for answering.
-At the start of the experiment, they were given 4 practice items with feedback.
-Each trial after the practice items started with a blank screen, followed by a flash of single words in the middle of the screen.
-After the sentence, they were asked a grammaticality judgment questions (Was the sentence you read was natural to you?) where they need to press P for *no* and press Q for *yes*.
-In the experiment, every participant saw 40 experimental item that is Latin-squared and 40 fillers.
-
-### Analysis
-
-Every experimental item from both experiments (Experiment 1 and @Lago2018) is included in the analysis.
-Participants that could not exceed the threshold of 0.25 difference in *yes* answer between the condition (c) and (d), namely Ungrammatical, SG attractor and Grammatical, SG attractor, were excluded.
+We verified that Turkish was their native language and that they predominantly used it in their daily lives.
+In the experiments, participants were asked to judge the acceptability of Turkish sentences. All of the sentences were presented one word at a time in the center of the screen for 500 ms per word.
+<!-- unlike @Lago2018 and @Wagers2009, in which the duration was 300 ms per word. -->
+The experiment was run on *Ibex Farm*, a web-based experiment platform (\url{http://spellout.net/ibexfarm}).
+All experimental stimuli, data, and documentation can be found on \url{https://github.com/utkuturk/AgreementAttraction_Experiment}.
+
+Participants were instructed to quickly clasify sentences as acceptable or unacceptable based on their intuition.
+They were further informed about the $XXXX ms$ time limit for answering.
+At the start of the experiment, they were given 4 practice trials, and received feedback on their response.
+Each trial after the practice items started with a blank screen, followed by a word-by-word RSVP presentaion of the sentence in the center of the screen.
+After the sentence presentation, they were asked for a grammaticality judgment
+(Was the sentence you read was natural to you?) 
+<!-- Is this really how it was phrased? -->
+responded Q for *yes*, and P for *no*. 
+The 40 experimental items were automatically divided into four lists according to a Latin-square design, and were intermixed with filler sentences, such that each participant saw 40 experimental items and 40 fillers in random order over the course of the experiment.
+
+### Data Analysis
+<!-- to-do: find out if the items from experiment 1 and Lago's paper were minimal pairs. Should
+at least some of them have the same item id? -->
+
+In order to find out whether the noun class, and thus the presence of an ambiguity between genitive and accusative affected the magnitude of the agreement attraction effect, we analyzed the data from our experiment
+together with the data from @Lago2018.
+
+Participants for whom the difference in the percentage of `yes' responses between grammatical and ungrammatical conditions without attraction (conditions c and d) was below $0.25$ were deemed to not have performed the task as instructed, and their data was excluded from further analysis.
+
+We used `R` `r citep(citation())` and the *tidyverse* R packages `r citep(citation("tidyverse"))` for data processing and plotting, and the R packages *brms* `r citep(citation("brms"))` and *rstan* `r citep(citation("rstan"))` to fit Bayesian hierarchical models [e.g.,@GelmanHill:2007, @McElreath:2016, @BDA3].
+
+A Bayesian hierarchical generalized linear model was fitted to the participant's responses
+
 I performed an analysis by fitting linear mixed-effect models to  my data, controlling for vowel ending, plural attractor, grammaticality and their interactions.
@@
 
-# # TODO: the following subjects have too much data: 11, 28, 36, 42, 55, 65, 73, 84, 92, 
-# #
-# x <- df_merged %>% subset(experiment == "Experiment 1") %>% group_by(subject) %>% dplyr::summarize(F = sum(is.na(attractor_num)),
-#                                                           N = length(is.na(attractor_num)) )
-# x %>% as.data.frame()
-# 
-# x$N %>% sum()
-# x$F %>% sum()
-
-#summary(as.factor(df_merged$attractor_num))
-
 df_merged %<>% within(., {
@@
 ```
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-<div id = "refs"></div>
-\endgroup

### 2019-08-26 Paper/paper_draft.rmd
Updates.

@@
   - name          : "Utku Türk"
-    affiliation   : ""
+    affiliation   : "1"
     corresponding : yes    # Define only one corresponding author
-    address       : ""
+    address       : "Postal address"
     email         : "utku.turk@boun.edu.tr"
-
+  - name          : "Pavel Logačev"
+    affiliation   : "1"
 affiliation:
-  - id            : ""
-    institution   : "Boğaziçi University"
-
-#authornote: |
-#  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-#
-#   Enter author note here.
-
+  - id            : "1"
+    institution   : "Boğaziçi University University, Istanbul, Turkey"
+authornote: |
+  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+  Enter author note here.
 abstract: |
-
-# keywords          : "keywords"
-# wordcount         : "X"
-
-bibliography      : ["myreferences.bib","r-references.bib"]
-
+  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
+
+  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
+
+  One sentence clearly stating the **general problem** being addressed by  this particular study.
+
+  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
+
+  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
+
+  One or two sentences to put the results into a more **general context**.
+
+  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
+
+  <!-- https://tinyurl.com/ybremelq -->
+keywords          : "keywords"
+wordcount         : "X"
+bibliography      : ["myreferences.bib", "library.bib", "r-references.bib"]
 floatsintext      : no
@@
 draft             : no
+documentclass     : "apa6"
+classoption       : "doc"
+output:
+  papaja::apa6_pdf:
+    citation_package: biblatex
+    includes:
+        in_header: paper_draft_preamble.tex
+
+editor_options: 
+  chunk_output_type: console
+keep_tex: TRUE
+keep_md: TRUE
+---
+
+<!--
 header-includes   :
@@
   - \usepackage{tikz-qtree}
-#  - \usepackage[mcolblock]{leipzig}
-#  - \makeglossaries
   - \let\eachwordone=\textit
-#  - \renewcommand{\eachwordone}{\footnotesize\textit}
-#  - \let\eachwordtwo=\footnotesize
   - \usepackage{geometry}
@@
   - \rfoot{\thepage}
-
-documentclass     : "apa6"
-classoption       : "doc"
-output:
-  papaja::apa6_pdf:
-    number_sections: true
-    citation_package: biblatex
-keep_tex: TRUE
-biblatexoptions: [maxbibnames=999]
----
-
+  - \usepackage{lmodern}
+
+-->
+
+<!--
+    includes:
+        in_header: paper_draft_preamble.tex
+-->
 <!--
@@
 For example, \ldots illusory npi licensing, agreement attraction \ldots
-One such comprehension error that is made has been dubbed agreement attraction (cite): Speakers may erroneously find sentences acceptable, in which the the verb erroneously agrees with an unreated noun phrase (*the attractor*) instead of the subject (*the agreement controller*).
-
-Some theories (cite) explain this phenomenon by means of a faulty representation of the number on the head of the agreement controller whereas other theories assume that the attraction is due to an error in the access to the number of the subject.
-
-In this paper, we report two experiments exploring another possible explanation for agreement attraction: shallow processing.
-The first experiment is a replication of @Lago2018 in which a potentially confounding variable is controlled.
-In the second experiment, we explore whether verbs with plural agreement can serve as as potential attractors.
-The results show that
+One such comprehension error is agreement attraction (cite): Speakers may erroneously find sentences acceptable in which the the verb erroneously agrees with a syntactically unreated noun phrase (*the attractor*) instead of the subject (*the agreement controller*).
+
+One instance of agreement attraction in language production is incorrect number-agreement between verb and a noun phrase which is not the agreement controller. For example, @Bock1991 found 
+that \ldots something interesting happends resulting in sentences like \ldots.
+<!-- to-do -->
+<!--
+in a sentence like \autoref{AAEx1}, the target of the agreement is the verb *are*, the attracting distractor is *bottles*, and the feature erroneously assessed is the number feature of the grammatical controller *label*.
+-->
+<!-- 
+This type of attraction, called number attraction in subject-verb agreement, first theorized by  
+@Quirk1972 and attested experimentally by
+-->
+<!-- to-do: use the original example here -->
+\begin{exe}
+\ex[*]{The key to the cabinets \textit{are} \ldots }
+\label{AAEx1}
+\end{exe}
+
+They interpreted the effect as \ldots some fairly theory neutral interpretation of what happens.
+
+And it turns out that agreement attraction surfaces in comprehension, too.  \ldots For example, here is another example from comprehension. \ldots
+
+Some theories (cite) explain this phenomenon by means of a faulty representation of the number on the head of the agreement controller whereas other theories assume that aagreement attraction is due to an error in the access to the number of the agreement controller.
+
+<!-- to-do: mention the Lago et al study briefly since we'll be referring to it. -->
+In this paper, we report the results of two experiments about agreement attraction: The first experiment adressed a potential confound in the @Lago2018 study.
+In the second experiment we tested an explanation of agreement attraction in Turkish as a task-specific strategy: we tested  whether verbs with plural agreement can serve as as potential attractors.
+The results show that \ldots 
 <!--
@@
 
-Agreement attraction are defined as instances of incorrect agreements of an element with a distractor that is not its grammatical controller.
-As in \autoref{E1}, the target of the agreement is the verb *are*, the attracting distractor is *bottles*, and the feature erroneously assessed is the number feature of the grammatical controller *label*.
-
-\begin{exe}
-\ex[*]{The key to the cabinets \textit{are} \ldots }
-\label{E1}
-\end{exe}
-
-This type of attraction, called number attraction in subject-verb agreement, first theorized by @Quirk1972 and attested experimentally by @Bock1991 in language production.
 One of the theoretical attempts to explain such phenomenon was Marking and Morphing Theories [@Bock2001; @Eberhard2005 among others].
@@
 In sentences like \autoref{E2}, the pronominal object *hen* triggers and agreement attraction without being a part of the subject.
-
++
 \begin{exe}
@@
 subject phrase, they cannot explain agreement attraction effects that are triggered by a distractor outside of the syntactic scope of the subject.
-Regardless, these effects may be explained in a framework where the source of the agreement attraction is placed on the trigger, i.e.
-verb.
+
+<!-- to-do: which theory do the terms trigger and probe come from? -->
+
+<!-- to-do: no idea what this means -->
+<!--
+Regardless, these effects may be explained in a framework where the source of the agreement attraction is placed on the trigger, i.e. verb. 
+--> 
 @Badecker2007 suggests that a process where the subject is retrieved from the memory plays a role in agreement attraction effects as well [see as well @Wagers2009].
@@
 ### Data Analysis
-<!-- to-do: find out if the items from experiment 1 and Lago's paper were minimal pairs. Should
-at least some of them have the same item id? -->
-
-In order to find out whether the noun class, and thus the presence of an ambiguity between genitive and accusative affected the magnitude of the agreement attraction effect, we analyzed the data from our experiment
-together with the data from @Lago2018.
-
-Participants for whom the difference in the percentage of `yes' responses between grammatical and ungrammatical conditions without attraction (conditions c and d) was below $0.25$ were deemed to not have performed the task as instructed, and their data was excluded from further analysis.
-
-We used `R` `r citep(citation())` and the *tidyverse* R packages `r citep(citation("tidyverse"))` for data processing and plotting, and the R packages *brms* `r citep(citation("brms"))` and *rstan* `r citep(citation("rstan"))` to fit Bayesian hierarchical models [e.g.,@GelmanHill:2007, @McElreath:2016, @BDA3].
-
-A Bayesian hierarchical generalized linear model was fitted to the participant's responses
-
-I performed an analysis by fitting linear mixed-effect models to  my data, controlling for vowel ending, plural attractor, grammaticality and their interactions.
-Models for responses were fit using Bernoulli distribution with probit link function and 95\% confidence intervals.
-Models for response times were fit using Lognormal distribution.
-
-### Results
-
-```{r identifyBadSubjects, eval =T, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-
-# identify participants 
-bad_subjects <- subset(avg_by_subj_wide, delta_dc <= 0.25 ) %>% .$subject
-
-#dataAvBySubj %>% subset(subject %in% bad_subjects) %>% ggplot(aes(grammatical, p_yes, group = paste(experiment,attracted), color = experiment )) + geom_point() + geom_line(aes(linetype =attracted)) + facet_wrap(~subject)
-
-data_clean <- data %>% subset(!subject %in% bad_subjects)
-
-```
 
@@
                     dplyr::select(-exp)
-
+```
+
+```{r identifyBadSubjects, eval =T, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+# identify participants 
+bad_subjects <- subset(avg_by_subj_wide, delta_dc <= 0.25 ) %>% .$subject
+data_clean <- data %>% subset(!subject %in% bad_subjects)
 ```
@@
 df_merged$item %<>% as.factor()
-```
-
-```{r computeAverages, eval =T, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-
-avg_clean <- 
-  df_merged %>%
+
+df_exp1_na_nofillers <- subset(df_merge_exp1, is.na(ResponseYes) & source != "filler")
+df_merged %<>% subset( !is.na(ResponseYes) )
+```
+
+<!-- to-do: find out if the items from experiment 1 and Lago's paper were minimal pairs. Should
+at least some of them have the same item id? -->
+
+In order to find out whether the noun class, and thus the presence of an ambiguity between genitive and accusative affected the magnitude of the agreement attraction effect, we analyzed the data from our experiment
+together with the data from @Lago2018.
+
+Participants for whom the difference in the percentage of `yes` responses between grammatical and ungrammatical conditions without attraction (conditions c and d) was below $0.25$ were deemed to not have performed the task as instructed, and their data was excluded from further analysis.
+In consequence, `r length(bad_subjects)` participants' data was excluded.
+
+Across participants, `r sum(is.na(df_exp1_na_nofillers$ResponseYes))` trials were not responded to before the deadline (by `r length(unique(df_exp1_na_nofillers$subject))` participants).
+The data from these trials was not used in the analysis of responses or reaction times.
+
+We used `R` `r citep(citation())` and the *tidyverse* R packages `r citep(citation("tidyverse"))` for data processing and plotting, and the R packages *brms* `r citep(citation("brms"))` and *rstan* `r citep(citation("rstan"))` to fit Bayesian hierarchical models [e.g.,@GelmanHill:2007; @McElreath:2016; @BDA3].
+
+Participants' responses were analyzed using Bayesian hierarchical generalized linear models using a Bernoulli distribution with a probit link.
+Models of response times were fit using the lognormal distribution.
+Both models were fit with the predictors
+<!-- to-do: fix the below formulation -->
+vowel ending, plural attractor, grammaticality and their interactions. 
+<!-- to-do: varying by-participants and by-items intercepts and slopes -->
+
+### Results
+
+```{r exp1AvgResponse, fig.height = 2.5, fig.width = 6, fig.cap="Estimates and 95% credible intervals for the analysis of the probability of a 'yes' response."}
+
+avg_clean <- df_merged %>%
      group_by(experiment, source, grammatical, attractor_num) %>%
      summarize(avgRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T))
-
-# ##
-# avg_clean1 <- df_merged %>%
-#                 group_by(experiment, source, grammatical, attractor_num, cat_n1) %>%
-#                 summarize(avgRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T))
-# 
-# p_avg_resp1 <- ggplot(avg_clean1 %>% subset(is.na(source) | source != "filler"), 
-#                      aes(grammatical, p_yes, #linetype = attractor_num, 
-#                          color = attractor_num, linetype = cat_n1, 
-#                          group = paste(attractor_num,cat_n1) )) + 
-#                 geom_point() + geom_line() + 
-#                 facet_wrap(cat_n1~experiment)
-# p_avg_resp1
-# 
-# ##
-# ##
-# 
-# avg_clean2 <- df_merged %>%
-#                 group_by(experiment, source, grammatical, attractor_num, cat_n2) %>%
-#                 summarize(avgRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T))
-# 
-# p_avg_resp2 <- ggplot(avg_clean2 %>% subset(is.na(source) | source != "filler"), 
-#                      aes(grammatical, p_yes, #linetype = attractor_num, 
-#                          color = attractor_num, linetype = cat_n2, 
-#                          group = paste(attractor_num,cat_n2) )) + 
-#                 geom_point() + geom_line() + 
-#                 facet_wrap(cat_n2~experiment)
-# p_avg_resp2
-# 
-# ##
-# ##
-# 
-# avg_clean3 <- df_merged %>%
-#                 group_by(experiment, source, grammatical, attractor_num, cat_n1n2) %>%
-#                 summarize(avgRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T))
-# 
-# p_avg_resp3 <- ggplot(avg_clean3 %>% subset(is.na(source) | source != "filler"), 
-#                      aes(grammatical, p_yes, #linetype = attractor_num, 
-#                          color = attractor_num, linetype = cat_n1n2, 
-#                          group = paste(attractor_num,cat_n1n2) )) + 
-#                 geom_point() + geom_line() + 
-#                 facet_wrap(~experiment)
-# p_avg_resp3
-# 
-# ##
-
-```
-
-```{r exp1AvgResponse, fig.height = 2.5, fig.width = 6, fig.cap="Estimates and 95% credible intervals for the analysis of the probability of a 'yes' response."}
 
@@
 
-p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) + geom_point(data = avg_fillers)
+p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) + geom_point(data = avg_fillers) + 
+              theme_bw() + theme( strip.background = element_rect(fill="white") ) +
+              xlab("") + ylab("Percentage 'acceptable'")
 
@@
 
-In Figure \@ref(fig:exp1AvgResponse), the y-axis shows the percentage of "acceptable" answers, and the x-axis indicates whether or not the sentences in that group are grammatical.
-As seen in the figure, `r round(as.numeric(avg_exp[3,6]), digits = 2)`% of the sentences with plural attractors and a singular verb were accepted by the participants, in line with the findings of @Lago2018.
-I also see a number attraction rate of `r round(as.numeric(avg_exp[3,6]), digits = 2)-round(as.numeric(avg_exp[4,6]), digits = 2)`% which was also observed in @Lago2018 with close results.
+Figure \@ref(fig:exp1AvgResponse) shows the percentage of "acceptable" answers as a function of sentence grammaticality and 
+with the grammaticality on the x-axis, and color marking the grammatical number of the attractor noun phrase.
+As seen in the figure, `r round(100*avg_exp[3,6])`% of the sentences with plural attractors and a singular verb were accepted by the participants, in line with the findings of @Lago2018.
+I also see a number attraction rate of `r round(100*(avg_exp[3,6]-avg_exp[4,6]))`% which was also observed in @Lago2018 with close results.
 
@@
 ```{r exp1ModelResponse, include=FALSE}
+
+library(brms)
 
@@
 
-n_chains <- 6
-n_cores <- 6
-n_iter <- 5000
-
+n_chains <- 4
+n_cores <- 4
+n_iter <- 2000
 fname_exp1_responses <- "../workspace_exp1/model_responses"
 
-library(brms)
-
-#with(df_merged_nofillers, cor(cFreqlog_n1, cFreqlog_n2))
-#with(df_merged_nofillers, cor(cFreqlog_n1, cFreqlog_n1n2))
-#with(df_merged_nofillers, cor(cFreqlog_n2, cFreqlog_n1n2))
-#
-# m <- glm(ResponseYes ~ (cFreqlog_n1n2) * #+ cFreqlog_n1n2
-#                         cEndsInVowel * cUngrammatical * cAttractorPlural,
-#                    data = df_merged_nofillers,
-#                    family = "binomial")
-# summary(m)
-
-# + cFreqlog_n1n2
-m_responses <- brm(ResponseYes ~ (cFreqlog_n1 + cFreqlog_n2) *
-                                  cEndsInVowel * cUngrammatical * cAttractorPlural + 
-                                 ((cFreqlog_n1 + cFreqlog_n2) * cUngrammatical * cAttractorPlural + 1| subject) +
+# to-do: Re-run, ESS low
+m_responses <- brm(ResponseYes ~ cEndsInVowel * cUngrammatical * cAttractorPlural + 
+                                 (cUngrammatical * cAttractorPlural + 1| subject) +
                                  (cUngrammatical * cAttractorPlural + 1| item),
                    data = df_merged_nofillers,
-                   init = "0",
+                   #init = "0",
                    family = bernoulli("probit"),
@@
 
-fname_exp3_responses <- "../workspace_exp1/model_responses_rt"
+fname_exp1_rts <- "../workspace_exp1/model_responses_rt"
 
@@
                    family = lognormal(),
-                   file = fname_exp3_responses, 
+                   file = fname_exp1_rts,
                    chains = n_chains, cores = n_cores, iter = n_iter)
@@
 
+<!-- to-do: relabel all 'vowel ending' stuff to be about ACC-GEN ambiguity -->
 ```{r exp1ResponseModelPlot, fig.height = 2.5, fig.width = 6, fig.cap="log-odd Estimates and 95% credible intervals for the regression coefficients in Accuracy."}
@@
 
-p_m_response <- stanplot(m_responses, pars = "^b_c" , type="areas")
-p_m_response <- p_m_response + xlab("Estimate (log-odds)")
+p_m_response <- create_model_coefs_plot( m_responses, plot_stats = T,
+                                  map_names = contrast_names,
+                              expand_right = 2.5, expand_top = 2, x_stat_adjust = 1.1
+                              ) + xlab("Estimate (log-odds)")
 print(p_m_response)
@@
 
-p_m_rt <- stanplot(m_rts, pars = "^b_c" , type="areas")
-p_m_rt <- p_m_rt + xlab("Estimate (log-odds)")
-print(p_m_rt)
+p_m_rts <- create_model_coefs_plot( m_rts, plot_stats = T, map_names = contrast_names,
+                              expand_right = 2.5, expand_top = 2, x_stat_adjust = 0.1
+                              )
+print(p_m_rts)
 
@@
 bad_subjects2 <- subset(avg_by_subj_wide2, delta_dc <= 0.25 ) %>% .$subject
-
-#dataAvBySubj %>% subset(subject %in% bad_subjects) %>% ggplot(aes(grammatical, p_yes, group = paste(experiment,attracted), color = experiment )) + geom_point() + geom_line(aes(linetype =attracted)) + facet_wrap(~subject)
 
@@
 
+df_exp2_na_nofillers <- subset(df_merge_exp2, is.na(ResponseYes))
+
 df_merged2 <- dplyr::bind_rows(df_merge_exp1, df_merge_exp2)
+df_merged2 %<>% subset(!is.na(ResponseYes))
 df_merged2$subject %<>% as.factor()
@@
 The procedure was exactly the same as Experiment 1.
-The participants in this experiment were completely different from Experiment 1.
+None of the participants in this experiment had participated in Experiment 1.
 
@@
 Every experimental item from both experiments (this experiment and Experiment (1) is included in the analysis. 
-Participants that could not exceed the threshold of 0.25 difference in *yes* answer between the condition (c) and (d), namely Ungrammatical, SG attractor and Grammatical, SG attractor, were excluded.
-I performed an analysis by fitting linear mixed-effect models to  my data, controlling for vowel ending, plural attractor, grammaticality and their interactions.
-Models were fit using Bernoulli distribution with probit link function and 95\% confidence intervals.
+Participants for whom the difference between grammatical and ungrammatical sentences with no potential for agreement attraction (conditions c and d) did not exceed a threshold of $0.25$ were deemed not to have performed the task as instructed, and their data was excluded from further analysis.
+In consequence, `r length(bad_subjects2)` participants' data was excluded.
+
+Across participants, `r sum(is.na(df_exp2_na_nofillers$ResponseYes))` trials were not responded to before the deadline (by `r length(unique(df_exp2_na_nofillers$subject))` participants).
+The data from these trials was not used in the analysis of responses or reaction times.
+
+We used `R` `r citep(citation())` and the *tidyverse* R packages `r citep(citation("tidyverse"))` for data processing and plotting, and the R packages *brms* `r citep(citation("brms"))` and *rstan* `r citep(citation("rstan"))` to fit Bayesian hierarchical models [e.g.,@GelmanHill:2007; @McElreath:2016; @BDA3].
+
+Participants' responses were analyzed using Bayesian hierarchical generalized linear models using a Bernoulli distribution with a probit link.
+Models of response times were fit using the lognormal distribution.
+Both models were fit with the predictors
+<!-- to-do: fix the below formulation -->
+\ldots predictors \ldots
+<!-- to-do: varying by-participants and by-items intercepts and slopes -->
 
 ### Results
+
+<!-- to-do: Omit the fillers from experiment 1 from plots unless they really add something to the interpretation. 
+            Mention it in the text instead, along with the fact that the 'acceptable' items were clearly no good at
+            doing what they were supposed to.
+-->
+
+<!-- to-do: add CIs to experiment 1 plot  -->
+<!-- to-do: add CIs to experiment 2 plot  -->
 
@@
 
-p_avg_resp2 <- ggplot(avg_exp2, 
-                     aes(grammatical, p_yes, #linetype = attractor_num, 
+p_avg_resp2 <- ggplot(avg_exp2, aes(grammatical, p_yes, #linetype = attractor_num, 
                                     color = attractor_num, group = attractor_num)) + 
                 geom_point() + geom_line() + 
-                facet_wrap(~experiment)
-
-p_avg_resp2 <- p_avg_resp2 + geom_line(data = avg_fillers) + geom_point(data = avg_fillers2)
+                facet_wrap(~experiment) +
+                theme_bw() + theme( strip.background = element_rect(fill="white") ) +
+                xlab("") + ylab("Percentage 'acceptable'")
 
@@
 ```{r exp2ModelResponse, include=FALSE}
-
-# # TODO: the following subjects have too much data: 11, 28, 36, 42, 55, 65, 73, 84, 92, 
-# #
-# x <- df_merged %>% subset(experiment == "Experiment 1") %>% group_by(subject) %>% dplyr::summarize(F = sum(is.na(attractor_num)),
-#                                                           N = length(is.na(attractor_num)) )
-# x %>% as.data.frame()
-# 
-# x$N %>% sum()
-# x$F %>% sum()
-
-#summary(as.factor(df_merged$attractor_num))
 
@@
 
-n_chains <- 6
-n_cores <- 6
-n_iter <- 5000
+n_chains <- 4
+n_cores <- 4
+n_iter <- 2000
 

### 2019-08-26 Paper/paper_draft.rmd
Update.

@@
 
-# Theories of attraction
-
-One of the theoretical attempts to explain such phenomenon was Marking and Morphing Theories [@Bock2001; @Eberhard2005 among others].
-The reason it is called *Marking* and *Morphing* is because there are two possible explanations within the framework with regards to where and when the attraction occurs.
+# Theories of agreement attraction
+
+One of the theoretical attempts to explain such phenomenon was *Marking and Morphing* [@Bock2001; @Eberhard2005 among others]. 
+<!-- to-do: PL, check whether the description below is correct. That's not how I remember it. -->
++
+*Marking* and *Morphing* assumes two possible explanations within the framework with regards to where and when the attraction occurs.
 The first possibility is the speaker can erroneously create a semantic representation of the head with the wrong number feature in the marking process in the marking process.
@@
 In the morphing process, these other morphemes with number information may contaminate the final number value with the percolation mechanism, which depends on the depth of the syntactic embedding.
-As the prediction goes, the more embedded an attractor is, the less attraction they trigger as shown in @Bock1992 in which authors show that attractors within a relative clause trigger less agreement attraction in the production.
-
-However, other studies have shown that other preverbal elements, such as objects, object relative clauses, object clefts, and object questions, may trigger agreement attraction [@Kimball1971; @Hartsuiker2001; @Franck2006; @Franck2015 among others].
-In sentences like \autoref{E2}, the pronominal object *hen* triggers and agreement attraction without being a part of the subject.
+One of the predictions of this account is that the more deeply embedded an attractor is, the less attraction it should trigger.
+\ldots presumably, there is even some evidence for it \ldots
+
+<!-- to-do: How is this related to depth???
+as shown in @Bock1992 in which authors show that attractors within a relative clause trigger less agreement attraction in the production. 
+-->
+
+Further studies have shown that other preverbal elements, such as objects, object relative clauses, object clefts, and object questions, may trigger agreement attraction [@Kimball1971; @Hartsuiker2001; @Franck2006; @Franck2015 among others].
+For example, @XXX showed that in sentences like \autoref{E2}, the pronominal object *hen* triggers and agreement attraction without being a part of the subject.
 +
@@
 \gll Theo denkt dat de knecht hen roep.\\
-     Theo thinks that the servant them call.\textsc{Pl}.\\
+     Theo thinks that the servant them call.\textsc{pl}.\\
 \trans  `Theo thinks that the servant \textit{call} them'}
@@
 
+<!-- to-do: please give example sentences more descriptive lables than 'E2'. Remember you're not numbering them, but labelling them. -->
+
 Since the Marking and Morphing theories put the source of the agreement attraction on the probe, i.e.
@@
 
-<!-- to-do: no idea what this means -->
-<!--
+<!-- to-do: no idea what the sentence below means 
 Regardless, these effects may be explained in a framework where the source of the agreement attraction is placed on the trigger, i.e. verb. 
 -->
-@Badecker2007 suggests that a process where the subject is retrieved from the memory plays a role in agreement attraction effects as well [see as well @Wagers2009].
-Building on the work in cue-based retrieval mechanism [@Gordon2001; @Lewis2005; @Lewis2006 among others], they argued that when speakers reach the verb, they try to retrieve the subject using certain features (cues) that essentially marks the *subjecthood*.
+
+<!-- to-do: I suggest that you use multiple author names or XxxEtAl in your citation keys. That way, you won't get the number agreement wrong when writing about a paper authored by several people. -->
+@Badecker2007 suggest that a process where the subject is retrieved from the memory plays a role in agreement attraction effects as well.
++
+<!-- to-do: Don't use "see also"/"cf." without a clear reason. 
+"Cf. X for a similar proposal" is fine, but
+"cf. X" isn't helpful.
+
+[see also @Wagers2009]. 
+-->
++
+<!-- to-do:
+Genuine question: What makes you think that @Gordon2001 is a "cue-based retrieval mechanism" paper??
+-->
++
+Building on the work on cue-based parsing [@Lewis2005; @Lewis2006 among others], they argued that when readers reach the verb, they try to retrieve the subject using certain features (cues) that essentially marks the *subjecthood*.
 Thus, any element that matches (or partially matches) with the cues in use may cause agreement attraction regardless of their position or syntactic relation to the subject.
 Going back to \autoref{E2}, it is expected, then, for an object which shares features like being preverbal, being a noun phrase, ability to bear agreement with a subject to trigger agreement attraction.
-
-Another challenge for the Marking and Morphing model was the grammaticality asymmetry.
-Due to the spreading activation formula utilized in the Marking and Morphing model [see @Dell1986], this model overgeneralizes the attraction effects to both ungrammatical and grammatical sentences and predicts both \autoref{E1} and \autoref{E3} to be present empirically, which is not the case [@Wagers2009].
+<!-- to-do: Plz revise the entire paragraph above for clarity. I don't think that you're sure what you mean here. -->
+
+<!-- to-do: Why "another" below? Did you mention another problem. -->
+Another challenge for the Marking and Morphing model was the grammaticality asymmetry. Due to the spreading activation formula 
+<!-- to-do: This is the first time you mention this formula, and the first time you mention that marking an morphing has anything to do with spreading activation.
+Please expand your explanation of M&M above.
+-->
+utilized in the Marking and Morphing model [see @Dell1986], this model overgeneralizes the attraction effects to both ungrammatical and grammatical sentences and predicts both \autoref{E1} and \autoref{E3} to be present empirically, which is not the case [@Wagers2009].
 
@@
 
+<!-- to-do: Move this paragraph up, before you mention the challenge for "Marking and morphing". Then conclude the section with the problem to M&M. This will improve the flow of the paragraph. -->
 On the other hand, cue-based retrieval models successfully predict the grammaticality asymmetry as shown by @Dillon2013 in an ACT-R simulation as well as numerous studies in self-paced reading, eye-tracking, and ERP studies [@Wagers2009; @Tucker2010; @Tanner2014; @Lago2015 among others].
@@
 
+<!-- to-do: This entire section needs rewriting, bigly! I'll do it.
+These reference-type sections don't go down well in psycholinguistics papers, because most ppl in the field don't care to learn more than they need to know about languages other than English.
+They also happen to interrupt the flow of the paper.
+-->
 ## Turkish relative clauses and plural marking

### 2019-08-28 Paper/paper_draft.rmd
Removed MPTs from draft, but added a new MPT to the models_mpt folder.

@@
 -->
-## Turkish relative clauses and plural marking
-
-Before discussing the experiments, I will touch upon the mechanisms that I utilize in the experiments: optional plural agreement, relative clause structure, and syncretism between possessive and accusative.
-
-Turkish plural agreement is quite similar with regards to the subject-verb number agreement in the first and second plural person.
-However, Turkish plural agreement is optional in third person plurals as shown in \autoref{TB1} and \autoref{TB2}.
-The other important characteristicc of Turkish plural agreement is the fact that the nominal and verbal plural marking is done by the same morpheme *-lAr*\footnote{The convention of using an uppercase A is to show that the morpheme can surface as either \textit{-ler} or \textit{-lar} according to the previous vowel due to the vowel harmony reasons.}.
-
-\begin{exe}
-\ex \label{TB1} Dün çocuk-\textsc{Lar} okul-a git-ti-\textsc{Ler} mi?
-\ex 
-\gll Dün çocuk-LAR okul-a git-ti mi?\\
-yesterday child-\textsc{Pl} school-\textsc{Dat} go-\textsc{Pst}(-\textsc{Pl}) Q\\
-\trans ``Did the children go to school yesterday?''
-\label{TB2}
-\end{exe}
-
-As for Turkish relative clauses, they always precede the external head noun [@Goksel2004; @Taylan2015] and they use either *-An* or *-dIk* nomilizers to show the referentiality of the subject within the relative clause as shown in \autoref{TB3} and \autoref{TB4} [@Haig1997].
-Moreover, due to pro-drop and null object properties of the Turkish [see @Ozturk2005], relative clauses can consist of only the verb itself in Turkish as in \autoref{TB5}.
-
-\begin{exe}
-\ex \label{TB3}
-\gll Kazı-lar-ın yap-ıl-dığ-ı alan ... \\
-excavation-\textsc{Pl}-\textsc{Gen} do-\textsc{Pass}-\textsc{Nmlz}-\textsc{Poss} area ... \\
-\glt ``The place where the excavations are done ...''
-\ex \label{TB4}
-\gll Kazı-lar yap-ıl-an alan ... \\
-excavation-\textsc{Pl} do-\textsc{Pass}-\textsc{Nmlz} area ... \\
-\glt ``A place where some excavations are done ...''
-\ex \label{TB5}
-\gll Gör-düğ-ü kuş çok güzel-di.\\
-see-\textsc{Nmlz}-\textsc{Poss} bird very pretty-\textsc{Pst}\\
-\glt ``The bird that he/she saw was very pretty.''
-\end{exe}
-
-Final characteristics that interest us in this paper is the morphological syncretism between the accusative case and possessive suffix in Turkish.
-When the possessive case is attached to a nominal stem that ends with a consonant, it is pronounced as \textit{-I}, which is exactly how the accusative case is also pronounced in the same environment in Turkish.
-However, the ambiguity is immediately resolved when they follow a nominal stem that ends with a vowel.
-In the latter environment, the accusative case surfaces as *-yI* whereas the possessive surfaces as *-sI(n)*\footnote{The final \textit{n} only surfaces when any other morphemes follow the possessive suffix.
-Otherwise, it surfaces as \textit{-sI}} as shown in \autoref{TB6}-\autoref{TB9}.
-
-\begin{exe}
-\ex
-\begin{xlist}
-\ex \label{TB6}
-\gll Kuş-\textbf{u} beğen-di-m.\\
-bird-\textsc{Acc} like-\textsc{Pst}-\textsc{1Sg}\\
-\glt ``I liked the bird.''
-\ex \label{TB7}
-\gll Emin'in kuş-\textbf{u} güzel-miş.\\
-Emin-\textsc{Gen} bird-\textsc{Poss} pretty-\textsc{Evd}\\
-\glt ``Emin's bird was pretty.''
-\ex \label{TB8}
-\gll Kedi-\textbf{yi} beğen-di-m.\\
-cat-\textsc{Acc} like-\textsc{Pst}-\textsc{1Sg}\\
-\glt ``I liked the cat.''
-\ex \label{TB9}
-\gll Emin'in kedi-\textbf{si} güzel-miş.\\
-Emin-\textsc{Gen} cat-\textsc{Poss} pretty-\textsc{Evd}\\
-\glt ``Emin's cat was pretty.''
-\end{xlist}
-\end{exe}
-
-# The Current Study
-
-In this study, I examine the question of whether agreement attraction is due to the shallow parsing that mainly depends on the memory of plural morpheme *-lAr* and matching the verbal plural morpheme with the nominal plural morpheme.
-
-First of all, I investigate the effects of ambiguous suffix with Experiment 1, which is a replication of @Lago2018.
+
+Agreement attraction in sentence comprehension has beeen attested in 
+English[@WagersEtAl:2009, @PatsonHusband:2015, @EnochsonCulbertson:2015, @HammerlyEtAl:2018]  (... more ...), 
+German [@ReifegersteEtAl:2016], 
+Arabic [@TuckerEtAl:2015], 
+Spanish [@LagoEtAl:2015], 
+Turkish [@LagoEtAl:2018], 
+Slovak [@BadeckerKuminiak:2007],
+Russian [@SlioussarMalko:2016], 
+Korean [@KwonSturt:2016]
+
+<!--
+production:
+  * @SlevcMartin:2016
+theoretical:
+  * @LinzenLeonard:2018
+  * @SmithFranck:2018
+  * @ParkerPhillips:2017
+  * @VasishthEtAl:2017 **
+other:
+  * @RisticMolinaroMancini:2016
+  * TannerBulkes:2015
+  * FranckColonnaRizzi:2015
+-->
+
+Recently, @Lago2018 demonstrated agreement attraction in Turkish. They used sentences like \ref{Lagoitem}, \ldots
+
 @Lago2018 makes use of genitive-possessive structures in the subject position, in which the possessive-marked noun is the head of the noun phrase which acts as the grammatical agreement controller, and the genitive noun serves as a potential attractor as in \autoref{Lagoitem}.
@@
 
+<!-- -->
+First of all, I investigate the effects of ambiguous suffix with Experiment 1, which is a replication of @Lago2018.
+
+# Experiment 1
+
+In this study, I examine the question of whether agreement attraction is due to the shallow parsing that mainly depends on the memory of plural morpheme *-lAr* and matching the verbal plural morpheme with the nominal plural morpheme.
+
+...
+
 With regards to percolation theories, this replication should yield no difference from @Lago2018.
@@
 An agreement attraction, then, is not a result of a partial matching or a representational error of number feature; instead, it is the result of a state of memory in which comprehenders misremember either the existence of the nominal plural morpheme or the place of the nominal plural morpheme as stated in the MPT model of the agreement attraction within shallow processor within \autoref{model1}, \autoref{model2}, \autoref{model3}\footnote{Author here wishes he knew more latex to do the MPT tree more neat.}.
-
-\begin{figure}[htb!]
-\centering
-\begin{tikzpicture}[
-    sibling distance        = 0.5em,
-    level distance          = 5em,
-    edge from parent/.style = {draw, -latex},
-    every node/.style       = {font=\scriptsize},
-    sloped
-  ]
-\Tree [.{\ }
-        \edge node[auto=left]{f}; [.\node[draw,rounded corners=.8ex]{generic failure};
-                                     \node[draw]{Ungrammatical};]
-        \edge node[auto=left]{1-f};
-        [.\node[draw,rounded corners=.8ex]{no failure};
-          \edge[dashed]; [.\node[]{Plural Verbs}; 
-                           \edge[dashed]; \node[]{With Distractor};
-                           \edge[dashed]; \node[]{Without Distractor};
-                         ] 
-          \edge[dashed]; [.\node[]{Singular Verbs}; 
-                          \edge[dashed]; [.\node[draw,rounded corners=.8ex]{No checking};
-                                           \node[draw]{Grammatical};]
-                         ] 
-        ] 
-      ]
-\end{tikzpicture}
-\caption{Proposed multinomial processing tree of how people judge sentences in a agreement attraction task}
-\label{model1}
-\end{figure}
-
-\begin{figure}[htb!]
-\centering
-\begin{tikzpicture}[
-    sibling distance        = 0.5em,
-    level distance          = 5em,
-    edge from parent/.style = {draw, -latex},
-    every node/.style       = {font=\scriptsize},
-    sloped
-  ]
-\Tree [.\node[]{Without Distractor}; 
-                                          \edge node[auto=left]{m$_2$}; [.\node[draw,rounded corners=.8ex]{No Memory of -lAr};
-                                                                        \edge node[auto=left]{g}; \node[draw]{Grammatical};
-                                                                        \edge node[auto=left]{1-g}; \node[draw]{Ungrammatical};]
-                                          \edge node[auto=left]{1-m$_2$}; [.\node[draw,rounded corners=.8ex]{Memory of -lAr}; 
-                                          \edge node[auto=left]{1-p$_2$}; [.\node[draw,rounded corners=.8ex]{No Place of -lAr};
-                                                                        \edge node[auto=left]{g}; \node[draw]{Grammatical};
-                                                                        \edge node[auto=left]{1-g}; \node[draw]{Ungrammatical};]
-                                          \edge node[auto=left]{p$_2$}; [.\node[draw,rounded corners=.8ex]{Misrepresented place of -lAr};
-                                                                        \node[draw]{Ungrammatical};]]]
-
-\end{tikzpicture}
-\caption{The Continuation of the proposed MPT with regards to the items which do not have an attractors with overt plural morphology but do have a plural marked verbs.}
-\label{model2}
-\end{figure}
-\begin{figure}[htb!]
-\centering
-\begin{tikzpicture}[
-    sibling distance        = 0.5em,
-    level distance          = 5em,
-    edge from parent/.style = {draw, -latex},
-    every node/.style       = {font=\scriptsize},
-    sloped
-  ]
-\Tree [.\node[]{With Distractor}; 
-                                          \edge node[auto=left]{m$_1$}; [.\node[draw,rounded corners=.8ex]{No Memory of -lAr};
-                                                                        \edge node[auto=left]{g}; \node[draw]{Grammatical};
-                                                                        \edge node[auto=left]{1-g}; \node[draw]{Ungrammatical};]
-                                          \edge node[auto=left]{1-m$_1$}; [.\node[draw,rounded corners=.8ex]{Memory of -lAr}; 
-                                          \edge node[auto=left]{1-p$_1$}; [.\node[draw,rounded corners=.8ex]{No Place of -lAr};
-                                                                        \edge node[auto=left]{g}; \node[draw]{Grammatical};
-                                                                        \edge node[auto=left]{1-g}; \node[draw]{Ungrammatical};]
-                                          \edge node[auto=left]{p$_1$}; [.\node[draw,rounded corners=.8ex]{Memory of place of -lAr};
-                                                                        \node[draw]{Grammatical};]]]
-
-\end{tikzpicture}
-\caption{The Continuation of the proposed MPT with regards to the items who have attractors with overt plural morphology and  plural marked verbs.}
-\label{model3}
-\end{figure}
 

### 2019-08-28 Paper/paper_draft.rmd
Update.

@@
   papaja::apa6_pdf:
-    citation_package: biblatex
     includes:
@@
 <!--
-header-includes   :
-  - \usepackage[utf8]{inputenc}
-  - \usepackage[T1]{fontenc}
-  - \usepackage{xcolor}
-  - \usepackage{hhline}
-  - \usepackage{mathtools}
-  - \linespread{1}
-  - \usepackage{gb4e}
-  - \noautomath #trying to see why shorttitle does not appear in the other paper. when done like this it appears.
-  - \usepackage{setspace}
-  - \makeatletter
-  - \apptocmd{\@exe}{\singlespacing}{}{}
-  - \makeatother
-  - \usepackage{sectsty}
-  - \allsectionsfont{\large}
-  - \usepackage{color}
-  - \usepackage{hyperref}
-  - \hypersetup{colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue} 
-  - \usepackage[english]{babel}
-  - \addto\extrasenglish{\renewcommand{\itemautorefname}{Item}}
-  - \renewcommand*{\nameyeardelim}{\addcomma\space}
-  - \usepackage{tikz}
-  - \usepackage{tikz-qtree}
-  - \let\eachwordone=\textit
-  - \usepackage{geometry}
-  - \geometry{margin=2cm}
-  - \usepackage{libertine}
-  - \usepackage{libertinust1math}
-  - \usepackage[T1]{fontenc}
-  - \usepackage{fancyhdr}
-  - \pagestyle{fancy}
-  - \fancyhf{}
-  - \rhead{Türk}
-  - \lhead{Agreement Attraction in Turkish}
-  - \rfoot{\thepage}
-  - \usepackage{lmodern}
-
--->
-
-<!--
-    includes:
-        in_header: paper_draft_preamble.tex
--->
+    citation_package: biblatex
+
+-->
+
 <!--

### 2019-08-29 Paper/paper_draft.rmd
Updates.

@@
       * Spanish: @LagoEtAl:2015
-      * Turkish: @LagoEtAl:2018
-      * Hammerly 2018 [@HammerlyEtAl:2018]
+      * Turkish: @LagoEtAl:2019
+      * Hammerly 2019 [@HammerlyEtAl:2019]
       * @LinzenLeonard:2018
@@
 <!-- to-do: mention the Lago et al study briefly since we'll be referring to it. -->
-In this paper, we report the results of two experiments about agreement attraction: The first experiment adressed a potential confound in the @Lago2018 study.
+In this paper, we report the results of two experiments about agreement attraction: The first experiment adressed a potential confound in the @LagoEtAl:2019 study.
 In the second experiment we tested an explanation of agreement attraction in Turkish as a task-specific strategy: we tested  whether verbs with plural agreement can serve as as potential attractors.
@@
 <!-- to-do: I suggest that you use multiple author names or XxxEtAl in your citation keys. That way, you won't get the number agreement wrong when writing about a paper authored by several people. -->
-@Badecker2007 suggest that a process where the subject is retrieved from the memory plays a role in agreement attraction effects as well.
-+
+@BadeckerKuminiak:2007 suggest that a process where the subject is retrieved from the memory plays a role in agreement attraction effects as well.
+
 <!-- to-do: Don't use "see also"/"cf." without a clear reason. 
@@
 
-[see also @Wagers2009]. 
--->
-+
+[see also @WagersEtAl:2009]. 
+-->
+
 <!-- to-do:
@@
 -->
-+
+
 Building on the work on cue-based parsing [@Lewis2005; @Lewis2006 among others], they argued that when readers reach the verb, they try to retrieve the subject using certain features (cues) that essentially marks the *subjecthood*.
@@
 -->
-utilized in the Marking and Morphing model [see @Dell1986], this model overgeneralizes the attraction effects to both ungrammatical and grammatical sentences and predicts both \autoref{E1} and \autoref{E3} to be present empirically, which is not the case [@Wagers2009].
+utilized in the Marking and Morphing model [see @Dell1986], this model overgeneralizes the attraction effects to both ungrammatical and grammatical sentences and predicts both \autoref{E1} and \autoref{E3} to be present empirically, which is not the case [@WagersEtAl:2009].
 
@@
 <!-- to-do: Move this paragraph up, before you mention the challenge for "Marking and morphing". Then conclude the section with the problem to M&M. This will improve the flow of the paragraph. -->
-On the other hand, cue-based retrieval models successfully predict the grammaticality asymmetry as shown by @Dillon2013 in an ACT-R simulation as well as numerous studies in self-paced reading, eye-tracking, and ERP studies [@Wagers2009; @Tucker2010; @Tanner2014; @Lago2015 among others].
+On the other hand, cue-based retrieval models successfully predict the grammaticality asymmetry as shown by @Dillon2013 in an ACT-R simulation as well as numerous studies in self-paced reading, eye-tracking, and ERP studies [@WagersEtAl:2009; @TuckerEtAl:2015; @TannerEtAl:2014; @LagoEtAl:2015 among others].
 This success was due to their replacement of source of the attraction.
@@
 Agreement attraction in sentence comprehension has beeen attested in 
-English[@WagersEtAl:2009, @PatsonHusband:2015, @EnochsonCulbertson:2015, @HammerlyEtAl:2018]  (... more ...), 
+Arabic [@TuckerEtAl:2015], 
+Armenian [@AvetisyanEtAl:2019],
+English [@WagersEtAl:2009; @PatsonHusband:2015; @EnochsonCulbertson:2015; @HammerlyEtAl:2019]  (... more ...), 
 German [@ReifegersteEtAl:2016],
-Arabic [@TuckerEtAl:2015], 
+Korean [@KwonSturt:2016],
+Russian [@SlioussarMalko:2016], 
+Slovak [@BadeckerKuminiak:2007],
 Spanish [@LagoEtAl:2015], 
-Turkish [@LagoEtAl:2018], 
-Slovak [@BadeckerKuminiak:2007],
-Russian [@SlioussarMalko:2016], 
-Korean [@KwonSturt:2016]
+Turkish [@LagoEtAl:2019]
 
@@
   * @VasishthEtAl:2017 **
+  * @LewisPhillips:2015
+  TannerEtAl:2014
+  TannerBulkes:2015
 other:
@@
 
-Recently, @Lago2018 demonstrated agreement attraction in Turkish. They used sentences like \ref{Lagoitem}, \ldots
-
-@Lago2018 makes use of genitive-possessive structures in the subject position, in which the possessive-marked noun is the head of the noun phrase which acts as the grammatical agreement controller, and the genitive noun serves as a potential attractor as in \autoref{Lagoitem}.
-In a speeded acceptability judgment study, @Lago2018 found a significant effect of number agreement attraction.
-However, the interpretation of their findings may be a result of the fact that non-subjecthood cues originate from their use of morphologically ambiguous forms of the possessive.
-In the possessive forms that are used, all the head nouns in their stimuli are ambiguous between possessive and accusative.
-
+<!--
+note: Utku's trees can go from left to right. The document below explains how:
+https://en.wikibooks.org/wiki/LaTeX/Linguistics
+-->
+
+# Agreement attraction in Turkish
+
+Recently, @LagoEtAl:2019 demonstrated agreement attraction in Turkish. In a speeded acceptability judgement study, they presented sentences like (\ref{Lagoitem}) to participants. 
+@LagoEtAl:2019 makes use of genitive-possessive structures in the subject position, in which the possessive-marked head of the complex noun phrase *'the singer's vocalist'* acts as the grammatical agreement controller, and the genitive noun serves as a potential attractor.
+
+<!-- to-do: where did the 'backup' come from in the translation ??? -->
+<!-- to-do: what is the singer's vocalist ??? does this expression make sense? -->
 \begin{exe}
 \ex \label{Lagoitem}
-\gll \c{S}ark{\i}c{\i}-n{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}-lar.\\
-singer-\textsc{Gen} vocalist-\textsc{Poss} stage-\textsc{Loc} non-stop jump-\textsc{Pst}-\textsc{3Pl}\\
+\gll *[Şarkıcı-nın \underline{vokalist-i}] sahne-de sürekli \underline{zıpla-dı-lar}.\\
+singer-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-\textsc{3pl}\\
 \glt The singer's backup vocalist jumped on the stage non-stop.
@@
 
+@LagoEtAl:2019 found a significant effect of number agreement attraction.
+They argue that genitive modifiers my cause agreement attraction in Turkish because Turkish makes frequent use of genitive subjects in embedded clauses.
+This would explain why genitive modifiers cause little to no agreement attraction in English
+[@NicolEtAl:2016]. <!-- to-do: read, double-check the claim above -->
+
+However, a potential complication in interpreting these results is the fact that all head nouns in Lago et al.'s stimuli were morphologically ambiguous between possessive and accusative case.
+\ldots two words of explanation why consonant-ending nouns are ambiguous \ldots
+
 In Turkish, accusative number agreement controllers are extremely rare, while genitive agreement controllers are very frequent.
-Thus, @Lago2018's finding could potentially be explained with occasional shallow processing.
-When all syntactic relations in the sentence were processed fully, the possessive noun may have been identified as the controller.
-Meanwhile, the genitive noun may sometimes have been erroneously identified as the controller during shallow processing because genitives are more likely to act as agreement controllers than accusatives.
-In order to check this effect, I have replicated @Lago2018 in Experiment 1.
-I have used different head nouns which ends with a vowel to differentiate between the accusative case and the possessive suffix, i.e.
-*taksici* (taxi driver) instead of *vokalist* in \autoref{Lagoitem}.
-
-<!-- -->
-First of all, I investigate the effects of ambiguous suffix with Experiment 1, which is a replication of @Lago2018.
+Thus, it is possible that the ambiguity of the head noun may occasionally render the genitive modifier a stronger contender for being the agreement controller, resulting in agreement attraction.
+
+In order to control for the effect of head noun ambiguity on the magnitude of agreement attraction, we replicated Lago et al.'s experiment with unambiguous head nouns.
+To this end, we modified Lago et al.'s stimuli by replacing the head nouns with unambiguous nouns.
+\ldots which end in a vowel to differentiate between the accusative case and the possessive suffix, i.e. *taksici* (taxi driver). 
+\ldots two words on why vowel-ending nouns don't exhibit this ambiguity \ldots
+For example, we changed sentence (\ref{Lagoitem}) to sentence (\ref{LagoiteModified}) instead of in \autoref{Lagoitem}.
+
+\begin{exe}
+\ex \label{LagoiteModified}
+\gll *[Şarkıcı-nın \underline{XXXX}] sahne-de sürekli \underline{zıpla-dı-lar}.\\
+singer-\textsc{gen} XXXX-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-\textsc{3pl}\\
+\glt The singer's XXXX jumped on the stage non-stop.
+\end{exe}
+
+<!-- to-do: 
+Some more details on the modification of nouns. Like, did we
+change only head nouns, or other parts too? How often?
+Did we change anything except the possessive and genitive nouns? If so, how often?
+-->
 
@@
 
-In this study, I examine the question of whether agreement attraction is due to the shallow parsing that mainly depends on the memory of plural morpheme *-lAr* and matching the verbal plural morpheme with the nominal plural morpheme.
-
-...
-
-With regards to percolation theories, this replication should yield no difference from @Lago2018.
-The syntactic depth has not changed, the number information of the head and distractor have not changed.
-Slight differences may be expected since I have changed some items which can be found in Appendix 1, and this situation can create erroneous number information to be used in the marking process.
-
-As for cue-based retrieval models, I should expect a lower agreement attraction effect in this replication.
-This prediction stems from the fact that the possibility of erroneous representation of features of the head noun is now lower due to  my efforts to differentiate between the accusative case and the possessive marking.
-@Lago2018 argues that due to the subjecthood information provided by the genitive case, there is an effect of agreement attraction.
-I eliminate the possibility of possible non-subjecthood clues given by the form that is shared by the accusative case and the possessive suffix.
-
-Within the shallow processing model, I would also expect a no change in the status of agreement attraction.
-In  my account of shallow processing, I argue that when the comprehenders reach the verb and saw plural morpheme, they engage in a matching mechanism where they try to match the verbal plural morpheme with a previous nominal plural morpheme.
-An agreement attraction, then, is not a result of a partial matching or a representational error of number feature; instead, it is the result of a state of memory in which comprehenders misremember either the existence of the nominal plural morpheme or the place of the nominal plural morpheme as stated in the MPT model of the agreement attraction within shallow processor within \autoref{model1}, \autoref{model2}, \autoref{model3}\footnote{Author here wishes he knew more latex to do the MPT tree more neat.}.
-
-In  my second experiment, I investigate the predictions made from  my model using a verbal plural morpheme within a distractor relative clause.
-As mentioned earlier, the verbal plural morpheme in Turkish is exactly the same as the nominal plural with regards to its stress, its behavior, and its form: *-lAr*.
-Since Turkish relative clauses are essentially nominals due to the nominalization process, they behave exactly like other nominals within the sentence [@Goksel2004; @Taylan2015].
-They can be marked with cases, plural agreement and they can have postpositions that any nominal also can.
-This syntactic formation enables us to question how shallow people process, how much syntactic information is relevant, or how perfectly people encode the features of the elements of the sentence.
-In  my experiment 2, I have used items in which the referential head noun of the subject is modified with a single-word relative clause as in \autoref{ouritem1}.
-
-\begin{exe}
-  \ex \label{ouritem1}
-      \gll D\"{o}v-d\"{u}k-(\textbf{ler})-i \c{c}ocuk mutfak-ta bayg{\i}n hal-de yat-{\i}yor-(\textbf{lar})-d{\i}.\\
-  beat-\textsc{Nmlz}-(\textsc{Pl})-\textsc{Poss} kid kitchen-\textsc{Loc} unconscious state-\textsc{Loc} lie-\textsc{Prog}-(\textsc{Pl})-\textsc{Pst}\\
-      \glt Intended: The kid that they beat were laying in the kitchen unconscious.
-\end{exe}
-
-Within the framework of percolation theories, I expect a harsh decline in the agreement attraction effects\footnote{Discussion with regards to how and where relative clauses adjoined is omitted due to the scope of the paper.
-However, it should be clear that a late insertion analysis where the relative clauses are actually above the head noun would yield different results.
-In this paper, I assume that modifiers like relative clauses are within the noun phrase, which deems them \textit{syntactically} deeper placed in the hierarchical three than the possessee.}.
-The reason for this expected decline is the fact that relative clauses being relative *deeper* in the hierarchical structure than the possessee of genitive-possessive structure.
-
-As for cue-based retrieval models, I would expect an agreement attraction quite similar to the one that I originally have in @Lago2018.
-The reason for this expected agreement attraction is the fact that apart from having a verbal root, the relative clauses and nominals behave exactly the same in terms of *nounness*.
-Like nominals, nominalized structures first marked with plural and then with the case or possessive suffix.
-From this perspective, it seems like there should be no difference.
-However, one may argue that the features related to the verbal and nominal can be encoded differently.
-Thus, there will no partial match at any time given due to the fact that verbal plural morpheme at the main verb does specify cues for a specific type of plural marking.
-One other question that may arise from this structure is that whether or not the parts of already-formed dependencies can feed the following dependency resolution.
-In other words, the verbal plural morpheme *-lar* on *dövdükleri* in \autoref{ouritem1} is already a trigger of a cue retrieval process.
-And, when it is merged with the nominal head *çocuk*, there is a formed semantic meaning that is  "a group of people has beaten a kid."  However, this *suggestion* assumes that relative clauses are formed at the very moment.
-Moreover, I also need to assume that after forming a relative clause they are unreachable, meaning that they do not contribute to the processing of the sentence, anymore.
-
-Lastly, in  my extremely shallow processing model, I would expect a significant effect of agreement attraction.
-Due to one of the writers' inability to *run the numbers* and *form the mpt trees in time*, this part---unfortunately---does not go beyond than a verbal argumentation.
-The reason I expect a significant effect of the agreement attraction is due to the fact that upon the agreement process is driven by the faulty memory of the place of the plural morpheme and uneducated guessing.
-Since the parsing is shallow, comprehenders do not engage in perfect attribution of the features, thus having a somewhat blurry representation behind.
-I expect this behavior to be omnipresent in other agreement attraction phenomenon that has been shown, as well as in @Lago2018 and in  my replication of it.
-Therefore, there is no reason to have anything to be different in experiment 2.
-
-## Experiment 1
+The aim of this study was examine the question of whether agreement attraction is due to the shallow parsing that mainly depends on the memory of plural morpheme *-lAr* and matching the verbal plural morpheme with the nominal plural morpheme.
 
@@
 
-In their study, @Lago2018 investigate the comprehension of subject-verb agreement  Turkish monolinguals.
-They use speeded acceptability judgments for the effects of number attraction in Turkish.
-Their sentences make us of genitive-possessive constructions in the subject position, where the genitive is the attractor and the possessive is the head noun.
-They manipulate the grammaticality of the sentence by changing the plural morphology of the verb, and they also manipulate the plurality of the attractor noun.
-In grammatical conditions, the subject and the verb both bear singular morphology with no overt morpheme.
-Moreover, in the ungrammatical conditions, the verb bears the overt *-lAr* morpheme whereas the subject is still singular as exemplified below.
+In order to test this hypothesis, I have replicated the experiment of @LagoEtAl:2019 with modified items, in which the possessive is not ambiguous with the accusative case.
+I tried to be as faithful as possible to the original sentences while also trying to make the sentences as plausible as possible.
+I keep the semantic relation between the head noun and the controller the same with what has been described in @LagoEtAl:2019, which is either a relation regarding profession or a service that is given by the head noun for the possessor.
+A set of sentences are exemplified below.
 
@@
 
-\ex \textsc{ungrammatical, sg attractor} \label{lago4}
-\gll \c{S}ark{\i}c{\i}-n{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}-lar.\\
-singer-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-\textsc{3Pl}\\
-\glt The singer's backup vocalist jumped on the stage non-stop.
-
-\ex \textsc{grammatical, pl attractor} \label{lago2}
-\gll \c{S}ark{\i}c{\i}-lar-{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}\\
-singer-\textsc{pl}-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-$\varnothing$\\
-\glt The singers' backup vocalist jumped on the stage non-stop.
-
-\ex \textsc{ungrammatical, sg attractor} \label{lago3}
-\gll \c{S}ark{\i}c{\i}-lar-{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}-lar.\\
-singer-\textsc{pl}-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-\textsc{3Pl}\\
-\glt The singers' backup vocalist jumped on the stage non-stop.
-
-\ex \textsc{grammatical, pl attractor} \label{lago1}
-\gll \c{S}ark{\i}c{\i}-n{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}\\
-singer-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-$\varnothing$\\
-\glt The singer's backup vocalist jumped on the stage non-stop.
+  \ex \textsc{ungrammatical, pl attractor} \label{exp1_a}
+      \gll Komedyen-ler-in yardımcı-sı poyraz-dan dolayi ü\c{s}ü-dü-ler.\\
+  comedian-\textsc{pl}-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}--\textsc{pl}\\
+      \glt Because of the northeaster, comedians' assistant felt chilly.
+
+  \ex \textsc{grammatical, pl attractor} \label{exp1_b}
+      \gll Komedyen-ler-in yardımcı-sı poyraz-dan dolayi ü\c{s}ü-dü.\\
+  comedian-\textsc{pl}-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}-$\varnothing$\\
+      \glt Because of the northeaster, comedians' assistant felt chilly.
+
+  \ex \textsc{ungrammatical, sg attractor} \label{exp1_c}
+      \gll Komedyen-in yardımcı-sı poyraz-dan dolayi ü\c{s}ü-dü-ler.\\
+  comedian-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}-\textsc{pl}\\
+      \glt Because of the northeaster, comedian's assistant felt chilly.
+
+  \ex \textsc{grammatical, sg attractor} \label{exp1_d}
+      \gll Komedyen-in yardımcı-sı poyraz-dan dolayi ü\c{s}ü-dü.\\
+  comedian-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}-$\varnothing$\\
+      \glt Because of the northeaster, comedian's assistant felt chilly.
 
@@
 
-They found a significant effect of number attraction in Turkish ranging between 11\%--15\% across monolinguals.
-@Lago2018 stipulate that the Turkish genitive case does not provide a strong cue against subjecthood since Turkish frequently makes use of genitive marked subjects in embedded clauses, as in \autoref{gensubj}.
-This is in contrast with English, in which the genitive case is compatible with subjecthood.
-Thus, @Lago2018 argue that this robust agreement attraction effect has been linked to the case information carried by accusative and genitive.
-
-\begin{exe}
-\ex \label{gensubj}
-\gll k\"{o}y-\"{u} bir haydut-un bas-t{\i}\u{g}-{\i}n-{\i} duy-du-m.\\
-village-\textsc{acc} a bandit-\textsc{gen} raid-\textsc{nmlz}-\textsc{3Sg}-\textsc{acc} hear-\textsc{pst}-\textsc{1Sg}\\
-\glt I heard that a (certain) robber raided the village. (Adapted from Woolford (2009))
-\end{exe}
-
-However,  my initial hypothesis postulates that participants engage in shallow processing, which results in a situation in which not only the genitive case but also the possessive case plays a significant role in delivering the case information.
-None of the experimental items in @Lago2018 have a head noun which ends with a vowel; thus, all of the possessive markers are morphologically and phonologically ambiguous between the accusative case and the possessive.
-Unlike the genitive case, it is extremely rare for the accusative case to appear on the head noun of the subject, which only occurs in raising predicates as in \autoref{dsm}.
-
-\begin{exe}
-\ex \label{dsm}
-\gll Ben sen-i git-ti-n san-d{\i}-m\\
-I you-\textsc{acc} go-\textsc{pst}-\textsc{2Sg} suppose-\textsc{pst}-\textsc{1Sg}\\
-\glt I thought you were gone.
-\end{exe}
-
-In order to test this hypothesis, I have replicated the experiment of @Lago2018 with modified items, in which the possessive is not ambiguous with the accusative case.
-I tried to be as faithful as possible to the original sentences while also trying to make the sentences as plausible as possible.
-I keep the semantic relation between the head noun and the controller the same with what has been described in @Lago2018, which is either a relation regarding profession or a service that is given by the head noun for the possessor.
-A set of sentences are exemplified below.
-
-\begin{exe}
-\ex
-  \begin{xlist}
-  \ex \underline{ungrammatical, pl attractor} \label{exp3}
-      \gll Komedyen-ler-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}-ler.\\
-  comedian-\textsc{pl}-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}--\textsc{pl}\\
-      \glt Because of the northeaster, comedians' assistant felt chilly.
-
-  \ex \underline{grammatical, pl attractor} \label{exp2}
-      \gll Komedyen-ler-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}.\\
-  comedian-\textsc{pl}-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}-$\varnothing$\\
-      \glt Because of the northeaster, comedians' assistant felt chilly.
-
-  \ex \underline{ungrammatical, sg attractor} \label{exp4}
-      \gll Komedyen-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}-ler.\\
-  comedian-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}-\textsc{pl}\\
-      \glt Because of the northeaster, comedian's assistant felt chilly.
-
-  \ex \underline{grammatical, sg attractor} \label{exp1}
-      \gll Komedyen-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}.\\
-  comedian-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}-$\varnothing$\\
-      \glt Because of the northeaster, comedian's assistant felt chilly.
-
-  \end{xlist}
-\end{exe}
-
-As seen in the examples, unlike @Lago2018's experimental items, all of  my items bear the *-sI* possessive marker instead of the ambiguous *-I* marker.
+As seen in the examples, unlike @LagoEtAl:2019's experimental items, all of  my items bear the *-sI* possessive marker instead of the ambiguous *-I* marker.
 As for the filler items, I could not use or modify the original experiment items since the fillers of the original study were not online.
@@
 \ex \label{fillera}
-\gll Adam-{\i}n anne-si fena-la\c{s}-{\i}nca inek kurban et-ti-ler.\\
+\gll Adam-ın anne-si fena-la\c{s}-ınca inek kurban et-ti-ler.\\
 man-\textsc{gen} mother-\textsc{poss} bad-\textsc{vrb}-\textsc{cvb} cow sacrifice do-\textsc{pst}-\textsc{pl}\\
@@
 \ex \label{fillerb}
-\gll *Pizzac{\i}-n{\i}n kurye-si t\"{o}kezle-yince sos-lar yer-e sa\c{c}-t{\i}.\\
+\gll *Pizzacı-nın kurye-si tökezle-yince sos-lar yer-e saç-tı.\\
 pizzaria-\textsc{gen} courier-\textsc{poss} trip-\textsc{cvb} sauce-\textsc{pl} floor-\textsc{dat} scatter-\textsc{pst}\\
@@
 In the experiments, participants were asked to judge the acceptability of Turkish sentences. All of the sentences were presented one word at a time in the center of the screen for 500 ms per word.
-<!-- unlike @Lago2018 and @Wagers2009, in which the duration was 300 ms per word. -->
+<!-- unlike @LagoEtAl:2019 and @WagersEtAl:2009, in which the duration was 300 ms per word. -->
 The experiment was run on *Ibex Farm*, a web-based experiment platform (\url{http://spellout.net/ibexfarm}).
@@
 In order to find out whether the noun class, and thus the presence of an ambiguity between genitive and accusative affected the magnitude of the agreement attraction effect, we analyzed the data from our experiment
-together with the data from @Lago2018.
+together with the data from @LagoEtAl:2019.
 
@@
 with the grammaticality on the x-axis, and color marking the grammatical number of the attractor noun phrase.
-As seen in the figure, `r round(100*avg_exp[3,6])`% of the sentences with plural attractors and a singular verb were accepted by the participants, in line with the findings of @Lago2018.
-I also see a number attraction rate of `r round(100*(avg_exp[3,6]-avg_exp[4,6]))`% which was also observed in @Lago2018 with close results.
+As seen in the figure, `r round(100*avg_exp[3,6])`% of the sentences with plural attractors and a singular verb were accepted by the participants, in line with the findings of @LagoEtAl:2019.
+I also see a number attraction rate of `r round(100*(avg_exp[3,6]-avg_exp[4,6]))`% which was also observed in @LagoEtAl:2019 with close results.
 
@@
 
-In Figure \@ref(fig:exp1AvgRTs), I see that average response times are significantly higher than the those of @Lago2018.
-I also see it in \@ref(exp1ResponseTimeModelPlot), since **b_cEndsinVowel** indicates whether or not it is Experiment 1 or Experiment from @Lago2018, i.e.
-distractors in items in @Lago2018 ends with a consonant, while ours ends in a vowel.
+In Figure \@ref(fig:exp1AvgRTs), I see that average response times are significantly higher than the those of @LagoEtAl:2019.
+I also see it in \@ref(exp1ResponseTimeModelPlot), since **b_cEndsinVowel** indicates whether or not it is Experiment 1 or Experiment from @LagoEtAl:2019, i.e.
+distractors in items in @LagoEtAl:2019 ends with a consonant, while ours ends in a vowel.
 Again, these results show the effect of disambiguation of the possessive suffix from the accusative case has surfaced as the difficulty in response and memory retrieval time.
@@
 
-Experiment 1 found number attraction effects, like also attested in @Lago2018, and also found a significant effect of form ambiguity of possessive and an interaction of plural attractor with ungrammaticality in response times.
+Experiment 1 found number attraction effects, like also attested in @LagoEtAl:2019, and also found a significant effect of form ambiguity of possessive and an interaction of plural attractor with ungrammaticality in response times.
 Illusionary agreement of the verb with the plural attractor was more than the singular attractor.
-In addition to what has been discussed by @Avetisyan2019.
+In addition to what has been discussed by @AvetisyanEtAl:2019.
 this results also show that not only the case itself but also the form of the case can affect the response times.
@@
 With more clearly formed genitive-possessive structures, participants do not have an easy time to partially match the cues with the phrases.
-This situation stems from the idea proposed by @Lago2018 with regards to the effects of the cases on numeral agreement attraction.
+This situation stems from the idea proposed by @LagoEtAl:2019 with regards to the effects of the cases on numeral agreement attraction.
 She argues that the frequency of the case being used in the subject position affects the agreement attraction effects in a positive manner.
 Since the accusative case is rarely used in Turkish, I have argued that it may give *wrong* clues an enable the distractors to even distract more.
-Yet, with clearly marked possessive suffix, I see that these enabling nature of the genitive possessive structure is eliminated, which is also shown in @Avetisyan2019.
+Yet, with clearly marked possessive suffix, I see that these enabling nature of the genitive possessive structure is eliminated, which is also shown in @AvetisyanEtAl:2019.
 
@@
 However, the existence of an extremely close degree of agreement attraction effects and non-significant nature of the effect of the vowel ending indicates that I cannot readily discard other explanations.
-Another reason for not jumping to the conclusion with percolation models can be related to the number of participants @Lago2018 have included in their study [see @Vasishth2018].
+Another reason for not jumping to the conclusion with percolation models can be related to the number of participants @LagoEtAl:2019 have included in their study [see @Vasishth2018].
+
+---
+
+Within the shallow processing model, I would also expect a no change in the status of agreement attraction.
+In  my account of shallow processing, I argue that when the comprehenders reach the verb and saw plural morpheme, they engage in a matching mechanism where they try to match the verbal plural morpheme with a previous nominal plural morpheme.
+An agreement attraction, then, is not a result of a partial matching or a representational error of number feature; instead, it is the result of a state of memory in which comprehenders misremember either the existence of the nominal plural morpheme or the place of the nominal plural morpheme as stated in the MPT model of the agreement attraction within shallow processor within \autoref{model1}, \autoref{model2}, \autoref{model3}\footnote{Author here wishes he knew more latex to do the MPT tree more neat.}.
+
+In  my second experiment, I investigate the predictions made from  my model using a verbal plural morpheme within a distractor relative clause.
+As mentioned earlier, the verbal plural morpheme in Turkish is exactly the same as the nominal plural with regards to its stress, its behavior, and its form: *-lAr*.
+Since Turkish relative clauses are essentially nominals due to the nominalization process, they behave exactly like other nominals within the sentence [@Goksel2004; @Taylan2015].
+They can be marked with cases, plural agreement and they can have postpositions that any nominal also can.
+This syntactic formation enables us to question how shallow people process, how much syntactic information is relevant, or how perfectly people encode the features of the elements of the sentence.
+In  my experiment 2, I have used items in which the referential head noun of the subject is modified with a single-word relative clause as in \autoref{ouritem1}.
+
+\begin{exe}
+  \ex \label{ouritem1}
+      \gll Döv-dük-(\textbf{ler})-i çocuk mutfak-ta baygın hal-de yat-ıyor-(\textbf{lar})-dı.\\
+  beat-\textsc{Nmlz}-(\textsc{Pl})-\textsc{Poss} kid kitchen-\textsc{Loc} unconscious state-\textsc{Loc} lie-\textsc{Prog}-(\textsc{Pl})-\textsc{Pst}\\
+      \glt Intended: The kid that they beat were laying in the kitchen unconscious.
+\end{exe}
+
+Within the framework of percolation theories, I expect a harsh decline in the agreement attraction effects\footnote{Discussion with regards to how and where relative clauses adjoined is omitted due to the scope of the paper.
+However, it should be clear that a late insertion analysis where the relative clauses are actually above the head noun would yield different results.
+In this paper, I assume that modifiers like relative clauses are within the noun phrase, which deems them \textit{syntactically} deeper placed in the hierarchical three than the possessee.}.
+The reason for this expected decline is the fact that relative clauses being relative *deeper* in the hierarchical structure than the possessee of genitive-possessive structure.
+
+As for cue-based retrieval models, I would expect an agreement attraction quite similar to the one that I originally have in @LagoEtAl:2019.
+The reason for this expected agreement attraction is the fact that apart from having a verbal root, the relative clauses and nominals behave exactly the same in terms of *nounness*.
+Like nominals, nominalized structures first marked with plural and then with the case or possessive suffix.
+From this perspective, it seems like there should be no difference.
+However, one may argue that the features related to the verbal and nominal can be encoded differently.
+Thus, there will no partial match at any time given due to the fact that verbal plural morpheme at the main verb does specify cues for a specific type of plural marking.
+One other question that may arise from this structure is that whether or not the parts of already-formed dependencies can feed the following dependency resolution.
+In other words, the verbal plural morpheme *-lar* on *dövdükleri* in \autoref{ouritem1} is already a trigger of a cue retrieval process.
+And, when it is merged with the nominal head *çocuk*, there is a formed semantic meaning that is  "a group of people has beaten a kid."  However, this *suggestion* assumes that relative clauses are formed at the very moment.
+Moreover, I also need to assume that after forming a relative clause they are unreachable, meaning that they do not contribute to the processing of the sentence, anymore.
+
+Lastly, in  my extremely shallow processing model, I would expect a significant effect of agreement attraction.
+Due to one of the writers' inability to *run the numbers* and *form the mpt trees in time*, this part---unfortunately---does not go beyond than a verbal argumentation.
+The reason I expect a significant effect of the agreement attraction is due to the fact that upon the agreement process is driven by the faulty memory of the place of the plural morpheme and uneducated guessing.
+Since the parsing is shallow, comprehenders do not engage in perfect attribution of the features, thus having a somewhat blurry representation behind.
+I expect this behavior to be omnipresent in other agreement attraction phenomenon that has been shown, as well as in @LagoEtAl:2019 and in  my replication of it.
+Therefore, there is no reason to have anything to be different in experiment 2.
+
+---
 
@@
 
-Having discussed the replication study of @Lago2018, I have shown that results favor the cue-based models, especially with the effect of disambiguated possessive suffix on response times.
+Having discussed the replication study of @LagoEtAl:2019, I have shown that results favor the cue-based models, especially with the effect of disambiguated possessive suffix on response times.
 However, due to the extremely similar effects on agreement attraction, I can still entertain shallow processing mechanism as explained in \autoref{model1}, \autoref{model2}, and \autoref{model3}.
@@
 The study consists of a speeded acceptability judgment experiment in the web-based platform Ibex Farm.
-In the experiment, I test whether or not speakers utilize even more shallow parser than what is stipulated by @Lago2018 and  my replication of @Lago2018 Experiment 2.
-This was investigated using syntactic structures similar to @Lago2018 materials, in which I have opted out the Genitive Construction (GC) for Relative Clause construction (RCC) as a distractor.
+In the experiment, I test whether or not speakers utilize even more shallow parser than what is stipulated by @LagoEtAl:2019 and  my replication of @LagoEtAl:2019 Experiment 2.
+This was investigated using syntactic structures similar to @LagoEtAl:2019 materials, in which I have opted out the Genitive Construction (GC) for Relative Clause construction (RCC) as a distractor.
 In Turkish, like GC, the relative clause in RCC precedes the head noun, and length-wise Turkish relative clauses can consist of only one word and the rest can be dropped.
@@
   \begin{xlist}
-  \ex \underline{Grammatical, SG attractor} \label{reg1}
-      \gll D\"{o}v-d\"{u}\u{g}-\"{u} \c{c}ocuk okul-a yorgun arg?n gel-di.\\
+  \ex \textsc{Grammatical, SG attractor} \label{reg1}
+      \gll Döv-düğ-ü çocuk okul-a yorgun arg?n gel-di.\\
   beat-\textsc{nmlz}-\textsc{poss} kid school-\textsc{dat} unconscious state-\textsc{loc} lie-\textsc{prog}-\textsc{pst}\\ 
       \glt The kid that he/she beats was laying in the kitchen unconscious.
-  \ex \underline{Grammatical, PL attractor} \label{reg2}
-      \gll D\"{o}v-d\"{u}k-ler-i \c{c}ocuk mutfak-ta bayg{\i}n hal-de yat-{\i}yor-du.\\
+  \ex \textsc{Grammatical, PL attractor} \label{reg2}
+      \gll Döv-dük-ler-i çocuk mutfak-ta baygın hal-de yat-ıyor-du.\\
   beat-\textsc{nmlz}-\textsc{pl}-\textsc{poss} kid kitchen-\textsc{loc} unconscious state-\textsc{loc} lie-\textsc{prog}-\textsc{pst}\\
       \glt The kid that they beat was laying in the kitchen unconscious.
-  \ex \underline{Ungrammatical, PL attractor} \label{reg3}
-      \gll D\"{o}v-d\"{u}k-ler-i \c{c}ocuk mutfak-ta bayg{\i}n hal-de yat-{\i}yor-lar-d{\i}.\\
+  \ex \textsc{Ungrammatical, PL attractor} \label{reg3}
+      \gll Döv-dük-ler-i çocuk mutfak-ta baygın hal-de yat-ıyor-lar-dı.\\
   beat-\textsc{nmlz}-\textsc{pl}-\textsc{poss} kid kitchen-\textsc{loc} unconscious state-\textsc{loc} lie-\textsc{prog}-\textsc{pl}-\textsc{pst}\\
       \glt Intended: The kid that they beat were laying in the kitchen unconscious.
-  \ex \underline{Ungrammatical, SG attractor} \label{reg4}
-      \gll D\"{o}v-d\"{u}\u{g}-\"{u} \c{c}ocuk mutfak-ta bayg{\i}n hal-de yat-{\i}yor-lar-d{\i}.\\
+  \ex \textsc{Ungrammatical, SG attractor} \label{reg4}
+      \gll Döv-düğ-ü çocuk mutfak-ta baygın hal-de yat-ıyor-lar-dı.\\
   beat-\textsc{nmlz}-\textsc{poss} kid kitchen-\textsc{loc} unconscious state-\textsc{loc} lie-\textsc{prog}-\textsc{pl}-\textsc{pst}\\

### 2019-09-01 Paper/paper_draft.rmd
More changes.

@@
                       echo = FALSE,
-                      results = 'hide')
+                      results = 'asis')
 options("citation_format" = "pandoc")
@@
 In order to control for the effect of head noun ambiguity on the magnitude of agreement attraction, we replicated Lago et al.'s experiment with unambiguous head nouns.
+
+# Experiment 1
+
+The aim of this study was examine the question of whether the agreement attraction effect @LagoEtAl:2019 found is mediated by the morphological ambiguity of the head noun.
 To this end, we modified Lago et al.'s stimuli by replacing the head nouns with unambiguous nouns. 
@@
 
-# Experiment 1
-
-The aim of this study was examine the question of whether agreement attraction is due to the shallow parsing that mainly depends on the memory of plural morpheme *-lAr* and matching the verbal plural morpheme with the nominal plural morpheme.
-
-```{r loadDataExp1, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-
-fname_data <- "../workspace_exp1/exp_data.rds"
-data <- readRDS(file = fname_data)
-
-# compute by-subject percentages of 'yes' responses, and average RTs 
-avg_by_subj <- data %>%
-                group_by(subject, experiment, condition, 
-                         grammatical, verb_num, attractor_num) %>%
-                summarize(avRT = mean(RT), 
-                          p_yes = mean(ResponseYes, na.rm = T), 
-                          N = sum(!is.na(ResponseYes))  )
-
-# reformat by-subject averages to a wide format
-avg_by_subj_wide <- avg_by_subj %>% 
-                      mutate(expcond = paste(experiment, condition, sep="_")) %>% 
-                      ungroup() %>%
-                      dplyr::select(-experiment, -condition, -avRT, -N,
-                                    -grammatical, -verb_num, -attractor_num) %>%
-                      tidyr::spread(expcond, p_yes) %>% 
-                      mutate(delta_dc = AgrAttr_d - AgrAttr_c)
-
-```
-
-```{r loadDataLago, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-
-# Load Lago et al.'s monolingual data
-fname_lagoetal <- "../Data/Lago_et_al/Lago_data.csv"
-df_lagoetal <- read.csv(fname_lagoetal, encoding = "UTF-8", as.is = T)
-df_lagoetal %<>% subset(Group == "monolingual")
-df_lagoetal %<>% dplyr::select(-Accuracy, -L1:-Group, -List:-SelfRateGerman)
-
-# Note: All rows with Experiment == "offline" also seem to be for 
-#       the UNP task ('Grammatical' is NA). I wonder if these were
-#       the same subjects, or if the subject labels were simply the same
-#       for the two experiments.
-with(df_lagoetal, stopifnot( is.na(Grammatical) == (Experiment == "offline") ))
-
-df_lagoetal_unp <- df_lagoetal %>% 
-                    subset(is.na(Grammatical)) %>%
-                    dplyr::select(-Grammatical:-Label)
-df_lagoetal_attr <- df_lagoetal %>% 
-                  subset(!is.na(Grammatical)) %>%
-                  dplyr::select(-Distance:-NewCond)
-```
-
-In order to test this hypothesis, I have replicated the experiment of @LagoEtAl:2019 with modified items, in which the possessive is not ambiguous with the accusative case.
-I tried to be as faithful as possible to the original sentences while also trying to make the sentences as plausible as possible.
-I keep the semantic relation between the head noun and the controller the same with what has been described in @LagoEtAl:2019, which is either a relation regarding profession or a service that is given by the head noun for the possessor.
-A set of sentences are exemplified below.
+We tried to keep the modified sentences as close as possible to the original sentences while also trying to make the sentences as plausible as possible.
+Like Lago et al., we keept the semantic relation between the head noun and the controller \ldots explain the relationship \ldots.
+
+### Materials
+
+Example (\ref{exp1_item}) shows one full set of experimental sentences. \ldots now explain the design again (yes, it's necessary) \ldots
+
+As seen in example (\ref{exp1_item}), unlike @LagoEtAl:2019's experimental sentences, the head nouns in our experiment are consonant-final and are therefore unambigously marked for posessive case -- the accusative form of *'yardımcı'* is *'XXX'*.
 
 \begin{exe}
-\ex
+\ex \label{exp1_item}
   \begin{xlist}
@@
 
-As seen in the examples, unlike @LagoEtAl:2019's experimental items, all of  my items bear the *-sI* possessive marker instead of the ambiguous *-I* marker.
-As for the filler items, I could not use or modify the original experiment items since the fillers of the original study were not online.
-I have used two types of filler sentences: grammatical sentences in which the verb bears plural agreement (\autoref{fillera}), and ungrammatical sentences in which the verb does not bear plural agreement (\autoref{fillerb}).
-I wanted to nullify a possible strategy by the participants where they associate the sentence-final morpheme directly with the acceptability of the sentence.
-And I also wanted to eliminate the possibility of participants disregarding other elements in the sentences while answering the questions I ask right after the sentence.
+We used two types of filler sentences: grammatical sentences in which the verb bears plural agreement, such as sentence (\ref{fillera}), and ungrammatical sentences with verbs without plural agreement, such as sentence (\ref{fillerb}).
+\ldots Were the fillers templatic like the experimental items, or not? If not, how did they vary? \ldots
+
+The purpose of using such filler sentences was to prevent participants from a adopting a response strategy of responding 'no' to sentences with verbs with plural agreement and 'yes' to verbs without plural agreement, while ignoring other words in the sentence.
 
@@
 
+```{r loadDataExp1, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+
+fname_data <- "../workspace_exp1/exp_data.rds"
+data_exp1 <- readRDS(file = fname_data)
+
+# compute by-subject percentages of 'yes' responses, and average RTs 
+avg_by_subj <- data_exp1 %>%
+                group_by(subject, experiment, condition, 
+                         grammatical, verb_num, attractor_num) %>%
+                summarize(avRT = mean(RT), 
+                          p_yes = mean(ResponseYes, na.rm = T), 
+                          N = sum(!is.na(ResponseYes))  )
+
+# reformat by-subject averages to a wide format
+avg_by_subj_wide <- avg_by_subj %>% 
+                      mutate(expcond = paste(experiment, condition, sep="_")) %>% 
+                      ungroup() %>%
+                      dplyr::select(-experiment, -condition, -avRT, -N,
+                                    -grammatical, -verb_num, -attractor_num) %>%
+                      tidyr::spread(expcond, p_yes) %>% 
+                      mutate(delta_dc = AgrAttr_d - AgrAttr_c)
+
+```
+
+```{r loadDataLago, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+
+# Load Lago et al.'s monolingual data
+fname_lagoetal <- "../Data/Lago_et_al/Lago_data.csv"
+df_lagoetal <- read.csv(fname_lagoetal, encoding = "UTF-8", as.is = T)
+df_lagoetal %<>% subset(Group == "monolingual")
+df_lagoetal %<>% dplyr::select(-Accuracy, -L1:-Group, -List:-SelfRateGerman)
+
+# Note: All rows with Experiment == "offline" also seem to be for 
+#       the UNP task ('Grammatical' is NA). I wonder if these were
+#       the same subjects, or if the subject labels were simply the same
+#       for the two experiments.
+with(df_lagoetal, stopifnot( is.na(Grammatical) == (Experiment == "offline") ))
+
+df_lagoetal_unp <- df_lagoetal %>% 
+                    subset(is.na(Grammatical)) %>%
+                    dplyr::select(-Grammatical:-Label)
+df_lagoetal_attr <- df_lagoetal %>% 
+                  subset(!is.na(Grammatical)) %>%
+                  dplyr::select(-Distance:-NewCond)
+
+df_lagoetal_attr %<>% mutate(ResponseYes = (Response == "yes") ) %>% 
+                      dplyr::select(-Response)
+df_lagoetal_attr %<>% ungroup() %>%
+                      dplyr::select(grammatical=Grammatical,
+                                    attractor_num=Attractor,
+                                    experiment=Experiment,
+                                    lagoetal_condition=Condition, 
+                                    subject=Participant, 
+                                    item=Item,
+                                    ResponseYes,
+                                    RT)
+
+# map to our condition labels
+lagoetal_condition_mapping <- data.frame(
+    condition = c("a", "b", "c", "d"),
+    lagoetal_condition = c("d", "b", "c", "a"), 
+    stringsAsFactors = F)
+
+df_lagoetal_attr %<>% left_join( lagoetal_condition_mapping, by = "lagoetal_condition" )
+
+# compute by-subject percentages of 'yes' responses, and average RTs 
+avg_by_subj_lagoetal <- df_lagoetal_attr %>%
+            group_by(subject, experiment, condition, grammatical, attractor_num) %>%
+            summarize(avRT = mean(RT), 
+                      p_yes = mean(ResponseYes, na.rm = T), 
+                      N = sum(!is.na(ResponseYes))  )
+
+# reformat by-subject averages to a wide format
+avg_by_subj_lagoetal_wide <- avg_by_subj_lagoetal %>% 
+            mutate(expcond = paste(experiment, condition, sep="_")) %>% 
+            ungroup() %>%
+            dplyr::select(-experiment, -condition, -avRT, -N,
+                          -grammatical, -attractor_num) %>%
+            tidyr::spread(expcond, p_yes) %>% 
+            mutate(delta_dc = online_d - online_c)
+
+```
+
 ### Participants and Procedure
 
-One hundred and seven Turkish speakers were recruited from Bogazici University in İstanbul.
+One hundred and eighteen Turkish speakers were recruited from the undergraduate population enrolled in linguistics classes at Bogazici University in İstanbul.
 We verified that Turkish was their native language and that they predominantly used it in their daily lives.
+<!-- to-do: When you say 'verified', do you mean 'asked'? 'Verify' sounds like you actually made sure they aren't lying. Tone down if appropriate. -->
+<!-- to-do: Did anyone say Turkish wasn't their first language? Did we exclude them? -->
+
 In the experiments, participants were asked to judge the acceptability of Turkish sentences. All of the sentences were presented one word at a time in the center of the screen for 500 ms per word.
@@
 
-Participants were instructed to quickly clasify sentences as acceptable or unacceptable based on their intuition.
+Participants were instructed to quickly classify sentences as acceptable or unacceptable based on their intuition.
 They were further informed about the $XXXX ms$ time limit for answering.
@@
 Each trial after the practice items started with a blank screen, followed by a word-by-word RSVP presentaion of the sentence in the center of the screen.
-After the sentence presentation, they were asked for a grammaticality judgment
-(Was the sentence you read was natural to you?) 
-<!-- Is this really how it was phrased? -->
-responded Q for *yes*, and P for *no*. 
+After the sentence presentation, they were asked for a grammaticality judgment.
+More specifically, they were asked:
+*'Was the sentence you read was natural to you?'*
+<!-- to-do: Is this really how it was phrased? -->
+Participants responded Q for *yes*, and P for *no*.
+
 The 40 experimental items were automatically divided into four lists according to a Latin-square design, and were intermixed with filler sentences, such that each participant saw 40 experimental items and 40 fillers in random order over the course of the experiment.
@@
 
-```{r loadFrequencies, eval =T, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+```{r loadFrequencies, eval=F, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
 
@@
 ```{r identifyBadSubjects, eval =T, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-# identify participants 
+
+# identify bad participants 
 bad_subjects <- subset(avg_by_subj_wide, delta_dc <= 0.25 ) %>% .$subject
-data_clean <- data %>% subset(!subject %in% bad_subjects)
+data_exp1_clean <- data_exp1 %>% subset(!subject %in% bad_subjects)
+
+# identify bad participants 
+bad_subjects_lagoetal <- subset(avg_by_subj_lagoetal_wide, delta_dc <= 0.25 ) %>% .$subject
+df_lagoetal_attr_clean <- df_lagoetal_attr %>% subset(!subject %in% bad_subjects_lagoetal)
+
 ```
@@
 
-df_merge_exp1 <- data_clean %>% ungroup() %>% 
+df_merge_exp1 <- data_exp1_clean %>% ungroup() %>% 
                       dplyr::select(source=experiment, 
@@
 df_merge_exp1$subject %<>% as.character()
-df_merge_exp1 %<>% left_join(word_freq_exp1, by = "item")
-
-df_lagoetal_attr %<>% mutate(ResponseYes = (Response == "yes") )
-df_merge_lago <- df_lagoetal_attr %>% ungroup() %>% 
-                      dplyr::select(grammatical=Grammatical,
-                                    attractor_num=Attractor,
-                                    #condition=Condition, 
-                                    subject=Participant, 
-                                    item=Item,
-                                    ResponseYes, RT)
-df_merge_lago %<>% left_join(word_freq_lago, by = "item")
-df_merge_lago$experiment <- "Lago et al. (2018)" 
+#df_merge_exp1 %<>% left_join(word_freq_exp1, by = "item")
+
+df_merge_lago <- df_lagoetal_attr_clean %>%
+                      ungroup() %>% 
+                      dplyr::select(grammatical, attractor_num,
+                                    subject, item, ResponseYes, RT)
+#df_merge_lago %<>% left_join(word_freq_lago, by = "item")
+df_merge_lago$experiment <- "Lago et al. (2019)" 
 df_merge_lago$source <- NA
@@
 
-<!-- to-do: find out if the items from experiment 1 and Lago's paper were minimal pairs. Should
-at least some of them have the same item id? -->
-
-In order to find out whether the noun class, and thus the presence of an ambiguity between genitive and accusative affected the magnitude of the agreement attraction effect, we analyzed the data from our experiment
+<!-- to-do: find out if the items from experiment 1 and Lago's paper were minimal pairs. Should at least some of them have the same item id? 
+To control for that, we'd probably need to use random effects for two sets of item ids, one cross-experimental, one within-experiment?? 
+-->
+
+In order to determine whether the ambiguity of the head noun type affected the magnitude of the agreement attraction effect, we analyzed the data from our experiment
 together with the data from @LagoEtAl:2019.
-
 Participants for whom the difference in the percentage of `yes` responses between grammatical and ungrammatical conditions without attraction (conditions c and d) was below $0.25$ were deemed to not have performed the task as instructed, and their data was excluded from further analysis.
-In consequence, `r length(bad_subjects)` participants' data was excluded.
-
-Across participants, `r sum(is.na(df_exp1_na_nofillers$ResponseYes))` trials were not responded to before the deadline (by `r length(unique(df_exp1_na_nofillers$subject))` participants).
+In consequence, the data for `r length(bad_subjects)` participants from experiment 1, and `r stopifnot(length(bad_subjects_lagoetal) == 1)` one participant from Lago et al.'s experiment was excluded from further analysis.
+Across participants, a total `r sum(is.na(df_exp1_na_nofillers$ResponseYes))` trials were not responded to before the deadline by `r length(unique(df_exp1_na_nofillers$subject))` participants.
 The data from these trials was not used in the analysis of responses or reaction times.
@@
 We used `R` `r citep(citation())` and the *tidyverse* R packages `r citep(citation("tidyverse"))` for data processing and plotting, and the R packages *brms* `r citep(citation("brms"))` and *rstan* `r citep(citation("rstan"))` to fit Bayesian hierarchical models [e.g.,@GelmanHill:2007; @McElreath:2016; @BDA3].
-
 Participants' responses were analyzed using Bayesian hierarchical generalized linear models using a Bernoulli distribution with a probit link.
@@
 Both models were fit with the predictors
-<!-- to-do: fix the below formulation -->
-vowel ending, plural attractor, grammaticality and their interactions. 
+head noun ambiguity, attractor number, grammaticality, their interactions, as well as varying by-participants and by-items intercepts with a maximal random-effect structure.
 <!-- to-do: varying by-participants and by-items intercepts and slopes -->
@@
 
-p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) + geom_point(data = avg_fillers) + 
-              theme_bw() + theme( strip.background = element_rect(fill="white") ) +
-              xlab("") + ylab("Percentage 'acceptable'")
+# p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) + 
+#                             geom_point(data = avg_fillers) +
+
+p_avg_resp <- p_avg_resp + theme( strip.background = element_rect(fill="white") ) +
+                           theme_bw() + xlab("") + ylab("Percentage 'acceptable'")
 
@@
 
-Figure \@ref(fig:exp1AvgResponse) shows the percentage of "acceptable" answers as a function of sentence grammaticality and 
-with the grammaticality on the x-axis, and color marking the grammatical number of the attractor noun phrase.
-As seen in the figure, `r round(100*avg_exp[3,6])`% of the sentences with plural attractors and a singular verb were accepted by the participants, in line with the findings of @LagoEtAl:2019.
-I also see a number attraction rate of `r round(100*(avg_exp[3,6]-avg_exp[4,6]))`% which was also observed in @LagoEtAl:2019 with close results.
+Figure \@ref(fig:exp1AvgResponse) shows the percentage of "acceptable" answers as a function of the grammatical of number the attractor noun phrase, and sentence grammaticality.
+While ungrammatical sentences with a plural attractor were found acceptable in `r round(100*avg_exp[[3,6]])`% of the cases, the accepability rate was only `r round(100*avg_exp[[4,6]])`% when the attractor was singular.
+This ovserved agreement attraction effect of `r round(100*(avg_exp[[3,6]]-avg_exp[[4,6]]))`%, as well as the condition averages are fairly close to Lago et al.'s attraction effect of `r round(100*(avg_exp[[7,6]]-avg_exp[[8,6]]))`%.
 
@@
   cEndsInVowel <- ifelse(experiment == "Experiment 1", .5, -.5)
-  cFreqlog_n1n2 <- scale(freqlog_n1n2)
-  cFreqlog_n1 <- scale(freqlog_n1)
-  cFreqlog_n2 <- scale(freqlog_n2)
+  #cFreqlog_n1n2 <- scale(freqlog_n1n2)
+  #cFreqlog_n1 <- scale(freqlog_n1)
+  #cFreqlog_n2 <- scale(freqlog_n2)
 })
@@
                     "cEndsInVowel:cUngrammatical:cAttractorPlural" = "Vowel Ending * Ungrammaticality * Plural Attractor")
+
+#options(warn = 2)
 

### 2019-09-01 scripts/misc.R

@@ -217,9 +217,10 @@ create_model_coefs_plot <- function(m,
     geom_errorbarh(aes(xmin = Q2.5, xmax = Q97.5), height=0) + 
     geom_vline(xintercept = 0, color = "grey")
   
-  if (plot_stats) {
-    
+  if (plot_stats)
+  {
     tbl$xmax <- with(tbl, max(c(Estimate, Q2.5, Q97.5))) + x_stat_adjust
+
     
     p <- p + scale_y_discrete(expand = expand_scale(mult = c(.05, .15*expand_top), 
                                                     add = c(0, 0)) )
@@ -230,9 +231,10 @@ create_model_coefs_plot <- function(m,
                            label = sprintf("[%s]", tbl$PBelowZeroStr)), 
                        family = "mono", hjust = "left")
     suppressWarnings({
+      label <- parse(text = "paste('P(', theta, ' < 0)')")
       p <-  p + geom_text(x = tbl$xmax[1], y = max(as.integer(tbl$coef))+1, 
                           # label = "P( < 0)", 
-                          label = parse(text = "paste('P(', theta, ' < 0)')"),
+                          label = label,
                           family = "mono", hjust = "left")#, fontface = "bold")
     })
   }

### 2019-09-03 Paper/paper_draft.rmd
Update.

@@
       * Spanish: @LagoEtAl:2015
-      * Turkish: @LagoEtAl:2019
+      * Turkish: @LagoEtAl:2018
       * Hammerly 2019 [@HammerlyEtAl:2019]
@@
 <!-- to-do: mention the Lago et al study briefly since we'll be referring to it. -->
-In this paper, we report the results of two experiments about agreement attraction: The first experiment adressed a potential confound in the @LagoEtAl:2019 study.
+In this paper, we report the results of two experiments about agreement attraction: The first experiment adressed a potential confound in the @LagoEtAl:2018 study.
 In the second experiment we tested an explanation of agreement attraction in Turkish as a task-specific strategy: we tested  whether verbs with plural agreement can serve as as potential attractors.
@@
 Spanish [@LagoEtAl:2015], 
-Turkish [@LagoEtAl:2019]
+Turkish [@LagoEtAl:2018]
 
@@
 
-Recently, @LagoEtAl:2019 demonstrated agreement attraction in Turkish. In a speeded acceptability judgement study, they presented sentences like (\ref{Lagoitem}) to participants. 
-@LagoEtAl:2019 makes use of genitive-possessive structures in the subject position, in which the possessive-marked head of the complex noun phrase *'the singer's vocalist'* acts as the grammatical agreement controller, and the genitive noun serves as a potential attractor.
+Recently, @LagoEtAl:2018 demonstrated agreement attraction in Turkish. In a speeded acceptability judgement study, they presented sentences like (\ref{Lagoitem}) to participants. 
+@LagoEtAl:2018 makes use of genitive-possessive structures in the subject position, in which the possessive-marked head of the complex noun phrase *'the singer's vocalist'* acts as the grammatical agreement controller, and the genitive noun serves as a potential attractor.
 
@@
 
-@LagoEtAl:2019 found a significant effect of number agreement attraction.
+@LagoEtAl:2018 found a significant effect of number agreement attraction.
 They argue that genitive modifiers my cause agreement attraction in Turkish because Turkish makes frequent use of genitive subjects in embedded clauses.
@@
 
-The aim of this study was examine the question of whether the agreement attraction effect @LagoEtAl:2019 found is mediated by the morphological ambiguity of the head noun.
+The aim of this study was examine the question of whether the agreement attraction effect @LagoEtAl:2018 found is mediated by the morphological ambiguity of the head noun.
 To this end, we modified Lago et al.'s stimuli by replacing the head nouns with unambiguous nouns. 
@@
 
-As seen in example (\ref{exp1_item}), unlike @LagoEtAl:2019's experimental sentences, the head nouns in our experiment are consonant-final and are therefore unambigously marked for posessive case -- the accusative form of *'yardımcı'* is *'XXX'*.
+As seen in example (\ref{exp1_item}), unlike @LagoEtAl:2018's experimental sentences, the head nouns in our experiment are consonant-final and are therefore unambigously marked for posessive case -- the accusative form of *'yardımcı'* is *'XXX'*.
 
@@
 
+### note: the low accuracy on fillers is not caused by a couple of items
+# filler_avgs <- 
+# data_exp1 %>% subset(Type == "filler") %>% group_by(Item, condition) %>% 
+#               summarize(M = mean(ResponseYes, na.rm = T)) %>%
+#               arrange(condition, Item)
+# fillers %>% subset(condition == "a") 
+# fillers %>% subset(condition == "b")
+###
+
 # compute by-subject percentages of 'yes' responses, and average RTs 
@@
 In the experiments, participants were asked to judge the acceptability of Turkish sentences. All of the sentences were presented one word at a time in the center of the screen for 500 ms per word.
-<!-- unlike @LagoEtAl:2019 and @WagersEtAl:2009, in which the duration was 300 ms per word. -->
+<!-- unlike @LagoEtAl:2018 and @WagersEtAl:2009, in which the duration was 300 ms per word. -->
 The experiment was run on *Ibex Farm*, a web-based experiment platform (\url{http://spellout.net/ibexfarm}).
@@
 #df_merge_lago %<>% left_join(word_freq_lago, by = "item")
-df_merge_lago$experiment <- "Lago et al. (2019)" 
+df_merge_lago$experiment <- "Lago et al. (2018)" 
 df_merge_lago$source <- NA
@@
 In order to determine whether the ambiguity of the head noun type affected the magnitude of the agreement attraction effect, we analyzed the data from our experiment
-together with the data from @LagoEtAl:2019.
+together with the data from @LagoEtAl:2018.
 Participants for whom the difference in the percentage of `yes` responses between grammatical and ungrammatical conditions without attraction (conditions c and d) was below $0.25$ were deemed to not have performed the task as instructed, and their data was excluded from further analysis.
@@
 Participants' responses were analyzed using Bayesian hierarchical generalized linear models using a Bernoulli distribution with a probit link. 
-Models of response times were fit using the lognormal distribution.
-Both models were fit with the predictors
+Response times were modeled assuming lognormally distributed errors.
+Models of response times were fit using the lognormal distribution. Both models were fit with the predictors
 head noun ambiguity, attractor number, grammaticality, their interactions, as well as varying by-participants and by-items intercepts with a maximal random-effect structure.
@@
 ### Results
+
+<!-- to-do: confidence intervals in plot, here and elsewhere -->
 
@@
                            theme_bw() + xlab("") + ylab("Percentage 'acceptable'")
-
+p_avg_resp <- p_avg_resp + scale_y_continuous(labels=scales::percent)#, breaks = c(0, .25, .5, .75, 1))
+p_avg_resp <- p_avg_resp + theme_bw()
+p_avg_resp <- p_avg_resp + scale_color_discrete(name = "Attractor Number")
 print(p_avg_resp)
@@
 
-Figure \@ref(fig:exp1AvgResponse) shows the percentage of "acceptable" answers as a function of the grammatical of number the attractor noun phrase, and sentence grammaticality.
-While ungrammatical sentences with a plural attractor were found acceptable in `r round(100*avg_exp[[3,6]])`% of the cases, the accepability rate was only `r round(100*avg_exp[[4,6]])`% when the attractor was singular.
-This ovserved agreement attraction effect of `r round(100*(avg_exp[[3,6]]-avg_exp[[4,6]]))`%, as well as the condition averages are fairly close to Lago et al.'s attraction effect of `r round(100*(avg_exp[[7,6]]-avg_exp[[8,6]]))`%.
-
-In Figure \@ref(fig:exp1ResponseModelPlot), I clearly see the effects of ungrammaticality and the interaction between the ungrammaticality and plural attractor.
+Figure \@ref(fig:exp1AvgResponse) shows the percentages of "acceptable" answers for experiment 1 as well as the Lago et al.
+data as a function of sentence grammaticality and the grammatical of number the attractor noun phrase.
+In our data, while ungrammatical sentences with a plural attractor were found acceptable in `r round(100*avg_exp[[3,6]])`% of the cases, the accepability rate was only `r round(100*avg_exp[[4,6]])`% when the attractor was singular.
+This observed agreement attraction effect of `r round(100*(avg_exp[[3,6]]-avg_exp[[4,6]]))`%, as well as the condition averages were fairly close to Lago et al.'s attraction effect of `r round(100*(avg_exp[[7,6]]-avg_exp[[8,6]]))`%.
+
+Figure \@ref(fig:exp1ResponseModelPlot) shows the estimates of the fixed effects of a Bayesian hierarchical model.
+It shows that ungrammatical sentences were judged as acceptable far less often than grammatical sentences (CI = [XXX]).
+It also shows that sentences with plural attractors were considered acceptable a little bit better than sentences (CI = [XXX]) with singular attractors.
+Importantly, we found an interaction between these two factors, such that plural attractors increased the likelihood of 'acceptable' responses disproportionately more in ungrammatical sentences (CI = [XXX]).
+
+<!-- to-do: fix-me, pavel --> 
+<!-- three-way interaction between ambiguity, ungrammaticality, and attractor number -->
+We found a small positive effect \ldots
+evidence that the ambiguity of the head noun affects the effect of attractor number on ungrammaticality (CI = [XXX]).
+\ldots no interesting difference between experiments \ldots
+\ldots we may even have produced a bayes factor or LOO metric, to test whether that three way interaction actually matters
 I see that the vowel ending is not significant even though it has a negative effect. 
@@
   cAttractorPlural <- ifelse(attractor_num == "plural", .5, -.5)
-  cEndsInVowel <- ifelse(experiment == "Experiment 1", .5, -.5)
+  cEndsInConsonant <- ifelse(experiment != "Experiment 1", .5, -.5)
   #cFreqlog_n1n2 <- scale(freqlog_n1n2)
@@
 # m <- glm(ResponseYes ~ (cFreqlog_n1 + cFreqlog_n2) *
-#            cEndsInVowel * cUngrammatical * cAttractorPlural,
+#            cEndsInConsonant * cUngrammatical * cAttractorPlural,
 #          data = df_merged_nofillers,
@@
 n_iter <- 2000
+
 fname_exp1_responses <- "../workspace_exp1/model_responses"
-
-# to-do: Re-run, ESS low
-m_responses <- brm(ResponseYes ~ cEndsInVowel * cUngrammatical * cAttractorPlural + 
+m_responses <- brm(ResponseYes ~ cEndsInConsonant * cUngrammatical * cAttractorPlural + 
                                  (cUngrammatical * cAttractorPlural + 1| subject) +
@@
                    data = df_merged_nofillers,
-                   #init = "0",
                    family = bernoulli("probit"),
@@
 
+fname_exp1_responses_minimal <- "../workspace_exp1/model_responses_minimal"
+m_responses_minimal <- brm(ResponseYes ~ (cEndsInConsonant + cUngrammatical + cAttractorPlural)^2 + 
+                                         (cUngrammatical * cAttractorPlural + 1| subject) +
+                                         (cUngrammatical * cAttractorPlural + 1| item),
+                   data = df_merged_nofillers,
+                   family = bernoulli("probit"),
+                   file = fname_exp1_responses_minimal, 
+                   chains = n_chains, cores = n_cores, iter = n_iter)
+
 fname_exp1_rts <- "../workspace_exp1/model_responses_rt"
-
-m_rts <- brm(RT ~ cEndsInVowel * cUngrammatical * cAttractorPlural +
+m_rts <- brm(RT ~ cEndsInConsonant * cUngrammatical * cAttractorPlural +
                                  (cUngrammatical * cAttractorPlural + 1| subject) +
@@
 <!-- to-do: relabel all 'vowel ending' stuff to be about ACC-GEN ambiguity -->
-```{r exp1ResponseModelPlot, fig.height = 2.5, fig.width = 6, fig.cap="log-odd Estimates and 95% credible intervals for the regression coefficients in Accuracy."}
+<!-- to-do: make sure the CIs are HPDIs, and say so -->
+
+```{r exp1ResponseModelPlot, fig.height = 2.5, fig.width = 6, fig.cap="Estimates and 95% credible intervals for the regression coefficients in accuracy (log-odds units)."}
 
@@
                     "cUngrammatical:cAttractorPlural" = "Ungrammaticality * Plural Attractor",
-                    "cEndsInVowel" = "Vowel Ending",
-                    "cEndsInVowel:cUngrammatical" = "Ungrammaticality * Vowel Ending",
-                    "cEndsInVowel:cAttractorPlural" = "Vowel Ending * Plural Attractor",
-                    "cEndsInVowel:cUngrammatical:cAttractorPlural" = "Vowel Ending * Ungrammaticality * Plural Attractor")
-
-#options(warn = 2)
-
-p_m_response <- create_model_coefs_plot( m_responses, plot_stats = T,
-                                  map_names = contrast_names,
-                              expand_right = 2.5, expand_top = 2, x_stat_adjust = 1.1
-                              ) + xlab("Estimate (log-odds)")
-print(p_m_response)
-
-```
-
-```{r exp1ResponseTimeModelPlot, fig.height = 2.5, fig.width = 6, fig.cap="log-odd Estimates and 95% credible intervals for the regression coefficients in Reading Times."}
-
-p_m_rts <- create_model_coefs_plot( m_rts, plot_stats = T, map_names = contrast_names,
-                              expand_right = 2.5, expand_top = 2, x_stat_adjust = 0.1
-                              )
-print(p_m_rts)
-
-```
-
-In Figure \@ref(fig:exp1AvgRTs), I see that average response times are significantly higher than the those of @LagoEtAl:2019.
-I also see it in \@ref(exp1ResponseTimeModelPlot), since **b_cEndsinVowel** indicates whether or not it is Experiment 1 or Experiment from @LagoEtAl:2019, i.e.
-distractors in items in @LagoEtAl:2019 ends with a consonant, while ours ends in a vowel.
+                    "cEndsInConsonant" = "Ambiguity",
+                    "cEndsInConsonant:cUngrammatical" = "Ambiguity * Ungrammaticality",
+                    "cEndsInConsonant:cAttractorPlural" = "Ambiguity * Plural Attractor",
+                    "cEndsInConsonant:cUngrammatical:cAttractorPlural" = "Ambiguity * Ungrammaticality * Plural Attractor")
+
+p_m_response <- 
+  create_model_coefs_plot( m_responses, 
+        plot_stats = T, map_names = contrast_names,
+        expand_right = 2.5, expand_top = 2, x_stat_adjust = 1.1,
+        x_breaks = c(-3,-2,-1, 0,1, 2) ) + 
+        xlab("Estimate (log-odds)")
+
+suppressWarnings({
+print(p_m_response + annotate(x=-3, xend=2, y=0, yend=0, lwd=0.25, geom="segment"))
+})
+
+```
+
+Figure \@ref(fig:exp1AvgRTs) shows higher
+
+, I see that average response times are significantly higher than the those of @LagoEtAl:2018.
+I also see it in \@ref(exp1ResponseTimeModelPlot), since **b_cEndsinVowel** indicates whether or not it is Experiment 1 or Experiment from @LagoEtAl:2018, i.e.
+distractors in items in @LagoEtAl:2018 ends with a consonant, while ours ends in a vowel.
 Again, these results show the effect of disambiguation of the possessive suffix from the accusative case has surfaced as the difficulty in response and memory retrieval time.
 
-```{r exp1AvgRTs, fig.height=2.5, fig.width = 6, fig.cap="Average response times for  my replication and Lago et. al. (2018)"}
-
-p_avg_rt <- ggplot(avg_clean, aes(grammatical, avgRT, linetype = attractor_num, color = experiment, group = paste(experiment, attractor_num))) + geom_point() + geom_line()
+```{r exp1AvgRTs, fig.height=2.5, fig.width = 6, fig.cap="Average response times for experiment 1 and Lago et. al. (2018)"}
+
+p_avg_rt <- avg_exp %>% ggplot(aes(grammatical, avgRT, linetype = attractor_num, color = experiment, group = paste(experiment, attractor_num))) + geom_point() + geom_line() + ylab("Response Time (ms)")
 
@@
 
+<!-- to-do: confidence intervals in plot -->
+```{r exp1ResponseTimeModelPlot, fig.height = 2.5, fig.width = 6, fig.cap="Estimates and 95% credible intervals for the regression coefficients in response times (log units)."}
+
+p_m_rts <- 
+  create_model_coefs_plot(
+        m_rts, plot_stats = T, map_names = contrast_names,
+        expand_right = 2.5, expand_top = 2, x_stat_adjust = 0.1,
+        x_breaks = c(-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3) )
+
+suppressWarnings({
+print(p_m_rts + annotate(x=-0.3, xend=0.3, y=0, yend=0, lwd=0.25, geom="segment") )
+})
+```
+
 ### Discussion
 
-Experiment 1 found number attraction effects, like also attested in @LagoEtAl:2019, and also found a significant effect of form ambiguity of possessive and an interaction of plural attractor with ungrammaticality in response times.
+Experiment 1 found number attraction effects, like also attested in @LagoEtAl:2018, and also found a significant effect of form ambiguity of possessive and an interaction of plural attractor with ungrammaticality in response times.
 Illusionary agreement of the verb with the plural attractor was more than the singular attractor.
@@
 With more clearly formed genitive-possessive structures, participants do not have an easy time to partially match the cues with the phrases.
-This situation stems from the idea proposed by @LagoEtAl:2019 with regards to the effects of the cases on numeral agreement attraction.
+This situation stems from the idea proposed by @LagoEtAl:2018 with regards to the effects of the cases on numeral agreement attraction.
 She argues that the frequency of the case being used in the subject position affects the agreement attraction effects in a positive manner.
@@
 However, the existence of an extremely close degree of agreement attraction effects and non-significant nature of the effect of the vowel ending indicates that I cannot readily discard other explanations.
-Another reason for not jumping to the conclusion with percolation models can be related to the number of participants @LagoEtAl:2019 have included in their study [see @Vasishth2018].
+Another reason for not jumping to the conclusion with percolation models can be related to the number of participants @LagoEtAl:2018 have included in their study [see @Vasishth2018].
 
@@
 
-As for cue-based retrieval models, I would expect an agreement attraction quite similar to the one that I originally have in @LagoEtAl:2019.
+As for cue-based retrieval models, I would expect an agreement attraction quite similar to the one that I originally have in @LagoEtAl:2018.
 The reason for this expected agreement attraction is the fact that apart from having a verbal root, the relative clauses and nominals behave exactly the same in terms of *nounness*.
@@
 Since the parsing is shallow, comprehenders do not engage in perfect attribution of the features, thus having a somewhat blurry representation behind.
-I expect this behavior to be omnipresent in other agreement attraction phenomenon that has been shown, as well as in @LagoEtAl:2019 and in  my replication of it.
+I expect this behavior to be omnipresent in other agreement attraction phenomenon that has been shown, as well as in @LagoEtAl:2018 and in  my replication of it.
 Therefore, there is no reason to have anything to be different in experiment 2.
@@
 
-Having discussed the replication study of @LagoEtAl:2019, I have shown that results favor the cue-based models, especially with the effect of disambiguated possessive suffix on response times.
+Having discussed the replication study of @LagoEtAl:2018, I have shown that results favor the cue-based models, especially with the effect of disambiguated possessive suffix on response times.
 However, due to the extremely similar effects on agreement attraction, I can still entertain shallow processing mechanism as explained in \autoref{model1}, \autoref{model2}, and \autoref{model3}.
@@
 The study consists of a speeded acceptability judgment experiment in the web-based platform Ibex Farm.
-In the experiment, I test whether or not speakers utilize even more shallow parser than what is stipulated by @LagoEtAl:2019 and  my replication of @LagoEtAl:2019 Experiment 2.
-This was investigated using syntactic structures similar to @LagoEtAl:2019 materials, in which I have opted out the Genitive Construction (GC) for Relative Clause construction (RCC) as a distractor.
+In the experiment, I test whether or not speakers utilize even more shallow parser than what is stipulated by @LagoEtAl:2018 and  my replication of @LagoEtAl:2018 Experiment 2.
+This was investigated using syntactic structures similar to @LagoEtAl:2018 materials, in which I have opted out the Genitive Construction (GC) for Relative Clause construction (RCC) as a distractor.
 In Turkish, like GC, the relative clause in RCC precedes the head noun, and length-wise Turkish relative clauses can consist of only one word and the rest can be dropped.
@@
 
+p_avg_resp2 <- p_avg_resp2 + scale_y_continuous(labels=scales::percent)
+p_avg_resp2 <- p_avg_resp2 + scale_color_discrete(name = "Attractor Number")
+
 print(p_avg_resp2)
@@
 # ## test model parameterization using a simple GLM first
-# m <- glm(ResponseYes ~ cEndsInVowel * cUngrammatical * cAttractorPlural,
+# m <- glm(ResponseYes ~ cEndsInConsonant * cUngrammatical * cAttractorPlural,
 #          data = df_merged_nofillers,
@@
 p_m_response2 <- p_m_response2 + xlab("Estimate (log-odds)")
-print(p_m_response2)
-
-```
-
-```{r exp2AvgRTs, fig.height=2.5, fig.width = 6 ,fig.cap="Average response times for  my replication and Experiment2"}
+print(p_m_response2 + annotate(x=-2, xend=2, y=0, yend=0, lwd=0.25, geom="segment"))
+
+```
+
+```{r exp2AvgRTs, fig.height=2.5, fig.width = 6 ,fig.cap="Average response times for experiment 1 and experiment 2."}
 

### 2019-09-03 scripts/misc.R

@@ -108,8 +108,8 @@ model_summary <- function(m, include_pp_below_zero = T)
     
     pref_coef_stats_df <- function(df, name) {
       df %>% as.data.frame(colnames = "x") %T>% 
-      { colnames(.) <- name } %T>%
-      { .$coef <- rownames(.) %>% gsub("^b_", "", .) }
+        { colnames(.) <- name } %T>%
+        { .$coef <- rownames(.) %>% gsub("^b_", "", .) }
     }
     
     p_below_zero <- samples %>% sapply(function(x) mean(x < 0)) %>% 
@@ -146,7 +146,9 @@ create_model_coefs_plot <- function(m,
                                     plot_stats = FALSE, 
                                     expand_right = 1, 
                                     expand_top = 1,
-                                    x_stat_adjust = 0)
+                                    x_stat_adjust = 0,
+                                    x_breaks = ggplot2::waiver(),
+                                    x_minor_breaks = ggplot2::waiver())
 {
   interaction_symbol <- " * "
   use_interaction_panels <- length(interaction_panels) > 0
@@ -220,22 +222,24 @@ create_model_coefs_plot <- function(m,
   if (plot_stats)
   {
     tbl$xmax <- with(tbl, max(c(Estimate, Q2.5, Q97.5))) + x_stat_adjust
-
+    
     
     p <- p + scale_y_discrete(expand = expand_scale(mult = c(.05, .15*expand_top), 
-                                                    add = c(0, 0)) )
+                                                    add = c(0, 0))
+                              )
     p <- p + scale_x_continuous(expand = expand_scale(mult = c(.05, .15*expand_right), 
-                                                      add = c(0, 0)) )
+                                                      add = c(0, 0)),
+                                breaks = x_breaks, 
+                                minor_breaks = x_minor_breaks)
     
     p <- p + geom_text(aes(x = tbl$xmax, y = tbl$coef,#_idx, 
                            label = sprintf("[%s]", tbl$PBelowZeroStr)), 
                        family = "mono", hjust = "left")
     suppressWarnings({
-      label <- parse(text = "paste('P(', theta, ' < 0)')")
+      label <- parse(text = "underline(paste('P(', theta, ' < 0)'))")
       p <-  p + geom_text(x = tbl$xmax[1], y = max(as.integer(tbl$coef))+1, 
-                          # label = "P( < 0)", 
                           label = label,
-                          family = "mono", hjust = "left")#, fontface = "bold")
[…]

### 2019-09-06 Paper/paper_draft.rmd
Update.

@@
 ---
-title             : "Agreement Attraction in Turkish: Who let the -lAr out?"
+title             : "Agreement Attraction in Turkish: Who can write a better title?"
 shorttitle        : "Agreement Attraction in Turkish"
@@
 
+df_merged %<>% mutate(ResponseCorrect = (ResponseYes == (grammatical == "grammatical") ) )
+
 avg_clean <- df_merged %>%
      group_by(experiment, source, grammatical, attractor_num) %>%
-     summarize(avgRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T))
+     summarize(avgRT = mean(RT), 
+               avgRT_ResponseCorrect = mean(RT[ResponseCorrect]), 
+               p_yes = mean(ResponseYes, na.rm = T))
 
@@
 data as a function of sentence grammaticality and the grammatical of number the attractor noun phrase.
-In our data, while ungrammatical sentences with a plural attractor were found acceptable in `r round(100*avg_exp[[3,6]])`% of the cases, the accepability rate was only `r round(100*avg_exp[[4,6]])`% when the attractor was singular.
-This observed agreement attraction effect of `r round(100*(avg_exp[[3,6]]-avg_exp[[4,6]]))`%, as well as the condition averages were fairly close to Lago et al.'s attraction effect of `r round(100*(avg_exp[[7,6]]-avg_exp[[8,6]]))`%.
+In our data, while ungrammatical sentences with a plural attractor were found acceptable in `r round(100*avg_exp$p_yes[3])`% of the cases, the accepability rate was only `r round(100*avg_exp$p_yes[4])`% when the attractor was singular.
+This observed agreement attraction effect of `r round(100*(avg_exp$p_yes[3]-avg_exp$p_yes[4]))`%, as well as the condition averages were fairly close to Lago et al.'s attraction effect of `r round(100*(avg_exp$p_yes[7]-avg_exp$p_yes[8]))`%.
+
+<!-- to-do: report the results of the fillers here, and provide a *very brief* explanation -->
 
@@
 
-<!-- to-do: relabel all 'vowel ending' stuff to be about ACC-GEN ambiguity -->
 <!-- to-do: make sure the CIs are HPDIs, and say so -->
@@
 
-Figure \@ref(fig:exp1AvgRTs) shows higher
-
-, I see that average response times are significantly higher than the those of @LagoEtAl:2018.
-I also see it in \@ref(exp1ResponseTimeModelPlot), since **b_cEndsinVowel** indicates whether or not it is Experiment 1 or Experiment from @LagoEtAl:2018, i.e.
-distractors in items in @LagoEtAl:2018 ends with a consonant, while ours ends in a vowel.
-Again, these results show the effect of disambiguation of the possessive suffix from the accusative case has surfaced as the difficulty in response and memory retrieval time.
-
-```{r exp1AvgRTs, fig.height=2.5, fig.width = 6, fig.cap="Average response times for experiment 1 and Lago et. al. (2018)"}
-
-p_avg_rt <- avg_exp %>% ggplot(aes(grammatical, avgRT, linetype = attractor_num, color = experiment, group = paste(experiment, attractor_num))) + geom_point() + geom_line() + ylab("Response Time (ms)")
-
+<!--
+Figure \@ref(fig:exp1AvgRTs) shows higher average RTs in our experiment compared to Lago et al.'s data.
+This is not surprising given that our response deadline was 6 seconds(?), and Lago et al.'s was 2 seconds (all RTs were $<$ $2~sec$).
+The really interesting finding is that we got an interaction in RTs, such that in experiment 1, there is a slowdown in the agreement attraction condition.
+There is no such effect in the Lago et al.
+data.
+The model estimates in figure \@ref(exp1ResponseTimeModelPlot) support this conclusion.
+
+```{r exp1AvgRTs, eval=F, fig.height=2.5, fig.width = 6, fig.cap="Average response times for experiment 1 and Lago et. al. (2018)"}
+
+p_avg_rt <- avg_exp %>% ggplot(aes(grammatical, avgRT_ResponseCorrect, linetype = attractor_num, color = experiment, group = paste(experiment, attractor_num))) + geom_point() + geom_line() + ylab("Response Time (ms)")
 print(p_avg_rt)
@@
 
-<!-- to-do: confidence intervals in plot -->
-```{r exp1ResponseTimeModelPlot, fig.height = 2.5, fig.width = 6, fig.cap="Estimates and 95% credible intervals for the regression coefficients in response times (log units)."}
+<!-- to-do: confidence intervals in plot - ->
+```{r exp1ResponseTimeModelPlot, eval=F, fig.height = 2.5, fig.width = 6, fig.cap="Estimates and 95% credible intervals for the regression coefficients in response times (log units)."}
 
@@
 ```
+-->
 
@@
 
-Experiment 1 found number attraction effects, like also attested in @LagoEtAl:2018, and also found a significant effect of form ambiguity of possessive and an interaction of plural attractor with ungrammaticality in response times.
-Illusionary agreement of the verb with the plural attractor was more than the singular attractor.
-In addition to what has been discussed by @AvetisyanEtAl:2019.
-this results also show that not only the case itself but also the form of the case can affect the response times.
-
+We replicated the number agreement attraction effect found by @LagoEtAl:2018, albeit with a larger sample size and while controlling for potential confound of head noun ambiguity.
+This finding suggests that the agreement attraction in Turkish is largely unaffected by the ambiguity of case marking of the head noun.
+\ldots The small difference between the two experiments that we do find is quite likely due to the shorter response deadline in the Lago et al.
+experiment.
+As a result of this short deadline, what we found in RT, they found in responses - i.e., in a slightly bigger agreement attraction effect
+\ldots this finding has some relationship to the findings in @AvetisyanEtAl:2019
+\ldots however, @AvetisyanEtAl:2019's findings as such have more predictions -- for example, they predict that Lago et al.'s speculation about the role of genitive case in this attraction effect is likely wrong.
+
+<!-- to-do: What do you mean by this? The difference that there is is likely caused by the difference in response deadlines (their 2 seconds vs. our 6 seconds).
+
+In addition to what has been discussed by @AvetisyanEtAl:2019. this results also show that not only the case itself but also the form of the case can affect the response times.
+-->
+
+\ldots discuss the effect in fillers: the most likely explanation for this finding is that we messed up the fillers by not checking their accuracy. \ldots discuss
+\ldots an alternative explanation is that we our fillers were ok, but the experiment design heavily biased participants towards 'no' answers \ldots this appears unlikely since we got pretty much the same numbers as Lago et al., who didn't have such fillers (as far as I am aware) \ldots however, in case that is what happened, this does not change the interpretation of our finding, because \ldots
+
+<!-- 
 In the previous sections, I have predicted that with an assumed mechanism where people do take the clues from the form of the plural morpheme itself and have a strategy based on matching the plural morphemes, I would expect no change with regards to the agreement attraction effects.
 I also should not expect increasing response times when an irrelevant morpheme for the mechanism I assume.
-
+-->
+
+<!--
 However, I see that response times have changed drastically when the suffixes are dismabiguated.
@@
 Yet, with clearly marked possessive suffix, I see that these enabling nature of the genitive possessive structure is eliminated, which is also shown in @AvetisyanEtAl:2019.
-
-However, these results can also be a result of badly formed filler sentences which are shown with a purple line.
-Participants may be biased towards saying no since most of the experimental items being ungrammatical.
-However, this can also be statistical *miss* since I may accidentally have a group such as this one.
-However, the visible effect of vowel ending and response time suggest that people do indeed care more than only the retrieval of plural morpheme *-lar* and its place.
-
+-->
+
+<!--
 These results go against what I have predicted for the Marking and Morphing model as well.
 Due to the no extreme semantic change in the experimental (*Marking*) and no change in the structural relations among the genitive-possessive constructions (*Morphing*), there should be no difference in agreement attraction.
-
-However, the existence of an extremely close degree of agreement attraction effects and non-significant nature of the effect of the vowel ending indicates that I cannot readily discard other explanations.
-Another reason for not jumping to the conclusion with percolation models can be related to the number of participants @LagoEtAl:2018 have included in their study [see @Vasishth2018].
-
+-->
+
+<!--
 ---
@@
 An agreement attraction, then, is not a result of a partial matching or a representational error of number feature; instead, it is the result of a state of memory in which comprehenders misremember either the existence of the nominal plural morpheme or the place of the nominal plural morpheme as stated in the MPT model of the agreement attraction within shallow processor within \autoref{model1}, \autoref{model2}, \autoref{model3}\footnote{Author here wishes he knew more latex to do the MPT tree more neat.}.
+
+-->
+
+---
+
+Now that we replicated Lago et al.'s findings, it seems like all is good -- there is a number attraction effect in Turkish.
 

### 2019-11-23 Paper/paper_draft.tex
pılot push

--- 2019-09-01 Paper/paper_draft.rmd
@@
----
-title             : "Agreement Attraction in Turkish: Who let the -lAr out?"
-shorttitle        : "Agreement Attraction in Turkish"
-author: 
-  - name          : "Utku Türk"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Postal address"
-    email         : "utku.turk@boun.edu.tr"
-  - name          : "Pavel Logačev"
-    affiliation   : "1"
-affiliation:
-  - id            : "1"
-    institution   : "Boğaziçi University University, Istanbul, Turkey"
-authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+\documentclass[doc]{apa6}
+\usepackage{lmodern}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+\else % if luatex or xelatex
+  \ifxetex
+    \usepackage{mathspec}
+  \else
+    \usepackage{fontspec}
+  \fi
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+\fi
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+% use microtype if available
+\IfFileExists{microtype.sty}{%
+\usepackage{microtype}
+\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\usepackage{hyperref}
+\hypersetup{unicode=true,
+            pdftitle={Agreement Attraction in Turkish: Who let the -lAr out?},
+            pdfauthor={Utku Türk~\& Pavel Logačev},
+            pdfkeywords={keywords},
+            pdfborder={0 0 0},
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
+\usepackage{graphicx,grffile}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{0}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
+
+%%% Use protect on footnotes to avoid problems with footnotes in titles
+\let\rmarkdownfootnote\footnote%
+\def\footnote{\protect\rmarkdownfootnote}
+
+  \title{Agreement Attraction in Turkish: Who let the -lAr out?}
+    \author{Utku Türk\textsuperscript{1}~\& Pavel Logačev\textsuperscript{1}}
+    \date{}
+
+\usepackage[utf8]{inputenc}
+ \usepackage[T1]{fontenc}
+ \usepackage{xcolor}
+ \usepackage{hhline}
+ \usepackage{mathtools}
+ \linespread{1}
+ \usepackage{gb4e}
+ \noautomath
+ \usepackage{setspace}
+ \makeatletter
+ \apptocmd{\@exe}{\singlespacing}{}{}
+ \makeatother
+ \usepackage{sectsty}
+ \allsectionsfont{\large}
+ \usepackage{color}
+ \usepackage{hyperref}
+ \hypersetup{colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue} 
+ \usepackage[english]{babel}
+ \addto\extrasenglish{\renewcommand{\itemautorefname}{Item}}
+\usepackage{tikz}
+ \usepackage{tikz-qtree}
+ \let\eachwordone=\textit
+ \usepackage{geometry}
+ \geometry{margin=2cm}
+ \usepackage{libertine}
+ \usepackage{libertinust1math}
+ \usepackage[T1]{fontenc}
+ \usepackage{fancyhdr}
+
+\authornote{Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
 Enter author note here.
-abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
 
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
+Correspondence concerning this article should be addressed to Utku Türk, Postal address. E-mail: \href{mailto:utku.turk@boun.edu.tr}{\nolinkurl{utku.turk@boun.edu.tr}}}
 
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
+\abstract{
+One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.
 
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
+Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.
 
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
+One sentence clearly stating the \textbf{general problem} being addressed by this particular study.
 
-  One or two sentences to put the results into a more **general context**.
+One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).
 
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
+Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
 
-  <!-- https://tinyurl.com/ybremelq -->
-keywords          : "keywords"
-wordcount         : "X"
-bibliography      : ["myreferences.bib", "library.bib", "r-references.bib"]
-floatsintext      : no
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : no
-mask              : no
-draft             : no
-documentclass     : "apa6"
-classoption       : "doc"
-output:
-  papaja::apa6_pdf:
-    includes:
-        in_header: paper_draft_preamble.tex
+One or two sentences to put the results into a more \textbf{general context}.
 
-editor_options: 
-  chunk_output_type: console
-keep_tex: TRUE
-keep_md: TRUE
----
+Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
 
-<!--
-    citation_package: biblatex
+}
 
--->
-
-<!--
-Introduction:
- - Review of the key attraction findings: 
-      * English. 
-      * German: @ReifegersteEtAl:2016
-      * Definitely Russian (Sliosar on gender). [@SlioussarMalko:2016]
-      * Arabic: @TuckerEtAl:2015
-      * Spanish: @LagoEtAl:2015
-      * Turkish: @LagoEtAl:2019
-      * Hammerly 2019 [@HammerlyEtAl:2019]
-      * @LinzenLeonard:2018
-      * @SmithFranck:2018
-      * @ParkerPhillips:2017
-      * @VasishthEtAl:2017 **
-      * @ReifegersteEtAl:2016
-      * @KwonSturt:2016
-      * @RisticMolinaroMancini:2016
-      * @SlevcMartin:2016
-      * @PatsonHusband:2015
-      * @Enochson:2015 **
-      * @FranckColonnaRizzi:2015
-      * @WagersEtAl:2009
-      * Slovak: @BadeckerKuminiak:2007
-      * @BockEtAl:2001
-      * @FiederEtAl:2014 **
-      * @Staub:2009
-      * @TannerNicolBrehm:2014
-      * @XiangEtAl:2013
-      * @NicenboimEtAl:2018
-
-      * @TannerBulkes:2015
-      * @Staub:2010
-      * @DankEtAl:2014 **
-      * @PearlmutterGarnseyBock:1999
-      * @FooteBock:2012
-      * @DillonEtAl:2013
-      - Shravan et al.'s new paper on Armenian
-
-Attraction attraction in the processing of subject-verb agreement have been an illuminating with regard to \ldots.
-
-errors in the production and comprehension of subject-verb agreement,
-
-in which a verb does not agree with the grammatical agreement controller, but with a potential attractor, have been the main topic of research in many studies for quite a long time.
-In fact, it is still a widely researched area in psycholinguistic studies.
-Despite the comprehensive research that has been carried out, studies that have been conducted on agreement attraction in Turkish have been very limited.
-In fact, @Lago is currently the only study that explores this phenomenon in Turkish.
-@Lago  makes use of genitive-possessive structures in the subject position, in which the possessive-marked noun is the head of the noun phrase which acts as the grammatical agreement controller, and the genitive noun serves as a potential attractor.
-In a speeded acceptability judgment study, @Lago found a significant effect of number agreement attraction.
-However, the interpretation of their findings may be a result of the fact that non-subjecthood cues originate from their use of morphologically ambiguous forms of the possessive.
-In the possessive forms that are used, all the head nouns in their stimuli are ambigiuous between possessive and accusative.
--->
-
-```{r setup, eval =T, include = FALSE, message=FALSE, warning=FALSE}
-library("papaja")
-library(knitcitations)
-library(tidyverse)
-library(magrittr)
-library(ggplot2)
-theme_set(theme_bw())
-
-library(car, warn.conflicts = FALSE)
-library(MASS)
-library(brms)
-library(xtable)
-library(ggpubr)
-
-library(languageR)
-library(tidyverse)
-library(gdata)
-library(MASS)
-library(magrittr)
-library(ggplot2)
-
-source("../scripts/misc.R")
-
-```
-
-```{r analysis-preferences, eval =T, message=FALSE, warning=FALSE}
-# Seed for random number generation
-set.seed(42)
-knitr::opts_chunk$set(encoding = 'UTF-8',
-                      cache.extra = knitr::rand_seed,
-                      echo = FALSE,
-                      results = 'asis')
-options("citation_format" = "pandoc")
-
-```
+\begin{document}
+\maketitle
 
@@
 For example, \ldots illusory npi licensing, agreement attraction \ldots
-One such comprehension error is agreement attraction (cite): Speakers may erroneously find sentences acceptable in which the the verb erroneously agrees with a syntactically unreated noun phrase (*the attractor*) instead of the subject (*the agreement controller*).
+One such comprehension error is agreement attraction (cite): Speakers may erroneously find sentences acceptable in which the the verb erroneously agrees with a syntactically unreated noun phrase (\emph{the attractor}) instead of the subject (\emph{the agreement controller}).
 
-One instance of agreement attraction in language production is incorrect number-agreement between verb and a noun phrase which is not the agreement controller. For example, @Bock1991 found 
+One instance of agreement attraction in language production is incorrect number-agreement between verb and a noun phrase which is not the agreement controller.
+For example, Bock and Miller (1991) found
 that \ldots something interesting happends resulting in sentences like \ldots.
-<!-- to-do -->
-<!--
-in a sentence like \autoref{AAEx1}, the target of the agreement is the verb *are*, the attracting distractor is *bottles*, and the feature erroneously assessed is the number feature of the grammatical controller *label*.
--->
-<!-- 
-This type of attraction, called number attraction in subject-verb agreement, first theorized by  
-@Quirk1972 and attested experimentally by
--->
-<!-- to-do: use the original example here -->
+
 \begin{exe}
@@
 
-<!-- to-do: mention the Lago et al study briefly since we'll be referring to it. -->
-In this paper, we report the results of two experiments about agreement attraction: The first experiment adressed a potential confound in the @LagoEtAl:2019 study.
+In this paper, we report the results of two experiments about agreement attraction: The first experiment adressed a potential confound in the Lago et al.
+(2018) study.
 In the second experiment we tested an explanation of agreement attraction in Turkish as a task-specific strategy: we tested whether verbs with plural agreement can serve as as potential attractors.
 The results show that \ldots
-<!--
-pvl: no idea what the text below means
-while people do indeed care more than just "matching" the forms of plural verbal.
-either comprehenders have some sort of restriction to not use cues from verbs upon accessing the number of the plural morpheme or there is a syntactic reason for the number feature of the plural morpheme to not "percolate."
--->
 
-# Theories of agreement attraction
+\hypertarget{theories-of-agreement-attraction}{%
+\section{Theories of agreement attraction}\label{theories-of-agreement-attraction}}
 
-One of the theoretical attempts to explain such phenomenon was *Marking and Morphing* [@Bock2001; @Eberhard2005 among others]. 
-<!-- to-do: PL, check whether the description below is correct. That's not how I remember it. -->
+One of the theoretical attempts to explain such phenomenon was \emph{Marking and Morphing} (Bock, Eberhard, Cutting, Meyer, \& Schriefers, 2001; Eberhard, Cutting, \& Bock, 2005 among others).
 +
-*Marking* and *Morphing* assumes two possible explanations within the framework with regards to where and when the attraction occurs.
+\emph{Marking} and \emph{Morphing} assumes two possible explanations within the framework with regards to where and when the attraction occurs.
 The first possibility is the speaker can erroneously create a semantic representation of the head with the wrong number feature in the marking process in the marking process.
@@
 
-<!-- to-do: How is this related to depth???
-as shown in @Bock1992 in which authors show that attractors within a relative clause trigger less agreement attraction in the production. 
--->
+Further studies have shown that other preverbal elements, such as objects, object relative clauses, object clefts, and object questions, may trigger agreement attraction (Franck, Lassi, Frauenfelder, \& Rizzi, 2006; Franck \& Wagers, 2015 among others; Hartsuiker, Antón-Méndez, \& Van Zee, 2001; Kimball \& Aissen, 1971).
+For example, ({\textbf{???}}) showed that in sentences like \autoref{E2}, the pronominal object \emph{hen} triggers and agreement attraction without being a part of the subject.
++
 
-Further studies have shown that other preverbal elements, such as objects, object relative clauses, object clefts, and object questions, may trigger agreement attraction [@Kimball1971; @Hartsuiker2001; @Franck2006; @Franck2015 among others].
-For example, @XXX showed that in sentences like \autoref{E2}, the pronominal object *hen* triggers and agreement attraction without being a part of the subject.
-+
 \begin{exe}
@@
 
-<!-- to-do: please give example sentences more descriptive lables than 'E2'. Remember you're not numbering them, but labelling them. -->
+Since the Marking and Morphing theories put the source of the agreement attraction on the probe, i.e.~subject phrase, they cannot explain agreement attraction effects that are triggered by a distractor outside of the syntactic scope of the subject.
 
-Since the Marking and Morphing theories put the source of the agreement attraction on the probe, i.e.
-subject phrase, they cannot explain agreement attraction effects that are triggered by a distractor outside of the syntactic scope of the subject.
+Badecker and Kuminiak (2007) suggest that a process where the subject is retrieved from the memory plays a role in agreement attraction effects as well.
 
-<!-- to-do: which theory do the terms trigger and probe come from? -->
-
-<!-- to-do: no idea what the sentence below means 
-Regardless, these effects may be explained in a framework where the source of the agreement attraction is placed on the trigger, i.e. verb. 
--->
-
-<!-- to-do: I suggest that you use multiple author names or XxxEtAl in your citation keys. That way, you won't get the number agreement wrong when writing about a paper authored by several people. -->
-@BadeckerKuminiak:2007 suggest that a process where the subject is retrieved from the memory plays a role in agreement attraction effects as well.
-
-<!-- to-do: Don't use "see also"/"cf." without a clear reason. 
-"Cf. X for a similar proposal" is fine, but
-"cf. X" isn't helpful.
-
-[see also @WagersEtAl:2009]. 
--->
-
-<!-- to-do:
-Genuine question: What makes you think that @Gordon2001 is a "cue-based retrieval mechanism" paper??
--->
-
-Building on the work on cue-based parsing [@Lewis2005; @Lewis2006 among others], they argued that when readers reach the verb, they try to retrieve the subject using certain features (cues) that essentially marks the *subjecthood*.
+Building on the work on cue-based parsing (Lewis \& Vasishth, 2005; Lewis, Vasishth, \& Van Dyke, 2006 among others), they argued that when readers reach the verb, they try to retrieve the subject using certain features (cues) that essentially marks the \emph{subjecthood}.
 Thus, any element that matches (or partially matches) with the cues in use may cause agreement attraction regardless of their position or syntactic relation to the subject.
 Going back to \autoref{E2}, it is expected, then, for an object which shares features like being preverbal, being a noun phrase, ability to bear agreement with a subject to trigger agreement attraction.
-<!-- to-do: Plz revise the entire paragraph above for clarity. I don't think that you're sure what you mean here. -->
 
-<!-- to-do: Why "another" below? Did you mention another problem. -->
 Another challenge for the Marking and Morphing model was the grammaticality asymmetry. Due to the spreading activation formula
-<!-- to-do: This is the first time you mention this formula, and the first time you mention that marking an morphing has anything to do with spreading activation.
-Please expand your explanation of M&M above.
--->
-utilized in the Marking and Morphing model [see @Dell1986], this model overgeneralizes the attraction effects to both ungrammatical and grammatical sentences and predicts both \autoref{E1} and \autoref{E3} to be present empirically, which is not the case [@WagersEtAl:2009].
+utilized in the Marking and Morphing model (see Dell, 1986), this model overgeneralizes the attraction effects to both ungrammatical and grammatical sentences and predicts both \autoref{E1} and \autoref{E3} to be present empirically, which is not the case (Wagers, Lau, \& Phillips, 2009).
 
@@
 
-<!-- to-do: Move this paragraph up, before you mention the challenge for "Marking and morphing". Then conclude the section with the problem to M&M. This will improve the flow of the paragraph. -->
-On the other hand, cue-based retrieval models successfully predict the grammaticality asymmetry as shown by @Dillon2013 in an ACT-R simulation as well as numerous studies in self-paced reading, eye-tracking, and ERP studies [@WagersEtAl:2009; @TuckerEtAl:2015; @TannerEtAl:2014; @LagoEtAl:2015 among others].
+On the other hand, cue-based retrieval models successfully predict the grammaticality asymmetry as shown by Dillon, Mishler, Sloggett, and Phillips (2013) in an ACT-R simulation as well as numerous studies in self-paced reading, eye-tracking, and ERP studies (Lago, Shalom, Sigman, Lau, \& Phillips, 2015 among others; Tanner, Nicol, \& Brehm, 2014; Tucker, Idrissi, \& Almeida, 2015; Wagers et al., 2009).
 This success was due to their replacement of source of the attraction.
 According to cue-based retrieval models, the probe, verb, present certain cues to retrieve an NP with matching features in agreement.
-When features of the grammatical controller of the verb do not *fully* match with the cues, no single NP will be satisfying the *agreement*.
+When features of the grammatical controller of the verb do not \emph{fully} match with the cues, no single NP will be satisfying the \emph{agreement}.
 Thus, another NP in the clause can match with cues presented by the VP, such as its case, syntactic position, grammatical number.
-Thus, if there is no *retrieval cue* in the first place, i.e.
-the verb is not marked plural, there will be no need for partial match.
-
-<!-- to-do: This entire section needs rewriting, bigly! I'll do it.
-These reference-type sections don't go down well in psycholinguistics papers, because most ppl in the field don't care to learn more than they need to know about languages other than English.
-They also happen to interrupt the flow of the paper.
--->
+Thus, if there is no \emph{retrieval cue} in the first place, i.e.~the verb is not marked plural, there will be no need for partial match.
 
 Agreement attraction in sentence comprehension has beeen attested in
-Arabic [@TuckerEtAl:2015], 
-Armenian [@AvetisyanEtAl:2019],
-English [@WagersEtAl:2009; @PatsonHusband:2015; @EnochsonCulbertson:2015; @HammerlyEtAl:2019]  (... more ...), 
-German [@ReifegersteEtAl:2016],
-Korean [@KwonSturt:2016],
-Russian [@SlioussarMalko:2016], 
-Slovak [@BadeckerKuminiak:2007],
-Spanish [@LagoEtAl:2015], 
-Turkish [@LagoEtAl:2019]
+Arabic (Tucker et al., 2015),
+Armenian (Avetisyan, Lago, \& Vasishth, n.d.),
+English (Enochson \& Culbertson, 2015; Hammerly, Staub, \& Dillon, 2019; Patson \& Husband, 2015; Wagers et al., 2009) (\ldots{} more \ldots{}),
+German (Reifegerste, Hauer, \& Felser, 2016),
+Korean (Kwon \& Sturt, 2016),
+Russian (Slioussar \& Malko, 2016),
+Slovak (Badecker \& Kuminiak, 2007),
+Spanish (Lago et al., 2015),
+Turkish (Lago et al., 2018)
 
-<!--
-production:
-  * @SlevcMartin:2016
-theoretical:
-  * @LinzenLeonard:2018
-  * @SmithFranck:2018
-  * @ParkerPhillips:2017
-  * @VasishthEtAl:2017 **
-  * @LewisPhillips:2015
-  TannerEtAl:2014
-  TannerBulkes:2015
-other:
-  * @RisticMolinaroMancini:2016
-  * TannerBulkes:2015
-  * FranckColonnaRizzi:2015
--->
+\hypertarget{agreement-attraction-in-turkish}{%
+\section{Agreement attraction in Turkish}\label{agreement-attraction-in-turkish}}
 
-<!--
-note: Utku's trees can go from left to right. The document below explains how:
-https://en.wikibooks.org/wiki/LaTeX/Linguistics
--->
+Recently, Lago et al. (2018) demonstrated agreement attraction in Turkish. In a speeded acceptability judgement study, they presented sentences like (\ref{Lagoitem}) to participants.
+Lago et al.
+(2018) makes use of genitive-possessive structures in the subject position, in which the possessive-marked head of the complex noun phrase \emph{`the singer's vocalist'} acts as the grammatical agreement controller, and the genitive noun serves as a potential attractor.
 
-# Agreement attraction in Turkish
-
-Recently, @LagoEtAl:2019 demonstrated agreement attraction in Turkish. In a speeded acceptability judgement study, they presented sentences like (\ref{Lagoitem}) to participants. 
-@LagoEtAl:2019 makes use of genitive-possessive structures in the subject position, in which the possessive-marked head of the complex noun phrase *'the singer's vocalist'* acts as the grammatical agreement controller, and the genitive noun serves as a potential attractor.
-
-<!-- to-do: where did the 'backup' come from in the translation ??? -->
-<!-- to-do: what is the singer's vocalist ??? does this expression make sense? -->
 \begin{exe}
@@
 
-@LagoEtAl:2019 found a significant effect of number agreement attraction.
+Lago et al. (2018) found a significant effect of number agreement attraction.
 They argue that genitive modifiers my cause agreement attraction in Turkish because Turkish makes frequent use of genitive subjects in embedded clauses.
 This would explain why genitive modifiers cause little to no agreement attraction in English
-[@NicolEtAl:2016]. <!-- to-do: read, double-check the claim above -->
+(Nicol, Barss, \& Barker, 2016).
 
@@
 
-# Experiment 1
+\hypertarget{experiment-1}{%
+\section{Experiment 1}\label{experiment-1}}
 
-The aim of this study was examine the question of whether the agreement attraction effect @LagoEtAl:2019 found is mediated by the morphological ambiguity of the head noun.
+The aim of this study was examine the question of whether the agreement attraction effect Lago et al. (2018) found is mediated by the morphological ambiguity of the head noun.
 To this end, we modified Lago et al.'s stimuli by replacing the head nouns with unambiguous nouns.
-\ldots which end in a vowel to differentiate between the accusative case and the possessive suffix, i.e. *taksici* (taxi driver). 
+\ldots which end in a vowel to differentiate between the accusative case and the possessive suffix, i.e. \emph{taksici} (taxi driver).
 \ldots two words on why vowel-ending nouns don't exhibit this ambiguity \ldots
@@
 
-<!-- to-do: 
-Some more details on the modification of nouns. Like, did we
-change only head nouns, or other parts too? How often?
-Did we change anything except the possessive and genitive nouns? If so, how often?
--->
-
 We tried to keep the modified sentences as close as possible to the original sentences while also trying to make the sentences as plausible as possible.
@@
 
-### Materials
+\hypertarget{materials}{%
+\subsubsection{Materials}\label{materials}}
 
@@
 
-As seen in example (\ref{exp1_item}), unlike @LagoEtAl:2019's experimental sentences, the head nouns in our experiment are consonant-final and are therefore unambigously marked for posessive case -- the accusative form of *'yardımcı'* is *'XXX'*.
+As seen in example (\ref{exp1_item}), unlike Lago et al.
+(2018)'s experimental sentences, the head nouns in our experiment are consonant-final and are therefore unambigously marked for posessive case -- the accusative form of \emph{`yardımcı'} is \emph{`XXX'}.
 
@@
 
-The purpose of using such filler sentences was to prevent participants from a adopting a response strategy of responding 'no' to sentences with verbs with plural agreement and 'yes' to verbs without plural agreement, while ignoring other words in the sentence.
+The purpose of using such filler sentences was to prevent participants from a adopting a response strategy of responding `no' to sentences with verbs with plural agreement and `yes' to verbs without plural agreement, while ignoring other words in the sentence.
 
@@
 
-```{r loadDataExp1, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-
-fname_data <- "../workspace_exp1/exp_data.rds"
-data_exp1 <- readRDS(file = fname_data)
-
-# compute by-subject percentages of 'yes' responses, and average RTs 
-avg_by_subj <- data_exp1 %>%
-                group_by(subject, experiment, condition, 
-                         grammatical, verb_num, attractor_num) %>%
-                summarize(avRT = mean(RT), 
-                          p_yes = mean(ResponseYes, na.rm = T), 
-                          N = sum(!is.na(ResponseYes))  )
-
-# reformat by-subject averages to a wide format
-avg_by_subj_wide <- avg_by_subj %>% 
-                      mutate(expcond = paste(experiment, condition, sep="_")) %>% 
-                      ungroup() %>%
-                      dplyr::select(-experiment, -condition, -avRT, -N,
-                                    -grammatical, -verb_num, -attractor_num) %>%
-                      tidyr::spread(expcond, p_yes) %>% 
-                      mutate(delta_dc = AgrAttr_d - AgrAttr_c)
-
-```
-
-```{r loadDataLago, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-
-# Load Lago et al.'s monolingual data
-fname_lagoetal <- "../Data/Lago_et_al/Lago_data.csv"
-df_lagoetal <- read.csv(fname_lagoetal, encoding = "UTF-8", as.is = T)
-df_lagoetal %<>% subset(Group == "monolingual")
-df_lagoetal %<>% dplyr::select(-Accuracy, -L1:-Group, -List:-SelfRateGerman)
-
-# Note: All rows with Experiment == "offline" also seem to be for 
-#       the UNP task ('Grammatical' is NA). I wonder if these were
-#       the same subjects, or if the subject labels were simply the same
-#       for the two experiments.
-with(df_lagoetal, stopifnot( is.na(Grammatical) == (Experiment == "offline") ))
-
-df_lagoetal_unp <- df_lagoetal %>% 
-                    subset(is.na(Grammatical)) %>%
-                    dplyr::select(-Grammatical:-Label)
-df_lagoetal_attr <- df_lagoetal %>% 
-                  subset(!is.na(Grammatical)) %>%
-                  dplyr::select(-Distance:-NewCond)
-
-df_lagoetal_attr %<>% mutate(ResponseYes = (Response == "yes") ) %>% 
-                      dplyr::select(-Response)
-df_lagoetal_attr %<>% ungroup() %>%
-                      dplyr::select(grammatical=Grammatical,
-                                    attractor_num=Attractor,
-                                    experiment=Experiment,
-                                    lagoetal_condition=Condition, 
-                                    subject=Participant, 
-                                    item=Item,
-                                    ResponseYes,
-                                    RT)
-
-# map to our condition labels
-lagoetal_condition_mapping <- data.frame(
-    condition = c("a", "b", "c", "d"),
-    lagoetal_condition = c("d", "b", "c", "a"), 
-    stringsAsFactors = F)
-
-df_lagoetal_attr %<>% left_join( lagoetal_condition_mapping, by = "lagoetal_condition" )
-
-# compute by-subject percentages of 'yes' responses, and average RTs 
-avg_by_subj_lagoetal <- df_lagoetal_attr %>%
-            group_by(subject, experiment, condition, grammatical, attractor_num) %>%
-            summarize(avRT = mean(RT), 
-                      p_yes = mean(ResponseYes, na.rm = T), 
-                      N = sum(!is.na(ResponseYes))  )
-
-# reformat by-subject averages to a wide format
-avg_by_subj_lagoetal_wide <- avg_by_subj_lagoetal %>% 
-            mutate(expcond = paste(experiment, condition, sep="_")) %>% 
-            ungroup() %>%
-            dplyr::select(-experiment, -condition, -avRT, -N,
-                          -grammatical, -attractor_num) %>%
-            tidyr::spread(expcond, p_yes) %>% 
-            mutate(delta_dc = online_d - online_c)
-
-```
-
-### Participants and Procedure
+\hypertarget{participants-and-procedure}{%
+\subsubsection{Participants and Procedure}\label{participants-and-procedure}}
 
@@
 We verified that Turkish was their native language and that they predominantly used it in their daily lives.
-<!-- to-do: When you say 'verified', do you mean 'asked'? 'Verify' sounds like you actually made sure they aren't lying. Tone down if appropriate. -->
-<!-- to-do: Did anyone say Turkish wasn't their first language? Did we exclude them? -->
 
 In the experiments, participants were asked to judge the acceptability of Turkish sentences. All of the sentences were presented one word at a time in the center of the screen for 500 ms per word.
-<!-- unlike @LagoEtAl:2019 and @WagersEtAl:2009, in which the duration was 300 ms per word. -->
-The experiment was run on *Ibex Farm*, a web-based experiment platform (\url{http://spellout.net/ibexfarm}).
+The experiment was run on \emph{Ibex Farm}, a web-based experiment platform (\url{http://spellout.net/ibexfarm}).
 All experimental stimuli, data, and documentation can be found on \url{https://github.com/utkuturk/AgreementAttraction_Experiment}.
@@
 Participants were instructed to quickly classify sentences as acceptable or unacceptable based on their intuition.
-They were further informed about the $XXXX ms$ time limit for answering.
+They were further informed about the \(XXXX ms\) time limit for answering.
 At the start of the experiment, they were given 4 practice trials, and received feedback on their response.
@@
 More specifically, they were asked:
-*'Was the sentence you read was natural to you?'*
-<!-- to-do: Is this really how it was phrased? -->
-Participants responded Q for *yes*, and P for *no*.
+\emph{`Was the sentence you read was natural to you?'}
+Participants responded Q for \emph{yes}, and P for \emph{no}.
 
@@
 
-### Data Analysis
-
-```{r loadFrequencies, eval=F, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-
-word_freq <- readxl::read_excel("../Data/freq.xlsx", sheet = 1)
-word_freq$freq_percentage %<>% as.numeric()
-word_freq %<>% dplyr::select(-freq_standardized, -freq_percentage, -word)
-word_freq %<>% tidyr::spread(place, freq_count)
-
-word_freq %<>% dplyr::group_by(exp) %>% 
-               dplyr::mutate( cat_n1 = ifelse(n1 > median(n1), "high", "low"),
-                              cat_n2 = ifelse(n2 > median(n2), "high", "low"),
-                              freqlog_n1 = scale(log(n1)),
-                              freqlog_n2 = scale(log(n2)),
-                              freqlog_n1n2 = log(n1) - log(n2)
-                            ) %>% 
-                ungroup()
-word_freq$cat_n1 %<>% as.factor()
-word_freq$cat_n2 %<>% as.factor()
-
-word_freq_exp1 <- word_freq %>% 
-                    subset(exp == "up") %>% 
-                    dplyr::select(-exp)
-word_freq_lago <- word_freq %>% 
-                    subset(exp == "lago") %>% 
-                    dplyr::select(-exp)
-```
-
-```{r identifyBadSubjects, eval =T, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-
-# identify bad participants 
-bad_subjects <- subset(avg_by_subj_wide, delta_dc <= 0.25 ) %>% .$subject
-data_exp1_clean <- data_exp1 %>% subset(!subject %in% bad_subjects)
-
-# identify bad participants 
-bad_subjects_lagoetal <- subset(avg_by_subj_lagoetal_wide, delta_dc <= 0.25 ) %>% .$subject
-df_lagoetal_attr_clean <- df_lagoetal_attr %>% subset(!subject %in% bad_subjects_lagoetal)
-
-```
-
-```{r mergeData, eval =T, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-
-df_merge_exp1 <- data_exp1_clean %>% ungroup() %>% 
-                      dplyr::select(source=experiment, 
-                                    grammatical, attractor_num,
-                                    # condition,
-                                    subject, item=Item,
-                                    ResponseYes, RT)
-df_merge_exp1$experiment <- "Experiment 1"
-df_merge_exp1$grammatical <- with(df_merge_exp1, 
-                                  ifelse(grammatical == "gram", 
-                                          "grammatical",
-                                          "ungrammatical"))
-df_merge_exp1$attractor_num <- with(df_merge_exp1, 
-                                    ifelse(attractor_num == "pl",
-                                           "plural", 
-                                           "singular"))
-df_merge_exp1$item %<>% as.integer()
-df_merge_exp1$subject %<>% as.character()
-#df_merge_exp1 %<>% left_join(word_freq_exp1, by = "item")
-
-df_merge_lago <- df_lagoetal_attr_clean %>%
-                      ungroup() %>% 
-                      dplyr::select(grammatical, attractor_num,
-                                    subject, item, ResponseYes, RT)
-#df_merge_lago %<>% left_join(word_freq_lago, by = "item")
-df_merge_lago$experiment <- "Lago et al. (2019)" 
-df_merge_lago$source <- NA
-df_merge_lago$item %<>% add(1000)
-
-df_merged <- dplyr::bind_rows(df_merge_exp1, df_merge_lago)
-df_merged$subject %<>% as.factor()
-df_merged$item %<>% as.factor()
-
-df_exp1_na_nofillers <- subset(df_merge_exp1, is.na(ResponseYes) & source != "filler")
-df_merged %<>% subset( !is.na(ResponseYes) )
-```
-
-<!-- to-do: find out if the items from experiment 1 and Lago's paper were minimal pairs. Should at least some of them have the same item id? 
-To control for that, we'd probably need to use random effects for two sets of item ids, one cross-experimental, one within-experiment?? 
--->
+\hypertarget{data-analysis}{%
+\subsubsection{Data Analysis}\label{data-analysis}}
 
 In order to determine whether the ambiguity of the head noun type affected the magnitude of the agreement attraction effect, we analyzed the data from our experiment
-together with the data from @LagoEtAl:2019.
-Participants for whom the difference in the percentage of `yes` responses between grammatical and ungrammatical conditions without attraction (conditions c and d) was below $0.25$ were deemed to not have performed the task as instructed, and their data was excluded from further analysis.
-In consequence, the data for `r length(bad_subjects)` participants from experiment 1, and `r stopifnot(length(bad_subjects_lagoetal) == 1)` one participant from Lago et al.'s experiment was excluded from further analysis.
-Across participants, a total `r sum(is.na(df_exp1_na_nofillers$ResponseYes))` trials were not responded to before the deadline by `r length(unique(df_exp1_na_nofillers$subject))` participants.
-The data from these trials was not used in the analysis of responses or reaction times.
+together with the data from Lago et al. (2018).
+Participants for whom the difference in the percentage of \texttt{yes} responses between grammatical and ungrammatical conditions without attraction (conditions c and d) was below \(0.25\) were deemed to not have performed the task as instructed, and their data was excluded from further analysis.
+In consequence, the data for 10 participants from experiment 1, and one participant from Lago et al.'s experiment was excluded from further analysis.
+Across participants, a total 42 trials were not responded to before the deadline by 33 participants. The data from these trials was not used in the analysis of responses or reaction times.
 
-We used `R` `r citep(citation())` and the *tidyverse* R packages `r citep(citation("tidyverse"))` for data processing and plotting, and the R packages *brms* `r citep(citation("brms"))` and *rstan* `r citep(citation("rstan"))` to fit Bayesian hierarchical models [e.g.,@GelmanHill:2007; @McElreath:2016; @BDA3].
+We used \texttt{R} ({\textbf{???}}) and the \emph{tidyverse} R packages ({\textbf{???}}) for data processing and plotting, and the R packages \emph{brms} ({\textbf{???}}; {\textbf{???}}) and \emph{rstan} ({\textbf{???}}) to fit Bayesian hierarchical models (e.g., Gelman \& Hill, 2007; Gelman et al., 2014; McElreath, 2016).
 Participants' responses were analyzed using Bayesian hierarchical generalized linear models using a Bernoulli distribution with a probit link.
-Models of response times were fit using the lognormal distribution.
-Both models were fit with the predictors
+Response times were modeled assuming lognormally distributed errors.
+Models of response times were fit using the lognormal distribution. Both models were fit with the predictors
 head noun ambiguity, attractor number, grammaticality, their interactions, as well as varying by-participants and by-items intercepts with a maximal random-effect structure.
-<!-- to-do: varying by-participants and by-items intercepts and slopes -->
 
-### Results
+\hypertarget{results}{%
+\subsubsection{Results}\label{results}}
 
-```{r exp1AvgResponse, fig.height = 2.5, fig.width = 6, fig.cap="Estimates and 95% credible intervals for the analysis of the probability of a 'yes' response."}
+\begin{figure}
+\centering
+\includegraphics{paper_draft_files/figure-latex/exp1AvgResponse-1.pdf}
+\caption{\label{fig:exp1AvgResponse}Estimates and 95\% credible intervals for the analysis of the probability of a `yes' response.}
+\end{figure}
 
-avg_clean <- df_merged %>%
-     group_by(experiment, source, grammatical, attractor_num) %>%
-     summarize(avgRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T))
+Figure \ref{fig:exp1AvgResponse} shows the percentages of ``acceptable'' answers for experiment 1 as well as the Lago et al.~data as a function of sentence grammaticality and the grammatical of number the attractor noun phrase.
+In our data, while ungrammatical sentences with a plural attractor were found acceptable in 22\% of the cases, the accepability rate was only 11\% when the attractor was singular.
+This observed agreement attraction effect of 10\%, as well as the condition averages were fairly close to Lago et al.'s attraction effect of 11\%.
 
-avg_exp <- avg_clean %>% subset(is.na(source) | source != "filler")
-avg_fillers <- avg_clean %>% subset(source == "filler")
+Figure \ref{fig:exp1ResponseModelPlot} shows the estimates of the fixed effects of a Bayesian hierarchical model.
+It shows that ungrammatical sentences were judged as acceptable far less often than grammatical sentences (CI = {[}XXX{]}).
+It also shows that sentences with plural attractors were considered acceptable a little bit better than sentences (CI = {[}XXX{]}) with singular attractors.
+Importantly, we found an interaction between these two factors, such that plural attractors increased the likelihood of `acceptable' responses disproportionately more in ungrammatical sentences (CI = {[}XXX{]}).
 
-p_avg_resp <- ggplot(avg_exp, 
-                     aes(grammatical, p_yes, #linetype = attractor_num, 
-                         color = attractor_num, group = attractor_num)) + 
-                geom_point() + geom_line() + 
-                facet_wrap(~experiment)
-
-# p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) + 
-#                             geom_point(data = avg_fillers) +
-
-p_avg_resp <- p_avg_resp + theme( strip.background = element_rect(fill="white") ) +
-                           theme_bw() + xlab("") + ylab("Percentage 'acceptable'")
-
-print(p_avg_resp)
-
-```
-
-Figure \@ref(fig:exp1AvgResponse) shows the percentage of "acceptable" answers as a function of the grammatical of number the attractor noun phrase, and sentence grammaticality.
-While ungrammatical sentences with a plural attractor were found acceptable in `r round(100*avg_exp[[3,6]])`% of the cases, the accepability rate was only `r round(100*avg_exp[[4,6]])`% when the attractor was singular.
-This ovserved agreement attraction effect of `r round(100*(avg_exp[[3,6]]-avg_exp[[4,6]]))`%, as well as the condition averages are fairly close to Lago et al.'s attraction effect of `r round(100*(avg_exp[[7,6]]-avg_exp[[8,6]]))`%.
-
-In Figure \@ref(fig:exp1ResponseModelPlot), I clearly see the effects of ungrammaticality and the interaction between the ungrammaticality and plural attractor.
+We found a small positive effect \ldots
+evidence that the ambiguity of the head noun affects the effect of attractor number on ungrammaticality (CI = {[}XXX{]}).
+\ldots no interesting difference between experiments \ldots
+\ldots we may even have produced a bayes factor or LOO metric, to test whether that three way interaction actually matters
 I see that the vowel ending is not significant even though it has a negative effect.
@@
 
-```{r exp1ModelResponse, include=FALSE}
+\begin{figure}
+\centering
+\includegraphics{paper_draft_files/figure-latex/exp1ResponseModelPlot-1.pdf}
+\caption{\label{fig:exp1ResponseModelPlot}Estimates and 95\% credible intervals for the regression coefficients in accuracy (log-odds units).}
+\end{figure}
 
-library(brms)
+Figure \ref{fig:exp1AvgRTs} shows higher
 
-df_merged %<>% within(., {
-  cGrammatical <- ifelse(grammatical == "grammatical", .5, -.5)
-  cUngrammatical <- ifelse(grammatical == "ungrammatical", .5, -.5)
-  cAttractorPlural <- ifelse(attractor_num == "plural", .5, -.5)
-  cEndsInVowel <- ifelse(experiment == "Experiment 1", .5, -.5)
-  #cFreqlog_n1n2 <- scale(freqlog_n1n2)
-  #cFreqlog_n1 <- scale(freqlog_n1)
-  #cFreqlog_n2 <- scale(freqlog_n2)
-})
-df_merged_nofillers <- df_merged %>% subset(is.na(source) | source != "filler")
-
-# ## test model parameterization using a simple GLM first
-# m <- glm(ResponseYes ~ (cFreqlog_n1 + cFreqlog_n2) *
-#            cEndsInVowel * cUngrammatical * cAttractorPlural,
-#          data = df_merged_nofillers,
-#          family = binomial("probit"))
-# summary(m)
-
-n_chains <- 4
-n_cores <- 4
-n_iter <- 2000
-fname_exp1_responses <- "../workspace_exp1/model_responses"
-
-# to-do: Re-run, ESS low
-m_responses <- brm(ResponseYes ~ cEndsInVowel * cUngrammatical * cAttractorPlural + 
-                                 (cUngrammatical * cAttractorPlural + 1| subject) +
-                                 (cUngrammatical * cAttractorPlural + 1| item),
-                   data = df_merged_nofillers,
-                   #init = "0",
-                   family = bernoulli("probit"),
-                   file = fname_exp1_responses, 
-                   chains = n_chains, cores = n_cores, iter = n_iter)
-
-fname_exp1_rts <- "../workspace_exp1/model_responses_rt"
-
-m_rts <- brm(RT ~ cEndsInVowel * cUngrammatical * cAttractorPlural +
-                                 (cUngrammatical * cAttractorPlural + 1| subject) +
-                                 (cUngrammatical * cAttractorPlural + 1| item),
-                   data = df_merged_nofillers,
-                   family = lognormal(),
-                   file = fname_exp1_rts,
-                   chains = n_chains, cores = n_cores, iter = n_iter)
-
-```
-
-<!-- to-do: relabel all 'vowel ending' stuff to be about ACC-GEN ambiguity -->
-```{r exp1ResponseModelPlot, fig.height = 2.5, fig.width = 6, fig.cap="log-odd Estimates and 95% credible intervals for the regression coefficients in Accuracy."}
-
-contrast_names <- c("cUngrammatical" = "Ungrammaticality",
-                    "cAttractorPlural" = "Plural Attactor",
-                    "cUngrammatical:cAttractorPlural" = "Ungrammaticality * Plural Attractor",
-                    "cEndsInVowel" = "Vowel Ending",
-                    "cEndsInVowel:cUngrammatical" = "Ungrammaticality * Vowel Ending",
-                    "cEndsInVowel:cAttractorPlural" = "Vowel Ending * Plural Attractor",
-                    "cEndsInVowel:cUngrammatical:cAttractorPlural" = "Vowel Ending * Ungrammaticality * Plural Attractor")
-
-#options(warn = 2)
-
-p_m_response <- create_model_coefs_plot( m_responses, plot_stats = T,
-                                  map_names = contrast_names,
-                              expand_right = 2.5, expand_top = 2, x_stat_adjust = 1.1
-                              ) + xlab("Estimate (log-odds)")
-print(p_m_response)
-
-```
-
-```{r exp1ResponseTimeModelPlot, fig.height = 2.5, fig.width = 6, fig.cap="log-odd Estimates and 95% credible intervals for the regression coefficients in Reading Times."}
-
-p_m_rts <- create_model_coefs_plot( m_rts, plot_stats = T, map_names = contrast_names,
-                              expand_right = 2.5, expand_top = 2, x_stat_adjust = 0.1
-                              )
-print(p_m_rts)
-
-```
-
-In Figure \@ref(fig:exp1AvgRTs), I see that average response times are significantly higher than the those of @LagoEtAl:2019.
-I also see it in \@ref(exp1ResponseTimeModelPlot), since **b_cEndsinVowel** indicates whether or not it is Experiment 1 or Experiment from @LagoEtAl:2019, i.e.
-distractors in items in @LagoEtAl:2019 ends with a consonant, while ours ends in a vowel.
+, I see that average response times are significantly higher than the those of Lago et al.
+(2018).
+I also see it in \ref{exp1ResponseTimeModelPlot}, since \textbf{b\_cEndsinVowel} indicates whether or not it is Experiment 1 or Experiment from Lago et al.
+(2018), i.e.~distractors in items in Lago et al.
+(2018) ends with a consonant, while ours ends in a vowel.
 Again, these results show the effect of disambiguation of the possessive suffix from the accusative case has surfaced as the difficulty in response and memory retrieval time.
 
-```{r exp1AvgRTs, fig.height=2.5, fig.width = 6, fig.cap="Average response times for  my replication and Lago et. al. (2018)"}
+\begin{figure}
+\centering
+\includegraphics{paper_draft_files/figure-latex/exp1AvgRTs-1.pdf}
+\caption{\label{fig:exp1AvgRTs}Average response times for experiment 1 and Lago et. al. (2018)}
+\end{figure}
 
-p_avg_rt <- ggplot(avg_clean, aes(grammatical, avgRT, linetype = attractor_num, color = experiment, group = paste(experiment, attractor_num))) + geom_point() + geom_line()
+\begin{figure}
+\centering
+\includegraphics{paper_draft_files/figure-latex/exp1ResponseTimeModelPlot-1.pdf}
+\caption{\label{fig:exp1ResponseTimeModelPlot}Estimates and 95\% credible intervals for the regression coefficients in response times (log units).}
+\end{figure}
 
-print(p_avg_rt)
+\hypertarget{discussion}{%
+\subsubsection{Discussion}\label{discussion}}
 
-```
-
-### Discussion
-
-Experiment 1 found number attraction effects, like also attested in @LagoEtAl:2019, and also found a significant effect of form ambiguity of possessive and an interaction of plural attractor with ungrammaticality in response times.
+Experiment 1 found number attraction effects, like also attested in Lago et al.
+(2018), and also found a significant effect of form ambiguity of possessive and an interaction of plural attractor with ungrammaticality in response times.
 Illusionary agreement of the verb with the plural attractor was more than the singular attractor.
-In addition to what has been discussed by @AvetisyanEtAl:2019.
+In addition to what has been discussed by Avetisyan et al.
+(n.d.).
 this results also show that not only the case itself but also the form of the case can affect the response times.
@@
 However, I see that response times have changed drastically when the suffixes are dismabiguated.
-It is clear from the Figure \@ref(fig:exp1AvgRTs), when people are prompted to judge the sentence, they have difficulty in resolving and back-tracking the dependencies of the sentence even though nothing relevant to the plural morpheme and its host word has changed.
+It is clear from the Figure \ref{fig:exp1AvgRTs}, when people are prompted to judge the sentence, they have difficulty in resolving and back-tracking the dependencies of the sentence even though nothing relevant to the plural morpheme and its host word has changed.
 
 The results follow from what a cue-based model would predict: slightly lower agreement attraction and increased response time.
-Due to the disambiguation between the accusative case and the possessive suffix, I speculated that the features related to the *non-subjecthood* of the head of the subject would not surface falsely in  my replication.
+Due to the disambiguation between the accusative case and the possessive suffix, I speculated that the features related to the \emph{non-subjecthood} of the head of the subject would not surface falsely in my replication.
 With more clearly formed genitive-possessive structures, participants do not have an easy time to partially match the cues with the phrases.
-This situation stems from the idea proposed by @LagoEtAl:2019 with regards to the effects of the cases on numeral agreement attraction.
+This situation stems from the idea proposed by Lago et al.
+(2018) with regards to the effects of the cases on numeral agreement attraction.
 She argues that the frequency of the case being used in the subject position affects the agreement attraction effects in a positive manner.
-Since the accusative case is rarely used in Turkish, I have argued that it may give *wrong* clues an enable the distractors to even distract more.
-Yet, with clearly marked possessive suffix, I see that these enabling nature of the genitive possessive structure is eliminated, which is also shown in @AvetisyanEtAl:2019.
+Since the accusative case is rarely used in Turkish, I have argued that it may give \emph{wrong} clues an enable the distractors to even distract more.
+Yet, with clearly marked possessive suffix, I see that these enabling nature of the genitive possessive structure is eliminated, which is also shown in Avetisyan et al.
+(n.d.).
 
@@
 Participants may be biased towards saying no since most of the experimental items being ungrammatical.
-However, this can also be statistical *miss* since I may accidentally have a group such as this one.
-However, the visible effect of vowel ending and response time suggest that people do indeed care more than only the retrieval of plural morpheme *-lar* and its place.
+However, this can also be statistical \emph{miss} since I may accidentally have a group such as this one.
+However, the visible effect of vowel ending and response time suggest that people do indeed care more than only the retrieval of plural morpheme \emph{-lar} and its place.
 
 These results go against what I have predicted for the Marking and Morphing model as well.
-Due to the no extreme semantic change in the experimental (*Marking*) and no change in the structural relations among the genitive-possessive constructions (*Morphing*), there should be no difference in agreement attraction.
+Due to the no extreme semantic change in the experimental (\emph{Marking}) and no change in the structural relations among the genitive-possessive constructions (\emph{Morphing}), there should be no difference in agreement attraction.
 
 However, the existence of an extremely close degree of agreement attraction effects and non-significant nature of the effect of the vowel ending indicates that I cannot readily discard other explanations.
-Another reason for not jumping to the conclusion with percolation models can be related to the number of participants @LagoEtAl:2019 have included in their study [see @Vasishth2018].
+Another reason for not jumping to the conclusion with percolation models can be related to the number of participants Lago et al.
+(2018) have included in their study (see Vasishth, Mertzen, Jäger, \& Gelman, 2018).
 
----
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
 
@@
 In my second experiment, I investigate the predictions made from my model using a verbal plural morpheme within a distractor relative clause.
-As mentioned earlier, the verbal plural morpheme in Turkish is exactly the same as the nominal plural with regards to its stress, its behavior, and its form: *-lAr*.
-Since Turkish relative clauses are essentially nominals due to the nominalization process, they behave exactly like other nominals within the sentence [@Goksel2004; @Taylan2015].
+As mentioned earlier, the verbal plural morpheme in Turkish is exactly the same as the nominal plural with regards to its stress, its behavior, and its form: \emph{-lAr}.
+Since Turkish relative clauses are essentially nominals due to the nominalization process, they behave exactly like other nominals within the sentence (Erguvanlı-Taylan, 2015; Göksel \& Kerslake, 2004).
 They can be marked with cases, plural agreement and they can have postpositions that any nominal also can.
@@
 In this paper, I assume that modifiers like relative clauses are within the noun phrase, which deems them \textit{syntactically} deeper placed in the hierarchical three than the possessee.}.
-The reason for this expected decline is the fact that relative clauses being relative *deeper* in the hierarchical structure than the possessee of genitive-possessive structure.
+The reason for this expected decline is the fact that relative clauses being relative \emph{deeper} in the hierarchical structure than the possessee of genitive-possessive structure.
 
-As for cue-based retrieval models, I would expect an agreement attraction quite similar to the one that I originally have in @LagoEtAl:2019.
-The reason for this expected agreement attraction is the fact that apart from having a verbal root, the relative clauses and nominals behave exactly the same in terms of *nounness*.
+As for cue-based retrieval models, I would expect an agreement attraction quite similar to the one that I originally have in Lago et al.
+(2018).
+The reason for this expected agreement attraction is the fact that apart from having a verbal root, the relative clauses and nominals behave exactly the same in terms of \emph{nounness}.
 Like nominals, nominalized structures first marked with plural and then with the case or possessive suffix.
@@
 One other question that may arise from this structure is that whether or not the parts of already-formed dependencies can feed the following dependency resolution.
-In other words, the verbal plural morpheme *-lar* on *dövdükleri* in \autoref{ouritem1} is already a trigger of a cue retrieval process.
-And, when it is merged with the nominal head *çocuk*, there is a formed semantic meaning that is  "a group of people has beaten a kid."  However, this *suggestion* assumes that relative clauses are formed at the very moment.
+In other words, the verbal plural morpheme \emph{-lar} on \emph{dövdükleri} in \autoref{ouritem1} is already a trigger of a cue retrieval process.
+And, when it is merged with the nominal head \emph{çocuk}, there is a formed semantic meaning that is ``a group of people has beaten a kid.'' However, this \emph{suggestion} assumes that relative clauses are formed at the very moment.
 Moreover, I also need to assume that after forming a relative clause they are unreachable, meaning that they do not contribute to the processing of the sentence, anymore.
@@
 Lastly, in my extremely shallow processing model, I would expect a significant effect of agreement attraction.
-Due to one of the writers' inability to *run the numbers* and *form the mpt trees in time*, this part---unfortunately---does not go beyond than a verbal argumentation.
+Due to one of the writers' inability to \emph{run the numbers} and \emph{form the mpt trees in time}, this part---unfortunately---does not go beyond than a verbal argumentation.
 The reason I expect a significant effect of the agreement attraction is due to the fact that upon the agreement process is driven by the faulty memory of the place of the plural morpheme and uneducated guessing.
 Since the parsing is shallow, comprehenders do not engage in perfect attribution of the features, thus having a somewhat blurry representation behind.
-I expect this behavior to be omnipresent in other agreement attraction phenomenon that has been shown, as well as in @LagoEtAl:2019 and in  my replication of it.
+I expect this behavior to be omnipresent in other agreement attraction phenomenon that has been shown, as well as in Lago et al.
+(2018) and in my replication of it.
 Therefore, there is no reason to have anything to be different in experiment 2.
 
----
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
 
-## Experiment 2
+\hypertarget{experiment-2}{%
+\subsection{Experiment 2}\label{experiment-2}}
 
-```{r loadDataExp2, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-
-fname_data2 <- "../workspace_exp2/exp_data.rds"
-data2 <- readRDS(file = fname_data2)
-
-# compute by-subject percentages of 'yes' responses, and average RTs 
-avg_by_subj2 <- data2 %>%
-                group_by(subject, experiment, condition, 
-                         grammatical, verb_num, attractor_num) %>%
-                summarize(avRT = mean(RT), 
-                          p_yes = mean(ResponseYes, na.rm = T), 
-                          N = sum(!is.na(ResponseYes))  )
-
-# reformat by-subject averages to a wide format
-avg_by_subj_wide2 <- avg_by_subj2 %>% 
-                      mutate(expcond = paste(experiment, condition, sep="_")) %>% 
-                      ungroup() %>%
-                      dplyr::select(-experiment, -condition, -avRT, -N,
-                                    -grammatical, -verb_num, -attractor_num) %>%
-                      tidyr::spread(expcond, p_yes) %>% 
-                      mutate(delta_dc = AgrAttr_d - AgrAttr_c)
-
-```
-
-```{r identifyBadSubjects2, eval =T, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-
-# identify participants 
-bad_subjects2 <- subset(avg_by_subj_wide2, delta_dc <= 0.25 ) %>% .$subject
-
-data_clean2 <- data2 %>% subset(!subject %in% bad_subjects)
-
-```
-
-```{r mergeData2, eval =T, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-
-df_merge_exp2 <- data_clean2 %>% ungroup() %>% 
-                      dplyr::select(source=experiment, grammatical, attractor_num, # condition,
-                                    subject, item=Item,
-                                    ResponseYes, RT)
-df_merge_exp2$experiment <- "Experiment 2"
-df_merge_exp2$grammatical <- with(df_merge_exp2, ifelse(grammatical == "gram", 
-                                                        "grammatical",
-                                                        "ungrammatical"))
-df_merge_exp2$attractor_num <- with(df_merge_exp2, ifelse(attractor_num == "pl", 
-                                                          "plural", 
-                                                          "singular"))
-df_merge_exp2$item %<>% as.integer()
-df_merge_exp2$subject %<>% as.character()
-
-df_exp2_na_nofillers <- subset(df_merge_exp2, is.na(ResponseYes))
-
-df_merged2 <- dplyr::bind_rows(df_merge_exp1, df_merge_exp2)
-df_merged2 %<>% subset(!is.na(ResponseYes))
-df_merged2$subject %<>% as.factor()
-df_merged2$item %<>% as.factor()
-```
-
-```{r computeAverages2, eval =T, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-
-avg_clean2 <- df_merged2 %>%
-                group_by(experiment, source, grammatical, attractor_num) %>%
-                summarize(avgRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T))
-```
-
-Having discussed the replication study of @LagoEtAl:2019, I have shown that results favor the cue-based models, especially with the effect of disambiguated possessive suffix on response times.
+Having discussed the replication study of Lago et al.
+(2018), I have shown that results favor the cue-based models, especially with the effect of disambiguated possessive suffix on response times.
 However, due to the extremely similar effects on agreement attraction, I can still entertain shallow processing mechanism as explained in \autoref{model1}, \autoref{model2}, and \autoref{model3}.
@@
 The study consists of a speeded acceptability judgment experiment in the web-based platform Ibex Farm.
-In the experiment, I test whether or not speakers utilize even more shallow parser than what is stipulated by @LagoEtAl:2019 and  my replication of @LagoEtAl:2019 Experiment 2.
-This was investigated using syntactic structures similar to @LagoEtAl:2019 materials, in which I have opted out the Genitive Construction (GC) for Relative Clause construction (RCC) as a distractor.
+In the experiment, I test whether or not speakers utilize even more shallow parser than what is stipulated by Lago et al.
+(2018) and my replication of Lago et al.
+(2018) Experiment 2.
+This was investigated using syntactic structures similar to Lago et al.
+(2018) materials, in which I have opted out the Genitive Construction (GC) for Relative Clause construction (RCC) as a distractor.
 In Turkish, like GC, the relative clause in RCC precedes the head noun, and length-wise Turkish relative clauses can consist of only one word and the rest can be dropped.
-Turkish allows us to use RCCs as distractors in the same place because Turkish plural morpheme in the verbal domain and nominal domain are the same: *-lAr*.
+Turkish allows us to use RCCs as distractors in the same place because Turkish plural morpheme in the verbal domain and nominal domain are the same: \emph{-lAr}.
 Both of them react similarly in the same phonological environments, and they also exhibit the same stress patterns.
 
-In the experimental items, the distractor RC and the matrix verb had f my configurations in which the number morpheme on the RCC (*plural* vs.
-*singular* marked RC verb) and matrix verb (*grammatical* vs.
-*ungrammatical*) as in \autoref{prereg1}.
+In the experimental items, the distractor RC and the matrix verb had f my configurations in which the number morpheme on the RCC (\emph{plural} vs.
+\emph{singular} marked RC verb) and matrix verb (\emph{grammatical} vs.
+\emph{ungrammatical}) as in \autoref{prereg1}.
 
@@
 
-### Participants and Procedure
+\hypertarget{participants-and-procedure-1}{%
+\subsubsection{Participants and Procedure}\label{participants-and-procedure-1}}
 
@@
 
-### Analysis
+\hypertarget{analysis}{%
+\subsubsection{Analysis}\label{analysis}}
 
 Every experimental item from both experiments (this experiment and Experiment (1) is included in the analysis.
-Participants for whom the difference between grammatical and ungrammatical sentences with no potential for agreement attraction (conditions c and d) did not exceed a threshold of $0.25$ were deemed not to have performed the task as instructed, and their data was excluded from further analysis.
-In consequence, `r length(bad_subjects2)` participants' data was excluded.
+Participants for whom the difference between grammatical and ungrammatical sentences with no potential for agreement attraction (conditions c and d) did not exceed a threshold of \(0.25\) were deemed not to have performed the task as instructed, and their data was excluded from further analysis.
+In consequence, 1 participants' data was excluded.
 
-Across participants, `r sum(is.na(df_exp2_na_nofillers$ResponseYes))` trials were not responded to before the deadline (by `r length(unique(df_exp2_na_nofillers$subject))` participants).
-The data from these trials was not used in the analysis of responses or reaction times.
+Across participants, 30 trials were not responded to before the deadline (by 24 participants). The data from these trials was not used in the analysis of responses or reaction times.
 
-We used `R` `r citep(citation())` and the *tidyverse* R packages `r citep(citation("tidyverse"))` for data processing and plotting, and the R packages *brms* `r citep(citation("brms"))` and *rstan* `r citep(citation("rstan"))` to fit Bayesian hierarchical models [e.g.,@GelmanHill:2007; @McElreath:2016; @BDA3].
+We used \texttt{R} ({\textbf{???}}) and the \emph{tidyverse} R packages ({\textbf{???}}) for data processing and plotting, and the R packages \emph{brms} ({\textbf{???}}; {\textbf{???}}) and \emph{rstan} ({\textbf{???}}) to fit Bayesian hierarchical models (e.g., Gelman \& Hill, 2007; Gelman et al., 2014; McElreath, 2016).
 
@@
 Both models were fit with the predictors
-<!-- to-do: fix the below formulation -->
 \ldots predictors \ldots
-<!-- to-do: varying by-participants and by-items intercepts and slopes -->
 
-### Results
+\hypertarget{results-1}{%
+\subsubsection{Results}\label{results-1}}
 
-<!-- to-do: Omit the fillers from experiment 1 from plots unless they really add something to the interpretation. 
-            Mention it in the text instead, along with the fact that the 'acceptable' items were clearly no good at
-            doing what they were supposed to.
--->
+\begin{figure}
+\centering
+\includegraphics{paper_draft_files/figure-latex/exp2AvgResponse-1.pdf}
+\caption{\label{fig:exp2AvgResponse}Estimates and 95\% credible intervals for the analysis of the probability of a `yes' response.}
+\end{figure}
 
-<!-- to-do: add CIs to experiment 1 plot  -->
-<!-- to-do: add CIs to experiment 2 plot  -->
+It is clear from Figure \ref{fig:exp2AvgResponse} that in the condition (c) where I expect an agreement attraction, participants find as unacceptable as the condition (d) with singular attractor, singular head noun, and plural matrix verb.
+While I do not see any agreement attraction (0.08\%), I also see a more firm analysis of the ungrammatical sentence with singular matrix verb ((0.08\%)).
 
-```{r exp2AvgResponse, fig.height = 2.5, fig.width = 6, fig.cap="Estimates and 95% credible intervals for the analysis of the probability of a 'yes' response."}
-
-avg_exp2 <- avg_clean2 %>% subset(is.na(source) | source != "filler")
-avg_fillers2 <- avg_clean2 %>% subset(source == "filler")
-
-p_avg_resp2 <- ggplot(avg_exp2, aes(grammatical, p_yes, #linetype = attractor_num, 
-                                    color = attractor_num, group = attractor_num)) + 
-                geom_point() + geom_line() + 
-                facet_wrap(~experiment) +
-                theme_bw() + theme( strip.background = element_rect(fill="white") ) +
-                xlab("") + ylab("Percentage 'acceptable'")
-
-print(p_avg_resp2)
-
-```
-
-It is clear from Figure \@ref(fig:exp2AvgResponse) that in the condition (c) where I expect an agreement attraction, participants find as unacceptable as the condition (d) with singular attractor, singular head noun, and plural matrix verb.
-While I do not see any agreement attraction (`r round(as.numeric(avg_exp2[7,6]), digits = 2)`%), I also see a more firm analysis of the ungrammatical sentence with singular matrix verb ((`r round(as.numeric(avg_exp2[7,6]), digits = 3)`%)).
-
-```{r exp2ModelResponse, include=FALSE}
-
-df_merged2 %<>% within(., {
-  cGrammatical <- ifelse(grammatical == "grammatical", .5, -.5)
-  cUngrammatical <- ifelse(grammatical == "ungrammatical", .5, -.5)
-  cAttractorPlural <- ifelse(attractor_num == "plural", .5, -.5)
-  cVerbalPlural <- ifelse(experiment == "Experiment 2", .5, -.5)
-})
-df_merged_nofillers2 <- df_merged2 %>% subset(is.na(source) | source != "filler")
-
-# ## test model parameterization using a simple GLM first
-# m <- glm(ResponseYes ~ cEndsInVowel * cUngrammatical * cAttractorPlural,
-#          data = df_merged_nofillers,
-#          family = binomial("probit"))
-# summary(m)
-
-n_chains <- 4
-n_cores <- 4
-n_iter <- 2000
-
-fname_exp2_responses <- "../workspace_exp2/model_responses"
-
-library(brms)
-
-m_responses2 <- brm(ResponseYes ~ cVerbalPlural * cUngrammatical * cAttractorPlural + 
-                                 (cUngrammatical * cAttractorPlural + 1| subject) +
-                                 (cUngrammatical * cAttractorPlural + 1| item),
-                   data = df_merged_nofillers2,
-                   family = bernoulli("probit"),
-                   file = fname_exp2_responses, 
-                   chains = n_chains, cores = n_cores, iter = n_iter)
-
-```
-
-As for the estimates of coefficients in \@ref(fig:exp2ResponseModelPlot), I can conclude that there is a significant negative effect of plural morpheme on the relative clause, which means that it does not cause any agreement affects.
+As for the estimates of coefficients in \ref{fig:exp2ResponseModelPlot}, I can conclude that there is a significant negative effect of plural morpheme on the relative clause, which means that it does not cause any agreement affects.
 Again, the effect of ungrammaticality that stems from the existence of plural morpheme on the matrix verb is visible.
@@
 
-```{r exp2ResponseModelPlot, fig.height = 2.5, fig.width = 6, fig.cap="log-odd Estimates and 95% credible intervals for the regression coefficients."}
+\begin{figure}
+\centering
+\includegraphics{paper_draft_files/figure-latex/exp2ResponseModelPlot-1.pdf}
+\caption{\label{fig:exp2ResponseModelPlot}log-odd Estimates and 95\% credible intervals for the regression coefficients.}
+\end{figure}
 
-contrast_names2 <- c("cUngrammatical" = "Ungrammaticality",
-                    "cAttractorPlural" = "Plural Attactor",
-                    "cUngrammatical:cAttractorPlural" = "Ungrammaticality * Plural Attractor",
-                    "cVerbalPlural" = "Verbal Plural",
-                    "cVerbalPlural:cUngrammatical" = "Ungrammaticality * Verbal Plural",
-                    "cVerbalPlural:cAttractorPlural" = "Verbal Plural * Plural Attractor",
-                    "cVerbalPlural:cUngrammatical:cAttractorPlural" = "Verbal Plural * Ungrammaticality * Plural Attractor")
+\begin{figure}
+\centering
+\includegraphics{paper_draft_files/figure-latex/exp2AvgRTs-1.pdf}
+\caption{\label{fig:exp2AvgRTs}Average response times for experiment 1 and experiment 2.}
+\end{figure}
 
-p_m_response2 <- create_model_coefs_plot(m_responses2, map_names = contrast_names2)
-p_m_response2 <- p_m_response2 + xlab("Estimate (log-odds)")
-print(p_m_response2)
-
-```
-
-```{r exp2AvgRTs, fig.height=2.5, fig.width = 6 ,fig.cap="Average response times for  my replication and Experiment2"}
-
-p_avg_rt2 <- ggplot(avg_clean2, aes(grammatical, avgRT, linetype = attractor_num, color = experiment, group = paste(experiment, attractor_num))) + geom_point() + geom_line()
-
-print(p_avg_rt2)
-
-```
-
-Finally, the response times of Experiment 2 is significantly lower than the Experiment 1 as seen from Figure \@ref(fig:exp2AvgRTs).
+Finally, the response times of Experiment 2 is significantly lower than the Experiment 1 as seen from Figure \ref{fig:exp2AvgRTs}.
 The even lower response time in ungrammatical plural (condition c) shows that participants were extremely confident with their decision and did not have any issue with the dependency resolution.
 
-### Discussion
+\hypertarget{discussion-1}{%
+\subsubsection{Discussion}\label{discussion-1}}
 
@@
 
-# Conclusion
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
 
@@
 
-Another take on the results may follow from the redefinition of the *shallowness* concept.
+Another take on the results may follow from the redefinition of the \emph{shallowness} concept.
 Experiments show that it is not only dependent on the form.
@@
 
-# References
-```{r create_r-references}
-r_refs(file = "r-references.bib")
-```
+\hypertarget{references}{%
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
+
+\hypertarget{refs}{}
+\leavevmode\hypertarget{ref-AvetisyanEtAl:2019}{}%
+Avetisyan, S., Lago, S., \& Vasishth, S. (n.d.). Does case marking affect agreement attraction in comprehension? doi:\href{https://doi.org/10.31234/OSF.IO/KMBGY}{10.31234/OSF.IO/KMBGY}
+
+\leavevmode\hypertarget{ref-BadeckerKuminiak:2007}{}%
+Badecker, W., \& Kuminiak, F.
+(2007).
+Morphology, agreement and working memory retrieval in sentence production: Evidence from gender and case in Slovak.
+\emph{Journal of Memory and Language}, \emph{56}(1), 65--85.
+
+\leavevmode\hypertarget{ref-Bock2001}{}%
+Bock, K., Eberhard, K. M., Cutting, J. C., Meyer, A. S., \& Schriefers, H. (2001). Some attractions of verb agreement. \emph{Cognitive Psychology}, \emph{43}(2), 83--128.
+
+\leavevmode\hypertarget{ref-Bock1991}{}%
+Bock, K., \& Miller, C. A. (1991). Broken agreement. \emph{Cognitive Psychology}, \emph{23}(1), 45--93.
+
+\leavevmode\hypertarget{ref-Dell1986}{}%
+Dell, G. S. (1986). A spreading-activation theory of retrieval in sentence production. \emph{Psychological Review}, \emph{93}(3), 283.
+
+\leavevmode\hypertarget{ref-Dillon2013}{}%
+Dillon, B., Mishler, A., Sloggett, S., \& Phillips, C.
+(2013).
+Contrasting intrusion profiles for agreement and anaphora: Experimental and modeling evidence.
+\emph{Journal of Memory and Language}, \emph{69}(2), 85--103.
+
+\leavevmode\hypertarget{ref-Eberhard2005}{}%
+Eberhard, K. M., Cutting, J. C., \& Bock, K. (2005). Making syntax of sense: Number agreement in sentence production. \emph{Psychological Review}, \emph{112}(3), 531.
+
+\leavevmode\hypertarget{ref-EnochsonCulbertson:2015}{}%
+Enochson, K., \& Culbertson, J.
+(2015).
+Collecting psycholinguistic response time data using Amazon Mechanical Turk.
+\emph{PLoS ONE}, \emph{10}(3), 1--17.
+doi:\href{https://doi.org/10.1371/journal.pone.0116946}{10.1371/journal.pone.0116946}
+
+\leavevmode\hypertarget{ref-Taylan2015}{}%
+Erguvanlı-Taylan, E. (2015). \emph{The phonology and morphology of turkish}. Boğaziçi Üniversitesi.
+
+\leavevmode\hypertarget{ref-Franck2006}{}%
+Franck, J., Lassi, G., Frauenfelder, U. H., \& Rizzi, L. (2006). Agreement and movement: A syntactic analysis of attraction. \emph{Cognition}, \emph{101}(1), 173--216.
+
+\leavevmode\hypertarget{ref-Franck2015}{}%
+Franck, J., \& Wagers, M. W. (2015). Hierarchical structure and memory retrieval mechanisms in attraction: An sat study. In \emph{28th annual cuny conference on human sentence processing}.
+
+\leavevmode\hypertarget{ref-BDA3}{}%
+Gelman, A., Carlin, J. B., Stern, H. S., Dunson, D. B., Vehtari, A., \& Rubin, D. B. (2014). \emph{Bayesian Data Analysis} (3rd ed.). London: CRC/Chapman-Hall.
+
+\leavevmode\hypertarget{ref-GelmanHill:2007}{}%
+Gelman, A., \& Hill, J. (2007). \emph{Data Analysis Using Regression and Multilevel/Hierarchical Models}. Cambridge, UK: Cambridge University Press.
+
+\leavevmode\hypertarget{ref-Goksel2004}{}%
+Göksel, A., \& Kerslake, C. (2004). \emph{Turkish: A comprehensive grammar}. Routledge.
+
+\leavevmode\hypertarget{ref-HammerlyEtAl:2019}{}%
+Hammerly, C., Staub, A., \& Dillon, B.
+(2019).
+The grammaticality asymmetry in agreement attraction reflects response bias: Experimental and modeling evidence.
+\emph{Cognitive Psychology}, \emph{110}(January), 70--104.
+doi:\href{https://doi.org/10.1016/j.cogpsych.2019.01.001}{10.1016/j.cogpsych.2019.01.001}
+
+\leavevmode\hypertarget{ref-Hartsuiker2001}{}%
+Hartsuiker, R. J., Antón-Méndez, I., \& Van Zee, M. (2001). Object attraction in subject-verb agreement construction. \emph{Journal of Memory and Language}, \emph{45}(4), 546--572.
+
+\leavevmode\hypertarget{ref-Kimball1971}{}%
+Kimball, J., \& Aissen, J. (1971). I think, you think, he think. \emph{Linguistic Inquiry}, \emph{2}(2), 241--246.
+
+\leavevmode\hypertarget{ref-KwonSturt:2016}{}%
+Kwon, N., \& Sturt, P.
+(2016).
+Attraction Effects in Honorific Agreement in Korean.
+\emph{Frontiers in Psychology}, \emph{7}(August), 1--13.
+doi:\href{https://doi.org/10.3389/fpsyg.2016.01302}{10.3389/fpsyg.2016.01302}
+
+\leavevmode\hypertarget{ref-LagoEtAl:2018}{}%
+Lago, S., Felser, C., Gračanin-Yuksek, M., Demir, O., Kırkıcı, B., \& Şafak, D.
+F.
+(2018).
+Straight from the horse's mouth: Agreement attraction effects with Turkish possessors.
+\emph{Linguistic Approaches to Bilingualism}, \emph{12}(1), 1--29.
+doi:\href{https://doi.org/10.1075/lab.17019.lag}{10.1075/lab.17019.lag}
+
+\leavevmode\hypertarget{ref-LagoEtAl:2015}{}%
+Lago, S., Shalom, D.
+E., Sigman, M., Lau, E.
+F., \& Phillips, C.
+(2015).
+Agreement attraction in Spanish comprehension.
+\emph{Journal of Memory and Language}, \emph{82}, 133--149.
+doi:\href{https://doi.org/10.1016/j.jml.2015.02.002}{10.1016/j.jml.2015.02.002}
+
+\leavevmode\hypertarget{ref-Lewis2005}{}%
+Lewis, R. L., \& Vasishth, S. (2005). An activation-based model of sentence processing as skilled memory retrieval. \emph{Cognitive Science}, \emph{29}(3), 375--419.
+
+\leavevmode\hypertarget{ref-Lewis2006}{}%
+Lewis, R. L., Vasishth, S., \& Van Dyke, J. A. (2006). Computational principles of working memory in sentence comprehension. \emph{Trends in Cognitive Sciences}, \emph{10}(10), 447--454.
+
+\leavevmode\hypertarget{ref-McElreath:2016}{}%
+McElreath, R. (2016). \emph{Statistical rethinking: A bayesian course with examples in R and Stan.} Boca Raton: CRC Press.
+
+\leavevmode\hypertarget{ref-NicolEtAl:2016}{}%
+Nicol, J.
+L., Barss, A., \& Barker, J.
+E.
+(2016).
+Minimal interference from possessor phrases in the production of subject-verb agreement.
+\emph{Frontiers in Psychology}, \emph{7}(MAY), 1--12.
+doi:\href{https://doi.org/10.3389/fpsyg.2016.00548}{10.3389/fpsyg.2016.00548}
+
+\leavevmode\hypertarget{ref-PatsonHusband:2015}{}%
+Patson, N.
+D., \& Husband, E.
+M.
+(2015).
+Misinterpretations in agreement and agreement attraction.
+\emph{Quarterly Journal of Experimental Psychology}, \emph{0218}(February), 1--22.
+doi:\href{https://doi.org/10.1080/17470218.2014.992445}{10.1080/17470218.2014.992445}
+
+\leavevmode\hypertarget{ref-ReifegersteEtAl:2016}{}%
+Reifegerste, J., Hauer, F., \& Felser, C.
+(2016).
+Agreement processing and attraction errors in aging: evidence from subject-verb agreement in German.
+\emph{Aging, Neuropsychology, and Cognition}, \emph{00}(00), 1--31.
+doi:\href{https://doi.org/10.1080/13825585.2016.1251550}{10.1080/13825585.2016.1251550}
+
+\leavevmode\hypertarget{ref-SlioussarMalko:2016}{}%
+Slioussar, N., \& Malko, A.
+(2016).
+Gender agreement attraction in Russian: production and comprehension evidence, \emph{7}(November), 1--20.
+doi:\href{https://doi.org/10.3389/fpsyg.2016.01651}{10.3389/fpsyg.2016.01651}
+
+\leavevmode\hypertarget{ref-TannerEtAl:2014}{}%
+Tanner, D., Nicol, J., \& Brehm, L.
+(2014).
+The time-course of feature interference in agreement comprehension: Multiple mechanisms and asymmetrical attraction.
+\emph{Journal of Memory and Language}, \emph{76}, 195--215.
+doi:\href{https://doi.org/10.1016/j.jml.2014.07.003}{10.1016/j.jml.2014.07.003}
+
+\leavevmode\hypertarget{ref-TuckerEtAl:2015}{}%
+Tucker, M.
+A., Idrissi, A., \& Almeida, D.
+(2015).
+Representing number in the real-time processing of agreement: Self-paced reading evidence from Arabic.
+\emph{Frontiers in Psychology}, \emph{6}(MAR), 1--21.
+doi:\href{https://doi.org/10.3389/fpsyg.2015.00347}{10.3389/fpsyg.2015.00347}
+
+\leavevmode\hypertarget{ref-Vasishth2018}{}%
+Vasishth, S., Mertzen, D., Jäger, L.
+A., \& Gelman, A.
+(2018).
+The statistical significance filter leads to overoptimistic expectations of replicability.
+\emph{Journal of Memory and Language}, \emph{103}, 151--175.
+
+\leavevmode\hypertarget{ref-WagersEtAl:2009}{}%
+Wagers, M.
+W., Lau, E.
+F., \& Phillips, C.
+(2009).
+Agreement attraction in comprehension: Representations and processes.
+\emph{Journal of Memory and Language}, \emph{61}(2), 206--237.
+doi:\href{https://doi.org/10.1016/j.jml.2009.04.002}{10.1016/j.jml.2009.04.002}
+
+\end{document}

### 2019-12-17 agremeent_draft_dec17/draft_dec17.Rnw
draft 2 coming along

\documentclass[a4paper,man,natbib]{apa6}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}

\title{The Role of Shallow Processing in Agreement Attraction}
\shorttitle{Your APA6-Style Manuscript}
\author{Utku Türk, Pavel Loga\v{c}ev}
\affiliation{Boğaziçi University}

\abstract{We report the results of two speeded acceptability judgment experiments in Turkish. We hypothesized an alternative explanation for agreement attraction effects in Turkish that is based on shallow processing. Our findings contradict our hypothesized form-driven processing strategy and support an account of agreement attraction based on the use of abstract linguistic features, rather than mere form.}
\input{settings.tex}
\begin{document}
\maketitle

section{Introduction} \label{sec:Intro}
\footnote{\printglossaries}. % add this to somewhere in the first page I suppose
\subsection{Agreement Attraction Thingy} \label{sec:Intro:literature}
\subsubsection{Morphophonology} \label{sec:Intro:literature:morphophonology}
%fill here accordingly to your results AFTER YOU WRITE THE RESULT.

\subsubsection{related sub-sub-field studies} \label{sec:Intro:literature:others}

\subsubsection{This work details} \label{sec:Intro:literature:thiswork}
% \citet{LagoEtAl:2018} hypothesize that genitive NPs can trigger agreement attraction in Turkish, because Turkish makes heavy use of genitive subjects, which means genitives are a priori likely to function as agreement controllers. The underlying assumption is that agreement processes rely on, at least partially, the case of an NP to determine its fit for the role of an agreement controller. 
% If that is so, their items are problematic %as in ... give an example
% in that the marking on the head noun is ambiguous between possessive and accusative case, while only possessive-marked NPs qualify as agreement controllers. Therefore, if engaged in shallow processing, readers may be more likely to misidentify the genitive NP as the agreement controller when the head noun, which is the only other alternative, is ambiguous, compared to when it is not.

% In Experiment 1, we decided to test this hypothesis

\section{Experiment 1} \label{sec:exp1}

In Experiment 1, we tested whether speakers of Turkish make fewer errors when the local ambiguity in the head noun is resolved. Specifically, we have replicated the \citet{LagoEtAl:2018} study. However, instead of using their NP heads, we chose to use nouns that end in a vowel, thus resolving the ambiguity between the accusative and possessive.

\subsection{Participants} \label{sec:exp1:participants}

One hundred seven native speakers of Turkish (\textit{X} male, \textit{Y} female) in Experiment 1. The mean age is \textit{Z}, ranging from \textit{Z1} to \textit{Z2}. Experiments in this paper were carried out following the Declaration of Helsinki and the regulations concerning ethics in research in Bo\u{g}azi\c{c}i University. All participants provided informed consent. They were tested online, on IbexFarm, using their preferred platform,

\subsection{Materials} \label{sec:exp1:materials}

In Experiment 1, participants first saw sentences word by word in the middle of their screen. As in \citet{LagoEtAl:2018} study, we used 40 sets of item and manipulated the grammaticality of the sentences (\textit{grammatical} x \textit{ungrammatical}) and the number of the attractor noun (\textit{singular} x \textit{plural}). All experimental sentences followed the following template: \textit{Noun$_{\Gen}$-Noun$_{\Poss}$-Adverb-Verb}. The distribution of the verb types followed the same pattern as in \citet{LagoEtAl:2018}, namely twenty unergatives, eighteen unaccusatives, and two optionally transitive verbs. The matrix verb was marked with overt plural marker \textit{-lar} in the half of experimental items. Adverbials in our experimental sentences were always pre-verbal and contained 2-3 words consisting of 15 characters on average. The second noun phrase is the head noun of the subject in all of our experimental sentences whereas the first noun phrase is the genitive modifier of the head, thus \textit{the attractor}. Unlike \citet{LagoEtAl:2018}, our head nouns were vowel-ending, which enables us to distinguish between accusative (\textit{-yI}) and possessive (\textit{-sI}). This change was due to the morpho-phonologic nature of possessive suffix in Turkish, which spell-outs as (\textit{-I}) after a consonant same as the accusative. While all of the head nouns were singular, the attractor noun was in its plural form in the half of the experimental items. One example set of experimental items can be seen in \ref{item:exp1ExperimentalItems}.

% there may be a better way of displaying items.
\ex. \label{item:exp1ExperimentalItems}
\a. \textit{Plural Attractor, Ungrammatical Verb} \label{item:exp1expitem-plpl}\\ 
\gll *Yönetici-ler-in aşcı-sı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
manager-\Pl{}-\Gen{}  cook-\Poss{} kitchen-\Loc{} non-stop  jump-\Prog{}-\Pl{}.\\
\glt `The cooks of the manager were jumping in the kitchen non-stop.' 
\b. \textit{Singular Attractor, Ungrammatical Verb} \label{item:exp1expitem-sgpl}\\ 
\gll *Yönetici-nin aşcı-sı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
manager-\Gen{}  cook-\Poss{} kitchen-\Loc{} non-stop  jump-\Prog{}-\Pl{}.\\
\glt `The cook of the manager were jumping in the kitchen non-stop.'
\c. \textit{Plural Attractor, Grammatical Verb} \label{item:exp1expitem-plsg}\\ 
\gll Yönetici-ler-in aşcı-sı mutfak-ta sürekli zıpl-ıyor.\\ 
manager-\Pl{}-\Gen{}  cook-\Poss{} kitchen-\Loc{} non-stop  jump-\Prog{}.\\
\glt `The cooks of the manager was jumping in the kitchen non-stop.'
\d. \textit{Singular Attractor, Grammatical Verb}\label{item:exp1expitem-sgsg}\\ 
\gll Yönetici-nin aşcı-sı mutfak-ta sürekli zıpl-ıyor. \\ 
manager-\Gen{}  cook-\Poss{} kitchen-\Loc{} non-stop  jump-\Prog{}.\\
\glt `The cook of the manager was jumping in the kitchen non-stop.'

As for the filler sentences, we have included forty sentences, half of which ends in singular and ungrammatical while the other half was plural and grammatical. These decisions were made due to the non-existence of such sentences in the experimental sentences. We wanted to rule out a possible task strategy where participants decide on the grammaticality of the sentence by merely checking the final plural marking. Even though filler items did not follow a strict template as the experimental items, they were created within a template of \textit{Noun$_{\Gen}$-Noun$_{\Poss}$-Converb-Noun-Adverb-Verb}. The ungrammaticality was created non-locally in the filler items to avoid task strategies. Example filler sentences can be seen in \ref{item:exp1FillerItems}.

\ex. \label{item:exp1FillerItems}
\a. \textit{Plural Grammatical Verb}\\ 
\gll Sosyolog-un öğrenci-si konuş-unca tutarsızlık açığ-a çıkar-dı-lar.\\ 
sociolog-\Gen{}  student-\Poss{} speak-\Nmlz{} inconsistency  open-\Dat{} deduct-\Pst{}-\Pl{}.\\
\glt `When the sociolog's student talked, they exposed an inconsistency.' 
\b. \textit{Singular Ungrammatical Verb}\\ 
\gll *Dansöz-ün koca-sı var-ınca kapı sakince aç-tı.\\ 
dancer-\Gen{}  husband-\Poss{} arrive-\Nmlz{} door slowly  open-\Pst{}.\\
\glt Intended:`When the husband of the dancer came, the door opened slowly.'

\subsection{Procedure} \label{sec:exp1:procedure}

Prior to the experiments, participants gave information regarding themselves and consent to participate in the experiment. They read the instructions where we showed what they will see in the experiment, and where we informed them to give quick and accurate answers during the experiment. They are also informed regarding the that there will be a time-limit in answering the question. Every session started with a practice session where participants have been informed to be a bit faster when they were not. The sentences were presented in the middle of the screen word-by-word on a web-based platform Ibex Farm (\url{http://spellout.net/ibexfarm/}). Each word was displayed with XX font size and stayed on the screen for 300 ms, unlike \citet{LagoEtAl:2018} and \citet{WagersEtAl:2009} where words stayed for 500 ms in the screen. After the sentence is completed, participants were asked: "How did they find the sentence?" They were informed to press P on their keyboard for \textit{good} and Q for bad. Apart from the practice items, we did not provide any feedback regarding their answers. However, participants were instructed to be faster when they waited more than 5,000 ms to answer the acceptability question.

Participants saw forty experimental and forty filler items. Experimental items were distributed among four different lists using Latin Square design. Every participant saw one version of the experiment with a specific list and one item per condition.

\subsection{Analysis} \label{sec:exp1:analysis}
% Maybe leave it to Pavel?

Every experimental item from both experiments (Experiment 1 and \citet{LagoEtAl:2018}) is included in the analysis. Participants (\textit{n=X}) that exceeded the threshold of 0.25 difference in giving accurate answers to grammatical conditions \ref{item:exp1expitem-sgsg} and \ref{item:exp1expitem-sgpl} are excluded from the analysis. We used R packages brms \citep{R-brms_b} and rstan \citep{R-stan} to fit Bayesian hierarchical models \citep{GelmanHill:2007}. We added our independent variables, i.e. grammaticality of the sentence and the overt number information on the distractors, and random variable experiment as a factor. Analyses by items and participants are also conducted as a part of the Bayesian hierarchical models. We added our independent variables, i.e. grammaticality of the sentence and the overt number information on the distractors, and random variable experiment as a factor. Analyses by items and participants are also conducted as a part of the Bayesian hierarchical models.
%I did not know how to state (1+x*y|subjet)
Data regarding our experiments and analysis can be found in \texttt{link hidden due to blind review}.

\subsection{Results} \label{sec:exp1:results}

\autoref{fig:exp1AvgResponse} shows the average proportions of ‘acceptable’ responses by experimental condition for both the original experiment in \citet{LagoEtAl:2018} and our replication with unambiguous possessive marking. It shows that ungrammatical sentences with plural attractors are rated as acceptable more often than their counterparts with singular attractors. In addition to ungrammatical conditions, accuracy rates within the grammatical conditions were comparable and high across conditions (mean = x\%, SE = x\%). As seen in \autoref{fig:exp1AvgResponse}, participants judged the sentences with plural attractor and singular verbs to be grammatical with the rate of X\%, which is in line with the findings reported in \citet{LagoEtAl:2018}.

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/exp1AvgResponse-1.png}
\caption{Percentage of ‘yes’ (acceptable) responses of Experiment 1 and \citet{LagoEtAl:2018}}
\label{fig:exp1AvgResponse}
\end{figure}

The estimates and 95\% CIs of a Bayesian GLM in \autoref{fig:exp1ResponseModel} confirm the observations we stated above: the positive interaction between sentence grammaticality and attractor number is in line with a larger effect of attractor number in ungrammatical sentences. The main effect of ungrammaticality was XX in log-odds, and the interaction between the ungrammaticality and plural attractor was XX in log-odds. Since other estimates' credible intervals range over zero, we conclude that they were not informative. %maybe speak with p values? 
% we did not do any nested analysis, should we? Should it say anything different than figure 2?

%Moreover, this findings are also predicted by cue-based retrieval models \citep{engelmann2019effect, vasishth2019computational} and last rendition of marking and morphing theory by \citet{HammerlyEtAl:2019}. %does it tho? especially with regards to what sol lago says: gen and morphophonology gives clues. maybe we should take a look at speeded acceptability? 
%maybe this is not the perfect place to write this.

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/exp1ResponseModelPlot-1.png}
\caption{Estimates and 95\% credible intervals for the regression coefficients for Experiment 1}
% give details regarding encoding etc.
\label{fig:exp1ResponseModel}
\end{figure}

\subsection{Discussion} \label{sec:exp1:discussion}

In Experiment 1, we have found number attraction effects in Turkish using genitive possessive structures, as it is also attested in \citet{LagoEtAl:2018}. To account for their findings, \citet{LagoEtAl:2018} assume a cue-based memory retrieval mechanism. That is, they assume that upon reaching the verb, the parser attempts to retrieve its agreement controller (the subject) using a cue-based retrieval mechanism \citep{LewisVasishth:2005,JagerEngelmannVasishth:2017}. The assumption is that in sentences such as \ref{item:exp1ExperimentalItems}, features such as case and number information are used to identify the agreement controller in memory. In ungrammatical sentences, when the verb bears plural agreement, no NP in memory will match both retrieval cues. However, in ungrammatical plural attractor conditions, the attractor matches one of the cues, which can lead to its erroneous retrieval on some occasions. This cannot happen in ungrammatical singular attractor conditions. This difference in the probability of erroneous retrievals is presumably what surfaced as a number agreement attraction effect, as observed in \citet{LagoEtAl:2018}, and our Experiment 1.

In their work, \citet{LagoEtAl:2018} argue that the agreement attraction in genitive-possessive structures in Turkish is due to the use of genitive case as a marker of embedded subjects in Turkish, i.e. differential subject marking (DSM) properties of Turkish \citep{kornfilt2009dom}. They argue that the genitive case in Turkish may not provide strong cue against subjecthood due to DSM while it does in English. Following this logic, we hypothesized that the other phenomenon that gives a strong clue against the subject should inhibit the illusionary dependencies as argued in \citet{nicol2016minimal}. One such phenomenon was present in the experimental items used in \citet{LagoEtAl:2018}: the morpho-phonologic ambiguity between the accusative and the possessive case. Since they use only consonant ending heads, the marking on the head is ambiguous between the accusative and the possessive marking. Following their argumentation, participants may search for other agreement controllers than the possessive marked heads when they are engaged in shallow processing and erroneously assign head as genitive marked distractor.

Nevertheless, we found that when the possessive marker is disambiguated agreement attraction does not diminish in effect size. As seen in \autoref{fig:exp1ResponseModel}, we successfully replicated the findings of \citet{LagoEtAl:2018} with disambiguated head nouns. Thus, we conclude that the morpho-phonological possessive-accusative ambiguity plays no role in number attraction in Turkish.

However, there is an alternative explanation that has yet to be ruled out: task-specific strategies. We hypothesized that readers may engage in an even shallower process in the evaluation of the sentences such as \ref{item:exp2ExperimentalItems} in which readers decide on the acceptability of the sentence with a faulty state of memory. In our model, we claim that after they read the sentence readers may end up with insufficient information to reliably judge the sentence. Upon such cases, readers may end up using extremely shallow processing methods such as matching the agreement-wise unrelated but form-wise related elements. % I should try a bit more to explain this part, I did not do a good job here.
We present our hypothesized decision tree in \autoref{fig:mptModel}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{example-grid-100x100pt} 
    \caption{Proposed multinomial processing tree of how people judge sentences in an agreement attraction task}
    \label{fig:mptModel}
\end{figure}

The aim of our second experiment was to test whether agreement attraction in Turkish may be an instance of a \textit{form-driven processing strategy}. Assuming that readers sometimes engage in shallow processing, they may end up with insufficient information to reliably classify a sentence as (un)acceptable. In such cases, participants may choose to classify sentences with plural-agreement-bearing verbs as acceptable if they have a memory of a nominal plural morpheme in the sentence. Such a response strategy would lead to a larger number of ‘acceptable’ responses in ungrammatical plural attractor conditions than in ungrammatical singular attractor conditions.

\section{Experiment 2} \label{sec:exp2}

In Experiment 2, we wanted to rule out the possibility of \textit{form-driven processing strategy}, namely participants deciding on the acceptability of a sentence using a memory of plural morpheme in the sentence when they do not have sufficient information to rate sentences (un)acceptable.

\subsection{Participants} \label{sec:exp2:participants}

Eighty native speakers of Turkish (\textit{X} male, \textit{Y} female) in Experiment 1. The mean age is \textit{Z}, ranging from \textit{Z1} to \textit{Z2}. Experiments in this paper were carried out following the Declaration of Helsinki and the regulations concerning ethics in research in Bo\u{g}azi\c{c}i University. All participants provided informed consent. They were tested online, on IbexFarm, using their preferred platform, % Find citation for using IbexFarm and online testing etc?

\subsection{Materials} \label{sec:exp2:materials}

In Experiment 2, participants saw the sentences word by word in the middle of their screen. We have again formed 40 sets of items. The grammaticality of the sentences (\textit{grammatical} x \textit{ungrammatical}) and the number of the attractor (\textit{singular} x \textit{plural}) were manipulated. Unlike Experiment 1, we used nominalized relative clause attractors instead of nouns. We took advantage of syncretism between Turkish nominal and verbal plural marker. Both of these morphemes spells-out as \textit{-lAr}, which enables us to check whether agreement attraction in Turkish can be explained by an extremely shallow dependency parsing based on the forms of morphemes rather than linguistic features.

All experimental sentences followed the same template as the experiment one except for the nature of the attractor: \textit{RC-Bare Noun-Adverb-Verb}. 
We have used the same verbs, and have not changed the distribution of verb types. We also utilized the same or extremely similar adverbials in length. We again did not manipulate the number of the head noun and manipulated the number of the attractor. Relative clauses we used in this experiment are all object relative clauses and they are all marked with canonical \textit{-dIK} nominalizer. Since Turkish is a pro-drop language, we also dropped the subject within the embedded clause, thus ending up with a one-word object relative clause whose head is also the controller of the number agreement on the matrix verb. One example set of experimental items can be seen in \ref{item:exp2ExperimentalItems}.

\ex. \label{item:exp2ExperimentalItems}
\a. \textit{Plural Attractor, Ungrammatical Verb}\\ 
\gll *Tut-tuk-lar-ı aşcı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
hire-\Nmlz{}-\Pl{}-\Poss{}  cook kitchen-\Loc{} non-stop  jump-\Prog{}-\Pl{}.\\
\glt `The cook that they hired were jumping in the kitchen non-stop.' 
\b. \textit{Singular Attractor, Ungrammatical Verb}\\ 
\gll *Tut-tuğ-u aşcı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
hıre-\Nmlz{}-\Poss{}  cook kitchen-\Loc{} non-stop  jump-\Prog{}-\Pl{}.\\
\glt `The cook that they hired were jumping in the kitchen non-stop.'
\c. \textit{Plural Attractor, Grammatical Verb}\\ 
\gll Tut-tuk-lar-ı aşcı mutfak-ta sürekli zıpl-ıyor.\\ 
hire-\Nmlz{}-\Pl{}-\Poss{}  cook kitchen-\Loc{} non-stop  jump-\Prog{}.\\
\glt `The cook that they hired was jumping in the kitchen non-stop.'
\d. \textit{Singular Attractor, Grammatical Verb}\\ 
\gll Tut-tuğ-u aşcı mutfak-ta sürekli zıpl-ıyor.\\ 
hıre-\Nmlz{}-\Poss{}  cook kitchen-\Loc{} non-stop  jump-\Prog{}.\\
\glt `The cook that they hired was jumping in the kitchen non-stop.'

In our filler items for Experiment 2, we made sure that every sentence starts with an object relative clause. We used plural distractors with grammatical verbs and singular distractors with ungrammatical verbs. In all of our filler sentences, the dependency between the first NP subject and its verb resolved in an adverbial embedded sentence. Grammatical filler items in Experiment 2 all had a template of \textit{RC$_{\Pl{}}$-Bare Noun-Adverb-Converb-Noun-Adverb-Verb$_{\Pl{}}$}, whereas ungrammatical filler items used a template of \textit{RC$_{\Sg{}}$-Bare Noun-Adverb-Converb-Noun-Adverb-Verb$_{\Sg{}}$}

Again, to avoid a possible strategy where participants use plural ending as a direct indication of ungrammaticality, half of our fillers were with an overt plural marking on a grammatical verb while the other half were without an overt plural marking on an ungrammatical verb. We used Turkish pro-drop characteristics which enable participants to form a dependency between the matrix verb and the null subject. Example filler sentences can be seen in \ref{item:exp2FillerItems}

\ex. \label{item:exp2FillerItems}
\a. \textit{Plural Grammatical Verb}\\ 
\gll Oku-t-tuk-lar-ı öğrenci başarılı ol-unca mutlu ol-du-lar.\\ 
read-\Caus{}-\Nmlz{}-\Pl{}-\Poss{}  student successful be-\Nmlz{} happy be-\Pst{}-\Pl{}.\\
\glt `When the student they sponsored become successful, they became happy.' 
\b. \textit{Singular Ungrammatical Verb}\\ 
\gll *Kandır-dığ-ı adam öde-me-yince bulaşık saatlerce yıka-dı.\\ 
trick-\Nmlz{}-\Poss{}  man pay-\Neg{}-\Nmlz{} dish for.hours clean-\Pst{}.\\
\glt Intended:`When the man he tricked did not pay, he cleaned dishes for hours.'

\subsection{Procedure and Analysis} \label{sec:exp2:procedure_analysis}

In Experiment 2, the same procedure as Experiment 1 has been followed with regards to how sentences are presented within the experiment.

We analyzed the percentages of 'yes' answers given by the participants in experimental conditions. In the analysis of this experiment, we have included experimental items from our Experiments 1 and 2 to check the interaction between experiments and quantify the difference between verbal and nominal plural markers. In Experiment 2 as well, we excluded participants (\textit{n=X}) who had more than 0.25 points of difference in accuracy between grammatical conditions, which implicates that they did not give enough attention to all conditions. We used R packages brms \citep{R-brms_b} and rstan \citep{R-stan} to fit Bayesian hierarchical models \citep{GelmanHill:2007}. We added our independent variables, i.e. grammaticality of the sentence and the overt number information on the distractors, and random variable experiment as a factor. Analyses by items and participants are also conducted as a 
part of the Bayesian hierarchical models. Data regarding our experiments and analysis can be found in \texttt{link hidden due to blind review}.

% Should I rephrase these parts?
%Prior the experiments, participant gave information regarding themselves and a consent to start to the experiment. They read the instructions where we showed what they will see in the experiment, what will be going to ask to participants, and where we informed them to be fast and accurate during the experiment. Every session started with practice session where participants have been informed being a bit faster when they were not. The sentences were presented in the middle of the screen word-by-word on a web-based platform Ibex Farm (\url{http://spellout.net/ibexfarm/}). Each word stayed on the screen for 300 ms, unlike \citet{LagoEtAl:2018} and \citet{WagersEtAl:2009} where words stayed for 500 ms in the screen. After the sentence is completed, participants were asked "How did they find the sentence?" They were informed to press P on their keyboard for \textit{good} and Q for bad. Apart from the practice items, we did not provide any feedback regarding their answer. However, participants were asked to be faster when they waited more than 5000 ms to answer the acceptability question.

\subsection{Results} \label{sec:exp2:results}

\autoref{fig:exp2AvgResponse} shows the average proportions of 'acceptable' responses by experimental conditions for both Experiment 1 and Experiment 2. We see that there is no effect resembling agreement attraction in the ungrammatical conditions of Experiment 2. Ungrammatical conditions showed comparable effects (X, Y) regardless of the attractor's number.  
\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/exp2AvgResponse-1.png}
\caption{Estimates and 95\% credible intervals for the regression coefficients for Experiment 1 and Experiment 2}
% give details regarding encoding etc.
\label{fig:exp2AvgResponse}
\end{figure}

The observations we made through \autoref{fig:exp2AvgResponse} also surfaces when we look at the estimates and 95\% CIs of a Bayesian GLM in \autoref{fig:exp2ResponseModel}. As is visible from the figure, the model shows a negative three-way interaction between grammaticality, type of attractor (nominal vs. verbal), and attractor number, which entails a reduced effect of agreement attraction in Experiment 2 compared to Experiment 1.

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/exp2ResponseModelPlot-1.png}
\caption{Estimates and 95\% credible intervals for the regression coefficients for Experiment 2}
% give details regarding encoding etc.
% similar to experiment1 model graph 
\label{fig:exp2ResponseModel}
\end{figure}

\subsection{Discussion} \label{sec:exp2:discussion}

In Experiment 2, we could not find any effect of agreement attraction in the acceptability ratings of ungrammatical conditions with a verbal plural attractor. However, number agreement attractions were observed when the attractors were nominal. Even though the forms of the two plural morphemes are the same form-wise, there is a distinct difference between the results of two experiments. One of the indications of zero-effect with verbal plural morpheme is that readers do not make decisions solely based on the form of the elements. This finding contradicts our hypothesized form-driven processing strategy and supports an account of agreement attraction based on the use of abstract linguistic features, rather than mere form.

However, results may be more telling with regards to the other theories of agreement attraction. These results seem unexpected within the cue-based retrieval mechanisms. Even though the root of the attractor is verbal, the morpheme is the same with the third person plural possessive marker since the relative clauses in Turkish are always nominalized and the subject is marked with the genitive case. The findings of this experiment indicate towards more fine-grained features needs to be utilized. One other possible explanation within the cue-based retrieval models can be formed around the status of agreement markers. One can say that the agreement process is completed in the verbal \textit{-lAr}; in other words, it is not the triggering morpheme but the probe of the agreement. This difference would mean that verbal \textit{-lAr} should not start any search for dependency resolution. In contrast to verbal \textit{-lAr}, the plural morpheme on the genitive is supposed to be triggering part of the agreement, not the probe. However, in Turkish embedded clauses, where genitive subjects can be seen, the number agreement works differently than the matrix level agreement. When the genitive subject of an embedded clause is marked with plural it is ungrammatical to have plural marking on the verb. 
This prohibition in return means that the genitive subjects should not create an expectation for a plural marked verb, which was believed to be the reason for the agreement attraction in \citet{LagoEtAl:2018}.

As for the marking and morphing theories, the results of Experiment 2 are completely expected and mitigated by the syntactic depth effects. Due to the genitive possessor's limited inner complexity compared to that of relative clause modifiers, marking and morphing theories would expect higher contribution from the genitive attractors to the final representation of number information.

\section{General Discussion} \label{sec:general_discussion}

\bibliography{library,new-references}

\end{document}

%
% Please see the package documentation for more information
% on the APA6 document class:
%
% http://www.ctan.org/pkg/apa6
%

### 2019-12-17 agremeent_draft_dec17/settings.tex
draft 2 coming along

\let\B\relax %to resolve a conflict in the definition of these commands between xyling and xunicode (the latter called by fontspec, called by charis)

\let\T\relax

\usepackage{xyling} %for trees; the use of xyling with the CharisSIL font produces poor results in the branches. This problem does not arise with the packages qtree or forest.
\usepackage[linguistics]{forest} %for nice trees!

\usepackage{leipzig}
\makeglossaries
\renewcommand{\glossarypreamble}{%
  Abbreviations are as follows:{\ }}

\usepackage{linguex}
\usepackage{hyperref}

### 2019-12-17 old_draft_Paper/paper_draft.rmd
draft 2 coming along

--- 2019-09-06 Paper/paper_draft.rmd
@@
 df_merged %<>% mutate(ResponseCorrect = (ResponseYes == (grammatical == "grammatical") ) )
-
-avg_clean <- df_merged %>%
-     group_by(experiment, source, grammatical, attractor_num) %>%
-     summarize(avgRT = mean(RT), 
-               avgRT_ResponseCorrect = mean(RT[ResponseCorrect]), 
-               p_yes = mean(ResponseYes, na.rm = T))
-
-avg_exp <- avg_clean %>% subset(is.na(source) | source != "filler")
-avg_fillers <- avg_clean %>% subset(source == "filler")
-
-p_avg_resp <- ggplot(avg_exp, 
-                     aes(grammatical, p_yes, #linetype = attractor_num, 
+df_merged_nonna <- df_merged %>% subset(!is.na(ResponseYes))
+
+# avg_clean <- 
+# df_merged %>% subset(experiment == "Lago et al. (2018)") %>%
+#      group_by(experiment, source, grammatical, attractor_num, subject) %>%
+#      summarize(p_yes = mean(ResponseYes, na.rm=T)) %>%
+#      summarize(p_yes = mean(p_yes))
+
+avg_clean <- list()
+avg_clean$resp <- df_merged_nonna %>% 
+              plyr::ddply(c("experiment"), function(df) {
+              df %>% se_cousineau(n_conditions = 4, subject, DV = ResponseYes, 
+                           group = c("experiment", "source", "grammatical", "attractor_num"), 
+                           is_proportion = TRUE)
+})
+
+avg_clean$rt <- df_merged_nonna %>%
+              plyr::ddply(c("experiment"), function(df) {
+              df %>% se_cousineau(n_conditions = 4, subject, DV = RT, 
+                           group = c("experiment", "source", "grammatical", "attractor_num"), 
+                           is_proportion = FALSE)
+})
+
+avg_clean$rt_correct <- df_merged_nonna %>% subset(ResponseCorrect) %>%
+              plyr::ddply(c("experiment"), function(df) {
+              df %>% se_cousineau(n_conditions = 4, subject, DV = RT, 
+                           group = c("experiment", "source", "grammatical", "attractor_num"), 
+                           is_proportion = FALSE)
+})
+
+avg_exp <- avg_clean %>% lapply(function(df) { df %>% subset(is.na(source) | source != "filler") })
+avg_fillers <- avg_clean %>% lapply(function(df) { df %>% subset(source == "filler") })
+
+p_avg_resp <- avg_exp$resp %>%
+              ggplot(aes(grammatical, M, #linetype = attractor_num, 
                          color = attractor_num, group = attractor_num)) + 
@@
                 facet_wrap(~experiment)
+
+p_avg_resp <- p_avg_resp + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1)
 
@@
 print(p_avg_resp)
+
+if (exists("le_poster")) {
+  p_avg_resp <- avg_exp$resp %>% subset(experiment == "Experiment 1") %>%
+                ggplot(aes(grammatical, M, #linetype = attractor_num, 
+                           color = attractor_num, group = attractor_num)) + 
+                  geom_point() + geom_line() + theme( strip.background = element_rect(fill="white")) +
+                  facet_wrap(~experiment)
+
+  p_avg_resp <- p_avg_resp + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1)
+
+  # p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) + 
+  #                             geom_point(data = avg_fillers) +
+
+  p_avg_resp <- p_avg_resp + theme( strip.background = element_rect(fill="white") ) +
+                             theme_bw() + xlab("") + ylab("Percentage 'acceptable'")
+  p_avg_resp <- p_avg_resp + scale_y_continuous(labels=scales::percent, limits = c(0,1))#, breaks = c(0, .25, .5, .75, 1))
+  p_avg_resp <- p_avg_resp + theme_bw()
+  p_avg_resp <- p_avg_resp + scale_color_discrete(name = "Attractor Number")
+  ggsave(filename = "./plots_le/exp1.jpeg", p_avg_resp, height = 2.5, width = 2.5*2)
+}
 
@@
 
+if (exists("le_poster"))
+{
+  fname_exp1_responses <- "../workspace_exp1/model_responses_justexp1"
+  m_responses_exp1 <- brm(ResponseYes ~ cUngrammatical * cAttractorPlural + 
+                                 (cUngrammatical * cAttractorPlural + 1| subject) +
+                                 (cUngrammatical * cAttractorPlural + 1| item),
+                   data = df_merged_nofillers %>% subset(experiment == "Experiment 1"),
+                   family = bernoulli("probit"),
+                   file = fname_exp1_responses, 
+                   chains = n_chains, cores = n_cores, iter = n_iter)
+
+}
+
 ```
@@
 })
+
+if (exists("le_poster"))
+{
+    p_m_response_exp1 <- 
+      create_model_coefs_plot( m_responses_exp1, 
+            plot_stats = T, map_names = contrast_names,
+            expand_right = 2.5, expand_top = 5, x_stat_adjust = 1.1,
+            x_breaks = c(-3,-2,-1, 0,1, 2) ) + 
+            xlab("Estimate (log-odds)")
+
+    p_m_response_exp1 <- p_m_response_exp1 + annotate(x=-3, xend=2, y=0, yend=0, lwd=0.25, geom="segment")
+
+    ggsave(filename = "./plots_le/m_exp1.jpeg", p_m_response_exp1, height = 1.5, width = 2.5*2)
+}
 
@@
 fname_data2 <- "../workspace_exp2/exp_data.rds"
-data2 <- readRDS(file = fname_data2)
+data_exp2 <- readRDS(file = fname_data2)
 
 # compute by-subject percentages of 'yes' responses, and average RTs 
-avg_by_subj2 <- data2 %>%
+avg_by_subj2 <- data_exp2 %>%
                 group_by(subject, experiment, condition, 
@@
 
-data_clean2 <- data2 %>% subset(!subject %in% bad_subjects)
+data_exp2_clean <- data_exp2 %>% subset(!subject %in% bad_subjects)
 
@@
 
-df_merge_exp2 <- data_clean2 %>% ungroup() %>% 
+df_merge_exp2 <- data_exp2_clean %>% ungroup() %>% 
                       dplyr::select(source=experiment, grammatical, attractor_num, # condition,
@@
 df_merged2 <- dplyr::bind_rows(df_merge_exp1, df_merge_exp2)
-df_merged2 %<>% subset(!is.na(ResponseYes))
 df_merged2$subject %<>% as.factor()
 df_merged2$item %<>% as.factor()
+
+df_merged2_nonna <- df_merged2 %>% subset(!is.na(ResponseYes))
 ```
@@
 
-avg_clean2 <- df_merged2 %>%
-                group_by(experiment, source, grammatical, attractor_num) %>%
-                summarize(avgRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T))
+# avg_clean2 <- df_merged2 %>%
+#                 group_by(experiment, source, grammatical, attractor_num) %>%
+#                 summarize(avgRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T))
+# # XXX
+
+avg_clean2 <- list()
+avg_clean2$resp <- df_merged2_nonna %>% 
+              plyr::ddply(c("experiment"), function(df) {
+              df %>% se_cousineau(n_conditions = 4, subject, DV = ResponseYes, 
+                           group = c("experiment", "source", "grammatical", "attractor_num"), 
+                           is_proportion = TRUE)
+})
+
+avg_clean2$rt <- df_merged2_nonna %>%
+              plyr::ddply(c("experiment"), function(df) {
+              df %>% se_cousineau(n_conditions = 4, subject, DV = RT, 
+                           group = c("experiment", "source", "grammatical", "attractor_num"), 
+                           is_proportion = FALSE)
+})
+
+# TODO: Code ResponseCorrect and re-enable
+# avg_clean$rt_correct <- df_merged2_nonna %>% subset(ResponseCorrect) %>%
+#               plyr::ddply(c("experiment"), function(df) {
+#               df %>% se_cousineau(n_conditions = 4, subject, DV = RT, 
+#                            group = c("experiment", "source", "grammatical", "attractor_num"), 
+#                            is_proportion = FALSE)
+# })
+
+avg_exp2 <- avg_clean2 %>% lapply(function(df) { df %>% subset(is.na(source) | source != "filler") })
+#avg_fillers <- avg_clean %>% lapply(function(df) { df %>% subset(source == "filler") })
+
 ```
@@
 
-<!-- to-do: add CIs to experiment 1 plot  -->
-<!-- to-do: add CIs to experiment 2 plot  -->
+<!-- note: Removed side-by-side plots for experiments 1 and 2. While it's a nice idea, it will inevitably lead to people misinterpreting the CIs for within-subject designs to
+           compare between experiments, and would like to prevent that. -->
 
@@
 
-avg_exp2 <- avg_clean2 %>% subset(is.na(source) | source != "filler")
-avg_fillers2 <- avg_clean2 %>% subset(source == "filler")
-
-p_avg_resp2 <- ggplot(avg_exp2, aes(grammatical, p_yes, #linetype = attractor_num, 
+avg_exp2 <- avg_clean2$resp %>% subset(is.na(source) | source != "filler") %>% subset(experiment == "Experiment 2")
+avg_fillers2 <- avg_clean2$resp %>% subset(source == "filler") %>% subset(experiment == "Experiment 2")
+
+p_avg_resp2 <- ggplot(avg_exp2, aes(grammatical, M, #linetype = attractor_num, 
                                     color = attractor_num, group = attractor_num)) + 
@@
 
+p_avg_resp2 <- p_avg_resp2 + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1)
 p_avg_resp2 <- p_avg_resp2 + scale_y_continuous(labels=scales::percent)
@@
 
+if (exists("le_poster")) {
+
+  p_avg_resp2 <- p_avg_resp2 + scale_y_continuous(labels=scales::percent, limits = c(0, 1))
+  ggsave(filename = "./plots_le/exp2.jpeg", p_avg_resp2, height = 2.5, width = 2.5*2)
+}
+
 ```
@@
 
+# to-do: Rename 'cVerbalPlural' to 'cVerbalAttractor'
 df_merged2 %<>% within(., {
@@
                     "cAttractorPlural" = "Plural Attactor",
+                    "cVerbalPlural" = "Verbal Attractor",
                     "cUngrammatical:cAttractorPlural" = "Ungrammaticality * Plural Attractor",
-                    "cVerbalPlural" = "Verbal Plural",
-                    "cVerbalPlural:cUngrammatical" = "Ungrammaticality * Verbal Plural",
-                    "cVerbalPlural:cAttractorPlural" = "Verbal Plural * Plural Attractor",
-                    "cVerbalPlural:cUngrammatical:cAttractorPlural" = "Verbal Plural * Ungrammaticality * Plural Attractor")
+                    "cVerbalPlural:cUngrammatical" = "Ungrammaticality * Verbal Attractor",
+                    "cVerbalPlural:cAttractorPlural" = "Verbal Attractor * Plural Attractor",
+                    "cVerbalPlural:cUngrammatical:cAttractorPlural" = "Verbal Attractor * Ungrammaticality * Plural Attractor")
 
@@
 print(p_m_response2 + annotate(x=-2, xend=2, y=0, yend=0, lwd=0.25, geom="segment"))
+
+if (exists("le_poster"))
+{
+contrast_names2_le <- c("cUngrammatical" = "Ungrammaticality",
+                    "cAttractorPlural" = "Plural Attactor",
+                    "cVerbalPlural" = "Verbal Attractor",
+                    "cUngrammatical:cAttractorPlural" = "Ungrammaticality * Plural Attractor",
+                    "cVerbalPlural:cUngrammatical" = "Ungrammaticality * Verbal Attractor",
+                    "cVerbalPlural:cAttractorPlural" = "Verbal Attractor * Plural Attractor",
+                    "cVerbalPlural:cUngrammatical:cAttractorPlural" = "Verbal Attractor * Ungrammaticality * Plural Attractor")
+
+    p_m_response_exp2 <- 
+      create_model_coefs_plot( m_responses2, 
+            plot_stats = T, map_names = contrast_names2_le,
+            expand_right = 4.5, expand_top = 1.5, x_stat_adjust = .75,
+            x_breaks = c(-3,-2,-1, 0, 1) ) + 
+            xlab("Estimate (log-odds)")
+
+    p_m_response_exp2 <- p_m_response_exp2 + annotate(x=-3, xend=1, y=0, yend=0, lwd=0.25, geom="segment")
+
+    ggsave(filename = "./plots_le/m_exp2.jpeg", p_m_response_exp2, height = 2.5, width = 2.5*2)
+}
 

### 2019-12-20 scripts/experiment1_eda.R
draft work

@@ -5,9 +5,9 @@ library(MASS)
 library(magrittr)
 library(ggplot2)
 
-fname_data <- "../workspace1/exp_data.rds"
+fname_data <- "../workspace_exp1/exp_data.rds"
 
-
+data <- readRDS(file = fname_data)
 dataAv <- data %>% 
   group_by(experiment, condition, grammatical, verb_num, attracted) %>%
   summarize(avRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T)) %>% 

### 2019-12-23 agremeent_draft_dec17/draft_dec17.Rnw
rnw done I guess

@@
-\documentclass[a4paper,man,natbib]{apa6}
-
+\documentclass[doc,a4paper,man,natbib,floatsintext,noextraspace]{apa6}
+<<echo=F>>=
+# Set the global chunk options
+set.seed(42)
+knitr::opts_chunk$set(encoding = 'UTF-8',
+                      cache.extra = knitr::rand_seed,
+                      echo = F,
+                      results = 'hide',
+                      message = F,
+                      warning = F)
+options("citation_format" = "pandoc")
+@
 \usepackage[english]{babel}
@@
 \usepackage[colorinlistoftodos]{todonotes}
+\usepackage[singlespacing]{setspace}
+<<>>=
+# load packages
+library(knitcitations)
+library(car, warn.conflicts = FALSE)
+library(MASS)
+library(brms)
+library(xtable)
+library(ggpubr)
+library(languageR)
+library(tidyverse)
+library(gdata)
+library(magrittr)
+library(ggplot2)
+theme_set(theme_bw())
 
+source("../scripts/misc.R")
+
+@
 \title{The Role of Shallow Processing in Agreement Attraction}
@@
 \begin{document}
+
 \maketitle
@@
 \section{Experiment 1} \label{sec:exp1}
+% do not do this in one chunk. differentiate the chunks and give them proper names.
+<<>>=
+fname_data <- "../workspace_exp1/exp_data.rds"
+data_exp1 <- readRDS(file = fname_data)
+
+### note: the low accuracy on fillers is not caused by a couple of items
+# filler_avgs <- 
+# data_exp1 %>% subset(Type == "filler") %>% group_by(Item, condition) %>% 
+#               summarize(M = mean(ResponseYes, na.rm = T)) %>%
+#               arrange(condition, Item)
+# fillers %>% subset(condition == "a") 
+# fillers %>% subset(condition == "b")
+###
+
+# compute by-subject percentages of 'yes' responses, and average RTs 
+avg_by_subj <- data_exp1 %>%
+                group_by(subject, experiment, condition, 
+                         grammatical, verb_num, attractor_num) %>%
+                summarize(avRT = mean(RT), 
+                          p_yes = mean(ResponseYes, na.rm = T), 
+                          N = sum(!is.na(ResponseYes))  )
+
+# reformat by-subject averages to a wide format
+avg_by_subj_wide <- avg_by_subj %>% 
+                      mutate(expcond = paste(experiment, condition, sep="_")) %>% 
+                      ungroup() %>%
+                      dplyr::select(-experiment, -condition, -avRT, -N,
+                                    -grammatical, -verb_num, -attractor_num) %>%
+                      tidyr::spread(expcond, p_yes) %>% 
+                      mutate(delta_dc = AgrAttr_d - AgrAttr_c)
+
+# Load Lago et al.'s monolingual data
+fname_lagoetal <- "../Data/Lago_et_al/Lago_data.csv"
+df_lagoetal <- read.csv(fname_lagoetal, encoding = "UTF-8", as.is = T)
+df_lagoetal %<>% subset(Group == "monolingual")
+df_lagoetal %<>% dplyr::select(-Accuracy, -L1:-Group, -List:-SelfRateGerman)
+
+# Note: All rows with Experiment == "offline" also seem to be for 
+#       the UNP task ('Grammatical' is NA). I wonder if these were
+#       the same subjects, or if the subject labels were simply the same
+#       for the two experiments.
+with(df_lagoetal, stopifnot( is.na(Grammatical) == (Experiment == "offline") ))
+
+df_lagoetal_unp <- df_lagoetal %>% 
+                    subset(is.na(Grammatical)) %>%
+                    dplyr::select(-Grammatical:-Label)
+df_lagoetal_attr <- df_lagoetal %>% 
+                  subset(!is.na(Grammatical)) %>%
+                  dplyr::select(-Distance:-NewCond)
+
+df_lagoetal_attr %<>% mutate(ResponseYes = (Response == "yes") ) %>% 
+                      dplyr::select(-Response)
+df_lagoetal_attr %<>% ungroup() %>%
+                      dplyr::select(grammatical=Grammatical,
+                                    attractor_num=Attractor,
+                                    experiment=Experiment,
+                                    lagoetal_condition=Condition, 
+                                    subject=Participant, 
+                                    item=Item,
+                                    ResponseYes,
+                                    RT)
+
+# map to our condition labels
+lagoetal_condition_mapping <- data.frame(
+    condition = c("a", "b", "c", "d"),
+    lagoetal_condition = c("d", "b", "c", "a"), 
+    stringsAsFactors = F)
+
+df_lagoetal_attr %<>% left_join( lagoetal_condition_mapping, by = "lagoetal_condition" )
+
+# compute by-subject percentages of 'yes' responses, and average RTs 
+avg_by_subj_lagoetal <- df_lagoetal_attr %>%
+            group_by(subject, experiment, condition, grammatical, attractor_num) %>%
+            summarize(avRT = mean(RT), 
+                      p_yes = mean(ResponseYes, na.rm = T), 
+                      N = sum(!is.na(ResponseYes))  )
+
+# reformat by-subject averages to a wide format
+avg_by_subj_lagoetal_wide <- avg_by_subj_lagoetal %>% 
+            mutate(expcond = paste(experiment, condition, sep="_")) %>% 
+            ungroup() %>%
+            dplyr::select(-experiment, -condition, -avRT, -N,
+                          -grammatical, -attractor_num) %>%
+            tidyr::spread(expcond, p_yes) %>% 
+            mutate(delta_dc = online_d - online_c)
+word_freq <- readxl::read_excel("../Data/freq.xlsx", sheet = 1)
+word_freq$freq_percentage %<>% as.numeric()
+word_freq %<>% dplyr::select(-freq_standardized, -freq_percentage, -word)
+word_freq %<>% tidyr::spread(place, freq_count)
+
+word_freq %<>% dplyr::group_by(exp) %>% 
+               dplyr::mutate( cat_n1 = ifelse(n1 > median(n1), "high", "low"),
+                              cat_n2 = ifelse(n2 > median(n2), "high", "low"),
+                              freqlog_n1 = scale(log(n1)),
+                              freqlog_n2 = scale(log(n2)),
+                              freqlog_n1n2 = log(n1) - log(n2)
+                            ) %>% 
+                ungroup()
+word_freq$cat_n1 %<>% as.factor()
+word_freq$cat_n2 %<>% as.factor()
+
+word_freq_exp1 <- word_freq %>% 
+                    subset(exp == "up") %>% 
+                    dplyr::select(-exp)
+word_freq_lago <- word_freq %>% 
+                    subset(exp == "lago") %>% 
+                    dplyr::select(-exp)
+
+# identify bad participants 
+bad_subjects <- subset(avg_by_subj_wide, delta_dc <= 0.25 ) %>% .$subject
+data_exp1_clean <- data_exp1 %>% subset(!subject %in% bad_subjects)
+
+# identify bad participants 
+bad_subjects_lagoetal <- subset(avg_by_subj_lagoetal_wide, delta_dc <= 0.25 ) %>% .$subject
+df_lagoetal_attr_clean <- df_lagoetal_attr %>% subset(!subject %in% bad_subjects_lagoetal)
+df_merge_exp1 <- data_exp1_clean %>% ungroup() %>% 
+                      dplyr::select(source=experiment, 
+                                    grammatical, attractor_num,
+                                    # condition,
+                                    subject, item=Item,
+                                    ResponseYes, RT)
+df_merge_exp1$experiment <- "Experiment 1"
+df_merge_exp1$grammatical <- with(df_merge_exp1, 
+                                  ifelse(grammatical == "gram", 
+                                          "grammatical",
+                                          "ungrammatical"))
+df_merge_exp1$attractor_num <- with(df_merge_exp1, 
+                                    ifelse(attractor_num == "pl",
+                                           "plural", 
+                                           "singular"))
+df_merge_exp1$item %<>% as.integer()
+df_merge_exp1$subject %<>% as.character()
+#df_merge_exp1 %<>% left_join(word_freq_exp1, by = "item")
+
+df_merge_lago <- df_lagoetal_attr_clean %>%
+                      ungroup() %>% 
+                      dplyr::select(grammatical, attractor_num,
+                                    subject, item, ResponseYes, RT)
+#df_merge_lago %<>% left_join(word_freq_lago, by = "item")
+df_merge_lago$experiment <- "Lago et al. (2018)" 
+df_merge_lago$source <- NA
+df_merge_lago$item %<>% add(1000)
+
+df_merged <- dplyr::bind_rows(df_merge_exp1, df_merge_lago)
+df_merged$subject %<>% as.factor()
+df_merged$item %<>% as.factor()
+
+df_exp1_na_nofillers <- subset(df_merge_exp1, is.na(ResponseYes) & source != "filler")
+df_merged %<>% subset( !is.na(ResponseYes) )
+
+@
 
@@
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=\textwidth]{figures/exp1AvgResponse-1.png}
-\caption{Percentage of ‘yes’ (acceptable) responses of Experiment 1 and \citet{LagoEtAl:2018}}
-\label{fig:exp1AvgResponse}
-\end{figure}
+<<exp1AvgResponse, fig.cap='Percentage of \\emph{yes} (acceptable) responses of Experiment 1 and \\citet{LagoEtAl:2018}', fig.height=3, fig.align='center'>>=
+
+df_merged %<>% mutate(ResponseCorrect = (ResponseYes == (grammatical == "grammatical") ) )
+df_merged_nonna <- df_merged %>% subset(!is.na(ResponseYes))
+
+# avg_clean <- 
+# df_merged %>% subset(experiment == "Lago et al. (2018)") %>%
+#      group_by(experiment, source, grammatical, attractor_num, subject) %>%
+#      summarize(p_yes = mean(ResponseYes, na.rm=T)) %>%
+#      summarize(p_yes = mean(p_yes))
+
+avg_clean <- list()
+avg_clean$resp <- df_merged_nonna %>% 
+              plyr::ddply(c("experiment"), function(df) {
+              df %>% se_cousineau(n_conditions = 4, subject, DV = ResponseYes, 
+                           group = c("experiment", "source", "grammatical", "attractor_num"), 
+                           is_proportion = TRUE)
+})
+
+avg_clean$rt <- df_merged_nonna %>%
+              plyr::ddply(c("experiment"), function(df) {
+              df %>% se_cousineau(n_conditions = 4, subject, DV = RT, 
+                           group = c("experiment", "source", "grammatical", "attractor_num"), 
+                           is_proportion = FALSE)
+})
+
+avg_clean$rt_correct <- df_merged_nonna %>% subset(ResponseCorrect) %>%
+              plyr::ddply(c("experiment"), function(df) {
+              df %>% se_cousineau(n_conditions = 4, subject, DV = RT, 
+                           group = c("experiment", "source", "grammatical", "attractor_num"), 
+                           is_proportion = FALSE)
+})
+
+avg_exp <- avg_clean %>% lapply(function(df) { df %>% subset(is.na(source) | source != "filler") })
+avg_fillers <- avg_clean %>% lapply(function(df) { df %>% subset(source == "filler") })
+
+p_avg_resp <- avg_exp$resp %>%
+              ggplot(aes(grammatical, M, #linetype = attractor_num, 
+                         color = attractor_num, group = attractor_num)) + 
+                geom_point() + geom_line() + 
+                facet_wrap(~experiment)
+
+p_avg_resp <- p_avg_resp + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1)
+
+# p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) + 
+#                             geom_point(data = avg_fillers) +
+
+p_avg_resp <- p_avg_resp + theme( strip.background = element_rect(fill="white") ) +
+                           theme_bw() + xlab("") + ylab("Percentage 'acceptable'")
+p_avg_resp <- p_avg_resp + scale_y_continuous(labels=scales::percent)#, breaks = c(0, .25, .5, .75, 1))
+p_avg_resp <- p_avg_resp + theme_bw()
+p_avg_resp <- p_avg_resp + scale_color_discrete(name = "Attractor Number")
+print(p_avg_resp)
+
+if (exists("le_poster")) {
+  p_avg_resp <- avg_exp$resp %>% subset(experiment == "Experiment 1") %>%
+                ggplot(aes(grammatical, M, #linetype = attractor_num, 
+                           color = attractor_num, group = attractor_num)) + 
+                  geom_point() + geom_line() + theme( strip.background = element_rect(fill="white")) +
+                  facet_wrap(~experiment)
+
+  p_avg_resp <- p_avg_resp + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1)
+
+  # p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) + 
+  #                             geom_point(data = avg_fillers) +
+
+  p_avg_resp <- p_avg_resp + theme( strip.background = element_rect(fill="white") ) +
+                             theme_bw() + xlab("") + ylab("Percentage 'acceptable'")
+  p_avg_resp <- p_avg_resp + scale_y_continuous(labels=scales::percent, limits = c(0,1))#, breaks = c(0, .25, .5, .75, 1))
+  p_avg_resp <- p_avg_resp + theme_bw()
+  p_avg_resp <- p_avg_resp + scale_color_discrete(name = "Attractor Number")
+  ggsave(filename = "./plots_le/exp1.jpeg", p_avg_resp, height = 2.5, width = 2.5*2)
+}
+
+@
 
@@
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=\textwidth]{figures/exp1ResponseModelPlot-1.png}
-\caption{Estimates and 95\% credible intervals for the regression coefficients for Experiment 1}
-% give details regarding encoding etc.
-\label{fig:exp1ResponseModel}
-\end{figure}
+<<>>=
+
+df_merged %<>% within(., {
+  cGrammatical <- ifelse(grammatical == "grammatical", .5, -.5)
+  cUngrammatical <- ifelse(grammatical == "ungrammatical", .5, -.5)
+  cAttractorPlural <- ifelse(attractor_num == "plural", .5, -.5)
+  cEndsInConsonant <- ifelse(experiment != "Experiment 1", .5, -.5)
+  #cFreqlog_n1n2 <- scale(freqlog_n1n2)
+  #cFreqlog_n1 <- scale(freqlog_n1)
+  #cFreqlog_n2 <- scale(freqlog_n2)
+})
+df_merged_nofillers <- df_merged %>% subset(is.na(source) | source != "filler")
+
+# ## test model parameterization using a simple GLM first
+# m <- glm(ResponseYes ~ (cFreqlog_n1 + cFreqlog_n2) *
+#            cEndsInConsonant * cUngrammatical * cAttractorPlural,
+#          data = df_merged_nofillers,
+#          family = binomial("probit"))
+# summary(m)
+
+n_chains <- 4
+n_cores <- 4
+n_iter <- 2000
+
+fname_exp1_responses <- "../workspace_exp1/model_responses"
+m_responses <- brm(ResponseYes ~ cEndsInConsonant * cUngrammatical * cAttractorPlural + 
+                                 (cUngrammatical * cAttractorPlural + 1| subject) +
+                                 (cUngrammatical * cAttractorPlural + 1| item),
+                   data = df_merged_nofillers,
+                   family = bernoulli("probit"),
+                   file = fname_exp1_responses, 
+                   chains = n_chains, cores = n_cores, iter = n_iter)
+
+fname_exp1_responses_minimal <- "../workspace_exp1/model_responses_minimal"
+m_responses_minimal <- brm(ResponseYes ~ (cEndsInConsonant + cUngrammatical + cAttractorPlural)^2 + 
+                                         (cUngrammatical * cAttractorPlural + 1| subject) +
+                                         (cUngrammatical * cAttractorPlural + 1| item),
+                   data = df_merged_nofillers,
+                   family = bernoulli("probit"),
+                   file = fname_exp1_responses_minimal, 
+                   chains = n_chains, cores = n_cores, iter = n_iter)
+
+fname_exp1_rts <- "../workspace_exp1/model_responses_rt"
+m_rts <- brm(RT ~ cEndsInConsonant * cUngrammatical * cAttractorPlural +
+                                 (cUngrammatical * cAttractorPlural + 1| subject) +
+                                 (cUngrammatical * cAttractorPlural + 1| item),
+                   data = df_merged_nofillers,
+                   family = lognormal(),
+                   file = fname_exp1_rts,
+                   chains = n_chains, cores = n_cores, iter = n_iter)
+
+if (exists("le_poster"))
+{
+  fname_exp1_responses <- "../workspace_exp1/model_responses_justexp1"
+  m_responses_exp1 <- brm(ResponseYes ~ cUngrammatical * cAttractorPlural + 
+                                 (cUngrammatical * cAttractorPlural + 1| subject) +
+                                 (cUngrammatical * cAttractorPlural + 1| item),
+                   data = df_merged_nofillers %>% subset(experiment == "Experiment 1"),
+                   family = bernoulli("probit"),
+                   file = fname_exp1_responses, 
+                   chains = n_chains, cores = n_cores, iter = n_iter)
+
+}
+
+@
+
+<<exp1ResponseModel, fig.cap='Estimates and 95\\% credible intervals for the regression coefficients for Experiment 1', fig.height=3, fig.align='center'>>=
+contrast_names <- c("cUngrammatical" = "Ungrammaticality",
+                    "cAttractorPlural" = "Plural Attactor",
+                    "cUngrammatical:cAttractorPlural" = "Ungrammaticality * Plural Attractor",
+                    "cEndsInConsonant" = "Ambiguity",
+                    "cEndsInConsonant:cUngrammatical" = "Ambiguity * Ungrammaticality",
+                    "cEndsInConsonant:cAttractorPlural" = "Ambiguity * Plural Attractor",
+                    "cEndsInConsonant:cUngrammatical:cAttractorPlural" = "Ambiguity * Ungrammaticality * Plural Attractor")
+
+p_m_response <- 
+  create_model_coefs_plot( m_responses, 
+        plot_stats = T, map_names = contrast_names,
+        expand_right = 2.5, expand_top = 2, x_stat_adjust = 1.1,
+        x_breaks = c(-3,-2,-1, 0,1, 2) ) + 
+        xlab("Estimate (log-odds)")
+
+suppressWarnings({
+print(p_m_response + annotate(x=-3, xend=2, y=0, yend=0, lwd=0.25, geom="segment"))
+})
+
+if (exists("le_poster"))
+{
+    p_m_response_exp1 <- 
+      create_model_coefs_plot( m_responses_exp1, 
+            plot_stats = T, map_names = contrast_names,
+            expand_right = 2.5, expand_top = 5, x_stat_adjust = 1.1,
+            x_breaks = c(-3,-2,-1, 0,1, 2) ) + 
+            xlab("Estimate (log-odds)")
+
+    p_m_response_exp1 <- p_m_response_exp1 + annotate(x=-3, xend=2, y=0, yend=0, lwd=0.25, geom="segment")
+
+    ggsave(filename = "./plots_le/m_exp1.jpeg", p_m_response_exp1, height = 1.5, width = 2.5*2)
+}
+@
 
@@
 
+<<loadExperiment2Data>>=
+fname_data2 <- "../workspace_exp2/exp_data.rds"
+data_exp2 <- readRDS(file = fname_data2)
+
+# compute by-subject percentages of 'yes' responses, and average RTs 
+avg_by_subj2 <- data_exp2 %>%
+                group_by(subject, experiment, condition, 
+                         grammatical, verb_num, attractor_num) %>%
+                summarize(avRT = mean(RT), 
+                          p_yes = mean(ResponseYes, na.rm = T), 
+                          N = sum(!is.na(ResponseYes))  )
+
+# reformat by-subject averages to a wide format
+avg_by_subj_wide2 <- avg_by_subj2 %>% 
+                      mutate(expcond = paste(experiment, condition, sep="_")) %>% 
+                      ungroup() %>%
+                      dplyr::select(-experiment, -condition, -avRT, -N,
+                                    -grammatical, -verb_num, -attractor_num) %>%
+                      tidyr::spread(expcond, p_yes) %>% 
+                      mutate(delta_dc = AgrAttr_d - AgrAttr_c)
+
+@
+
+<<badSubjects2>>=
+# identify participants 
+bad_subjects2 <- subset(avg_by_subj_wide2, delta_dc <= 0.25 ) %>% .$subject
+
+data_exp2_clean <- data_exp2 %>% subset(!subject %in% bad_subjects)
+
+@
+
+<<mergeData2>>=
+
+df_merge_exp2 <- data_exp2_clean %>% ungroup() %>% 
+                      dplyr::select(source=experiment, grammatical, attractor_num, # condition,
+                                    subject, item=Item,
+                                    ResponseYes, RT)
+df_merge_exp2$experiment <- "Experiment 2"
+df_merge_exp2$grammatical <- with(df_merge_exp2, ifelse(grammatical == "gram", 
+                                                        "grammatical",
+                                                        "ungrammatical"))
+df_merge_exp2$attractor_num <- with(df_merge_exp2, ifelse(attractor_num == "pl", 
+                                                          "plural", 
+                                                          "singular"))
+df_merge_exp2$item %<>% as.integer()
+df_merge_exp2$subject %<>% as.character()
+
+df_exp2_na_nofillers <- subset(df_merge_exp2, is.na(ResponseYes))
+
+df_merged2 <- dplyr::bind_rows(df_merge_exp1, df_merge_exp2)
+df_merged2$subject %<>% as.factor()
+df_merged2$item %<>% as.factor()
+
+df_merged2_nonna <- df_merged2 %>% subset(!is.na(ResponseYes))
+@
+
+<<computeAverages2>>=
+
+# avg_clean2 <- df_merged2 %>%
+#                 group_by(experiment, source, grammatical, attractor_num) %>%
+#                 summarize(avgRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T))
+# # XXX
+
+avg_clean2 <- list()
+avg_clean2$resp <- df_merged2_nonna %>% 
+              plyr::ddply(c("experiment"), function(df) {
+              df %>% se_cousineau(n_conditions = 4, subject, DV = ResponseYes, 
+                           group = c("experiment", "source", "grammatical", "attractor_num"), 
+                           is_proportion = TRUE)
+})
+
+avg_clean2$rt <- df_merged2_nonna %>%
+              plyr::ddply(c("experiment"), function(df) {
+              df %>% se_cousineau(n_conditions = 4, subject, DV = RT, 
+                           group = c("experiment", "source", "grammatical", "attractor_num"), 
+                           is_proportion = FALSE)
+})
+
+# TODO: Code ResponseCorrect and re-enable
+# avg_clean$rt_correct <- df_merged2_nonna %>% subset(ResponseCorrect) %>%
+#               plyr::ddply(c("experiment"), function(df) {
+#               df %>% se_cousineau(n_conditions = 4, subject, DV = RT, 
+#                            group = c("experiment", "source", "grammatical", "attractor_num"), 
+#                            is_proportion = FALSE)
+# })
+
+avg_exp2 <- avg_clean2 %>% lapply(function(df) { df %>% subset(is.na(source) | source != "filler") })
+#avg_fillers <- avg_clean %>% lapply(function(df) { df %>% subset(source == "filler") })
+
+@
+
 In Experiment 2, the same procedure as Experiment 1 has been followed with regards to how sentences are presented within the experiment.
@@
 Ungrammatical conditions showed comparable effects (X, Y) regardless of the attractor's number.
-\begin{figure}[h]
-\centering
-\includegraphics[width=\textwidth]{figures/exp2AvgResponse-1.png}
-\caption{Estimates and 95\% credible intervals for the regression coefficients for Experiment 1 and Experiment 2}
-% give details regarding encoding etc.
-\label{fig:exp2AvgResponse}
-\end{figure}
+
+<<exp2AvgResponse, fig.cap='Estimates and 95\\% credible intervals for the regression coefficients for Experiment 1 and Experiment 2', fig.height=3, fig.align='center'>>=
+
+avg_exp2 <- avg_clean2$resp %>% subset(is.na(source) | source != "filler") %>% subset(experiment == "Experiment 2")
+avg_fillers2 <- avg_clean2$resp %>% subset(source == "filler") %>% subset(experiment == "Experiment 2")
+
+p_avg_resp2 <- ggplot(avg_exp2, aes(grammatical, M, #linetype = attractor_num, 
+                                    color = attractor_num, group = attractor_num)) + 
+                geom_point() + geom_line() + 
+                facet_wrap(~experiment) +
+                theme_bw() + theme( strip.background = element_rect(fill="white") ) +
+                xlab("") + ylab("Percentage 'acceptable'")
+
+p_avg_resp2 <- p_avg_resp2 + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1)
+p_avg_resp2 <- p_avg_resp2 + scale_y_continuous(labels=scales::percent)
+p_avg_resp2 <- p_avg_resp2 + scale_color_discrete(name = "Attractor Number")
+
+print(p_avg_resp2)
+
+if (exists("le_poster")) {
+
+  p_avg_resp2 <- p_avg_resp2 + scale_y_continuous(labels=scales::percent, limits = c(0, 1))
+  ggsave(filename = "./plots_le/exp2.jpeg", p_avg_resp2, height = 2.5, width = 2.5*2)
+}
+
+@
 
@@
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=\textwidth]{figures/exp2ResponseModelPlot-1.png}
-\caption{Estimates and 95\% credible intervals for the regression coefficients for Experiment 2}
-% give details regarding encoding etc.
-% similar to experiment1 model graph 
-\label{fig:exp2ResponseModel}
-\end{figure}
+<<Model>>=
+
+# to-do: Rename 'cVerbalPlural' to 'cVerbalAttractor'
+df_merged2 %<>% within(., {
+  cGrammatical <- ifelse(grammatical == "grammatical", .5, -.5)
+  cUngrammatical <- ifelse(grammatical == "ungrammatical", .5, -.5)
+  cAttractorPlural <- ifelse(attractor_num == "plural", .5, -.5)
+  cVerbalPlural <- ifelse(experiment == "Experiment 2", .5, -.5)
+})
+df_merged_nofillers2 <- df_merged2 %>% subset(is.na(source) | source != "filler")
+
+# ## test model parameterization using a simple GLM first
+# m <- glm(ResponseYes ~ cEndsInConsonant * cUngrammatical * cAttractorPlural,
+#          data = df_merged_nofillers,
+#          family = binomial("probit"))
+# summary(m)
+
+n_chains <- 4
+n_cores <- 4
+n_iter <- 2000
+
+fname_exp2_responses <- "../workspace_exp2/model_responses"
+
+library(brms)
+
+m_responses2 <- brm(ResponseYes ~ cVerbalPlural * cUngrammatical * cAttractorPlural + 
+                                 (cUngrammatical * cAttractorPlural + 1| subject) +
+                                 (cUngrammatical * cAttractorPlural + 1| item),
+                   data = df_merged_nofillers2,
+                   family = bernoulli("probit"),
+                   file = fname_exp2_responses, 
+                   chains = n_chains, cores = n_cores, iter = n_iter)
+
+@
+
+<<exp2ResponseModel, fig.cap='Estimates and 95\\% credible intervals for the regression coefficients for Experiment 2', fig.height=3, fig.align='center'>>=
+
+contrast_names2 <- c("cUngrammatical" = "Ungrammaticality",
+                    "cAttractorPlural" = "Plural Attactor",
+                    "cVerbalPlural" = "Verbal Attractor",
+                    "cUngrammatical:cAttractorPlural" = "Ungrammaticality * Plural Attractor",
+                    "cVerbalPlural:cUngrammatical" = "Ungrammaticality * Verbal Attractor",
+                    "cVerbalPlural:cAttractorPlural" = "Verbal Attractor * Plural Attractor",
+                    "cVerbalPlural:cUngrammatical:cAttractorPlural" = "Verbal Attractor * Ungrammaticality * Plural Attractor")
+
+p_m_response2 <- create_model_coefs_plot(m_responses2, map_names = contrast_names2)
+p_m_response2 <- p_m_response2 + xlab("Estimate (log-odds)")
+print(p_m_response2 + annotate(x=-2, xend=2, y=0, yend=0, lwd=0.25, geom="segment"))
+
+if (exists("le_poster"))
+{
+contrast_names2_le <- c("cUngrammatical" = "Ungrammaticality",
+                    "cAttractorPlural" = "Plural Attactor",
+                    "cVerbalPlural" = "Verbal Attractor",
+                    "cUngrammatical:cAttractorPlural" = "Ungrammaticality * Plural Attractor",
+                    "cVerbalPlural:cUngrammatical" = "Ungrammaticality * Verbal Attractor",
+                    "cVerbalPlural:cAttractorPlural" = "Verbal Attractor * Plural Attractor",
+                    "cVerbalPlural:cUngrammatical:cAttractorPlural" = "Verbal Attractor * Ungrammaticality * Plural Attractor")
+
+    p_m_response_exp2 <- 
+      create_model_coefs_plot( m_responses2, 
+            plot_stats = T, map_names = contrast_names2_le,
+            expand_right = 4.5, expand_top = 1.5, x_stat_adjust = .75,
+            x_breaks = c(-3,-2,-1, 0, 1) ) + 
+            xlab("Estimate (log-odds)")
+
+    p_m_response_exp2 <- p_m_response_exp2 + annotate(x=-3, xend=1, y=0, yend=0, lwd=0.25, geom="segment")
+
+    ggsave(filename = "./plots_le/m_exp2.jpeg", p_m_response_exp2, height = 2.5, width = 2.5*2)
+}
+
+@
 

### 2019-12-23 agremeent_draft_dec17/draft_dec17.tex
draft work
rnw done I guess

--- 2019-12-17 agremeent_draft_dec17/draft_dec17.Rnw
@@
-\documentclass[a4paper,man,natbib]{apa6}
+\documentclass[doc,a4paper,man,natbib,floatsintext,noextraspace]{apa6}\usepackage[]{graphicx}\usepackage[]{color}
+% maxwidth is the original width if it is less than linewidth
+% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+\let\hlipl\hlkwb
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}
 
@@
 \usepackage[colorinlistoftodos]{todonotes}
+\usepackage[singlespacing]{setspace}
 
@@
 \input{settings.tex}
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}
+
 \maketitle
@@
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=\textwidth]{figures/exp1AvgResponse-1.png}
-\caption{Percentage of ‘yes’ (acceptable) responses of Experiment 1 and \citet{LagoEtAl:2018}}
-\label{fig:exp1AvgResponse}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+
+{\centering \includegraphics[width=\maxwidth]{figure/exp1AvgResponse-1}
+
+}
+
+\caption{Percentage of \emph{yes} (acceptable) responses of Experiment 1 and \citet{LagoEtAl:2018}}\label{fig:exp1AvgResponse}
 \end{figure}
+
+\end{knitrout}
 

### 2019-12-23 agremeent_draft_dec17/draft_dec17.Rnw
rnw still being done

@@
 @
+
+<<setup, echo=FALSE, cache=FALSE>>=
+## numbers >= 10^5 will be denoted in scientific notation,
+## and rounded to 2 digits
+options(scipen = 1, digits = 2)
+@
+
 \usepackage[english]{babel}
@@
 data_exp1 <- readRDS(file = fname_data)
+fname_form <- "../workspace_exp1/exp_form.rds"
+form_exp1 <- readRDS(file = fname_form)
+form_exp1[106,2] = 18 # manually changed on sekiz to 18
 
@@
 One hundred seven native speakers of Turkish (\textit{X} male, \textit{Y} female) in Experiment 1.
-The mean age is \textit{Z}, ranging from \textit{Z1} to \textit{Z2}.
+The mean age is \Sexpr{mean(as.numeric(as.character(form_exp1$Age)))} , ranging from \Sexpr{min(as.numeric(as.character(form_exp1$Age)))} to \Sexpr{max(as.numeric(as.character(form_exp1$Age)))}.
 Experiments in this paper were carried out following the Declaration of Helsinki and the regulations concerning ethics in research in Bo\u{g}azi\c{c}i University.
@@
 Every experimental item from both experiments (Experiment 1 and \citet{LagoEtAl:2018}) is included in the analysis.
-Participants (\textit{n=X}) that exceeded the threshold of 0.25 difference in giving accurate answers to grammatical conditions \ref{item:exp1expitem-sgsg} and \ref{item:exp1expitem-sgpl} are excluded from the analysis.
+Participants (\Sexpr{length(bad_subjects)}) that exceeded the threshold of 0.25 difference in giving accurate answers to grammatical conditions \ref{item:exp1expitem-sgsg} and \ref{item:exp1expitem-sgpl} are excluded from the analysis.
 We used R packages brms \citep{R-brms_b} and rstan \citep{R-stan} to fit Bayesian hierarchical models \citep{GelmanHill:2007}.

### 2019-12-23 agremeent_draft_dec17/draft_dec17.Rnw
models are run,use lfs for big files

@@
 \usepackage{amsmath}
+\usepackage{amsthm}
 \usepackage{graphicx}
@@
 # load packages
+library(patchSynctex)
 library(knitcitations)
@@
 
+\printglossary[title=\MakeUppercase{glosses}, style=block,nonumberlist]
+
 section{Introduction} \label{sec:Intro}
-\footnote{\printglossaries}. % add this to somewhere in the first page I suppose
+%\footnote{\printglossaries}. % add this to somewhere in the first page I suppose
 \subsection{Agreement Attraction Thingy} \label{sec:Intro:literature}
@@
 The mean age is \Sexpr{mean(as.numeric(as.character(form_exp1$Age)))} , ranging from \Sexpr{min(as.numeric(as.character(form_exp1$Age)))} to \Sexpr{max(as.numeric(as.character(form_exp1$Age)))}.
+Across participants, a total \sExpr{sum(is.na(df_exp1_na_nofillers$ResponseYes))} trials were not responded to before the 5 second deadline by \Sexpr{length(unique(df_exp1_na_nofillers$subject))} participants.
 Experiments in this paper were carried out following the Declaration of Helsinki and the regulations concerning ethics in research in Bo\u{g}azi\c{c}i University.
@@
 
-<<>>=
+<<exp1models, include=FALSE>>=
 
@@
 data_exp2 <- readRDS(file = fname_data2)
-
+### PUT FORM###
 # compute by-subject percentages of 'yes' responses, and average RTs 
@@
 
-<<Model>>=
+<<Model, include=FALSE>>=
 

### 2019-12-23 agremeent_draft_dec17/draft_dec17.tex
models are run,use lfs for big files

@@
 \section{Experiment 1} \label{sec:exp1}
+% do not do this in one chunk. differentiate the chunks and give them proper names.
 
@@
 One hundred seven native speakers of Turkish (\textit{X} male, \textit{Y} female) in Experiment 1.
-The mean age is \textit{Z}, ranging from \textit{Z1} to \textit{Z2}.
+The mean age is 20.14 , ranging from 18 to 32.
+Across participants, a total \sExpr{sum(is.na(df_exp1_na_nofillers$ResponseYes))} trials were not responded to before the 5 second deadline by 33 participants.
 Experiments in this paper were carried out following the Declaration of Helsinki and the regulations concerning ethics in research in Bo\u{g}azi\c{c}i University.
@@
 Every experimental item from both experiments (Experiment 1 and \citet{LagoEtAl:2018}) is included in the analysis.
-Participants (\textit{n=X}) that exceeded the threshold of 0.25 difference in giving accurate answers to grammatical conditions \ref{item:exp1expitem-sgsg} and \ref{item:exp1expitem-sgpl} are excluded from the analysis.
+Participants (10) that exceeded the threshold of 0.25 difference in giving accurate answers to grammatical conditions \ref{item:exp1expitem-sgsg} and \ref{item:exp1expitem-sgpl} are excluded from the analysis.
 We used R packages brms \citep{R-brms_b} and rstan \citep{R-stan} to fit Bayesian hierarchical models \citep{GelmanHill:2007}.
@@
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=\textwidth]{figures/exp1ResponseModelPlot-1.png}
-\caption{Estimates and 95\% credible intervals for the regression coefficients for Experiment 1}
-% give details regarding encoding etc.
-\label{fig:exp1ResponseModel}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+
+{\centering \includegraphics[width=\maxwidth]{figure/exp1ResponseModel-1}
+
+}
+
+\caption[Estimates and 95\% credible intervals for the regression coefficients for Experiment 1]{Estimates and 95\% credible intervals for the regression coefficients for Experiment 1}\label{fig:exp1ResponseModel}
 \end{figure}
+
+\end{knitrout}
 
@@
 Ungrammatical conditions showed comparable effects (X, Y) regardless of the attractor's number.
-\begin{figure}[h]
-\centering
-\includegraphics[width=\textwidth]{figures/exp2AvgResponse-1.png}
-\caption{Estimates and 95\% credible intervals for the regression coefficients for Experiment 1 and Experiment 2}
-% give details regarding encoding etc.
-\label{fig:exp2AvgResponse}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+
+{\centering \includegraphics[width=\maxwidth]{figure/exp2AvgResponse-1}
+
+}
+
+\caption[Estimates and 95\% credible intervals for the regression coefficients for Experiment 1 and Experiment 2]{Estimates and 95\% credible intervals for the regression coefficients for Experiment 1 and Experiment 2}\label{fig:exp2AvgResponse}
 \end{figure}
+
+\end{knitrout}
 
@@
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=\textwidth]{figures/exp2ResponseModelPlot-1.png}
-\caption{Estimates and 95\% credible intervals for the regression coefficients for Experiment 2}
-% give details regarding encoding etc.
-% similar to experiment1 model graph 
-\label{fig:exp2ResponseModel}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+
+{\centering \includegraphics[width=\maxwidth]{figure/exp2ResponseModel-1}
+
+}
+
+\caption[Estimates and 95\% credible intervals for the regression coefficients for Experiment 2]{Estimates and 95\% credible intervals for the regression coefficients for Experiment 2}\label{fig:exp2ResponseModel}
 \end{figure}
+
+\end{knitrout}
 

### 2019-12-23 old_draft_Paper/paper_draft.rmd
models are run,use lfs for big files

@@
         in_header: paper_draft_preamble.tex
-
 editor_options: 

### 2019-12-23 scripts/experiment1_prepare.R

@@ -7,7 +7,7 @@ library(ggplot2)
 
 fname_data <- "../Data/Experiment1/results/results"
 fname_data_out <- "../workspace_exp1/exp_data.rds"
-
+fname_form_out <- "../workspace_exp1/exp_form.rds"
 data <- read.csv(fname_data, 
                  header = F, 
                  comment.char = "#", 
@@ -85,5 +85,6 @@ conditions_info <- data.frame(experiment =    c("AgrAttr", "AgrAttr", "AgrAttr",
                               stringsAsFactors = FALSE)
 data %<>% left_join(conditions_info)
 data %<>% subset(Type != "practice") %>% drop.levels()
-
+saveRDS(FormPart, file = fname_form_out)
 saveRDS(data, file = fname_data_out)
+

### 2020-01-03 agremeent_draft_dec17/draft_dec17.Rnw
XXXs are done

--- 2019-12-23 agremeent_draft_dec17/draft_dec17.Rnw
@@
 Our findings contradict our hypothesized form-driven processing strategy and support an account of agreement attraction based on the use of abstract linguistic features, rather than mere form.}
+
 \input{settings.tex}
+
 \begin{document}
@@
 
-section{Introduction} \label{sec:Intro}
-\footnote{\printglossaries}. % add this to somewhere in the first page I suppose
+\section{Introduction} \label{sec:Intro}
+
+%\footnote{\printglossaries}. % add this to somewhere in the first page I suppose
+
 \subsection{Agreement Attraction Thingy} \label{sec:Intro:literature}
+
 \subsubsection{Morphophonology} \label{sec:Intro:literature:morphophonology}
+
 %fill here accordingly to your results AFTER YOU WRITE THE RESULT.
@@
 \subsubsection{This work details} \label{sec:Intro:literature:thiswork}
+
 % \citet{LagoEtAl:2018} hypothesize that genitive NPs can trigger agreement attraction in Turkish, because Turkish makes heavy use of genitive subjects, which means genitives are a priori likely to function as agreement controllers.
@@
 \section{Experiment 1} \label{sec:exp1}
+
 % do not do this in one chunk. differentiate the chunks and give them proper names.
@@
 fname_data <- "../workspace_exp1/exp_data.rds"
-data_exp1 <- readRDS(file = fname_data)
+data_exp1 <- readRDS(fname_data)
 fname_form <- "../workspace_exp1/exp_form.rds"
@@
 
-One hundred seven native speakers of Turkish (\textit{X} male, \textit{Y} female) in Experiment 1.
-The mean age is \Sexpr{mean(as.numeric(as.character(form_exp1$Age)))} , ranging from \Sexpr{min(as.numeric(as.character(form_exp1$Age)))} to \Sexpr{max(as.numeric(as.character(form_exp1$Age)))}.
+One hundred seven native speakers of Turkish in Experiment 1.
+The mean age is \Sexpr{mean(as.numeric(as.character(form_exp1$Age)))}, ranging from \Sexpr{min(as.numeric(as.character(form_exp1$Age)))} to \Sexpr{max(as.numeric(as.character(form_exp1$Age)))}.
+Across participants, a total \Sexpr{sum(is.na(df_exp1_na_nofillers$ResponseYes))} items were not responded to before the 5 second deadline by \Sexpr{length(unique(df_exp1_na_nofillers$subject))} different participants.
+These items were not included in the analysis.
 Experiments in this paper were carried out following the Declaration of Helsinki and the regulations concerning ethics in research in Bo\u{g}azi\c{c}i University.
 All participants provided informed consent.
-They were tested online, on IbexFarm, using their preferred platform,
+They were tested online, on IbexFarm, using their preferred platform.
 
@@
 As in \citet{LagoEtAl:2018} study, we used 40 sets of item and manipulated the grammaticality of the sentences (\textit{grammatical} x \textit{ungrammatical}) and the number of the attractor noun (\textit{singular} x \textit{plural}).
-All experimental sentences followed the following template: \textit{Noun$_{\Gen}$-Noun$_{\Poss}$-Adverb-Verb}.
+All experimental sentences followed the following template: \textit{Noun$_{{\textsc{gen}}}$-Noun$_{{\textsc{poss}}}$-Adverb-Verb}.
 The distribution of the verb types followed the same pattern as in \citet{LagoEtAl:2018}, namely twenty unergatives, eighteen unaccusatives, and two optionally transitive verbs.
@@
 \gll *Yönetici-ler-in aşcı-sı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
-manager-\Pl{}-\Gen{}  cook-\Poss{} kitchen-\Loc{} non-stop  jump-\Prog{}-\Pl{}.\\
+manager-\textsc{pl}-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
 \glt `The cooks of the manager were jumping in the kitchen non-stop.' 
@@
 \gll *Yönetici-nin aşcı-sı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
-manager-\Gen{}  cook-\Poss{} kitchen-\Loc{} non-stop  jump-\Prog{}-\Pl{}.\\
+manager-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
 \glt `The cook of the manager were jumping in the kitchen non-stop.'
@@
 \gll Yönetici-ler-in aşcı-sı mutfak-ta sürekli zıpl-ıyor.\\ 
-manager-\Pl{}-\Gen{}  cook-\Poss{} kitchen-\Loc{} non-stop  jump-\Prog{}.\\
+manager-\textsc{pl}-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
 \glt `The cooks of the manager was jumping in the kitchen non-stop.'
@@
 \gll Yönetici-nin aşcı-sı mutfak-ta sürekli zıpl-ıyor. \\ 
-manager-\Gen{}  cook-\Poss{} kitchen-\Loc{} non-stop  jump-\Prog{}.\\
+manager-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
 \glt `The cook of the manager was jumping in the kitchen non-stop.'
@@
 We wanted to rule out a possible task strategy where participants decide on the grammaticality of the sentence by merely checking the final plural marking.
-Even though filler items did not follow a strict template as the experimental items, they were created within a template of \textit{Noun$_{\Gen}$-Noun$_{\Poss}$-Converb-Noun-Adverb-Verb}.
+Even though filler items did not follow a strict template as the experimental items, they were created within a template of \textit{Noun$_{{\textsc{gen}}}$-Noun$_{{\textsc{gen}}}$-Converb-Noun-Adverb-Verb}.
 The ungrammaticality was created non-locally in the filler items to avoid task strategies.
@@
 \gll Sosyolog-un öğrenci-si konuş-unca tutarsızlık açığ-a çıkar-dı-lar.\\ 
-sociolog-\Gen{}  student-\Poss{} speak-\Nmlz{} inconsistency  open-\Dat{} deduct-\Pst{}-\Pl{}.\\
+sociolog-\textsc{gen}  student-\textsc{poss} speak-\textsc{nmlz} inconsistency  open-\Dat{} deduct-\textsc{pst}-\textsc{pl}.\\
 \glt `When the sociolog's student talked, they exposed an inconsistency.' 
@@
 \gll *Dansöz-ün koca-sı var-ınca kapı sakince aç-tı.\\ 
-dancer-\Gen{}  husband-\Poss{} arrive-\Nmlz{} door slowly  open-\Pst{}.\\
+dancer-\textsc{gen}  husband-\textsc{poss} arrive-\textsc{nmlz} door slowly  open-\textsc{pst}.\\
 \glt Intended:`When the husband of the dancer came, the door opened slowly.'
@@
 The sentences were presented in the middle of the screen word-by-word on a web-based platform Ibex Farm (\url{http://spellout.net/ibexfarm/}).
-Each word was displayed with XX font size and stayed on the screen for 300 ms, unlike \citet{LagoEtAl:2018} and \citet{WagersEtAl:2009} where words stayed for 500 ms in the screen.
+Each word was displayed with 30 font size and stayed on the screen for 300 ms, unlike \citet{LagoEtAl:2018} and \citet{WagersEtAl:2009} where words stayed for 500 ms in the screen.
 After the sentence is completed, participants were asked: "How did they find the sentence?" They were informed to press P on their keyboard for \textit{good} and Q for bad.
@@
 
-\autoref{fig:exp1AvgResponse} shows the average proportions of ‘acceptable’ responses by experimental condition for both the original experiment in \citet{LagoEtAl:2018} and our replication with unambiguous possessive marking.
-It shows that ungrammatical sentences with plural attractors are rated as acceptable more often than their counterparts with singular attractors.
-In addition to ungrammatical conditions, accuracy rates within the grammatical conditions were comparable and high across conditions (mean = x\%, SE = x\%).
-As seen in \autoref{fig:exp1AvgResponse}, participants judged the sentences with plural attractor and singular verbs to be grammatical with the rate of X\%, which is in line with the findings reported in \citet{LagoEtAl:2018}.
-
-<<exp1AvgResponse, fig.cap='Percentage of \\emph{yes} (acceptable) responses of Experiment 1 and \\citet{LagoEtAl:2018}', fig.height=3, fig.align='center'>>=
+<<>>=
 
@@
 avg_fillers <- avg_clean %>% lapply(function(df) { df %>% subset(source == "filler") })
-
+pd <- position_dodge(0.1)
 p_avg_resp <- avg_exp$resp %>%
@@
                          color = attractor_num, group = attractor_num)) + 
-                geom_point() + geom_line() + 
+                geom_point(position = pd) + geom_line(position = pd) + 
                 facet_wrap(~experiment)
 
-p_avg_resp <- p_avg_resp + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1)
+p_avg_resp <- p_avg_resp + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1, position = pd)
 
@@
 p_avg_resp <- p_avg_resp + scale_color_discrete(name = "Attractor Number")
-print(p_avg_resp)
-
-if (exists("le_poster")) {
-  p_avg_resp <- avg_exp$resp %>% subset(experiment == "Experiment 1") %>%
-                ggplot(aes(grammatical, M, #linetype = attractor_num, 
-                           color = attractor_num, group = attractor_num)) + 
-                  geom_point() + geom_line() + theme( strip.background = element_rect(fill="white")) +
-                  facet_wrap(~experiment)
-
-  p_avg_resp <- p_avg_resp + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1)
-
-  # p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) + 
-  #                             geom_point(data = avg_fillers) +
-
-  p_avg_resp <- p_avg_resp + theme( strip.background = element_rect(fill="white") ) +
-                             theme_bw() + xlab("") + ylab("Percentage 'acceptable'")
-  p_avg_resp <- p_avg_resp + scale_y_continuous(labels=scales::percent, limits = c(0,1))#, breaks = c(0, .25, .5, .75, 1))
-  p_avg_resp <- p_avg_resp + theme_bw()
-  p_avg_resp <- p_avg_resp + scale_color_discrete(name = "Attractor Number")
-  ggsave(filename = "./plots_le/exp1.jpeg", p_avg_resp, height = 2.5, width = 2.5*2)
-}
 
@@
 
-The estimates and 95\% CIs of a Bayesian GLM in \autoref{fig:exp1ResponseModel} confirm the observations we stated above: the positive interaction between sentence grammaticality and attractor number is in line with a larger effect of attractor number in ungrammatical sentences.
-The main effect of ungrammaticality was XX in log-odds, and the interaction between the ungrammaticality and plural attractor was XX in log-odds.
-Since other estimates' credible intervals range over zero, we conclude that they were not informative.
-%maybe speak with p values?
-% we did not do any nested analysis, should we? Should it say anything different than figure 2?
+\autoref{fig:exp1AvgResponse} shows the average proportions of ‘acceptable’ responses by experimental condition for both the original experiment in \citet{LagoEtAl:2018} and our replication with unambiguous possessive marking.
+It shows that ungrammatical sentences with plural attractors are rated as acceptable more often (M = \Sexpr{avg_exp$resp$M[3]}\%, SE = \Sexpr{avg_exp$resp$SE[3]}\%) than their counterparts with singular attractors (M=\Sexpr{avg_exp$resp$M[4]}\%, SE=\Sexpr{avg_exp$resp$SE[4]}\%).
+In addition to ungrammatical conditions, accuracy rates within the grammatical conditions were comparable and high across conditions (M = \Sexpr{avg_exp$resp$M[1]}\% and \Sexpr{avg_exp$resp$M[2]}\%, SE = \Sexpr{avg_exp$resp$SE[1]}\% and \Sexpr{avg_exp$resp$SE[2]}\% for singular and plural attractors respectively).
+As seen in \autoref{fig:exp1AvgResponse}, participants judged the sentences with plural attractor and singular verbs to be grammatical with the rate of \Sexpr{avg_exp$resp$M[3]-avg_exp$resp$M[4]}\%, which is in line with the findings reported in \citet{LagoEtAl:2018}.
 
-%Moreover, this findings are also predicted by cue-based retrieval models \citep{engelmann2019effect, vasishth2019computational} and last rendition of marking and morphing theory by \citet{HammerlyEtAl:2019}.
-%does it tho?
-especially with regards to what sol lago says: gen and morphophonology gives clues.
-maybe we should take a look at speeded acceptability?
-%maybe this is not the perfect place to write this.
+<<exp1AvgResponse, fig.cap='Percentage of \\emph{yes} (acceptable) responses of Experiment 1 and \\citet{LagoEtAl:2018}', fig.height=3, fig.align='center'>>=
+print(p_avg_resp)
 
-<<>>=
+@
+
+<<exp1models, include=FALSE>>=
 
@@
                                          (cUngrammatical * cAttractorPlural + 1| subject) +
-                                         (cUngrammatical * cAttractorPlural + 1| item),
+                                         (cUngrammatical * cAttractorPlural + 1| item),  #Can we omit this one out?
+We do not have every condition for every item from each subject?
+It goes to minus infinity.
                    data = df_merged_nofillers,
@@
 
-if (exists("le_poster"))
-{
-  fname_exp1_responses <- "../workspace_exp1/model_responses_justexp1"
-  m_responses_exp1 <- brm(ResponseYes ~ cUngrammatical * cAttractorPlural + 
-                                 (cUngrammatical * cAttractorPlural + 1| subject) +
-                                 (cUngrammatical * cAttractorPlural + 1| item),
-                   data = df_merged_nofillers %>% subset(experiment == "Experiment 1"),
-                   family = bernoulli("probit"),
-                   file = fname_exp1_responses, 
-                   chains = n_chains, cores = n_cores, iter = n_iter)
+model_results_table <- fixef(m_responses, summary = T, robust = F) %>% 
+  as.data.frame() %>% tibble::rownames_to_column("variables")
+@
 
-}
+The estimates and 95\% CIs of a Bayesian GLM in \autoref{fig:exp1ResponseModel} confirm the observations we stated above: the positive interaction between sentence grammaticality and attractor number is in line with a larger effect of attractor number in ungrammatical sentences.
+The main effect of ungrammaticality was \Sexpr{model_results_table[3,2]}[\Sexpr{model_results_table[3,4]};\Sexpr{model_results_table[3,4]}] in log-odds, and the interaction between the ungrammaticality and plural attractor was \Sexpr{model_results_table[7,2]}[\Sexpr{model_results_table[7,4]};\Sexpr{model_results_table[7,5]}] in log-odds.
+Since other estimates' credible intervals range over zero, we conclude that they were not informative.
+%maybe speak with p values?
+% we did not do any nested analysis, should we? Should it say anything different than figure 2?
 
-@
+%Moreover, this findings are also predicted by cue-based retrieval models \citep{engelmann2019effect, vasishth2019computational} and last rendition of marking and morphing theory by \citet{HammerlyEtAl:2019}.
+%does it tho?
+especially with regards to what sol lago says: gen and morphophonology gives clues.
+maybe we should take a look at speeded acceptability?
+%maybe this is not the perfect place to write this.
 
@@
 
-if (exists("le_poster"))
-{
-    p_m_response_exp1 <- 
-      create_model_coefs_plot( m_responses_exp1, 
-            plot_stats = T, map_names = contrast_names,
-            expand_right = 2.5, expand_top = 5, x_stat_adjust = 1.1,
-            x_breaks = c(-3,-2,-1, 0,1, 2) ) + 
-            xlab("Estimate (log-odds)")
-
-    p_m_response_exp1 <- p_m_response_exp1 + annotate(x=-3, xend=2, y=0, yend=0, lwd=0.25, geom="segment")
-
-    ggsave(filename = "./plots_le/m_exp1.jpeg", p_m_response_exp1, height = 1.5, width = 2.5*2)
-}
 @
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{example-grid-100x100pt} 
+                      \begin{forest}
+                  for tree = {
+                  % nodes
+                      draw, 
+                      align=center,
+                      minimum height=5ex,
+                      minimum width=3em,
+                      font=\linespread{0.84}\selectfont,
+                  % tree
+                      grow'=0,
+                      parent anchor=east,
+                      child  anchor=west,
+                      s sep = 4mm,    
+                      l sep = 12mm, 
+                  % edge
+                      edge = {semithick},
+                  % level styles
+                  if level = 0{}{rounded corners=2ex},
+                  where n children=0{tier=level, sharp corners}{calign=edge midpoint},
+                  % edge labels
+                  EL/.style={edge label={node [pos=0.5, fill=white,
+                                               font=\scriptsize\sffamily,
+                                               inner sep=2pt] {$#1$}}
+                                      }
+                              }% end for tree
+                  [,coordinate
+                  [target\\ item,no edge
+                      [recolection\\ certainity, EL=r
+                          ["yes"]
+                      ]
+                      [recolection\\ uncertainity, EL=1-r,
+                          [guess "yes", tier=L1, EL=g,
+                              ["yes"]
+                          ]
+                          [guess "no", tier=L1, EL=1-g
+                              ["no"]
+                          ]
+                      ]
+                  ]
+                  [,coordinate, no edge]
+                  [target\\ item, no edge
+                      [guess "yes", tier=L1, EL=g,
+                              ["yes"]
+                      ]
+                      [guess "no", tier=L1, EL=1-g
+                          ["no"]
+                      ]
+                   ]
+                  ]
+                      \end{forest} 
     \caption{Proposed multinomial processing tree of how people judge sentences in an agreement attraction task}
@@
 
-In Experiment 2, we wanted to rule out the possibility of \textit{form-driven processing strategy}, namely participants deciding on the acceptability of a sentence using a memory of plural morpheme in the sentence when they do not have sufficient information to rate sentences (un)acceptable.
-
-\subsection{Participants} \label{sec:exp2:participants}
-
-Eighty native speakers of Turkish (\textit{X} male, \textit{Y} female) in Experiment 1.
-The mean age is \textit{Z}, ranging from \textit{Z1} to \textit{Z2}.
-Experiments in this paper were carried out following the Declaration of Helsinki and the regulations concerning ethics in research in Bo\u{g}azi\c{c}i University.
-All participants provided informed consent.
-They were tested online, on IbexFarm, using their preferred platform, % Find citation for using IbexFarm and online testing etc?
-
-\subsection{Materials} \label{sec:exp2:materials}
-
-In Experiment 2, participants saw the sentences word by word in the middle of their screen.
-We have again formed 40 sets of items.
-The grammaticality of the sentences (\textit{grammatical} x \textit{ungrammatical}) and the number of the attractor (\textit{singular} x \textit{plural}) were manipulated.
-Unlike Experiment 1, we used nominalized relative clause attractors instead of nouns.
-We took advantage of syncretism between Turkish nominal and verbal plural marker.
-Both of these morphemes spells-out as \textit{-lAr}, which enables us to check whether agreement attraction in Turkish can be explained by an extremely shallow dependency parsing based on the forms of morphemes rather than linguistic features.
-
-All experimental sentences followed the same template as the experiment one except for the nature of the attractor: \textit{RC-Bare Noun-Adverb-Verb}. 
-We have used the same verbs, and have not changed the distribution of verb types.
-We also utilized the same or extremely similar adverbials in length.
-We again did not manipulate the number of the head noun and manipulated the number of the attractor.
-Relative clauses we used in this experiment are all object relative clauses and they are all marked with canonical \textit{-dIK} nominalizer.
-Since Turkish is a pro-drop language, we also dropped the subject within the embedded clause, thus ending up with a one-word object relative clause whose head is also the controller of the number agreement on the matrix verb.
-One example set of experimental items can be seen in \ref{item:exp2ExperimentalItems}.
-
-\ex. \label{item:exp2ExperimentalItems}
-\a. \textit{Plural Attractor, Ungrammatical Verb}\\ 
-\gll *Tut-tuk-lar-ı aşcı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
-hire-\Nmlz{}-\Pl{}-\Poss{}  cook kitchen-\Loc{} non-stop  jump-\Prog{}-\Pl{}.\\
-\glt `The cook that they hired were jumping in the kitchen non-stop.' 
-\b. \textit{Singular Attractor, Ungrammatical Verb}\\ 
-\gll *Tut-tuğ-u aşcı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
-hıre-\Nmlz{}-\Poss{}  cook kitchen-\Loc{} non-stop  jump-\Prog{}-\Pl{}.\\
-\glt `The cook that they hired were jumping in the kitchen non-stop.'
-\c. \textit{Plural Attractor, Grammatical Verb}\\ 
-\gll Tut-tuk-lar-ı aşcı mutfak-ta sürekli zıpl-ıyor.\\ 
-hire-\Nmlz{}-\Pl{}-\Poss{}  cook kitchen-\Loc{} non-stop  jump-\Prog{}.\\
-\glt `The cook that they hired was jumping in the kitchen non-stop.'
-\d. \textit{Singular Attractor, Grammatical Verb}\\ 
-\gll Tut-tuğ-u aşcı mutfak-ta sürekli zıpl-ıyor.\\ 
-hıre-\Nmlz{}-\Poss{}  cook kitchen-\Loc{} non-stop  jump-\Prog{}.\\
-\glt `The cook that they hired was jumping in the kitchen non-stop.'
-
-In our filler items for Experiment 2, we made sure that every sentence starts with an object relative clause.
-We used plural distractors with grammatical verbs and singular distractors with ungrammatical verbs.
-In all of our filler sentences, the dependency between the first NP subject and its verb resolved in an adverbial embedded sentence.
-Grammatical filler items in Experiment 2 all had a template of \textit{RC$_{\Pl{}}$-Bare Noun-Adverb-Converb-Noun-Adverb-Verb$_{\Pl{}}$}, whereas ungrammatical filler items used a template of \textit{RC$_{\Sg{}}$-Bare Noun-Adverb-Converb-Noun-Adverb-Verb$_{\Sg{}}$}
-
-Again, to avoid a possible strategy where participants use plural ending as a direct indication of ungrammaticality, half of our fillers were with an overt plural marking on a grammatical verb while the other half were without an overt plural marking on an ungrammatical verb.
-We used Turkish pro-drop characteristics which enable participants to form a dependency between the matrix verb and the null subject.
-Example filler sentences can be seen in \ref{item:exp2FillerItems}
-
-\ex. \label{item:exp2FillerItems}
-\a. \textit{Plural Grammatical Verb}\\ 
-\gll Oku-t-tuk-lar-ı öğrenci başarılı ol-unca mutlu ol-du-lar.\\ 
-read-\Caus{}-\Nmlz{}-\Pl{}-\Poss{}  student successful be-\Nmlz{} happy be-\Pst{}-\Pl{}.\\
-\glt `When the student they sponsored become successful, they became happy.' 
-\b. \textit{Singular Ungrammatical Verb}\\ 
-\gll *Kandır-dığ-ı adam öde-me-yince bulaşık saatlerce yıka-dı.\\ 
-trick-\Nmlz{}-\Poss{}  man pay-\Neg{}-\Nmlz{} dish for.hours clean-\Pst{}.\\
-\glt Intended:`When the man he tricked did not pay, he cleaned dishes for hours.'
-
-\subsection{Procedure and Analysis} \label{sec:exp2:procedure_analysis}
-
 <<loadExperiment2Data>>=
@@
 data_exp2 <- readRDS(file = fname_data2)
+fname_form <- "../workspace_exp2/exp_form.rds"
+form_exp2 <- readRDS(file = fname_form)
+form_exp2 <- form_exp2[-c(56),]
 
@@
 
+df_exp2_na_nofillers <- subset(df_merged2, is.na(ResponseYes) & source != "filler")
+
 df_merged2_nonna <- df_merged2 %>% subset(!is.na(ResponseYes))
+
 @
+
+In Experiment 2, we wanted to rule out the possibility of \textit{form-driven processing strategy}, namely participants deciding on the acceptability of a sentence using a memory of plural morpheme in the sentence when they do not have sufficient information to rate sentences (un)acceptable.
+
+\subsection{Participants} \label{sec:exp2:participants}
+
+Eighty native speakers of Turkish in Experiment 1.
+The mean age is \Sexpr{mean(as.numeric(as.character(form_exp2$Age)))}, ranging from \Sexpr{min(as.numeric(as.character(form_exp2$Age)))} to \Sexpr{max(as.numeric(as.character(form_exp2$Age)))}.
+Across participants, a total \Sexpr{sum(is.na(df_exp2_na_nofillers$ResponseYes))} items were not responded to before the 5 second deadline by \Sexpr{length(unique(df_exp2_na_nofillers$subject))} different participants.
+These items were not included in the analysis.
+Experiments in this paper were carried out following the Declaration of Helsinki and the regulations concerning ethics in research in Bo\u{g}azi\c{c}i University.
+All participants provided informed consent.
+They were tested online, on IbexFarm, using their preferred platform, % Find citation for using IbexFarm and online testing etc?
+
+\subsection{Materials} \label{sec:exp2:materials}
+
+In Experiment 2, participants saw the sentences word by word in the middle of their screen.
+We have again formed 40 sets of items.
+The grammaticality of the sentences (\textit{grammatical} x \textit{ungrammatical}) and the number of the attractor (\textit{singular} x \textit{plural}) were manipulated.
+Unlike Experiment 1, we used nominalized relative clause attractors instead of nouns.
+We took advantage of syncretism between Turkish nominal and verbal plural marker.
+Both of these morphemes spells-out as \textit{-lAr}, which enables us to check whether agreement attraction in Turkish can be explained by an extremely shallow dependency parsing based on the forms of morphemes rather than linguistic features.
+
+All experimental sentences followed the same template as the experiment one except for the nature of the attractor: \textit{RC-Bare Noun-Adverb-Verb}. 
+We have used the same verbs, and have not changed the distribution of verb types.
+We also utilized the same or extremely similar adverbials in length.
+We again did not manipulate the number of the head noun and manipulated the number of the attractor.
+Relative clauses we used in this experiment are all object relative clauses and they are all marked with canonical \textit{-dIK} nominalizer.
+Since Turkish is a pro-drop language, we also dropped the subject within the embedded clause, thus ending up with a one-word object relative clause whose head is also the controller of the number agreement on the matrix verb.
+One example set of experimental items can be seen in \ref{item:exp2ExperimentalItems}.
+
+\ex. \label{item:exp2ExperimentalItems}
+\a. \textit{Plural Attractor, Ungrammatical Verb}\\ 
+\gll *Tut-tuk-lar-ı aşcı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
+hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
+\glt `The cook that they hired were jumping in the kitchen non-stop.' 
+\b. \textit{Singular Attractor, Ungrammatical Verb}\\ 
+\gll *Tut-tuğ-u aşcı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
+hıre-\textsc{nmlz}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
+\glt `The cook that they hired were jumping in the kitchen non-stop.'
+\c. \textit{Plural Attractor, Grammatical Verb}\\ 
+\gll Tut-tuk-lar-ı aşcı mutfak-ta sürekli zıpl-ıyor.\\ 
+hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
+\glt `The cook that they hired was jumping in the kitchen non-stop.'
+\d. \textit{Singular Attractor, Grammatical Verb}\\ 
+\gll Tut-tuğ-u aşcı mutfak-ta sürekli zıpl-ıyor.\\ 
+hıre-\textsc{nmlz}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
+\glt `The cook that they hired was jumping in the kitchen non-stop.'
+
+In our filler items for Experiment 2, we made sure that every sentence starts with an object relative clause.
+We used plural distractors with grammatical verbs and singular distractors with ungrammatical verbs.
+In all of our filler sentences, the dependency between the first NP subject and its verb resolved in an adverbial embedded sentence.
+Grammatical filler items in Experiment 2 all had a template of \textit{RC$_{\textsc{pl}}$-Bare Noun-Adverb-Converb-Noun-Adverb-Verb$_{\textsc{pl}}$}, whereas ungrammatical filler items used a template of \textit{RC$_{\Sg{}}$-Bare Noun-Adverb-Converb-Noun-Adverb-Verb$_{\Sg{}}$}
+
+Again, to avoid a possible strategy where participants use plural ending as a direct indication of ungrammaticality, half of our fillers were with an overt plural marking on a grammatical verb while the other half were without an overt plural marking on an ungrammatical verb.
+We used Turkish pro-drop characteristics which enable participants to form a dependency between the matrix verb and the null subject.
+Example filler sentences can be seen in \ref{item:exp2FillerItems}
+
+\ex. \label{item:exp2FillerItems}
+\a. \textit{Plural Grammatical Verb}\\ 
+\gll Oku-t-tuk-lar-ı öğrenci başarılı ol-unca mutlu ol-du-lar.\\ 
+read-\Caus{}-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  student successful be-\textsc{nmlz} happy be-\textsc{pst}-\textsc{pl}.\\
+\glt `When the student they sponsored become successful, they became happy.' 
+\b. \textit{Singular Ungrammatical Verb}\\ 
+\gll *Kandır-dığ-ı adam öde-me-yince bulaşık saatlerce yıka-dı.\\ 
+trick-\textsc{nmlz}-\textsc{poss}  man pay-\Neg{}-\textsc{nmlz} dish for.hours clean-\textsc{pst}.\\
+\glt Intended:`When the man he tricked did not pay, he cleaned dishes for hours.'
+
+\subsection{Procedure and Analysis} \label{sec:exp2:procedure_analysis}
 
@@
 In the analysis of this experiment, we have included experimental items from our Experiments 1 and 2 to check the interaction between experiments and quantify the difference between verbal and nominal plural markers.
-In Experiment 2 as well, we excluded participants (\textit{n=X}) who had more than 0.25 points of difference in accuracy between grammatical conditions, which implicates that they did not give enough attention to all conditions.
+In Experiment 2 as well, we excluded participants (\Sexpr{length(bad_subjects2)}) who had more than 0.25 points of difference in accuracy between grammatical conditions, which implicates that they did not give enough attention to all conditions.
 We used R packages brms \citep{R-brms_b} and rstan \citep{R-stan} to fit Bayesian hierarchical models \citep{GelmanHill:2007}.
@@
 We see that there is no effect resembling agreement attraction in the ungrammatical conditions of Experiment 2.
-Ungrammatical conditions showed comparable effects (X, Y) regardless of the attractor's number.
+Ungrammatical conditions showed comparable effects (\Sexpr{avg_exp2$resp$M[7]} and \Sexpr{avg_exp2$resp$M[8]} for plural and singular attractors respeectively) regardless of the attractor's number.
 
@@
                                     color = attractor_num, group = attractor_num)) + 
-                geom_point() + geom_line() + 
+                geom_point(position = pd) + geom_line(position = pd) + 
                 facet_wrap(~experiment) +
@@
 
-p_avg_resp2 <- p_avg_resp2 + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1)
-p_avg_resp2 <- p_avg_resp2 + scale_y_continuous(labels=scales::percent)
+p_avg_resp2 <- p_avg_resp2 + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1, position = pd)
+p_avg_resp2 <- p_avg_resp2 + scale_y_continuous(labels=scales::percent, limits = c(0, 1))
 p_avg_resp2 <- p_avg_resp2 + scale_color_discrete(name = "Attractor Number")
@@
 print(p_avg_resp2)
-
-if (exists("le_poster")) {
-
-  p_avg_resp2 <- p_avg_resp2 + scale_y_continuous(labels=scales::percent, limits = c(0, 1))
-  ggsave(filename = "./plots_le/exp2.jpeg", p_avg_resp2, height = 2.5, width = 2.5*2)
-}
 
@@
 
-contrast_names2 <- c("cUngrammatical" = "Ungrammaticality",
-                    "cAttractorPlural" = "Plural Attactor",
-                    "cVerbalPlural" = "Verbal Attractor",
-                    "cUngrammatical:cAttractorPlural" = "Ungrammaticality * Plural Attractor",
-                    "cVerbalPlural:cUngrammatical" = "Ungrammaticality * Verbal Attractor",
-                    "cVerbalPlural:cAttractorPlural" = "Verbal Attractor * Plural Attractor",
-                    "cVerbalPlural:cUngrammatical:cAttractorPlural" = "Verbal Attractor * Ungrammaticality * Plural Attractor")
-
-p_m_response2 <- create_model_coefs_plot(m_responses2, map_names = contrast_names2)
-p_m_response2 <- p_m_response2 + xlab("Estimate (log-odds)")
-print(p_m_response2 + annotate(x=-2, xend=2, y=0, yend=0, lwd=0.25, geom="segment"))
-
-if (exists("le_poster"))
-{
 contrast_names2_le <- c("cUngrammatical" = "Ungrammaticality",
@@
     p_m_response_exp2 <- p_m_response_exp2 + annotate(x=-3, xend=1, y=0, yend=0, lwd=0.25, geom="segment")
-
-    ggsave(filename = "./plots_le/m_exp2.jpeg", p_m_response_exp2, height = 2.5, width = 2.5*2)
-}
+print(p_m_response_exp2)
 

### 2020-01-03 agremeent_draft_dec17/draft_dec17.tex
XXXs are done

@@
 Our findings contradict our hypothesized form-driven processing strategy and support an account of agreement attraction based on the use of abstract linguistic features, rather than mere form.}
+
 \input{settings.tex}
@@
 
-\printglossary[title=\MakeUppercase{glosses}, style=block,nonumberlist]
+\section{Introduction} \label{sec:Intro}
 
-section{Introduction} \label{sec:Intro}
 %\footnote{\printglossaries}. % add this to somewhere in the first page I suppose
+
 \subsection{Agreement Attraction Thingy} \label{sec:Intro:literature}
+
 \subsubsection{Morphophonology} \label{sec:Intro:literature:morphophonology}
+
 %fill here accordingly to your results AFTER YOU WRITE THE RESULT.
@@
 
-One hundred seven native speakers of Turkish (\textit{X} male, \textit{Y} female) in Experiment 1.
-The mean age is 20.14 , ranging from 18 to 32.
-Across participants, a total \sExpr{sum(is.na(df_exp1_na_nofillers$ResponseYes))} trials were not responded to before the 5 second deadline by 33 participants.
+One hundred seven native speakers of Turkish in Experiment 1.
+The mean age is 20.14, ranging from 18 to 32.
+Across participants, a total 42 items were not responded to before the 5 second deadline by 33 different participants.
+These items were not included in the analysis.
 Experiments in this paper were carried out following the Declaration of Helsinki and the regulations concerning ethics in research in Bo\u{g}azi\c{c}i University.
 All participants provided informed consent.
-They were tested online, on IbexFarm, using their preferred platform,
+They were tested online, on IbexFarm, using their preferred platform.
 
@@
 \autoref{fig:exp1AvgResponse} shows the average proportions of ‘acceptable’ responses by experimental condition for both the original experiment in \citet{LagoEtAl:2018} and our replication with unambiguous possessive marking.
-It shows that ungrammatical sentences with plural attractors are rated as acceptable more often than their counterparts with singular attractors.
-In addition to ungrammatical conditions, accuracy rates within the grammatical conditions were comparable and high across conditions (mean = x\%, SE = x\%).
-As seen in \autoref{fig:exp1AvgResponse}, participants judged the sentences with plural attractor and singular verbs to be grammatical with the rate of X\%, which is in line with the findings reported in \citet{LagoEtAl:2018}.
+It shows that ungrammatical sentences with plural attractors are rated as acceptable more often (M = 0.22\%, SE = 0.01\%) than their counterparts with singular attractors (M=0.11\%, SE=0.01\%).
+In addition to ungrammatical conditions, accuracy rates within the grammatical conditions were comparable and high across conditions (M = 0.92\% and 0.93\%, SE = 0.01\% and 0.01\% for singular and plural attractors respectively).
+As seen in \autoref{fig:exp1AvgResponse}, participants judged the sentences with plural attractor and singular verbs to be grammatical with the rate of 0.1\%, which is in line with the findings reported in \citet{LagoEtAl:2018}.
 
@@
 The estimates and 95\% CIs of a Bayesian GLM in \autoref{fig:exp1ResponseModel} confirm the observations we stated above: the positive interaction between sentence grammaticality and attractor number is in line with a larger effect of attractor number in ungrammatical sentences.
-The main effect of ungrammaticality was XX in log-odds, and the interaction between the ungrammaticality and plural attractor was XX in log-odds.
+The main effect of ungrammaticality was -3.09[-3.34;-3.34] in log-odds, and the interaction between the ungrammaticality and plural attractor was 0.72[0.43;1.02] in log-odds.
 Since other estimates' credible intervals range over zero, we conclude that they were not informative.
@@
 
-Eighty native speakers of Turkish (\textit{X} male, \textit{Y} female) in Experiment 1.
-The mean age is \textit{Z}, ranging from \textit{Z1} to \textit{Z2}.
+Eighty native speakers of Turkish in Experiment 1.
+The mean age is 21.51, ranging from 18 to 31.
+Across participants, a total 55 items were not responded to before the 5 second deadline by 41 different participants.
+These items were not included in the analysis.
 Experiments in this paper were carried out following the Declaration of Helsinki and the regulations concerning ethics in research in Bo\u{g}azi\c{c}i University.
@@
 \gll *Tut-tuk-lar-ı aşcı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
-hire-\Nmlz{}-\Pl{}-\Poss{}  cook kitchen-\Loc{} non-stop  jump-\Prog{}-\Pl{}.\\
+hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
 \glt `The cook that they hired were jumping in the kitchen non-stop.' 
@@
 \gll *Tut-tuğ-u aşcı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
-hıre-\Nmlz{}-\Poss{}  cook kitchen-\Loc{} non-stop  jump-\Prog{}-\Pl{}.\\
+hıre-\textsc{nmlz}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
 \glt `The cook that they hired were jumping in the kitchen non-stop.'
@@
 \gll Tut-tuk-lar-ı aşcı mutfak-ta sürekli zıpl-ıyor.\\ 
-hire-\Nmlz{}-\Pl{}-\Poss{}  cook kitchen-\Loc{} non-stop  jump-\Prog{}.\\
+hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
 \glt `The cook that they hired was jumping in the kitchen non-stop.'
@@
 \gll Tut-tuğ-u aşcı mutfak-ta sürekli zıpl-ıyor.\\ 
-hıre-\Nmlz{}-\Poss{}  cook kitchen-\Loc{} non-stop  jump-\Prog{}.\\
+hıre-\textsc{nmlz}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
 \glt `The cook that they hired was jumping in the kitchen non-stop.'
@@
 In all of our filler sentences, the dependency between the first NP subject and its verb resolved in an adverbial embedded sentence.
-Grammatical filler items in Experiment 2 all had a template of \textit{RC$_{\Pl{}}$-Bare Noun-Adverb-Converb-Noun-Adverb-Verb$_{\Pl{}}$}, whereas ungrammatical filler items used a template of \textit{RC$_{\Sg{}}$-Bare Noun-Adverb-Converb-Noun-Adverb-Verb$_{\Sg{}}$}
+Grammatical filler items in Experiment 2 all had a template of \textit{RC$_{\textsc{pl}}$-Bare Noun-Adverb-Converb-Noun-Adverb-Verb$_{\textsc{pl}}$}, whereas ungrammatical filler items used a template of \textit{RC$_{\Sg{}}$-Bare Noun-Adverb-Converb-Noun-Adverb-Verb$_{\Sg{}}$}
 
@@
 \gll Oku-t-tuk-lar-ı öğrenci başarılı ol-unca mutlu ol-du-lar.\\ 
-read-\Caus{}-\Nmlz{}-\Pl{}-\Poss{}  student successful be-\Nmlz{} happy be-\Pst{}-\Pl{}.\\
+read-\Caus{}-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  student successful be-\textsc{nmlz} happy be-\textsc{pst}-\textsc{pl}.\\
 \glt `When the student they sponsored become successful, they became happy.' 
@@
 \gll *Kandır-dığ-ı adam öde-me-yince bulaşık saatlerce yıka-dı.\\ 
-trick-\Nmlz{}-\Poss{}  man pay-\Neg{}-\Nmlz{} dish for.hours clean-\Pst{}.\\
+trick-\textsc{nmlz}-\textsc{poss}  man pay-\Neg{}-\textsc{nmlz} dish for.hours clean-\textsc{pst}.\\
 \glt Intended:`When the man he tricked did not pay, he cleaned dishes for hours.'
@@
 In the analysis of this experiment, we have included experimental items from our Experiments 1 and 2 to check the interaction between experiments and quantify the difference between verbal and nominal plural markers.
-In Experiment 2 as well, we excluded participants (\textit{n=X}) who had more than 0.25 points of difference in accuracy between grammatical conditions, which implicates that they did not give enough attention to all conditions.
+In Experiment 2 as well, we excluded participants (1) who had more than 0.25 points of difference in accuracy between grammatical conditions, which implicates that they did not give enough attention to all conditions.
 We used R packages brms \citep{R-brms_b} and rstan \citep{R-stan} to fit Bayesian hierarchical models \citep{GelmanHill:2007}.
@@
 We see that there is no effect resembling agreement attraction in the ungrammatical conditions of Experiment 2.
-Ungrammatical conditions showed comparable effects (X, Y) regardless of the attractor's number.
+Ungrammatical conditions showed comparable effects (0.07 and 0.07 for plural and singular attractors respeectively) regardless of the attractor's number.
 

### 2020-01-03 agremeent_draft_dec17/le_poster.R

@@ -1,0 +1,56 @@
+
+
+if (exists("le_poster")) {
+  p_avg_resp <- avg_exp$resp %>% subset(experiment == "Experiment 1") %>%
+    ggplot(aes(grammatical, M, #linetype = attractor_num, 
+               color = attractor_num, group = attractor_num)) + 
+    geom_point() + geom_line() + theme( strip.background = element_rect(fill="white")) +
+    facet_wrap(~experiment)
+  
+  p_avg_resp <- p_avg_resp + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1)
+  
+  # p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) + 
+  #                             geom_point(data = avg_fillers) + 
+  
+  p_avg_resp <- p_avg_resp + theme( strip.background = element_rect(fill="white") ) +
+    theme_bw() + xlab("") + ylab("Percentage 'acceptable'")
+  p_avg_resp <- p_avg_resp + scale_y_continuous(labels=scales::percent, limits = c(0,1))#, breaks = c(0, .25, .5, .75, 1))
+  p_avg_resp <- p_avg_resp + theme_bw()
+  p_avg_resp <- p_avg_resp + scale_color_discrete(name = "Attractor Number")
+  ggsave(filename = "./plots_le/exp1.jpeg", p_avg_resp, height = 2.5, width = 2.5*2)
+}
+
+
+if (exists("le_poster"))
+{
+  fname_exp1_responses <- "../workspace_exp1/model_responses_justexp1"
+  m_responses_exp1 <- brm(ResponseYes ~ cUngrammatical * cAttractorPlural + 
+                            (cUngrammatical * cAttractorPlural + 1| subject) +
+                            (cUngrammatical * cAttractorPlural + 1| item),
+                          data = df_merged_nofillers %>% subset(experiment == "Experiment 1"),
+                          family = bernoulli("probit"),
+                          file = fname_exp1_responses, 
+                          chains = n_chains, cores = n_cores, iter = n_iter)
+  
+}
+if (exists("le_poster"))
+{
+  p_m_response_exp1 <- 
+    create_model_coefs_plot( m_responses_exp1, 
+                             plot_stats = T, map_names = contrast_names,
[…]

### 2020-01-03 scripts/experiment2_prepare.R

@@ -7,6 +7,8 @@ library(ggplot2)
 
 fname_data <- "../Data/Experiment2/results/results"
 fname_data_out <- "../workspace_exp2/exp_data.rds"
+fname_form_out <- "../workspace_exp2/exp_form.rds"
+
 
 data <- read.csv(fname_data, 
                  header = F, 
@@ -78,3 +80,5 @@ data %<>% left_join(conditions_info)
 data %<>% subset(Type != "practice") %>% drop.levels()
 
 saveRDS(data, file = fname_data_out)
+saveRDS(FormPart, file = fname_form_out)
+

### 2020-01-08 agremeent_draft_dec17/draft_dec17.Rnw
Minor fixes.

@@
 \usepackage[singlespacing]{setspace}
+
 <<>>=
@@
 
-%\footnote{\printglossaries}. % add this to somewhere in the first page I suppose
-
-\subsection{Agreement Attraction Thingy} \label{sec:Intro:literature}
-
-\subsubsection{Morphophonology} \label{sec:Intro:literature:morphophonology}
-
-%fill here accordingly to your results AFTER YOU WRITE THE RESULT.
-
-\subsubsection{related sub-sub-field studies} \label{sec:Intro:literature:others}
-
-\subsubsection{This work details} \label{sec:Intro:literature:thiswork}
+% %\footnote{\printglossaries}. % add this to somewhere in the first page I suppose
+% 
+% \subsection{Agreement Attraction Thingy} \label{sec:Intro:literature}
+% 
+% \subsubsection{Morphophonology} \label{sec:Intro:literature:morphophonology}
+% 
+% %fill here accordingly to your results AFTER YOU WRITE THE RESULT.
+% 
+% 
+% \subsubsection{related sub-sub-field studies} \label{sec:Intro:literature:others}
+% 
+% \subsubsection{This work details} \label{sec:Intro:literature:thiswork}
 
@@
 form_exp1 <- readRDS(file = fname_form)
-form_exp1[106,2] = 18 # manually changed on sekiz to 18
 
@@
             mutate(delta_dc = online_d - online_c)
-word_freq <- readxl::read_excel("../Data/freq.xlsx", sheet = 1)
+word_freq <- readxl::read_excel("../Data/frequencies_exp1_and_lago.xlsx", sheet = 1)
 word_freq$freq_percentage %<>% as.numeric()
@@
 
+% to-do: Why are all sentences in aorist instead of past (as they are in the actual items)?
 % there may be a better way of displaying items.
 \ex. \label{item:exp1ExperimentalItems}
-\a. \textit{Plural Attractor, Ungrammatical Verb} \label{item:exp1expitem-plpl}\\ 
-\gll *Yönetici-ler-in aşcı-sı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
+%
+\a. \textsc{Plural Attractor, Plural Verb} \label{item:exp1expitem-plpl}\\ 
+  \gll *[Yönetici-ler-in \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpl-ıyor-lar}.\\ 
   manager-\textsc{pl}-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
-\glt `The cooks of the manager were jumping in the kitchen non-stop.' 
-\b. \textit{Singular Attractor, Ungrammatical Verb} \label{item:exp1expitem-sgpl}\\ 
-\gll *Yönetici-nin aşcı-sı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
+  \glt \textit{`The cooks of the manager were jumping in the kitchen non-stop.'}
+%
+\b. \textsc{Plural Attractor, Singular Verb} \label{item:exp1expitem-plsg}\\ 
+  \gll [Yönetici-ler-in \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpl-ıyor}.\\ 
+  manager-\textsc{pl}-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
+  \glt \textit{`The cooks of the manager was jumping in the kitchen non-stop.'}
+%
+\c. \textsc{Singular Attractor, Plural Verb} \label{item:exp1expitem-sgpl}\\ 
+  \gll *[Yönetici-nin \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpl-ıyor-lar}.\\ 
   manager-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
-\glt `The cook of the manager were jumping in the kitchen non-stop.'
-\c. \textit{Plural Attractor, Grammatical Verb} \label{item:exp1expitem-plsg}\\ 
-\gll Yönetici-ler-in aşcı-sı mutfak-ta sürekli zıpl-ıyor.\\ 
-manager-\textsc{pl}-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
-\glt `The cooks of the manager was jumping in the kitchen non-stop.'
-\d. \textit{Singular Attractor, Grammatical Verb}\label{item:exp1expitem-sgsg}\\ 
-\gll Yönetici-nin aşcı-sı mutfak-ta sürekli zıpl-ıyor. \\ 
+  \glt \textit{`The cook of the manager were jumping in the kitchen non-stop.'}
+%
+\d. \textsc{Singular Attractor, Singular Verb}\label{item:exp1expitem-sgsg}\\ 
+  \gll [Yönetici-nin \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpl-ıyor}. \\ 
   manager-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
-\glt `The cook of the manager was jumping in the kitchen non-stop.'
+  \glt \textit{`The cook of the manager was jumping in the kitchen non-stop.'}
 
@@
 \ex. \label{item:exp1FillerItems}
-\a. \textit{Plural Grammatical Verb}\\ 
-\gll Sosyolog-un öğrenci-si konuş-unca tutarsızlık açığ-a çıkar-dı-lar.\\ 
+%
+\a. \textsc{Grammatical, Plural Verb}\\ 
+\gll [Sosyolog-un \textbf{öğrenci-si}] konuş-unca tutarsızlık açığ-a \textbf{çıkar-dı-lar}.\\ 
 sociolog-\textsc{gen}  student-\textsc{poss} speak-\textsc{nmlz} inconsistency  open-\Dat{} deduct-\textsc{pst}-\textsc{pl}.\\
-\glt `When the sociolog's student talked, they exposed an inconsistency.' 
-\b. \textit{Singular Ungrammatical Verb}\\ 
-\gll *Dansöz-ün koca-sı var-ınca kapı sakince aç-tı.\\ 
+\glt \textit{`When the sociolog's student talked, they exposed an inconsistency.'}
+%
+\b. \textsc{Ungrammatical, Singular Verb}\\ 
+\gll *[Dansöz-ün \textbf{koca-sı}] var-ınca kapı sakince \textbf{aç-tı}.\\ 
 dancer-\textsc{gen}  husband-\textsc{poss} arrive-\textsc{nmlz} door slowly  open-\textsc{pst}.\\
-\glt Intended:`When the husband of the dancer came, the door opened slowly.'
+\glt \textit{Intended:`When the husband of the dancer came, the door opened slowly.'}
+% to-do: Does the above mean that it's grammatical with another meaning?
 
@@
 
-Prior to the experiments, participants gave information regarding themselves and consent to participate in the experiment.
+Prior to the start of the experiment, participants provided demographic information, as well as informed consent to participate in the experiment.
 They read the instructions where we showed what they will see in the experiment, and where we informed them to give quick and accurate answers during the experiment.
@@
 
-fname_exp1_responses <- "../workspace_exp1/model_responses"
+fname_exp1_responses <- "../workspace_exp1/fit_responses"
 m_responses <- brm(ResponseYes ~ cEndsInConsonant * cUngrammatical * cAttractorPlural + 
@@
                    family = bernoulli("probit"), 
-                   file = fname_exp1_responses, 
-                   chains = n_chains, cores = n_cores, iter = n_iter)
+                   chains = n_chains, cores = n_cores, iter = n_iter,
+                   file = fname_exp1_responses)
 
-fname_exp1_responses_minimal <- "../workspace_exp1/model_responses_minimal"
-m_responses_minimal <- brm(ResponseYes ~ (cEndsInConsonant + cUngrammatical + cAttractorPlural)^2 + 
-                                         (cUngrammatical * cAttractorPlural + 1| subject) +
-                                         (cUngrammatical * cAttractorPlural + 1| item),  #Can we omit this one out?
-We do not have every condition for every item from each subject?
-It goes to minus infinity.
-                   data = df_merged_nofillers,
-                   family = bernoulli("probit"),
-                   file = fname_exp1_responses_minimal, 
-                   chains = n_chains, cores = n_cores, iter = n_iter)
+# fname_exp1_responses_minimal <- "../workspace_exp1/model_responses_minimal"
+# m_responses_minimal <- brm(ResponseYes ~ (cEndsInConsonant + cUngrammatical + cAttractorPlural)^2 + 
+#                                          (cUngrammatical * cAttractorPlural + 1| subject) +
+#                                          (cUngrammatical * cAttractorPlural + 1| item),  
+#! *Utku* Can we omit this one out? We do not have every condition for every item from each subject? It goes to minus infinity.
+#! *PL* Are you talking about the starting values?
+#                    data = df_merged_nofillers,
+#                    family = bernoulli("probit"),
+#                    file = fname_exp1_responses_minimal, 
+#                    chains = n_chains, cores = n_cores, iter = n_iter)
 
-fname_exp1_rts <- "../workspace_exp1/model_responses_rt"
+fname_exp1_rts <- "../workspace_exp1/fit_responses_rt"
 m_rts <- brm(RT ~ cEndsInConsonant * cUngrammatical * cAttractorPlural +
@@
                    family = lognormal(),
-                   file = fname_exp1_rts,
-                   chains = n_chains, cores = n_cores, iter = n_iter)
+                   chains = n_chains, cores = n_cores, iter = n_iter,
+                   file = fname_exp1_rts)
 
@@
 form_exp2 <- readRDS(file = fname_form)
-form_exp2 <- form_exp2[-c(56),]
+
+#! No idea what this is about. Excluding for now.
+# form_exp2 <- form_exp2[-c(56),]
 
@@
 \ex. \label{item:exp2ExperimentalItems}
-\a. \textit{Plural Attractor, Ungrammatical Verb}\\ 
+%
+\a. \textit{Plural Attractor, Plural Verb}\label{item:exp2expitem-plpl}\\ 
   \gll *Tut-tuk-lar-ı aşcı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
   hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
-\glt `The cook that they hired were jumping in the kitchen non-stop.' 
-\b. \textit{Singular Attractor, Ungrammatical Verb}\\ 
+  \glt \textit{`The cook that they hired were jumping in the kitchen non-stop.'}
+%
+\b. \textit{Plural Attractor, Singular Verb}\label{item:exp2expitem-plsg}\\ 
+  \gll Tut-tuk-lar-ı aşcı mutfak-ta sürekli zıpl-ıyor.\\ 
+  hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
+  \glt \textit{`The cook that they hired was jumping in the kitchen non-stop.'}
+%
+\c. \textit{Singular Attractor, Plural Verb}\label{item:exp2expitem-sgpl}\\
   \gll *Tut-tuğ-u aşcı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
   hıre-\textsc{nmlz}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
-\glt `The cook that they hired were jumping in the kitchen non-stop.'
-\c. \textit{Plural Attractor, Grammatical Verb}\\ 
-\gll Tut-tuk-lar-ı aşcı mutfak-ta sürekli zıpl-ıyor.\\ 
-hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
-\glt `The cook that they hired was jumping in the kitchen non-stop.'
-\d. \textit{Singular Attractor, Grammatical Verb}\\ 
+  \glt \textit{`The cook that they hired were jumping in the kitchen non-stop.'}
+%
+\d. \textit{Singular Attractor, Singular Verb}\label{item:exp2expitem-sgsg}\\ 
   \gll Tut-tuğ-u aşcı mutfak-ta sürekli zıpl-ıyor.\\ 
   hıre-\textsc{nmlz}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
-\glt `The cook that they hired was jumping in the kitchen non-stop.'
+  \glt \textit{`The cook that they hired was jumping in the kitchen non-stop.'}
 
@@
 
-# to-do: Rename 'cVerbalPlural' to 'cVerbalAttractor'
 df_merged2 %<>% within(., {
@@
   cAttractorPlural <- ifelse(attractor_num == "plural", .5, -.5)
-  cVerbalPlural <- ifelse(experiment == "Experiment 2", .5, -.5)
+  cVerbalAttractor <- ifelse(experiment == "Experiment 2", .5, -.5)
 })
@@
 
-fname_exp2_responses <- "../workspace_exp2/model_responses"
+fname_exp2_responses <- "../workspace_exp2/fit_responses"
 
@@
 
-m_responses2 <- brm(ResponseYes ~ cVerbalPlural * cUngrammatical * cAttractorPlural + 
+# TODO: Data seems to contain NAs in relevant columns; fix it
+m_responses2 <- brm(ResponseYes ~ cVerbalAttractor * cUngrammatical * cAttractorPlural + 
                                  (cUngrammatical * cAttractorPlural + 1| subject) +
@@
                     "cAttractorPlural" = "Plural Attactor",
-                    "cVerbalPlural" = "Verbal Attractor",
+                    "cVerbalAttractor" = "Verbal Attractor",
                     "cUngrammatical:cAttractorPlural" = "Ungrammaticality * Plural Attractor",
-                    "cVerbalPlural:cUngrammatical" = "Ungrammaticality * Verbal Attractor",
-                    "cVerbalPlural:cAttractorPlural" = "Verbal Attractor * Plural Attractor",
-                    "cVerbalPlural:cUngrammatical:cAttractorPlural" = "Verbal Attractor * Ungrammaticality * Plural Attractor")
+                    "cVerbalAttractor:cUngrammatical" = "Ungrammaticality * Verbal Attractor",
+                    "cVerbalAttractor:cAttractorPlural" = "Verbal Attractor * Plural Attractor",
+                    "cVerbalAttractor:cUngrammatical:cAttractorPlural" = "Verbal Attractor * Ungrammaticality * Plural Attractor")
 

### 2020-01-08 agremeent_draft_dec17/draft_dec17.tex
Minor fixes.

@@
 \ex. \label{item:exp1FillerItems}
-\a. \textit{Plural Grammatical Verb}\\ 
-\gll Sosyolog-un öğrenci-si konuş-unca tutarsızlık açığ-a çıkar-dı-lar.\\ 
+%
+\a. \textit{Grammatical, Plural Verb}\\ 
+\gll [Sosyolog-un öğrenci-si] konuş-unca tutarsızlık açığ-a çıkar-dı-lar.\\ 
 sociolog-\textsc{gen}  student-\textsc{poss} speak-\textsc{nmlz} inconsistency  open-\Dat{} deduct-\textsc{pst}-\textsc{pl}.\\
-\glt `When the sociolog's student talked, they exposed an inconsistency.' 
-\b. \textit{Singular Ungrammatical Verb}\\ 
-\gll *Dansöz-ün koca-sı var-ınca kapı sakince aç-tı.\\ 
+\glt \textit{`When the sociolog's student talked, they exposed an inconsistency.'}
+%
+\b. \textit{Ungrammatical, Singular Verb}\\ 
+\gll *[Dansöz-ün koca-sı] var-ınca kapı sakince aç-tı.\\ 
 dancer-\textsc{gen}  husband-\textsc{poss} arrive-\textsc{nmlz} door slowly  open-\textsc{pst}.\\
-\glt Intended:`When the husband of the dancer came, the door opened slowly.'
+\glt \textit{Intended:`When the husband of the dancer came, the door opened slowly.'}
 
@@
 The estimates and 95\% CIs of a Bayesian GLM in \autoref{fig:exp1ResponseModel} confirm the observations we stated above: the positive interaction between sentence grammaticality and attractor number is in line with a larger effect of attractor number in ungrammatical sentences.
-The main effect of ungrammaticality was -3.09[-3.34;-3.34] in log-odds, and the interaction between the ungrammaticality and plural attractor was 0.72[0.43;1.02] in log-odds.
+The main effect of ungrammaticality was -3.09[-3.35;-3.35] in log-odds, and the interaction between the ungrammaticality and plural attractor was 0.72[0.42;1.02] in log-odds.
 Since other estimates' credible intervals range over zero, we conclude that they were not informative.
@@
 Eighty native speakers of Turkish in Experiment 1.
-The mean age is 21.51, ranging from 18 to 31.
+The mean age is 21.22, ranging from 0 to 31.
 Across participants, a total 55 items were not responded to before the 5 second deadline by 41 different participants.

### 2020-01-08 scripts/experiment1_prepare.R

@@ -40,6 +40,7 @@ lenForm <- length(levels(factor(FormPart$Timestamp)))
 timestampForm <- levels(factor(FormPart$Timestamp))
 timeform_subject <- data.frame("Timestamp" = timestampForm, "subject" = sprintf("S[%s]",seq(lenForm)))
 FormPart <- merge(FormPart,timeform_subject, all = T)
+FormPart$Age %<>% as.character() %>% gsub("on sekiz", "18", .) %>% as.integer()
 
 data$Timestamp %<>% as.character()
 timeform_subject$Timestamp %<>% as.character()

### 2020-01-15 agremeent_draft_dec17/draft_dec17.Rnw
Fixed method and results for experiment 1

@@
 <<>>=
+
 fname_data <- "../workspace_exp1/exp_data.rds"
@@
 
-In Experiment 1, we tested whether speakers of Turkish make fewer errors when the local ambiguity in the head noun is resolved.
-Specifically, we have replicated the \citet{LagoEtAl:2018} study.
-However, instead of using their NP heads, we chose to use nouns that end in a vowel, thus resolving the ambiguity between the accusative and possessive.
+In Experiment 1, we tested whether speakers of Turkish make fewer agreement attraction errors when the local ambiguity in the head noun is resolved. 
+Specifically, we tried to replicate \citet{LagoEtAl:2018} study.
+However, instead of using morphologically ambiguous head nouns, we uses nouns ending in a vowel, thus resolving the ambiguity between the accusative and possessive.
 
@@
 
-One hundred seven native speakers of Turkish in Experiment 1.
-The mean age is \Sexpr{mean(as.numeric(as.character(form_exp1$Age)))}, ranging from \Sexpr{min(as.numeric(as.character(form_exp1$Age)))} to \Sexpr{max(as.numeric(as.character(form_exp1$Age)))}.
-Across participants, a total \Sexpr{sum(is.na(df_exp1_na_nofillers$ResponseYes))} items were not responded to before the 5 second deadline by \Sexpr{length(unique(df_exp1_na_nofillers$subject))} different participants.
+We recruited 118 undergraduate students to participate in Experiment 1 in exchange for course credit.
+All participants were native speakers of Turkish, with an average age of \Sexpr{round(mean(form_exp1$Age))} (range: \Sexpr{min(form_exp1$Age)} -- \Sexpr{max(form_exp1$Age)}).
 These items were not included in the analysis.
-Experiments in this paper were carried out following the Declaration of Helsinki and the regulations concerning ethics in research in Bo\u{g}azi\c{c}i University.
+Experiments in this paper were carried out following the Declaration of Helsinki and the regulations concerning ethics at research in Bo\u{g}azi\c{c}i University.
 All participants provided informed consent.
-They were tested online, on IbexFarm, using their preferred platform.
+They were tested online, on IbexFarm.
+%to-do: cite ibexfarm
 
@@
 
-In Experiment 1, participants first saw sentences word by word in the middle of their screen.
-As in \citet{LagoEtAl:2018} study, we used 40 sets of item and manipulated the grammaticality of the sentences (\textit{grammatical} x \textit{ungrammatical}) and the number of the attractor noun (\textit{singular} x \textit{plural}).
-All experimental sentences followed the following template: \textit{Noun$_{{\textsc{gen}}}$-Noun$_{{\textsc{poss}}}$-Adverb-Verb}.
+We used 40 sets of sentences like (\ref{item:exp1ExperimentalItems}), in which we manipulated 
+(i) the number of the attractor noun, and
+(ii) the number agreement on the verb. 
+Plural number and plural agreement were both marked with the affix \textit{-ler/-lar}, while singular number and singular agreement were marked with its absence. 
+%
+All sentences started with a complex subject NP like \textit{`the manager's cook'} (\textit{yöneticinin aşcısı}), in which the possessor, which functioned as the attractor, carried genitive case, and the head noun cassied possessive case.
+Because the head noun was singular in all conditions, sentences with plural verb agreement were ungrammatical.
+% to-do: Didn't we use Lago's items as a base?? If so, we need to say this here, and also how much we've changed, and how much remained.
+Unlike the \citet{LagoEtAl:2018} sentences, our head nouns were vowel-ending, and therefore not ambiguous between accusative case, for which the case suffix is \textit{-yI}, and possessive case, for which the suffix is \textit{-sI}.
+
+% to-do: This all needs to go up, to the description of the potential confound in Lago et al.'s study.
+%This change was due to the morpho-phonologic nature of possessive suffix in Turkish, which spell-outs as (\textit{-I}) after a consonant same as the accusative. 
 The distribution of the verb types followed the same pattern as in \citet{LagoEtAl:2018}, namely twenty unergatives, eighteen unaccusatives, and two optionally transitive verbs. 
-The matrix verb was marked with overt plural marker \textit{-lar} in the half of experimental items.
-Adverbials in our experimental sentences were always pre-verbal and contained 2-3 words consisting of 15 characters on average.
-The second noun phrase is the head noun of the subject in all of our experimental sentences whereas the first noun phrase is the genitive modifier of the head, thus \textit{the attractor}.
-Unlike \citet{LagoEtAl:2018}, our head nouns were vowel-ending, which enables us to distinguish between accusative (\textit{-yI}) and possessive (\textit{-sI}).
-This change was due to the morpho-phonologic nature of possessive suffix in Turkish, which spell-outs as (\textit{-I}) after a consonant same as the accusative.
-While all of the head nouns were singular, the attractor noun was in its plural form in the half of the experimental items.
-One example set of experimental items can be seen in \ref{item:exp1ExperimentalItems}.
+%
+The pre-verbal adverbials preceding the verb in our experimental sentences consisted of 2-3 words (15 characters on average).
 
 % to-do: Why are all sentences in aorist instead of past (as they are in the actual items)?
-% there may be a better way of displaying items.
 \ex. \label{item:exp1ExperimentalItems}
 %
-\a. \textsc{Plural Attractor, Plural Verb} \label{item:exp1expitem-plpl}\\ 
+\a. \textsc{Plural Attractor, Ungrammatical (Plural Verb)} \label{item:exp1expitem-plpl}\\ 
   \gll *[Yönetici-ler-in \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpl-ıyor-lar}.\\ 
@@
 %
-\b. \textsc{Plural Attractor, Singular Verb} \label{item:exp1expitem-plsg}\\ 
+\b. \textsc{Plural Attractor, Grammatical (Singular Verb)} \label{item:exp1expitem-plsg}\\ 
   \gll [Yönetici-ler-in \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpl-ıyor}.\\ 
@@
 %
-\c. \textsc{Singular Attractor, Plural Verb} \label{item:exp1expitem-sgpl}\\ 
+\c. \textsc{Singular Attractor, Ungrammatical (Plural Verb)} \label{item:exp1expitem-sgpl}\\ 
   \gll *[Yönetici-nin \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpl-ıyor-lar}.\\ 
@@
 %
-\d. \textsc{Singular Attractor, Singular Verb}\label{item:exp1expitem-sgsg}\\ 
+\d. \textsc{Singular Attractor, Grammatical (Singular Verb)}\label{item:exp1expitem-sgsg}\\ 
   \gll [Yönetici-nin \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpl-ıyor}. \\ 
@@
 
-As for the filler sentences, we have included forty sentences, half of which ends in singular and ungrammatical while the other half was plural and grammatical.
-These decisions were made due to the non-existence of such sentences in the experimental sentences.
-We wanted to rule out a possible task strategy where participants decide on the grammaticality of the sentence by merely checking the final plural marking.
-Even though filler items did not follow a strict template as the experimental items, they were created within a template of \textit{Noun$_{{\textsc{gen}}}$-Noun$_{{\textsc{gen}}}$-Converb-Noun-Adverb-Verb}.
+We intermixed our experimental sentences with 40 filler sentences of two types, as illustrated in (\ref{item:exp1FillerItems}).
+To compensate for the fact that among experimental sentences, all ungrammatical sentences ended in a plural-agreeing verb, while all grammatical sentences ended in a singular-agreeing verb, we included 20 grammatical sentences with plural verbs, and 20 ungrammatical sentences with singular agreement.
+This was done in order to discourage participants from using a strategy based on verb number.
+
+%Even though filler items did not follow a strict template as the experimental items, they were created within a template of \textit{Noun$_{{\textsc{gen}}}$-Noun$_{{\textsc{gen}}}$-Converb-Noun-Adverb-Verb}.
 The ungrammaticality was created non-locally in the filler items to avoid task strategies.
@@
 %
-\a. \textsc{Grammatical, Plural Verb}\\ 
+\a. \textsc{Grammatical Filler (Plural Verb)}\\ 
   \gll [Sosyolog-un \textbf{öğrenci-si}] konuş-unca tutarsızlık açığ-a \textbf{çıkar-dı-lar}.\\ 
-sociolog-\textsc{gen}  student-\textsc{poss} speak-\textsc{nmlz} inconsistency  open-\Dat{} deduct-\textsc{pst}-\textsc{pl}.\\
-\glt \textit{`When the sociolog's student talked, they exposed an inconsistency.'}
+  sociolog-\textsc{gen}  student-\textsc{poss} speak-\textsc{nmlz} inconsistency  open-\textsc{dat} deduct-\textsc{pst}-\textsc{pl}.\\
+  \glt \textit{`When the sociologist's student talked, they exposed an inconsistency.'}
+%to-do: Translation above doesn't make sense.
 %
-\b. \textsc{Ungrammatical, Singular Verb}\\ 
+%
+\b. \textsc{Ungrammatical Filler (Singular Verb)}\\ 
 \gll *[Dansöz-ün \textbf{koca-sı}] var-ınca kapı sakince \textbf{aç-tı}.\\ 
@@
 
+The experiment was run online, using the web-based platform Ibex Farm (\url{http://spellout.net/ibexfarm/}). Each experimental session took approximately XXX minutes to complete.
+% to-do: How much time did it take?
+%
 Prior to the start of the experiment, participants provided demographic information, as well as informed consent to participate in the experiment.
-They read the instructions where we showed what they will see in the experiment, and where we informed them to give quick and accurate answers during the experiment.
-They are also informed regarding the that there will be a time-limit in answering the question.
-Every session started with a practice session where participants have been informed to be a bit faster when they were not.
-The sentences were presented in the middle of the screen word-by-word on a web-based platform Ibex Farm (\url{http://spellout.net/ibexfarm/}).
-Each word was displayed with 30 font size and stayed on the screen for 300 ms, unlike \citet{LagoEtAl:2018} and \citet{WagersEtAl:2009} where words stayed for 500 ms in the screen.
-After the sentence is completed, participants were asked: "How did they find the sentence?" They were informed to press P on their keyboard for \textit{good} and Q for bad.
-Apart from the practice items, we did not provide any feedback regarding their answers.
-However, participants were instructed to be faster when they waited more than 5,000 ms to answer the acceptability question.
+They read the instructions, and were given 9 practice trials before the experiment began.
+%
+Each trial began with a blank screen for 600 ms, followed by a word-by-word RSVP presentation of the sentence in the center of the screen, followed by an acceptability judgment. 
+Sentences were presented word-by-word in 30pt font size, and at a rate of 400 ms per word.
+Participants pressed the key 'P' for \textit{'acceptable'} and 'Q' for \textit{'unacceptable'}.
+They were instructed to provide an acceptability rating before the 5,000 ms deadline.
+During the experiment, they were reminded to respond faster if they responded too slowly.
 
-Participants saw forty experimental and forty filler items.
-Experimental items were distributed among four different lists using Latin Square design.
+Participants saw 40 experimental and 40 filler sentences.
+Experimental sentences were distributed among four different lists according to a Latin-square design.
 Every participant saw one version of the experiment with a specific list and one item per condition.
@@
 \subsection{Analysis} \label{sec:exp1:analysis}
-% Maybe leave it to Pavel?
 
-Every experimental item from both experiments (Experiment 1 and \citet{LagoEtAl:2018}) is included in the analysis.
-Participants (\Sexpr{length(bad_subjects)}) that exceeded the threshold of 0.25 difference in giving accurate answers to grammatical conditions \ref{item:exp1expitem-sgsg} and \ref{item:exp1expitem-sgpl} are excluded from the analysis.
-We used R packages brms \citep{R-brms_b} and rstan \citep{R-stan} to fit Bayesian hierarchical models \citep{GelmanHill:2007}.
-We added our independent variables, i.e.
-grammaticality of the sentence and the overt number information on the distractors, and random variable experiment as a factor.
-Analyses by items and participants are also conducted as a part of the Bayesian hierarchical models.
-We added our independent variables, i.e.
-grammaticality of the sentence and the overt number information on the distractors, and random variable experiment as a factor.
-Analyses by items and participants are also conducted as a part of the Bayesian hierarchical models.
-%I did not know how to state (1+x*y|subjet)
-Data regarding our experiments and analysis can be found in \texttt{link hidden due to blind review}.
+Since our aim was to test whether the morphological ambiguity present in the \citet{LagoEtAl:2018} items affected the presence or magnitude of the agreement attraction effect, statistically, we needed to test for the presence of an interaction between (i) the presence of the morphological ambiguity on the head noun, and (ii) the agreement attraction effect.
+In order to do so, we decided to analyze the data from the present experiment together with Lago et al.'s data, using experiment as an additional factor in the analysis.
+
+%All experimental trials from both experiments (Experiment 1 and Lago et al.'s study) was included in the analysis.
+
+Prior to analysis we removed the data for all participants who failed to show sufficient sentitivity to the effect of grammaticality in singular attractor conditions, i.e., when no agreement attraction was expected.
+Specifically, we removed all participants for whom the difference in the percentage of `yes' responses between the grammatical condition \ref{item:exp1expitem-sgsg} and the ungrammatical condition \ref{item:exp1expitem-sgpl} was below the threshold of 25 percentage points.
+As a result, we excluded \Sexpr{length(bad_subjects)} participants from experiment 1, and \Sexpr{stopifnot(length(bad_subjects_lagoetal) == 1)} one participant from the Lago et al.
+experiment.
+
+We used the R packages brms \citep{R-brms_b} and rstan \citep{R-stan} to fit Bayesian hierarchical models \citep[e.g.,]{GelmanHill:2007}.
+We analyzed only experimental sentences, and used (i) grammaticality of the sentence, (ii) attractor number, and (iii) presence of morphological ambiguity (i.e., experiment), as well as all their interactions as predictors.
+Moreover, we used by-participant and by-item intercepts and slopes for all predictors.
+
+Data for experiment 1, along with our analysis scripts can be found \texttt{link hidden due to blind review}.
+% to-do: Please create a repo where we can put all of this, or specify the github URL. I'm not aware of any blind reviews.
 
@@
 avg_fillers <- avg_clean %>% lapply(function(df) { df %>% subset(source == "filler") })
-pd <- position_dodge(0.1)
+
+pd <- position_dodge(0.0)
 p_avg_resp <- avg_exp$resp %>%
@@
 
+<<>>=
+avg_exp_resp_exp1 <- avg_exp$resp %>% subset(experiment == "Experiment 1")
+avg_exp_resp_lagoetal <- avg_exp$resp %>% subset(experiment == "Lago et al. (2018)")
+
+@
+
 \autoref{fig:exp1AvgResponse} shows the average proportions of ‘acceptable’ responses by experimental condition for both the original experiment in \citet{LagoEtAl:2018} and our replication with unambiguous possessive marking.
-It shows that ungrammatical sentences with plural attractors are rated as acceptable more often (M = \Sexpr{avg_exp$resp$M[3]}\%, SE = \Sexpr{avg_exp$resp$SE[3]}\%) than their counterparts with singular attractors (M=\Sexpr{avg_exp$resp$M[4]}\%, SE=\Sexpr{avg_exp$resp$SE[4]}\%).
-In addition to ungrammatical conditions, accuracy rates within the grammatical conditions were comparable and high across conditions (M = \Sexpr{avg_exp$resp$M[1]}\% and \Sexpr{avg_exp$resp$M[2]}\%, SE = \Sexpr{avg_exp$resp$SE[1]}\% and \Sexpr{avg_exp$resp$SE[2]}\% for singular and plural attractors respectively).
-As seen in \autoref{fig:exp1AvgResponse}, participants judged the sentences with plural attractor and singular verbs to be grammatical with the rate of \Sexpr{avg_exp$resp$M[3]-avg_exp$resp$M[4]}\%, which is in line with the findings reported in \citet{LagoEtAl:2018}.
+\Sexpr{ 
+cur_entry1 = avg_exp$resp %>% filter(experiment == "Experiment 1", grammatical == "ungrammatical", attractor_num == "plural");
+cur_entry2 = avg_exp$resp %>% filter(experiment == "Experiment 1", grammatical == "ungrammatical", attractor_num == "singular") }%
+It shows that ungrammatical sentences with plural attractors are rated as acceptable more often
+(M = \Sexpr{cur_entry1$M}, 
+SE = \Sexpr{cur_entry1$SE}) 
+than their counterparts with singular attractors 
+(M=\Sexpr{cur_entry2$M}, 
+SE=\Sexpr{cur_entry2$SE}).
+%
+\Sexpr{ 
+cur_entry1lago = avg_exp$resp %>% filter(experiment == "Lago et al. (2018)", grammatical == "ungrammatical", attractor_num == "plural");
+cur_entry2lago = avg_exp$resp %>% filter(experiment == "Lago et al. (2018)", grammatical == "ungrammatical", attractor_num == "singular") }%
+%This means that ungrammatical sentences with plural attractors were classified as acceptable more often than their counterparts with singular attractors. 
+The magnitude of the effect (\Sexpr{sprintf("%0.2f", cur_entry1$M-cur_entry2$M)}) was in line with the findings reported in \citet{LagoEtAl:2018}, where the difference was \Sexpr{sprintf("%0.2f", cur_entry1lago$M-cur_entry2lago$M)}.
+%
+Accuracy rates for grammatical conditions were nearly equal
+\Sexpr{ 
+cur_entry3 = avg_exp$resp %>% filter(experiment == "Experiment 1", grammatical == "grammatical", attractor_num == "singular");
+cur_entry4 = avg_exp$resp %>% filter(experiment == "Experiment 1", grammatical == "grammatical", attractor_num == "plural"); }%
+(M = \Sexpr{cur_entry3$M} and \Sexpr{cur_entry4$M}, SE = \Sexpr{cur_entry3$SE} and \Sexpr{cur_entry4$SE}, for singular and plural attractors respectively).
 
-<<exp1AvgResponse, fig.cap='Percentage of \\emph{yes} (acceptable) responses of Experiment 1 and \\citet{LagoEtAl:2018}', fig.height=3, fig.align='center'>>=
+<<exp1AvgResponse, fig.cap='Average percentages of `acceptable\' responses in Experiment 1 and \\citet{LagoEtAl:2018}.
+Within-subject 95\\% confidence intervals in brackets \\cite{Cousineau:2005,Morey:2008}.', fig.height=3, fig.align='center'>>=
 print(p_avg_resp)
@@
 
-# fname_exp1_responses_minimal <- "../workspace_exp1/model_responses_minimal"
-# m_responses_minimal <- brm(ResponseYes ~ (cEndsInConsonant + cUngrammatical + cAttractorPlural)^2 + 
-#                                          (cUngrammatical * cAttractorPlural + 1| subject) +
-#                                          (cUngrammatical * cAttractorPlural + 1| item),  
-#! *Utku* Can we omit this one out? We do not have every condition for every item from each subject? It goes to minus infinity.
-#! *PL* Are you talking about the starting values?
-#                    data = df_merged_nofillers,
-#                    family = bernoulli("probit"),
-#                    file = fname_exp1_responses_minimal, 
-#                    chains = n_chains, cores = n_cores, iter = n_iter)
-
 fname_exp1_rts <- "../workspace_exp1/fit_responses_rt"
@@
 model_results_table <- fixef(m_responses, summary = T, robust = F) %>% 
-  as.data.frame() %>% tibble::rownames_to_column("variables")
+  as.data.frame() #%>% tibble::rownames_to_column("variables")
+
 @
 
-The estimates and 95\% CIs of a Bayesian GLM in \autoref{fig:exp1ResponseModel} confirm the observations we stated above: the positive interaction between sentence grammaticality and attractor number is in line with a larger effect of attractor number in ungrammatical sentences.
-The main effect of ungrammaticality was \Sexpr{model_results_table[3,2]}[\Sexpr{model_results_table[3,4]};\Sexpr{model_results_table[3,4]}] in log-odds, and the interaction between the ungrammaticality and plural attractor was \Sexpr{model_results_table[7,2]}[\Sexpr{model_results_table[7,4]};\Sexpr{model_results_table[7,5]}] in log-odds.
-Since other estimates' credible intervals range over zero, we conclude that they were not informative.
-%maybe speak with p values?
-% we did not do any nested analysis, should we? Should it say anything different than figure 2?
+A Bayesian GLM assuming a Bernoulli distribution with a probit-link function was fit to participants' `acceptable' responses.
+The model's estimates and 95\% credible intervals are shown in \autoref{fig:exp1ResponseModel}.
+%
+%They confirm the observations we stated above: the positive interaction between sentence grammaticality and attractor number is in line with a larger effect of attractor number in ungrammatical sentences.
+%
+The main effect of \textit{ungrammaticality} (\Sexpr{print_estimate_with_ci( m_responses, 'cUngrammatical' )}) indicates that, on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences.
+Meanwhile, the positive interaction between \textit{ungrammaticality} and \textit{attractor number} (\Sexpr{print_estimate_with_ci( m_responses, 'cUngrammatical:cAttractorPlural')}) indicated a larger effect of attractor number in ungrammatical conditions, and thus a number agreement attraction effect.
+Importantly, there was no evidence for a three-way interaction between \textit{the presence of ambiguity}, \textit{ungrammaticality} and \textit{attractor number} (\Sexpr{print_estimate_with_ci( m_responses, 'cEndsInConsonant:cUngrammatical:cAttractorPlural')}).
+
+% to-do:
+% Importantly, even if there was an interaction with experiment, it's relatively small, so it wouldn't reduce the other interaction to 0.
 
@@
 
-<<exp1ResponseModel, fig.cap='Estimates and 95\\% credible intervals for the regression coefficients for Experiment 1', fig.height=3, fig.align='center'>>=
+<<exp1ResponseModel, fig.cap='Estimates and 95\\% credible intervals for the regression coefficients for Experiment 1.', fig.height=3, fig.align='center'>>=
 contrast_names <- c("cUngrammatical" = "Ungrammaticality",
@@
         x_breaks = c(-3,-2,-1, 0,1, 2) ) + 
-        xlab("Estimate (log-odds)")
+        xlab("Estimate (probit)")
 
@@
 In all of our filler sentences, the dependency between the first NP subject and its verb resolved in an adverbial embedded sentence.
-Grammatical filler items in Experiment 2 all had a template of \textit{RC$_{\textsc{pl}}$-Bare Noun-Adverb-Converb-Noun-Adverb-Verb$_{\textsc{pl}}$}, whereas ungrammatical filler items used a template of \textit{RC$_{\Sg{}}$-Bare Noun-Adverb-Converb-Noun-Adverb-Verb$_{\Sg{}}$}
+Grammatical filler items in Experiment 2 all had a template of
+XXX
+%\textit{RC$_{\textsc{pl}}$-Bare Noun-Adverb-Converb-Noun-Adverb-Verb$_{\textsc{pl}}$}, 
+whereas ungrammatical filler items used a template of 
+XXX
+%\textit{RC$_{\textsc{sg}}$-Bare Noun-Adverb-Converb-Noun-Adverb-Verb$_{\textsc{sg}$}
 
@@
 \ex. \label{item:exp2FillerItems}
+%
 \a. \textit{Plural Grammatical Verb}\\ 
   \gll Oku-t-tuk-lar-ı öğrenci başarılı ol-unca mutlu ol-du-lar.\\ 
-read-\Caus{}-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  student successful be-\textsc{nmlz} happy be-\textsc{pst}-\textsc{pl}.\\
+  read-\textsc{caus}-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  student successful be-\textsc{nmlz} happy be-\textsc{pst}-\textsc{pl}.\\
   \glt `When the student they sponsored become successful, they became happy.' 
+%
 \b. \textit{Singular Ungrammatical Verb}\\ 
   \gll *Kandır-dığ-ı adam öde-me-yince bulaşık saatlerce yıka-dı.\\ 
-trick-\textsc{nmlz}-\textsc{poss}  man pay-\Neg{}-\textsc{nmlz} dish for.hours clean-\textsc{pst}.\\
+  trick-\textsc{nmlz}-\textsc{poss}  man pay-\textsc{neg}-\textsc{nmlz} dish for.hours clean-\textsc{pst}.\\
   \glt Intended:`When the man he tricked did not pay, he cleaned dishes for hours.'
@@
 
-<<exp2AvgResponse, fig.cap='Estimates and 95\\% credible intervals for the regression coefficients for Experiment 1 and Experiment 2', fig.height=3, fig.align='center'>>=
+<<exp2AvgResponse, fig.cap='Estimates and 95\\% credible intervals for the regression coefficients for Experiment 1 and Experiment 2.
+Within-subject 95\\% confidence intervals in brackets \\cite{Cousineau:2005,Morey:2008}.', fig.height=3, fig.align='center'>>=
 
@@
 
-\bibliography{library,new-references}
+\bibliography{new-references,library}
 

### 2020-01-15 agremeent_draft_dec17/draft_dec17.tex
Fixed method and results for experiment 1

@@
 
-One hundred seven native speakers of Turkish in Experiment 1.
-The mean age is 20.14, ranging from 18 to 32.
-Across participants, a total 42 items were not responded to before the 5 second deadline by 33 different participants.
+We recruited 118 undergraduate students to participate in Experiment 1 in exchange for course credit. All participants were native speakers of Turkish, with an average age of 20 (range: 18 -- 32). 
 These items were not included in the analysis.
-Experiments in this paper were carried out following the Declaration of Helsinki and the regulations concerning ethics in research in Bo\u{g}azi\c{c}i University.
+Experiments in this paper were carried out following the Declaration of Helsinki and the regulations concerning ethics at research in Bo\u{g}azi\c{c}i University.
 All participants provided informed consent.
-They were tested online, on IbexFarm, using their preferred platform.
+They were tested online, on IbexFarm.
+%to-do: cite ibexfarm
 
@@
 %
-\a. \textit{Grammatical, Plural Verb}\\ 
-\gll [Sosyolog-un öğrenci-si] konuş-unca tutarsızlık açığ-a çıkar-dı-lar.\\ 
-sociolog-\textsc{gen}  student-\textsc{poss} speak-\textsc{nmlz} inconsistency  open-\Dat{} deduct-\textsc{pst}-\textsc{pl}.\\
-\glt \textit{`When the sociolog's student talked, they exposed an inconsistency.'}
+\a. \textsc{Grammatical Filler (Plural Verb)}\\ 
+  \gll [Sosyolog-un \textbf{öğrenci-si}] konuş-unca tutarsızlık açığ-a \textbf{çıkar-dı-lar}.\\ 
+  sociolog-\textsc{gen}  student-\textsc{poss} speak-\textsc{nmlz} inconsistency  open-\textsc{dat} deduct-\textsc{pst}-\textsc{pl}.\\
+  \glt \textit{`When the sociologist's student talked, they exposed an inconsistency.'}
+%to-do: Translation above doesn't make sense.
 %
-\b. \textit{Ungrammatical, Singular Verb}\\ 
-\gll *[Dansöz-ün koca-sı] var-ınca kapı sakince aç-tı.\\ 
+%
+\b. \textsc{Ungrammatical Filler (Singular Verb)}\\ 
+\gll *[Dansöz-ün \textbf{koca-sı}] var-ınca kapı sakince \textbf{aç-tı}.\\ 
 dancer-\textsc{gen}  husband-\textsc{poss} arrive-\textsc{nmlz} door slowly  open-\textsc{pst}.\\
 \glt \textit{Intended:`When the husband of the dancer came, the door opened slowly.'}
+% to-do: Does the above mean that it's grammatical with another meaning?
 
@@
 
-Prior to the experiments, participants gave information regarding themselves and consent to participate in the experiment.
-They read the instructions where we showed what they will see in the experiment, and where we informed them to give quick and accurate answers during the experiment.
-They are also informed regarding the that there will be a time-limit in answering the question.
-Every session started with a practice session where participants have been informed to be a bit faster when they were not.
-The sentences were presented in the middle of the screen word-by-word on a web-based platform Ibex Farm (\url{http://spellout.net/ibexfarm/}).
-Each word was displayed with 30 font size and stayed on the screen for 300 ms, unlike \citet{LagoEtAl:2018} and \citet{WagersEtAl:2009} where words stayed for 500 ms in the screen.
-After the sentence is completed, participants were asked: "How did they find the sentence?" They were informed to press P on their keyboard for \textit{good} and Q for bad.
-Apart from the practice items, we did not provide any feedback regarding their answers.
-However, participants were instructed to be faster when they waited more than 5,000 ms to answer the acceptability question.
+The experiment was run online, using the web-based platform Ibex Farm (\url{http://spellout.net/ibexfarm/}). Each experimental session took approximately XXX minutes to complete.
+% to-do: How much time did it take?
+%
+Prior to the start of the experiment, participants provided demographic information, as well as informed consent to participate in the experiment.
+They read the instructions, and were given 9 practice trials before the experiment began.
+%
+Each trial began with a blank screen for 600 ms, followed by a word-by-word RSVP presentation of the sentence in the center of the screen, followed by an acceptability judgment. 
+Sentences were presented word-by-word in 30pt font size, and at a rate of 400 ms per word.
+Participants pressed the key 'P' for \textit{'acceptable'} and 'Q' for \textit{'unacceptable'}.
+They were instructed to provide an acceptability rating before the 5,000 ms deadline.
+During the experiment, they were reminded to respond faster if they responded too slowly.
 
-Participants saw forty experimental and forty filler items.
-Experimental items were distributed among four different lists using Latin Square design.
+Participants saw 40 experimental and 40 filler sentences.
+Experimental sentences were distributed among four different lists according to a Latin-square design.
 Every participant saw one version of the experiment with a specific list and one item per condition.
@@
 \subsection{Analysis} \label{sec:exp1:analysis}
-% Maybe leave it to Pavel?
 
-Every experimental item from both experiments (Experiment 1 and \citet{LagoEtAl:2018}) is included in the analysis.
-Participants (10) that exceeded the threshold of 0.25 difference in giving accurate answers to grammatical conditions \ref{item:exp1expitem-sgsg} and \ref{item:exp1expitem-sgpl} are excluded from the analysis.
-We used R packages brms \citep{R-brms_b} and rstan \citep{R-stan} to fit Bayesian hierarchical models \citep{GelmanHill:2007}.
-We added our independent variables, i.e.
-grammaticality of the sentence and the overt number information on the distractors, and random variable experiment as a factor.
-Analyses by items and participants are also conducted as a part of the Bayesian hierarchical models.
-We added our independent variables, i.e.
-grammaticality of the sentence and the overt number information on the distractors, and random variable experiment as a factor.
-Analyses by items and participants are also conducted as a part of the Bayesian hierarchical models.
-%I did not know how to state (1+x*y|subjet)
-Data regarding our experiments and analysis can be found in \texttt{link hidden due to blind review}.
+Since our aim was to test whether the morphological ambiguity present in the \citet{LagoEtAl:2018} items affected the presence or magnitude of the agreement attraction effect, statistically, we needed to test for the presence of an interaction between (i) the presence of the morphological ambiguity on the head noun, and (ii) the agreement attraction effect.
+In order to do so, we decided to analyze the data from the present experiment together with Lago et al.'s data, using experiment as an additional factor in the analysis.
+
+%All experimental trials from both experiments (Experiment 1 and Lago et al.'s study) was included in the analysis.
+
+Prior to analysis we removed the data for all participants who failed to show sufficient sentitivity to the effect of grammaticality in singular attractor conditions, i.e., when no agreement attraction was expected.
+Specifically, we removed all participants for whom the difference in the percentage of `yes' responses between the grammatical condition \ref{item:exp1expitem-sgsg} and the ungrammatical condition \ref{item:exp1expitem-sgpl} was below the threshold of 25 percentage points.
+As a result, we excluded 10 participants from experiment 1, and  one participant from the Lago et al.
+experiment.
+
+We used the R packages brms \citep{R-brms_b} and rstan \citep{R-stan} to fit Bayesian hierarchical models \citep[e.g.,]{GelmanHill:2007}.
+We analyzed only experimental sentences, and used (i) grammaticality of the sentence, (ii) attractor number, and (iii) presence of morphological ambiguity (i.e., experiment), as well as all their interactions as predictors.
+Moreover, we used by-participant and by-item intercepts and slopes for all predictors.
+
+Data for experiment 1, along with our analysis scripts can be found \texttt{link hidden due to blind review}.
+% to-do: Please create a repo where we can put all of this, or specify the github URL. I'm not aware of any blind reviews.
 
@@
 \autoref{fig:exp1AvgResponse} shows the average proportions of ‘acceptable’ responses by experimental condition for both the original experiment in \citet{LagoEtAl:2018} and our replication with unambiguous possessive marking.
-It shows that ungrammatical sentences with plural attractors are rated as acceptable more often (M = 0.22\%, SE = 0.01\%) than their counterparts with singular attractors (M=0.11\%, SE=0.01\%).
-In addition to ungrammatical conditions, accuracy rates within the grammatical conditions were comparable and high across conditions (M = 0.92\% and 0.93\%, SE = 0.01\% and 0.01\% for singular and plural attractors respectively).
-As seen in \autoref{fig:exp1AvgResponse}, participants judged the sentences with plural attractor and singular verbs to be grammatical with the rate of 0.1\%, which is in line with the findings reported in \citet{LagoEtAl:2018}.
+%
+It shows that ungrammatical sentences with plural attractors are rated as acceptable more often
+(M = 0.22, 
+SE = 0.01) 
+than their counterparts with singular attractors 
+(M=0.11, 
+SE=0.01).
+%
+%
+%This means that ungrammatical sentences with plural attractors were classified as acceptable more often than their counterparts with singular attractors. 
+The magnitude of the effect (0.10) was in line with the findings reported in \citet{LagoEtAl:2018}, where the difference was 0.11.
+%
+Accuracy rates for grammatical conditions were nearly equal
+%
+(M = 0.93 and 0.92, SE = 0.01 and 0.01, for singular and plural attractors respectively).
 
@@
 
-\caption{Percentage of \emph{yes} (acceptable) responses of Experiment 1 and \citet{LagoEtAl:2018}}\label{fig:exp1AvgResponse}
+\caption{Average percentages of `acceptable' responses in Experiment 1 and \citet{LagoEtAl:2018}.
+Within-subject 95\% confidence intervals in brackets \cite{Cousineau:2005,Morey:2008}.}\label{fig:exp1AvgResponse}
 \end{figure}
@@
 
-The estimates and 95\% CIs of a Bayesian GLM in \autoref{fig:exp1ResponseModel} confirm the observations we stated above: the positive interaction between sentence grammaticality and attractor number is in line with a larger effect of attractor number in ungrammatical sentences.
-The main effect of ungrammaticality was -3.09[-3.35;-3.35] in log-odds, and the interaction between the ungrammaticality and plural attractor was 0.72[0.42;1.02] in log-odds.
-Since other estimates' credible intervals range over zero, we conclude that they were not informative.
-%maybe speak with p values?
-% we did not do any nested analysis, should we? Should it say anything different than figure 2?
+A Bayesian GLM assuming a Bernoulli distribution with a probit-link function was fit to participants' `acceptable' responses.
+The model's estimates and 95\% credible intervals are shown in \autoref{fig:exp1ResponseModel}.
+%
+%They confirm the observations we stated above: the positive interaction between sentence grammaticality and attractor number is in line with a larger effect of attractor number in ungrammatical sentences.
+%
+The main effect of \textit{ungrammaticality} ($\hat{\beta}=-3.09;$ $CI=[-3.35; -2.84];$ $P(\beta<0)> .999$) indicates that, on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences.
+Meanwhile, the positive interaction between \textit{ungrammaticality} and \textit{attractor number} ($\hat{\beta}=0.72;$ $CI=[0.42; 1.02];$ $P(\beta<0)< .001$) indicated a larger effect of attractor number in ungrammatical conditions, and thus a number agreement attraction effect.
+Importantly, there was no evidence for a three-way interaction between \textit{the presence of ambiguity}, \textit{ungrammaticality} and \textit{attractor number} ($\hat{\beta}=0.30;$ $CI=[-0.20; 0.79];$ $P(\beta<0)=    .12$).
 
@@
 
-\caption[Estimates and 95\% credible intervals for the regression coefficients for Experiment 1]{Estimates and 95\% credible intervals for the regression coefficients for Experiment 1}\label{fig:exp1ResponseModel}
+\caption[Estimates and 95\% credible intervals for the regression coefficients for Experiment 1]{Estimates and 95\% credible intervals for the regression coefficients for Experiment 1.}\label{fig:exp1ResponseModel}
 \end{figure}
@@
 
-\caption[Estimates and 95\% credible intervals for the regression coefficients for Experiment 1 and Experiment 2]{Estimates and 95\% credible intervals for the regression coefficients for Experiment 1 and Experiment 2}\label{fig:exp2AvgResponse}
+\caption{Estimates and 95\% credible intervals for the regression coefficients for Experiment 1 and Experiment 2.
+Within-subject 95\% confidence intervals in brackets \cite{Cousineau:2005,Morey:2008}.}\label{fig:exp2AvgResponse}
 \end{figure}

### 2020-01-15 scripts/misc.R

@@ -152,6 +152,7 @@ model_summary <- function(m, include_pp_below_zero = T)
     
   }
   
+  rownames(tbl) <- tbl$coef
   tbl
 }
 
@@ -286,3 +287,15 @@ create_model_coefs_plot <- function(m,
   
   return (p)
 }
+
+
+print_estimate_with_ci <- function(model, contr_name, fmt = "%0.2f") {
+  full_fmt <- sprintf("$\\hat{\\beta}=%s;$ $CI=[%s; %s];$ $P(\\beta<0)%s$", fmt, fmt, fmt, "%s")
+  est <- fixef(model, summary = T, robust = F) %>% .[contr_name,]
+  post_prob <- model_summary(model) %>% .[contr_name,]
+  post_prob %<>% mutate( is_extreme = post_prob[['PBelowZero']] < .001 | post_prob[['PBelowZero']] > .999 )
+  post_prob %<>% mutate( PBelowZeroStr = ifelse(is_extreme, as.character(PBelowZeroStr), paste("=", PBelowZeroStr) ) )
+  sprintf(full_fmt, est[['Estimate']], est[['Q2.5']], est[['Q97.5']], post_prob[['PBelowZeroStr']])
+}
+
+

### 2020-01-15 agremeent_draft_dec17/draft_dec17.Rnw
minor fix

@@
 <<>>=
+
 # load packages
@@
 <<loadExperiment2Data>>=
+
 fname_data2 <- "../workspace_exp2/exp_data.rds"
@@
 form_exp2 <- readRDS(file = fname_form)
-
-#! No idea what this is about. Excluding for now.
-# form_exp2 <- form_exp2[-c(56),]
 
@@
 <<badSubjects2>>=
-# identify participants 
+
+# identify bad participants 
 bad_subjects2 <- subset(avg_by_subj_wide2, delta_dc <= 0.25 ) %>% .$subject
 
-data_exp2_clean <- data_exp2 %>% subset(!subject %in% bad_subjects)
+data_exp2_clean <- data_exp2 %>% subset(!subject %in% bad_subjects2)
 
@@
 df_merge_exp2$experiment <- "Experiment 2"
-df_merge_exp2$grammatical <- with(df_merge_exp2, ifelse(grammatical == "gram", 
-                                                        "grammatical",
-                                                        "ungrammatical"))
-df_merge_exp2$attractor_num <- with(df_merge_exp2, ifelse(attractor_num == "pl", 
-                                                          "plural", 
-                                                          "singular"))
-df_merge_exp2$item %<>% as.integer()
-df_merge_exp2$subject %<>% as.character()
+df_merge_exp2$grammatical %<>% dplyr::recode("gram"="grammatical", "ungram"="ungrammatical")
+df_merge_exp2$attractor_num %<>% dplyr::recode("pl"="plural", "sg"="singular")
+df_merge_exp2 %<>% mutate( item = sprintf("I2[%s]", as.character(item)), subject = as.character(subject) )
 
@@
 
+df_merge_exp1$item %<>% as.character()
 df_merged2 <- dplyr::bind_rows(df_merge_exp1, df_merge_exp2)
-df_merged2$subject %<>% as.factor()
-df_merged2$item %<>% as.factor()
+df_merged2 %<>% mutate( subject = as.character(subject), item = as.character(item) )
 
-df_exp2_na_nofillers <- subset(df_merged2, is.na(ResponseYes) & source != "filler")
-
+df_exp2_na_nofillers <- df_merged2 %>% subset(is.na(ResponseYes) & source != "filler")
 df_merged2_nonna <- df_merged2 %>% subset(!is.na(ResponseYes))
@@
 
-Eighty native speakers of Turkish in Experiment 1.
-The mean age is \Sexpr{mean(as.numeric(as.character(form_exp2$Age)))}, ranging from \Sexpr{min(as.numeric(as.character(form_exp2$Age)))} to \Sexpr{max(as.numeric(as.character(form_exp2$Age)))}.
-Across participants, a total \Sexpr{sum(is.na(df_exp2_na_nofillers$ResponseYes))} items were not responded to before the 5 second deadline by \Sexpr{length(unique(df_exp2_na_nofillers$subject))} different participants.
-These items were not included in the analysis.
+We recruited 79 native speakers of Turkish to participate in Experiment 2.
+Their average age was \Sexpr{round(mean(form_exp2$Age))}, ranging from \Sexpr{min(form_exp2$Age)} to \Sexpr{max(form_exp2$Age)}.
+
 Experiments in this paper were carried out following the Declaration of Helsinki and the regulations concerning ethics in research in Bo\u{g}azi\c{c}i University.
@@
 %
-\a. \textit{Plural Attractor, Plural Verb}\label{item:exp2expitem-plpl}\\ 
+\a. \textsc{Plural Attractor, Ungrammatical (Plural Verb)}\label{item:exp2expitem-plpl}\\ 
   \gll *Tut-tuk-lar-ı aşcı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
@@
 %
-\b. \textit{Plural Attractor, Singular Verb}\label{item:exp2expitem-plsg}\\ 
+\b. \textit{Plural Attractor, Grammatical (Singular Verb)}\label{item:exp2expitem-plsg}\\ 
   \gll Tut-tuk-lar-ı aşcı mutfak-ta sürekli zıpl-ıyor.\\ 
@@
 %
-\c. \textit{Singular Attractor, Plural Verb}\label{item:exp2expitem-sgpl}\\
+\c. \textit{Singular Attractor, Ungrammatical (Plural Verb)}\label{item:exp2expitem-sgpl}\\
   \gll *Tut-tuğ-u aşcı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
@@
 %
-\d. \textit{Singular Attractor, Singular Verb}\label{item:exp2expitem-sgsg}\\ 
+\d. \textit{Singular Attractor, Grammatical (Singular Verb)}\label{item:exp2expitem-sgsg}\\ 
   \gll Tut-tuğ-u aşcı mutfak-ta sürekli zıpl-ıyor.\\ 
@@
 
-In Experiment 2, the same procedure as Experiment 1 has been followed with regards to how sentences are presented within the experiment.
+% to-do: some more details.
+% In Experiment 2, the same procedure as Experiment 1 has been followed with regards to how sentences are presented within the experiment.
 
@@
 part of the Bayesian hierarchical models. Data regarding our experiments and analysis can be found in \texttt{link hidden due to blind review}.
+
+Across participants, a total \Sexpr{sum(is.na(df_exp2_na_nofillers$ResponseYes))} items were not responded to before the 5 second deadline by \Sexpr{length(unique(df_exp2_na_nofillers$subject))} different participants.
+These items were not included in the analysis.
 
@@
 # ## test model parameterization using a simple GLM first
-# m <- glm(ResponseYes ~ cEndsInConsonant * cUngrammatical * cAttractorPlural,
-#          data = df_merged_nofillers,
+# m <- glm(ResponseYes ~ cVerbalAttractor * cUngrammatical * cAttractorPlural,
+#          data = df_merged_nofillers2,
 #          family = binomial("probit"))
@@
                                  (cUngrammatical * cAttractorPlural + 1| item),
-                   data = df_merged_nofillers2,
+                   data = df_merged_nofillers2 %>% subset(!is.na(ResponseYes)),
                    family = bernoulli("probit"),
@@
         x_breaks = c(-3,-2,-1, 0, 1) ) + 
-            xlab("Estimate (log-odds)")
+        xlab("Estimate (probit)")
 

### 2020-01-15 agremeent_draft_dec17/draft_dec17.tex
minor fix

@@
 
+% to-do:
+% Importantly, even if there was an interaction with experiment, it's relatively small, so it wouldn't reduce the other interaction to 0.
+
 %Moreover, this findings are also predicted by cue-based retrieval models \citep{engelmann2019effect, vasishth2019computational} and last rendition of marking and morphing theory by \citet{HammerlyEtAl:2019}.
@@
 
-Eighty native speakers of Turkish in Experiment 1.
-The mean age is 21.22, ranging from 0 to 31.
-Across participants, a total 55 items were not responded to before the 5 second deadline by 41 different participants.
-These items were not included in the analysis.
+We recruited 79 native speakers of Turkish to participate in Experiment 2. Their average age was 21, ranging from 18 to 31.
+
 Experiments in this paper were carried out following the Declaration of Helsinki and the regulations concerning ethics in research in Bo\u{g}azi\c{c}i University.
@@
 part of the Bayesian hierarchical models. Data regarding our experiments and analysis can be found in \texttt{link hidden due to blind review}.
+
+Across participants, a total 55 items were not responded to before the 5 second deadline by 45 different participants. These items were not included in the analysis.
 
@@
 We see that there is no effect resembling agreement attraction in the ungrammatical conditions of Experiment 2.
-Ungrammatical conditions showed comparable effects (0.07 and 0.07 for plural and singular attractors respeectively) regardless of the attractor's number.
+Ungrammatical conditions showed comparable effects (0.05 and 0.06 for plural and singular attractors respeectively) regardless of the attractor's number.
 

### 2020-01-15 scripts/experiment2_prepare.R

@@ -1,3 +1,5 @@
+
+
 library(languageR)
 library(tidyverse)
 library(gdata)
@@ -16,40 +18,52 @@ data <- read.csv(fname_data,
                  encoding = "UTF-8" , 
                  col.names = paste0("V",seq_len(11)), 
                  fill = TRUE)
-colnames(data) = c("Time", "MD5", "ControllerType", "SentenceNoInStimFile", "Element", "Type", "Item", "Sentence", "Question","Answer", "RT")
+colnames(data) = c("Timestamp", "MD5", "ControllerType", "SentenceNoInStimFile", "Element", "Type", "Item", "Sentence", "Question","Answer", "RT")
+#data %<>% dplyr::select(-MD5)
 
-FormEntries <- subset(data, ControllerType != "DashedAcceptabilityJudgment" ) %>% drop.levels(); nrow(data)
+FormEntries <- subset(data, ControllerType != "DashedAcceptabilityJudgment" ) %>% 
+                      drop.levels(); 
+nrow(data)
+
 data %<>% subset(ControllerType == "DashedAcceptabilityJudgment")
-age <- dplyr::select(FormEntries, MD5,Sentence,Question) %>% 
-  dplyr::filter(Sentence == "age") %>%
-  dplyr::select(MD5, Age = Question)
-natturk <- dplyr::select(FormEntries, MD5,Sentence,Question) %>% 
-  dplyr::filter(Sentence == "natturk") %>%
-  dplyr::select(MD5, Natturk = Question) %>%
-  mutate(Natturk = Natturk == "male")
-dex <- dplyr::select(FormEntries, MD5,Sentence,Question) %>% 
-  dplyr::filter(Sentence == "dex") %>%
-  dplyr::select(MD5, Dex = Question) %>%
-  mutate(Dex = ifelse(Dex == "male", "right-handed", "left-handed"))
-FormPart <- dplyr::left_join(age, natturk, by = "MD5") %>% 
-  dplyr::left_join(., dex , by = "MD5" ) %>% 
-  unique()
-lenForm <- length(levels(factor(FormPart$MD5))); lenForm
-md5form <- levels(factor(FormPart$MD5))
-md5form_subject <- data.frame("MD5" = md5form, "subject" = sprintf("S[%s]",seq((lenForm))))
-FormPart <- merge(FormPart,md5form_subject, all = T)
+age <- dplyr::select(FormEntries, Timestamp,Sentence,Question,MD5) %>% 
[…]

### 2020-01-21 agremeent_draft_dec17/draft_dec17.Rnw
Number Check: 1 out of 4

@@
 % In Experiment 1, we decided to test this hypothesis
+
+% to-do: This all needs to go up, to the description of the potential confound in Lago et al.'s study.
+%This change was due to the morpho-phonologic nature of possessive suffix in Turkish, which spell-outs as (\textit{-I}) after a consonant same as the accusative.
 
@@
 All participants were native speakers of Turkish, with an average age of \Sexpr{round(mean(form_exp1$Age))} (range: \Sexpr{min(form_exp1$Age)} -- \Sexpr{max(form_exp1$Age)}).
-These items were not included in the analysis.
-Experiments in this paper were carried out following the Declaration of Helsinki and the regulations concerning ethics at research in Bo\u{g}azi\c{c}i University.
-All participants provided informed consent.
-They were tested online, on IbexFarm.
-%to-do: cite ibexfarm
+Experiment were carried out following the Declaration of Helsinki and the regulations concerning ethics at research in Bo\u{g}azi\c{c}i University.
+All participants provided informed consent prior to their participation.
 
@@
 %
-All sentences started with a complex subject NP like \textit{`the manager's cook'} (\textit{yöneticinin aşcısı}), in which the possessor, which functioned as the attractor, carried genitive case, and the head noun cassied possessive case.
+We have used the experimental items in \citet{LagoEtAl:2018} as a base. 
+All sentences started with a complex subject NP like \textit{`the manager's cook'} (\textit{yöneticinin aşcısı}), in which the possessor, which functioned as the attractor, carried genitive case, and the head noun carried possessive case.
 Because the head noun was singular in all conditions, sentences with plural verb agreement were ungrammatical. 
-% to-do: Didn't we use Lago's items as a base?? If so, we need to say this here, and also how much we've changed, and how much remained.
+Moreover, as in the original study, the properties of the nouns in the complex subject NP and the relation between these nouns held constant in our replication. 
+The distribution of the verb types followed the same pattern as in \citet{LagoEtAl:2018}, namely twenty unergatives, eighteen unaccusatives, and two optionally transitive verbs. 
+Both in \citet{LagoEtAl:2018} and in our replication, pre-verbal adverbials consisting of 2-3 words (15 characters on average) are used.
 Unlike the \citet{LagoEtAl:2018} sentences, our head nouns were vowel-ending, and therefore not ambiguous between accusative case, for which the case suffix is \textit{-yI}, and possessive case, for which the suffix is \textit{-sI}.
 
-% to-do: This all needs to go up, to the description of the potential confound in Lago et al.'s study.
-%This change was due to the morpho-phonologic nature of possessive suffix in Turkish, which spell-outs as (\textit{-I}) after a consonant same as the accusative. 
-The distribution of the verb types followed the same pattern as in \citet{LagoEtAl:2018}, namely twenty unergatives, eighteen unaccusatives, and two optionally transitive verbs. 
-%
-The pre-verbal adverbials preceding the verb in our experimental sentences consisted of 2-3 words (15 characters on average).
-
-% to-do: Why are all sentences in aorist instead of past (as they are in the actual items)?
 \ex. \label{item:exp1ExperimentalItems}
@@
 \a. \textsc{Plural Attractor, Ungrammatical (Plural Verb)} \label{item:exp1expitem-plpl}\\ 
-  \gll *[Yönetici-ler-in \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpl-ıyor-lar}.\\ 
-  manager-\textsc{pl}-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
+  \gll *[Yönetici-ler-in \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpla-dı-lar}.\\ 
+  manager-\textsc{pl}-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{pst}-\textsc{pl}.\\
   \glt \textit{`The cooks of the manager were jumping in the kitchen non-stop.'}
@@
 \b. \textsc{Plural Attractor, Grammatical (Singular Verb)} \label{item:exp1expitem-plsg}\\ 
-  \gll [Yönetici-ler-in \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpl-ıyor}.\\ 
-  manager-\textsc{pl}-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
+  \gll [Yönetici-ler-in \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpla-dı}.\\ 
+  manager-\textsc{pl}-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{pst}.\\
   \glt \textit{`The cooks of the manager was jumping in the kitchen non-stop.'}
@@
 \c. \textsc{Singular Attractor, Ungrammatical (Plural Verb)} \label{item:exp1expitem-sgpl}\\ 
-  \gll *[Yönetici-nin \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpl-ıyor-lar}.\\ 
-  manager-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
+  \gll *[Yönetici-nin \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpla-dı-lar}.\\ 
+  manager-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{pst}-\textsc{pl}.\\
   \glt \textit{`The cook of the manager were jumping in the kitchen non-stop.'}
@@
 \d. \textsc{Singular Attractor, Grammatical (Singular Verb)}\label{item:exp1expitem-sgsg}\\ 
-  \gll [Yönetici-nin \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpl-ıyor}. \\ 
-  manager-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
+  \gll [Yönetici-nin \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpla-dı}. \\ 
+  manager-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{pst}.\\
   \glt \textit{`The cook of the manager was jumping in the kitchen non-stop.'}
@@
 This was done in order to discourage participants from using a strategy based on verb number. 
+Filler items followed a similar template in which sentence again started with a complex genitive-possessive noun phrase. 
+However, in filler items, they were the controller of an embedded clause which serves as a adverbial. 
+In grammatical fillers, we have made use of pro-dropped subject strategy in Turkish; thus, it enabled us to use plural verb without having ungrammatical sentences as in (\ref{item:exp1GrammaticalFiller}).
+The object \textit{tutarsızlık} is a bare nominal preceding a light verb construction.
+Differently in ungrammatical fillers, bare nominal did not precede a light verb construction, but an adverb and a verb.
+Since Turkish only allows bare nominals right next to the verb, sentences were deemed ungrammatical when the participants read the verb.
 
@@
 %
-\a. \textsc{Grammatical Filler (Plural Verb)}\\ 
-  \gll [Sosyolog-un \textbf{öğrenci-si}] konuş-unca tutarsızlık açığ-a \textbf{çıkar-dı-lar}.\\ 
+\a. \label{item:exp1GrammaticalFiller} \textsc{Grammatical Filler (Plural Verb)}\\ 
+  \gll [Sosyolog-un \textbf{öğrenci-si}] konuş-unca tutarsızlık açığ-a \textbf{çıkar-dı-lar}.\\ %utku: what does this bold mean?
+if it the dependency between them then the bold parts are not correct.
+ogrencisi is the subject of the verb konusunca, and the subject of the matrix verb cikardilar is omitted.
   sociolog-\textsc{gen}  student-\textsc{poss} speak-\textsc{nmlz} inconsistency  open-\textsc{dat} deduct-\textsc{pst}-\textsc{pl}.\\
-  \glt \textit{`When the sociologist's student talked, they exposed an inconsistency.'}
+  \glt \textit{`When the student of the sociologist spoke, they revealed an inconsistency.'}
 %to-do: Translation above doesn't make sense.
@@
 
-The experiment was run online, using the web-based platform Ibex Farm (\url{http://spellout.net/ibexfarm/}). Each experimental session took approximately XXX minutes to complete.
-% to-do: How much time did it take?
+The experiment was run online, using the web-based platform Ibex Farm (\url{http://spellout.net/ibexfarm/}). Each experimental session took approximately 25 minutes to complete.
 %
@@
 Sentences were presented word-by-word in 30pt font size, and at a rate of 400 ms per word.
+Between each word, participants saw a blank screen for 100 ms.
 Participants pressed the key 'P' for \textit{'acceptable'} and 'Q' for \textit{'unacceptable'}.
@@
 
-Since our aim was to test whether the morphological ambiguity present in the \citet{LagoEtAl:2018} items affected the presence or magnitude of the agreement attraction effect, statistically, we needed to test for the presence of an interaction between (i) the presence of the morphological ambiguity on the head noun, and (ii) the agreement attraction effect.
+Since our aim was to test whether the morphological ambiguity present in the \citet{LagoEtAl:2018} items affected the presence or magnitude of the agreement attraction effect, statistically, we needed to test for the presence of an interaction between
+(i) the presence of the morphological ambiguity on the head noun, and 
+(ii) the agreement attraction effect. 
 In order to do so, we decided to analyze the data from the present experiment together with Lago et al.'s data, using experiment as an additional factor in the analysis.
@@
 
-We used the R packages brms \citep{R-brms_b} and rstan \citep{R-stan} to fit Bayesian hierarchical models \citep[e.g.,]{GelmanHill:2007}.
-We analyzed only experimental sentences, and used (i) grammaticality of the sentence, (ii) attractor number, and (iii) presence of morphological ambiguity (i.e., experiment), as well as all their interactions as predictors.
+We used the R packages brms \citep{R-brms_b} and rstan \citep{R-stan} to fit Bayesian hierarchical models \citep[e.g.,][]{GelmanHill:2007}. We analyzed only experimental sentences, and used 
+(i) grammaticality of the sentence, 
+(ii) attractor number, and 
+(iii) presence of morphological ambiguity (i.e., experiment), as well as all their interactions as predictors. 
 Moreover, we used by-participant and by-item intercepts and slopes for all predictors.
-
-Data for experiment 1, along with our analysis scripts can be found \texttt{link hidden due to blind review}.
-% to-do: Please create a repo where we can put all of this, or specify the github URL. I'm not aware of any blind reviews.
+Data for experiment 1, along with our analysis scripts can be found in \url{https://github.com/utkuturk/replication_lagoetal2018}.
 
@@
 
-We recruited 79 native speakers of Turkish to participate in Experiment 2.
-Their average age was \Sexpr{round(mean(form_exp2$Age))}, ranging from \Sexpr{min(form_exp2$Age)} to \Sexpr{max(form_exp2$Age)}.
-
-Experiments in this paper were carried out following the Declaration of Helsinki and the regulations concerning ethics in research in Bo\u{g}azi\c{c}i University.
-All participants provided informed consent.
-They were tested online, on IbexFarm, using their preferred platform, % Find citation for using IbexFarm and online testing etc?
+We recruited 79 undergraduate students to participate in Experiment 2 in exchange for course credit.
+All participants were native speakers of Turkish, with an average age of \Sexpr{round(mean(form_exp2$Age))} (range: \Sexpr{min(form_exp2$Age)} - \Sexpr{max(form_exp2$Age)}).
+Experiment were carried out following the Declaration of Helsinki and the regulations concerning ethics at research in Bo\u{g}azi\c{c}i University.
+All participants provided informed consent prior to their participation.
 
@@
 
-In Experiment 2, participants saw the sentences word by word in the middle of their screen.
-We have again formed 40 sets of items.
-The grammaticality of the sentences (\textit{grammatical} x \textit{ungrammatical}) and the number of the attractor (\textit{singular} x \textit{plural}) were manipulated.
-Unlike Experiment 1, we used nominalized relative clause attractors instead of nouns.
+We used 40 sets of sentences like
+(\ref{item:exp2ExperimentalItems}), in which we manipulated
+(i) the number of the attractor, and
+(ii) the number agreement on the verb. 
+Unlike Experiment 1, we used the verb of a nominalized relative clause (i.e. \textit{tuttukları}) as an attractor instead of a genitive marked noun. 
 We took advantage of syncretism between Turkish nominal and verbal plural marker.
@@
 
-All experimental sentences followed the same template as the experiment one except for the nature of the attractor: \textit{RC-Bare Noun-Adverb-Verb}. 
-We have used the same verbs, and have not changed the distribution of verb types.
-We also utilized the same or extremely similar adverbials in length.
-We again did not manipulate the number of the head noun and manipulated the number of the attractor.
-Relative clauses we used in this experiment are all object relative clauses and they are all marked with canonical \textit{-dIK} nominalizer.
-Since Turkish is a pro-drop language, we also dropped the subject within the embedded clause, thus ending up with a one-word object relative clause whose head is also the controller of the number agreement on the matrix verb.
+All sentences started with a complex subject NP like \textit{`the cook that they hired'} (\textit{tuttukları aşçı}), in which the verb of the relative clause functioned as the attractor.
+Because the head noun was singular in all conditions, sentences with plural verb agreement were ungrammatical.
+We have used the same verbs, and have not changed the distribution of verb types. We also utilized the same or similar adverbials in length.
+Relative clauses we used in this experiment are all object relative clauses, and they are all marked with canonical \textit{-dIK} nominalizer.
+Since Turkish is a pro-drop language, we also dropped the subject within the embedded clause, thus ending up with a one-word object relative clause whose head is the controller of the number agreement on the matrix verb.
 One example set of experimental items can be seen in \ref{item:exp2ExperimentalItems}.
@@
 \a. \textsc{Plural Attractor, Ungrammatical (Plural Verb)}\label{item:exp2expitem-plpl}\\ 
-  \gll *Tut-tuk-lar-ı aşcı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
-  hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
+  \gll *[Tut-tuk-lar-ı \textbf{aşcı}] mutfak-ta sürekli \textbf{zıpla-dı-lar}.\\ 
+  hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{pst}-\textsc{pl}.\\
   \glt \textit{`The cook that they hired were jumping in the kitchen non-stop.'}
 %
-\b. \textit{Plural Attractor, Grammatical (Singular Verb)}\label{item:exp2expitem-plsg}\\ 
-  \gll Tut-tuk-lar-ı aşcı mutfak-ta sürekli zıpl-ıyor.\\ 
-  hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
+\b. \textsc{Plural Attractor, Grammatical (Singular Verb)}\label{item:exp2expitem-plsg}\\ 
+  \gll [Tut-tuk-lar-ı \textbf{aşcı}] mutfak-ta sürekli \textbf{zıpla-dı}.\\ 
+  hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{pst}.\\
   \glt \textit{`The cook that they hired was jumping in the kitchen non-stop.'}
 %
-\c. \textit{Singular Attractor, Ungrammatical (Plural Verb)}\label{item:exp2expitem-sgpl}\\
-  \gll *Tut-tuğ-u aşcı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
-  hıre-\textsc{nmlz}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
+\c. \textsc{Singular Attractor, Ungrammatical (Plural Verb)}\label{item:exp2expitem-sgpl}\\
+  \gll *[Tut-tuğ-u \textbf{aşcı}] mutfak-ta sürekli \textbf{zıpla-dı-lar}.\\ 
+  hire-\textsc{nmlz}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{pst}-\textsc{pl}.\\
   \glt \textit{`The cook that they hired were jumping in the kitchen non-stop.'}
 %
-\d. \textit{Singular Attractor, Grammatical (Singular Verb)}\label{item:exp2expitem-sgsg}\\ 
-  \gll Tut-tuğ-u aşcı mutfak-ta sürekli zıpl-ıyor.\\ 
-  hıre-\textsc{nmlz}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
+\d. \textsc{Singular Attractor, Grammatical (Singular Verb)}\label{item:exp2expitem-sgsg}\\ 
+  \gll [Tut-tuğ-u \textbf{aşcı}] mutfak-ta sürekli \textbf{zıpla-fı}.\\ 
+  hire-\textsc{nmlz}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{pst}.\\
   \glt \textit{`The cook that they hired was jumping in the kitchen non-stop.'}
 
-In our filler items for Experiment 2, we made sure that every sentence starts with an object relative clause.
-We used plural distractors with grammatical verbs and singular distractors with ungrammatical verbs.
-In all of our filler sentences, the dependency between the first NP subject and its verb resolved in an adverbial embedded sentence.
-Grammatical filler items in Experiment 2 all had a template of
-XXX
-%\textit{RC$_{\textsc{pl}}$-Bare Noun-Adverb-Converb-Noun-Adverb-Verb$_{\textsc{pl}}$}, 
-whereas ungrammatical filler items used a template of 
-XXX
-%\textit{RC$_{\textsc{sg}}$-Bare Noun-Adverb-Converb-Noun-Adverb-Verb$_{\textsc{sg}$}
-
-Again, to avoid a possible strategy where participants use plural ending as a direct indication of ungrammaticality, half of our fillers were with an overt plural marking on a grammatical verb while the other half were without an overt plural marking on an ungrammatical verb.
-We used Turkish pro-drop characteristics which enable participants to form a dependency between the matrix verb and the null subject.
-Example filler sentences can be seen in \ref{item:exp2FillerItems}
+In addition to the experimental items, we used 40 filler sentences of two types, both of which starts with an object relative clause, as illustrated in (\ref{item:exp2FillerItems}).
+Similar to Experiment 1, our filler items included 20 grammatical sentences with an overtly plural marked verbs, and 20 ungrammatical sentences with no overt plural marking, thus singular.
+This was done in order to discourage participants from using a strategy based on verb number. 
+In all of our filler sentences, the dependency between the first complex NP subject modified with an object relative clause and its verb resolved in an adverbial embedded sentence. 
+In grammatical fillers, we have used intransitive verbs with a pro-dropped subject as in (\ref{item:exp2FillerItems_plural}). 
+In ungrammatical fillers, we created the ungrammaticality by placing an adverbial between the bare nominal object and the verb as in (\ref{item:exp2FillerItems_singular}).
 
@@
 %
-\a. \textit{Plural Grammatical Verb}\\ 
+\a. \label{item:exp2FillerItems_plural} \textsc{Grammatical Filler (Plural Verb)}\\ 
   \gll Oku-t-tuk-lar-ı öğrenci başarılı ol-unca mutlu ol-du-lar.\\ 
@@
 %
-\b. \textit{Singular Ungrammatical Verb}\\ 
+\b. \label{item:exp2FillerItems_singular} \textit{Ungrammatical Filler (Singular Verb)}\\ 
   \gll *Kandır-dığ-ı adam öde-me-yince bulaşık saatlerce yıka-dı.\\ 
@@
 
-\subsection{Procedure and Analysis} \label{sec:exp2:procedure_analysis}
+\subsection{Procedure} \label{sec:exp2:procedure}
+
+The experiment was run online, using the web-based platform Ibex Farm (\url{http://spellout.net/ibexfarm/}). For each participant, experiment took approximately 25 minutes to complete.
+Participants were asked to provide information regarding their native language and age. They were also asked for their consent to participate in the experiment.
+Prior to experimental items, participants read the instructions, and were given 9 practice items with feedback on their accuracy.
+Each trial began with a blank screen for 600 ms, followed by a word-by-word RSVP presentantion of the sentence in the center of the screen, followed by an acceptability judgment.
+Sentences were presented in 30pt font size, and at a rate of 400 ms per word.
+Between each word, participants saw a blank screen for 100 ms.
+Participants pressed the key `P' for `\textit{acceptable}' and `Q' for `\textit{unacceptable}'.
+Within instructions, they were told to provide an acceptability rating before 5,000 ms deadline. During the experiment, they were reminded to respondfaster if they did not respond within 5,000 ms.
+
+Participants saw 40 experimental and 40 filler sentences.
+Experimental sentences were distributed among four different lists according to a Latin-square design.
+Every participant saw one version of the experiment with a specific list and one item per condition.
+
+\subsection{Analysis} \label{sec:exp2:analysis}
 
@@
 
-% to-do: some more details.
-% In Experiment 2, the same procedure as Experiment 1 has been followed with regards to how sentences are presented within the experiment.
+In our analysis, we used the items from Experiment 1, as well as the items from Experiment 2.
+this decision was made to answer our hypothesis that whether or not participants use the form of the plural suffix rather than the linguistic features.
+A presence of interaction between the attractor type (\textit{nominal} vs.
+\textit{verbal}) and the agreement attraction effect would indicate that people use the linguistic features rather than the form of the plural suffix.
 
-We analyzed the percentages of 'yes' answers given by the participants in experimental conditions.
-In the analysis of this experiment, we have included experimental items from our Experiments 1 and 2 to check the interaction between experiments and quantify the difference between verbal and nominal plural markers.
-In Experiment 2 as well, we excluded participants (\Sexpr{length(bad_subjects2)}) who had more than 0.25 points of difference in accuracy between grammatical conditions, which implicates that they did not give enough attention to all conditions.
-We used R packages brms \citep{R-brms_b} and rstan \citep{R-stan} to fit Bayesian hierarchical models \citep{GelmanHill:2007}.
-We added our independent variables, i.e.
-grammaticality of the sentence and the overt number information on the distractors, and random variable experiment as a factor.
-Analyses by items and participants are also conducted as a
-part of the Bayesian hierarchical models. Data regarding our experiments and analysis can be found in \texttt{link hidden due to blind review}.
+Similar to Experiment 1, we removed the data for all participants who did not exceed the threshold of 25 percentage points in `yes' responses between the grammatical condition and the ungrammatical condition with singular attractors.
+As a result, we excluded \Sexpr{stopifnot(length(bad_subjects2) == 1)} one participant from the Experiment 2, and \Sexpr{length(bad_subjects)} participant from the Experiment 1.
 
-Across participants, a total \Sexpr{sum(is.na(df_exp2_na_nofillers$ResponseYes))} items were not responded to before the 5 second deadline by \Sexpr{length(unique(df_exp2_na_nofillers$subject))} different participants.
+We used R packages brms \citep{R-brms_b} and rstan \citep{R-stan} to fit Bayesian hierarchical models \citep[e.g.,][]{GelmanHill:2007}.
+We aalyzed only experimental sentences, and used (i) grammaticality of the sentence, (ii) attractor number, and (iii) type of the plural suffix (i.e., experiment), as well as their interactions as predictors.
+Moreover, we used by-participant and by-item intercepts and slopes for all predictors.
+Data for Experiment 2, along with our analysis scripts can be found in \url{https://github.com/utkuturk/orc-attractor_numberattraction}.
+
+%Across participants, a total \Sexpr{sum(is.na(df_exp2_na_nofillers$ResponseYes))} items were not responded to before the 5 second deadline by \Sexpr{length(unique(df_exp2_na_nofillers$subject))} different participants.
 These items were not included in the analysis.
-
-% Should I rephrase these parts?
-%Prior the experiments, participant gave information regarding themselves and a consent to start to the experiment.
-They read the instructions where we showed what they will see in the experiment, what will be going to ask to participants, and where we informed them to be fast and accurate during the experiment.
-Every session started with practice session where participants have been informed being a bit faster when they were not.
-The sentences were presented in the middle of the screen word-by-word on a web-based platform Ibex Farm (\url{http://spellout.net/ibexfarm/}).
-Each word stayed on the screen for 300 ms, unlike \citet{LagoEtAl:2018} and \citet{WagersEtAl:2009} where words stayed for 500 ms in the screen.
-After the sentence is completed, participants were asked "How did they find the sentence?" They were informed to press P on their keyboard for \textit{good} and Q for bad.
-Apart from the practice items, we did not provide any feedback regarding their answer.
-However, participants were asked to be faster when they waited more than 5000 ms to answer the acceptability question.
 
@@
 
-\autoref{fig:exp2AvgResponse} shows the average proportions of 'acceptable' responses by experimental conditions for both Experiment 1 and Experiment 2.
-We see that there is no effect resembling agreement attraction in the ungrammatical conditions of Experiment 2.
-Ungrammatical conditions showed comparable effects (\Sexpr{avg_exp2$resp$M[7]} and \Sexpr{avg_exp2$resp$M[8]} for plural and singular attractors respeectively) regardless of the attractor's number.
+<<curEntries>>=
+
+exp2_cur_entry1 = avg_exp2$resp %>% filter(experiment == "Experiment 2", grammatical == "ungrammatical", attractor_num == "plural")
+exp2_cur_entry2 = avg_exp2$resp %>% filter(experiment == "Experiment 2", grammatical == "ungrammatical", attractor_num == "singular")
+
+exp2_cur_entry3 = avg_exp2$resp %>% filter(experiment == "Experiment 2", grammatical == "grammatical", attractor_num == "singular")
+exp2_cur_entry4 = avg_exp2$resp %>% filter(experiment == "Experiment 2", grammatical == "grammatical", attractor_num == "plural")
+
+@
+
+\autoref{fig:exp2AvgResponse} shows the average proportions of 'acceptable' responses by experimental conditions for Experiment 2. 
+It shows that ungrammatical sentences with plural attractors are rated as acceptable 
+(M = \Sexpr{exp2_cur_entry1$M}, 
+SE = \Sexpr{exp2_cur_entry1$SE}) 
+as their counterparts with singular attractors 
+(M = \Sexpr{exp2_cur_entry2$M}, 
+SE = \Sexpr{exp2_cur_entry2$SE}).
+The lack of effect (\Sexpr{sprintf("%0.2f", exp2_cur_entry1$M-exp2_cur_entry2$M)}) compared to the magnitude of the effect in Experiment 1 (\Sexpr{sprintf("%0.2f", cur_entry1$M-cur_entry2$M)}) indicates that the verbal plural morpheme does not trigger an illusionary agreement.
+%
+Accuracy rates for grammatical conditions were nearly equal
+(M = \Sexpr{exp2_cur_entry3$M} and \Sexpr{exp2_cur_entry4$M}, 
+SE = \Sexpr{exp2_cur_entry3$SE} and \Sexpr{exp2_cur_entry4$SE}, for singular and plural attractors respectively).
 
@@
 @
-
-The observations we made through \autoref{fig:exp2AvgResponse} also surfaces when we look at the estimates and 95\% CIs of a Bayesian GLM in \autoref{fig:exp2ResponseModel}.
-As is visible from the figure, the model shows a negative three-way interaction between grammaticality, type of attractor (nominal vs.
-verbal), and attractor number, which entails a reduced effect of agreement attraction in Experiment 2 compared to Experiment 1.
 
@@
 
+ model2_results_table <- fixef(m_responses2, summary = T, robust = F) %>% 
+  as.data.frame() #%>% tibble::rownames_to_column("variables")
+
  @
+
+A Bayesian GLM assuming a Bernoulli distribution with a probit-link function was fit to participants' `acceptable' responses.
+The model's estimates and 95\% credible intervals are shown in \autoref{fig:exp2ResponseModel}.
+The main effect of \textit{ungrammaticality} (\Sexpr{print_estimate_with_ci( m_responses2, 'cUngrammatical' )}) indicates that, 
+on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences. 
+Meanwhile, there was no evidence for an interaction between \textit{ungrammaticality} and \textit{attractor number} (\Sexpr{print_estimate_with_ci( m_responses2, 'cUngrammatical:cAttractorPlural')}), indicating
+a similar effect of attractor number in ungrammatical conditions compared to grammatical conditions, and thus no number agreement attraction effect.
+Importantly, the negative effect between \textit{the presence of the verbal plural}, \textit{ungrammaticality} and \textit{attractor number} (\Sexpr{print_estimate_with_ci( m_responses2, 'cVerbalAttractor:cUngrammatical:cAttractorPlural')}) indicated that the plural morpheme on the verb of the object relative clause lowered the agreement attraction effects.
 

### 2020-01-21 agremeent_draft_dec17/draft_dec17.tex
Number Check: 1 out of 4

@@
 
+% to-do: This all needs to go up, to the description of the potential confound in Lago et al.'s study.
+%This change was due to the morpho-phonologic nature of possessive suffix in Turkish, which spell-outs as (\textit{-I}) after a consonant same as the accusative.
+
 \section{Experiment 1} \label{sec:exp1}
@@
 We recruited 118 undergraduate students to participate in Experiment 1 in exchange for course credit. All participants were native speakers of Turkish, with an average age of 20 (range: 18 -- 32).  
-These items were not included in the analysis.
-Experiments in this paper were carried out following the Declaration of Helsinki and the regulations concerning ethics at research in Bo\u{g}azi\c{c}i University.
-All participants provided informed consent.
-They were tested online, on IbexFarm.
-%to-do: cite ibexfarm
+Experiment were carried out following the Declaration of Helsinki and the regulations concerning ethics at research in Bo\u{g}azi\c{c}i University.
+All participants provided informed consent prior to their participation.
 
@@
 %
-The main effect of \textit{ungrammaticality} ($\hat{\beta}=-3.09;$ $CI=[-3.35; -2.84];$ $P(\beta<0)> .999$) indicates that, on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences.
-Meanwhile, the positive interaction between \textit{ungrammaticality} and \textit{attractor number} ($\hat{\beta}=0.72;$ $CI=[0.42; 1.02];$ $P(\beta<0)< .001$) indicated a larger effect of attractor number in ungrammatical conditions, and thus a number agreement attraction effect.
-Importantly, there was no evidence for a three-way interaction between \textit{the presence of ambiguity}, \textit{ungrammaticality} and \textit{attractor number} ($\hat{\beta}=0.30;$ $CI=[-0.20; 0.79];$ $P(\beta<0)=    .12$).
+The main effect of \textit{ungrammaticality} ($\hat{\beta}=-3.09;$ $CI=[-3.34; -2.85];$ $P(\beta<0)> .999$) indicates that, on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences.
+Meanwhile, the positive interaction between \textit{ungrammaticality} and \textit{attractor number} ($\hat{\beta}=0.72;$ $CI=[0.41; 1.02];$ $P(\beta<0)< .001$) indicated a larger effect of attractor number in ungrammatical conditions, and thus a number agreement attraction effect.
+Importantly, there was no evidence for a three-way interaction between \textit{the presence of ambiguity}, \textit{ungrammaticality} and \textit{attractor number} ($\hat{\beta}=0.31;$ $CI=[-0.21; 0.83];$ $P(\beta<0)=    .12$).
 
@@
 
-We recruited 79 native speakers of Turkish to participate in Experiment 2. Their average age was 21, ranging from 18 to 31.
-
-Experiments in this paper were carried out following the Declaration of Helsinki and the regulations concerning ethics in research in Bo\u{g}azi\c{c}i University.
-All participants provided informed consent.
-They were tested online, on IbexFarm, using their preferred platform, % Find citation for using IbexFarm and online testing etc?
+We recruited 79 undergraduate students to participate in Experiment 2 in exchange for course credit. All participants were native speakers of Turkish, with an average age of 21 (range: 18 - 31). 
+Experiment were carried out following the Declaration of Helsinki and the regulations concerning ethics at research in Bo\u{g}azi\c{c}i University.
+All participants provided informed consent prior to their participation.
 
@@
 
-\subsection{Procedure and Analysis} \label{sec:exp2:procedure_analysis}
+\subsection{Procedure} \label{sec:exp2:procedure}
 
-% to-do: some more details.
-% In Experiment 2, the same procedure as Experiment 1 has been followed with regards to how sentences are presented within the experiment.
+The experiment was run online, using the web-based platform Ibex Farm (\url{http://spellout.net/ibexfarm/}). For each participant, experiment took approximately 25 minutes to complete.
+Participants were asked to provide information regarding their native language and age. They were also asked for their consent to participate in the experiment.
+Prior to experimental items, participants read the instructions, and were given 9 practice items with feedback on their accuracy.
+Each trial began with a blank screen for 600 ms, followed by a word-by-word RSVP presentantion of the sentence in the center of the screen, followed by an acceptability judgment.
+Sentences were presented in 30pt font size, and at a rate of 400 ms per word.
+Between each word, participants saw a blank screen for 100 ms.
+Participants pressed the key `P' for `\textit{acceptable}' and `Q' for `\textit{unacceptable}'.
+Within instructions, they were told to provide an acceptability rating before 5,000 ms deadline. During the experiment, they were reminded to respondfaster if they did not respond within 5,000 ms.
 
-We analyzed the percentages of 'yes' answers given by the participants in experimental conditions.
-In the analysis of this experiment, we have included experimental items from our Experiments 1 and 2 to check the interaction between experiments and quantify the difference between verbal and nominal plural markers.
-In Experiment 2 as well, we excluded participants (1) who had more than 0.25 points of difference in accuracy between grammatical conditions, which implicates that they did not give enough attention to all conditions.
-We used R packages brms \citep{R-brms_b} and rstan \citep{R-stan} to fit Bayesian hierarchical models \citep{GelmanHill:2007}.
-We added our independent variables, i.e.
-grammaticality of the sentence and the overt number information on the distractors, and random variable experiment as a factor.
-Analyses by items and participants are also conducted as a
-part of the Bayesian hierarchical models. Data regarding our experiments and analysis can be found in \texttt{link hidden due to blind review}.
+Participants saw 40 experimental and 40 filler sentences.
+Experimental sentences were distributed among four different lists according to a Latin-square design.
+Every participant saw one version of the experiment with a specific list and one item per condition.
 
-Across participants, a total 55 items were not responded to before the 5 second deadline by 45 different participants. These items were not included in the analysis.
+\subsection{Analysis} \label{sec:exp2:analysis}
 
-% Should I rephrase these parts?
-%Prior the experiments, participant gave information regarding themselves and a consent to start to the experiment.
-They read the instructions where we showed what they will see in the experiment, what will be going to ask to participants, and where we informed them to be fast and accurate during the experiment.
-Every session started with practice session where participants have been informed being a bit faster when they were not.
-The sentences were presented in the middle of the screen word-by-word on a web-based platform Ibex Farm (\url{http://spellout.net/ibexfarm/}).
-Each word stayed on the screen for 300 ms, unlike \citet{LagoEtAl:2018} and \citet{WagersEtAl:2009} where words stayed for 500 ms in the screen.
-After the sentence is completed, participants were asked "How did they find the sentence?" They were informed to press P on their keyboard for \textit{good} and Q for bad.
-Apart from the practice items, we did not provide any feedback regarding their answer.
-However, participants were asked to be faster when they waited more than 5000 ms to answer the acceptability question.
+In our analysis, we used the items from Experiment 1, as well as the items from Experiment 2.
+this decision was made to answer our hypothesis that whether or not participants use the form of the plural suffix rather than the linguistic features.
+A presence of interaction between the attractor type (\textit{nominal} vs.
+\textit{verbal}) and the agreement attraction effect would indicate that people use the linguistic features rather than the form of the plural suffix.
+
+Similar to Experiment 1, we removed the data for all participants who did not exceed the threshold of 25 percentage points in `yes' responses between the grammatical condition and the ungrammatical condition with singular attractors.
+As a result, we excluded  one participant from the Experiment 2, and 10 participant from the Experiment 1.
+
+We used R packages brms \citep{R-brms_b} and rstan \citep{R-stan} to fit Bayesian hierarchical models \citep[e.g.,][]{GelmanHill:2007}.
+We aalyzed only experimental sentences, and used (i) grammaticality of the sentence, (ii) attractor number, and (iii) type of the plural suffix (i.e., experiment), as well as their interactions as predictors.
+Moreover, we used by-participant and by-item intercepts and slopes for all predictors.
+Data for Experiment 2, along with our analysis scripts can be found in \url{https://github.com/utkuturk/orc-attractor_numberattraction}.
+
+%Across participants, a total sum(is.na(df_exp2_na_nofillers$ResponseYes)) items were not responded to before the 5 second deadline by length(unique(df_exp2_na_nofillers$subject)) different participants.
+These items were not included in the analysis.
 
@@
 
-\autoref{fig:exp2AvgResponse} shows the average proportions of 'acceptable' responses by experimental conditions for both Experiment 1 and Experiment 2.
-We see that there is no effect resembling agreement attraction in the ungrammatical conditions of Experiment 2.
-Ungrammatical conditions showed comparable effects (0.05 and 0.06 for plural and singular attractors respeectively) regardless of the attractor's number.
+\autoref{fig:exp2AvgResponse} shows the average proportions of 'acceptable' responses by experimental conditions for Experiment 2. 
+It shows that ungrammatical sentences with plural attractors are rated as acceptable 
+(M = 0.05, 
+SE = 0.01) 
+as their counterparts with singular attractors 
+(M = 0.06, 
+SE = 0.01). The lack of effect (-0.01) compared to the magnitude of the effect in Experiment 1 (0.10) indicates that the verbal plural morpheme does not trigger an illusionary agreement.
+%
+Accuracy rates for grammatical conditions were nearly equal
+(M = 0.91 and 0.94, 
+SE = 0.01 and 0.01, for singular and plural attractors respectively).
 
@@
 
-The observations we made through \autoref{fig:exp2AvgResponse} also surfaces when we look at the estimates and 95\% CIs of a Bayesian GLM in \autoref{fig:exp2ResponseModel}.
-As is visible from the figure, the model shows a negative three-way interaction between grammaticality, type of attractor (nominal vs.
-verbal), and attractor number, which entails a reduced effect of agreement attraction in Experiment 2 compared to Experiment 1.
+A Bayesian GLM assuming a Bernoulli distribution with a probit-link function was fit to participants' `acceptable' responses.
+The model's estimates and 95\% credible intervals are shown in \autoref{fig:exp2ResponseModel}.
+The main effect of \textit{ungrammaticality} ($\hat{\beta}=-3.41;$ $CI=[-3.63; -3.19];$ $P(\beta<0)> .999$) indicates that, 
+on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences. 
+Meanwhile, there was no evidence for an interaction between \textit{ungrammaticality} and \textit{attractor number} ($\hat{\beta}=-0.03;$ $CI=[-0.33; 0.25];$ $P(\beta<0)=    .58$), indicating 
+a similar effect of attractor number in ungrammatical conditions compared to grammatical conditions, and thus no number agreement attraction effect.
+Importantly, the negative effect between \textit{the presence of the verbal plural}, \textit{ungrammaticality} and \textit{attractor number} ($\hat{\beta}=-1.07;$ $CI=[-1.53; -0.61];$ $P(\beta<0)> .999$) indicated that the plural morpheme on the verb of the object relative clause lowered the agreement attraction effects.
 

### 2020-02-07 agremeent_draft_dec17/draft_dec17.Rnw
Added simpler by-experiment analyses.

@@
 
+fname_exp1_responses_exp1only <- "../workspace_exp1/fit_responses_exp1only"
+m_responses_exp1only <- brm(ResponseYes ~ cUngrammatical * cAttractorPlural + 
+                                 (cUngrammatical * cAttractorPlural + 1| subject) + 
+                                 (cUngrammatical * cAttractorPlural + 1| item),
+                   data = df_merged_nofillers %>% subset(experiment == "Experiment 1"),
+                   family = bernoulli("probit"), 
+                   chains = n_chains, cores = n_cores, iter = n_iter,
+                   file = fname_exp1_responses_exp1only)
+
+fname_exp1_responses_Lagoonly <- "../workspace_exp1/fit_responses_Lagoonly"
+m_responses_Lagoonly <- brm(ResponseYes ~ cUngrammatical * cAttractorPlural + 
+                                 (cUngrammatical * cAttractorPlural + 1| subject) + 
+                                 (cUngrammatical * cAttractorPlural + 1| item),
+                   data = df_merged_nofillers %>% subset(experiment != "Experiment 1"),
+                   family = bernoulli("probit"), 
+                   chains = n_chains, cores = n_cores, iter = n_iter,
+                   file = fname_exp1_responses_Lagoonly)
+
 fname_exp1_rts <- "../workspace_exp1/fit_responses_rt"
@@
 
-<<exp1ResponseModel, fig.cap='Estimates and 95\\% credible intervals for the regression coefficients for Experiment 1.', fig.height=3, fig.align='center'>>=
+<<exp1ResponseModel, fig.cap='Estimates and 95\\% credible intervals for the regression coefficients for the model of Experiment 1 and Lago et al. (2018).', fig.height=3, fig.align='center'>>=
 contrast_names <- c("cUngrammatical" = "Ungrammaticality",
@@
 print(p_m_response + annotate(x=-3, xend=2, y=0, yend=0, lwd=0.25, geom="segment"))
+})
+
+@
+
+<<exp1ResponseModelSepExp1, fig.cap='Estimates and 95\\% credible intervals for the regression coefficients for Experiment 1.', fig.height=1.5, fig.align='center'>>=
+contrast_names_exp1 <- c("cUngrammatical" = "Experiment 1: Ungrammaticality",
+                         "cAttractorPlural" = "Experiment 1: Plural Attactor",
+                         "cUngrammatical:cAttractorPlural" = "Experiment 1: Ungrammaticality * Plural Attractor"
+                        )
+
+p_m_response_exp1 <- 
+  create_model_coefs_plot( m_responses_exp1only, 
+        plot_stats = T, map_names = contrast_names_exp1,
+        expand_right = 2.5, expand_top = 2, x_stat_adjust = 1.1,
+        x_breaks = c(-3,-2,-1, 0,1, 2) ) + 
+        xlab("Estimate (probit)")
+
+suppressWarnings({
+print(p_m_response_exp1 + annotate(x=-3, xend=2, y=0, yend=0, lwd=0.25, geom="segment"))
+})
+
+contrast_names_lago <- c("cUngrammatical" = "Lago et al.: Ungrammaticality",
+                         "cAttractorPlural" = "Lago et al.: Plural Attactor",
+                         "cUngrammatical:cAttractorPlural" = "Lago et al.: Ungrammaticality * Plural Attractor"
+                        )
+
+@
+
+<<exp1ResponseModelSepExp2, fig.cap='Estimates and 95\\% credible intervals for the regression coefficients for Lago et al. (2018).', fig.height=1.5, fig.align='center'>>=
+p_m_response_lago <- 
+  create_model_coefs_plot( m_responses_Lagoonly, 
+        plot_stats = T, map_names = contrast_names_lago,
+        expand_right = 2.5, expand_top = 2, x_stat_adjust = 1.1,
+        x_breaks = c(-3,-2,-1, 0,1, 2) ) + 
+        xlab("Estimate (probit)")
+
+suppressWarnings({
+print(p_m_response_lago + annotate(x=-3, xend=2, y=0, yend=0, lwd=0.25, geom="segment"))
 })
@@
 
-# avg_clean2 <- df_merged2 %>%
-#                 group_by(experiment, source, grammatical, attractor_num) %>%
-#                 summarize(avgRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T))
-# # XXX
-
 avg_clean2 <- list()
@@
 
+library(brms)
+
 fname_exp2_responses <- "../workspace_exp2/fit_responses"
-
-library(brms)
-
-# TODO: Data seems to contain NAs in relevant columns; fix it
 m_responses2 <- brm(ResponseYes ~ cVerbalAttractor * cUngrammatical * cAttractorPlural + 
@@
 
+fname_exp2only_responses <- "../workspace_exp2/fit_responses_exp2only"
+m_responses2_exp2only <- brm(ResponseYes ~ cUngrammatical * cAttractorPlural + 
+                                 (cUngrammatical * cAttractorPlural + 1| subject) +
+                                 (cUngrammatical * cAttractorPlural + 1| item),
+                   data = df_merged_nofillers2 %>% 
+                              subset(!is.na(ResponseYes)) %>% 
+                              subset(experiment == "Experiment 2"),
+                   family = bernoulli("probit"),
+                   file = fname_exp2only_responses, 
+                   chains = n_chains, cores = n_cores, iter = n_iter)
+
  model2_results_table <- fixef(m_responses2, summary = T, robust = F) %>% 
@@
 
-<<exp2ResponseModel, fig.cap='Estimates and 95\\% credible intervals for the regression coefficients for Experiment 2', fig.height=3, fig.align='center'>>=
+<<exp2ResponseModel, fig.cap='Estimates and 95\\% credible intervals for the regression coefficients for a model of Experiment 1 and Experiment 2.', fig.height=3, fig.align='center'>>=
 
@@
 print(p_m_response_exp2)
+@
+
+<<exp2ResponseModelExp2Only, fig.cap='Estimates and 95\\% credible intervals for the regression coefficients for Experiment 2.', fig.height=1.5, fig.align='center'>>=
+
+p_m_response_exp2_exp2only <- 
+  create_model_coefs_plot( m_responses2_exp2only, 
+        plot_stats = T, map_names = contrast_names2_le,
+        expand_right = 4.5, expand_top = 1.5, x_stat_adjust = .75,
+        x_breaks = c(-3,-2,-1, 0, 1) ) + 
+        xlab("Estimate (probit)")
+
+p_m_response_exp2only <- p_m_response_exp2_exp2only + annotate(x=-3, xend=1, y=0, yend=0, lwd=0.25, geom="segment")
+print(p_m_response_exp2only)
 

### 2020-02-07 agremeent_draft_dec17/draft_dec17.tex
Added simpler by-experiment analyses.

@@
 %
-The main effect of \textit{ungrammaticality} ($\hat{\beta}=-3.09;$ $CI=[-3.34; -2.85];$ $P(\beta<0)> .999$) indicates that, on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences.
-Meanwhile, the positive interaction between \textit{ungrammaticality} and \textit{attractor number} ($\hat{\beta}=0.72;$ $CI=[0.41; 1.02];$ $P(\beta<0)< .001$) indicated a larger effect of attractor number in ungrammatical conditions, and thus a number agreement attraction effect.
-Importantly, there was no evidence for a three-way interaction between \textit{the presence of ambiguity}, \textit{ungrammaticality} and \textit{attractor number} ($\hat{\beta}=0.31;$ $CI=[-0.21; 0.83];$ $P(\beta<0)=    .12$).
+The main effect of \textit{ungrammaticality} ($\hat{\beta}=-3.09;$ $CI=[-3.35; -2.84];$ $P(\beta<0)> .999$) indicates that, on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences.
+Meanwhile, the positive interaction between \textit{ungrammaticality} and \textit{attractor number} ($\hat{\beta}=0.72;$ $CI=[0.42; 1.02];$ $P(\beta<0)< .001$) indicated a larger effect of attractor number in ungrammatical conditions, and thus a number agreement attraction effect.
+Importantly, there was no evidence for a three-way interaction between \textit{the presence of ambiguity}, \textit{ungrammaticality} and \textit{attractor number} ($\hat{\beta}=0.30;$ $CI=[-0.20; 0.79];$ $P(\beta<0)=    .12$).
 
@@
 
-\caption[Estimates and 95\% credible intervals for the regression coefficients for Experiment 1]{Estimates and 95\% credible intervals for the regression coefficients for Experiment 1.}\label{fig:exp1ResponseModel}
+\caption[Estimates and 95\% credible intervals for the regression coefficients for the model of Experiment 1 and Lago et al]{Estimates and 95\% credible intervals for the regression coefficients for the model of Experiment 1 and Lago et al.
+(2018).}\label{fig:exp1ResponseModel}
+\end{figure}
+
+\end{knitrout}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+
+{\centering \includegraphics[width=\maxwidth]{figure/exp1ResponseModelSepExp1-1}
+
+}
+
+\caption[Estimates and 95\% credible intervals for the regression coefficients for Experiment 1]{Estimates and 95\% credible intervals for the regression coefficients for Experiment 1.}\label{fig:exp1ResponseModelSepExp1}
+\end{figure}
+
+\end{knitrout}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+
+{\centering \includegraphics[width=\maxwidth]{figure/exp1ResponseModelSepExp2-1}
+
+}
+
+\caption[Estimates and 95\% credible intervals for the regression coefficients for Lago et al]{Estimates and 95\% credible intervals for the regression coefficients for Lago et al.
+(2018).}\label{fig:exp1ResponseModelSepExp2}
 \end{figure}
@@
 The model's estimates and 95\% credible intervals are shown in \autoref{fig:exp2ResponseModel}.
-The main effect of \textit{ungrammaticality} ($\hat{\beta}=-3.41;$ $CI=[-3.63; -3.19];$ $P(\beta<0)> .999$) indicates that, 
+The main effect of \textit{ungrammaticality} ($\hat{\beta}=-3.09;$ $CI=[-3.31; -2.88];$ $P(\beta<0)> .999$) indicates that, 
 on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences. 
-Meanwhile, there was no evidence for an interaction between \textit{ungrammaticality} and \textit{attractor number} ($\hat{\beta}=-0.03;$ $CI=[-0.33; 0.25];$ $P(\beta<0)=    .58$), indicating 
+Meanwhile, there was no evidence for an interaction between \textit{ungrammaticality} and \textit{attractor number} ($\hat{\beta}=0.06;$ $CI=[-0.18; 0.30];$ $P(\beta<0)=    .30$), indicating 
 a similar effect of attractor number in ungrammatical conditions compared to grammatical conditions, and thus no number agreement attraction effect.
-Importantly, the negative effect between \textit{the presence of the verbal plural}, \textit{ungrammaticality} and \textit{attractor number} ($\hat{\beta}=-1.07;$ $CI=[-1.53; -0.61];$ $P(\beta<0)> .999$) indicated that the plural morpheme on the verb of the object relative clause lowered the agreement attraction effects.
+Importantly, the negative effect between \textit{the presence of the verbal plural}, \textit{ungrammaticality} and \textit{attractor number} ($\hat{\beta}=-0.94;$ $CI=[-1.31; -0.57];$ $P(\beta<0)> .999$) indicated that the plural morpheme on the verb of the object relative clause lowered the agreement attraction effects.
 
@@
 
-\caption[Estimates and 95\% credible intervals for the regression coefficients for Experiment 2]{Estimates and 95\% credible intervals for the regression coefficients for Experiment 2}\label{fig:exp2ResponseModel}
+\caption[Estimates and 95\% credible intervals for the regression coefficients for a model of Experiment 1 and Experiment 2]{Estimates and 95\% credible intervals for the regression coefficients for a model of Experiment 1 and Experiment 2.}\label{fig:exp2ResponseModel}
+\end{figure}
+
+\end{knitrout}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+
+{\centering \includegraphics[width=\maxwidth]{figure/exp2ResponseModelExp2Only-1}
+
+}
+
+\caption[Estimates and 95\% credible intervals for the regression coefficients for Experiment 2]{Estimates and 95\% credible intervals for the regression coefficients for Experiment 2.}\label{fig:exp2ResponseModelExp2Only}
 \end{figure}

### 2020-02-21 agremeent_draft_dec17/le_poster.R
Renamed paper draft file.

@@ -1,56 +1,0 @@
-
-
-if (exists("le_poster")) {
-  p_avg_resp <- avg_exp$resp %>% subset(experiment == "Experiment 1") %>%
-    ggplot(aes(grammatical, M, #linetype = attractor_num, 
-               color = attractor_num, group = attractor_num)) + 
-    geom_point() + geom_line() + theme( strip.background = element_rect(fill="white")) +
-    facet_wrap(~experiment)
-  
-  p_avg_resp <- p_avg_resp + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1)
-  
-  # p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) + 
-  #                             geom_point(data = avg_fillers) + 
-  
-  p_avg_resp <- p_avg_resp + theme( strip.background = element_rect(fill="white") ) +
-    theme_bw() + xlab("") + ylab("Percentage 'acceptable'")
-  p_avg_resp <- p_avg_resp + scale_y_continuous(labels=scales::percent, limits = c(0,1))#, breaks = c(0, .25, .5, .75, 1))
-  p_avg_resp <- p_avg_resp + theme_bw()
-  p_avg_resp <- p_avg_resp + scale_color_discrete(name = "Attractor Number")
-  ggsave(filename = "./plots_le/exp1.jpeg", p_avg_resp, height = 2.5, width = 2.5*2)
-}
-
-
-if (exists("le_poster"))
-{
-  fname_exp1_responses <- "../workspace_exp1/model_responses_justexp1"
-  m_responses_exp1 <- brm(ResponseYes ~ cUngrammatical * cAttractorPlural + 
-                            (cUngrammatical * cAttractorPlural + 1| subject) +
-                            (cUngrammatical * cAttractorPlural + 1| item),
-                          data = df_merged_nofillers %>% subset(experiment == "Experiment 1"),
-                          family = bernoulli("probit"),
-                          file = fname_exp1_responses, 
-                          chains = n_chains, cores = n_cores, iter = n_iter)
-  
-}
-if (exists("le_poster"))
-{
-  p_m_response_exp1 <- 
-    create_model_coefs_plot( m_responses_exp1, 
-                             plot_stats = T, map_names = contrast_names,
[…]

### 2020-02-23 text/paper_draft.rnw
Updated models for experiment 1 and changed the text location.

--- 2020-02-07 agremeent_draft_dec17/draft_dec17.Rnw
@@
 
+# to-do: check that the CI-computation code is up-to-date
 source("../scripts/misc.R")
@@
 ### note: the low accuracy on fillers is not caused by a couple of items
+###       -> see below
 # filler_avgs <- 
@@
 # map to our condition labels
-lagoetal_condition_mapping <- data.frame(
-    condition = c("a", "b", "c", "d"),
+lagoetal_condition_mapping <- data.frame( condition = c("a", "b", "c", "d"),
                                           lagoetal_condition = c("d", "b", "c", "a"), 
                                           stringsAsFactors = F)
-
 df_lagoetal_attr %<>% left_join( lagoetal_condition_mapping, by = "lagoetal_condition" )
@@
                                     mutate(delta_dc = online_d - online_c)
+
+# identify bad participants 
+bad_subjects <- subset(avg_by_subj_wide, delta_dc <= 0.25 ) %>% .$subject
+data_exp1_clean <- data_exp1 %>% subset(!subject %in% bad_subjects)
+
+# identify bad participants 
+bad_subjects_lagoetal <- subset(avg_by_subj_lagoetal_wide, delta_dc <= 0.25 ) %>% .$subject
+df_lagoetal_attr_clean <- df_lagoetal_attr %>% subset(!subject %in% bad_subjects_lagoetal)
+
+# merge both datasets
+df_merge_exp1 <- data_exp1_clean %>% ungroup() %>% 
+                      dplyr::select(source=experiment, 
+                                    grammatical, 
+                                    attractor_num,
+                                    # condition,
+                                    subject, 
+                                    item=Item,
+                                    ResponseYes, 
+                                    RT)
+df_merge_exp1$experiment <- "Experiment 1"
+df_merge_exp1$grammatical %<>% dplyr::recode(gram="grammatical", ungram="ungrammatical")
+df_merge_exp1$attractor_num %<>% dplyr::recode(pl="plural", sg="singular")
+
+df_merge_exp1$item %<>% as.integer()
+df_merge_exp1$subject %<>% as.character()
+
+df_merge_lago <- df_lagoetal_attr_clean %>%
+                      ungroup() %>% 
+                      dplyr::select(grammatical, attractor_num,
+                                    subject, item, ResponseYes, RT)
+df_merge_lago$experiment <- "Lago et al. (2018)" 
+df_merge_lago$source <- NA
+
 word_freq <- readxl::read_excel("../Data/frequencies_exp1_and_lago.xlsx", sheet = 1)
@@
 word_freq %<>% dplyr::group_by(exp) %>% 
-               dplyr::mutate( cat_n1 = ifelse(n1 > median(n1), "high", "low"),
-                              cat_n2 = ifelse(n2 > median(n2), "high", "low"),
+               dplyr::mutate( freq_cat_n1 = ifelse(n1 > median(n1), "high", "low"),
+                              freq_cat_n2 = ifelse(n2 > median(n2), "high", "low"),
                               freqlog_n1 = scale(log(n1)),
@@
                 ungroup()
-word_freq$cat_n1 %<>% as.factor()
-word_freq$cat_n2 %<>% as.factor()
-
-word_freq_exp1 <- word_freq %>% 
-                    subset(exp == "up") %>% 
-                    dplyr::select(-exp)
-word_freq_lago <- word_freq %>% 
-                    subset(exp == "lago") %>% 
-                    dplyr::select(-exp)
-
-# identify bad participants 
-bad_subjects <- subset(avg_by_subj_wide, delta_dc <= 0.25 ) %>% .$subject
-data_exp1_clean <- data_exp1 %>% subset(!subject %in% bad_subjects)
-
-# identify bad participants 
-bad_subjects_lagoetal <- subset(avg_by_subj_lagoetal_wide, delta_dc <= 0.25 ) %>% .$subject
-df_lagoetal_attr_clean <- df_lagoetal_attr %>% subset(!subject %in% bad_subjects_lagoetal)
-df_merge_exp1 <- data_exp1_clean %>% ungroup() %>% 
-                      dplyr::select(source=experiment, 
-                                    grammatical, attractor_num,
-                                    # condition,
-                                    subject, item=Item,
-                                    ResponseYes, RT)
-df_merge_exp1$experiment <- "Experiment 1"
-df_merge_exp1$grammatical <- with(df_merge_exp1, 
-                                  ifelse(grammatical == "gram", 
-                                          "grammatical",
-                                          "ungrammatical"))
-df_merge_exp1$attractor_num <- with(df_merge_exp1, 
-                                    ifelse(attractor_num == "pl",
-                                           "plural", 
-                                           "singular"))
-df_merge_exp1$item %<>% as.integer()
-df_merge_exp1$subject %<>% as.character()
-#df_merge_exp1 %<>% left_join(word_freq_exp1, by = "item")
-
-df_merge_lago <- df_lagoetal_attr_clean %>%
-                      ungroup() %>% 
-                      dplyr::select(grammatical, attractor_num,
-                                    subject, item, ResponseYes, RT)
-#df_merge_lago %<>% left_join(word_freq_lago, by = "item")
-df_merge_lago$experiment <- "Lago et al. (2018)" 
-df_merge_lago$source <- NA
+# word_freq$freq_cat_n1 %<>% as.factor()
+# word_freq$freq_cat_n2 %<>% as.factor()
+
+word_freq_exp1 <- word_freq %>% subset(exp == "exp1") %>% dplyr::select(-exp)
+df_merge_exp1 %<>% left_join(word_freq_exp1, by = "item")
+
+word_freq_lago <- word_freq %>% subset(exp == "lagoetal") %>% dplyr::select(-exp)
+df_merge_lago %<>% left_join(word_freq_lago, by = "item")
 df_merge_lago$item %<>% add(1000)
@@
 As a result, we excluded \Sexpr{length(bad_subjects)} participants from experiment 1, and \Sexpr{stopifnot(length(bad_subjects_lagoetal) == 1)} one participant from the Lago et al.
-experiment.
+data
 
@@
 fname_exp1_responses_exp1only <- "../workspace_exp1/fit_responses_exp1only"
-m_responses_exp1only <- brm(ResponseYes ~ cUngrammatical * cAttractorPlural + 
-                                 (cUngrammatical * cAttractorPlural + 1| subject) + 
+m_responses_exp1only <- brm(ResponseYes ~ cUngrammatical * cAttractorPlural * freqlog_n1n2 + 
+                                 (cUngrammatical * cAttractorPlural * freqlog_n1n2 + 1| subject) + 
                                  (cUngrammatical * cAttractorPlural + 1| item),
@@
                    family = bernoulli("probit"), 
-                   chains = n_chains, cores = n_cores, iter = n_iter,
-                   file = fname_exp1_responses_exp1only)
-
-fname_exp1_responses_Lagoonly <- "../workspace_exp1/fit_responses_Lagoonly"
-m_responses_Lagoonly <- brm(ResponseYes ~ cUngrammatical * cAttractorPlural + 
-                                 (cUngrammatical * cAttractorPlural + 1| subject) + 
+                   chains = n_chains, cores = n_cores, iter = n_iter, init_r = .1,
+                   file = fname_exp1_responses_exp1only
+                   )
+
+fname_exp1_responses_Lagoonly <- "../workspace_exp1/fit_responses_lagoonly"
+m_responses_Lagoonly <- brm(ResponseYes ~ cUngrammatical * cAttractorPlural * freqlog_n1n2 + 
+                                 (cUngrammatical * cAttractorPlural * freqlog_n1n2 + 1| subject) + 
                                  (cUngrammatical * cAttractorPlural + 1| item),
@@
                    family = bernoulli("probit"), 
-                   chains = n_chains, cores = n_cores, iter = n_iter,
+                   chains = n_chains, cores = n_cores, iter = n_iter, init_r = .1,
                    file = fname_exp1_responses_Lagoonly)
@@
 fname_exp1_rts <- "../workspace_exp1/fit_responses_rt"
-m_rts <- brm(RT ~ cEndsInConsonant * cUngrammatical * cAttractorPlural +
-                                 (cUngrammatical * cAttractorPlural + 1| subject) +
+m_rts <- brm(RT ~ cEndsInConsonant * cUngrammatical * cAttractorPlural * freqlog_n1n2 +
+                                 (cUngrammatical * cAttractorPlural * freqlog_n1n2 + 1| subject) +
                                  (cUngrammatical * cAttractorPlural + 1| item),
@@
 suppressWarnings({
-print(p_m_response + annotate(x=-3, xend=2, y=0, yend=0, lwd=0.25, geom="segment"))
+print(p_m_response + annotate(x=-3, xend=2, y=0, yend=0, lwd=0.25, geom="segment") + facet_wrap(~"Experiment 1 and Lago et al. (2018)"))
 })
@@
 
-<<exp1ResponseModelSepExp1, fig.cap='Estimates and 95\\% credible intervals for the regression coefficients for Experiment 1.', fig.height=1.5, fig.align='center'>>=
-contrast_names_exp1 <- c("cUngrammatical" = "Experiment 1: Ungrammaticality",
-                         "cAttractorPlural" = "Experiment 1: Plural Attactor",
-                         "cUngrammatical:cAttractorPlural" = "Experiment 1: Ungrammaticality * Plural Attractor"
+<<exp1ResponseModelSepExp1AndLago, fig.cap='Estimates and 95\\% credible intervals for the regression coefficients for Experiment1 and Lago et al. (2018).', fig.height=5, fig.align='center'>>=
+
+contrast_names_exp1 <- c("cUngrammatical" = "Ungrammaticality",
+                         "cAttractorPlural" = "Plural Attactor",
+                         "freqlog_n1n2"="log Frequency: N1-N2",
+                         "cUngrammatical:freqlog_n1n2" = "Ungrammaticality * log Frequency: N1-N2",
+                         "cAttractorPlural:freqlog_n1n2" = "Plural Attactor * log Frequency: N1-N2",
+                         "cUngrammatical:cAttractorPlural" = "Ungrammaticality * Plural Attractor",
+                         "cUngrammatical:cAttractorPlural:freqlog_n1n2" = "Ungrammaticality * Plural Attractor * log Frequency: N1-N2"
                         )
@@
 
-suppressWarnings({
-print(p_m_response_exp1 + annotate(x=-3, xend=2, y=0, yend=0, lwd=0.25, geom="segment"))
-})
-
-contrast_names_lago <- c("cUngrammatical" = "Lago et al.: Ungrammaticality",
-                         "cAttractorPlural" = "Lago et al.: Plural Attactor",
-                         "cUngrammatical:cAttractorPlural" = "Lago et al.: Ungrammaticality * Plural Attractor"
-                        )
-
-@
-
-<<exp1ResponseModelSepExp2, fig.cap='Estimates and 95\\% credible intervals for the regression coefficients for Lago et al. (2018).', fig.height=1.5, fig.align='center'>>=
+p_m_response_exp1 <- p_m_response_exp1 + facet_wrap(~"Experiment 1") + annotate(x=-3, xend=2, y=0, yend=0, lwd=0.25, geom="segment")
+
 p_m_response_lago <- 
   create_model_coefs_plot( m_responses_Lagoonly, 
-        plot_stats = T, map_names = contrast_names_lago,
+        plot_stats = T, map_names = contrast_names_exp1,
         expand_right = 2.5, expand_top = 2, x_stat_adjust = 1.1,
@@
 
+p_m_response_lago <- p_m_response_lago + facet_wrap(~"Lago et al. (2018)") + annotate(x=-3, xend=2, y=0, yend=0, lwd=0.25, geom="segment")
+
+p_m_response_exp1_and_lago <- ggarrange(p_m_response_exp1, p_m_response_lago, ncol = 1)
+
 suppressWarnings({
-print(p_m_response_lago + annotate(x=-3, xend=2, y=0, yend=0, lwd=0.25, geom="segment"))
+print(p_m_response_exp1_and_lago)
 })

### 2020-09-01 ongoing_draft/ongoing_paper.Rmd
yet another directory cuz I suck at gitdiff

--- 2020-02-23 text/paper_draft.rnw
@@
-\documentclass[doc,a4paper,man,natbib,floatsintext,noextraspace]{apa6}
-<<echo=F>>=
-# Set the global chunk options
-set.seed(42)
-knitr::opts_chunk$set(encoding = 'UTF-8',
-                      cache.extra = knitr::rand_seed,
-                      echo = F,
-                      results = 'hide',
-                      message = F,
-                      warning = F)
-options("citation_format" = "pandoc")
-@
-
-<<setup, echo=FALSE, cache=FALSE>>=
-## numbers >= 10^5 will be denoted in scientific notation,
-## and rounded to 2 digits
-options(scipen = 1, digits = 2)
-@
-
-\usepackage[english]{babel}
-\usepackage[utf8x]{inputenc}
-\usepackage{amsmath}
-\usepackage{amsthm}
-\usepackage{graphicx}
-\usepackage[colorinlistoftodos]{todonotes}
-\usepackage[singlespacing]{setspace}
-
-<<>>=
-
-# load packages
-library(patchSynctex)
+---
+title             : "Agreement Attraction in Turkish"
+shorttitle        : "Agreement Attraction in Turkish"
+author: 
+  - name          : "Utku Türk"
+    affiliation   : "1"
+    corresponding : yes    # Define only one corresponding author
+    address       : "Postal address"
+    email         : "utku.turk@boun.edu.tr"
+affiliation:
+  - id            : "1"
+    institution   : "Boğaziçi University University, Istanbul, Turkey"
+authornote: |
+  authornote
+abstract: |
+  We report the results of two speeded acceptability judgment experiments in Turkish.
+We hypothesized an alternative explanation for agreement attraction effects in Turkish that is based on shallow processing.
+Our findings contradict our hypothesized form-driven processing strategy and support an account of agreement attraction based on the use of abstract linguistic features, rather than mere form.
+keywords          : "keywords"
+wordcount         : "X"
+bibliography      : ["new-references.bib","r-references.bib"]
+floatsintext      : yes
+figurelist        : no
+tablelist         : no
+numbersections    : yes
+geometry          : left=25mm, right=25mm, top=25mm, bottom=25mm
+#fontsize          : 10pt
+footnotelist      : no
+linenumbers       : no
+mask              : no
+draft             : no
+documentclass     : "apa6"
+classoption       : "doc"
+output:
+  papaja::apa6_pdf:
+    latex_engine: xelatex
+    includes:
+        in_header: paper_draft_preamble.tex
+editor_options: 
+  chunk_output_type: console
+keep_tex: FALSE
+keep_md: FALSE
+---
+
+```{r setup, eval =T, include = FALSE, message=FALSE, warning=FALSE}
+library("papaja")
 library(knitcitations)
-library(car, warn.conflicts = FALSE)
+library(tidyverse)
+library(magrittr)
+library(ggplot2)
+theme_set(theme_bw())
+
+library(car, warn.conflicts = FALE)
 library(MASS)
@@
 library(ggpubr)
+
 library(languageR)
@@
 library(gdata)
+library(MASS)
 library(magrittr)
 library(ggplot2)
-theme_set(theme_bw())
-
-# to-do: check that the CI-computation code is up-to-date
+
 source("../scripts/misc.R")
 
-@
-\title{The Role of Shallow Processing in Agreement Attraction}
-\shorttitle{Your APA6-Style Manuscript}
-\author{Utku Türk, Pavel Loga\v{c}ev}
-\affiliation{Boğaziçi University}
-
-\abstract{We report the results of two speeded acceptability judgment experiments in Turkish.
-We hypothesized an alternative explanation for agreement attraction effects in Turkish that is based on shallow processing.
-Our findings contradict our hypothesized form-driven processing strategy and support an account of agreement attraction based on the use of abstract linguistic features, rather than mere form.}
-
-\input{settings.tex}
-
-\begin{document}
-
-\maketitle
-
-\section{Introduction} \label{sec:Intro}
-
-% %\footnote{\printglossaries}. % add this to somewhere in the first page I suppose
-% 
-% \subsection{Agreement Attraction Thingy} \label{sec:Intro:literature}
-% 
-% \subsubsection{Morphophonology} \label{sec:Intro:literature:morphophonology}
-% 
-% %fill here accordingly to your results AFTER YOU WRITE THE RESULT.
-% 
-% 
-% \subsubsection{related sub-sub-field studies} \label{sec:Intro:literature:others}
-% 
-% \subsubsection{This work details} \label{sec:Intro:literature:thiswork}
-
-% \citet{LagoEtAl:2018} hypothesize that genitive NPs can trigger agreement attraction in Turkish, because Turkish makes heavy use of genitive subjects, which means genitives are a priori likely to function as agreement controllers.
-The underlying assumption is that agreement processes rely on, at least partially, the case of an NP to determine its fit for the role of an agreement controller.
-% If that is so, their items are problematic %as in ... give an example
-% in that the marking on the head noun is ambiguous between possessive and accusative case, while only possessive-marked NPs qualify as agreement controllers.
-Therefore, if engaged in shallow processing, readers may be more likely to misidentify the genitive NP as the agreement controller when the head noun, which is the only other alternative, is ambiguous, compared to when it is not.
-
-% In Experiment 1, we decided to test this hypothesis
-
-% to-do: This all needs to go up, to the description of the potential confound in Lago et al.'s study.
-%This change was due to the morpho-phonologic nature of possessive suffix in Turkish, which spell-outs as (\textit{-I}) after a consonant same as the accusative.
-
-\section{Experiment 1} \label{sec:exp1}
-
-% do not do this in one chunk. differentiate the chunks and give them proper names.
-<<>>=
+```
+
+```{r analysis-preferences, eval =T, message=FALSE, warning=FALSE}
+# Seed for random number generation
+set.seed(42)
+knitr::opts_chunk$set(encoding = 'UTF-8',
+                      cache.extra = knitr::rand_seed,
+                      echo = FALSE,
+                      results = 'asis')
+options("citation_format" = "pandoc")
+
+```
+
+# Introduction
+
+It has been observed that speakers often fail to accurately process grammatical dependencies between the parts of a sentence [@GibsonThomas:1999; @PhillipsEtAl:2011]. 
+For example, ungrammatical center-embedded structures like  *The patient who the nurse who the clinic had hired met Jack* are found grammatical by native English speakers. 
+One such comprehension error is agreement attraction [@Nicoletal:1997; @PearlmutterGarnseyBock:1999; @WagersEtAl:2009]. 
+Speakers may erroneously find sentences acceptable in which the verb erroneously agrees with a syntactically unrelated noun phrase (*the attractor*) instead of the subject (*the agreement controller*) as in \@ref(item:wagers2009).
+
+\begin{exe}
+\ex \label{item:wagers2009} * The key to the cells are rusty from many years of disuse. 
+\end{exe}
+
+<!-- for some reason I could not add citation in the examples. \hfill \footnotesize{[@WagersEtAl:2009]} -->
+
+These effects were found to be robust in a variety of constructions in different languages, e.g.
+English , German , Russian, Arabic, Spanish, Armenian, Slovak, Greek, and Turkish [@LagoEtAl2018; @LagoEtAl:2015; @ReifegersteEtAl:2016; @BadeckerKuminiak:2007; @TuckerEtAl:2015; @PaspaliMarinis:2020; @AvetisyanEtAl:2020] using structures like object relative clauses, subject relative clauses, possessive relative clauses, and genitive-possessive noun phrases [@LagoEtAl2018; @WagersEtAl:2009; @LagoEtAl:2015; @FranckColonnaRizzi:2015; @TuckerEtAl:2015; @ParkerEtAl:2015; @Dillon2013a; @Haussler2009].
+These effects are found both in grammatical marking of the gender and the number [@BadeckerKuminiak:2007; @Slioussar:2016; @PaspaliMarinis:2020], and attested with various methods including maze tasks, ERP, eye tracking to name a few [@TannerEtAl:2014; @WagersEtAl:2009; @Nicoletal:1997].
+
+One instance of agreement attraction is found in the production processes in which participants were asked to complete sentence fragments [@Bock1991].
+Participants used the wrong verb more often when the attractor (*cabinets*) were plural, and the agreement controller (*key*) were singular as in \@ref(item:bock1991).
+
+\begin{exe}
+\ex The key to the cabinets \ldots 
+\label{item:bock1991}
+\end{exe}
+
+Agreement attraction is also found in the comprehension studies.
+In these studies, agreement attraction is found either as a facilitation in reading times or as a effect in the acceptability rates [@WagersEtAl:2009].
+When reading times are checked, they found that the participants read the ungrammatical sentences with a plural attractor easier then the ungrammatical sentences without a plural attractor. 
+Similarly, participants found ungrammatical sentences with a plural attractor acceptable more often than that of with a singular attractor.
+
+Some theories [@EberhardEtAl:2005; @HammerlyEtAl:2019] explain this phenomenon through a faulty representation of the number on the head of the agreement controller whereas other theories assume that agreement attraction is due to an error in the access to the number of the agreement controller [@WagersEtAl:2009; @NicenboimEtAl:2018].
+
+Agreement attraction effects can equally well be explained by assuming shallow processing.
+Recent studies in psychology literature show that in certain environments people may not notice ungrammaticalities in a sentence or may not compute dependencies in a sentence completely [@OteroKintsch:1992; @FerreiraBaileyFerraro:2002].
+
+To investigate this possibility, we report two speeded acceptability judgment experiments in this paper.
+The first one inspects the recent @LagoEtAl2018 findings.
+They found number attraction effects in genitive-possessive constructions such as `_[[the child's] toy]_' ([[_çocuğ-un\textsubscript{Gen}_] _oyuncağ-ı\textsubscript{Poss}_]).
+They justify the use of this construction with the findings of @NicolEtAl:2016.
+Since the genitive case is a possible subject marker, the participants can consider genitive marked attractors a candidate for the agreement controller.
+However, case marking on all subject heads is locally ambiguous the accusative and the possessive.
+In our experiment 1, we disambiguate the subject head and test whether or not the results were due to the shallow processing of the head subject and sticking with the accusative marked representation under some conditions.
+
+In experiment 2, we test whether or not the agreement attraction effects in Turkish are due to form-driven processing strategy.
+Instead of processing the whole sentence, participants develop a mental shortcut, matching the form-identical number marking on the attractor and the matrix verb in the Turkish case, specific to the task in hand.
+We used the verbs of the object relative clauses as an attractor and speculated that if the participants are using the mentioned task-specific strategy, we would see comparable agreement attraction effects.
+
+This paper is organized as \ldots
+
+# Theories of agreement attraction
+
+The difference between the theories that explain the agreement attraction phenomenon lies in the assumption regarding the origin of the illusion.
+Some theories [@BockEberhard:1993; @ViglioccoEtAl:1995; @Eberhard:1997; @FranckEtAl:2002; @BergenGibson:2012] explain this phenomenon by hypothesizing that the representations formed from the linguistic input is faulty.
+One theory in this group is Marking and Morphing Theory.
+MMT suggests that the subject phrase can hold a continuous number value from 1 (unambiguously plural) to -1 (unambiguously singular).
+This value is affected by the _percolation_ of the grammatical feature which can happen in any direction.
+The implementation of such models suggests that the final number of the phrase depends on the number morphology on the head and the elements within the phrase, and the syntactic proximity of these elements to the root node of the phrase.
+
+Another type of model within this family is based on the idea that linguistic input is noisy, and it is accompanied by a priori linguistic knowledge [@BergenGibson:2012].
+This account is an extension of the noisy channel model proposed by @Levy2008, which uses Bayesian inference to model the participants' inference given the word string.
+@PatsonHusband:2016 provide additional evidence for this type of analysis by showing that final interpretations of agreement attraction cases are not based on the actual string, meaning that the participants infer a plural-marked head noun whereas it is not marked by any plural inflection.
+
+On the other side, some theories assume that agreement attraction is due to an error in the access to the number of the agreement controller [@WagersEtAl:2009; @NicenboimEtAl:2018].
+Unlike MMT, these models do not assume an erroneous representation to form.
+Rather, the agreement attraction effects surface when there is a feature interference in the ungrammatical sentences like \@ref(item:wagers2009).
+This interference is triggered due to the partial match between the sought retrieval cues and the ones within the subject phrase.
+On some occasions, when there is no single item matching the necessary cues from the verb, number related matching cue from the attractor may satisfy the retrieval.
+
+# Agreement Attraction in Turkish
+
+Recently, @LagoEtAl2018 demonstrated comparable agreement attraction effects in comprehension with Turkish stimuli. 
+They used the speeded acceptability judgment method with the following question that asks participants whether or not the sentence sounded acceptable. 
+They used sentences like (\@ref(item:LagoExp))\footnote{Abbreviations used in the paper are as follows: \printglossaries} with genitive-marked attractors.
+They manipulated the number morphology on the attractor (plural x singular) and the grammaticality of the verb (grammatical (SG) x ungrammatical (PL)).
+The example given here represents all four conditions.
+In an ungrammatical condition with a plural attractor, the word _ressamların_ (painters') is expected to create a grammaticality illusion and mistaken for the agreement controller instead of the head subject _rakibi_ (rival\textsubscript{poss}).
+
+\begin{exe}
+\ex \label{item:LagoExp}
+\gll Ressam-$\emptyset$/lar-(n){\i}n rakib-i at\"{o}lye-den h{\i}zla uzakla\c{s}-t{\i}-$\emptyset$/lar.\\
+painter-\Sg{}/\Pl{}-\Gen{} rival-\Poss{} workshop-\Abl{} quickly walked.away-\Pst{}-\Sg{}/\Pl{}\\
+\glt `The painter's/painters' rival walked\textsubscript{sg/pl} away from the workshop quickly.'
+\end{exe}
+
+Following previous work on agreement attraction, they
+argue
+that non-intervening genitive marked attractor may create grammaticality illusions in Turkish.
+They base their argument on the inhibition constraint proposed by @NicolEtAl:2016.
+@NicolEtAl:2016 show in a production experiment that genitive attractors do not trigger grammaticality illusions.
+According to their hypothesis, the reason behind their results is the fact that the participants may never consider genitive-marked NPs as a potential candidate for subjects.
+However, this is not the case in Turkish.
+In embedded sentences, the definite subject is always marked with the genitive case, which makes the genitive-marked NPs a candidate for the subjecthood in Turkish.
+
+However, a potential complication in interpreting these results is the fact that all head nouns in Lago et al.'s stimuli were morphologically ambiguous between possessive and accusative case.
+This ambiguity is the result of the consonant-ending subject head usage.
+In Turkish, both the accusative case and the possessive surface as -I.
+\footnote{Throughout the paper, we present the archiphonemes with the capitalized form of the symbol.
+The suffix -I can surface as \textit{-i, -ı, -u, -ü}.
+}
+Because of this local ambiguity, all experimental sentences have two possible parses up until to the end of the sentence.
+Check the following examples in \@ref(parse:LagoExpAcc) and \@ref(parse:LagoExpPoss).
+
+\begin{exe}
+\ex \label{parse:LagoExpAcc}
+\gll [\textsubscript{CP}[\textsubscript{CP}Ressam-lar-{\i}n rakib-i at\"{o}lye-den h{\i}zla uzakla\c{s}-t{\i}ğ-{\i}n-{\i}] bil-iyor-um.]\\
+painter-\Pl{}-\Gen{} rival-\Acc{} workshop-\Abl{} quickly walked.away-\Nmlz{}-\Poss{}-\Acc{} know-\Prog{}-\Fsg{}.\\
+\glt `I know that the painters' rival walked away from the workshop quickly.'
+\ex \label{parse:LagoExpPoss}
+\gll [\textsubscript{CP}Ressam-lar-{\i}n rakib-i at\"{o}lye-den h{\i}zla uzakla\c{s}-t{\i}.]\\
+painter-\Pl{}-\Gen{} rival-\Poss{} workshop-\Abl{} quickly walked.away-\Pst.\Tsg{}.\\
+\glt `the painters' rival walked away from the workshop quickly.'
+\end{exe}
+
+The local ambiguity between the accusative and the possessive is not resolved until the verb _uzaklaştı_.
+Regardless of the assumption for parallel or serial processing, there may exist certain conditions where participants are stuck with a rival-\Acc{} representation.
+Since accusative number agreement controllers are extremely rare, while genitive agreement controllers are very frequent in Turkish, the ambiguity of the head noun may occasionally render the genitive modifier a stronger contender for being the agreement controller, resulting in agreement attraction.
+The problem with such cases for the Inhibition hypothesis is that it is not clear whether the possible non-subjecthood clue from the accusative case plays a role or the possible subjecthood clue from the genitive case plays a role.
+
+# Experiment 1
+
+```{r Exp1:DataWrangling, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
 
@@
 
+```
+
+```{r Exp1:wordFreq, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+# word frequencies: 
+# Utku: are these still relevant for us?
+
 word_freq <- readxl::read_excel("../Data/frequencies_exp1_and_lago.xlsx", sheet = 1)
@@
 df_merged$item %<>% as.factor()
-
-df_exp1_na_nofillers <- subset(df_merge_exp1, is.na(ResponseYes) & source != "filler")
-df_merged %<>% subset( !is.na(ResponseYes) )
-
-@
-
-In Experiment 1, we tested whether speakers of Turkish make fewer agreement attraction errors when the local ambiguity in the head noun is resolved. 
-Specifically, we tried to replicate \citet{LagoEtAl:2018} study.
-However, instead of using morphologically ambiguous head nouns, we uses nouns ending in a vowel, thus resolving the ambiguity between the accusative and possessive.
-
-\subsection{Participants} \label{sec:exp1:participants}
+```
+
+Previous work in agreement attraction found significant effects in comprehension using forced-choice acceptability judgment tasks [@HammerlyEtAl:2019; @LagoEtAl2018; @WagersEtAl:2009].
+The goal of experiment 1 is to control for the effect of head noun ambiguity on the magnitude of agreement attraction effect.
+To this end, we replicated @LagoEtAl2018 experiment with unambiguous head nouns.
+We disambiguated the cases by using vowel-ending head nouns.
+When attached to a vowel-ending noun, the accusative case and the possessive surface with a different floating consonant.
+For example, we changed sentence (\@ref(item:LagoExpContrast)) to sentence (\@ref(item:OurExpContrast)).
+
+\begin{exe}
+\ex \label{item:LagoExpContrast}
+\gll Şarkıcı-$\emptyset$/lar-(n)ın vokalist-i sahne-de sürekli zıpla-dı-$\emptyset$/lar.\\
+singer-\Sg{}/\Pl{}\Gen{} vocalist-\Poss{} stage-\Loc{} non-stop jump-\Pst{}-\Sg{}/\Pl{}\\
+\glt `The singer's/singers' backup vocalist jumped\textsubscript{sg/pl} on the stage non-stop.'
+
+\ex \label{item:OurExpContrast}
+\gll Yönetici-$\emptyset$/ler-(n)in aşçı-sı mutfak-de sürekli zıpla-dı-$\emptyset$/lar.\\
+manager-\Sg{}/\Pl{}\Gen{} cook-\Poss{} kitchen-\Loc{} non-stop jump-\Pst{}-\Sg{}/\Pl{}\\
+\glt `The manager's/managers' cook jumped\textsubscript{sg/pl} in the kitchen non-stop.'
+\end{exe}
+
+We hypothesized that if the morpho-phonological ambiguity, thus the Inhibition from the accusative case, was a key factor in agreement attraction in Turkish, resolving it should diminish the attraction affects.
+This would tell us that readers may indeed get affected by local ambiguities which may serve as a supporting point for shallow processing.
+
+## Participants
 
 We recruited 118 undergraduate students to participate in Experiment 1 in exchange for course credit.
-All participants were native speakers of Turkish, with an average age of \Sexpr{round(mean(form_exp1$Age))} (range: \Sexpr{min(form_exp1$Age)} -- \Sexpr{max(form_exp1$Age)}).
+All participants were native speakers of Turkish, with an average age of `r printnum(mean(form_exp1$Age))` (range: `r min(form_exp1$Age)` -- `r max(form_exp1$Age)`).
 Experiment were carried out following the Declaration of Helsinki and the regulations concerning ethics at research in Bo\u{g}azi\c{c}i University.
@@
 
-\subsection{Materials} \label{sec:exp1:materials}
-
-We used 40 sets of sentences like (\ref{item:exp1ExperimentalItems}), in which we manipulated 
+## Materials
+
+We used 40 sets of sentences like \@ref(item:exp1ExperimentalItems), in which we manipulated 
 (i) the number of the attractor noun, and
@@
 Plural number and plural agreement were both marked with the affix \textit{-ler/-lar}, while singular number and singular agreement were marked with its absence. 
-%
-We have used the experimental items in \citet{LagoEtAl:2018} as a base. 
-All sentences started with a complex subject NP like \textit{`the manager's cook'} (\textit{yöneticinin aşcısı}), in which the possessor, which functioned as the attractor, carried genitive case, and the head noun carried possessive case.
+We have used the experimental items in @LagoEtAl2018 as a base. 
+All sentences started with a complex subject NP like \textit{`the manager's cook'} (\textit{yöneticinin aşcısı}), in which the possessor, which functioned as the attractor, carried genitive case, and the head noun carried unambiguous possessive case.
 Because the head noun was singular in all conditions, sentences with plural verb agreement were ungrammatical. 
 Moreover, as in the original study, the properties of the nouns in the complex subject NP and the relation between these nouns held constant in our replication. 
-The distribution of the verb types followed the same pattern as in \citet{LagoEtAl:2018}, namely twenty unergatives, eighteen unaccusatives, and two optionally transitive verbs. 
-Both in \citet{LagoEtAl:2018} and in our replication, pre-verbal adverbials consisting of 2-3 words (15 characters on average) are used.
-Unlike the \citet{LagoEtAl:2018} sentences, our head nouns were vowel-ending, and therefore not ambiguous between accusative case, for which the case suffix is \textit{-yI}, and possessive case, for which the suffix is \textit{-sI}.
-
-\ex. \label{item:exp1ExperimentalItems}
-%
-\a. \textsc{Plural Attractor, Ungrammatical (Plural Verb)} \label{item:exp1expitem-plpl}\\ 
+The distribution of the verb types followed the same pattern as in @LagoEtAl2018, namely twenty unergatives, eighteen unaccusatives, and two optionally transitive verbs. 
+Both in @LagoEtAl2018 and in our replication, pre-verbal adverbials consisting of 2-3 words (15 characters on average) are used.
+We changed this adverbials for plausability reasons, such that with head nouns like cooks we used locational adverbs like kitchen, instead of the stage.
+Unlike the @LagoEtAl2018 sentences, our head nouns were vowel-ending, and therefore not ambiguous between accusative case, for which the case suffix is \textit{-yI}, and possessive case, for which the suffix is \textit{-sI}.
+
+\begin{exe}
+\ex \label{item:exp1ExperimentalItems}
+  \begin{xlist}
+
+  \ex \textsc{Plural Attractor, Ungrammatical (Plural Verb)} \label{item:exp1expitem-plpl} 
   \gll *[Yönetici-ler-in \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpla-dı-lar}.\\ 
@@
   \glt \textit{`The cooks of the manager were jumping in the kitchen non-stop.'}
-%
-\b. \textsc{Plural Attractor, Grammatical (Singular Verb)} \label{item:exp1expitem-plsg}\\ 
+
+\ex \textsc{Plural Attractor, Grammatical (Singular Verb)} \label{item:exp1expitem-plsg} 
   \gll [Yönetici-ler-in \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpla-dı}.\\ 
@@
   \glt \textit{`The cooks of the manager was jumping in the kitchen non-stop.'}
-%
-\c. \textsc{Singular Attractor, Ungrammatical (Plural Verb)} \label{item:exp1expitem-sgpl}\\ 
+
+\ex \textsc{Singular Attractor, Ungrammatical (Plural Verb)} \label{item:exp1expitem-sgpl} 
   \gll *[Yönetici-nin \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpla-dı-lar}.\\ 
@@
   \glt \textit{`The cook of the manager were jumping in the kitchen non-stop.'}
-%
-\d. \textsc{Singular Attractor, Grammatical (Singular Verb)}\label{item:exp1expitem-sgsg}\\ 
+
+\ex \textsc{Singular Attractor, Grammatical (Singular Verb)}\label{item:exp1expitem-sgsg}
   \gll [Yönetici-nin \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpla-dı}. \\ 
@@
   \glt \textit{`The cook of the manager was jumping in the kitchen non-stop.'}
-
-We intermixed our experimental sentences with 40 filler sentences of two types, as illustrated in (\ref{item:exp1FillerItems}). 
+  \end{xlist}
+\end{exe}
+
+We intermixed our experimental sentences with 40 filler sentences of two types, as illustrated in \@ref(item:exp1FillerItems). 
 To compensate for the fact that among experimental sentences, all ungrammatical sentences ended in a plural-agreeing verb, while all grammatical sentences ended in a singular-agreeing verb, we included 20 grammatical sentences with plural verbs, and 20 ungrammatical sentences with singular agreement.
@@
 However, in filler items, they were the controller of an embedded clause which serves as a adverbial. 
-In grammatical fillers, we have made use of pro-dropped subject strategy in Turkish; thus, it enabled us to use plural verb without having ungrammatical sentences as in (\ref{item:exp1GrammaticalFiller}).
+In grammatical fillers, we have made use of pro-dropped subject strategy in Turkish; thus, it enabled us to use plural verb without having ungrammatical sentences as in \@ref(item:exp1GrammaticalFiller).
 The object \textit{tutarsızlık} is a bare nominal preceding a light verb construction.
@@
 
-%Even though filler items did not follow a strict template as the experimental items, they were created within a template of \textit{Noun$_{{\textsc{gen}}}$-Noun$_{{\textsc{gen}}}$-Converb-Noun-Adverb-Verb}.
-The ungrammaticality was created non-locally in the filler items to avoid task strategies.
-Example filler sentences can be seen in \ref{item:exp1FillerItems}.
-
-\ex. \label{item:exp1FillerItems}
-%
-\a. \label{item:exp1GrammaticalFiller} \textsc{Grammatical Filler (Plural Verb)}\\ 
-  \gll [Sosyolog-un \textbf{öğrenci-si}] konuş-unca tutarsızlık açığ-a \textbf{çıkar-dı-lar}.\\ %utku: what does this bold mean?
-if it the dependency between them then the bold parts are not correct.
-ogrencisi is the subject of the verb konusunca, and the subject of the matrix verb cikardilar is omitted.
+\begin{exe}
+\ex \label{item:exp1FillerItems}
+\begin{xlist}
+\ex \textsc{Grammatical Filler (Plural Verb)} \label{item:exp1GrammaticalFiller}
+\gll [Sosyolog-un \textbf{öğrenci-si}] konuş-unca tutarsızlık açığ-a \textbf{çıkar-dı-lar}.\\ 
 sociolog-\textsc{gen}  student-\textsc{poss} speak-\textsc{nmlz} inconsistency  open-\textsc{dat} deduct-\textsc{pst}-\textsc{pl}.\\
 \glt \textit{`When the student of the sociologist spoke, they revealed an inconsistency.'}
-%to-do: Translation above doesn't make sense.
-%
-%
-\b. \textsc{Ungrammatical Filler (Singular Verb)}\\ 
-\gll *[Dansöz-ün \textbf{koca-sı}] var-ınca kapı sakince \textbf{aç-tı}.\\ 
+
+\ex \textsc{Ungrammatical Filler (Singular Verb)}
+\gll *[Dansöz-ün \textbf{koca-sı}] var-ınca kapı sakince \textbf{aç-tı}. \\
 dancer-\textsc{gen}  husband-\textsc{poss} arrive-\textsc{nmlz} door slowly  open-\textsc{pst}.\\
 \glt \textit{Intended:`When the husband of the dancer came, the door opened slowly.'}
-% to-do: Does the above mean that it's grammatical with another meaning?
-
-\subsection{Procedure} \label{sec:exp1:procedure}
+\end{xlist}
+\end{exe}
+
+## Procedure
 
 The experiment was run online, using the web-based platform Ibex Farm (\url{http://spellout.net/ibexfarm/}). Each experimental session took approximately 25 minutes to complete.
-%
+
 Prior to the start of the experiment, participants provided demographic information, as well as informed consent to participate in the experiment.
 They read the instructions, and were given 9 practice trials before the experiment began.
-%
+
 Each trial began with a blank screen for 600 ms, followed by a word-by-word RSVP presentation of the sentence in the center of the screen, followed by an acceptability judgment. 
@@
 
-\subsection{Analysis} \label{sec:exp1:analysis}
-
-Since our aim was to test whether the morphological ambiguity present in the \citet{LagoEtAl:2018} items affected the presence or magnitude of the agreement attraction effect, statistically, we needed to test for the presence of an interaction between
+## Analysis
+
+Since our aim was to test whether the morphological ambiguity present in the @LagoEtAl2018 items affected the presence or magnitude of the agreement attraction effect, statistically, we needed to test for the presence of an interaction between
 (i) the presence of the morphological ambiguity on the head noun, and 
@@
 
-%All experimental trials from both experiments (Experiment 1 and  Lago et al.'s study) was included in the analysis.
-
 Prior to analysis we removed the data for all participants who failed to show sufficient sentitivity to the effect of grammaticality in singular attractor conditions, i.e., when no agreement attraction was expected.
-Specifically, we removed all participants for whom the difference in the percentage of `yes' responses between the grammatical condition \ref{item:exp1expitem-sgsg} and the ungrammatical condition \ref{item:exp1expitem-sgpl} was below the threshold of 25 percentage points.
-As a result, we excluded \Sexpr{length(bad_subjects)} participants from experiment 1, and \Sexpr{stopifnot(length(bad_subjects_lagoetal) == 1)} one participant from the Lago et al.
+Specifically, we removed all participants for whom the difference in the percentage of 'yes' responses between the grammatical condition \@ref(item:exp1expitem-sgsg) and the ungrammatical condition \@ref(item:exp1expitem-sgpl) was below the threshold of 25 percentage points.
+As a result, we excluded `r length(bad_subjects)` participants from experiment 1, and `r stopifnot(length(bad_subjects_lagoetal) == 1)` one participant from the Lago et al.
 data
 
-We used the R packages brms \citep{R-brms_b} and rstan \citep{R-stan} to fit Bayesian hierarchical models \citep[e.g.,][]{GelmanHill:2007}. We analyzed only experimental sentences, and used 
+We used the R packages brms [@brms] and rstan [@stan] to fit Bayesian hierarchical models [e.g., @GelmanHill2007]. We analyzed only experimental sentences, and used 
 (i) grammaticality of the sentence, 
@@
 
-\subsection{Results} \label{sec:exp1:results}
-
-<<>>=
+## Results
+
+```{r Exp1:PreparePlots, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+df_exp1_na_nofillers <- subset(df_merge_exp1, is.na(ResponseYes) & source != "filler")
+df_merged %<>% subset( !is.na(ResponseYes) )
 
@@
 
-@
-
-<<>>=
 avg_exp_resp_exp1 <- avg_exp$resp %>% subset(experiment == "Experiment 1")
 avg_exp_resp_lagoetal <- avg_exp$resp %>% subset(experiment == "Lago et al. (2018)")
-
-@
-
-\autoref{fig:exp1AvgResponse} shows the average proportions of ‘acceptable’ responses by experimental condition for both the original experiment in \citet{LagoEtAl:2018} and our replication with unambiguous possessive marking.
-\Sexpr{ 
-cur_entry1 = avg_exp$resp %>% filter(experiment == "Experiment 1", grammatical == "ungrammatical", attractor_num == "plural");
-cur_entry2 = avg_exp$resp %>% filter(experiment == "Experiment 1", grammatical == "ungrammatical", attractor_num == "singular") }%
+```
+
+```{r Exp1:PrepareTextInputs, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+exp1_cur_entry1 = avg_exp$resp %>% filter(experiment == "Experiment 1", grammatical == "ungrammatical", attractor_num == "plural")
+exp1_cur_entry2 = avg_exp$resp %>% filter(experiment == "Experiment 1", grammatical == "ungrammatical", attractor_num == "singular")
+
+exp1_cur_entry3 = avg_exp$resp %>% filter(experiment == "Experiment 1", grammatical == "grammatical", attractor_num == "singular")
+exp1_cur_entry4 = avg_exp$resp %>% filter(experiment == "Experiment 1", grammatical == "grammatical", attractor_num == "plural")
+
+lago_cur_entry1 = avg_exp$resp %>% filter(experiment == "Lago et al. (2018)", grammatical == "ungrammatical", attractor_num == "plural")
+lago_cur_entry2 = avg_exp$resp %>% filter(experiment == "Lago et al. (2018)", grammatical == "ungrammatical", attractor_num == "singular")
+```
+
+Figure \@ref(fig:exp1AvgResponse) shows the average proportions of ‘acceptable’ responses by experimental condition for both the original experiment in @LagoEtAl2018 and our replication with unambiguous possessive marking.
 It shows that ungrammatical sentences with plural attractors are rated as acceptable more often
-(M = \Sexpr{cur_entry1$M}, 
-SE = \Sexpr{cur_entry1$SE}) 
+(M = `r printnum(exp1_cur_entry1$M)`, 
+SE = `r printnum(exp1_cur_entry1$SE)`) 
 than their counterparts with singular attractors 
-(M=\Sexpr{cur_entry2$M}, 
-SE=\Sexpr{cur_entry2$SE}).
-%
-\Sexpr{ 
-cur_entry1lago = avg_exp$resp %>% filter(experiment == "Lago et al. (2018)", grammatical == "ungrammatical", attractor_num == "plural");
-cur_entry2lago = avg_exp$resp %>% filter(experiment == "Lago et al. (2018)", grammatical == "ungrammatical", attractor_num == "singular") }%
-%This means that ungrammatical sentences with plural attractors were classified as acceptable more often than their counterparts with singular attractors. 
-The magnitude of the effect (\Sexpr{sprintf("%0.2f", cur_entry1$M-cur_entry2$M)}) was in line with the findings reported in \citet{LagoEtAl:2018}, where the difference was \Sexpr{sprintf("%0.2f", cur_entry1lago$M-cur_entry2lago$M)}.
-% 
+(M=`r printnum(exp1_cur_entry2$M)`, 
+SE=`r printnum(exp1_cur_entry2$SE)`).
+The magnitude of the effect (`r sprintf("%0.2f", exp1_cur_entry1$M-exp1_cur_entry2$M)`) was in line with the findings reported in @LagoEtAl2018, where the difference was `r sprintf("%0.2f", lago_cur_entry1$M-lago_cur_entry2$M)`.
 Accuracy rates for grammatical conditions were nearly equal
-\Sexpr{ 
-cur_entry3 = avg_exp$resp %>% filter(experiment == "Experiment 1", grammatical == "grammatical", attractor_num == "singular");
-cur_entry4 = avg_exp$resp %>% filter(experiment == "Experiment 1", grammatical == "grammatical", attractor_num == "plural"); }%
-(M = \Sexpr{cur_entry3$M} and \Sexpr{cur_entry4$M}, SE = \Sexpr{cur_entry3$SE} and \Sexpr{cur_entry4$SE}, for singular and plural attractors respectively).
-
-<<exp1AvgResponse, fig.cap='Average percentages of `acceptable\' responses in Experiment 1 and \\citet{LagoEtAl:2018}.
-Within-subject 95\\% confidence intervals in brackets \\cite{Cousineau:2005,Morey:2008}.', fig.height=3, fig.align='center'>>=
+(M = `r printnum(exp1_cur_entry3$M)` and `r printnum(exp1_cur_entry4$M)`, SE = `r printnum(exp1_cur_entry3$SE)` and `r printnum(exp1_cur_entry4$SE)`, for singular and plural attractors respectively).
+
+```{r exp1AvgResponse, fig.height=3 ,fig.cap="Average response times for experiment 1 and experiment 2."}
 print(p_avg_resp)
-
-@
-
-<<exp1models, include=FALSE>>=
-
+```
+
+A Bayesian GLM assuming a Bernoulli distribution with a probit-link function was fit to participants' `acceptable' responses.
+The model's estimates and 95\% credible intervals are shown in Figure \@ref(fig:exp1ResponseModel).
+<!-- They confirm the observations we stated above: the positive interaction between sentence grammaticality and attractor number is in line with a larger effect of attractor number in ungrammatical sentences.
+-->
+
+```{r Exp1:BayesianModels, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
 df_merged %<>% within(., {
@@
 
-@
-
-A Bayesian GLM assuming a Bernoulli distribution with a probit-link function was fit to participants' `acceptable' responses.
-The model's estimates and 95\% credible intervals are shown in \autoref{fig:exp1ResponseModel}.
-%
-%They confirm the observations we stated above: the positive interaction between sentence grammaticality and attractor number is in line with a larger effect of attractor number in ungrammatical sentences.
-%
-The main effect of \textit{ungrammaticality} (\Sexpr{print_estimate_with_ci( m_responses, 'cUngrammatical' )}) indicates that, on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences.
-Meanwhile, the positive interaction between \textit{ungrammaticality} and \textit{attractor number} (\Sexpr{print_estimate_with_ci( m_responses, 'cUngrammatical:cAttractorPlural')}) indicated a larger effect of attractor number in ungrammatical conditions, and thus a number agreement attraction effect.
-Importantly, there was no evidence for a three-way interaction between \textit{the presence of ambiguity}, \textit{ungrammaticality} and \textit{attractor number} (\Sexpr{print_estimate_with_ci( m_responses, 'cEndsInConsonant:cUngrammatical:cAttractorPlural')}).
-
-% to-do:
-% Importantly, even if there was an interaction with experiment, it's relatively small, so it wouldn't reduce the other interaction to 0.
-
-%Moreover, this findings are also predicted by cue-based retrieval models \citep{engelmann2019effect, vasishth2019computational} and last rendition of marking and morphing theory by \citet{HammerlyEtAl:2019}.
-%does it tho?
+```
+
+The main effect of \textit{ungrammaticality} (`r print_estimate_with_ci( m_responses, 'cUngrammatical' )`) indicates that, on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences.
+Meanwhile, the positive interaction between \textit{ungrammaticality} and \textit{attractor number} (`r print_estimate_with_ci( m_responses, 'cUngrammatical:cAttractorPlural')`) indicated a larger effect of attractor number in ungrammatical conditions, and thus a number agreement attraction effect.
+Importantly, there was no evidence for a three-way interaction between \textit{the presence of ambiguity}, \textit{ungrammaticality} and \textit{attractor number} (`r print_estimate_with_ci( m_responses, 'cEndsInConsonant:cUngrammatical:cAttractorPlural')`).
+
+<!-- % to-do:
+Importantly, even if there was an interaction with experiment, it's relatively small, so it wouldn't reduce the other interaction to 0.
+
+Moreover, this findings are also predicted by cue-based retrieval models \citep{engelmann2019effect, vasishth2019computational} and last rendition of marking and morphing theory by \citet{HammerlyEtAl:2019}.
+does it tho?
 especially with regards to what sol lago says: gen and morphophonology gives clues.
 maybe we should take a look at speeded acceptability?
-%maybe this is not the perfect place to write this.
-
-<<exp1ResponseModel, fig.cap='Estimates and 95\\% credible intervals for the regression coefficients for the model of Experiment 1 and Lago et al. (2018).', fig.height=3, fig.align='center'>>=
+maybe this is not the perfect place to write this. -->
+
+```{r Exp1:ModelPlots, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
 contrast_names <- c("cUngrammatical" = "Ungrammaticality",
@@
         xlab("Estimate (probit)")
-
-suppressWarnings({
-print(p_m_response + annotate(x=-3, xend=2, y=0, yend=0, lwd=0.25, geom="segment") + facet_wrap(~"Experiment 1 and Lago et al. (2018)"))
-})
-
-@
-
-<<exp1ResponseModelSepExp1AndLago, fig.cap='Estimates and 95\\% credible intervals for the regression coefficients for Experiment1 and Lago et al. (2018).', fig.height=5, fig.align='center'>>=
-
 contrast_names_exp1 <- c("cUngrammatical" = "Ungrammaticality",
@@
 
+```
+
+```{r exp1ResponseModel, fig.height=3 ,fig.cap="Estimates and 95% credible intervals for the regression coefficients for the model of Experiment 1 and Lago et al. (2018)."}
+suppressWarnings({
+print(p_m_response + annotate(x=-3, xend=2, y=0, yend=0, lwd=0.25, geom="segment"))
+})
+```
+
+```{r exp1ResponseModelSepExp1AndLago, fig.height=5  ,fig.cap="Estimates and 95% credible intervals for the regression coefficients for Experiment1 and Lago et al. (2018)."}
 suppressWarnings({
@@
 })
-
-@
-
-\subsection{Discussion} \label{sec:exp1:discussion}
-
-In Experiment 1, we have found number attraction effects in Turkish using genitive possessive structures, as it is also attested in \citet{LagoEtAl:2018}.
-To account for their findings, \citet{LagoEtAl:2018} assume a cue-based memory retrieval mechanism.
-That is, they assume that upon reaching the verb, the parser attempts to retrieve its agreement controller (the subject) using a cue-based retrieval mechanism \citep{LewisVasishth:2005,JagerEngelmannVasishth:2017}.
+```
+
+## Discussion
+
+In Experiment 1, we have found number attraction effects in Turkish using genitive possessive structures, as it is also attested in @LagoEtAl2018.
+To account for their findings, @LagoEtAl2018 assume a cue-based memory retrieval mechanism.
+That is, they assume that upon reaching the verb, the parser attempts to retrieve its agreement controller (the subject) using a cue-based retrieval mechanism [@LewisVasishth2005,@JagerEngelmannVasishth:2017].
 The assumption is that in sentences such as \ref{item:exp1ExperimentalItems}, features such as case and number information are used to identify the agreement controller in memory.
@@
 This cannot happen in ungrammatical singular attractor conditions.
-This difference in the probability of erroneous retrievals is presumably what surfaced as a number agreement attraction effect, as observed in \citet{LagoEtAl:2018}, and our Experiment 1.
-
-In their work, \citet{LagoEtAl:2018} argue that the agreement attraction in genitive-possessive structures in Turkish is due to the use of genitive case as a marker of embedded subjects in Turkish, i.e.
-differential subject marking (DSM) properties of Turkish \citep{kornfilt2009dom}.
+This difference in the probability of erroneous retrievals is presumably what surfaced as a number agreement attraction effect, as observed in @LagoEtAl2018, and our Experiment 1.
+
+In their work, @LagoEtAl2018 argue that the agreement attraction in genitive-possessive structures in Turkish is due to the use of genitive case as a marker of embedded subjects in Turkish, i.e.
+differential subject marking (DSM) properties of Turkish [@kornfilt2009dom].
 They argue that the genitive case in Turkish may not provide strong cue against subjecthood due to DSM while it does in English.
-Following this logic, we hypothesized that the other phenomenon that gives a strong clue against the subject should inhibit the illusionary dependencies as argued in \citet{nicol2016minimal}.
-One such phenomenon was present in the experimental items used in \citet{LagoEtAl:2018}: the morpho-phonologic ambiguity between the accusative and the possessive case.
+Following this logic, we hypothesized that the other phenomenon that gives a strong clue against the subjecthood should inhibit the illusionary dependencies as argued in @NicolEtAl:2016.
+One such phenomenon was present in the experimental items used in @LagoEtAl2018: the morpho-phonologic ambiguity between the accusative and the possessive case.
 Since they use only consonant ending heads, the marking on the head is ambiguous between the accusative and the possessive marking.
@@
 Nevertheless, we found that when the possessive marker is disambiguated agreement attraction does not diminish in effect size.
-As seen in \autoref{fig:exp1ResponseModel}, we successfully replicated the findings of \citet{LagoEtAl:2018} with disambiguated head nouns.
+As seen in Figure \@ref(fig:exp1ResponseModel), we successfully replicated the findings of @LagoEtAl2018 with disambiguated head nouns.
 Thus, we conclude that the morpho-phonological possessive-accusative ambiguity plays no role in number attraction in Turkish.
@@
 However, there is an alternative explanation that has yet to be ruled out: task-specific strategies.
-We hypothesized that readers may engage in an even shallower process in the evaluation of the sentences such as \ref{item:exp2ExperimentalItems} in which readers decide on the acceptability of the sentence with a faulty state of memory.
+We hypothesized that readers may engage in an even shallower process in the evaluation of the sentences in which readers decide on the acceptability of the sentence with a faulty state of memory.
 In our model, we claim that after they read the sentence readers may end up with insufficient information to reliably judge the sentence.
 Upon such cases, readers may end up using extremely shallow processing methods such as matching the agreement-wise unrelated but form-wise related elements.
-% I should try a bit more to explain this part, I did not do a good job here.
-We present our hypothesized decision tree in \autoref{fig:mptModel}
+We present our hypothesized decision tree in Figure \@ref(fig:mptModel).
 
@@
     \centering
+    \tiny\noindent
                       \begin{forest}
@@
                       child  anchor=west,
-                      s sep = 4mm,    
-                      l sep = 12mm, 
+                      s sep = 5mm,    
+                      l sep = 10mm, 
                   % edge
@@
 
-The aim of our second experiment was to test whether agreement attraction in Turkish may be an instance of a \textit{form-driven processing strategy}.
+<!-- I will fill this one in, but I cannot find the picture of your whiteboard. -->
+
+The aim of our second experiment is to test whether agreement attraction in Turkish is be an instance of a \textit{form-driven processing strategy}.
 Assuming that readers sometimes engage in shallow processing, they may end up with insufficient information to reliably classify a sentence as (un)acceptable.
 In such cases, participants may choose to classify sentences with plural-agreement-bearing verbs as acceptable if they have a memory of a nominal plural morpheme in the sentence.
-Such a response strategy would lead to a larger number of ‘acceptable’ responses in ungrammatical plural attractor conditions than in ungrammatical singular attractor conditions.
-
-\section{Experiment 2} \label{sec:exp2}
-
-<<loadExperiment2Data>>=
-
+Such a response strategy would lead to a larger number of ‘acceptable’ responses in ungrammatical plural attractor conditions than in ungrammatical singular attractor conditions even when there is no interfering noun with plural morphology but, let's say, a plural verb.
+
+# Experiment 2
+
+```{r Exp2:DataWrangling, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
 fname_data2 <- "../workspace_exp2/exp_data.rds"
@@
                       mutate(delta_dc = AgrAttr_d - AgrAttr_c)
-
-@
-
-<<badSubjects2>>=
-
 # identify bad participants 
@@
 data_exp2_clean <- data_exp2 %>% subset(!subject %in% bad_subjects2)
-
-@
-
-<<mergeData2>>=
 
@@
 
-@
-
-In Experiment 2, we wanted to rule out the possibility of \textit{form-driven processing strategy}, namely participants deciding on the acceptability of a sentence using a memory of plural morpheme in the sentence when they do not have sufficient information to rate sentences (un)acceptable.
-
-\subsection{Participants} \label{sec:exp2:participants}
-
-We recruited 79 undergraduate students to participate in Experiment 2 in exchange for course credit.
-All participants were native speakers of Turkish, with an average age of \Sexpr{round(mean(form_exp2$Age))} (range: \Sexpr{min(form_exp2$Age)} - \Sexpr{max(form_exp2$Age)}).
-Experiment were carried out following the Declaration of Helsinki and the regulations concerning ethics at research in Bo\u{g}azi\c{c}i University.
-All participants provided informed consent prior to their participation.
-
-\subsection{Materials} \label{sec:exp2:materials}
-
-We used 40 sets of sentences like
-(\ref{item:exp2ExperimentalItems}), in which we manipulated
-(i) the number of the attractor, and
-(ii) the number agreement on the verb. 
-Unlike Experiment 1, we used the verb of a nominalized relative clause (i.e. \textit{tuttukları}) as an attractor instead of a genitive marked noun. 
-We took advantage of syncretism between Turkish nominal and verbal plural marker.
-Both of these morphemes spells-out as \textit{-lAr}, which enables us to check whether agreement attraction in Turkish can be explained by an extremely shallow dependency parsing based on the forms of morphemes rather than linguistic features.
-
-All sentences started with a complex subject NP like \textit{`the cook that they hired'} (\textit{tuttukları aşçı}), in which the verb of the relative clause functioned as the attractor.
-Because the head noun was singular in all conditions, sentences with plural verb agreement were ungrammatical.
-We have used the same verbs, and have not changed the distribution of verb types. We also utilized the same or similar adverbials in length.
-Relative clauses we used in this experiment are all object relative clauses, and they are all marked with canonical \textit{-dIK} nominalizer.
-Since Turkish is a pro-drop language, we also dropped the subject within the embedded clause, thus ending up with a one-word object relative clause whose head is the controller of the number agreement on the matrix verb.
-One example set of experimental items can be seen in \ref{item:exp2ExperimentalItems}.
-
-\ex. \label{item:exp2ExperimentalItems}
-%
-\a. \textsc{Plural Attractor, Ungrammatical (Plural Verb)}\label{item:exp2expitem-plpl}\\ 
-  \gll *[Tut-tuk-lar-ı \textbf{aşcı}] mutfak-ta sürekli \textbf{zıpla-dı-lar}.\\ 
-  hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{pst}-\textsc{pl}.\\
-  \glt \textit{`The cook that they hired were jumping in the kitchen non-stop.'}
-%
-\b. \textsc{Plural Attractor, Grammatical (Singular Verb)}\label{item:exp2expitem-plsg}\\ 
-  \gll [Tut-tuk-lar-ı \textbf{aşcı}] mutfak-ta sürekli \textbf{zıpla-dı}.\\ 
-  hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{pst}.\\
-  \glt \textit{`The cook that they hired was jumping in the kitchen non-stop.'}
-%
-\c. \textsc{Singular Attractor, Ungrammatical (Plural Verb)}\label{item:exp2expitem-sgpl}\\
-  \gll *[Tut-tuğ-u \textbf{aşcı}] mutfak-ta sürekli \textbf{zıpla-dı-lar}.\\ 
-  hire-\textsc{nmlz}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{pst}-\textsc{pl}.\\
-  \glt \textit{`The cook that they hired were jumping in the kitchen non-stop.'}
-%
-\d. \textsc{Singular Attractor, Grammatical (Singular Verb)}\label{item:exp2expitem-sgsg}\\ 
-  \gll [Tut-tuğ-u \textbf{aşcı}] mutfak-ta sürekli \textbf{zıpla-fı}.\\ 
-  hire-\textsc{nmlz}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{pst}.\\
-  \glt \textit{`The cook that they hired was jumping in the kitchen non-stop.'}
-
-In addition to the experimental items, we used 40 filler sentences of two types, both of which starts with an object relative clause, as illustrated in (\ref{item:exp2FillerItems}).
-Similar to Experiment 1, our filler items included 20 grammatical sentences with an overtly plural marked verbs, and 20 ungrammatical sentences with no overt plural marking, thus singular.
-This was done in order to discourage participants from using a strategy based on verb number. 
-In all of our filler sentences, the dependency between the first complex NP subject modified with an object relative clause and its verb resolved in an adverbial embedded sentence. 
-In grammatical fillers, we have used intransitive verbs with a pro-dropped subject as in (\ref{item:exp2FillerItems_plural}). 
-In ungrammatical fillers, we created the ungrammaticality by placing an adverbial between the bare nominal object and the verb as in (\ref{item:exp2FillerItems_singular}).
-
-\ex. \label{item:exp2FillerItems}
-%
-\a. \label{item:exp2FillerItems_plural} \textsc{Grammatical Filler (Plural Verb)}\\ 
-  \gll Oku-t-tuk-lar-ı öğrenci başarılı ol-unca mutlu ol-du-lar.\\ 
-  read-\textsc{caus}-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  student successful be-\textsc{nmlz} happy be-\textsc{pst}-\textsc{pl}.\\
-  \glt `When the student they sponsored become successful, they became happy.' 
-%
-\b. \label{item:exp2FillerItems_singular} \textit{Ungrammatical Filler (Singular Verb)}\\ 
-  \gll *Kandır-dığ-ı adam öde-me-yince bulaşık saatlerce yıka-dı.\\ 
-  trick-\textsc{nmlz}-\textsc{poss}  man pay-\textsc{neg}-\textsc{nmlz} dish for.hours clean-\textsc{pst}.\\
-  \glt Intended:`When the man he tricked did not pay, he cleaned dishes for hours.'
-
-\subsection{Procedure} \label{sec:exp2:procedure}
-
-The experiment was run online, using the web-based platform Ibex Farm (\url{http://spellout.net/ibexfarm/}). For each participant, experiment took approximately 25 minutes to complete.
-Participants were asked to provide information regarding their native language and age. They were also asked for their consent to participate in the experiment.
-Prior to experimental items, participants read the instructions, and were given 9 practice items with feedback on their accuracy.
-Each trial began with a blank screen for 600 ms, followed by a word-by-word RSVP presentantion of the sentence in the center of the screen, followed by an acceptability judgment.
-Sentences were presented in 30pt font size, and at a rate of 400 ms per word.
-Between each word, participants saw a blank screen for 100 ms.
-Participants pressed the key `P' for `\textit{acceptable}' and `Q' for `\textit{unacceptable}'.
-Within instructions, they were told to provide an acceptability rating before 5,000 ms deadline. During the experiment, they were reminded to respondfaster if they did not respond within 5,000 ms.
-
-Participants saw 40 experimental and 40 filler sentences.
-Experimental sentences were distributed among four different lists according to a Latin-square design.
-Every participant saw one version of the experiment with a specific list and one item per condition.
-
-\subsection{Analysis} \label{sec:exp2:analysis}
-
-<<computeAverages2>>=
-
 avg_clean2 <- list()
@@
 #avg_fillers <- avg_clean %>% lapply(function(df) { df %>% subset(source == "filler") })
-
-@
-
-In our analysis, we used the items from Experiment 1, as well as the items from Experiment 2.
-this decision was made to answer our hypothesis that whether or not participants use the form of the plural suffix rather than the linguistic features.
-A presence of interaction between the attractor type (\textit{nominal} vs.
-\textit{verbal}) and the agreement attraction effect would indicate that people use the linguistic features rather than the form of the plural suffix.
-
-Similar to Experiment 1, we removed the data for all participants who did not exceed the threshold of 25 percentage points in `yes' responses between the grammatical condition and the ungrammatical condition with singular attractors.
-As a result, we excluded \Sexpr{stopifnot(length(bad_subjects2) == 1)} one participant from the Experiment 2, and \Sexpr{length(bad_subjects)} participant from the Experiment 1.
-
-We used R packages brms \citep{R-brms_b} and rstan \citep{R-stan} to fit Bayesian hierarchical models \citep[e.g.,][]{GelmanHill:2007}.
-We aalyzed only experimental sentences, and used (i) grammaticality of the sentence, (ii) attractor number, and (iii) type of the plural suffix (i.e., experiment), as well as their interactions as predictors.
-Moreover, we used by-participant and by-item intercepts and slopes for all predictors.
-Data for Experiment 2, along with our analysis scripts can be found in \url{https://github.com/utkuturk/orc-attractor_numberattraction}.
-
-%Across participants, a total \Sexpr{sum(is.na(df_exp2_na_nofillers$ResponseYes))} items were not responded to before the 5 second deadline by \Sexpr{length(unique(df_exp2_na_nofillers$subject))} different participants.
-These items were not included in the analysis.
-
-\subsection{Results} \label{sec:exp2:results}
-
-<<curEntries>>=
+```
+
+```{r Exp2:PrepareTextInputs, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
 
@@
 exp2_cur_entry4 = avg_exp2$resp %>% filter(experiment == "Experiment 2", grammatical == "grammatical", attractor_num == "plural")
-
-@
-
-\autoref{fig:exp2AvgResponse} shows the average proportions of 'acceptable' responses by experimental conditions for Experiment 2. 
-It shows that ungrammatical sentences with plural attractors are rated as acceptable 
-(M = \Sexpr{exp2_cur_entry1$M}, 
-SE = \Sexpr{exp2_cur_entry1$SE}) 
-as their counterparts with singular attractors 
-(M = \Sexpr{exp2_cur_entry2$M}, 
-SE = \Sexpr{exp2_cur_entry2$SE}).
-The lack of effect (\Sexpr{sprintf("%0.2f", exp2_cur_entry1$M-exp2_cur_entry2$M)}) compared to the magnitude of the effect in Experiment 1 (\Sexpr{sprintf("%0.2f", cur_entry1$M-cur_entry2$M)}) indicates that the verbal plural morpheme does not trigger an illusionary agreement.
-%
-Accuracy rates for grammatical conditions were nearly equal
-(M = \Sexpr{exp2_cur_entry3$M} and \Sexpr{exp2_cur_entry4$M}, 
-SE = \Sexpr{exp2_cur_entry3$SE} and \Sexpr{exp2_cur_entry4$SE}, for singular and plural attractors respectively).
-
-<<exp2AvgResponse, fig.cap='Estimates and 95\\% credible intervals for the regression coefficients for Experiment 1 and Experiment 2.
-Within-subject 95\\% confidence intervals in brackets \\cite{Cousineau:2005,Morey:2008}.', fig.height=3, fig.align='center'>>=
+```
+
+```{r Exp2:PreparePlots, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
 
@@
 p_avg_resp2 <- p_avg_resp2 + scale_color_discrete(name = "Attractor Number")
-
-print(p_avg_resp2)
-
-@
-
-<<Model, include=FALSE>>=
+```
+
+```{r Exp2:BayesianModels, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
 
@@
 
- @
-
-A Bayesian GLM assuming a Bernoulli distribution with a probit-link function was fit to participants' `acceptable' responses.
-The model's estimates and 95\% credible intervals are shown in \autoref{fig:exp2ResponseModel}.
-The main effect of \textit{ungrammaticality} (\Sexpr{print_estimate_with_ci( m_responses2, 'cUngrammatical' )}) indicates that, 
-on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences. 
-Meanwhile, there was no evidence for an interaction between \textit{ungrammaticality} and \textit{attractor number} (\Sexpr{print_estimate_with_ci( m_responses2, 'cUngrammatical:cAttractorPlural')}), indicating
-a similar effect of attractor number in ungrammatical conditions compared to grammatical conditions, and thus no number agreement attraction effect.
-Importantly, the negative effect between \textit{the presence of the verbal plural}, \textit{ungrammaticality} and \textit{attractor number} (\Sexpr{print_estimate_with_ci( m_responses2, 'cVerbalAttractor:cUngrammatical:cAttractorPlural')}) indicated that the plural morpheme on the verb of the object relative clause lowered the agreement attraction effects.
-
-<<exp2ResponseModel, fig.cap='Estimates and 95\\% credible intervals for the regression coefficients for a model of Experiment 1 and Experiment 2.', fig.height=3, fig.align='center'>>=
+```
+
+```{r Exp2:ModelPlots, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
 
@@
 p_m_response_exp2 <- p_m_response_exp2 + annotate(x=-3, xend=1, y=0, yend=0, lwd=0.25, geom="segment")
-print(p_m_response_exp2)
-@
-
-<<exp2ResponseModelExp2Only, fig.cap='Estimates and 95\\% credible intervals for the regression coefficients for Experiment 2.', fig.height=1.5, fig.align='center'>>=
 
@@
 p_m_response_exp2only <- p_m_response_exp2_exp2only + annotate(x=-3, xend=1, y=0, yend=0, lwd=0.25, geom="segment")
+
+```
+
+The aim of the Experiment 2 is to control for _form-driven processing strategies_ which may be employed by the participants in the processing of Turkish number agreement.
+A processing mechanism that is driven by form itself, rather than the embedded linguistic features, would predict the comparable agreement attraction effects even when the attractor does not contain a possible nominal plural feature to create interference but contains a form-identical morpheme.
+To this end, we utilized syncretism between nominal and verbal plural marking in Turkish.
+Instead of genitive marked nouns, we used the verb of a object relative clauses as in \@ref(item:exp2Items).
+We expect that under some conditions in which participants do not have sufficient information to rate sentences (un)acceptable, they will decide on the grammaticality of the sentence based on their memory of plural morpheme string, regardless of the feature itself.
+
+\begin{exe}
+\ex \label{item:exp2Items}
+\gll Tut-tuk-$\emptyset$/lar-(n)ı aşçı mutfak-de sürekli zıpla-dı-$\emptyset$/lar.\\
+hire-\Nmlz{}-\Sg{}/\Pl{}-\Poss{} cook kitchen-\Loc{} non-stop jump-\Pst{}-\Sg{}/\Pl{}\\
+\glt `The cook that they hired\textsubscript{sg/pl} jumped\textsubscript{sg/pl} in the kitchen non-stop.'
+\end{exe}
+
+_Form-driven processing strategies_ predicts that  we wanted to rule out the possibility of \textit{form-driven processing strategy}, namely participants deciding on the acceptability of a sentence using a memory of plural morpheme in the sentence when they do not have sufficient information to rate sentences (un)acceptable.
+
+## Participants
+
+We recruited 79 undergraduate students to participate in Experiment 2 in exchange for course credit.
+All participants were native speakers of Turkish, with an average age of `r printnum(mean(form_exp2$Age))` (range: `r min(form_exp2$Age)` - `r max(form_exp2$Age)`).
+Experiment were carried out following the Declaration of Helsinki and the regulations concerning ethics at research in Bo\u{g}azi\c{c}i University.
+All participants provided informed consent prior to their participation.
+
+## Materials
+
+We used 40 sets of sentences like
+(\ref{item:exp2ExperimentalItems}), in which we manipulated
+(i) the number of the attractor, and
+(ii) the number agreement on the verb. 
+Unlike Experiment 1, we used the verb of a nominalized relative clause (i.e. \textit{tuttukları}) as an attractor instead of a genitive marked noun. 
+We took advantage of syncretism between Turkish nominal and verbal plural marker.
+Both of these morphemes spells-out as \textit{-lAr}, which enables us to check whether agreement attraction in Turkish can be explained by an extremely shallow dependency parsing based on the forms of morphemes rather than linguistic features.
+
+All sentences started with a complex subject NP like \textit{`the cook that they hired'} (\textit{tuttukları aşçı}), in which the verb of the relative clause functioned as the attractor.
+Because the head noun was singular in all conditions, sentences with plural verb agreement were ungrammatical.
+We have used the same verbs, and have not changed the distribution of verb types. We also utilized the same or similar adverbials in length.
+Relative clauses we used in this experiment are all object relative clauses, and they are all marked with canonical \textit{-dIK} nominalizer.
+Since Turkish is a pro-drop language, we also dropped the subject within the embedded clause, thus ending up with a one-word object relative clause whose head is the controller of the number agreement on the matrix verb.
+One example set of experimental items can be seen in \ref{item:exp2ExperimentalItems}.
+
+\begin{exe}
+\ex \label{item:exp2ExperimentalItems}
+\begin{xlist}
+
+\ex \textsc{Plural Attractor, Ungrammatical (Plural Verb)}\label{item:exp2expitem-plpl}
+  \gll *[Tut-tuk-lar-ı \textbf{aşcı}] mutfak-ta sürekli \textbf{zıpla-dı-lar}.\\ 
+  hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{pst}-\textsc{pl}.\\
+  \glt \textit{`The cook that they hired were jumping in the kitchen non-stop.'}
+
+\ex \textsc{Plural Attractor, Grammatical (Singular Verb)}\label{item:exp2expitem-plsg}
+  \gll [Tut-tuk-lar-ı \textbf{aşcı}] mutfak-ta sürekli \textbf{zıpla-dı}.\\ 
+  hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{pst}.\\
+  \glt \textit{`The cook that they hired was jumping in the kitchen non-stop.'}
+
+\ex \textsc{Singular Attractor, Ungrammatical (Plural Verb)}\label{item:exp2expitem-sgpl}
+  \gll *[Tut-tuğ-u \textbf{aşcı}] mutfak-ta sürekli \textbf{zıpla-dı-lar}.\\ 
+  hire-\textsc{nmlz}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{pst}-\textsc{pl}.\\
+  \glt \textit{`The cook that they hired were jumping in the kitchen non-stop.'}
+
+\ex \textsc{Singular Attractor, Grammatical (Singular Verb)}\label{item:exp2expitem-sgsg}
+  \gll [Tut-tuğ-u \textbf{aşcı}] mutfak-ta sürekli \textbf{zıpla-fı}.\\ 
+  hire-\textsc{nmlz}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{pst}.\\
+  \glt \textit{`The cook that they hired was jumping in the kitchen non-stop.'}
+\end{xlist}
+\end{exe}
+
+In addition to the experimental items, we used 40 filler sentences of two types, both of which starts with an object relative clause, as illustrated in (\ref{item:exp2FillerItems}).
+Similar to Experiment 1, our filler items included 20 grammatical sentences with an overtly plural marked verbs, and 20 ungrammatical sentences with no overt plural marking, thus singular.
+This was done in order to discourage participants from using a strategy based on verb number. 
+In all of our filler sentences, the dependency between the first complex NP subject modified with an object relative clause and its verb resolved in an adverbial embedded sentence. 
+In grammatical fillers, we have used intransitive verbs with a pro-dropped subject as in (\ref{item:exp2FillerItems_plural}). 
+In ungrammatical fillers, we created the ungrammaticality by placing an adverbial between the bare nominal object and the verb as in (\ref{item:exp2FillerItems_singular}).
+
+\begin{exe}
+\ex \label{item:exp2FillerItems}
+\begin{xlist}
+
+\ex \label{item:exp2FillerItems_plural} \textsc{Grammatical Filler (Plural Verb)}\\ 
+  \gll Oku-t-tuk-lar-ı öğrenci başarılı ol-unca mutlu ol-du-lar.\\ 
+  read-\textsc{caus}-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  student successful be-\textsc{nmlz} happy be-\textsc{pst}-\textsc{pl}.\\
+  \glt `When the student they sponsored become successful, they became happy.'
+
+\ex \label{item:exp2FillerItems_singular} \textit{Ungrammatical Filler (Singular Verb)}\\ 
+  \gll *Kandır-dığ-ı adam öde-me-yince bulaşık saatlerce yıka-dı.\\ 
+  trick-\textsc{nmlz}-\textsc{poss}  man pay-\textsc{neg}-\textsc{nmlz} dish for.hours clean-\textsc{pst}.\\
+  \glt Intended:`When the man he tricked did not pay, he cleaned dishes for hours.'
+\end{xlist}
+\end{exe}
+
+## Procedure
+
+The experiment was run online, using the web-based platform Ibex Farm (\url{http://spellout.net/ibexfarm/}). For each participant, experiment took approximately 25 minutes to complete.
+Participants were asked to provide information regarding their native language and age. They were also asked for their consent to participate in the experiment.
+Prior to experimental items, participants read the instructions, and were given 9 practice items with feedback on their accuracy.
+Each trial began with a blank screen for 600 ms, followed by a word-by-word RSVP presentantion of the sentence in the center of the screen, followed by an acceptability judgment.
+Sentences were presented in 30pt font size, and at a rate of 400 ms per word.
+Between each word, participants saw a blank screen for 100 ms.
+Participants pressed the key `P' for `\textit{acceptable}' and `Q' for `\textit{unacceptable}'.
+Within instructions, they were told to provide an acceptability rating before 5,000 ms deadline. During the experiment, they were reminded to respondfaster if they did not respond within 5,000 ms.
+
+Participants saw 40 experimental and 40 filler sentences.
+Experimental sentences were distributed among four different lists according to a Latin-square design.
+Every participant saw one version of the experiment with a specific list and one item per condition.
+
+## Analysis
+
+In our analysis, we used the items from Experiment 1, as well as the items from Experiment 2.
+this decision was made to answer our hypothesis that whether or not participants use the form of the plural suffix rather than the linguistic features.
+A presence of interaction between the attractor type (\textit{nominal} vs.
+\textit{verbal}) and the agreement attraction effect would indicate that people use the linguistic features rather than the form of the plural suffix.
+
+Similar to Experiment 1, we removed the data for all participants who did not exceed the threshold of 25 percentage points in 'yes' responses between the grammatical condition and the ungrammatical condition with singular attractors.
+As a result, we excluded `r stopifnot(length(bad_subjects2) == 1)` one participant from the Experiment 2, and `r length(bad_subjects)` participant from the Experiment 1.
+
+We used R packages brms [@brms] and rstan [@stan] to fit Bayesian hierarchical models [e.g., @GelmanHill2007].
+We aalyzed only experimental sentences, and used (i) grammaticality of the sentence, (ii) attractor number, and (iii) type of the plural suffix (i.e., experiment), as well as their interactions as predictors.
+Moreover, we used by-participant and by-item intercepts and slopes for all predictors.
+Data for Experiment 2, along with our analysis scripts can be found in \url{https://github.com/utkuturk/orc-attractor_numberattraction}.
+
+## Results
+
+\autoref{fig:exp2AvgResponse} shows the average proportions of 'acceptable' responses by experimental conditions for Experiment 2. 
+It shows that ungrammatical sentences with plural attractors are rated as acceptable 
+(M = `r exp2_cur_entry1$M`, 
+SE = `r exp2_cur_entry1$SE`) 
+as their counterparts with singular attractors 
+(M = `r exp2_cur_entry2$M`, 
+SE = `r exp2_cur_entry2$SE`).
+The lack of effect (`r sprintf("%0.2f", exp2_cur_entry1$M-exp2_cur_entry2$M)`) compared to the magnitude of the effect in Experiment 1 (`r sprintf("%0.2f", exp2_cur_entry1$M-exp2_cur_entry2$M)`) indicates that the verbal plural morpheme does not trigger an illusionary agreement.
+Accuracy rates for grammatical conditions were nearly equal
+(M = `r exp2_cur_entry3$M` and `r exp2_cur_entry4$M`, 
+SE = `r exp2_cur_entry3$SE` and `r exp2_cur_entry4$SE`, for singular and plural attractors respectively).
+
+```{r exp2AvgResponse, fig.height=3 ,fig.cap="Estimates and 95% credible intervals for the regression coefficients for Experiment 1 and Experiment 2.
+Within-subject 95% confidence intervals in brackets."}
+# \\cite{Cousineau:2005,Morey:2008}
+print(p_avg_resp2)
+
+```
+
+A Bayesian GLM assuming a Bernoulli distribution with a probit-link function was fit to participants' `acceptable' responses.
+The model's estimates and 95\% credible intervals are shown in \@ref(fig:exp2ResponseModel).
+The main effect of \textit{ungrammaticality} (`r print_estimate_with_ci( m_responses2, 'cUngrammatical' )`) indicates that, 
+on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences. 
+Meanwhile, there was no evidence for an interaction between \textit{ungrammaticality} and \textit{attractor number} (`r print_estimate_with_ci( m_responses2, 'cUngrammatical:cAttractorPlural')`), indicating
+a similar effect of attractor number in ungrammatical conditions compared to grammatical conditions, and thus no number agreement attraction effect.
+Importantly, the negative effect between \textit{the presence of the verbal plural}, \textit{ungrammaticality} and \textit{attractor number} (`r print_estimate_with_ci( m_responses2, 'cVerbalAttractor:cUngrammatical:cAttractorPlural')`) indicated that the plural morpheme on the verb of the object relative clause lowered the agreement attraction effects.
+
+```{r exp2ResponseModel, fig.height=3 ,fig.cap="Estimates and 95% credible intervals for the regression coefficients for a model of Experiment 1 and Experiment 2."}
+print(p_m_response_exp2)
+
+```
+
+```{r exp2ResponseModelExp2Only, fig.cap="Estimates and 95% credible intervals for the regression coefficients for Experiment 2.", fig.height=1.5}
 print(p_m_response_exp2only)
 
-@
-
-\subsection{Discussion} \label{sec:exp2:discussion}
+```
+
+## Discussion
 
@@
 However, results may be more telling with regards to the other theories of agreement attraction.
-These results seem unexpected within the cue-based retrieval mechanisms.
-Even though the root of the attractor is verbal, the morpheme is the same with the third person plural possessive marker since the relative clauses in Turkish are always nominalized and the subject is marked with the genitive case.
+From the perspective of cue-based retrieval processes, these results tell us that the notion of feature \texttt{+plural} is more complex than previously reported.
+When a language have syncretic verbal and nominal plurals, it is now reasonable to say that participants distinguish even more and consider the base of the suffixes that they attach.
 The findings of this experiment indicate towards more fine-grained features needs to be utilized.
-One other possible explanation within the cue-based retrieval models can be formed around the status of agreement markers.
-One can say that the agreement process is completed in the verbal \textit{-lAr}; in other words, it is not the triggering morpheme but the probe of the agreement.
+One other possible explanation within the cue-based retrieval models can be formed around the satisfaction of a dependency.
+Considering our results, we can manipulate that once a feature is used for a certain representation, it cannot be used again.
+One can say that the agreement process is completed when the verbal plural on the attractor verb is read.
+In other words, since the plural morpheme on the attractor verb is not the agreement-triggering morpheme but the probe of the agreement, the retrieval mechanism should not even consider a possibility of retrieving a plural cue from the verb.
+This may be because either verbal plural are not encoded with \texttt{+plural} cue or they are encoded with \texttt{+plural} and an additional cue which transmits that the dependency is satisfied.
 This difference would mean that verbal \textit{-lAr} should not start any search for dependency resolution.
-In contrast to verbal \textit{-lAr}, the plural morpheme on the genitive is supposed to be triggering part of the agreement, not the probe.
+In contrast to verbal \textit{-lAr}, the plural morpheme on the noun attractor is supposed to be triggering part of the agreement, not the probe.
+
+<!--
+
 However, in Turkish embedded clauses, where genitive subjects can be seen, the number agreement works differently than the matrix level agreement.
 When the genitive subject of an embedded clause is marked with plural it is ungrammatical to have plural marking on the verb.
-This prohibition in return means that the genitive subjects should not create an expectation for a plural marked verb, which was believed to be the reason for the agreement attraction in \citet{LagoEtAl:2018}.
-
-As for the marking and morphing theories, the results of Experiment 2 are completely expected and mitigated by the syntactic depth effects.
-Due to the genitive possessor's limited inner complexity compared to that of relative clause modifiers, marking and morphing theories would expect higher contribution from the genitive attractors to the final representation of number information.
-
-\section{General Discussion} \label{sec:general_discussion}
-
-\bibliography{new-references,library}
-
-\end{document}
-
-%
-% Please see the package documentation for more information
-% on the APA6 document class:
-%
-% http://www.ctan.org/pkg/apa6
-%
+This prohibition in return means that the genitive subjects should not create an expectation for a plural marked verb, which was believed to be the reason for the agreement attraction in @LagoEtAl2018.
+
+-->
+
+As for the marking and morphing theories, the results of experiment 2 are completely expected.
+The effects founds in experiment 2 can be explained by the spreading activation.
+In the experiment 2 spreading activation were lower due to the distance between the verbal plural and the root note of the head subject compared to the spreading activation with genitive attractors which are closer to root node.
+Due to the genitive possessor's limited inner complexity and syntactic depth compared to that of relative clause constructions, marking and morphing theories would expect higher contribution from the genitive attractors to the final representation of number information.
+
+<!-- By depth, I mean how many root nodes between the plural item and the root node. I always understood as such. -->
+
+# General Discussions
+
+We investigated the role of shallow processing in generating agreement attraction effects.
+We were not able to find any significant finding for the role of morphological local ambiguity (Experiment 1) and the role of form-driven processing strategies (Experiment 2).
+The results of experiment 1 showed us that the link between the Inhibition Hypothesis and the shallow processing explanation would not predict agreement attraction effects in Turkish.
+Furthermore, our results of experiment 2 also falsify our hypothesis which was based on the use of morpho-orthographic form for acceptability judgment when there is no enough information.
+
+Our results align with the already existing theories that argue for the role of structural embedding in agreement attraction: MMT.
+Following the minimalist framework, I assume the following trees as in \@ref(syntax:genposs) and \@ref(syntax:orc).
+Since the plural containing item is embedded deeper in the tree, the verb within the object relative clause would contribute less than  the genitive marked NP.
+
+<!-- Utku: I do not think you assume this, that is why I used first person pronoun here.
+we may not include this part, or write something entirely different, but I wanted to be as clear as possible with my assumption.
+Because I know you are going to ask about them :D  -->
+\begin{multicols}{2}
+
+\begin{exe}
+\ex \label{syntax:genposs}
+\begin{forest}
+ned
+[DP
+  [
+    [NP
+    [N\\yöneticiler]
+    ]
+    [D\\-in]
+  ]
+  [
+    [NP\\aşçısı]
+    [D]
+  ]
+]
+\path[fill=red] (.parent anchor) circle[radius=2pt];
+\path[fill=red] (!1.child anchor) circle[radius=2pt];
+\path[fill=red] (!11.child anchor) circle[radius=2pt];
+\path[fill=red] (!111.child anchor) circle[radius=2pt];
+\end{forest}
+
+\ex \label{syntax:orc}
+\begin{forest}
+ned
+[DP
+  [
+    [
+      [pro]
+      [
+        [VP
+          [NP\\ t\textsubscript{1}]
+          [V\\Tuttukları]
+        ]
+        [T]
+      ]
+    ]
+    [C]
+  ]
+  [
+    [NP\\aşçı]
+    [D]
+  ]
+]
+\path[fill=red] (.parent anchor) circle[radius=2pt];
+\path[fill=red] (!1.child anchor) circle[radius=2pt];
+\path[fill=red] (!11.child anchor) circle[radius=2pt];
+\path[fill=red] (!112.child anchor) circle[radius=2pt];
+\path[fill=red] (!1121.south) circle[radius=2pt];
+\path[fill=red] (!11212.child anchor) circle[radius=2pt];
+\end{forest}
+\end{exe}
+
+\end{multicols}
+
+<!-- utku todo: find the analysis for dp-gen-pos for turkish from aygen phd thesis. RC and the NP must be sister correct that.-->
+
+Additionally, our results suggest fine-tuning within the cue-based retrieval explanation.
+Retrieving \texttt{+plural} is not enough as shown in our experiment 2.
+Other pieces of information are necessary to stimulate agreement attraction effects.
+One possibility is retrieval only happens among the non-satisfied dependencies.
+Another possibility is that the base of the plural is also encoded.
+
+As for our hypothesized shallow processing explanation for agreement attraction, we could not provide any evidence towards it.
+We can say that with these structures we were not able to generate agreement attractions.
+
+# Conclusion
+
+In this paper, we reported two experiments on number agreement attraction effects in Turkish.
+We observed number agreement attraction with nominal plural morphemes in experiment 1, but not with verbal plural morphemes in experiment 2.
+In Experiment 1, our findings were parallel to those of @LagoEtAl2018 with unambiguously possessive marked heads.
+In Experiment 2, we failed to observe number agreement attraction effects with object relative clause attractors.
+
+Our results suggest that morpho-phonological ambiguities do not play a role in number agreement attraction in Turkish, and speakers do not use form solely in decision making processes.
+These findings support an agreement attraction theory which makes use of abstract linguistic features.
+
+# References
+```{r create_r-references}
+r_refs(file = "r-references.bib")
+```
+
+\begingroup
+\setlength{\parindent}{-0.5in}
+
+<div id="refs" custom-style="Bibliography"></div>
+\endgroup

### 2020-09-01 ongoing_draft/ongoing_paper.tex

--- 2020-09-01 ongoing_draft/ongoing_paper.Rmd
@@
----
-title             : "Agreement Attraction in Turkish"
-shorttitle        : "Agreement Attraction in Turkish"
-author: 
-  - name          : "Utku Türk"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Postal address"
-    email         : "utku.turk@boun.edu.tr"
-affiliation:
-  - id            : "1"
-    institution   : "Boğaziçi University University, Istanbul, Turkey"
-authornote: |
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[
+  english,
+  doc,floatsintext]{apa6}
+
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{5}
+% Make \paragraph and \subparagraph free-standing
+\ifx\paragraph\undefined\else
+  \let\oldparagraph\paragraph
+  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+  \let\oldsubparagraph\subparagraph
+  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
+
+%\usepackage[utf8x]{inputenc}
+\usepackage{amsmath}
+\usepackage{amsthm}
+\usepackage{graphicx}
+\usepackage[colorinlistoftodos]{todonotes}
+\usepackage[singlespacing]{setspace}
+
+\let\B\relax
+
+\let\T\relax
+
+\usepackage{gb4e}
+\exewidth{(\thexnumi)} %ex number no indent setting
+\let\eachwordone=\textit %first line italic
+\noautomath
+
+\usepackage[linguistics,edges]{forest} 
+\forestset{
+ned/.style={%
+    for tree={calign=fixed edge angles},
+    delay={%
+      where content={}{%
+        shape=coordinate,
+        for nodewalk={%
+          Nodewalk={%
+            on invalid=fake,
+          }{%
+            parent,
+          }{%
+            for children={anchor=north},
+          }
+        }{},
+      }{},
+    },
+},
+fned/.style={
+        delay={where content={}{shape=coordinate,
+              for siblings={anchor=north}}{}},
+		for tree={s sep=4mm}},
+}
+
+\usepackage{leipzig}
+\makeglossaries
+
+\usepackage{hyperref}
+\hypersetup{colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue}
+\usepackage{multicol}
+% Manuscript styling
+\usepackage{upgreek}
+\captionsetup{font=singlespacing,justification=justified}
+
+% Table formatting
+\usepackage{longtable}
+\usepackage{lscape}
+% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
+\usepackage{multirow}		% Table styling
+\usepackage{tabularx}		% Control Column width
+\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
+\usepackage{threeparttablex}            % Lets threeparttable work with longtable
+
+% Create new environments so endfloat can handle them
+% \newenvironment{ltable}
+%   {\begin{landscape}\begin{center}\begin{threeparttable}}
+%   {\end{threeparttable}\end{center}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
+
+% Enables adjusting longtable caption width to table width
+% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
+\makeatletter
+\newcommand\LastLTentrywidth{1em}
+\newlength\longtablewidth
+\setlength{\longtablewidth}{1in}
+\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
+
+% \setlength{\parindent}{0.5in}
+% \setlength{\parskip}{0pt plus 0pt minus 0pt}
+
+% \usepackage{etoolbox}
+\makeatletter
+\patchcmd{\HyOrg@maketitle}
+  {\section{\normalfont\normalsize\abstractname}}
+  {\section*{\normalfont\normalsize\abstractname}}
+  {}{\typeout{Failed to patch abstract.}}
+\patchcmd{\HyOrg@maketitle}
+  {\section{\protect\normalfont{\@title}}}
+  {\section*{\protect\normalfont{\@title}}}
+  {}{\typeout{Failed to patch title.}}
+\makeatother
+\shorttitle{Agreement Attraction in Turkish}
+\keywords{keywords\newline\indent Word count: X}
+\usepackage{csquotes}
+\geometry{left=25mm, right=25mm, top=25mm, bottom=25mm}
+
+\ifxetex
+  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
+\else
+  \usepackage[shorthands=off,main=english]{babel}
+\fi
+\ifluatex
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newenvironment{cslreferences}%
+  {\setlength{\parindent}{0pt}%
+  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
+  {\par}
+
+\title{Agreement Attraction in Turkish}
+\author{Utku Türk\textsuperscript{1}}
+\date{}
+
+\authornote{
+
 authornote
-abstract: |
+
+Correspondence concerning this article should be addressed to Utku Türk, Postal address. E-mail: \href{mailto:utku.turk@boun.edu.tr}{\nolinkurl{utku.turk@boun.edu.tr}}
+
+}
+
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Boğaziçi University University, Istanbul, Turkey}
+
+\abstract{
 We report the results of two speeded acceptability judgment experiments in Turkish.
@@
 Our findings contradict our hypothesized form-driven processing strategy and support an account of agreement attraction based on the use of abstract linguistic features, rather than mere form.
-keywords          : "keywords"
-wordcount         : "X"
-bibliography      : ["new-references.bib","r-references.bib"]
-floatsintext      : yes
-figurelist        : no
-tablelist         : no
-numbersections    : yes
-geometry          : left=25mm, right=25mm, top=25mm, bottom=25mm
-#fontsize          : 10pt
-footnotelist      : no
-linenumbers       : no
-mask              : no
-draft             : no
-documentclass     : "apa6"
-classoption       : "doc"
-output:
-  papaja::apa6_pdf:
-    latex_engine: xelatex
-    includes:
-        in_header: paper_draft_preamble.tex
-editor_options: 
-  chunk_output_type: console
-keep_tex: FALSE
-keep_md: FALSE
----
-
-```{r setup, eval =T, include = FALSE, message=FALSE, warning=FALSE}
-library("papaja")
-library(knitcitations)
-library(tidyverse)
-library(magrittr)
-library(ggplot2)
-theme_set(theme_bw())
-
-library(car, warn.conflicts = FALE)
-library(MASS)
-library(brms)
-library(xtable)
-library(ggpubr)
-
-library(languageR)
-library(tidyverse)
-library(gdata)
-library(MASS)
-library(magrittr)
-library(ggplot2)
-
-source("../scripts/misc.R")
-
-```
-
-```{r analysis-preferences, eval =T, message=FALSE, warning=FALSE}
-# Seed for random number generation
-set.seed(42)
-knitr::opts_chunk$set(encoding = 'UTF-8',
-                      cache.extra = knitr::rand_seed,
-                      echo = FALSE,
-                      results = 'asis')
-options("citation_format" = "pandoc")
-
-```
-
-# Introduction
-
-It has been observed that speakers often fail to accurately process grammatical dependencies between the parts of a sentence [@GibsonThomas:1999; @PhillipsEtAl:2011]. 
-For example, ungrammatical center-embedded structures like  *The patient who the nurse who the clinic had hired met Jack* are found grammatical by native English speakers. 
-One such comprehension error is agreement attraction [@Nicoletal:1997; @PearlmutterGarnseyBock:1999; @WagersEtAl:2009]. 
-Speakers may erroneously find sentences acceptable in which the verb erroneously agrees with a syntactically unrelated noun phrase (*the attractor*) instead of the subject (*the agreement controller*) as in \@ref(item:wagers2009).
+}
+
+\begin{document}
+\maketitle
+
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
+
+It has been observed that speakers often fail to accurately process grammatical dependencies between the parts of a sentence (Gibson \& Thomas, 1999; Phillips, Wagers, \& Lau, 2011).
+For example, ungrammatical center-embedded structures like \emph{The patient who the nurse who the clinic had hired met Jack} are found grammatical by native English speakers.
+One such comprehension error is agreement attraction (Nicol, Forster, \& Veres, 1997; Pearlmutter, Garnsey, \& Bock, 1999; Wagers, Lau, \& Phillips, 2009).
+Speakers may erroneously find sentences acceptable in which the verb erroneously agrees with a syntactically unrelated noun phrase (\emph{the attractor}) instead of the subject (\emph{the agreement controller}) as in \ref{item:wagers2009}.
 
@@
 
-<!-- for some reason I could not add citation in the examples. \hfill \footnotesize{[@WagersEtAl:2009]} -->
-
-These effects were found to be robust in a variety of constructions in different languages, e.g.
-English , German , Russian, Arabic, Spanish, Armenian, Slovak, Greek, and Turkish [@LagoEtAl2018; @LagoEtAl:2015; @ReifegersteEtAl:2016; @BadeckerKuminiak:2007; @TuckerEtAl:2015; @PaspaliMarinis:2020; @AvetisyanEtAl:2020] using structures like object relative clauses, subject relative clauses, possessive relative clauses, and genitive-possessive noun phrases [@LagoEtAl2018; @WagersEtAl:2009; @LagoEtAl:2015; @FranckColonnaRizzi:2015; @TuckerEtAl:2015; @ParkerEtAl:2015; @Dillon2013a; @Haussler2009].
-These effects are found both in grammatical marking of the gender and the number [@BadeckerKuminiak:2007; @Slioussar:2016; @PaspaliMarinis:2020], and attested with various methods including maze tasks, ERP, eye tracking to name a few [@TannerEtAl:2014; @WagersEtAl:2009; @Nicoletal:1997].
-
-One instance of agreement attraction is found in the production processes in which participants were asked to complete sentence fragments [@Bock1991].
-Participants used the wrong verb more often when the attractor (*cabinets*) were plural, and the agreement controller (*key*) were singular as in \@ref(item:bock1991).
+These effects were found to be robust in a variety of constructions in different languages, e.g.~English , German , Russian, Arabic, Spanish, Armenian, Slovak, Greek, and Turkish (Avetisyan, Lago, \& Vasishth, 2020; Badecker \& Kuminiak, 2007; Lago et al., 2018; Lago, Shalom, Sigman, Lau, \& Phillips, 2015; Paspali \& Marinis, 2020; Reifegerste, Hauer, \& Felser, 2016; Tucker, Idrissi, \& Almeida, 2015) using structures like object relative clauses, subject relative clauses, possessive relative clauses, and genitive-possessive noun phrases (Dillon, Clifton, \& Frazier, 2013; Franck, Colonna, \& Rizzi, 2015; Häussler \& Bader, 2009; Lago et al., 2018, 2015; Parker, Lago, \& Phillips, 2015; Tucker et al., 2015; Wagers et al., 2009).
+These effects are found both in grammatical marking of the gender and the number (Badecker \& Kuminiak, 2007; Paspali \& Marinis, 2020; Slioussar \& Malko, 2016), and attested with various methods including maze tasks, ERP, eye tracking to name a few (Nicol et al., 1997; Tanner, Nicol, \& Brehm, 2014; Wagers et al., 2009).
+
+One instance of agreement attraction is found in the production processes in which participants were asked to complete sentence fragments (Bock \& Miller, 1991).
+Participants used the wrong verb more often when the attractor (\emph{cabinets}) were plural, and the agreement controller (\emph{key}) were singular as in \ref{item:bock1991}.
 
@@
 Agreement attraction is also found in the comprehension studies.
-In these studies, agreement attraction is found either as a facilitation in reading times or as a effect in the acceptability rates [@WagersEtAl:2009].
+In these studies, agreement attraction is found either as a facilitation in reading times or as a effect in the acceptability rates (Wagers et al., 2009).
 When reading times are checked, they found that the participants read the ungrammatical sentences with a plural attractor easier then the ungrammatical sentences without a plural attractor.
@@
 
-Some theories [@EberhardEtAl:2005; @HammerlyEtAl:2019] explain this phenomenon through a faulty representation of the number on the head of the agreement controller whereas other theories assume that agreement attraction is due to an error in the access to the number of the agreement controller [@WagersEtAl:2009; @NicenboimEtAl:2018].
+Some theories (Eberhard, Cutting, \& Bock, 2005; Hammerly, Staub, \& Dillon, 2019) explain this phenomenon through a faulty representation of the number on the head of the agreement controller whereas other theories assume that agreement attraction is due to an error in the access to the number of the agreement controller (Nicenboim, Vasishth, Engelmann, \& Suckow, 2018; Wagers et al., 2009).
 
 Agreement attraction effects can equally well be explained by assuming shallow processing.
-Recent studies in psychology literature show that in certain environments people may not notice ungrammaticalities in a sentence or may not compute dependencies in a sentence completely [@OteroKintsch:1992; @FerreiraBaileyFerraro:2002].
+Recent studies in psychology literature show that in certain environments people may not notice ungrammaticalities in a sentence or may not compute dependencies in a sentence completely (Ferreira, Bailey, \& Ferraro, 2002; Otero \& Kintsch, 1992).
 
 To investigate this possibility, we report two speeded acceptability judgment experiments in this paper.
-The first one inspects the recent @LagoEtAl2018 findings.
-They found number attraction effects in genitive-possessive constructions such as `_[[the child's] toy]_' ([[_çocuğ-un\textsubscript{Gen}_] _oyuncağ-ı\textsubscript{Poss}_]).
-They justify the use of this construction with the findings of @NicolEtAl:2016.
+The first one inspects the recent Lago et al.
+(2018) findings.
+They found number attraction effects in genitive-possessive constructions such as `\emph{{[}{[}the child's{]} toy{]}}' ({[}{[}\emph{çocuğ-un\textsubscript{Gen}}{]} \emph{oyuncağ-ı\textsubscript{Poss}}{]}).
+They justify the use of this construction with the findings of Nicol, Barss, and Barker (2016).
 Since the genitive case is a possible subject marker, the participants can consider genitive marked attractors a candidate for the agreement controller.
@@
 
-# Theories of agreement attraction
+\hypertarget{theories-of-agreement-attraction}{%
+\section{Theories of agreement attraction}\label{theories-of-agreement-attraction}}
 
 The difference between the theories that explain the agreement attraction phenomenon lies in the assumption regarding the origin of the illusion.
-Some theories [@BockEberhard:1993; @ViglioccoEtAl:1995; @Eberhard:1997; @FranckEtAl:2002; @BergenGibson:2012] explain this phenomenon by hypothesizing that the representations formed from the linguistic input is faulty.
+Some theories (Bergen \& Gibson, 2012; Bock \& Eberhard, 1993; Eberhard, 1997; Franck, Vigliocco, \& Nicol, 2002; Vigliocco, Butterworth, \& Semenza, 1995) explain this phenomenon by hypothesizing that the representations formed from the linguistic input is faulty.
 One theory in this group is Marking and Morphing Theory.
 MMT suggests that the subject phrase can hold a continuous number value from 1 (unambiguously plural) to -1 (unambiguously singular).
-This value is affected by the _percolation_ of the grammatical feature which can happen in any direction.
+This value is affected by the \emph{percolation} of the grammatical feature which can happen in any direction.
 The implementation of such models suggests that the final number of the phrase depends on the number morphology on the head and the elements within the phrase, and the syntactic proximity of these elements to the root node of the phrase.
 
-Another type of model within this family is based on the idea that linguistic input is noisy, and it is accompanied by a priori linguistic knowledge [@BergenGibson:2012].
-This account is an extension of the noisy channel model proposed by @Levy2008, which uses Bayesian inference to model the participants' inference given the word string.
-@PatsonHusband:2016 provide additional evidence for this type of analysis by showing that final interpretations of agreement attraction cases are not based on the actual string, meaning that the participants infer a plural-marked head noun whereas it is not marked by any plural inflection.
-
-On the other side, some theories assume that agreement attraction is due to an error in the access to the number of the agreement controller [@WagersEtAl:2009; @NicenboimEtAl:2018].
+Another type of model within this family is based on the idea that linguistic input is noisy, and it is accompanied by a priori linguistic knowledge (Bergen \& Gibson, 2012).
+This account is an extension of the noisy channel model proposed by Levy (2008), which uses Bayesian inference to model the participants' inference given the word string.
+Patson and Husband (2016) provide additional evidence for this type of analysis by showing that final interpretations of agreement attraction cases are not based on the actual string, meaning that the participants infer a plural-marked head noun whereas it is not marked by any plural inflection.
+
+On the other side, some theories assume that agreement attraction is due to an error in the access to the number of the agreement controller (Nicenboim et al., 2018; Wagers et al., 2009).
 Unlike MMT, these models do not assume an erroneous representation to form.
-Rather, the agreement attraction effects surface when there is a feature interference in the ungrammatical sentences like \@ref(item:wagers2009).
+Rather, the agreement attraction effects surface when there is a feature interference in the ungrammatical sentences like \ref{item:wagers2009}.
 This interference is triggered due to the partial match between the sought retrieval cues and the ones within the subject phrase.
@@
 
-# Agreement Attraction in Turkish
-
-Recently, @LagoEtAl2018 demonstrated comparable agreement attraction effects in comprehension with Turkish stimuli. 
+\hypertarget{agreement-attraction-in-turkish}{%
+\section{Agreement Attraction in Turkish}\label{agreement-attraction-in-turkish}}
+
+Recently, Lago et al. (2018) demonstrated comparable agreement attraction effects in comprehension with Turkish stimuli.
 They used the speeded acceptability judgment method with the following question that asks participants whether or not the sentence sounded acceptable.
-They used sentences like (\@ref(item:LagoExp))\footnote{Abbreviations used in the paper are as follows: \printglossaries} with genitive-marked attractors.
+They used sentences like (\ref{item:LagoExp})\footnote{Abbreviations used in the paper are as follows: \printglossaries} with genitive-marked attractors.
 They manipulated the number morphology on the attractor (plural x singular) and the grammaticality of the verb (grammatical (SG) x ungrammatical (PL)).
-The example given here represents all four conditions.
-In an ungrammatical condition with a plural attractor, the word _ressamların_ (painters') is expected to create a grammaticality illusion and mistaken for the agreement controller instead of the head subject _rakibi_ (rival\textsubscript{poss}).
+The example given here represents all four conditions.\\
+In an ungrammatical condition with a plural attractor, the word \emph{ressamların} (painters') is expected to create a grammaticality illusion and mistaken for the agreement controller instead of the head subject \emph{rakibi} (rival\textsubscript{poss}).
 
@@
 that non-intervening genitive marked attractor may create grammaticality illusions in Turkish.
-They base their argument on the inhibition constraint proposed by @NicolEtAl:2016.
-@NicolEtAl:2016 show in a production experiment that genitive attractors do not trigger grammaticality illusions.
+They base their argument on the inhibition constraint proposed by Nicol et al.
+(2016).
+Nicol et al.
+(2016) show in a production experiment that genitive attractors do not trigger grammaticality illusions.
 According to their hypothesis, the reason behind their results is the fact that the participants may never consider genitive-marked NPs as a potential candidate for subjects.
@@
 Because of this local ambiguity, all experimental sentences have two possible parses up until to the end of the sentence.
-Check the following examples in \@ref(parse:LagoExpAcc) and \@ref(parse:LagoExpPoss).
+Check the following examples in \ref{parse:LagoExpAcc} and \ref{parse:LagoExpPoss}.
 
@@
 
-The local ambiguity between the accusative and the possessive is not resolved until the verb _uzaklaştı_.
+The local ambiguity between the accusative and the possessive is not resolved until the verb \emph{uzaklaştı}.
 Regardless of the assumption for parallel or serial processing, there may exist certain conditions where participants are stuck with a rival-\Acc{} representation.
@@
 
-# Experiment 1
-
-```{r Exp1:DataWrangling, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-
-fname_data <- "../workspace_exp1/exp_data.rds"
-data_exp1 <- readRDS(fname_data)
-fname_form <- "../workspace_exp1/exp_form.rds"
-form_exp1 <- readRDS(file = fname_form)
-
-### note: the low accuracy on fillers is not caused by a couple of items
-###       -> see below
-# filler_avgs <- 
-# data_exp1 %>% subset(Type == "filler") %>% group_by(Item, condition) %>% 
-#               summarize(M = mean(ResponseYes, na.rm = T)) %>%
-#               arrange(condition, Item)
-# fillers %>% subset(condition == "a") 
-# fillers %>% subset(condition == "b")
-###
-
-# compute by-subject percentages of 'yes' responses, and average RTs 
-avg_by_subj <- data_exp1 %>%
-                group_by(subject, experiment, condition, 
-                         grammatical, verb_num, attractor_num) %>%
-                summarize(avRT = mean(RT), 
-                          p_yes = mean(ResponseYes, na.rm = T), 
-                          N = sum(!is.na(ResponseYes))  )
-
-# reformat by-subject averages to a wide format
-avg_by_subj_wide <- avg_by_subj %>% 
-                      mutate(expcond = paste(experiment, condition, sep="_")) %>% 
-                      ungroup() %>%
-                      dplyr::select(-experiment, -condition, -avRT, -N,
-                                    -grammatical, -verb_num, -attractor_num) %>%
-                      tidyr::spread(expcond, p_yes) %>% 
-                      mutate(delta_dc = AgrAttr_d - AgrAttr_c)
-
-# Load Lago et al.'s monolingual data
-fname_lagoetal <- "../Data/Lago_et_al/Lago_data.csv"
-df_lagoetal <- read.csv(fname_lagoetal, encoding = "UTF-8", as.is = T)
-df_lagoetal %<>% subset(Group == "monolingual")
-df_lagoetal %<>% dplyr::select(-Accuracy, -L1:-Group, -List:-SelfRateGerman)
-
-# Note: All rows with Experiment == "offline" also seem to be for 
-#       the UNP task ('Grammatical' is NA). I wonder if these were
-#       the same subjects, or if the subject labels were simply the same
-#       for the two experiments.
-with(df_lagoetal, stopifnot( is.na(Grammatical) == (Experiment == "offline") ))
-
-df_lagoetal_unp <- df_lagoetal %>% 
-                    subset(is.na(Grammatical)) %>%
-                    dplyr::select(-Grammatical:-Label)
-df_lagoetal_attr <- df_lagoetal %>% 
-                  subset(!is.na(Grammatical)) %>%
-                  dplyr::select(-Distance:-NewCond)
-
-df_lagoetal_attr %<>% mutate(ResponseYes = (Response == "yes") ) %>% 
-                      dplyr::select(-Response)
-df_lagoetal_attr %<>% ungroup() %>%
-                      dplyr::select(grammatical=Grammatical,
-                                    attractor_num=Attractor,
-                                    experiment=Experiment,
-                                    lagoetal_condition=Condition, 
-                                    subject=Participant, 
-                                    item=Item,
-                                    ResponseYes,
-                                    RT)
-
-# map to our condition labels
-lagoetal_condition_mapping <- data.frame( condition = c("a", "b", "c", "d"),
-                                          lagoetal_condition = c("d", "b", "c", "a"), 
-                                          stringsAsFactors = F)
-df_lagoetal_attr %<>% left_join( lagoetal_condition_mapping, by = "lagoetal_condition" )
-
-# compute by-subject percentages of 'yes' responses, and average RTs 
-avg_by_subj_lagoetal <- df_lagoetal_attr %>%
-                            group_by(subject, experiment, condition, grammatical, attractor_num) %>%
-                            summarize(avRT = mean(RT), 
-                                      p_yes = mean(ResponseYes, na.rm = T), 
-                                      N = sum(!is.na(ResponseYes))  )
-
-# reformat by-subject averages to a wide format
-avg_by_subj_lagoetal_wide <- avg_by_subj_lagoetal %>% 
-                                    mutate(expcond = paste(experiment, condition, sep="_")) %>% 
-                                    ungroup() %>%
-                                    dplyr::select(-experiment, -condition, -avRT, -N,
-                                                  -grammatical, -attractor_num) %>%
-                                    tidyr::spread(expcond, p_yes) %>% 
-                                    mutate(delta_dc = online_d - online_c)
-
-# identify bad participants 
-bad_subjects <- subset(avg_by_subj_wide, delta_dc <= 0.25 ) %>% .$subject
-data_exp1_clean <- data_exp1 %>% subset(!subject %in% bad_subjects)
-
-# identify bad participants 
-bad_subjects_lagoetal <- subset(avg_by_subj_lagoetal_wide, delta_dc <= 0.25 ) %>% .$subject
-df_lagoetal_attr_clean <- df_lagoetal_attr %>% subset(!subject %in% bad_subjects_lagoetal)
-
-# merge both datasets
-df_merge_exp1 <- data_exp1_clean %>% ungroup() %>% 
-                      dplyr::select(source=experiment, 
-                                    grammatical, 
-                                    attractor_num,
-                                    # condition,
-                                    subject, 
-                                    item=Item,
-                                    ResponseYes, 
-                                    RT)
-df_merge_exp1$experiment <- "Experiment 1"
-df_merge_exp1$grammatical %<>% dplyr::recode(gram="grammatical", ungram="ungrammatical")
-df_merge_exp1$attractor_num %<>% dplyr::recode(pl="plural", sg="singular")
-
-df_merge_exp1$item %<>% as.integer()
-df_merge_exp1$subject %<>% as.character()
-
-df_merge_lago <- df_lagoetal_attr_clean %>%
-                      ungroup() %>% 
-                      dplyr::select(grammatical, attractor_num,
-                                    subject, item, ResponseYes, RT)
-df_merge_lago$experiment <- "Lago et al. (2018)" 
-df_merge_lago$source <- NA
-
-```
-
-```{r Exp1:wordFreq, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-# word frequencies: 
-# Utku: are these still relevant for us?
-
-word_freq <- readxl::read_excel("../Data/frequencies_exp1_and_lago.xlsx", sheet = 1)
-word_freq$freq_percentage %<>% as.numeric()
-word_freq %<>% dplyr::select(-freq_standardized, -freq_percentage, -word)
-word_freq %<>% tidyr::spread(place, freq_count)
-
-word_freq %<>% dplyr::group_by(exp) %>% 
-               dplyr::mutate( freq_cat_n1 = ifelse(n1 > median(n1), "high", "low"),
-                              freq_cat_n2 = ifelse(n2 > median(n2), "high", "low"),
-                              freqlog_n1 = scale(log(n1)),
-                              freqlog_n2 = scale(log(n2)),
-                              freqlog_n1n2 = log(n1) - log(n2)
-                            ) %>% 
-                ungroup()
-# word_freq$freq_cat_n1 %<>% as.factor()
-# word_freq$freq_cat_n2 %<>% as.factor()
-
-word_freq_exp1 <- word_freq %>% subset(exp == "exp1") %>% dplyr::select(-exp)
-df_merge_exp1 %<>% left_join(word_freq_exp1, by = "item")
-
-word_freq_lago <- word_freq %>% subset(exp == "lagoetal") %>% dplyr::select(-exp)
-df_merge_lago %<>% left_join(word_freq_lago, by = "item")
-df_merge_lago$item %<>% add(1000)
-
-df_merged <- dplyr::bind_rows(df_merge_exp1, df_merge_lago)
-df_merged$subject %<>% as.factor()
-df_merged$item %<>% as.factor()
-```
-
-Previous work in agreement attraction found significant effects in comprehension using forced-choice acceptability judgment tasks [@HammerlyEtAl:2019; @LagoEtAl2018; @WagersEtAl:2009].
+\hypertarget{experiment-1}{%
+\section{Experiment 1}\label{experiment-1}}
+
+Previous work in agreement attraction found significant effects in comprehension using forced-choice acceptability judgment tasks (Hammerly et al., 2019; Lago et al., 2018; Wagers et al., 2009).
 The goal of experiment 1 is to control for the effect of head noun ambiguity on the magnitude of agreement attraction effect.
-To this end, we replicated @LagoEtAl2018 experiment with unambiguous head nouns.
+To this end, we replicated Lago et al.
+(2018) experiment with unambiguous head nouns.
 We disambiguated the cases by using vowel-ending head nouns.
 When attached to a vowel-ending noun, the accusative case and the possessive surface with a different floating consonant.
-For example, we changed sentence (\@ref(item:LagoExpContrast)) to sentence (\@ref(item:OurExpContrast)).
+For example, we changed sentence (\ref{item:LagoExpContrast}) to sentence (\ref{item:OurExpContrast}).
 
@@
 
-## Participants
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
 
 We recruited 118 undergraduate students to participate in Experiment 1 in exchange for course credit.
-All participants were native speakers of Turkish, with an average age of `r printnum(mean(form_exp1$Age))` (range: `r min(form_exp1$Age)` -- `r max(form_exp1$Age)`).
+All participants were native speakers of Turkish, with an average age of 20.14 (range: 18 -- 32).\\
 Experiment were carried out following the Declaration of Helsinki and the regulations concerning ethics at research in Bo\u{g}azi\c{c}i University.
@@
 
-## Materials
-
-We used 40 sets of sentences like \@ref(item:exp1ExperimentalItems), in which we manipulated 
+\hypertarget{materials}{%
+\subsection{Materials}\label{materials}}
+
+We used 40 sets of sentences like \ref{item:exp1ExperimentalItems}, in which we manipulated
 (i) the number of the attractor noun, and
@@
 Plural number and plural agreement were both marked with the affix \textit{-ler/-lar}, while singular number and singular agreement were marked with its absence.
-We have used the experimental items in @LagoEtAl2018 as a base. 
+We have used the experimental items in Lago et al. (2018) as a base.
 All sentences started with a complex subject NP like \textit{`the manager's cook'} (\textit{yöneticinin aşcısı}), in which the possessor, which functioned as the attractor, carried genitive case, and the head noun carried unambiguous possessive case.
@@
 Moreover, as in the original study, the properties of the nouns in the complex subject NP and the relation between these nouns held constant in our replication.
-The distribution of the verb types followed the same pattern as in @LagoEtAl2018, namely twenty unergatives, eighteen unaccusatives, and two optionally transitive verbs. 
-Both in @LagoEtAl2018 and in our replication, pre-verbal adverbials consisting of 2-3 words (15 characters on average) are used.
+The distribution of the verb types followed the same pattern as in Lago et al. (2018), namely twenty unergatives, eighteen unaccusatives, and two optionally transitive verbs.
+Both in Lago et al.
+(2018) and in our replication, pre-verbal adverbials consisting of 2-3 words (15 characters on average) are used.
 We changed this adverbials for plausability reasons, such that with head nouns like cooks we used locational adverbs like kitchen, instead of the stage.
-Unlike the @LagoEtAl2018 sentences, our head nouns were vowel-ending, and therefore not ambiguous between accusative case, for which the case suffix is \textit{-yI}, and possessive case, for which the suffix is \textit{-sI}.
+Unlike the Lago et al.
+(2018) sentences, our head nouns were vowel-ending, and therefore not ambiguous between accusative case, for which the case suffix is \textit{-yI}, and possessive case, for which the suffix is \textit{-sI}.
 
@@
 
-We intermixed our experimental sentences with 40 filler sentences of two types, as illustrated in \@ref(item:exp1FillerItems). 
+We intermixed our experimental sentences with 40 filler sentences of two types, as illustrated in \ref{item:exp1FillerItems}.
 To compensate for the fact that among experimental sentences, all ungrammatical sentences ended in a plural-agreeing verb, while all grammatical sentences ended in a singular-agreeing verb, we included 20 grammatical sentences with plural verbs, and 20 ungrammatical sentences with singular agreement.
@@
 However, in filler items, they were the controller of an embedded clause which serves as a adverbial.
-In grammatical fillers, we have made use of pro-dropped subject strategy in Turkish; thus, it enabled us to use plural verb without having ungrammatical sentences as in \@ref(item:exp1GrammaticalFiller).
+In grammatical fillers, we have made use of pro-dropped subject strategy in Turkish; thus, it enabled us to use plural verb without having ungrammatical sentences as in \ref{item:exp1GrammaticalFiller}.
 The object \textit{tutarsızlık} is a bare nominal preceding a light verb construction.
@@
 
-## Procedure
+\hypertarget{procedure}{%
+\subsection{Procedure}\label{procedure}}
 
@@
 Between each word, participants saw a blank screen for 100 ms.
-Participants pressed the key 'P' for \textit{'acceptable'} and 'Q' for \textit{'unacceptable'}.
+Participants pressed the key `P' for \textit{'acceptable'} and `Q' for \textit{'unacceptable'}.
 They were instructed to provide an acceptability rating before the 5,000 ms deadline.
@@
 
-## Analysis
-
-Since our aim was to test whether the morphological ambiguity present in the @LagoEtAl2018 items affected the presence or magnitude of the agreement attraction effect, statistically, we needed to test for the presence of an interaction between
+\hypertarget{analysis}{%
+\subsection{Analysis}\label{analysis}}
+
+Since our aim was to test whether the morphological ambiguity present in the Lago et al.
+(2018) items affected the presence or magnitude of the agreement attraction effect, statistically, we needed to test for the presence of an interaction between
 (i) the presence of the morphological ambiguity on the head noun, and
@@
 Prior to analysis we removed the data for all participants who failed to show sufficient sentitivity to the effect of grammaticality in singular attractor conditions, i.e., when no agreement attraction was expected.
-Specifically, we removed all participants for whom the difference in the percentage of 'yes' responses between the grammatical condition \@ref(item:exp1expitem-sgsg) and the ungrammatical condition \@ref(item:exp1expitem-sgpl) was below the threshold of 25 percentage points.
-As a result, we excluded `r length(bad_subjects)` participants from experiment 1, and `r stopifnot(length(bad_subjects_lagoetal) == 1)` one participant from the Lago et al.
-data
-
-We used the R packages brms [@brms] and rstan [@stan] to fit Bayesian hierarchical models [e.g., @GelmanHill2007]. We analyzed only experimental sentences, and used 
+Specifically, we removed all participants for whom the difference in the percentage of `yes' responses between the grammatical condition \ref{item:exp1expitem-sgsg} and the ungrammatical condition \ref{item:exp1expitem-sgpl} was below the threshold of 25 percentage points.
+As a result, we excluded 10 participants from experiment 1, and one participant from the Lago et al.~data
+
+We used the R packages brms (Bürkner, 2018) and rstan (Stan Development Team, 2019) to fit Bayesian hierarchical models (e.g., Gelman \& Hill, 2007). We analyzed only experimental sentences, and used
 (i) grammaticality of the sentence,
@@
 
-## Results
-
-```{r Exp1:PreparePlots, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-df_exp1_na_nofillers <- subset(df_merge_exp1, is.na(ResponseYes) & source != "filler")
-df_merged %<>% subset( !is.na(ResponseYes) )
-
-df_merged %<>% mutate(ResponseCorrect = (ResponseYes == (grammatical == "grammatical") ) )
-df_merged_nonna <- df_merged %>% subset(!is.na(ResponseYes))
-
-# avg_clean <- 
-# df_merged %>% subset(experiment == "Lago et al. (2018)") %>%
-#      group_by(experiment, source, grammatical, attractor_num, subject) %>%
-#      summarize(p_yes = mean(ResponseYes, na.rm=T)) %>%
-#      summarize(p_yes = mean(p_yes))
-
-avg_clean <- list()
-avg_clean$resp <- df_merged_nonna %>% 
-              plyr::ddply(c("experiment"), function(df) {
-              df %>% se_cousineau(n_conditions = 4, subject, DV = ResponseYes, 
-                           group = c("experiment", "source", "grammatical", "attractor_num"), 
-                           is_proportion = TRUE)
-})
-
-avg_clean$rt <- df_merged_nonna %>%
-              plyr::ddply(c("experiment"), function(df) {
-              df %>% se_cousineau(n_conditions = 4, subject, DV = RT, 
-                           group = c("experiment", "source", "grammatical", "attractor_num"), 
-                           is_proportion = FALSE)
-})
-
-avg_clean$rt_correct <- df_merged_nonna %>% subset(ResponseCorrect) %>%
-              plyr::ddply(c("experiment"), function(df) {
-              df %>% se_cousineau(n_conditions = 4, subject, DV = RT, 
-                           group = c("experiment", "source", "grammatical", "attractor_num"), 
-                           is_proportion = FALSE)
-})
-
-avg_exp <- avg_clean %>% lapply(function(df) { df %>% subset(is.na(source) | source != "filler") })
-avg_fillers <- avg_clean %>% lapply(function(df) { df %>% subset(source == "filler") })
-
-pd <- position_dodge(0.0)
-p_avg_resp <- avg_exp$resp %>%
-              ggplot(aes(grammatical, M, #linetype = attractor_num, 
-                         color = attractor_num, group = attractor_num)) + 
-                geom_point(position = pd) + geom_line(position = pd) + 
-                facet_wrap(~experiment)
-
-p_avg_resp <- p_avg_resp + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1, position = pd)
-
-# p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) + 
-#                             geom_point(data = avg_fillers) +
-
-p_avg_resp <- p_avg_resp + theme( strip.background = element_rect(fill="white") ) +
-                           theme_bw() + xlab("") + ylab("Percentage 'acceptable'")
-p_avg_resp <- p_avg_resp + scale_y_continuous(labels=scales::percent)#, breaks = c(0, .25, .5, .75, 1))
-p_avg_resp <- p_avg_resp + theme_bw()
-p_avg_resp <- p_avg_resp + scale_color_discrete(name = "Attractor Number")
-
-avg_exp_resp_exp1 <- avg_exp$resp %>% subset(experiment == "Experiment 1")
-avg_exp_resp_lagoetal <- avg_exp$resp %>% subset(experiment == "Lago et al. (2018)")
-```
-
-```{r Exp1:PrepareTextInputs, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-exp1_cur_entry1 = avg_exp$resp %>% filter(experiment == "Experiment 1", grammatical == "ungrammatical", attractor_num == "plural")
-exp1_cur_entry2 = avg_exp$resp %>% filter(experiment == "Experiment 1", grammatical == "ungrammatical", attractor_num == "singular")
-
-exp1_cur_entry3 = avg_exp$resp %>% filter(experiment == "Experiment 1", grammatical == "grammatical", attractor_num == "singular")
-exp1_cur_entry4 = avg_exp$resp %>% filter(experiment == "Experiment 1", grammatical == "grammatical", attractor_num == "plural")
-
-lago_cur_entry1 = avg_exp$resp %>% filter(experiment == "Lago et al. (2018)", grammatical == "ungrammatical", attractor_num == "plural")
-lago_cur_entry2 = avg_exp$resp %>% filter(experiment == "Lago et al. (2018)", grammatical == "ungrammatical", attractor_num == "singular")
-```
-
-Figure \@ref(fig:exp1AvgResponse) shows the average proportions of ‘acceptable’ responses by experimental condition for both the original experiment in @LagoEtAl2018 and our replication with unambiguous possessive marking.
+\hypertarget{results}{%
+\subsection{Results}\label{results}}
+
+Figure \ref{fig:exp1AvgResponse} shows the average proportions of `acceptable' responses by experimental condition for both the original experiment in Lago et al.
+(2018) and our replication with unambiguous possessive marking.
 It shows that ungrammatical sentences with plural attractors are rated as acceptable more often
-(M = `r printnum(exp1_cur_entry1$M)`, 
-SE = `r printnum(exp1_cur_entry1$SE)`) 
+(M = 0.22,
+SE = 0.01)
 than their counterparts with singular attractors
-(M=`r printnum(exp1_cur_entry2$M)`, 
-SE=`r printnum(exp1_cur_entry2$SE)`).
-The magnitude of the effect (`r sprintf("%0.2f", exp1_cur_entry1$M-exp1_cur_entry2$M)`) was in line with the findings reported in @LagoEtAl2018, where the difference was `r sprintf("%0.2f", lago_cur_entry1$M-lago_cur_entry2$M)`.
+(M=0.11,
+SE=0.01).
+The magnitude of the effect (0.10) was in line with the findings reported in Lago et al. (2018), where the difference was 0.11.
 Accuracy rates for grammatical conditions were nearly equal
-(M = `r printnum(exp1_cur_entry3$M)` and `r printnum(exp1_cur_entry4$M)`, SE = `r printnum(exp1_cur_entry3$SE)` and `r printnum(exp1_cur_entry4$SE)`, for singular and plural attractors respectively).
-
-```{r exp1AvgResponse, fig.height=3 ,fig.cap="Average response times for experiment 1 and experiment 2."}
-print(p_avg_resp)
-```
+(M = 0.93 and 0.92, SE = 0.01 and 0.01, for singular and plural attractors respectively).
+
+\begin{figure}
+\centering
+\includegraphics{ongoing_paper_files/figure-latex/exp1AvgResponse-1.pdf}
+\caption{\label{fig:exp1AvgResponse}Average response times for experiment 1 and experiment 2.}
+\end{figure}
 
 A Bayesian GLM assuming a Bernoulli distribution with a probit-link function was fit to participants' `acceptable' responses.
-The model's estimates and 95\% credible intervals are shown in Figure \@ref(fig:exp1ResponseModel).
-<!-- They confirm the observations we stated above: the positive interaction between sentence grammaticality and attractor number is in line with a larger effect of attractor number in ungrammatical sentences.
--->
-
-```{r Exp1:BayesianModels, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-df_merged %<>% within(., {
-  cGrammatical <- ifelse(grammatical == "grammatical", .5, -.5)
-  cUngrammatical <- ifelse(grammatical == "ungrammatical", .5, -.5)
-  cAttractorPlural <- ifelse(attractor_num == "plural", .5, -.5)
-  cEndsInConsonant <- ifelse(experiment != "Experiment 1", .5, -.5)
-  #cFreqlog_n1n2 <- scale(freqlog_n1n2)
-  #cFreqlog_n1 <- scale(freqlog_n1)
-  #cFreqlog_n2 <- scale(freqlog_n2)
-})
-df_merged_nofillers <- df_merged %>% subset(is.na(source) | source != "filler")
-
-# ## test model parameterization using a simple GLM first
-# m <- glm(ResponseYes ~ (cFreqlog_n1 + cFreqlog_n2) *
-#            cEndsInConsonant * cUngrammatical * cAttractorPlural,
-#          data = df_merged_nofillers,
-#          family = binomial("probit"))
-# summary(m)
-
-n_chains <- 4
-n_cores <- 4
-n_iter <- 2000
-
-fname_exp1_responses <- "../workspace_exp1/fit_responses"
-m_responses <- brm(ResponseYes ~ cEndsInConsonant * cUngrammatical * cAttractorPlural + 
-                                 (cUngrammatical * cAttractorPlural + 1| subject) + 
-                                 (cUngrammatical * cAttractorPlural + 1| item),
-                   data = df_merged_nofillers,
-                   family = bernoulli("probit"), 
-                   chains = n_chains, cores = n_cores, iter = n_iter,
-                   file = fname_exp1_responses)
-
-fname_exp1_responses_exp1only <- "../workspace_exp1/fit_responses_exp1only"
-m_responses_exp1only <- brm(ResponseYes ~ cUngrammatical * cAttractorPlural * freqlog_n1n2 + 
-                                 (cUngrammatical * cAttractorPlural * freqlog_n1n2 + 1| subject) + 
-                                 (cUngrammatical * cAttractorPlural + 1| item),
-                   data = df_merged_nofillers %>% subset(experiment == "Experiment 1"),
-                   family = bernoulli("probit"), 
-                   chains = n_chains, cores = n_cores, iter = n_iter, init_r = .1,
-                   file = fname_exp1_responses_exp1only
-                   )
-
-fname_exp1_responses_Lagoonly <- "../workspace_exp1/fit_responses_lagoonly"
-m_responses_Lagoonly <- brm(ResponseYes ~ cUngrammatical * cAttractorPlural * freqlog_n1n2 + 
-                                 (cUngrammatical * cAttractorPlural * freqlog_n1n2 + 1| subject) + 
-                                 (cUngrammatical * cAttractorPlural + 1| item),
-                   data = df_merged_nofillers %>% subset(experiment != "Experiment 1"),
-                   family = bernoulli("probit"), 
-                   chains = n_chains, cores = n_cores, iter = n_iter, init_r = .1,
-                   file = fname_exp1_responses_Lagoonly)
-
-fname_exp1_rts <- "../workspace_exp1/fit_responses_rt"
-m_rts <- brm(RT ~ cEndsInConsonant * cUngrammatical * cAttractorPlural * freqlog_n1n2 +
-                                 (cUngrammatical * cAttractorPlural * freqlog_n1n2 + 1| subject) +
-                                 (cUngrammatical * cAttractorPlural + 1| item),
-                   data = df_merged_nofillers,
-                   family = lognormal(),
-                   chains = n_chains, cores = n_cores, iter = n_iter,
-                   file = fname_exp1_rts)
-
-model_results_table <- fixef(m_responses, summary = T, robust = F) %>% 
-  as.data.frame() #%>% tibble::rownames_to_column("variables")
-
-```
-
-The main effect of \textit{ungrammaticality} (`r print_estimate_with_ci( m_responses, 'cUngrammatical' )`) indicates that, on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences.
-Meanwhile, the positive interaction between \textit{ungrammaticality} and \textit{attractor number} (`r print_estimate_with_ci( m_responses, 'cUngrammatical:cAttractorPlural')`) indicated a larger effect of attractor number in ungrammatical conditions, and thus a number agreement attraction effect.
-Importantly, there was no evidence for a three-way interaction between \textit{the presence of ambiguity}, \textit{ungrammaticality} and \textit{attractor number} (`r print_estimate_with_ci( m_responses, 'cEndsInConsonant:cUngrammatical:cAttractorPlural')`).
-
-<!-- % to-do:
-Importantly, even if there was an interaction with experiment, it's relatively small, so it wouldn't reduce the other interaction to 0.
-
-Moreover, this findings are also predicted by cue-based retrieval models \citep{engelmann2019effect, vasishth2019computational} and last rendition of marking and morphing theory by \citet{HammerlyEtAl:2019}.
-does it tho?
-especially with regards to what sol lago says: gen and morphophonology gives clues.
-maybe we should take a look at speeded acceptability?
-maybe this is not the perfect place to write this. -->
-
-```{r Exp1:ModelPlots, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-contrast_names <- c("cUngrammatical" = "Ungrammaticality",
-                    "cAttractorPlural" = "Plural Attactor",
-                    "cUngrammatical:cAttractorPlural" = "Ungrammaticality * Plural Attractor",
-                    "cEndsInConsonant" = "Ambiguity",
-                    "cEndsInConsonant:cUngrammatical" = "Ambiguity * Ungrammaticality",
-                    "cEndsInConsonant:cAttractorPlural" = "Ambiguity * Plural Attractor",
-                    "cEndsInConsonant:cUngrammatical:cAttractorPlural" = "Ambiguity * Ungrammaticality * Plural Attractor")
-
-p_m_response <- 
-  create_model_coefs_plot( m_responses, 
-        plot_stats = T, map_names = contrast_names,
-        expand_right = 2.5, expand_top = 2, x_stat_adjust = 1.1,
-        x_breaks = c(-3,-2,-1, 0,1, 2) ) + 
-        xlab("Estimate (probit)")
-contrast_names_exp1 <- c("cUngrammatical" = "Ungrammaticality",
-                         "cAttractorPlural" = "Plural Attactor",
-                         "freqlog_n1n2"="log Frequency: N1-N2",
-                         "cUngrammatical:freqlog_n1n2" = "Ungrammaticality * log Frequency: N1-N2",
-                         "cAttractorPlural:freqlog_n1n2" = "Plural Attactor * log Frequency: N1-N2",
-                         "cUngrammatical:cAttractorPlural" = "Ungrammaticality * Plural Attractor",
-                         "cUngrammatical:cAttractorPlural:freqlog_n1n2" = "Ungrammaticality * Plural Attractor * log Frequency: N1-N2"
-                        )
-
-p_m_response_exp1 <- 
-  create_model_coefs_plot( m_responses_exp1only, 
-        plot_stats = T, map_names = contrast_names_exp1,
-        expand_right = 2.5, expand_top = 2, x_stat_adjust = 1.1,
-        x_breaks = c(-3,-2,-1, 0,1, 2) ) + 
-        xlab("Estimate (probit)")
-
-p_m_response_exp1 <- p_m_response_exp1 + facet_wrap(~"Experiment 1") + annotate(x=-3, xend=2, y=0, yend=0, lwd=0.25, geom="segment")
-
-p_m_response_lago <- 
-  create_model_coefs_plot( m_responses_Lagoonly, 
-        plot_stats = T, map_names = contrast_names_exp1,
-        expand_right = 2.5, expand_top = 2, x_stat_adjust = 1.1,
-        x_breaks = c(-3,-2,-1, 0,1, 2) ) + 
-        xlab("Estimate (probit)")
-
-p_m_response_lago <- p_m_response_lago + facet_wrap(~"Lago et al. (2018)") + annotate(x=-3, xend=2, y=0, yend=0, lwd=0.25, geom="segment")
-
-p_m_response_exp1_and_lago <- ggarrange(p_m_response_exp1, p_m_response_lago, ncol = 1)
-
-```
-
-```{r exp1ResponseModel, fig.height=3 ,fig.cap="Estimates and 95% credible intervals for the regression coefficients for the model of Experiment 1 and Lago et al. (2018)."}
-suppressWarnings({
-print(p_m_response + annotate(x=-3, xend=2, y=0, yend=0, lwd=0.25, geom="segment"))
-})
-```
-
-```{r exp1ResponseModelSepExp1AndLago, fig.height=5  ,fig.cap="Estimates and 95% credible intervals for the regression coefficients for Experiment1 and Lago et al. (2018)."}
-suppressWarnings({
-print(p_m_response_exp1_and_lago)
-})
-```
-
-## Discussion
-
-In Experiment 1, we have found number attraction effects in Turkish using genitive possessive structures, as it is also attested in @LagoEtAl2018.
-To account for their findings, @LagoEtAl2018 assume a cue-based memory retrieval mechanism.
-That is, they assume that upon reaching the verb, the parser attempts to retrieve its agreement controller (the subject) using a cue-based retrieval mechanism [@LewisVasishth2005,@JagerEngelmannVasishth:2017].
+The model's estimates and 95\% credible intervals are shown in Figure \ref{fig:exp1ResponseModel}.
+
+The main effect of \textit{ungrammaticality} (\(\hat{\beta}=-3.09;\) \(CI=[-3.35; -2.84];\) \(P(\beta<0)> .999\)) indicates that, on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences.
+Meanwhile, the positive interaction between \textit{ungrammaticality} and \textit{attractor number} (\(\hat{\beta}=0.72;\) \(CI=[0.42; 1.02];\) \(P(\beta<0)< .001\)) indicated a larger effect of attractor number in ungrammatical conditions, and thus a number agreement attraction effect.
+Importantly, there was no evidence for a three-way interaction between \textit{the presence of ambiguity}, \textit{ungrammaticality} and \textit{attractor number} (\(\hat{\beta}=0.31;\) \(CI=[-0.19; 0.81];\) \(P(\beta<0)= .12\)).
+
+\begin{figure}
+\centering
+\includegraphics{ongoing_paper_files/figure-latex/exp1ResponseModel-1.pdf}
+\caption{\label{fig:exp1ResponseModel}Estimates and 95\% credible intervals for the regression coefficients for the model of Experiment 1 and Lago et al.~(2018).}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{ongoing_paper_files/figure-latex/exp1ResponseModelSepExp1AndLago-1.pdf}
+\caption{\label{fig:exp1ResponseModelSepExp1AndLago}Estimates and 95\% credible intervals for the regression coefficients for Experiment1 and Lago et al.~(2018).}
+\end{figure}
+
+\hypertarget{discussion}{%
+\subsection{Discussion}\label{discussion}}
+
+In Experiment 1, we have found number attraction effects in Turkish using genitive possessive structures, as it is also attested in Lago et al.
+(2018).
+To account for their findings, Lago et al.
+(2018) assume a cue-based memory retrieval mechanism.
+That is, they assume that upon reaching the verb, the parser attempts to retrieve its agreement controller (the subject) using a cue-based retrieval mechanism (Lewis \& Vasishth, 2005, p.
+@JagerEngelmannVasishth:2017).
 The assumption is that in sentences such as \ref{item:exp1ExperimentalItems}, features such as case and number information are used to identify the agreement controller in memory.
@@
 This cannot happen in ungrammatical singular attractor conditions.
-This difference in the probability of erroneous retrievals is presumably what surfaced as a number agreement attraction effect, as observed in @LagoEtAl2018, and our Experiment 1.
-
-In their work, @LagoEtAl2018 argue that the agreement attraction in genitive-possessive structures in Turkish is due to the use of genitive case as a marker of embedded subjects in Turkish, i.e.
-differential subject marking (DSM) properties of Turkish [@kornfilt2009dom].
+This difference in the probability of erroneous retrievals is presumably what surfaced as a number agreement attraction effect, as observed in Lago et al.
+(2018), and our Experiment 1.
+
+In their work, Lago et al.
+(2018) argue that the agreement attraction in genitive-possessive structures in Turkish is due to the use of genitive case as a marker of embedded subjects in Turkish, i.e.~differential subject marking (DSM) properties of Turkish (Kornfilt, 2009).
 They argue that the genitive case in Turkish may not provide strong cue against subjecthood due to DSM while it does in English.
-Following this logic, we hypothesized that the other phenomenon that gives a strong clue against the subjecthood should inhibit the illusionary dependencies as argued in @NicolEtAl:2016.
-One such phenomenon was present in the experimental items used in @LagoEtAl2018: the morpho-phonologic ambiguity between the accusative and the possessive case.
+Following this logic, we hypothesized that the other phenomenon that gives a strong clue against the subjecthood should inhibit the illusionary dependencies as argued in Nicol et al.
+(2016).
+One such phenomenon was present in the experimental items used in Lago et al.
+(2018): the morpho-phonologic ambiguity between the accusative and the possessive case.
 Since they use only consonant ending heads, the marking on the head is ambiguous between the accusative and the possessive marking.
@@
 Nevertheless, we found that when the possessive marker is disambiguated agreement attraction does not diminish in effect size.
-As seen in Figure \@ref(fig:exp1ResponseModel), we successfully replicated the findings of @LagoEtAl2018 with disambiguated head nouns.
+As seen in Figure \ref{fig:exp1ResponseModel}, we successfully replicated the findings of Lago et al.
+(2018) with disambiguated head nouns.
 Thus, we conclude that the morpho-phonological possessive-accusative ambiguity plays no role in number attraction in Turkish.
@@
 Upon such cases, readers may end up using extremely shallow processing methods such as matching the agreement-wise unrelated but form-wise related elements.
-We present our hypothesized decision tree in Figure \@ref(fig:mptModel).
+We present our hypothesized decision tree in Figure \ref{fig:mptModel}.
 
@@
 
-<!-- I will fill this one in, but I cannot find the picture of your whiteboard. -->
-
 The aim of our second experiment is to test whether agreement attraction in Turkish is be an instance of a \textit{form-driven processing strategy}.
@@
 In such cases, participants may choose to classify sentences with plural-agreement-bearing verbs as acceptable if they have a memory of a nominal plural morpheme in the sentence.
-Such a response strategy would lead to a larger number of ‘acceptable’ responses in ungrammatical plural attractor conditions than in ungrammatical singular attractor conditions even when there is no interfering noun with plural morphology but, let's say, a plural verb.
-
-# Experiment 2
-
-```{r Exp2:DataWrangling, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-fname_data2 <- "../workspace_exp2/exp_data.rds"
-data_exp2 <- readRDS(file = fname_data2)
-fname_form <- "../workspace_exp2/exp_form.rds"
-form_exp2 <- readRDS(file = fname_form)
-
-# compute by-subject percentages of 'yes' responses, and average RTs 
-avg_by_subj2 <- data_exp2 %>%
-                group_by(subject, experiment, condition, 
-                         grammatical, verb_num, attractor_num) %>%
-                summarize(avRT = mean(RT), 
-                          p_yes = mean(ResponseYes, na.rm = T), 
-                          N = sum(!is.na(ResponseYes))  )
-
-# reformat by-subject averages to a wide format
-avg_by_subj_wide2 <- avg_by_subj2 %>% 
-                      mutate(expcond = paste(experiment, condition, sep="_")) %>% 
-                      ungroup() %>%
-                      dplyr::select(-experiment, -condition, -avRT, -N,
-                                    -grammatical, -verb_num, -attractor_num) %>%
-                      tidyr::spread(expcond, p_yes) %>% 
-                      mutate(delta_dc = AgrAttr_d - AgrAttr_c)
-# identify bad participants 
-bad_subjects2 <- subset(avg_by_subj_wide2, delta_dc <= 0.25 ) %>% .$subject
-
-data_exp2_clean <- data_exp2 %>% subset(!subject %in% bad_subjects2)
-
-df_merge_exp2 <- data_exp2_clean %>% ungroup() %>% 
-                      dplyr::select(source=experiment, grammatical, attractor_num, # condition,
-                                    subject, item=Item,
-                                    ResponseYes, RT)
-df_merge_exp2$experiment <- "Experiment 2"
-df_merge_exp2$grammatical %<>% dplyr::recode("gram"="grammatical", "ungram"="ungrammatical")
-df_merge_exp2$attractor_num %<>% dplyr::recode("pl"="plural", "sg"="singular")
-df_merge_exp2 %<>% mutate( item = sprintf("I2[%s]", as.character(item)), subject = as.character(subject) )
-
-df_exp2_na_nofillers <- subset(df_merge_exp2, is.na(ResponseYes))
-
-df_merge_exp1$item %<>% as.character()
-df_merged2 <- dplyr::bind_rows(df_merge_exp1, df_merge_exp2)
-df_merged2 %<>% mutate( subject = as.character(subject), item = as.character(item) )
-
-df_exp2_na_nofillers <- df_merged2 %>% subset(is.na(ResponseYes) & source != "filler")
-df_merged2_nonna <- df_merged2 %>% subset(!is.na(ResponseYes))
-
-avg_clean2 <- list()
-avg_clean2$resp <- df_merged2_nonna %>% 
-              plyr::ddply(c("experiment"), function(df) {
-              df %>% se_cousineau(n_conditions = 4, subject, DV = ResponseYes, 
-                           group = c("experiment", "source", "grammatical", "attractor_num"), 
-                           is_proportion = TRUE)
-})
-
-avg_clean2$rt <- df_merged2_nonna %>%
-              plyr::ddply(c("experiment"), function(df) {
-              df %>% se_cousineau(n_conditions = 4, subject, DV = RT, 
-                           group = c("experiment", "source", "grammatical", "attractor_num"), 
-                           is_proportion = FALSE)
-})
-
-# TODO: Code ResponseCorrect and re-enable
-# avg_clean$rt_correct <- df_merged2_nonna %>% subset(ResponseCorrect) %>%
-#               plyr::ddply(c("experiment"), function(df) {
-#               df %>% se_cousineau(n_conditions = 4, subject, DV = RT, 
-#                            group = c("experiment", "source", "grammatical", "attractor_num"), 
-#                            is_proportion = FALSE)
-# })
-
-avg_exp2 <- avg_clean2 %>% lapply(function(df) { df %>% subset(is.na(source) | source != "filler") })
-#avg_fillers <- avg_clean %>% lapply(function(df) { df %>% subset(source == "filler") })
-```
-
-```{r Exp2:PrepareTextInputs, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-
-exp2_cur_entry1 = avg_exp2$resp %>% filter(experiment == "Experiment 2", grammatical == "ungrammatical", attractor_num == "plural")
-exp2_cur_entry2 = avg_exp2$resp %>% filter(experiment == "Experiment 2", grammatical == "ungrammatical", attractor_num == "singular")
-
-exp2_cur_entry3 = avg_exp2$resp %>% filter(experiment == "Experiment 2", grammatical == "grammatical", attractor_num == "singular")
-exp2_cur_entry4 = avg_exp2$resp %>% filter(experiment == "Experiment 2", grammatical == "grammatical", attractor_num == "plural")
-```
-
-```{r Exp2:PreparePlots, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-
-avg_exp2 <- avg_clean2$resp %>% subset(is.na(source) | source != "filler") %>% subset(experiment == "Experiment 2")
-avg_fillers2 <- avg_clean2$resp %>% subset(source == "filler") %>% subset(experiment == "Experiment 2")
-
-p_avg_resp2 <- ggplot(avg_exp2, aes(grammatical, M, #linetype = attractor_num, 
-                                    color = attractor_num, group = attractor_num)) + 
-                geom_point(position = pd) + geom_line(position = pd) + 
-                facet_wrap(~experiment) +
-                theme_bw() + theme( strip.background = element_rect(fill="white") ) +
-                xlab("") + ylab("Percentage 'acceptable'")
-
-p_avg_resp2 <- p_avg_resp2 + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1, position = pd)
-p_avg_resp2 <- p_avg_resp2 + scale_y_continuous(labels=scales::percent, limits = c(0, 1))
-p_avg_resp2 <- p_avg_resp2 + scale_color_discrete(name = "Attractor Number")
-```
-
-```{r Exp2:BayesianModels, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-
-df_merged2 %<>% within(., {
-  cGrammatical <- ifelse(grammatical == "grammatical", .5, -.5)
-  cUngrammatical <- ifelse(grammatical == "ungrammatical", .5, -.5)
-  cAttractorPlural <- ifelse(attractor_num == "plural", .5, -.5)
-  cVerbalAttractor <- ifelse(experiment == "Experiment 2", .5, -.5)
-})
-df_merged_nofillers2 <- df_merged2 %>% subset(is.na(source) | source != "filler")
-
-# ## test model parameterization using a simple GLM first
-# m <- glm(ResponseYes ~ cVerbalAttractor * cUngrammatical * cAttractorPlural,
-#          data = df_merged_nofillers2,
-#          family = binomial("probit"))
-# summary(m)
-
-n_chains <- 4
-n_cores <- 4
-n_iter <- 2000
-
-library(brms)
-
-fname_exp2_responses <- "../workspace_exp2/fit_responses"
-m_responses2 <- brm(ResponseYes ~ cVerbalAttractor * cUngrammatical * cAttractorPlural + 
-                                 (cUngrammatical * cAttractorPlural + 1| subject) +
-                                 (cUngrammatical * cAttractorPlural + 1| item),
-                   data = df_merged_nofillers2 %>% subset(!is.na(ResponseYes)),
-                   family = bernoulli("probit"),
-                   file = fname_exp2_responses, 
-                   chains = n_chains, cores = n_cores, iter = n_iter)
-
-fname_exp2only_responses <- "../workspace_exp2/fit_responses_exp2only"
-m_responses2_exp2only <- brm(ResponseYes ~ cUngrammatical * cAttractorPlural + 
-                                 (cUngrammatical * cAttractorPlural + 1| subject) +
-                                 (cUngrammatical * cAttractorPlural + 1| item),
-                   data = df_merged_nofillers2 %>% 
-                              subset(!is.na(ResponseYes)) %>% 
-                              subset(experiment == "Experiment 2"),
-                   family = bernoulli("probit"),
-                   file = fname_exp2only_responses, 
-                   chains = n_chains, cores = n_cores, iter = n_iter)
-
-model2_results_table <- fixef(m_responses2, summary = T, robust = F) %>% 
-  as.data.frame() #%>% tibble::rownames_to_column("variables")
-
-```
-
-```{r Exp2:ModelPlots, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-
-contrast_names2_le <- c("cUngrammatical" = "Ungrammaticality",
-                    "cAttractorPlural" = "Plural Attactor",
-                    "cVerbalAttractor" = "Verbal Attractor",
-                    "cUngrammatical:cAttractorPlural" = "Ungrammaticality * Plural Attractor",
-                    "cVerbalAttractor:cUngrammatical" = "Ungrammaticality * Verbal Attractor",
-                    "cVerbalAttractor:cAttractorPlural" = "Verbal Attractor * Plural Attractor",
-                    "cVerbalAttractor:cUngrammatical:cAttractorPlural" = "Verbal Attractor * Ungrammaticality * Plural Attractor")
-
-p_m_response_exp2 <- 
-  create_model_coefs_plot( m_responses2, 
-        plot_stats = T, map_names = contrast_names2_le,
-        expand_right = 4.5, expand_top = 1.5, x_stat_adjust = .75,
-        x_breaks = c(-3,-2,-1, 0, 1) ) + 
-        xlab("Estimate (probit)")
-
-p_m_response_exp2 <- p_m_response_exp2 + annotate(x=-3, xend=1, y=0, yend=0, lwd=0.25, geom="segment")
-
-p_m_response_exp2_exp2only <- 
-  create_model_coefs_plot( m_responses2_exp2only, 
-        plot_stats = T, map_names = contrast_names2_le,
-        expand_right = 4.5, expand_top = 1.5, x_stat_adjust = .75,
-        x_breaks = c(-3,-2,-1, 0, 1) ) + 
-        xlab("Estimate (probit)")
-
-p_m_response_exp2only <- p_m_response_exp2_exp2only + annotate(x=-3, xend=1, y=0, yend=0, lwd=0.25, geom="segment")
-
-```
-
-The aim of the Experiment 2 is to control for _form-driven processing strategies_ which may be employed by the participants in the processing of Turkish number agreement.
+Such a response strategy would lead to a larger number of `acceptable' responses in ungrammatical plural attractor conditions than in ungrammatical singular attractor conditions even when there is no interfering noun with plural morphology but, let's say, a plural verb.
+
+\hypertarget{experiment-2}{%
+\section{Experiment 2}\label{experiment-2}}
+
+The aim of the Experiment 2 is to control for \emph{form-driven processing strategies} which may be employed by the participants in the processing of Turkish number agreement.
 A processing mechanism that is driven by form itself, rather than the embedded linguistic features, would predict the comparable agreement attraction effects even when the attractor does not contain a possible nominal plural feature to create interference but contains a form-identical morpheme.
 To this end, we utilized syncretism between nominal and verbal plural marking in Turkish.
-Instead of genitive marked nouns, we used the verb of a object relative clauses as in \@ref(item:exp2Items).
+Instead of genitive marked nouns, we used the verb of a object relative clauses as in \ref{item:exp2Items}.
 We expect that under some conditions in which participants do not have sufficient information to rate sentences (un)acceptable, they will decide on the grammaticality of the sentence based on their memory of plural morpheme string, regardless of the feature itself.
@@
 
-_Form-driven processing strategies_ predicts that  we wanted to rule out the possibility of \textit{form-driven processing strategy}, namely participants deciding on the acceptability of a sentence using a memory of plural morpheme in the sentence when they do not have sufficient information to rate sentences (un)acceptable.
-
-## Participants
-
-We recruited 79 undergraduate students to participate in Experiment 2 in exchange for course credit.
-All participants were native speakers of Turkish, with an average age of `r printnum(mean(form_exp2$Age))` (range: `r min(form_exp2$Age)` - `r max(form_exp2$Age)`).
+\emph{Form-driven processing strategies} predicts that we wanted to rule out the possibility of \textit{form-driven processing strategy}, namely participants deciding on the acceptability of a sentence using a memory of plural morpheme in the sentence when they do not have sufficient information to rate sentences (un)acceptable.
+
+\hypertarget{participants-1}{%
+\subsection{Participants}\label{participants-1}}
+
+We recruited 79 undergraduate students to participate in Experiment 2 in exchange for course credit. All participants were native speakers of Turkish, with an average age of 21.46 (range: 18 - 31).
 Experiment were carried out following the Declaration of Helsinki and the regulations concerning ethics at research in Bo\u{g}azi\c{c}i University.
@@
 
-## Materials
+\hypertarget{materials-1}{%
+\subsection{Materials}\label{materials-1}}
 
@@
 (ii) the number agreement on the verb.
-Unlike Experiment 1, we used the verb of a nominalized relative clause (i.e. \textit{tuttukları}) as an attractor instead of a genitive marked noun. 
+Unlike Experiment 1, we used the verb of a nominalized relative clause (i.e.~\textit{tuttukları}) as an attractor instead of a genitive marked noun.
 We took advantage of syncretism between Turkish nominal and verbal plural marker.
@@
 All sentences started with a complex subject NP like \textit{`the cook that they hired'} (\textit{tuttukları aşçı}), in which the verb of the relative clause functioned as the attractor.
-Because the head noun was singular in all conditions, sentences with plural verb agreement were ungrammatical.
+Because the head noun was singular in all conditions, sentences with plural verb agreement were ungrammatical.\\
 We have used the same verbs, and have not changed the distribution of verb types. We also utilized the same or similar adverbials in length.
@@
 
-## Procedure
+\hypertarget{procedure-1}{%
+\subsection{Procedure}\label{procedure-1}}
 
@@
 Between each word, participants saw a blank screen for 100 ms.
-Participants pressed the key `P' for `\textit{acceptable}' and `Q' for `\textit{unacceptable}'.
+Participants pressed the key \texttt{P\textquotesingle{}\ for}\textit{acceptable}' and \texttt{Q\textquotesingle{}\ for}\textit{unacceptable}'.
 Within instructions, they were told to provide an acceptability rating before 5,000 ms deadline. During the experiment, they were reminded to respondfaster if they did not respond within 5,000 ms.
@@
 
-## Analysis
+\hypertarget{analysis-1}{%
+\subsection{Analysis}\label{analysis-1}}
 
@@
 this decision was made to answer our hypothesis that whether or not participants use the form of the plural suffix rather than the linguistic features.
-A presence of interaction between the attractor type (\textit{nominal} vs.
-\textit{verbal}) and the agreement attraction effect would indicate that people use the linguistic features rather than the form of the plural suffix.
-
-Similar to Experiment 1, we removed the data for all participants who did not exceed the threshold of 25 percentage points in 'yes' responses between the grammatical condition and the ungrammatical condition with singular attractors.
-As a result, we excluded `r stopifnot(length(bad_subjects2) == 1)` one participant from the Experiment 2, and `r length(bad_subjects)` participant from the Experiment 1.
-
-We used R packages brms [@brms] and rstan [@stan] to fit Bayesian hierarchical models [e.g., @GelmanHill2007].
+A presence of interaction between the attractor type (\textit{nominal} vs.~\textit{verbal}) and the agreement attraction effect would indicate that people use the linguistic features rather than the form of the plural suffix.
+
+Similar to Experiment 1, we removed the data for all participants who did not exceed the threshold of 25 percentage points in `yes' responses between the grammatical condition and the ungrammatical condition with singular attractors.
+As a result, we excluded one participant from the Experiment 2, and 10 participant from the Experiment 1.
+
+We used R packages brms (Bürkner, 2018) and rstan (Stan Development Team, 2019) to fit Bayesian hierarchical models (e.g., Gelman \& Hill, 2007).
 We aalyzed only experimental sentences, and used (i) grammaticality of the sentence, (ii) attractor number, and (iii) type of the plural suffix (i.e., experiment), as well as their interactions as predictors.
@@
 
-## Results
-
-\autoref{fig:exp2AvgResponse} shows the average proportions of 'acceptable' responses by experimental conditions for Experiment 2. 
+\hypertarget{results-1}{%
+\subsection{Results}\label{results-1}}
+
+\autoref{fig:exp2AvgResponse} shows the average proportions of `acceptable' responses by experimental conditions for Experiment 2.
 It shows that ungrammatical sentences with plural attractors are rated as acceptable
-(M = `r exp2_cur_entry1$M`, 
-SE = `r exp2_cur_entry1$SE`) 
+(M = 0.05,
+SE = 0.01)
 as their counterparts with singular attractors
-(M = `r exp2_cur_entry2$M`, 
-SE = `r exp2_cur_entry2$SE`).
-The lack of effect (`r sprintf("%0.2f", exp2_cur_entry1$M-exp2_cur_entry2$M)`) compared to the magnitude of the effect in Experiment 1 (`r sprintf("%0.2f", exp2_cur_entry1$M-exp2_cur_entry2$M)`) indicates that the verbal plural morpheme does not trigger an illusionary agreement.
+(M = 0.06,
+SE = 0.01). The lack of effect (-0.01) compared to the magnitude of the effect in Experiment 1 (-0.01) indicates that the verbal plural morpheme does not trigger an illusionary agreement.
 Accuracy rates for grammatical conditions were nearly equal
-(M = `r exp2_cur_entry3$M` and `r exp2_cur_entry4$M`, 
-SE = `r exp2_cur_entry3$SE` and `r exp2_cur_entry4$SE`, for singular and plural attractors respectively).
-
-```{r exp2AvgResponse, fig.height=3 ,fig.cap="Estimates and 95% credible intervals for the regression coefficients for Experiment 1 and Experiment 2.
-Within-subject 95% confidence intervals in brackets."}
-# \\cite{Cousineau:2005,Morey:2008}
-print(p_avg_resp2)
-
-```
+(M = 0.91 and 0.94,
+SE = 0.01 and 0.01, for singular and plural attractors respectively).
+
+\begin{figure}
+\centering
+\includegraphics{ongoing_paper_files/figure-latex/exp2AvgResponse-1.pdf}
+\caption{\label{fig:exp2AvgResponse}Estimates and 95\% credible intervals for the regression coefficients for Experiment 1 and Experiment 2. Within-subject 95\% confidence intervals in brackets.}
+\end{figure}
 
 A Bayesian GLM assuming a Bernoulli distribution with a probit-link function was fit to participants' `acceptable' responses.
-The model's estimates and 95\% credible intervals are shown in \@ref(fig:exp2ResponseModel).
-The main effect of \textit{ungrammaticality} (`r print_estimate_with_ci( m_responses2, 'cUngrammatical' )`) indicates that, 
+The model's estimates and 95\% credible intervals are shown in \ref{fig:exp2ResponseModel}.
+The main effect of \textit{ungrammaticality} (\(\hat{\beta}=-3.41;\) \(CI=[-3.64; -3.19];\) \(P(\beta<0)> .999\)) indicates that,
 on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences.
-Meanwhile, there was no evidence for an interaction between \textit{ungrammaticality} and \textit{attractor number} (`r print_estimate_with_ci( m_responses2, 'cUngrammatical:cAttractorPlural')`), indicating
+Meanwhile, there was no evidence for an interaction between \textit{ungrammaticality} and \textit{attractor number} (\(\hat{\beta}=-0.04;\) \(CI=[-0.32; 0.24];\) \(P(\beta<0)= .60\)), indicating
 a similar effect of attractor number in ungrammatical conditions compared to grammatical conditions, and thus no number agreement attraction effect.
-Importantly, the negative effect between \textit{the presence of the verbal plural}, \textit{ungrammaticality} and \textit{attractor number} (`r print_estimate_with_ci( m_responses2, 'cVerbalAttractor:cUngrammatical:cAttractorPlural')`) indicated that the plural morpheme on the verb of the object relative clause lowered the agreement attraction effects.
-
-```{r exp2ResponseModel, fig.height=3 ,fig.cap="Estimates and 95% credible intervals for the regression coefficients for a model of Experiment 1 and Experiment 2."}
-print(p_m_response_exp2)
-
-```
-
-```{r exp2ResponseModelExp2Only, fig.cap="Estimates and 95% credible intervals for the regression coefficients for Experiment 2.", fig.height=1.5}
-print(p_m_response_exp2only)
-
-```
-
-## Discussion
+Importantly, the negative effect between \textit{the presence of the verbal plural}, \textit{ungrammaticality} and \textit{attractor number} (\(\hat{\beta}=-1.08;\) \(CI=[-1.56; -0.61];\) \(P(\beta<0)> .999\)) indicated that the plural morpheme on the verb of the object relative clause lowered the agreement attraction effects.
+
+\begin{verbatim}
+## Warning in is.na(x): is.na() (liste veya vekt"or) olmayan 'expression' tipinin
+\end{verbatim}
+
+\begin{figure}
+\centering
+\includegraphics{ongoing_paper_files/figure-latex/exp2ResponseModel-1.pdf}
+\caption{\label{fig:exp2ResponseModel}Estimates and 95\% credible intervals for the regression coefficients for a model of Experiment 1 and Experiment 2.}
+\end{figure}
+
+\begin{verbatim}
+## Warning in is.na(x): is.na() (liste veya vekt"or) olmayan 'expression' tipinin
+\end{verbatim}
+
+\begin{figure}
+\centering
+\includegraphics{ongoing_paper_files/figure-latex/exp2ResponseModelExp2Only-1.pdf}
+\caption{\label{fig:exp2ResponseModelExp2Only}Estimates and 95\% credible intervals for the regression coefficients for Experiment 2.}
+\end{figure}
+
+\hypertarget{discussion-1}{%
+\subsection{Discussion}\label{discussion-1}}
 
@@
 
-<!--
-
-However, in Turkish embedded clauses, where genitive subjects can be seen, the number agreement works differently than the matrix level agreement.
-When the genitive subject of an embedded clause is marked with plural it is ungrammatical to have plural marking on the verb.
-This prohibition in return means that the genitive subjects should not create an expectation for a plural marked verb, which was believed to be the reason for the agreement attraction in @LagoEtAl2018.
-
--->
-
 As for the marking and morphing theories, the results of experiment 2 are completely expected.
@@
 
-<!-- By depth, I mean how many root nodes between the plural item and the root node. I always understood as such. -->
-
-# General Discussions
+\hypertarget{general-discussions}{%
+\section{General Discussions}\label{general-discussions}}
 
@@
 Our results align with the already existing theories that argue for the role of structural embedding in agreement attraction: MMT.
-Following the minimalist framework, I assume the following trees as in \@ref(syntax:genposs) and \@ref(syntax:orc).
+Following the minimalist framework, I assume the following trees as in \ref{syntax:genposs} and \ref{syntax:orc}.
 Since the plural containing item is embedded deeper in the tree, the verb within the object relative clause would contribute less than the genitive marked NP.
 
-<!-- Utku: I do not think you assume this, that is why I used first person pronoun here.
-we may not include this part, or write something entirely different, but I wanted to be as clear as possible with my assumption.
-Because I know you are going to ask about them :D  -->
 \begin{multicols}{2}
@@
 
-<!-- utku todo: find the analysis for dp-gen-pos for turkish from aygen phd thesis. RC and the NP must be sister correct that.-->
-
 Additionally, our results suggest fine-tuning within the cue-based retrieval explanation.
@@
 We observed number agreement attraction with nominal plural morphemes in experiment 1, but not with verbal plural morphemes in experiment 2.
-In Experiment 1, our findings were parallel to those of @LagoEtAl2018 with unambiguously possessive marked heads.
+In Experiment 1, our findings were parallel to those of Lago et al.
+(2018) with unambiguously possessive marked heads.
 In Experiment 2, we failed to observe number agreement attraction effects with object relative clause attractors.
@@
 
-# References
-```{r create_r-references}
-r_refs(file = "r-references.bib")
-```
+\hypertarget{references}{%
+\section{References}\label{references}}
 
@@
 
-<div id="refs" custom-style="Bibliography"></div>
+\hypertarget{refs}{}
+\begin{cslreferences}
+\leavevmode\hypertarget{ref-AvetisyanEtAl:2020}{}%
+Avetisyan, S., Lago, S., \& Vasishth, S. (2020). Does case marking affect agreement attraction in comprehension? \emph{Journal of Memory and Language}, \emph{112}, 104087.
+
+\leavevmode\hypertarget{ref-BadeckerKuminiak:2007}{}%
+Badecker, W., \& Kuminiak, F.
+(2007).
+Morphology, agreement and working memory retrieval in sentence production: Evidence from gender and case in Slovak.
+\emph{Journal of Memory and Language}, \emph{56}(1), 65--85.
+
+\leavevmode\hypertarget{ref-BergenGibson:2012}{}%
+Bergen, L., \& Gibson, E. (2012). Agreement errors as rational encoding errors. In \emph{Poster presented at the 25th annual cuny conference on human sentence processing, new york, ny}.
+
+\leavevmode\hypertarget{ref-BockEberhard:1993}{}%
+Bock, K., \& Eberhard, K.
+M.
+(1993).
+Meaning, sound and syntax in english number agreement.
+\emph{Language and Cognitive Processes}, \emph{8}(1), 57--99.
+\url{https://doi.org/10.1080/01690969308406949}
+
+\leavevmode\hypertarget{ref-Bock1991}{}%
+Bock, K., \& Miller, C. A. (1991). Broken agreement. \emph{Cognitive Psychology}, \emph{23}(1), 45--93.
+
+\leavevmode\hypertarget{ref-brms}{}%
+Bürkner, P.-C. (2018). \emph{Advanced Bayesian multilevel modeling with the R package brms}. \emph{The R Journal} (Vol. 10, pp. 395--411). \url{https://doi.org/10.32614/RJ-2018-017}
+
+\leavevmode\hypertarget{ref-Dillon2013a}{}%
+Dillon, B., Clifton, C., \& Frazier, L.
+(2013).
+Pushed aside: Parentheticals, memory and processing.
+\emph{Language, Cognition and Neuroscience}, \emph{29}(4), 483--498.
+\url{https://doi.org/10.1080/01690965.2013.866684}
+
+\leavevmode\hypertarget{ref-Eberhard:1997}{}%
+Eberhard, K. M. (1997). The marked effect of number on subject--verb agreement. \emph{Journal of Memory and Language}, \emph{36}(2), 147--164.
+
+\leavevmode\hypertarget{ref-EberhardEtAl:2005}{}%
+Eberhard, K. M., Cutting, J. C., \& Bock, K. (2005). Making syntax of sense: Number agreement in sentence production. \emph{Psychological Review}, \emph{112}(3), 531.
+
+\leavevmode\hypertarget{ref-FerreiraBaileyFerraro:2002}{}%
+Ferreira, F., Bailey, K. G. D., \& Ferraro, V. (2002). Good-Enough Representations in Language Comprehension. \emph{Current Directions in Psychological Science}, \emph{11}(1).
+
+\leavevmode\hypertarget{ref-FranckColonnaRizzi:2015}{}%
+Franck, J., Colonna, S., \& Rizzi, L.
+(2015).
+Task-dependency and structure-dependency in number interference effects in sentence comprehension.
+\emph{Frontiers in Psychology}, \emph{6}(MAR), 1--15.
+\url{https://doi.org/10.3389/fpsyg.2015.00349}
+
+\leavevmode\hypertarget{ref-FranckEtAl:2002}{}%
+Franck, J., Vigliocco, G., \& Nicol, J. (2002). Subject-verb agreement errors in french and english: The role of syntactic hierarchy. \emph{Language and Cognitive Processes}, \emph{17}(4), 371--404.
+
+\leavevmode\hypertarget{ref-GelmanHill2007}{}%
+Gelman, A., \& Hill, J. (2007). \emph{Data Analysis Using Regression and Multilevel/Hierarchical Models}. Cambridge, UK: Cambridge University Press.
+
+\leavevmode\hypertarget{ref-GibsonThomas:1999}{}%
+Gibson, E., \& Thomas, J. (1999). Memory Limitations and Structural Forgetting: The Perception of Complex Ungrammatical Sentences as Grammatical. \emph{Language and Cognitive Processes}, \emph{14}(3).
+
+\leavevmode\hypertarget{ref-HammerlyEtAl:2019}{}%
+Hammerly, C., Staub, A., \& Dillon, B.
+(2019).
+The grammaticality asymmetry in agreement attraction reflects response bias: Experimental and modeling evidence.
+\emph{Cognitive Psychology}, \emph{110}, 70--104.
+
+\leavevmode\hypertarget{ref-Haussler2009}{}%
+Häussler, J., \& Bader, M. (2009). Agreement checking and number attraction in sentence comprehension: Insights from german relative clauses. \emph{Trav. Cercle Linguist. Prague}, \emph{7}.
+
+\leavevmode\hypertarget{ref-JagerEngelmannVasishth:2017}{}%
+Jäger, L.
+A., Engelmann, F., \& Vasishth, S.
+(2017).
+Similarity-based interference in sentence comprehension: Literature review and Bayesian meta-analysis.
+\emph{Journal of Memory and Language}, \emph{94}, 316--339.
+\url{https://doi.org/10.1016/j.jml.2017.01.004}
+
+\leavevmode\hypertarget{ref-kornfilt2009dom}{}%
+Kornfilt, J. (2009). DOM and two types of dsm in turkish. In \emph{Differential subject marking} (pp. 79--111). Springer.
+
+\leavevmode\hypertarget{ref-LagoEtAl2018}{}%
+Lago, S., Felser, C., Gračanin-Yuksek, M., Demir, O., Kırkıcı, B., \& Şafak, D.
+F.
+(2018).
+Straight from the horse's mouth: Agreement attraction effects with Turkish possessors.
+\emph{Linguistic Approaches to Bilingualism}, \emph{12}(1), 1--29.
+\url{https://doi.org/10.1075/lab.17019.lag}
+
+\leavevmode\hypertarget{ref-LagoEtAl:2015}{}%
+Lago, S., Shalom, D.
+E., Sigman, M., Lau, E.
+F., \& Phillips, C.
+(2015).
+Agreement attraction in Spanish comprehension.
+\emph{Journal of Memory and Language}, \emph{82}, 133--149.
+\url{https://doi.org/10.1016/j.jml.2015.02.002}
+
+\leavevmode\hypertarget{ref-Levy2008}{}%
+Levy, R. (2008). Expectation-based syntactic comprehension. \emph{Cognition}, \emph{106}(3), 1126--1177. \url{https://doi.org/10.1016/j.cognition.2007.05.006}
+
+\leavevmode\hypertarget{ref-LewisVasishth2005}{}%
+Lewis, R.
+L., \& Vasishth, S.
+(2005).
+An activation-based model of sentence processing as skilled memory retrieval.
+\emph{Cognitive Science}, \emph{29}(3), 375--419.
+\url{https://doi.org/10.1207/s15516709cog0000_25}
+
+\leavevmode\hypertarget{ref-NicenboimEtAl:2018}{}%
+Nicenboim, B., Vasishth, S., Engelmann, F., \& Suckow, K.
+(2018).
+Exploratory and confirmatory analyses in sentence processing: A case study of number interference in german.
+\emph{Cognitive Science}, \emph{42}, 1075--1100.
+
+\leavevmode\hypertarget{ref-NicolEtAl:2016}{}%
+Nicol, J. L., Barss, A., \& Barker, J. E. (2016). Minimal interference from possessor phrases in the production of subject-verb agreement. \emph{Frontiers in Psychology}, \emph{7}, 548.
+
+\leavevmode\hypertarget{ref-Nicoletal:1997}{}%
+Nicol, J. L., Forster, K. I., \& Veres, C. (1997). Subject--verb agreement processes in comprehension. \emph{Journal of Memory and Language}, \emph{36}(4), 569--587.
+
+\leavevmode\hypertarget{ref-OteroKintsch:1992}{}%
+Otero, J., \& Kintsch, W. (1992). Failures to detect contradictions in a text: What readers believe versus what they read. \emph{Psychological Science}, \emph{3}(4), 229--236.
+
+\leavevmode\hypertarget{ref-ParkerEtAl:2015}{}%
+Parker, D., Lago, S., \& Phillips, C.
+(2015).
+Interference in the processing of adjunct control.
+\emph{Frontiers in Psychology}, \emph{6}(September), 1--13.
+\url{https://doi.org/10.3389/fpsyg.2015.01346}
+
+\leavevmode\hypertarget{ref-PaspaliMarinis:2020}{}%
+Paspali, A., \& Marinis, T. (2020). Gender agreement attraction in greek comprehension. \emph{Frontiers in Psychology}, \emph{11}, 717.
+
+\leavevmode\hypertarget{ref-PatsonHusband:2016}{}%
+Patson, N. D., \& Husband, E. M. (2016). Misinterpretations in agreement and agreement attraction. \emph{The Quarterly Journal of Experimental Psychology}, \emph{69}(5), 950--971.
+
+\leavevmode\hypertarget{ref-PearlmutterGarnseyBock:1999}{}%
+Pearlmutter, N. J., Garnsey, S. M., \& Bock, K. (1999). Agreement Processes in Sentence Comprehension. \emph{Journal of Memory and Language}, \emph{41}.
+
+\leavevmode\hypertarget{ref-PhillipsEtAl:2011}{}%
+Phillips, C., Wagers, M., \& Lau, E.
+F.
+(2011).
+Grammatical Illusions and Selective Fallibility in Real-Time Language Comprehension.
+\emph{Syntax and Semantics 37: Experiments at the Interfaces}, \emph{37}(2011), 53--186.
+
+\leavevmode\hypertarget{ref-ReifegersteEtAl:2016}{}%
+Reifegerste, J., Hauer, F., \& Felser, C.
+(2016).
+Agreement processing and attraction errors in aging: evidence from subject-verb agreement in German.
+\emph{Aging, Neuropsychology, and Cognition}, \emph{00}(00), 1--31.
+\url{https://doi.org/10.1080/13825585.2016.1251550}
+
+\leavevmode\hypertarget{ref-Slioussar:2016}{}%
+Slioussar, N., \& Malko, A. (2016). Gender agreement attraction in russian: Production and comprehension evidence. \emph{Frontiers in Psychology}, \emph{7}, 1651.
+
+\leavevmode\hypertarget{ref-stan}{}%
+Stan Development Team. (2019). RStan: The R interface to Stan. Retrieved from \url{http://mc-stan.org/}
+
+\leavevmode\hypertarget{ref-TannerEtAl:2014}{}%
+Tanner, D., Nicol, J., \& Brehm, L.
+(2014).
+The time-course of feature interference in agreement comprehension: Multiple mechanisms and asymmetrical attraction.
+\emph{Journal of Memory and Language}, \emph{76}, 195--215.
+
+\leavevmode\hypertarget{ref-TuckerEtAl:2015}{}%
+Tucker, M.
+A., Idrissi, A., \& Almeida, D.
+(2015).
+Representing number in the real-time processing of agreement: Self-paced reading evidence from Arabic.
+\emph{Frontiers in Psychology}, \emph{6}(MAR), 1--21.
+\url{https://doi.org/10.3389/fpsyg.2015.00347}
+
+\leavevmode\hypertarget{ref-ViglioccoEtAl:1995}{}%
+Vigliocco, G., Butterworth, B., \& Semenza, C.
+(1995).
+Constructing subject-verb agreement in speech: The role of semantic and morphological factors.
+\emph{Journal of Memory and Language}, \emph{34}(2), 186--215.
+
+\leavevmode\hypertarget{ref-WagersEtAl:2009}{}%
+Wagers, M.
+W., Lau, E.
+F., \& Phillips, C.
+(2009).
+Agreement attraction in comprehension: Representations and processes.
+\emph{Journal of Memory and Language}, \emph{61}(2), 206--237.
+\url{https://doi.org/10.1016/j.jml.2009.04.002}
+\end{cslreferences}
+
 \endgroup
+
+\end{document}

### 2020-09-01 ongoing_draft/ongoing_paper.Rmd
Another merge with PLs version.

@@
   chunk_output_type: console
-keep_tex: FALSE
-keep_md: FALSE
+keep_tex: TRUE
+keep_md: TRUE
 ---
@@
 
-library(car, warn.conflicts = FALE)
+library(car, warn.conflicts = FALSE)
 library(MASS)
